### 2022-01-28 popl2022.tex
m

\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

    \acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
\acmArticle{1}
\acmYear{2018}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\copyrightyear{2018}           %% If different from \acmYear

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Note: Authors migrating a paper from PACMPL format to traditional
%% SIGPLAN proceedings format must update the '\documentclass' and
%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\usepackage{enumerate}
\usepackage[utf8]{inputenc}
\usepackage{parcolumns}
\usepackage[spanish,english]{babel}
\usepackage{amsmath}
\usepackage{csquotes}
\usepackage{varwidth}
\newcommand{\key}[1]{\textcolor{purple}{\code{#1}}}
\newcommand{\jskey}[1]{\textcolor{blue}{\code{#1}}}
\newcommand{\es}{\textcolor{black}{\ensuremath{{es}}}}
\definecolor{palered-violet}{rgb}{0.86, 0.44, 0.58}
\definecolor{bittersweet}{rgb}{1.0, 0.44, 0.37}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\definecolor{persianplum}{rgb}{0.44, 0.11, 0.11}
\newcommand{\hide}[1]{}
\newcommand{\siderule}[1]{
\code{\footnotesize{\textcolor{mGray}{#1}}}}
\usepackage{adjustbox}
\usepackage{ebproof}
\usepackage{cancel}
\newcommand{\env}{\code{\mathcal{E}}}

\usepackage{xcolor}
\definecolor{javablue}{rgb}{0.25,0,1} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc
\definecolor{mGray}{rgb}{0.4,0.4,0.4}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{huntergreen}{rgb}{0.33, 0.42, 0.18}

\definecolor{darkpastelred}{rgb}{0, 0, 0}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}
\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
\definecolor{red}{rgb}{0.6,0,0} 
\definecolor{blue}{rgb}{0,0,0.6}
\definecolor{green}{rgb}{0,0.8,0}
\definecolor{cyan}{rgb}{0.0,0.6,0.6}
\definecolor{cloudwhite}{rgb}{0.9412, 0.9608, 0.8471} 
\definecolor{davysgrey}{rgb}{0.33, 0.33, 0.33}
\definecolor{deepfuchsia}{rgb}{0.76, 0.33, 0.76}
\definecolor{deeplilac}{rgb}{0.6, 0.33, 0.73}
\definecolor{deepskyblue}{rgb}{0.0, 0.75, 1.0}
\definecolor{indianred}{rgb}{0.8, 0.36, 0.36}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
\usepackage{wrapfig}
\newcommand{\effect}{\textcolor{black}{\ensuremath{\mathrm{\Phi}}}}
\definecolor{color_pure}{RGB}{3,35,14}
\newcommand\pure[1]{ \textcolor{black}{#1}}
\usepackage{epigraph}
\newcommand{\anyevent}[1]{{\textcolor{darkred}
{\underline{\textbf{\footnotesize #1}}}}}
\newcommand{\seq}{\cdot}
\newcommand{\choice}{\vee}
\newcommand{\fullname}{Integrated Dependent Effects}
\newcommand{\name}{integrated effects}
\newcommand{\code}[1]{{\tt{\ensuremath{\m{#1}}}}}
\newcommand{\codeme}[1]{{\tt{\ensuremath{#1}}}}
\newcommand{\esn}[2]{\ensuremath{#1^{#2}}}
\newcommand{\empt}{\textcolor{black}{\ensuremath{\epsilon}}}
\newcommand{\bott}{\textcolor{black}{\ensuremath{\bot}}}
\newcommand{\CONTAIN}{\sqsubseteq}
\newcommand{\underscore}{\textcolor{vividauburn}{\code{\_}}}
\newcommand{\m}{\mathit}  
\newcommand{\toolName}{Tvide}
\def\defeq{\ensuremath{\,\triangleq}}
\definecolor{regalia}{rgb}{0.32, 0.18, 0.5}
\newcommand{\inclusion}{\code{\mathcal{I}}}
\definecolor{mypink}{RGB}{219, 48, 122}
\definecolor{darklavender}{rgb}{0.45, 0.31, 0.59}
\definecolor{deepcerise}{rgb}{0.85, 0.2, 0.53}
\newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}.}
\newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}

\newcommand\theoref[1]{Theorem~\textcolor{blue}{\ref{#1}}}
\newcommand\lemmaref[1]{Lemma~\textcolor{blue}{\ref{#1}}}
\newcommand\appref[1]{Appendix~\textcolor{blue}{\ref{#1}}}
\newcommand\defref[1]{Definition~\textcolor{blue}{\ref{#1}}}
\newcommand\algoref[1]{Algorithm~\textcolor{blue}{\ref{#1}}}
\usepackage{listings}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, const, new, true, false, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{darklavender}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstset{
   language=JavaScript,
   %%backgroundcolor=\color{lightgray},
   extendedchars=true,
   basicstyle=\footnotesize\ttfamily,
   showstringspaces=false,
   showspaces=false,
%frame=single
numbers=left,   
xleftmargin=1.5em, 
    numberstyle=\tiny\color{mGray},
   numbersep=10pt,
   tabsize=4,
   breaklines=true,
   showtabs=false,
   captionpos=b,
   keywordstyle=[2]\color{purple}\bfseries, %
   morekeywords=[2]{do, hiphop,every, loop,suspend, when, signal, end, present, nothing, emit,in, out, yield, module,abort, fork, par, run},
}

%\lstset{
%  frame=none,
%  xleftmargin=2pt,
%  stepnumber=1,
%  numbers=left,
%  numbersep=5pt,
%  numberstyle=\ttfamily\tiny\color[gray]{0.3},
%  belowcaptionskip=\bigskipamount,
%  captionpos=b,
%  escapeinside={*'}{'*},
%  language=JavaScript,
%  tabsize=2,
%  emphstyle={\bf},
%  stringstyle=\mdseries\rmfamily,
%  showspaces=false,
%  keywordstyle=\bfseries\rmfamily\color{deepcerise},
%  columns=flexible,
%  basicstyle=\small\sffamily,
%  showstringspaces=false,
%  morecomment=[l]\%,
%  keywordstyle=[2]\color{darklavender}, %
%  keywords={},
%    morekeywords=[2]{hiphop,emit, abour,async,Cmd,MorePlease,Sub,Success,Failure, Roll, Html, Random, NewFace, Int, String},
%  commentstyle=\color{black}\it %mypink
%}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}
\citestyle{acmauthoryear}   %% For author/year citations

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Automated Timed Temporal Verification for a Mixed Sync-Async Concurrency Paradigm}

%% Automated Temporal Verification for Mixed Sync-Async Reactive Paradigm

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{(Anonymous Authors)}
%\author{Valerie B\'eranger}
%\affiliation{%
%  \institution{Inria Paris-Rocquencourt}
%  \city{Rocquencourt}
%  \country{France}
%}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Trovato and Tobin, et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract} 
To make reactive programming more concise and flexible, it is promising to deploy a mixed concurrency paradigm \cite{berry2020hiphop} that
integrates Esterel's synchrony and preemption \cite{berry1999constructive}  
with JavaScript's asynchrony \cite{madsen2017model}. 
%HipHop.js \cite{berry2020hiphop} is the first web language that 
Existing temporal verification techniques have not been designed to handle such a blending of two concurrency
models.
We propose a novel solution via a 
compositional 
Hoare-style forward verifier and a term rewriting system (TRS) on \emph{Timed Synchronous Effects} (TSE).

Firstly, we introduce TSE, a new effects logic, that extends \emph{Kleene Algebra} with value-dependent constraints, providing real-time bounds for logical-time synchronous traces \cite{von2017real}. 
Secondly, we establish an axiomatic semantics  for a core language \code{\lambda_{HH}}, generalising the mixed paradigm. 
% HipHop.js,  based on our effects logic. 
%Secondly, we formalise a set of construction rules to infer the program effects based on a . using a set of inductive rules
Thirdly, we present a purely algebraic TRS, to efficiently check language inclusions between expressive timed effects.  
To demonstrate the feasibility of our proposals, we prototype the  verification system; prove its correctness; investigate how it can help to debug errors related to both synchronous and asynchronous programs.

\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%

\ccsdesc[500]{Theory of computation~Logic}
\ccsdesc[300]{Theory of computation~Semantics and reasoning}
\ccsdesc[100]{Models of computation~Concurrency}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Temporal Verification,
Dependant Effects,
Hoare-style Forward Verifier,
Term Rewriting System,
Reactive System Design}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
\label{Introduction}

As it recently proposed,  reactive languages such as Hiphop.js\footnote{Hiphop.js is a JavaScript extension of Esterel \cite{berry1992esterel}
(or vice versa)
for reactive web applications: \url{https://www-sop.inria.fr/members/Colin.Vidal/hiphop/}.}   \cite{vidal2018hiphop,berry2020hiphop} are designed to be
based on a smooth integration of (i) Asynchronous concurrent programs, which perform interactions between components or with the environment with uncontrollable timing, such as network-based communication; (ii) Synchronous reactive programs, which react to external events in a conceptually instantaneous and deterministic way; and (iii) Preemption, the explicit cancellation and resumption of an ongoing orchestration subactivity.

%Recent research has

%One of the major difficulties of reactive web programming is \emph{callback hell} \cite{kambona2013evaluation}, which is the problem of appropriately handling the asynchronous events appearing in program executions. To avoid using callbacks, efforts have been made: 
%%\cite{madsen2017model}
%(i) JavaScript has provided  \emph{promises} and \emph{async/await} primitives, making it possible to chain asynchronous actions in a specific sequential order; (ii) High-level abstractions such as \emph{Functional Reactive Programming} has been carried up to the web applications \cite{czaplicki2013asynchronous}, which adopts the data flow declarative programming style: when a variable is modified, any expression that references it is implicitly reevaluated. 
%
%To go further with this problem and achieve a better web orchestration,  the language Hiphop.js \cite{vidal2018hiphop,berry2020hiphop} is designed to be a JavaScript extension of Esterel \cite{berry1992esterel} (or vice versa) based on a smooth integration of (i) Asynchronous concurrent programs, which perform interactions between components or with the environment with uncontrollable timing, such as network-based communication; (ii) Synchronous reactive programs, which react to external events in a conceptually instantaneous and deterministic way; and (iii) Preemption, the explicit cancellation and resumption of an ongoing orchestration subactivity.

\textit{"Such a combination makes reactive programming more powerful and flexible than plain JavaScript because it makes the temporal geometry of complex executions explicit instead of hidden in implicit relations between state variables." \cite{berry2020hiphop}}

Given such a multi-paradigm (mixed Sync-Async) concurrency model, the verification of its temporal behaviour becomes engaging and challenging. 
%which, however, has not been intensely exploited. 
Existing techniques are based on a transformation to convert the asynchronous chunk into semantically equivalent synchronization\footnote{Usually the transformation is incomplete, i.e., not all the asynchronous programs can be translated into a semantically equivalent synchronization.}; then reason about the behaviours based on the synchronous semantics \cite{damian2019communication,gleissenthall2019pretend,tarawneh2018formal}. This approach (i) suffers from the limited expressiveness, restricted by finite-state automata (FSA); (ii) lacks the modularity to reason about programs compositionally; (iii) loses time awareness due to the conversion to synchronous models; and (iv) has the \emph{state explosion problem}  when proving language inclusions between FSA.
 %finite-state automata
 % PSPACE-complete complexity

To tackle the above issues and exploit the best of both synchronous and asynchronous concurrency models, we propose a novel temporal specification language, which enables a compositional verification via a  Hoare-style forward verifier and a term rewriting system (TRS). 
More specifically, we specify system behaviours in the form of \emph{Timed Synchronous Effects (TSE)}, which integrates the Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous,broda2015deciding} with dependent values and arithmetic constraints, 
%gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
to 
%capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
provide real-time abstractions into traditional synchronous verification. 
%Resource usages, provided by a \emph{dynamic ticks}\cite{von2017real}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
For example, one safety property, \textit{"The event \anyevent{Done} will be triggered no later than one second"}\footnote{For simplicity, we  follow the convention of JavaScript, and use integer values to represent milliseconds in this paper, while it can be easily extended to real numbers and other time measurement units.}, is expressed in our effects logic as: 
\begin{align*}
&\code{\effect \defeq \  0 {\leq} t {<}1000 : (\{{\anyevent{}\}^\star} \cdot \{\anyevent{Done}\} ) \# t}.
\end{align*}  
%The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
%and .
%which replaces temporal operators by time-constrained versions from 
Here, \code{\#} is the parallel operator specifying the \emph{real-time} constraints for the \emph{logical-time} sequences \cite{von2017real}; 
curly braces \code{\{\}} enclose a single  logical-time instance\footnote{A time instance is a set of signals (possible empty) with status, logically concurring at the same time (cf. {\secref{subsec:Specification_language}}).}; 
Kleene star \code{\star} denotes trace repetition.
The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1000)}\ }\anyevent{Done}' in metric temporal logic (MTL), reads \textit{"within one second, \anyevent{Done} finally happens"}. Moreover, the time bounds can be dependent on the program inputs. For example, we express, the effects of \code{send(d)} as:
\begin{align*}
&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5000 \wedge  0 {\leq} t {<} d) : (\{{\anyevent{Send}\} \# t)} \cdot \{\anyevent{Done}\}}.
\end{align*}  
The \code{send} method takes a parameter \code{d}, and \anyevent{Send}s out a message at time \code{t}.  
The above formula  \code{\effect^{send (d)}} indicates that the input  \code{d} is positive and smaller or equal to \code{5000}; the method generates a finite trace, with the first time instance containing the event \anyevent{Send}, followed by a second time instance containing the event \anyevent{Done}; and the instance \code{\{}\anyevent{Send}\code{\}} takes a no more than \code{d} milliseconds delay to finish. 
Although these examples are simple, they show the benefits of deploying value-dependent time bounds. Intuitively, if traditional timed automata \cite{larsen1997uppaal} define an \emph{exact} transition system, our timed effects define a set (possibly infinite) of exact transition systems.

   %they already illustrate the gain of expressiveness from  existing temporal logics and traditional timed automata.

%properties beyond

Having the effects logic as the specification language, we are interested in the following verification problem: 
Given a program \code{\mathcal{P}}, and a temporal property \code{\effect^{\prime}}, does \code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds? In a typical verification
context, checking the inclusion/entailment between the program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.

Traditional ways of temporal verification either (i) rely on a translation from specification languages, such as LTL or CSP, into finite state automata \cite{sun2009pat}, which potentially gives rise to an exponential blow-up; %such as NFAs or DFAs; 
or (ii) use expressive automata to model the program logic directly, such as timed automata, which fails to capture the bugs introduced by the real implementation.

In this paper, we present a new solution of extensive temporal verification comprising: a front-end verifier computes the program's  temporal behaviour, to be the \code{\effect^{\mathcal{P}}}, via inference rules at the source level; %defining program evaluation syntactically; 
and a back-end TRS, to soundly check \code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}}.

The TRS  is inspired by Antimirov and Mosses’ algorithm \cite{antimirov1995rewriting}\footnote{Antimirov and Mosses' algorithm was designed for deciding the inequalities of regular expressions based on an 
complete 
axiomatic algorithm of the algebra of regular sets.} but solving the language inclusions between more expressive timed synchronous effects.  A TRS is a refutation method that normalizes expressions in such a way that checking their inclusion corresponds to an iterated process of checking the inclusion of their \emph{partial derivatives} \cite{antimirov1995partial}. 
Works based on such a TRS \cite{song2020automated,antimirov1995rewriting,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.

This work targets timed temporal verification, and to the best of the authors’ knowledge, it proposes the first axiomatic semantics and the first algebraic TRS (proven sound and complete) for the mixed synchronous and asynchronous concurrency model.  Our main contributions are:% as follows:

\begin{enumerate}
\item \textbf{The Timed Synchronous Effects:} We define the syntax ({\secref{subsec:Specification_language}}) and semantics ({\secref{subsec:Specification_Semantics}}) of timed synchronous effects, to be the specification language, which captures the target programs' behaviours and non-trivial temporal properties.

\item \textbf{Automated Forward Verifier:} Targeting a core language \code{\lambda_{HH}} ({\secref{subsec:Targetlanguage}}), we 
establish its axiomatic semantics via a set of inductive transition rules (\secref{sec:Verification}), enabling a compositional verifier to infer the program's effects. The verifier triggers the back-end solver TRS.

%which tightly The semantics model closely captures the temporal behaviour of the program,

\item \textbf{An Efficient TRS:}
We present the rewriting rules, to prove 
the inferred effects against given temporal properties, both expressed by timed synchronous effects (\secref{sec:Entailment_Prover}).

\item \textbf{Implementation and Evaluation:} We prototype the novel effects logic and the automated verification system, %on top of the HIP/SLEEK system\cite{chin2012automated}, 
%which is available online\cite{Demo}, 
prove the correctness, report on a case study investigating how it can help to debug errors related to both synchronous and asynchronous programs (\secref{subsec:Case_Studies}).

\end{enumerate}

\noindent\textbf{\textit{Organization.}} 
\secref{sec:Preliminaries} introduces the language features of synchronous Esterel programs, JavaScript promises, and the web reactive language HipHop.js. 
\secref{sec:Overview} gives motivation examples to highlight the key methodologies and contributions. 
\secref{sec:LanguageSpecifications} formally presents the core   language \code{\lambda_{HH}}, and the syntax and semantics of timed synchronous effects.
\secref{sec:Verification} presents the forward verification rules.
\secref{sec:Entailment_Prover} explains the TRS for effects inclusion checking, and displays the essential auxiliary functions. 
\secref{sec:Evaluation} demonstrates the implementation and cases studies. % via a number of . 
We discuss related works in \secref{sec:Related_work} and conclude in  \secref{sec:conclusion}. Omitted proofs can be found in the Appendix.

\section{Background: Esterel, Async-Await, and Hiphop.js }
\label{sec:Preliminaries}

It has been an active research topic to build flexible programming paradigms for reactive systems in different domains. This section identifies: i) \emph{Synchronous programming}, represented by Esterel  \cite{berry1992esterel}, ii) \emph{Asynchronous programming}, represented by JavaScript promises \cite{madsen2017model}, and iii) A \emph{mixed Sync-Async} paradigm, recently proposed by HipHop.js  \cite{berry2020hiphop}. Meanwhile, we discuss the real-world programming challenges of each paradigm; and show how our proposal addresses them in the cases studies, \secref{subsec:Case_Studies}.

 %language abstractions

\subsection{A Sense of Esterel: Synchronous and Preemptive}

%Synchronous programming (also synchronous reactive programming or SRP) is a computer programming paradigm supported by synchronous programming languages.

The principle of synchronous programming is to design a high-level abstraction where the timing characteristics of the electronic transistors are neglected \cite{esterel_wiki}. Such an abstraction makes reasoning about time a lot simpler, thanks to the notion of \emph{logical ticks}: a synchronous program reacts to its environment in a sequence of ticks, and computations within a tick are assumed to be instantaneous. 
As one of the first few well-known synchronous languages, Esterel's high-level imperative style allows the simple expression of parallelism and preemption, making it natural for programmers to specify and reason about control-dominated model designs. Esterel has found success in many safety-critical applications such as nuclear power plant control software. The success with real-time and embedded systems in domains that need strong guarantees can be partially attributed to its precise semantics and computational model  \cite{berry1992esterel,berry1999constructive, song2021synchronous}.

Esterel treats computation as a series of deterministic reactions to external signals. All parts of a reaction complete in a single, discrete-time step called an \emph{instance}. Besides, instances exhibit deterministic concurrency; each reaction may contain concurrent threads without execution order affecting the computation result. Primitive constructs execute in zero time except for the \code{yield} (pause) statement. Hence, time flows as a sequence of logical instances separated by explicit pauses. In each instance, several elementary instantaneous computations take place simultaneously.

\begin{lstlisting}
fork {emit A; yield; emit B; emit C} par {emit E; yield; emit F; yield; emit G}
\end{lstlisting}

The synchronous parallelism in Esterel is constructed by the \code{\m{fork} \{...\} \m{par}  \{...\}  } statement. 
It remains active as long as one of its branches remains active, 
% unless some branch exits a trap, 
and it terminates when both branches are terminated. The branches can terminate in different instances, and wait for the last one to terminate.
As the above example shows, the first branch generates effects $\{\textbf{A}\} \cdot \{\textbf{B}, \textbf{C}\}$ while the second branch generates effects $\{\textbf{E}\} \cdot \{\textbf{F}\} \cdot \{\textbf{G}\}$; then the final effects should be $\{\textbf{A},\textbf{E}\}\cdot \{\textbf{B}, \textbf{C}, \textbf{F}\} \cdot \{\textbf{G}\}$.

To maintain determinism and synchrony, evaluation in one thread of execution may affect code arbitrarily far away in the program. In other words, there is a strong relationship between signal status and control propagation: a signal status determines which branch of a \code{present} test is executed, which in turn determines which \code{emit} statements are executed (See \secref{subsec:Targetlanguage} for the language syntax). 
%For instance, selecting a particular branch of execution in one thread may immediately unblock a different thread of execution. 
%The selection of the other branch may render the entire program invalid\citeref{florence2019calculus}. 
The first semantic challenge of programming Esterel is the \emph{Logical Correctness} issue, caused by these non-local executions, which is simply the requirement that there exists precisely \textbf{one} status for each signal. For example, consider the program below:

\begin{lstlisting}
signal S1 in present S1 then nothing else emit S1 end present end signal
\end{lstlisting}

If the local signal {\textbf{S1}} were \emph{present}, the program would take the first branch of the condition, and the program would terminate without having emitted {\textbf{S1}} (\code{nothing} leaves \code{\textbf{S1}} with   \emph{absent}). If \code{\textbf{S1}} were absent, the program would choose the second branch and emit the signal. Both executions lead to a contradiction. Therefore there are no valid assignments of signals in this program. This program is logically incorrect.

\begin{lstlisting}
signal S1 in present S1 then emit S1 else nothing end present end signal
\end{lstlisting}

Consider the revised program above. If the local signal {\textbf{S1}} were present, the conditional would take the first branch, and  {\textbf{S1}} would be emitted, justifying
the choice of signal value. 
If {\textbf{S1}} were absent, the signal would not be emitted, and the choice of absence is also justified. Thus there are two possible assignments to the signals in this program, which is also logically incorrect.

\begin{wrapfigure}{R}{0.41\columnwidth}
    \vspace{-1mm}
\centering
\begin{lstlisting}
module a_loop: output A,B,C;
  emit A;
  loop 
  	emit B; yield; emit C
  end loop  
end module
\end{lstlisting}  
     \vspace{-1mm}
 \caption{A Loop Example in Esterel \cite{song2021synchronous}.} 
  \label{fig:loop1}
       \vspace{-1mm}
\end{wrapfigure}

Esterel's instantaneous nature requires a special distinction when it comes to loop statements, which increases the difficulty of the effects invariants inference.  
As shown in \figref{fig:loop1}, the program firstly emits signal {\textbf{A}}, then enters into a loop which emits signal \code{\textbf{B}} followed by a \code{\m{yield}} followed by emitting signal {\textbf{C}} at the end. 
The effects of it is $ \{\textbf{A}, \textbf{B}\} \cdot \{ \textbf{B}, \textbf{C}\} \cdot \{ \textbf{B}, \textbf{C}\} \cdot \{ \textbf{B}, \textbf{C}\} ...$,
which says that in the first time instance, signals {\textbf{A}} and {\textbf{B}} will be present, 
as there is no explicit yield between $emit\ \textbf{A}$ and $emit\ \textbf{B}$; 
then for the following instances (in an infinite trace), signals {\textbf{B}} and {\textbf{C}} are present all the time, because after executing $emit\ \textbf{C}$, it immediately executes from the beginning of the loop, which is $emit\ \textbf{B}$.

 %one deals with concurrent processes that coordinate with each other.

Coordination in concurrent systems can result from information exchange, using messages circulating on channels with possible implied synchronization. In Esterel, it can also result from \emph{process preemption}  \cite{berry1993preemption}, which is a more implicit control mechanism that consists in denying the right to work to a process, either permanently (abortion, cf. \figref{fig:overview_eg1}) or temporarily (e.g. suspension). Preemption is particularly important in control-dominated reactive and real-time programming, where most of the works consist of handling interrupts and controlling computation.

%
%\begin{wrapfigure}{L}{0.4\columnwidth}
%    \vspace{-1mm}
%\centering
%\begin{lstlisting}
%suspend
%	loop emit A; yield; yield;
%	end loop
%when B end suspend
%\end{lstlisting}  
%     \vspace{-1mm}
% \caption{A Suspend Example in Esterel.} 
%  \label{fig:Suspend}
%       \vspace{5mm}
%\includegraphics[width=0.39\columnwidth]{suspend.png}
%        \vspace{-1mm}
%\caption{\label{fig:Suspend}Graphical Illustration of \figref{fig:Suspend}}
%        \vspace{0mm}
%\end{wrapfigure}
%
%
%\figref{fig:Suspend} presents a suspend statement, one of the preemptive operations in Esterel. When the preemption condition satisfied, it pauses the execution of a group of statements, and resume it from the next time instance. 
%As \figref{fig:Suspend_pbg} illustrates, without the preemption, the effects is a repeated pattern: \code{\{\textbf{A}\}\cdot\{\}\cdot\{\textbf{A}\}\cdot\{\} \cdot ...} . Due to the presence of signal \code{\textbf{B}}, it delays emission of \code{\textbf{A}} by one cycle (at {\textcircled{1}} and {\textcircled{2}}), and resumes from the next cycle.

While the flexibility they provide us, preemption primitives often with loose or complex semantics, making abstract reasoning difficult. 
Most existing languages offer a small set of preemption primitives, often insufficient to program reactive systems concisely.

\subsection{Asynchrony from JavaScript Promises: Async–Await}

\noindent \textit{"Who can wait quietly while the mud settles? Who can remain still until the moment of action?"}\\
\textcolor{white}{.}\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad \textit{ -- Laozi, Tao Te Ching}

A number of mainstream languages, such as C\code{\#}, JavaScript, Rust, and Swift, have recently added support for async–await and the accompanying promises abstraction\footnote{JavaScript's asynchrony arises in situations such as web-based user-interfaces, communicating with servers through HTTP requests, and non-blocking I/O.}, also known as \emph{futures} or \emph{tasks} \cite{bierman2012pause}. As an example, consider the JavaScript program in \figref{fig:json}, 
it uses the {\ttfamily{fs}} module (line 1) to load the file into a variable (line 6) using async/await syntax.

\begin{figure}[h]
    \vspace{-2mm}
\centering
\begin{lstlisting}
const fs = require('fs').promises;

async function read (filePath) {
	const task = fs.readFile(filePath);
    ... // do things that do not depend on the result of the loading file
    const data = await task; // block execution until the file is loaded
	... // logging or data processing of the Json file 
}
\end{lstlisting}  
     \vspace{-3mm}
 \caption{Using Async-Await in JavaScript.} 
  \label{fig:json}
       \vspace{-2mm}
\end{figure}

The function {\ttfamily{read}} accepts one argument, a string called {\ttfamily{filePath}}. As it is declared {\textbf{\color{blue}\ttfamily{async}}}, reading a file (line 4) does not block computations that do not depend on the result (line 5). The programmer {\textbf{\color{blue}\ttfamily{await}}}s the task when they need the result to be ready. Reading a file may raise exceptions (e.g., the file is non-existent), then the point for such an exception to emerge is where the tasks are awaited (lines 6). While await sends a signal to a task scheduler on the runtime stack, the exceptions appear to propagate in the opposite direction, from the runtime to the await sites.

Unfortunately, existing languages that support async–await do not enforce at compile time that exceptions raised by asynchronous computations are handled. The lack of this static assurance makes asynchronous programming error-prone. For example, the JavaScript compiler accepts the program above without requiring that an exception handler to be provided, which leads to program crashes if the asynchronous computation results in an exception. 
%The worse situation is: an exception raised asynchronously is possibly silently swallowed if not otherwise caught. 
Such unhandled exceptions have been identified as a common vulnerability in JavaScript programs \cite{madsen2017model,alimadadi2018finding}.
Furthermore, \cite{madsen2017model,alimadadi2018finding} display a set of other \emph{anti-patterns} including: 
attempting to settle a promise multiple times; unsettled promises; unreachable reactions; 
%implicit returns in reactions; 
and unnecessary promises, which are mostly caused by using promises without sufficient static checking.

   \vspace{2mm}
\subsection{HipHop.js -- A mixture of Esterel and JavaScript}
\label{subsection:HipHop}

\begin{figure}[h]
\noindent
   \vspace{-2mm}
\begin{varwidth}{.5\textwidth}
\begin{lstlisting}
function enableLoginButton(){
  return (Rname.length >= 2 
	   && Rpasswd.length >= 2);}
function nameKeypress(value){
  Rname = value;
  RenableLogin=enableLoginButton();}
function passwdKeypress(value){ 
  Rpasswd = value;
  RenableLogin=enableLoginButton();}
\end{lstlisting}
\end{varwidth}%
\begin{varwidth}{.5\textwidth}
\begin{lstlisting}
hiphop module Identity(
			in name, in passwd, 
			out enableLogin){
  do{
	  emit enableLogin(
		  		name.length >= 2 
		  	 && passwd.length >= 2); 
  } every(name || passwd)
}
\end{lstlisting}  
\end{varwidth}
      \vspace{0mm}
\caption{A comparison between JavaScript (left) and HipHop.js (right) for a same login button implementation \cite{berry2020hiphop}. (On the right, {\ttfamily{name}}, {\ttfamily{passwd}} and {\ttfamily{enableLogin}} are reactive input/output signals.)}
  \label{fig:login_compare}  
      \vspace{0mm}
\end{figure}

HipHop.js is a reactive web language that adds synchronous concurrency and preemption to JavaScript, which is compiled into plain  JavaScript and executes on runtime environments \cite{berry2020hiphop}. 
To show the advantages of such a mixture, \figref{fig:login_compare} presents a comparison between JavaScript and HipHop.js to achieve the same login button. Here, {\ttfamily{Rname}}, {\ttfamily{Rpasswd}}, {\ttfamily{RenableLogin}} are global variables to model the application's states. Dis/En-abling login is done by setting {\ttfamily{RenableLogin}}. However, while more and more features get added to the specification, state variable interactions can lead to a large number of implicit and  invisible global control states.

Whereas, HipHop.js simplifies and modularizes designs, and synchronous signaling makes it possible to instantly communicate between concurrent statements to exchange data and coordination signals. 
Second, powerful event-driven reactive preemption borrowed from Esterel finely controls the lifetime of the arbitrarily complex program statements they apply, instantly killing them when their control events occur. 
More examples are discussed in the following sections.

%Third, an extension of async that synchronously signals termination completion to concurrent statements and automatically performs automatic resource cleaning when preempted.

%

\section{Overview}\label{sec:Overview}
%We now give a summary of our techniques using running examples.

%\subsection{HipHop.js and Dependent Effects}
\subsection{Timed Synchronous Effects}
As shown in \figref{fig:overview_eg1}, we define Hoare-triple style specifications (enclosed in \textcolor{darklavender}{\ttfamily{{/*@ ... @*/}}}) for each program, which leads to a compositional verification strategy, where static checking and timed temporal verification can be done locally. %The set of signals to be present in one logical time instance are represented within one \code{\{\}}.

\begin{figure}[h]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
hiphop module authenticate(var d, var name, var passwd, in Tick, out Connecting, out Connected)
/*@ requires d>3000 : {}^*.{Login} @*/
/*@ ensures	(3000<t/\t<d : {Connecting}#t.{Connected}) \/ (t=d :  {Connecting}#t) @*/
{
   abort count(d, Tick) { // Abort the execution at d milliseconds
      async Connected {
         emit Connecting; 
         // Execute authenticateSvc after a 3000 milliseconds' delay
         setTimeout (authenticateSvc(name, passwd).post().then( v => this.notify(v)), 3000);}}}
\end{lstlisting}  
      \vspace{0mm}
      \caption{Dependent Values for Time Bounds (the program is from  \cite{berry2020hiphop}).}\label{fig:overview_eg1}
         \vspace{0mm}
\end{figure}

The {\ttfamily{authenticate}} module checks the validity of the identity at each click on login button. The operations of requesting the server are wrapped in an {\textbf{\color{purple}\ttfamily{abort}}} statement, which preempts the execution when the responding time goes beyond \code{\m{d}} (given signal \code{\anyevent{Tick}} is present every second).

After emitting the signal \anyevent{Connecting}, it emits  \anyevent{Connected} if the connection succeeds before the  preemptive deadline; otherwise, no signal is emitted. 
The precondition \code{d{>}3000 : \{
\}^\star \cdot\{\m{Login}\} } requires that the input variable \code{d} is greater than 3000, and before entering into this module, the signal \anyevent{Login} should be emitted at the last time instance, indicating that a login request has been sent. 
The postcondition contains two parts and connected using the disjunction mark \code{{\vee}}: when \code{3000{<}t{<}d}, the effects contains two time instances, \code{\{\m{Connecting}\}} and \code{\{\m{Connected}\}}, while the first  time instance finishes at time \code{t}, %(assuming to reset the clock when executing the module), 
which is no later than \code{\m{d}} milliseconds; otherwise, the effects contains one time instance \code{\{Connecting\}} which finishes at time \code{d}. \emph{(See a demo from \cite{CODE1})}

As for another example, shown in \figref{fig:overview_eg2}, the module {\ttfamily{main}} %contains a \code{\m{fork/par}   } statement, which 
spawns two threads running in  parallel.
The first thread firstly waits for the signal \anyevent{Ready}, then emits  \anyevent{Go}. 
The second thread firstly emits  \anyevent{Prep}, then calls the function {\ttfamily{cook}} asynchronously. 
The precondition of {\ttfamily{main}} requires no arithmetic constraints on its input values (expressed as \code{\m{true}}), neither any pre-traces  (expressed as \code{\m{emp}} or \code{\epsilon}, indicating an empty trace). The postcondition ensures a trace, where the second time instance contains at least one signal \code{\anyevent{Cook}} and finishes within 3000 milliseconds after the completion of the first time instance. Then we do not care about the rest of the trace (\code{\{\}} is similar to a wildcard). 
%We omit the implementation of \code{cook} here, while provide the specifications of it. 
Taking {\ttfamily{main}} as an example, the work flow of the forward verifier is presented in the following sub-section. \emph{(See a demo from \cite{CODE2})}

\begin{figure}[h]
      \vspace{-2mm}
\begin{lstlisting}[columns=fullflexible]
hiphop module main (out Prep, in Tick, out Ready, out Go, out Cook)
/*@ requires true : emp @*/
/*@ ensures  0<=t/\t<3000 : {}.({Cook})#t.{}^* @*/
{
	fork{ // The effects of the first thread is true : Ready?.{Go}
		await Ready; emit Go; 
	}par{ // The effects of the second thread is 0<t<3000 : {Prep, Cook}#t.{Ready}
		emit Prep;
		async Ready { run cook (3000, Tick, Cook); }}}
// The final effects for main is  0<=t/\t<3000 : ({Prep}.{Cook})#t.{Ready}.{Go}

hiphop module cook (var d, in Tick, out Cook)
/*@ requires d>2000  : {}^*.{Prep} @*/
/*@ ensures  0<=t/\t<d : ({}.{Cook})#t @*/
{	abort count(d, Tick) { yield; emit Cook; }}
\end{lstlisting}  
      \vspace{-1mm}
      \caption{Mixed Synchronous and Asynchronous Concurrency with Function Calls.}\label{fig:overview_eg2}
            \vspace{-1mm}
\end{figure}

%We demonstrate

%%, and a function call from module \code{main} to \code{cook}.

      \vspace{-2mm}
\subsection{Forward Verification}
As shown in \figref{fig:forward_example}, we demonstrate the forward verification process of the module  {\ttfamily{main}}. The program effects states  are captured in the form of \code{\langle \textcolor{huntergreen}{\effect} \rangle}. To facilitate the illustration, we label the verification steps by (1), ..., (9), and mark the deployed inference rules (cf. \secref{Forward_Rules}) in \textcolor{mGray}{[gray]}.

{
\begin{figure}[h]
      \vspace{0mm}
     \begin{minipage}[c]{\columnwidth}
      \vspace{0mm}
         \centering
         {\small
\begin{enumerate}
  \item  \code{\key{fork}\{    } 
                 \textcolor{mGray}{  \emph{(– initialize the current effects state using the module precondition –)}}
  \\
 \code{\langle  \textcolor{darklavender}{true : emp} \rangle }
                  \textcolor{mGray}{  \emph{(– emp indicates an empty trace –)}}
  \item    \code{~\qquad \key{await}\ Ready;}
   \\
 \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\{\} } \rangle }
     \siderule{ [FV\text{-}Await]}
     \\
   \item    \code{~\qquad \key{emit}\ Go;}
         \\
 \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\{Go\}} \rangle }
     \siderule{ [FV\text{-}Emit]}
     \\
  \item \code{ \} \key{par}\{ }
       \textcolor{mGray}{  \emph{(– initialize the current effects state using the module precondition –)}}
  \\
 \code{\langle  \textcolor{darklavender}{true : emp} \rangle }
  \item    \code{~\qquad \key{emit}\ Prep; }
     \\
 \code{\langle  \textcolor{darklavender}{true : \{Prep\}} \rangle }
     \siderule{ [FV\text{-}Emit]}
     \\
  \item    \code{~\qquad \key{async}\ Ready\{}
  %   \item    \code{~\qquad \key{yield}; }
 %     \\
% \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\{\}} \rangle }
 %    \siderule{ [FV\text{-}Yield]}
%     \\
  \item      \code{~\qquad \ \qquad \key{run}\ cook\ (3000, Cook) 
     \}\}\}}
      \\
                     \textcolor{mGray}{\emph{(-TRS: check the  precondition of module cook-) }} \\
              \code{  \textcolor{darkred}{d{=}3000 : \{Prep\}  \CONTAIN  d{>}2000 \wedge \{Prep\}} }   \\

               \textcolor{mGray}{\emph{(-TRS: succeed-) }}
      \\
     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3000 : (\{Prep\}\cdot \{Cook\})\# t}  \rangle } 
     \siderule{ [FV\text{-}Call]}
      \\
     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3000 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}}  \rangle } 
     \siderule{ [FV\text{-}Async]}
     \\ \item
                   \code{\langle \textcolor{huntergreen}{(true \wedge 0{\leq}t {<}3000) :  Ready? \cdot\{Go\}  \ || \  (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}} \rangle }   \siderule{ [FV\text{-}Fork]} 
        \\ 
         \code{\langle \textcolor{huntergreen}{0{\leq}t {<}3000 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}} \rangle }
         \siderule{ [Effects\text{-}Normalization]} 
         \\
              \item 
               \textcolor{mGray}{  \emph{(-TRS: check the  postcondition of module main; Succeed, cf. \tabref{tab:rewriting_tree_send}-) }}\\
                  \code{  \textcolor{darkred}{
{0 {\leq} t {<}3000} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN {0 {\leq} t  {<}3000} : \{\}\cdot (\{Cook\})\# t \cdot\{\}^\star} 
                  }    \\

\end{enumerate}}

     \end{minipage}
      \vspace{0mm}
      \caption{The forward verification example for the module {\ttfamily{main}}. }\label{fig:forward_example}
      \vspace{-1mm}
\end{figure}
}

The effects states (1) and (4) are initial effects entering into the \code{fork/par} statement. The effects state (2) is obtained by [FV-Await], which concatenates a blocking signal 
%(with a question mark) 
%followed by a new empty time instance
 to the current effects. 
%The effects state (3) is obtained by [FV-Emit], which simply adds  %concatenates an empty time instance to the current effects. %to be the new current state. 
The effects states (3) and (5) are obtained by [FV-Emit], which simply adds the emitted  signal to the current time instance. The intermediate effects state of (7) is obtained by [FV-Call]. 
Before each function call, it invokes the TRS to check whether the current effects state satisfies the precondition of the callee module. If it is not satisfied, the verification fails, otherwise it concatenates the callee's postcondition to the current effects state. The final effects state of (7) is obtained by [FV-Async], which adds a new time instance \code{\{Ready\}} to the current effects state, indicating that the asynchronous program has been resolved. 
In step (8), we parallel compose the effects from both of the branches, and normalize the final effects. 
After these states transformations, step (9) checks the satisfiability of the inferred effects against the declared postcondition by invoking the TRS.

\subsection{The TRS}
Our TRS is obligated to check the inclusions between timed synchronous effects, which is an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{antimirov1995rewriting}  
%a TRS 
%for deciding the inequalities of regular expressions (REs), based on a complete axiomatic algorithm of the algebra of regular sets. 
%This method is shown to be a better average-case algorithm than those based on the comparison of minimal deterministic finite automatons (DFAs).}
%Basically, 
decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their \emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
\code{[DISPROVE]}, which infers false from trivially inconsistent inequalities; and  
\code{[UNFOLD]}, which applies \defref{RegularInclusion} to generate new inequalities.

Given \code{\Sigma} is the whole set of the alphabet, 
\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the signal \code{\anyevent{A}}.

\begin{definition}[REs Inequality]\label{RegularInclusion}  For REs \code{r} and \code{s}, \code{r \preceq s \Leftrightarrow \forall (\anyevent{A} \in \Sigma).\ D_{\anyevent{A}}(r) \preceq D_{\anyevent{A}}(s)}.
\end{definition}

Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between timed synchronous effects, where \code{D_{I\# t}(\effect)} is the partial derivative of \code{\effect} w.r.t the time instance \code{I} and time bound \code{t}.

\begin{definition}[Timed Synchronous Effects Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
For timed synchronous effects \code{\effect_1 } and \code{\effect_2}, 
\code{\effect_1  \CONTAIN \effect_2 \Leftrightarrow \forall I. \forall t {\geq} 0.\ D_{I\# t}(\effect_1)  \CONTAIN D_{I\# t}(\effect_2)}.
\end{definition}
%\in fst(\effect_1)

%Adapting to the context of checking inclusions between timed synchronous effects, we extend the Antimirov algorithm with

%The rule \code{[REOCCUR]} finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{brotherston2005cyclic}. (We use \code{\textcolor{persianplum}{(\dagger)}} in \tabref{tab:rewriting_tree_send} to indicate such pairings.)

%(introduce \code{t_L^1} and \code{t_L^2}, let \code{t_L^1 {+} t_L^2 {=} t_L}

%(\code{\{Cook\} {\Rightarrow} \{Cook\}}, \code{t_L^1 {+} t_L^2 {<}3 {\Rightarrow} t_L^1 {<}3})

Next, we continue with the step (9) in \figref{fig:forward_example}, to 
demonstrate how the TRS handles arithmetic constraints and dependent values. 
%We use the postcondition proving for module \code{main} as an example to briefly demonstrate the rewriting process. 
As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
 satisfy the declared postcondition. 
%property \code{\effect^\prime  {=} 0{\leq} t {<}3 : \{\}\cdot(\{Cook\}\# t)\cdot\{\}^\star}, 
%where \code{\effect^\prime} simply indicates that the signal \anyevent{Cook} needs to happen at the second time instance, and takes no more than \code{3000} milliseconds after the first time instance has completed; and \code{\{\}^\star} means we do not care the rest of the traces. 
We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.

{
\begin{table*}[h]
\centering
      \vspace{0mm}
\caption{\label{tab:rewriting_tree_send} The inclusion proving example. (For simplicity, we use 3 seconds to replace the 3000 milliseconds.)}

\vspace{-1mm}
\begin{adjustbox}{width=1\textwidth}
 \Large\begin{tabular}[t]{l}
  \hline\\
{

\begin{prooftree}
\Hypo{
\code{\textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
}  \Rightarrow 
\textcolor {darkred}{t_R {<}3}
} \qquad
\code{emp  \CONTAIN  \{\}^\star}
}
\Infer[dashed]1[{\siderule{\textcircled{8}[PROVE]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} :  emp
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee \{\}^\star}}
\Infer[dashed]1[{\siderule{\textcircled{7}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} :  \cancel{\{Go\}}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\{\}} \cdot \{\}^\star}}
\Infer[dashed]1[{\siderule{\textcircled{6}[Normalization]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} :  \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee  \{\}^\star}}
\Infer[dashed]1[{\siderule{\textcircled{5}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
{\wedge}   t_L^2 {=} t_R
} 
:  \cancel{\{ Ready\}} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\{\}} \cdot \{\}^\star}}
\Infer[dashed]1[{\siderule{\textcircled{4}[UNFOLD{-}UNIFY]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L
 } : \cancel{\{Cook\} \# t_L^2} \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\# t_R}\cdot\{\}^\star}  }
\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L } : \cancel{\{Prep\}\# t_L^1} \cdot \{Cook\} \# t_L^2 \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\{\}}\cdot\{Cook\}\# t_R \cdot\{\}^\star}  }
\Infer[dashed]1[{\siderule{\textcircled{2}[SPLIT]}}]{\code{ \textcolor {darkred}{t_L {<}3} : (\{Prep\}\cdot \{Cook\})\# t_L \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t_R {<}3} : \{\}\cdot\{Cook\}\# t_R\cdot\{\}^\star}  }
 \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{ \textcolor {darkred}{t {<}3} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
 \CONTAIN \textcolor {darkred}{t {<}3} : \{\}\cdot\{Cook\}\# t\cdot\{\}^\star}  }
\end{prooftree}}
\\~\\

\hline

\end{tabular}
\end{adjustbox}
            \vspace{0mm}
\end{table*}
}

Note that time instance \code{\{Prep\}} entails \code{\{\}} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
Intuitively, we use \code{[DISPROVE]} wherever the left-hand side (LHS) is \emph{nullable}\footnote{If the event sequence is possibly empty, i.e. contains \code{\empt}, we call it nullable, formally defined in \defref{Nullable}.} while the right-hand side (RHS) is not. 
\code{[DISPROVE]} is the heuristic refutation step to disprove the inclusion early, improving the verification efficiency.

As shown in \tabref{tab:rewriting_tree_send}, in step \code{\textcircled{1}}, we rename the time variables to avoid the name clashes between the antecedent and the consequent.  
In step \code{\textcircled{2}}, we design a new rule \code{[SPLIT]} to accommodate the extended real-time constraints, which introduces two new time variables \code{t_L^1} and \code{t_L^2}, and 
extends the previous constraint \code{t_L {<} 3} with constraints  \code{t_L^1 {+} t_L^2 {=} t_L}. Then \code{t_L^1} and \code{t_L^2} mark the real-time constraints for time instances  \code{\{Prep\}} and \code{\{Cook\}} respectively. 
Then in step \code{\textcircled{3}}, we eliminate \code{\{Prep\}} from the LHS and \code{\{\}} from the RHS, as the instances entailment  \code{\{Prep\} \subseteq \{\}} holds.  
In step \code{\textcircled{4}}, in order to conduct a further unfolding, we unify time variables \code{t_L^2} and \code{t_R} by adding the constraint \code{t_L^2 {=} t_R}. 
In step \code{\textcircled{5}}, from the RHS, since \code{\{\}^\star {=} emp \vee \{\} \cdot \{\}^\star}, eliminating one time instance \code{\{Ready\}} from it will lead to \code{\bot \vee \{\}^\star}, which can be normalised into \code{\{\}^\star} in step \code{\textcircled{6}}.
At the end of the rewriting, we manage to prove that \code{(t_L {<}3 {\wedge} t_L^1 {+} t_L^2 {=}t_L {\wedge}t_L^2 {=} t_R)  \Rightarrow  t_R {<} 3} \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.

%(\code{\{Go\} \Rightarrow \{\}})
%(\code{\{Ready\} \Rightarrow \{\}}, \code{t_L^2 \Rightarrow true})
Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic} (cf. \tabref{tab:rewriting_tree_case_study_finit_infinit}).

\section{Language and Specifications}
\label{sec:LanguageSpecifications}

\subsection{The Target Language}
\label{subsec:Targetlanguage}

To formulate the target language, we generalise the design of  Hiphop.js into a core language \code{\lambda_{HH}}, 
%Based on the design of , but not too specific to Hiphop.js, we summarise a core language to be our target language, 
which provides the infrastructure for mixing synchronous and asynchronous concurrency models. 
We here formally define the syntax of \code{\lambda_{HH}}, as shown in \figref{fig:Hiphop_Syntax} The statements marked as \textcolor{purple} {purple} come from the  Esterel v5 \cite{berry1999constructive,berry2000esterel} endorsed by current academic compilers; while the statements marked as \textcolor{blue} {blue} provide the asynchrony coming from the usage of JavaScript promises. 
In this work, we are mainly interested in signal status and control propagation, which are not related to data, therefore the data variables and data-handling primitives are abstracted away.

%as our target language because it Given that Hiphop.js is an integration of Esterel and JavaScript,

Meta-variables are {\textbf{S}}, \code{x} and \code{nm} . Basic signal types include \code{IN} for input signals, \code{OUT} for output signals, \code{INOUT} for both and \code{int} for integer variables. {\textbf{var}} represents the countably infinite set of arbitrary distinct identifiers. We assume that programs are well-typed conforming to basic types \code{\tau}.

A program \code{\mathcal{P} } comprises a list of module definitions \code{ \overrightarrow{module}}. Here, we use the \code{ \overrightarrow{}} script to denote a finite vector (possibly empty) of items.
Each \code{module} has a name \code{nm}, a list of well-typed arguments \code{ \overrightarrow{\tau\ x} } and $ \overrightarrow{\tau\ \textbf{S}}$, a statement-oriented body \code{{p}}, associated with a precondition \code{\effect_{pre}} and a postcondition \code{\effect_{post}}. (The syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects})

{

\begin{figure*}[h]
  \vspace{0mm}
\renewcommand{\arraystretch}{1.1}
\centering
  $
  \begin{array}{lrcl}
 \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }& \
    \code{%{datat^*}  \  
   \overrightarrow{module}} 
\qquad  \ \ 
    \m{(Basic\ Types)} \quad  \code{\tau\ } \code{  ::= } \
     \code{IN\ |\ OUT\ |\ INOUT \ | \ int }
    \\

      \m{(Module\ Def.)} &  \code{module}&\code{  ::= }&
  \code{ \ nm  \ \ {(\overrightarrow{\tau\ x}, \  \overrightarrow{\tau\ \textbf{S}} )}\ \ \langle\textbf{requires}\ \ \effect_{pre}\ \ \textbf{ensures}\ \  \effect_{post} \rangle\ \  {p} }
  \\

  \m{(Statement)} &  \code{{{p, \ q}}}&\code{  ::= }&
 \textcolor{purple} {  \code{ 
    \ nothing
         \ |\ yield
      \ |\ emit \ \textbf{S}
     \ |\ present \ \textbf{S} \ {p} \ {q}
     \ |\ seq\  {p} \ {q}  
          \  |\ fork\  {p}  \ {q}    
   }}\\
&&&  
 \textcolor{purple} {\code{ 
        |\ loop \ {p} 
%\  |\ run \ nm \ {( x ^*, \textbf{S}^*)}
\ | \ run \ nm \ {( \overrightarrow{x}, \overrightarrow{ \textbf{S}})}
%\  | \ every \  \textbf{S} \  {p}
  \   |\ abort\ {p}\ when\ d  
%  \ |\ trap \  \textbf{T} \ \textbf{p}
 % \  |\ exit \   \textbf{T}_k
   } }
   \\
%&&&  
% \textcolor{purple} {\code{ 
% %  
%%   |\ signal \ \textbf{S} \ {p}
%
%}}
%   \\
%   
   &&&

     \textcolor{ blue} {|\ async\ \textbf{S} \ {p} \ d
 \ |\ await\ \textbf{S}
 } 
 \ |\ assert\ \effect

  \\~\\

    \multicolumn{4}{c}{
      \code{\textbf{S} \in \text{signal variables}}  
      \qquad\quad \ 
\code{\text{nm, x} \in \textbf{var}}
   \qquad\quad \ 
       \code{
          \m{(Finite\ List) \ \overrightarrow{}}}
 \qquad\quad \ 
\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{Z^+}}    
    }\\

    \hline
  \end{array}  
  $
    \vspace{0mm}
 \caption{Syntax of \code{\lambda_{HH}}.} 
 \label{fig:Hiphop_Syntax}
  \vspace{0mm}
\end{figure*}
}

We here explain the intuitive semantics, while the axiomatic semantics model is defined in \secref{sec:Verification}.
The statement \code{nothing} in \code{\lambda_{HH}} resets all the output signals into absent. 
%is the Esterel equivalent of unit, void or skip in other languages. 
A thread of execution suspends itself for the current time instance using the \code{yield}  construct, and resumes when the next time instance started. The statement $emit \ \textbf{S}$ broadcasts the signal {\textbf{S}} to be set as  present and terminates instantaneously. The emission of {\textbf{S}} is valid for the current instance only.

The statement $present \ \textbf{S} \ p \ q$ immediately starts \code{p} if {\textbf{S}} is present in the current instance; otherwise it starts \code{q} when {\textbf{S}} is absent.
The sequence statement \code{seq\  p \ q} immediately starts \code{p} and behaves 
as \code{p} as long as \code{p} remains active.
When \code{p} terminates, control is passed instantaneously to \code{q}, which determines the behaviour of the sequence from then on. \emph{(Notice that `$emit\ \textbf{S1};\ emit \  \textbf{S2}$' leads to $\{S1, S2\}$, which  emits {{\textbf{S1}}} and ${\textbf{S2}}$ simultaneously and terminates instantaneously.)}

%If \code{p} exits a \code{trap}, so does the whole sequence,
%  \code{q} being discarded in this case.

 %\code{q} is never started if \code{p} always pauses.

 The parallel statement \code{fork\  p  \ q} runs p  and q in parallel. It remains active as long as one of its branches remains active. The parallel statement terminates when both \code{p} and \code{q} are terminated. The branches can terminate in different instances, and the parallel waits for the last one to terminate.

 The statement \code{loop \ p} implements an infinite loop, but it is possible to be aborted or suspended by enclosing it within a preemptive statement.  
% escape from the loop by enclosing it within a trap and executing an exit statement. 
 When \code{p} terminates, it is immediately restarted. 
 %If \code{p} exits a trap, so does the whole loop. 
 The body of a loop is not allowed to terminate instantaneously when started, i.e., it must execute a yield statement to avoid an `infinite instance'. 
For example, `$loop \ emit\ \textbf{S}$' is not a correct program.

%The statement \code{run \ nm \ {( x ^*, \textbf{S}^*)}} makes a function calls to \code{nm} with parameters.

The statement $run \ nm \ {( \overrightarrow{x}, \overrightarrow{ \textbf{S}})}$ is a call to module \code{nm}, parametrising with values and signals.

%providing the list of IO signals.

%The statement \code{every \  \textbf{S} \  {p}} behaves as its body p once the \textbf{S} is present occurs, where the whole watchdog statement terminates without transferring control to p in this instant. The watchdog construct is used to abort the body when an event occurs.

%To facilitate the preemptive concurrency, \code{\lambda_{HH}} includes two primitive statements: \code{every}  and \code{abort}.

To facilitate a preemptive concurrency, as well as provide necessary  real-time bounds, \code{\lambda_{HH}} includes the primitive statement  \code{abort\ p\ when\ d}, which runs statement \code{p} to completion. If the execution  reached the time bound \code{d}, it terminates immediately.

%Parallel branches may simultaneously exit traps. If one branch exits a trap \code{\textbf{T}} or both branches exit the same trap \code{\textbf{T}}, then the parallel exits \code{\textbf{T}}. If both statements exit distinct traps \code{\textbf{T}} and \code{\textbf{U}} in the same instant, then the parallel only exits the higher prioritized one.

%The statement  \code{signal \ \textbf{S} \ p} starts p with a fresh signal \textbf{S}, overriding any that might already exist.

%The statement \code{abort\ {p}\ when\ d  } is used to abort the body when an event occurs. It behaves as its body \code{p} until the first following instant where \code{\textbf{S}} occurs, where the whole statement terminates without transferring control to \code{p} in this instant.

%In the \code{suspend \   {p}\  when \   \textbf{S}} suspension statement, \textbf{S} is called the guard. The guard controls execution of the body in each instant except for the first one, where it is ignored (masked in common terminology). In the initial instant, the body \code{p} is started; if p terminates or exits a trap, so does the suspend statement, and the guard is transparent. Interesting things only happen in the following instants if p paused in the first instant. Then, as long as p remains active, the guard signal \textbf{S} is tested for presence.
%– If \textbf{S} is present, then p is not executed in the instant and it is kept frozen for the next instant. The whole suspend statement pauses. In this case, we say that p is suspended for the instant.
%– If \textbf{S} is absent, then p receives the control for the instant. We say that p is activated for the instant. If p terminates or exits a trap, so does the suspend statement. If p pauses, then the suspend statement also pauses.

\emph{Async statements implement long lasting background operations. They are the essential ingredient for mixing indeterministic asynchronous computation and deterministic synchronous computations.} In other words, the \code{async} statement enables well-behaving synchronous to regulate unsteady asynchronous computations. The statement  $async\ \textbf{S} \ p \ d$ is supposed to spawn a long lasting background computation, where \code{d} represents an execution delay. When it completes, the asynchronous block will resume the synchronous machine.
%by calling the function that composes the async JavaScript API. 
Therefore when a signal {\textbf{S}} is specified with the {async} call, it emits {\textbf{S}} when the asynchronous block completes.

The statement $await\ \textbf{S}$ blocks the execution and waits for the signal {\textbf{S}} to be emitted across the threads. 
%The assertion statement is parametrized with effects $\effect$.
The statement assert \code{\effect} is used to guarantee the temporal property \code{\effect} asserted at a certain point of the programs.
%Prior work
\cite{kambona2013evaluation} shows that such a language combination makes reactive programming more powerful and flexible than the traditional web programming. % (cf. \secref{subsection:HipHop}).

%

\subsection{The Specification Language}
\label{subsec:Specification_language}

We plant the effects specifications into the Hoare-style verification system, using \code{ \effect_{pre}} and \code{  \effect_{post} }  to capture the temporal pre/post 
condition. %\code{\effect_{pre}} and the postcondition \code{\effect_{post}}.

{
    \vspace{0mm}
\begin{figure*}[h]
\renewcommand{\arraystretch}{1.1}
\centering
  $
  \begin{array}{rrcl}

    \m{(Timed\ Effects)} &  \effect &\code{\  ::=\ }&
    \code{
          \pure{\pi} : \es  
   \ | \ \effect_1 \vee \effect_2
}
    \\
 \m{(Timed \ Sequence)}  & \ \code{\es}   &\code{\ ::=\ }&

   \code{ \bott
   \  | \ \empt 
    \ | \ I 
    \ | \ \textbf{S}?
    %   \ | \ \anyevent{a}
   \  | \ \es_1 {\seq} \es_2
    \ | \ \es_1 {\vee} \es_2
      %    \  | \ \es_1 \times \es_2
      \  | \ \es_1  ||  \es_2
      \ | \ \es \# t 
 %  \  | \  \esn{\es}{t}    
   \  | \  \esn{\es}{\star}    
   \  | \ \esn{\es}{\omega} 
    }
            \\
    \m{(Time \ Instance)} &  \code{I} &\code{::= }&

    \code{
    \{ \} \ | \ \{ \textbf{S} \} \ | \ \{ \overline{\textbf{S}} \} \ | \ I_1 \cup I_2
    }
%(\textbf{S} \mapsto \theta )^*

%    \\
%        \m{(Real\ Time)} &  \mathcal{O} &\code{::= }&
%    
%    \code{
%   %n \ | \ 
%   c \ | \ (c, {+}\infty) \ | \  [0, c) \ | \  \mathcal{O}_1 \wedge \mathcal{O}_2 \ | \  \mathcal{O}_1 \vee \mathcal{O}_2
%    }

    \\

    \m{(Pure)}  & \code{\code{\pure{\pi}}}&\code{\  ::=\ }&
\pure{ \pure{True}}
   \ | \  \pure{False}
   \ | \ \pure{A(}{t_1, t_2}\pure{)}
  \   | \  \pure{\pure{\pi_1}} \wedge \code{\pure{\pi}}_2
   \  | \ \pure{\pure{\pi_1}} \vee \code{\pure{\pi}}_2
   \  | \ \neg\code{\pure{\pi}}

    \\

    & &&\code{
       | \  \pure{\pure{\pi_1}} \Rightarrow \pure{\pure{\pi_2}}
   \  | \ \forall x. \code{\pure{\pi}}
   \  | \ \exists x. \code{\pure{\pi}}
   }\\

    \m{(Real\text{-}Time\ Term)}  & \code{t} &\code{\  ::=\ }&
    \code{ c
    \ | \  n
    \ | \  t_1{+}t_2
    \ | \  t_1\text{-}t_2
    %\ | \ k {\times} n
   }

    \\~\\
    \multicolumn{4}{l}{
   \qquad   \code{\textbf{S} \in \text{signal variables}}   
   \qquad\qquad\qquad\quad
    \code{c ::\in \mathbb{R}^{+}} 
     \qquad \qquad\qquad \quad
           \code{n  ::\in \textbf{var} }

     }\\

         \multicolumn{4}{l}{
       \   \m{(Blocking)}\ \code{?}
          \qquad  \qquad \ \
     \m{(Real\ Time\ Bound)}\ \code{\#}
     \qquad\qquad \ \
        \m{(Kleene\ Star) \ \star}   
         \qquad\qquad \ \
         \m{(Infinity) \ \omega}

}\\     
      \hline

  \end{array}  
  $ \\
  \caption{Syntax of Timed Synchronous Effects.}
  \label{fig:Syntax_of_Types_and_Effects}
  \vspace{0mm}
\end{figure*}

}

The  syntax of the timed synchronous effects is formally defined in \figref{fig:Syntax_of_Types_and_Effects} Effects is  a conditioned time  instance sequence \code{\pure{\pi} : \es} or a disjunction of two effects $\effect_1 \vee \effect_2$.
Timed sequences comprise \textit{nil} ($\bott$);
 an empty trace $\empt$;
a single time instance represented by \code{I};
a waiting for a single signal \code{\textbf{S}?};
  %where \anyevent{a} is an element from a finite set of events, donated by \code{\Sigma};
%parametrized event \code{ \anyevent{a}.\iota} where \code{\iota} is a list pattern expressing a possibly infinite list (for example, \code{\anyevent{a}.[1,2,3,4]},  \code{\anyevent{a}.[1 .. 4]} and \code{\anyevent{a}.[1, 2.. 4]} all refer to the finite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot \anyevent{a}.4},
%while \code{\anyevent{a}.[1 ..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot}..., and \code{\anyevent{a}.[1, 3..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.3 \cdot \anyevent{a}.5\cdot}...);
 sequences concatenation \code{\es_1\cdot \es_2};
disjunction  \code{\es_1\vee \es_2};
synchronous parallelism   \code{\es_1 || \es_2}.
%negation \code{\neg \es};
 %

 We introduce a new operator \code{\#}, and the effects \code{\es \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace; or constructed by \code{\omega}, representing an definitely infinite repetition of a trace.

There are two possible states for a signal: present \textbf{S}, or absent $\overline{\textbf{S}}$, 
%or waiting \anyevent{S?}. 
The default state of signals in a new time instance is absent. 
A time instance \code{I} is a set of signals; and it can be possible empty sets \code{ \{ \}}, indicating that there is no signal constraints for the time instance.

We use \code{\pure{\pi}} to donate a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
We use \code{\pure{A(}{t_1, t_2}\pure{)}} to represent atomic formulas of two terms (including $  {=},
   \ {>},
   \ {<},
   \ {\geq}\ $ and $ {\leq} $).
%e.g. the equality between constant 0 and an integer variable \code{x}.
A term can be a constant integer value \code{c}, an integer variable \code{n} which is an input parameter of the program and can be constrained by a pure formula. 
A term also allows simple computations of terms, \code{t_1{+}t_2} and \code{t_1\text{-}t_2}. To abstract the elapsed time, the default and implicit pure constraints of all the terms is to be greater or e
qual to  0.

\subsection{Semantic Model of Timed Effects}
\label{subsec:Specification_Semantics}

\begin{figure}[h]
    \vspace{-1mm}
    \renewcommand{\arraystretch}{1}
\begin{align*} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                          Disjunction                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models \effect_1 {\vee} \effect_2}  
&\m{iff}\quad 
&  d, \varphi \models \effect_1 \ or \ d, \varphi \models \effect_2
\\[0.2em]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                          EMPTY                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models \pi : \empt }  
&\m{iff}\quad 
&  d{=}0 \ and\  {\tt{SAT}(\pi)}  \ and \ \varphi {=} [] 
\\[0.2em]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                          I                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models  \pi : I }  &\m{iff}\quad 
& d {\geq} 0 \ and\ {\tt{SAT}(\pi)}  \ and \ 
\varphi {=} \code{[I]}
  \\[0.2em]
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                          waiting                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models  \pi : \textbf{S}?}  &\m{iff}\quad 
& d {\geq} 0  \ and\  {\tt{SAT}(\pi)}  \ and \
\exists n {\geq} 0.\ \varphi {=} \code{\{ \overline{\textbf{S}} \}^{n} {+}{+} [\{ {\textbf{S}} \}] }
  \\[0.2em]
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                            CONCATE                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models  \pi : (\es_1{\cdot}\es_2)}  
&\m{iff}\quad 
& {\tt{SAT}(\pi)}  \ and \ \exists \code{\varphi_1, \varphi_2, d_1, d_2}\ and\ \code{
\varphi {=} \varphi_1 {+}{+} \varphi_2, d {=} d_1 {+} d_2 \ and 
}\\
& & &
\code{d_1, \varphi_1 \models  \pi : \es_1}  \ and \ 
\code{d_2, \varphi_2 \models  \pi : \es_2}  
 \\[0.2em]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                       DISJUNCTION                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models  \pi : (\es_1 {\vee} \es_2)}  
&\m{iff}\quad 
& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ or \ 
 \code{d, \varphi \models  \pi :  \es_2}  
\\[0.2em]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                       par                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models  \pi : (\es_1 || \es_2) }  
&\m{iff}\quad 
& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ and \ 
 \code{d, \varphi \models  \pi :  \es_2}  
\\[0.2em]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                       timed                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d, \varphi \models  \pi : \es \# t }  
&\m{iff}\quad 
& d, \varphi \models  (\pi \wedge t{=}d) : \es
\\[0.2em]
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                            KLEENE                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d,  \varphi \models \pi : \esn{\es}{\star}  }  
&\m{iff}\quad 
&d, \varphi \models \pi :  \empt \ or \ 
d, \varphi \models \pi :  (\es \cdot \esn{\es}{\star} ) 
 \\[0.2em]
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                            OMEGA                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{d,  \varphi \models \pi : \esn{\es}{\omega}   }  
&\m{iff}\quad 
&
d, \varphi \models \pi :  (\es \cdot \esn{\es}{\omega} )  
 \\[0.2em]
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                            FALSE                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
& \code{d, \varphi \models False : \bot }  
&\m{iff}\quad 
&   otherwise
%{\tt{UNSAT}(\pi)}  \ or \  \varphi  {=} \bot
%\exists t, d(t) \not\models \llbracket \pure{\pi} \rrbracket_{t}
\end{align*}
    \vspace{-3mm}
\caption{Semantics of Timed Synchronous Effects.}
\label{fig:Sementic}
  \vspace{-1mm}
\end{figure}

To define the semantic model, 
we use \code{\varphi} (\emph{a trace of sets of signals})  to represent the computation execution (or time-instance multi-trees, per se), indicating the sequential constraint of the temporal behaviour; and we use \code{d} to record the computation duration of given effects. 
Let \code{d, \varphi \models \effect} denote the model relation, i.e., 
the effects \code{\effect} take exactly \code{d} milliseconds to complete; and 
the linear temporal sequence \code{\varphi} satisfies the sequential time  instances defined from \code{\effect}, with \code{d}, \code{\varphi} from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{Z^+}} and \code{\varphi}   {\defeq}\ \code{list\ of\ I} (a sequence of time instances).

As shown in \figref{fig:Sementic}, we define the semantics of timed synchronous effects. 
We use 
$[]$ to represent the empty sequence;
${+}{+}$ to represent the append operation of two traces;
\code{[I]} to represent the sequence only contains one time instance.

\code{{\tt{SAT}(\pi)} } indicates the pure \code{\pi} is satisfiable, which is discharged by the constraint solver Z3 \cite{de2008z3}.  
\code{I} is a list of mappings from signals to status. For example, the time instance $\{\textbf{S}\}$ indicates that signal \textbf{S} is present regardless of the status of other non-mentioned signals, i.e.,  time instances which at least contain $\textbf{S}$ to be present. Any time instance contains contradictions, such as $\{\textbf{S}, \overline{\textbf{S}}\}$, will lead to \code{false}, as a signal {\textbf{S}} can not be both present and absent.

%The signals shown in one time instance  represent the \emph{minimal} set of signals which are required/guaranteed to be there. An empty set \code{\{\}} represents any set of signals

\section{Automated Forward Verification}\label{sec:Verification}

\begin{wrapfigure}{R}{0.5\columnwidth}
    \vspace{-3mm}
\centering
\includegraphics[width=0.5\columnwidth]{verification.png}
        \vspace{-3mm}
\caption{\label{fig:Verification_oberview}System Overview.}
      \vspace{-1mm}
\end{wrapfigure}

An overview of our automated verification system is given in \figref{fig:Verification_oberview} It consists of a Hoare-style forward verifier and a TRS. 
The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in timed synchronous effects (cf. \figref{fig:overview_eg1}).

The input of the TRS is a pair of effects LHS and RHS, referring to the inclusion LHS \code{\CONTAIN} RHS to be checked 
\textit{(LHS refers to left-hand side effects, and RHS refers to right-hand side effects.)}. Besides, the verifier calls the TRS to prove produced inclusions, i.e., between the effects states and pre/post conditions or assertions (cf. \figref{fig:forward_example}). The TRS will be explained in \secref{sec:Entailment_Prover}.

In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\lambda_{HH}}, by formalising a set of forward inductive rules. 
These rules transfer program states and systematically accumulate the effects syntactically. 
To define the model, we introduce an environment \env\ and describe a program state in a four-elements tuple \code{\langle \Pi, H, C, T \rangle}, with the following concrete domains:
\begin{flalign*}
\Pi {\defeq} t {\rightarrow} \pi, \qquad
H  {\defeq} es, \qquad
C {\defeq} \overrightarrow{\textbf{S} {\rightarrow} \Delta}\  | \ \textbf{S}?, \qquad
T {\defeq} t, \qquad 
\env {\defeq} \overrightarrow{\textbf{S}}, \qquad
\Delta {\defeq} \m{Present} \ | \ \m{Absent}  \ | \  \m{Undef}
\end{flalign*}

Let \code{\Pi} represents the pure constraints for all the terms; \code{H} represents the trace of \emph{history}; \code{C} represents the \emph{current} time instance or a waiting signal; 
\code{T} is a term binding \code{C}; 
\env\ be the environment containing all the local and output signals; 
\code{\Delta} marks the signal status.

%We describe the input and output histories of ESTEREL programs by streams carrying sets of signals.

%which is used for the description of a reactive program.

%The main difficulty in giving a semantics to \code{\lambda_{HH}} consists in the idea of instantaneous reactions of ESTEREL programs to input signals.

%We base this semantics on a functional model of behaviour. We describe the input and output histories of ESTEREL programs by streams carrying sets of signals.

%we mainly present the forward verifier
% based on the syntax of each statement.

%We present the intermediate representation of program states in \figref{fig:intermediate_representation}

%\noindent   the second element represents the  containing the path constraints (\code{\pi}) and signal assignments (\code{\phi})\footnote{The difference between \code{\textbf{S} = \theta} and \code{\textbf{S} \mapsto \theta } is: the former one denotes the constraints along the execution path, which creates \emph{false} if there are two different status assignments to the same signal; while the latter one records the current status of one signal, and will be overwritten when the presence of a signal had been determined.};

\subsection{Forward Inference Rules}
\label{Forward_Rules}
To help with reasoning logical errors (cf. \secref{subsec:LogicalIncorrectCatching}), the rule \code{[FV\text{-}Nothing]} extends the current time instance with all the signals in the environment pointing to absent. 
%is the Esterel equivalent of unit, void or skip in other languages, 
% obtains the next program state by inheriting the current program state.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                          NOTHING                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&\code{\frac{
%\forall \textbf{S} \in \env.\  C[ \textbf{S}\mapsto  Absent]
C^\prime {=} \{\textbf{S}\mapsto  Absent\ |\  \forall \textbf{S} \in \env\}
}{\env \vdash \langle \Pi, H, C, T \rangle\  nothing \ \langle
 \Pi, H, C {+}{+} C^\prime, T \rangle}\ [FV\text{-}Nothing]} 
\end{flalign*}
The rule \code{[FV\text{-}Emit]} extends the current time instance with signal {\textbf{S}}  pointing to \code{Present}. %status of signal \code{\textbf{S}} (from \code{Undef}) to \code{Present}; keeps the pure constraints, the history trace and the current term unchanged.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                              EMIT                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
C^\prime {=} C {+}{+} [ (\textbf{S}\mapsto  Present)]
}{\env \vdash \langle \Pi, H, C, T \rangle\  emit \ \textbf{S} \ \langle  \Pi, H, C^\prime, T \rangle}\ [FV\text{-}Emit] } 
\end{flalign*}
The rule \code{[FV\text{-}Yield]} archives the current time instance to the history trace; then initializes a new time instance where all the signals from \code{\env} are set to be undefined. Then the new \emph{current} is bound with a fresh non-negative term \code{ T^\prime}.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                            PAUSE                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\Pi^\prime {=} \Pi \wedge  T^\prime {\geq}0 \qquad 
C^\prime {=} \{\textbf{S}\mapsto  Undef\ |\  \forall \textbf{S} \in \env\} \qquad
H^\prime {=} H \cdot (C\# T) \qquad
( T^\prime\ is\ fresh)
}{\env \vdash 
\langle  \Pi, H, C, T  \rangle\  yield \ \langle 
 \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle}\ [FV\text{-}Yield]} 
\end{flalign*}

The rule \code{[FV\text{-}Present]} 
enters into branches \code{p} and \code{q} after setting the status of  {\textbf{S}} in the current time instance to \code{Present} and \code{Absent} respectively. We deploy the \code{cut} function to reallocate the next program state. {Each signal can be reset from \code{\m{Undef}} to \code{\m{Present}} or \code{\m{Absent}} maximum once.}
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                          PRESENT                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\begin{matrix}
\text{\code{
 \env \vdash \langle  \Pi, H, C[ \textbf{S}\mapsto  Present], T  \rangle\  {p} \ \langle 
 \Pi_1, H_1, C_1,  T_1 
 \rangle
}}\\
 \text{\code{
\env \vdash \langle  \Pi, H, C[ \textbf{S}\mapsto  Absent], T  \rangle\  {q} \ \langle 
 \Pi_2, H_2, C_2,  T_2 
\rangle 
}}
\\
 \text{
\code{
\langle   \Pi^\prime , H^\prime, C^\prime,  T^\prime \rangle {=} cut \ (\Pi_1 \wedge \Pi_2 : H_1 \cdot (C_1\#T_1) \vee H_2 \cdot (C_2\#T_2) )
} 
 }
\end{matrix}
}{\env \vdash \langle  \Pi, H, C, T  \rangle\  present \ \textbf{S} \ {p} \ {q}  \ \langle  \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle}\ [FV\text{-}Present] } 
\end{flalign*}
}
%Intuitively, Cut is defined in, with the intuition of cutting a trace es into a history trace H and a current time instance \code{C\#T}.
\begin{definition}[Cut]\label{Def_cut} 
Given any \code{\pi} and \code{\es}, we define: 
\code{cut(\pi{:} \es)} computes \code{\langle \Pi, H, C, T \rangle. 
} In particular, 
{ 
\begin{gather*}
\code{cut(\pi:\es^\prime \cdot I){=} \langle \pi\wedge T{\geq}0, \es^\prime, I, T \rangle}    \qquad  (\es{=}\es^\prime \cdot I, \ T\ is\ \m{fresh})
\\
 \code{cut(\pi:(\es^\prime \cdot I) \# t) {=} \langle \pi\wedge T_1{\geq}0\wedge T_2{\geq}0 \wedge T_1{+}T_2{=}t, \es^\prime \#T_1, I, T_2 \rangle} \quad \ 
 (\es{=}(\es^\prime \cdot I)\# t, \ T_1, \ T_2 \ are\ \m{fresh})
\end{gather*}}
\end{definition}

The rule \code{[FV\text{-}Fork]} gets \code{\langle \Pi_1, H_1, C_1, k_1   \rangle} and 
\code{\langle \Pi_2, H_2, C_2, k_2 \rangle} by executing \code{{p}} and \code{{q}} independently. 
We parallel synchronise the effects from these two branches; and use the \code{cut} function to reallocate the next program state. 
\begin{flalign*}
&
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                             PAR                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\code{\frac{
\begin{matrix}
\text{\code{
\env \vdash \langle  \Pi, H, C, T  \rangle\  {p} \ \langle  \Pi_1, H_1, C_1, T_1 
 \rangle 
}}\qquad\quad
 \text{\code{
\env \vdash \langle  \Pi, H, C, T  \rangle\  {q} \ \langle \Pi_2, H_2, C_2, T_2 
\rangle 
 }}\\
 \text{\code{
\langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle {=} cut\ (
\Pi_1 \wedge \Pi_2 :  H_1 \cdot (C_1\#T_1) \ || \ H_2 \cdot (C_2\#T_2))
 }}
\end{matrix}
}{\env \vdash \langle  \Pi, H, C, T  \rangle\  fork\  {p}  \ {q} \ \langle   \Pi^\prime , H^\prime, C^\prime,  T^\prime \rangle} \ [FV\text{-}Fork] } 
\end{flalign*}
The rule \code{[FV\text{-}Seq]} firstly gets \code{ \langle \Pi_1, H_1, C_1, T_1  \rangle} by executing \code{{p}}. Then it further gets  \code{ \langle \Pi_2, H_2, C_2, T_2 \rangle}  by continuously executing \code{{q}}, to be the final program state.
%and returns \code{\effect_1^{k_1}} to be the final effects. 
%the rule splits \code{\effect_1} into \code{\tau^{\prime}} and  \code{ (\Pi^\prime {\wedge}  \phi^\prime )}; constructs the final effect \code{\effect_2^{k_2}} by  executing \code{\textbf{p}_2}.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                             SEQ                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\begin{matrix}
\text{\code{
\env \vdash \langle  \Pi, H, C, T  \rangle\  {p} \ \langle  \Pi_1, H_1, C_1, T_1 
 \rangle 
}}\qquad\quad
 \text{\code{
\env \vdash \langle \Pi_1, H_1, C_1, T_1  \rangle\  {q} \ \langle \Pi_2, H_2, C_2, T_2 
\rangle 
 }}
\end{matrix}
}{\varrho \vdash \langle \Pi, H, C, T \rangle \  seq\  {p} \ {q}  \ \langle \Pi_2, H_2, C_2, T_2 
\rangle  }\ [FV\text{-}Seq]  } 
\end{flalign*}

The rule \code{[FV\text{-}Loop]} computes a fixpoint (as the invariant effects of the loop body) \code{\langle \Pi_2, H_2, C_2, T_2 \rangle} by continuously executing \code{p} twice\footnote{The deterministic loop invariant can be fixed after the second run of the loop body, cf. \appref{proof:twice} for the proof.}, starting from temporary initialised program states \code{\langle \Pi, \empt,  C , T \rangle} and 
\code{\langle \Pi_1, \empt,  C_1 , T_1  \rangle} respectively. 
The final state will contain a repeated trace \code{(H_2 \cdot C_2\# T_2 )^\star}.
% Then anything following an infinite trace will be abandoned. (cf. \tabref{table:normalization})
%gets \code{\langle\effect^k \rangle} by initializing the precondition with \code{\empt} to be the history trace and the current instant by mapping all the local signals to \code{absent} before executing \code{ \textbf{p}}. When there is no exit from the loop body (\code{k{=}0}), the final effects is an infinite trace constructed by \code{(\tau \cdot (\Pi \wedge  \phi) \cdot \effect^\omega)^0}. Otherwise, when there is an exit in the loop body, the final effects is a finite trace \code{(\tau \cdot (\Pi \wedge  \phi) \cdot \effect)^k}, reflecting the completion code \code{k}.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                             LOOP                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\begin{matrix}
\text{\code{
\env \vdash  \langle \Pi, \empt,  C , T  \rangle\  {p} \ \langle \Pi_1, H_1, C_1, T_1 \rangle \qquad\quad 
\env \vdash  \langle \Pi_1, \empt,  C_1 , T_1  \rangle\  {p} \ \langle \Pi_2, H_2, C_2, T_2\rangle  
 }}\\
 \text{
\code{
H^\prime {=} H \cdot H_1 \cdot (H_2 \cdot C_2\# T_2 )^\star \cdot H_2
} 
 }
 %\qquad \code{C^\prime = \{\textbf{S}\mapsto  absent\ |\  \forall \textbf{S} \in \varrho\}}
\end{matrix}
}{\env \vdash \langle \Pi, H, C, T \rangle\  loop \ {p} \ \langle  \Pi_2, H^\prime, C_2 , T_2 \rangle} \ [FV\text{-}Loop]} 
\end{flalign*}

%The rule \code{[FV\text{-}Trap]} gets \code{\langle \Pi^\prime, H^\prime, C^\prime, k^\prime \rangle} by executing the trap body \code{ \textbf{p}}.
%When there is no exit from the trap body (\code{k{=}0}), or there is an exit which can be exactly catched by the current trap (\code{k{=}1}), we leave the final completion code to be 0. When there is an exit with a higher priority, (\code{k{>}1}), indicating to exit from a outer trap, we get the final \code{k_f} by decreasing  the completion code by one.

%\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                             TRAP                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&
%\code{\frac{
%\begin{matrix}
%\text{\code{
% \env \vdash \langle \Pi, H, C, k  \rangle\  \textbf{p} \ \langle \Pi^\prime, H^\prime, C^\prime, k^\prime 
%   \rangle
% }}\\
% \text{\code{
%k_f  = 0  \qquad\qquad\   when \quad k^\prime {\leq} 1 }}\\
%\text{\code{
%k_f  = k^\prime\text{-}1  \qquad\quad\   when \quad k^\prime {>} 1 }}
%\end{matrix}
%}{\env \vdash \langle \Pi, H, C, k  \rangle\  trap\ \textbf{T} \ \textbf{p} \ \langle   \Pi^\prime, H^\prime, C^\prime, k_f \rangle}\ [FV\text{-}Trap]} 
%\end{flalign*}
%
%As \code{exit \ \textbf{T}_{k^\prime}} will abort execution up to the \code{(k^\prime{+}1)}th enclosing of the trap \code{\textbf{T}}.
%%reducing it to nothing. It can be used for exception handling, but also for non-exceptional control flow. 
%The rule \code{[FV\text{-}Exit]} sets the value of \code{k} using \code{k^\prime{+}1}. %and keeps the history trace and the current time instant unchanged. 
%\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                             EXIT                                %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%&
%\code{\frac{
%}{\env \vdash \langle \Pi, H, C, k \rangle\  exit \ \textbf{T}_{k^\prime} \  \langle  \Pi, H, C, k^\prime{+}1 \rangle}\ [FV\text{-}Exit]} 
%\end{flalign*}
%
The rule \code{[FV\text{-}Call]} triggers the back-end solver TRS to  check if the precondition of the callee, \code{\effect_{pre}}, is satisfied by the current effects state or not. If it holds, the rule obtains the next program state by concatenating the postcondition \code{\effect_{post}} to the current effects state. (cf. \figref{fig:forward_example}) 
\begin{flalign*}
&
\code{\frac{
\begin{matrix}
\code{nm  \ \ {(\overrightarrow{\tau\ x}, \  \overrightarrow{\tau\ \textbf{S}} )}\ \langle\textbf{requires}\  \effect_{pre}\ \ \textbf{ensures}\ \effect_{post} \rangle\ {p} \in \mathcal{P}}\\
\code{\textit{TRS}  \vdash  \Pi : H \cdot (C\# T)  \CONTAIN \effect_{pre} }
\qquad\quad
\code{
\langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle {=} cut\ (\Pi :  H \cdot (C\#T) \cdot \effect_{post})
}
\end{matrix}
}{\env \vdash \langle \Pi, H, C, T \rangle\  run \ nm \ {( \overrightarrow{x}, \overrightarrow{ \textbf{S}})} \ \langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle } \ [FV\text{-}Call]  } 
\end{flalign*}

The rule \code{[FV\text{-}Abort]} initialises the state using \code{\langle  \Pi, \epsilon, C, T  \rangle} before entering into \code{ {p}}, and  obtains \code{\langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle} after the execution; then uses a fresh time variable  \code{T_d} to set an upper-bound for the execution \code{H^\prime \cdot (C^\prime \# T^\prime)}, where the constraint on \code{T_d} is \code{0{\leq}T_d{\leq} d}. Lastly, it sets the new current time instance \code{C^{\prime\prime}} by setting all the existing signals to undefined, which is bound with a fresh non-negative term \code{ T_f}.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                              ABORT                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\begin{matrix}
\text{
\code{
\env \vdash \langle  \Pi, \epsilon, C, T  \rangle\   {p} \ \langle \Pi^\prime, H^\prime, C^{\prime},  T^\prime  \rangle
\qquad\quad
\Pi^{\prime\prime} {=} \Pi^{\prime} \wedge (0 {\leq}T_d{<} d) \wedge (T_f {\geq}0)
}}
 \\
\text{
\code{
H^{\prime\prime} {=} (H^\prime \cdot (C^{\prime}\#  T^\prime)) \# T_d
}}\qquad
\text{\code{
C^{\prime\prime} {=} \{\textbf{S}\mapsto  \m{Undef}\ |\  \forall \textbf{S} \in \env\}
\qquad\quad \m{(T_d, T_f\ are\ fresh)}
}}
\end{matrix}
}{\env \vdash \langle \Pi, H, C, T \rangle\  abort\ {p}\ when\ d \ \langle \Pi^{\prime\prime}, H\cdot H^{\prime\prime}, C^{\prime\prime}, T_f  \rangle} \ [FV\text{-}Abort]} 
\end{flalign*}

Dually, the rule \code{[FV\text{-}Async]} initialises the states using \code{\langle  \Pi, \epsilon, C, k  \rangle} before entering into \code{ {p}}, and  obtains \code{\langle \Pi^\prime, H^\prime, C^\prime, k^\prime \rangle} after the execution; then uses a fresh time variable  \code{T_d} to set a lower-bound for the execution \code{H^\prime \cdot (C^{\prime} \# T^\prime)}, where the constraint on \code{T_d} is \code{T_d{\geq} d}. Lastly, it creates the new current time instance  \code{C^{\prime\prime}}  by
setting \textbf{S} to present instantaneously, and the rest of the signals in \code{\env}  to undefined (as it emits \textbf{S} once the asynchronous execution is completed), which is bound with a fresh non-negative term \code{ T_f}.
%[ \textbf{S} \mapsto  present]
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                              ASYNC                              %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\begin{matrix}
\text{\code{\env \vdash \langle  \Pi, \epsilon, C, T  \rangle\   {p} \ \langle \Pi^\prime, H^\prime, C^{\prime},  T^\prime  \rangle
\qquad\quad \m{(T_d, T_f\ are\ fresh)}
}}
 \\
\text{
\code{
\Pi^{\prime\prime} {=} \Pi^{\prime} \wedge (T_d{\geq} d)  \wedge (T_f {\geq} 0)
\qquad \qquad
H^{\prime\prime} {=}  (H^{\prime} \cdot (C^{\prime}\#  T^\prime)) \# T_d
}}\\
\text{\code{
C^{\prime\prime} {=} \{\textbf{S}^\prime \mapsto  \m{Undef}\ |\  \forall \textbf{S}^\prime \in (\env \symbol{92} \textbf{S}) \} \cup \{ \textbf{S} \mapsto  Present\}
}}
\end{matrix}
}{\env \vdash \langle \Pi, H, C, T \rangle\  async\ \textbf{S} \ {p} \  d \  \langle \Pi^{\prime\prime}, H \cdot H^{\prime\prime}, C^{\prime\prime}, T_f \rangle}\ [FV\text{-}Async]} 
\end{flalign*}

The rule \code{[FV\text{-}Await]} archives the current time instance to the history trace, then sets a new current instance as a waiting for signal {\textbf{S}}, bound with a fresh non-negative term \code{ T^\prime}.
%updates the current status of signal \code{\textbf{S}} to \code{waiting}; keeps the pure constraints, history trace and completion code unchanged.
\begin{flalign*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                              AWAIT                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
&
\code{\frac{
\Pi^\prime {=} \Pi \wedge  T^\prime {\geq}0 \qquad  
H^\prime {=} H \cdot (C\# t) \qquad ( T^\prime\ is\ fresh)
}{\env \vdash \langle \Pi, H, C, T \rangle\  await \ \textbf{S} \ \langle  \Pi^\prime, H^\prime, \textbf{S}?,  T^\prime \rangle}\ [FV\text{-}Await] } 
\end{flalign*}

The rule \code{[FV\text{-}Assert]} simply checks if the asserted property \code{\effect} is satisfied by the current effects state. If not, a compilation error will be raised. 
\begin{flalign*}
&
\code{\frac{
\begin{matrix}
\code{\textit{TRS}  \vdash  \Pi \wedge (H \cdot (C\#T ) \CONTAIN \effect }
\end{matrix}
}{\env \vdash \langle \Pi, H, C, T  \rangle\  assert\ \effect  \ \langle \Pi, H, C, T  \rangle}\ [FV\text{-}Assert]} 
\end{flalign*}

\section{Temporal Verification via a TRS}
\label{sec:Entailment_Prover}

The TRS  is an automated entailment checker to prove language inclusions among timed synchronous effects (cf. \defref{Inclusion} and \tabref{tab:rewriting_tree_send}). It is triggered i) prior to temporal property assertions; ii) prior to module calls for the precondition checking; and iii) at the end of verifying a module for the post condition checking. Given two effects \code{\effect_1,\ \effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.

During the effects rewriting process, the inclusions are in the form of \code{\Gamma \vdash  \effect_1 \CONTAIN^{\effect}  \effect_2 }, a shorthand for: \code{\Gamma \vdash  \effect \cdot \effect_1 \CONTAIN   \effect \cdot  \effect_2}. To prove such inclusions is to check whether all the possible timed traces in the antecedent \code{\effect_1} are legitimately allowed  in the possible timed traces from the consequent \code{\effect_2}.
\code{\Gamma} is the proof context, i.e., a set of effects inclusion hypothesis, \code{\effect} is the history effects from the antecedent that have been used to match the effects from the consequent.
Note that \code{\Gamma}, \code{\effect} are derived during the inclusion proof. 
The inclusion checking is initially invoked with \code{\Gamma{=}\{\}} and \code{\effect{=} True : \empt}.

\paragraph{\textbf{Effects Disjunctions.}}
An inclusion with a disjunctive antecedent succeeds if both disjunctions entail the consequent.  An inclusion with a disjunctive consequent succeeds if the antecedent entails either of the disjunctions.  
{ 
\input{rules/rule7}
}

Now, the inclusions are disjunction-free formulas. 
Next we provide the definitions and implementations of auxiliary functions \emph{Nullable}(\code{\delta}), \emph{First}(\code{fst}) and \emph{Derivative}(\code{D}) respectively.
Intuitively, the Nullable function \code{\delta(\es)} returns a boolean value indicating whether \code{\es} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \es)} computes a set of possible initial time instances of \code{\pure{\pi} : \es}; and the Derivative function \code{D_{I\# t}^{\pure{\pi}}(\es)} computes a next-state effects after eliminating one time instance \code{I} w.r.t. the execution time \code{t} from the current effects \code{\pure{\pi} : \es}.

%\subsection{closure of clock constrains}
%how to eliminate the unobservable transitions. 
%
%we allow the $\empt$transitions without carrying constraints and resetting clocks at the same time.

\begin{definition}[Nullable]\label{Nullable}
Given any time sequence \code{\es}, we recursively define \code{\delta(\es)} as:\\
{
\code{\delta(\es) :bool {=}
\begin{cases}
      \code{true} & \code{if\ \empt \in \es}\\
      \code{false} & \code{if\ \empt \notin \es}
    \end{cases} }
    }, where   
{ 
\begin{gather*}
\code{\delta(\bott) {=} false} 
\qquad\quad
\code{\delta(\empt) {=} true} 
\qquad\quad
\code{\delta(I){=} false}   
\qquad\quad
\code{\delta(\textbf{S}?){=} false}   
\qquad\quad\
    \code{\delta(\esn{\es}{\star} ) {=} true}   
\\ 
\code{\delta(\es_1 \seq \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
\qquad\qquad
  \code{\delta(\es_1 \choice \es_2) {=} \delta(\es_1) \vee \delta(\es_2)}   
  \qquad\quad
  \code{\delta(\esn{\es}{\omega} ) {=} false}     
  \\
\code{\delta(\es_1 || \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
\qquad\qquad\quad
 \code{\delta(\es \# t) {=} \delta(\es)}
\end{gather*}}
\end{definition}

To better outline our contribution, we first present the original \emph{First} function used in  Antimirov's rewriting system, denoted using \code{fst^\prime}, defined as follows:

\begin{definition}[Antimirov's First]\label{First1}
Let \code{fst^\prime(\es){:=}\{ I\ |\  (I \cdot \es^\prime) \in \llbracket  \es \rrbracket  \}} be the set of initial instances derivable from  sequence \code{\es}. (\code{\llbracket  \es \rrbracket } represents all the traces contained in \code{\es}.)
{ 
 \begin{gather*} 
\code{fst^\prime( \bott) {=} \{ \} } \qquad\ 
\code{ fst^\prime(\empt) {=} \{ \}} \qquad\ 
\code{fst^\prime( I) {=} \{ I \} }
 \qquad\ 
\code{fst^\prime(  \es_1 {\vee} \es_2) {=} fst^\prime(  \es_1) \cup fst^\prime(  \es_2)}
\\
{
\code{fst^\prime( \esn{\es}{\star} ) {=} fst^\prime({ \es})} 
\qquad\quad\
\code{fst^\prime(\es_1 {\seq} \es_2) {=} } 
\begin{cases}
      \code{\code{fst^\prime(  \es_1)} \cup \code{fst^\prime(  \es_2)} } \quad & \code{ if\ \delta(\es_1) {=} true}\\
      \code{\code{fst^\prime(  \es_1)}} & \code{  if\ \delta(\es_1) {=} false}
    \end{cases} 
    }
\end{gather*}
}
\end{definition}

As shown, \code{fst^\prime} does not handle 
%the concurrent operator \code{||} nor contains 
any arithmetic constraints, nor 
the real-time bounds constructor \code{\#}. Next, we define the novel  \emph{First} function used in this work, denoted using \code{fst}. 
%but helps to build up our \emph{First} function \code{fst}.

\begin{definition}[First]\label{First}
Let \code{fst_{\pure{\pi}}(\es){:=}\{ (I,  \pi, t) \ |\  \pi {\wedge} t{\geq}0 : (I\# t) \cdot \es^\prime \in \llbracket  \pi {:} \es \rrbracket \}} be the set of initial time instances derivable from effects \code{\pi {:} \es}. (\code{\llbracket  \pi {:} \es \rrbracket } represents all the time  traces contained in \code{\pi {:} \es}) 
{ 
 \begin{gather*} 
\code{fst_{\pure{\pi}}( \bott) {=} \{ \} } \qquad\quad
\code{fst_{\pure{\pi}}(\empt) {=} \{ \} } \qquad\quad
\code{fst_{\pure{\pi}}( I ) {=} \{ (I, \pi {\wedge} t{\geq}0, t) \}  \ (t\ is\ fresh)} 
\qquad\quad
   \code{fst_{\pure{\pi}}(  \es \# t) {=}  fst_{pi}(\es)}
 \\
\code{fst_{\pure{\pi}}( \esn{\es}{\star} ) {=} fst_{\pure{\pi}}({ \es})}
\qquad\quad
\code{fst_{\pure{\pi}}( \esn{\es}{\omega} ) {=} fst_{\pure{\pi}}({ \es})} 
\qquad\quad
\code{fst_{\pure{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{\pure{\pi}}(  \es_1) \cup fst_{\pure{\pi}}(  \es_2)  }  \\
\code{fst_{\pure{\pi}}( \textbf{S}? ) {=} fst_{\pure{\pi}}( \{\textbf{S}\} ) \cup fst_{\pure{\pi}}( \{ \overline{\textbf{S}} \} ) }
    \qquad\qquad\quad
   \code{fst_{\pure{\pi}}(  \es_1 {||} \es_2) {=} unify \ 
    (fst_{\pure{\pi}}(  \es_1)) \  (fst_{\pure{\pi}}(  \es_2))  }  
   \\
{
\code{fst_{\pure{\pi}}(\es_1 {\seq} \es_2) {=} } 
\begin{cases}
      \code{\code{fst_{\pure{\pi}}(  \es_1)} \cup \code{fst_{\pure{\pi}}(  \es_2)} } & \code{ if\ \delta(\es_1) {=} true}\\
      \code{\code{fst_{\pure{\pi}}(  \es_1)}} & \code{  if\ \delta(\es_1) {=} false}
    \end{cases} 
    }  
\end{gather*}
}
\end{definition}

\begin{definition}[First-Tuples Unification]\label{unify} Given two first tuples \code{(I_1, \pi_1, t_1)} and \code{(I_2, \pi_2, t_2) }, we define that: 
%We deploy a \code{unify} function to merge two time instances, where \\ 
\code{unify\ (I_1, \pi_1, t_1)\  (I_2, \pi_2, t_2) = (I_1 \cup I_2, \pi_1 \wedge \pi_2 \wedge (t1 {=} t2), t_1)}.
\end{definition}

\begin{definition}[Instances Subsumption]\label{Subsumption}
Given two instances \code{I} and \code{J}, we define the subset relation \code{I {\subseteq} J} as: the set of present signals in \code{J} is a subset of the set of present signals in \code{I}, and the set of absent signals in \code{J} is a subset of the set of absent signals in \code{I}\footnote{As in having more constraints refers to a smaller set of satisfying instances.}.
Formally, 
 \begin{gather*} 
 \code{I {\subseteq} J \Leftrightarrow  \{\textbf{S}\ |\ (\textbf{S} {\mapsto} Present) \in J \}  \subseteq  \{\textbf{S}\ |\ (\textbf{S} {\mapsto} Present) \in I \}} \\
  \code{ \quad\  and  \ 
 \{\textbf{S}\ |\ (\textbf{S} \mapsto Absent) \in J \}  \subseteq  \{\textbf{S}\ |\ (\textbf{S} \mapsto Absent) \in I \}
 }
\end{gather*}

\end{definition}

\begin{definition}[Time Instances Subsumption]\label{Subsumption1}
Given two time instances \code{(I, \pi_1, t_1)} and \code{(J, \pi_2, t_2)}, we define the subset relation \code{(I, \pi_1, t_1) {\subseteq} (J, \pi_2, t_2)} as:  \code{I {\subseteq} J} and \code{\pi_1[t_2/t_1]  {\Rightarrow}   \pi_2  }.

\end{definition}

\begin{definition}[Partial Derivative\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bott}; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}. Here we come up with a new notion of partial derivative for timed synchronous effects. 
}]\label{Derivative}
The partial derivative \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\es)} 
of effects \code{\pi : \es} 
w.r.t. a time instance \code{(I, \pi^\prime, t^\prime)} computes the  effects for the left quotient \code{(I, \pi^\prime, t^\prime)^{\text{-}1}\llbracket \pi : \es \rrbracket}. \footnote{For understanding of the derivative rule for \code{es\# t} (cf. \tabref{tab:rewriting_tree_send}  step \textcircled{3}), it is essentially splitting \code{\es} with a head and a tail, bound with fresh terms \code{t_1} and \code{t_2} respectively. Meanwhile it unifies \code{t_1} with \code{t^\prime} and  adds the constraint \code{t_1 {+} t_2 {=} t}.}
%\footnote{As the reader may notice, our First and Derivative function does not handle the timed sequences constructed by \code{||}, as the synchronous parallel is reduced during the normalization phase.}
\begin{gather*}
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\bott) {=}}  
 \code{False : \bott} 
\qquad\ 
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \empt) {=}}   
\code{False : \bott} 
\qquad \ 
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(es_1 || es_2)} {=} \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(es_1)} || \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}( es_2)} 
    \\
        \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \esn{\es}{\star}) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\es}) \cdot (\esn{\es}{\star})}  
        \qquad\qquad
                \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \esn{\es}{\omega}) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\es}) \cdot (\esn{\es}{\omega})}  
\\
{
 \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \es_1 \seq \es_2) {=} }
\begin{cases}
      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \es_1) \cdot  \es_2 \vee  D^{\pi}_{(I, \pi^\prime, t^\prime)}( \es_2)} \quad &\code{if\ \delta(\es_1) {=} true}   \\
      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}  ( \es_1) \cdot  \es_2} & \code{if\ \delta(\es_1) {=} false} 
    \end{cases} 
    }
 \\
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1 \choice \es_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1) \choice D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_2)} 
%\\
%\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1 \ ||\  \es_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1) \ ||\ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_2)} 
\\
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es \# t) } {=}
\code{
\pi \wedge(t_1{+} t_2 {=}t) \wedge (t_1{=}t^\prime) : (D^{\pi}_{(I, \pi^\prime, t^\prime)}(\es))\# t_2} \ \ \ 
\code{(fresh \ t_1\ t_2 )}
\\
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} \{\textbf{S}\})}
\qquad
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \textbf{S}?\ (}\code{ I {\not\subseteq} \{\textbf{S}\})}
\\
\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(J)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} J)}
\qquad\ 
    \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}( J)} {=} \code{False : \bott \ (}\code{I {\not\subseteq} J)} 
\end{gather*}
\end{definition}

\subsection{Rewriting Rules}
\label{InferenceRules}
Given the well-defined auxiliary functions above, we now discuss the key steps and related rewriting rules that we may use in such an effects inclusion proof.

\begin{enumerate}
\item 
\textbf{Axiom rules.}
\label{Base}
Analogous to  the standard propositional logic, \code{\bott} (referring to \textit{false}) entails any effects, while no \textit{non-false} effects entails \code{\bott}.
\input{rules/rule1}

\item 
\textbf{Disprove (Heuristic Refutation).}
\label{Refutation}
This rule is used to disprove the inclusions when the antecedent is nullable, while the consequent is not nullable. Intuitively, the antecedent contains at least one more trace (the empty trace) than the consequent. Therefore, the inclusion is invalid.

\vspace{-4mm}
\input{rules/rule2}

\item 
\textbf{Prove.}
\label{Prove}
We use two rules to prove an inclusion: (i) \codeme{[PROVE]} is used when the fst set of the antecedent is empty; and (ii) $\code{[REOCCUR]}$ to prove an inclusion
when there exist inclusion hypotheses 
in the proof context $\m{\Gamma}$, which are able to soundly prove the current goal. One of the special cases of this rule is when the identical inclusion is shown in the proof context, we then terminate the procedure and prove it as a valid inclusion. 
\input{rules/rule3}

\item 
\textbf{Unfolding (Induction).}
\label{unfolding}
This is the inductive step of unfolding the inclusions. Firstly, we make use of the auxiliary function \code{fst} to get a set of instances \code{F}, which are all the possible initial time instances from the antecedent. 
Secondly, we obtain a new proof context \code{\Gamma^\prime} by adding the current inclusion, as an inductive hypothesis, into the current proof context \code{\Gamma}. 
%(The soundness condition is guaranteed by rule \code{[REOCCUR]} to avoid the possible cyclicity evident in the proof context) 
Thirdly, we iterate each element \code{(I, \pi, t) \in F}, and compute the partial derivatives (\emph{next-state} effects) of both the antecedent and consequent w.r.t \code{(I, \pi, t)}. The proof of the original inclusion succeeds if all the derivative inclusions succeeds.
\input{rules/rule4}

\item 
\textbf{Normalization.}
We present a set of normalization rules to soundly transfer the timed effects into a normal form, in particular after getting their derivatives. 
Before getting into the above inference rules, we assume that the effects formulae are tailored accordingly based on the axioms shown in
\tabref{table:normalization}
We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A11), suggested by \cite{salomaa1966two}, which was designed for regular languages. We develop axioms (A12) to (A22) to further accommodate effects constructed by \code{||},   \code{\#} and \code{\omega}.

%\begin{table}[h]
%\vspace{0mm}
%  \caption{Some Normalization Lemmas for timed synchronous effects.}
%  \label{table:normalization}
%\setlength{\tabcolsep}{13pt}
%\renewcommand{\arraystretch}{1.1}
%\centering
%\vspace{0mm}
%\begin{tabular}{l || l || l}
%\hline
%  \code{\es \choice \es \rightarrow \es} 
%  &\code{\bott \cdot \es \rightarrow \bott }  
%  &
% 
%  
%\\ \hline
%
%  \code{\bott \choice \es \rightarrow \es } & \code{ \es  \cdot \bott \rightarrow \bott }  &
%
%\code{ (\es_1 \cdot \es_2) \cdot \es_3 \rightarrow \es_1 \cdot (\es_2 \cdot \es_3)}
%\\ \hline
%
%\code{ \es \choice \bott \rightarrow \es }
%&\code{\bott ^\star \rightarrow \empt}
%& 
%
%
%
%\\ \hline
%
%
% \code{\empt \cdot \es  \rightarrow \es }
% &  \code{\epsilon^\star \rightarrow \epsilon}
% &  
%
% 
%\\ \hline
%
%
%\code{ \es \cdot \empt \rightarrow \es}
%& \code{(\empt \vee \es)^\star \rightarrow \es^\star}
%& \code{ }
%
% 
% 
%\\ \hline
%
%
% 
%
%\\ \hline
%
%\end{tabular}
%\vspace{0mm}
%\end{table}

\begin{table}[h]
\caption{Normalization Axioms for Timed Synchronous Effects.}
\label{table:normalization}
\setlength{\tabcolsep}{10pt}
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{rl}
\footnotesize

\begin{minipage}[t]{0.4\textwidth}
\begin{tabular}{||l|l}
\hline
(A1)  &
\code{\es_1 \vee (\es_2 \vee \es_3) \rightarrow   (\es_1 \vee \es_2) \vee \es_3 }\\
\hline
(A2)  &
\code{\es_1 \cdot (\es_2 \cdot \es_3)\rightarrow     (\es_1 \cdot \es_2) \cdot \es_3 }\\
\hline
(A3)  &
\code{\es_1 \vee \es_2 \rightarrow   \es_2 \vee \es_1 }\\
\hline
(A4)  &
\code{\es \cdot (\es_1 \vee \es_2)  \rightarrow \es \cdot \es_1  \vee \es \cdot \es_2 }\\
\hline
(A5)  &
 \code{(\es_1 \vee \es_2)\cdot \es   \rightarrow \es_1 \cdot \es   \vee  \es_2 \cdot \es}\\
\hline
(A6)  &
 \code{\es \vee \es   \rightarrow \es}\\
\hline
(A7)  &
 \code{  \es \cdot \epsilon   \rightarrow \es}\\
\hline
(A8)  &
 \code{  \es \cdot  \bot \rightarrow \bot}\\
\hline
(A9)  &
 \code{\es \vee \bot   \rightarrow \es}\\
\hline
(A10)  &
 \code{\epsilon \vee (\es \cdot \es^\star)   \rightarrow  \es^\star}\\
\hline
(A11)  &
 \code{(\epsilon \vee \es)^\star   \rightarrow  \es^\star}\\
\hline

\end{tabular}
  \end{minipage}

  &
\footnotesize
  \begin{minipage}[t]{0.6\textwidth}
\begin{tabular}{||l|l|}
\hline
(A12)  &
\code{\bot^\omega  \rightarrow \bot }\\
\hline
(A13)  &
\code{\es^\omega \cdot \es_1 \rightarrow \es^\omega }\\
\hline
(A14)  &
\code{\epsilon^\omega \rightarrow \bot }\\
\hline
(A15)  &
\code{ \es\ ||\ \empt \rightarrow \es}\\
\hline
(A16)  &
\code{ \es\ ||\ \bott \rightarrow \bott}\\
\hline
(A17)  &
 \code{(I\# t) \cdot \es_1\ ||\ J \cdot\es_2 \rightarrow ((I  {\cup} J) \# t) \cdot (\es_1 || \es_2)}\\
\hline
(A18)  &
\code{\pi : (\es \# t_1 ) \# t_2 \rightarrow \pi  \wedge (t_1 {=} t_2) : \es \# t_1 }\\
\hline
(A19)  &
 \code{\empt \# t \rightarrow \empt}\\
\hline
(A20)  &
 \code{\bot \# t \rightarrow  \bott}\\
\hline
(A21)  &
 \code{{\pure{False}} : \es \rightarrow {\pure{False}} : \bott}\\
\hline
(A22)  &
 \code{{\pi} : \bott \rightarrow {\pure{False}} : \bott}\\
\hline
 %\code{\es \choice \es \rightarrow \es} 
%  &\code{\bott \cdot \es \rightarrow \bott }  
%  &

\end{tabular}
  \end{minipage}

\end{tabular}
\end{table}

\end{enumerate}

\begin{theorem}[Termination]\label{termination}
The rewriting system TRS is terminating.
\end{theorem}
\begin{proof}
See %the technical report\cite{TR}. 
\appref{proof:TerminationProof}.
\end{proof}

 \begin{theorem}[Soundness]\label{Cyclicsoundness}
Given an inclusion \code{\effect_1 \CONTAIN \effect_2}, if the TRS returns \code{TRUE} when proving \code{\effect_1 \CONTAIN \effect_2}, i.e., it has a cyclic proof, 
then \code{\effect_1 \CONTAIN \effect_2} is valid.
\end{theorem}

\begin{proof}
See %the technical report\cite{TR}. 
\appref{proof:SoundnessProof}.
\end{proof}

%\begin{lemma}
%The set of axioms (A1)-(A11) and (A15)-(A22) are complete for timed effects.
%\begin{proof} 
%
%\end{proof}
%\end{lemma}

 \begin{theorem}[Completeness]\label{Completeness}
 The set of axioms (A1)-(A22) is complete for timed synchronous effects.

%Given an inclusion \code{\effect_1 \CONTAIN \effect_2}, if \code{\effect_1 \CONTAIN \effect_2} is valid, then the TRS returns  \code{TRUE} by providing a proof.

\end{theorem}

\begin{proof} 
One can observe that by succinct applications of (A17) to (A22), we have a normal form, 
\begin{align}
\pi_1 : (I\# t_1) \cdot \es_1\ ||\ \pi_2 :  (J\# t_2) \cdot\es_2 \rightarrow  (\pi_1 \wedge \pi_2 \wedge t_1{=}t_2) :  ((I  {\cup} J) \# t_1) \cdot (\es_1\ ||\ \es_2)
\end{align}

Then for any ground timed synchronous effects \code{\es}, the expression \code{\epsilon || \es} can be reduced to either \code{\epsilon} or \code{\es} by the applications of (A15) and (A16).  
The expression \code{\es^\omega} can be reduced to either \code{\bot} or \code{\es^\omega} by the applications of (A12) to (A14).

Then, by the semantics defined in \figref{fig:Sementic}, effects constructed by Kleene star \code{\star} (possibly finite and possibly infinite) are supersets of effects constructed by \code{\omega} (definite infinite).

Then one can apply literally all the constructions of \cite{salomaa1966two} used in the completeness proof of \code{F_1} (A1) to (A11).

\end{proof}

\section{Implementation and Case Study}
\label{sec:Evaluation}

\subsection{Implementation}
To show the feasibility of our approach, we have prototyped our automated verification system 
using OCaml \emph{(A demo page  and source code are available from \cite{CODE})}. 
The proof obligations generated by the verifier are discharged using constraint solver Z3 \citep{de2008z3}. 
We prove termination and correctness of the TRS. We validate the front-end forward verifier for conformance, against two implementations: the Columbia Esterel Compiler (CEC) 
\cite{CEC} and Hiphop.js \cite{HH_im}.

CEC is an open-source compiler designed for research in both hardware and software generation from the Esterel synchronous language to C or Verilog circuit description. It currently supports a subset of Esterel V5, and provides pure Esterel programs for testing. Hiphop.js's implementation facilitates the design of complex web applications by smoothly integrating Esterel and JavaScript, and provides a bench of programs for testing purposes.

%The core implementation is less than 3500 LOC, roughly, 1000{+} LOC for the verifier, and 2000{+} LOC for the TRS. We prove the soundness of the TRS. 
%Next, we show case studies to demonstrate the feasibilities of our timed synchronous effects comparing to timed automata.

%We summarize the underlying reasons which lead to the improvement: (1)When the transition states of the models are small, the average execution time spent by the T.r.s is even less than the automata construction time, which means it is not necessary to construct the automata when a TRS solves it faster; (2)When the total states become larger, on average, the TRS outperforms automata-based algorithms, due to the significantly reduced search branches provided by the normalization lemmas; and (3)For the invalid cases, the TRS disproves them earlier without constructing the whole automata.

%\subsubsection{Experimental Setup}~\\

   %   \vspace{-2mm}

Based on these two benchmarks, we validate the verifier using 155  programs, varying from 15 lines to 300 lines. We manually annotate temporal specifications in our timed effects, including both succeeded and failed instances (roughly with the a 1:1 ratio). 
Out of the whole test suite, 101 were from the CEC benchmark, 54 were from the Hiphop.js benchmark.  Since async-await was inherited from JavaScript features, it only presents in the 54 hiphop.js programs.
We conduct experiments on a MacBook Pro with a 2.6 GHz Intel Core i7 processor. Given our benchmark, the running time varying from 0 to 500 ms.

%We claim that the extra expressiveness gained from our logic is the symbolic time-bounds. The timed effects represent not only one exact Timed Automata but also a set of Timed Automata. Together with our back-end inclusion solver, it enables a verification framework for a group of Automata. More specifically, instead of running the model checker many times for one non-deterministic time-bound at each time, we can define arithmetic constraints bounding the time variable. And to test that, we cover a number of test cases with function calls, and the callee's parameters would be used as the time bounds.

Our implementation is the first that solves the  inclusion problem of symbolic timed automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i. e., whose timing constants are not known yet), and hence cannot be used in early design phases; ii) verifying a system for a set of timing constants usually requires to enumerate all of them one by one if they are supposed to be integer-valued; in addition, timed automata cannot be used to verify a system for a set of timing constants that are to be taken in a real-valued dense interval.

A term rewriting system is efficient because \emph{it only constructs automata as far as it needed}, which makes it more efficient when disproving incorrect specifications, as we can disprove it earlier without constructing the whole automata. In other words, the more incorrect specifications are, the more efficient our solver is.

%
%\subsubsection{Experimental Results}~\\
%\label{subsec:Experimental_Results}
%
%\begin{table}[h]
%        \vspace{-2mm}
%\caption{\label{tab:Experimental} The experiments are based on 16 real world C programs, we record the lines of code (LOC), the number of testing temporal properties ($\#$Prop.), and the (dis-) proving times (in milliseconds) using PAT and our T.r.s respectively. }
%\centering
%\footnotesize
%\renewcommand{\arraystretch}{1.1}
%\begin{tabular} {l|c|c|c|c}
%\hline
%\textbf{Programs} & \textbf{LOC} & \textbf{$\#$Prop.}  & \textbf{PAT(ms)} & \textbf{T.r.s(ms)} \\ \hline\hline
%1. Chrome\_Dino\_Game    &      80    &    12  &  32.09 &  7.66  \\ \hline
%2. Cradle\_with\_Joystick  &      89     &   12   &  31.22    &   9.85  \\ \hline
%3. Small\_Linear\_Actuator  &    180  &     12  &   21.65      &  38.68  \\ \hline
%4. Large\_Linear\_Actuator &    155   &    12   &  17.41   &   14.66   \\ \hline
%5. Train\_Detect  &                    78   &     12    &   19.50   & 17.35     \\ \hline
%6. Motor\_Control  &                 216  &    15  &     22.89  &  4.71  \\ \hline
%7. Train\_Demo\_2  &                133  &   15    &     49.51   &  59.28   \\ \hline
% 8. Fridge\_Timer  &                  292   &    15   &   17.05   & 9.11 \\ \hline
%  9. Match\_the\_Light   &         143     &    15  &  23.34    &  49.65 \\ \hline
%   10. Tank\_Control  &              104   &    15    &  24.96   &   19.39 \\ 
%     \hline
%  \textbf{\quad \ \ Total}  & 2546    &  235   &  446.88   &   305.33   \\ \hline
%\end{tabular}
%        \vspace{0mm}
%\end{table}
%
%
%        \vspace{-2mm}
%
%
%

\subsection{Case Studies}
\label{subsec:Case_Studies}

Let's recall the existing challenges in different programming paradigms discussed in \secref{sec:Preliminaries}. In this section, we first investigate how our effects logic can help to debug errors related to both synchronous and asynchronous programs. Specifically, it effectively resolves the logical correctness checking (for synchronous languages) and critical anti-patterns checking (for premise asynchrony). 
Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.

%how our proposal makes it flexible for different effects logics.

\subsubsection{Logical Incorrect Catching}~\\
\label{subsec:LogicalIncorrectCatching}

      \vspace{-2mm}
%We say that the program is logically reactive (resp. logically deterministic) w.r.t. the input event if there is at least (resp. at most) one logically coherent global status.

%A program is logically correct if there exists precisely \textbf{one} status for each signal that respects the coherence law. 
%it is both logically reactive and deterministic. 
%To effectively check logical correctness, 
We regard these programs, which have precisely one safe trace reacting to each input assignments, as logical correct. 
To effectively check logical correctness, in this work, given a synchronous  program, after been applied to the forward rules, we compute the possible execution traces in a disjunctive form; then prune the traces contain contradictions, following these principles: (i) explicit present and absent; (ii) each local signal should have
only one status; (iii) lookahead should work for both present and absent; (iv) signal emissions are idempotent; (v) signal status should not be contradictory.
Finally, upon each assignment of inputs, programs have none or multiple output traces that will be rejected, corresponding to no-valid or multiple-valid assignments.

\begin{table}[h]
\centering
\begin{tabular}{c|c|c}
\footnotesize
\begin{minipage}[t]{0.32\textwidth}
\begin{enumerate}
  \item  \code{\key{present}\ S1 } 
  \\
 \code{\langle  \textcolor{darklavender}{true : \{\}} \rangle }

  \item    \code{~\qquad \jskey{then}}
   \\
 \code{\langle  \textcolor{darklavender}{true : \{S1\} } \rangle }
   \item    \code{~\qquad~\qquad \key{nothing}}
         \\
 \code{\langle  \textcolor{darklavender}{true : \{S1, \overline{S1}\}} \rangle }
  \item \code{~\qquad  \jskey{else} }
  \\
 \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}\} } \rangle }
  \item    \code{~\qquad~\qquad \key{emit}\ S1 }
     \\
 \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}, S1\}} \rangle }
     \item    \code{  \key{end}\  \key{present} }
     \\
 \code{\langle  \textcolor{darklavender}{true : \{S1, \overline{S1}\} \vee \{\overline{S1}, S1\}} \rangle }
     \\
      \code{\langle  \textcolor{darklavender}{false : \bot} \rangle }

\end{enumerate}

  \end{minipage}

  &
  \small
  \begin{minipage}[t]{0.32\textwidth}
   \begin{enumerate}
  \item  \code{\key{present}\ S1 } 
  \\
 \code{\langle  \textcolor{darklavender}{true : \{\}} \rangle }

  \item    \code{~\qquad \jskey{then}}
   \\
 \code{\langle  \textcolor{darklavender}{true : \{S1\} } \rangle }
  \item    \code{~\qquad~\qquad \key{emit}\ S1 }
     \\
 \code{\langle  \textcolor{darklavender}{true : \{{S1}, S1\}} \rangle }

  \item \code{~\qquad  \jskey{else} }
  \\
 \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}\} } \rangle }
   \item    \code{~\qquad~\qquad \key{nothing}}
         \\
 \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}, \overline{S1}\}} \rangle }
     \item    \code{  \key{end}\  \key{present} }
     \\
 \code{\langle  \textcolor{darklavender}{true : \{{S1}, S1\} \vee \{\overline{S1}, \overline{S1}\}} \rangle }
     \\
      \code{\langle  \textcolor{darklavender}{true : \{{S1}\} \vee \{\overline{S1}\} }\rangle }

\end{enumerate}

  \end{minipage}

    &
  \small
  \begin{minipage}[t]{0.32\textwidth}
   \begin{enumerate}
  \item  \code{\key{abort} } 
    \\
 \code{\langle  \textcolor{darklavender}{true : emp} \rangle }     
       \item  \code{~\qquad \key{yield}}  
           \\
 \code{\langle  \textcolor{darklavender}{true : \{\}} \rangle }
 \item  \code{~\qquad \key{emit}\ A}  
      \\
 \code{\langle  \textcolor{darklavender}{true : \{A\}} \rangle }

            \item  \code{ \key{when}\  A} 
      \\
 \code{\langle  \textcolor{darklavender}{true : \{A, \overline{A}\} \vee \{\overline{A}, A\} } \rangle }
      \\
      \code{\langle  \textcolor{darklavender}{false : \bot} \rangle }

\end{enumerate}

  \end{minipage}

  \\
&& 
 \\
(a) 
&
(b)
&
(c)

\end{tabular}

       \vspace{5mm}
      \caption{Logical incorrect examples, caught by the effect logic.}\label{fig:Logical_Incorrect}
         \vspace{-4mm}
\end{table}

As shown in \figref{fig:Logical_Incorrect} (a), there are no valid assignments of signal {\textbf{S1}} in this program. 
As shown in in \figref{fig:Logical_Incorrect} (b), it is also logical incorrect because there are two possible assignments of signal {\textbf{S1}} in this program. 
As the example shows in \figref{fig:Logical_Incorrect} (c), it is logical incorrect because: if the abortion does not happen, indicating {\textbf{A}} is absent, then the program emits {\textbf{A}}. If the abortion does happen, indicating {\textbf{A}} is present, then the program does nothing leaving {\textbf{A}} absent. Both way lead to contradiction.

\subsubsection{A Strange Logically Correct Program.}~\\

\begin{wrapfigure}{R}{0.6\columnwidth}
      \vspace{-6mm}
\begin{lstlisting}[columns=fullflexible]
fork { present S1 then emit S1 else nothing end present
}par { present S1 
				then	present S2 
						then nothing 
						else emit S2 end present 
				else nothing 
		end present}        
\end{lstlisting}  
      \vspace{-1mm}
      \caption{Logical Correct.}\label{fig:A_Strange}
         \vspace{-2mm}
\end{wrapfigure}

      \vspace{-2mm}
Another example for synchronous languages shows that composing programs can lead to counter-intuitive phenomena. As the program shows in \figref{fig:A_Strange}, 
the first parallel branch is the logical incorrect program \figref{fig:Logical_Incorrect} (b), while the second branch contains a non-reactive program enclosed in  "present {\textbf{S1}}" statement. Surprisingly, this program is logical correct, since there is only one logically coherent assumption: {\textbf{S1}} absent and {\textbf{S2}}  absent. With this assumption, the first present {{S1}}  statement takes its empty else branch, which justifies {{S1}}  absent. The second "present \code{\textbf{S1}}" statement also takes its empty else branch, and "emit {\textbf{S2}}" is not executed, which justifies {\textbf{S2}}  absent. And our effects logic is able to soundly detect above mentioned correctness checking.

\subsubsection{Semantics of Await}~\\

      \vspace{-2mm}
We use 
\tabref{tab:await} as an example to demonstrate the semantics of \code{A?}, i.e., "waiting for the signal \code{A}". 
%of the \code{Await} language structure.
%Awaiting an event \code{A} is represented as \code{A?}.
Formally, we define, 
%And the semantic of

\vspace{-4mm}
{\small
\begin{align*}
A? \equiv \exists n, n{\geq}0 \wedge \{\overline{A}\}^n \cdot\{A\}
\end{align*}
}
\vspace{-4mm}

\noindent where\code{\{\overline{A}\}} refers to all the time instances containing \code{A} to be absent.

As shown in \tabref{tab:await},
the LHS \code{\{A\}\cdot\{C\}\cdot B? \cdot \{D\}} entails the
RHS \code{\{A\}\cdot B? \cdot \{D\}}, as intuitively \code{\{C\}\cdot B?} is a
special case of \code{B?}.
In step \code{\textcircled{1}}, \code{\{A\}} is eliminated.
In step \code{\textcircled{3}}, \code{B?} is normalised into 
\code{\{B\} \vee (\{\overline{B}\}\cdot B?)}, 
%In step \code{\textcircled{3}}, \code{B?} is unfolded into 
%\code{(\epsilon \vee \{\overline{B}\})\cdot B?}, and 
By the step of \code{\textcircled{4}}, 
\code{\{C\}} is eliminated 
together with \code{\{\overline{B}\}} because \code{\{C\} \subseteq \{\overline{B}\}}.
Now the rest part is \code{B? \cdot \{D\} \CONTAIN B? \cdot \{D\}}.
Here, we further normalise \code{B?} from the LHS into a disjunction, leading to two proof sub-trees. 
From the first sub-tree, we keep unfolding the inclusion with \code{\{B\}} (\code{\textcircled{6}}) and \code{\{D\}} (\code{\textcircled{7}}) till we can prove it. 
Continue with the second sub-tree, we unfold it with \code{\{\overline{B}\}}; then in step \code{\textcircled{8}} we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. We prove it using the \code{[REOCCUR]} rule and finish the whole writing process. 
%Finally from  to \code{\textcircled{7}},
%we find the inclusion reoccurs, hence we prove this example.

{
\begin{table*}[h]
\centering
      \vspace{0mm}
\caption{\label{tab:await} The example for Await.}

\vspace{-2mm}
\begin{adjustbox}{width=0.87\textwidth}
 \Large\begin{tabular}[t]{l}
  \hline\\
{

\begin{prooftree}

\Hypo{
  \code{    
     \empt
    \CONTAIN    
  \empt
  }
}

\Infer[dashed]1[{\siderule{\textcircled{7}[PROVE]}}]{
  \code{    
   \cancel{ \{D\}}
    \CONTAIN    
   \cancel{ \{D\}}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{6}[UNFOLD]}}]{
  \code{    
    \cancel{\{ B\}} \cdot \{D\}
    \CONTAIN   
     (\cancel{\{B\}} \vee \bot) \cdot \{D\}
  }
}
%%%%%%%%%%%

\Hypo{
  \code{    
     B? \cdot \{D\}
    \CONTAIN
     B? \cdot \{D\} \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{8}[REOCCUR]}}]{
  \code{    
     \cancel{\{\overline{B}\}} \cdot B? \cdot \{D\}
    \CONTAIN    
      (\bot \vee (\cancel{\{\overline{B}\}} \cdot B?)) \cdot \{D\}
  }
}

\Infer[dashed]2[{\siderule{\textcircled{5}[Disj\text{-}L]}}]{
  \code{    
     B? \cdot \{D\}
    \CONTAIN    
     B? \cdot \{D\} \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{4}[Normalisation]}}]{
  \code{    
     \cancel{\{C\}} \cdot B? \cdot \{D\}
    \CONTAIN    
     (\bot \vee (\cancel{\{\overline{B}\}} \cdot B?)) \cdot \{D\}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{
  \code{
     \{C\}\cdot B? \cdot \{D\}
    \CONTAIN
     (\{B\} \vee (\{\overline{B}\}\cdot B?)) \cdot \{D\}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{2}[Normalisation]}}]{
  \code{
     \cancel{\{A\}}\cdot\{C\}\cdot B? \cdot \{D\}
    \CONTAIN
     \cancel{\{A\}}\cdot B? \cdot \{D\}
  }
}
\Infer[dashed]1[{\siderule{\textcircled{1}[UNFOLD]}}]{
  \code{
    \textcolor {darkred}{True} : \{A\}\cdot\{C\}\cdot B? \cdot \{D\}
    \CONTAIN
    \textcolor {darkred}{True} : \{A\}\cdot B? \cdot \{D\}
  }
}

\end{prooftree}}
\\~\\

\hline

\end{tabular}
\end{adjustbox}
            \vspace{-1mm}
\end{table*}
}

\subsubsection{Broken Promises Chain} ~\\

      \vspace{-2mm}
As the prior work \cite{madsen2017model,alimadadi2018finding} present, one of the critical issues of using promise is the broken chain of the interdependent promises; and they propose the \emph{promise graph}, as a graphical aid, to understand and debug promise-based code.

%provide solutions to detect such anti-patterns by constructing

\begin{definition}[Well-Synchronised Traces]\label{WELL}
Based on the syntax (\secref{subsec:Specification_Semantics}) and semantics (\secref{subsec:Specification_language}) defined for timed synchronous effects, in this paper, we call traces without any blocking signals well-synchronised traces. 
\end{definition}

We here show that our algebraic effects can capture non well-synchronised traces during the   
rewriting process by computing the derivative.   
 For example, the parallel composition of traces:
\begin{align*}
\{\textbf{A}\}\cdot\{\textbf{B}\}\cdot\{\textbf{C}\} \cdot\{\textbf{D}\}\  || \ \{\textbf{E}\}\cdot\ \textbf{C}? \cdot\{\textbf{F}\}
\end{align*}
 leads to the final behaviour of $\{\textbf{A},\textbf{E} \}\cdot\{\textbf{B}\}\cdot\{\textbf{C}\}\cdot\{\textbf{D}, \textbf{F}\}$, which is well-synchronised for all the time instances. However, if we were composing traces:
 \begin{align*}
\{\textbf{A}\}\cdot\{\textbf{B}\} \cdot\{\textbf{D}\}\  || \ \{\textbf{E}\}\cdot\ \textbf{C}? \cdot\{\textbf{F}\}
\end{align*}
due to the reasons that forgetting to emit {\textbf{C}} (In JavaScript, it could be the case that forgetting to explicitly return a promise result), it leads to a problematic trace  $\{\textbf{A},\textbf{E} \}\cdot\{\textbf{B}\}\cdot\{\textbf{D}\} \cdot \textbf{C}? \cdot \{\textbf{F}\}$. The final effects contain a dangling signal waiting of {\textbf{C}}, which  indicates the corresponding anti-pattern.

\subsubsection{Handling Finite and Infinite Effects Simultaneously}~\\
\label{rec:finit_infinite}

      \vspace{-2mm}
To further demonstrate the expressiveness of our timed effects, we use an example shows in \figref{fig:case_study_finit_infinit}
It declares a recursive module named \code{send}, making a deterministic choice depending on input \code{n}: in one case it emits one  signal  \anyevent{Done}; otherwise it emits a signal 
\anyevent{Send}, then makes a recursive call with parameter \code{n{-}1}.  Note that the post condition contains both finite effects and infinite effects in one single formula, separated by arithmetic constrains.

\begin{wrapfigure}{R}{0.5\columnwidth}
      \vspace{-2mm}
\begin{lstlisting}[columns=fullflexible]
hiphop module send (var n, out Send, out Done)
/*@ requires true : emp @*/
/*@ ensures	(n>=0 : {}^*. {Done}) 
          \/ (n<0   : {Send}^w)  @*/
{
	if (n==0) { emit Done; }
	else {
		emit Send;
		yield;
		send (d, n-1, Send, Done); }}
\end{lstlisting}  
      \vspace{-1mm}
      \caption{A recursive \ttfamily{Send} module.}\label{fig:case_study_finit_infinit}
         \vspace{-2mm}
\end{wrapfigure}

We here bring up the discussion distinguishing our work from the closely related prior work,  which deploys an effects tuple (\code{\effect_{u},\effect_{v}}) \cite{nanjo2018fixpoint},  separating the finite (\code{\effect_{u}}) and infinite (\code{\effect_{v}}) effects, therefore it leads to separated sets of effects semantics, and a separated reasoning on inductive and co-inductive definitions. 
%The paper cites a piece of work by Nanjo et al. [27] which is very closely related to this paper. They also define an effect system capturing finite and infinite temporal behaviours, including contexts and effects that can depend on program variables. They also give a proof system for discharging obligations that come up in type checking. Yet the present paper does not discuss them in any detail. The only mention is an off-hand comment about this work handling finite and infinite behaviors together while Nanjo et al. do not, which seems completely incorrect to me.
In our work, by merging finite and infinite effects into a single disjunctive form, it not only eliminates duplicate operators, but also enables an effective reasoning of both effects logics simultaneously.  
The inclusion checking process on the \code{send}'s postcondition is demonstrated in \tabref{tab:rewriting_tree_case_study_finit_infinit} [REOCCUR], which finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{brotherston2005cyclic}.

{
\begin{table*}[h]
\centering
      \vspace{0mm}
\caption{\label{tab:rewriting_tree_case_study_finit_infinit} Term Rewriting for \figref{fig:case_study_finit_infinit} (We use \code{(\dagger)} to indicate the pairing of buds with companions.)}

\vspace{0mm}
\begin{adjustbox}{width=1\textwidth}
 \Large\begin{tabular}[t]{l}
  \hline\\
{

\begin{prooftree}
\Hypo{
\code{
\textcolor {darkred}{n{=}0} \Rightarrow \textcolor {darkred}{n{\geq}0} \qquad emp \subseteq \{\}^\star \qquad  \code{\siderule{[PROVE]}}
}
}
\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : emp
 \CONTAIN \textcolor {darkred}{n{\geq}0} :  \bot \vee \{\}^\star \vee emp }  
 }
\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : {\{Done\}} 
 \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} }  
 }
\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : \{Done\} 
 \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} \vee
 \textcolor {darkred}{n{<}0} :
  \{Send\}^\omega}  }
  \Hypo{
\code{ \textcolor {darkred}{n {\neq} 0} {:}  \{Send\}^\omega 
 \CONTAIN 
 \textcolor {darkred}{n{<}0} {:}
  \{Send\}^\omega  (\dagger) } 
}
  \Infer[dashed]1[\code{\siderule{[REOCCUR]}}]{\code{ \textcolor {darkred}{n {\neq} 0} {:}  \{Send\}^\omega 
 \CONTAIN 
 \textcolor {darkred}{n{<}0} {:}
  \{Send\}^\omega}  (\dagger)
  }
  \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \{Send\}^\omega 
 \CONTAIN 
 \textcolor {darkred}{n{<}0} :
  \{Send\}^\omega}  
  }
  \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post}
 \CONTAIN 
 \textcolor {darkred}{n{<}0} :
  \{Send\}^\omega}  
  }
  \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post} 
 \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} \vee
 \textcolor {darkred}{n{<}0} :
  \{Send\}^\omega}  }
 \Infer[dashed]2[]{\code{ \textcolor {darkred}{n{=}0} : \{Done\} \vee  \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post} 
 \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} \vee
 \textcolor {darkred}{n{<}0} :
  \{Send\}^\omega}  }
\end{prooftree}}
\\~\\

\hline

\end{tabular}
\end{adjustbox}
            \vspace{0mm}
\end{table*}
}

\subsubsection{Prove it when Reoccur}~\\

      \vspace{-2mm}
%(\code{\{Go\} \Rightarrow \{\}})
%(\code{\{Ready\} \Rightarrow \{\}}, \code{t_L^2 \Rightarrow true})
Termination of TRS is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic}, i.e., the rule \code{[REOCCUR]}. % Check out this following example:

As shown in \tabref{tab:reoccur}, the LHS formula is a disjunction of two effects. An inclusion with a disjunctive antecedent succeeds if both disjunctions entail the consequent, shown in step \code{\textcircled{1}}.  
%Now we have 2 subtrees, the first subtree is for
%  \code{
%    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \# t_L \cdot \{B\}
%    \CONTAIN
%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
%  }
%and the second one is for
%  \code{
%    \textcolor {darkred}{True} : {B} \CONTAIN
%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
%  }.
%In order to prove the original proposition, both of the two new propositions have
%to be proved.
%Using the disjunction rule \code{\effect_1 \vee \effect_2 \CONTAIN \effect \iff
%\effect_1 \CONTAIN \effect \ and \  \effect_2 \CONTAIN \effect}, we split the proposition
%in . 
In step \code{\textcircled{2}} of the first sub-tree, in order to eliminate the first instance \code{\{B\}}, \code{\{A\}^\star \# t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch. 
% is 
%eliminated by \code{\epsilon}, 
Then in steps \code{\code{\textcircled{4}}}, we
can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} succeed.
%and \code{\epsilon \CONTAIN \epsilon}.

Looking at the second sub-tree, in step \code{\textcircled{5}}, \code{t_L} and \code{t_R} are firstly split 
into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
Then in step \code{\textcircled{6}}, 
\code{\{A\} \# t_L^1} together with \code{\{A\} \# t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
%, also
%are unified as new constraint \code{t_L^1{=}t_R^1}.
In step \code{\textcircled{7}}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
%one in
%step \code{\textcircled{1}}, 
Hence we apply the rule \code{[REOCCUR]} to prove it with a succeed side constraints entailment: \code{\textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    }\Rightarrow
    \textcolor {darkred}{t_R{<}4} }. 
%Since the structure of terms \code{t_L^2, t_L} and \code{t_R^2, t_R} are isomorphic,
%we will need to unify \code{t_L^2} and \code{t_R^2} in order to get enough
%time constraints. And in step \code{\textcircled{5}} we prove the proposition to
%be true.

{
\begin{table}[h]
      \vspace{0mm}
\caption{\label{tab:reoccur} The reoccurrence proving example. 
\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}

\vspace{-1mm}
\begin{adjustbox}{width=1\textwidth}
 \Large\begin{tabular}[t]{l}
  \hline\\

\code{I:}\
{

\begin{prooftree}

\Hypo{
  \code{
    \textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True} \qquad
    \epsilon \CONTAIN \epsilon
  }
}

\Infer[dashed]1[{\siderule{\textcircled{4}[PROVE]}}]{
  \code{
    \textcolor {darkred}{True} : \epsilon \CONTAIN
    \textcolor {darkred}{True} : \epsilon
  }
}

\Infer[dashed]1[{\siderule{\textcircled{3}[Normalisation]}}]{
  \code{
    \textcolor {darkred}{True} : \cancel{\{B\}} \CONTAIN
    \textcolor {darkred}{True} : \cancel{\empt \cdot \{B\}}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{2}[UNFOLD]}}]{
  \code{
    \textcolor {darkred}{True} : \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
  }
}
\Hypo{\code{II}}

\Infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \# t_L {\cdot} \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \# t_R {\cdot} \{B\}
  }
}

\Infer[dashed]2[{\siderule{\textcircled{1}[Disj\text{-}L]}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \# t_L \cdot \{B\}
    \vee \textcolor {darkred}{True} : \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
  }
}
\end{prooftree}}
\\~\\

\hline \\
\code{II:} 
{\begin{prooftree}
\Hypo{
  \code{
    \textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    } \Rightarrow
    \textcolor {darkred}{t_R{<}4} 
%\qquad
%     \{A\}^\star \cdot \{B\}
%    \CONTAIN
%     \{A\}^\star \cdot \{B\}
  }
}

\Infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {
      darkred}{\cdots {\wedge} \cdots
%      
%      t_L^1{+}t_L^2{=}t_L{<}3 {\wedge} t_R{=}t_R^1{+}t_R^2 {\wedge} t_L^1{=}t_R^1
%      {\wedge} t_L^2{=}t_R^2
    } :
     \{A\}^\star \# t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} :
     \{A\}^\star \# t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{7}[REOCCUR]}}]{
  \code{
    \textcolor {
      darkred}{
%t_L^1{+}t_L^2{=}t_L {\wedge} t_R{=}t_R^1{+}t_R^2 {\wedge}      
       t_L^1{=}t_R^1
    } :
     \cancel{\{A\} \# t_L^1} {\cdot} \{A\}^\star \# t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} :
     \cancel{\{A\} \# t_R^1} {\cdot} \{A\}^\star \# t_R^2 \cdot \{B\}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{6}[UNFOLD]}}]{
  \code{
    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L {\wedge} t_R{=}t_R^1{+}t_R^2} :
     ( \{A\} \# t_L^1 {\cdot} \{A\}^\star \# t_L^2) \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} :
     ( \{A\} \# t_R^1 {\cdot} \{A\}^\star \# t_R^2) \cdot \{B\}
  }
}

\Infer[dashed]1[{\siderule{\textcircled{5}[SPLIT]}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \# t_L \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}  \quad \textcolor{darklavender}{(\ddagger)}
  }
}
\end{prooftree}}

\\~\\

\hline

\end{tabular}
\end{adjustbox}
            \vspace{-3mm}
\end{table}
}

\subsection{Discussion}

As the examples show, our proposed effects logic and the abstract semantics for \code{\lambda_{HH}} not only tightly capture the behaviours of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm. Meanwhile, the inferred temporal traces from a given reactive program enable a compositional timed temporal verification at the source level, which is not yet supported by existing temporal verification techniques.

\section{Related Work}\label{sec:Related_work}

This work is related to i) semantics of synchronous languages and asynchronous promises; ii) research on real-time system modelling and verification; and iii) existing traces-based effects systems.

\subsection{Semantics of Esterel and JavaScript's asynchrony} 
% 
The web orchestration language HipHop.js \cite{berry2020hiphop} integrates Esterel’s synchrony with JavaScript’s asynchrony, which provides the infrastructure for our work on mixed synchronous and asynchronous concurrency models. To the best of authors' knowledge, the inference rules in this work formally define the first axiomatic semantics for a core language of HipHop.js, which are established on top of the existing semantics of Esterel and JavaScript's asynchrony.

For the pure Esterel, the communication kernel of the Esterel synchronous reactive language, 
prior work gave two semantics, a macrostep logical semantics called the behavioural semantics \cite{berry1999constructive}, and a small-step semantics called execution/operational semantics \cite{berry1992esterel}. 
%A subsequent work \cite{} gave an update to the logical behavioural macrostep semantics to make it more \emph{constructive}. 
%The logical behavioural semantics requires existence and uniqueness of a behaviour, while the constructive behavioural semantics introduces \emph{Can} function to determine execution paths in an effective but restricted way. 
Our timed synchronous effects of Esterel primitives closely follow the work of states-based semantics \cite{berry1999constructive}. In particular, we borrow the idea of internalizing state into effects using \emph{history} instance trace and \emph{current} time instance, that bind a partial store embedded at any level in a program. However, as the existing semantics are not ideal for compositional reasoning in terms of the source program, our forward verifier can help meet 
this requirement for better modularity.

In JavaScript programs, the primitives \code{async} and \code{await} serve for \emph{promises}-based (supported in ECMAScript 6 \cite{ecma1999262}) asynchronous programs, which can be written in a synchronous style, leading to more scalable code. 
However, the ECMAScript 6 standard specifies the semantics of promises informally and in operational terms, which is not a suitable basis for formal reasoning or program analysis. Prior work \cite{madsen2017model,alimadadi2018finding}, in order to understand promise-related bugs, present the \code{\lambda_p} calculus, which provides a formal semantics for JavaScript promises. Based on these, our work defines the semantics of \code{async} and \code{await} in the event-driven synchronous concurrent context. In particular, the asynchronous primitive \code{setTimeout} provides the lower real-time bounds, cooperating with the preemptive primitive \code{abort} from Esterel,  which provides the upper real-time bounds for the program execution.

%``Traditional" FRP was initially implemented as an embedded langauge in Haskell\cite{hudak1996building}, making assertions about the cost of a computation was non-trivial. Embedding a language into a higher-order language introduces all of the power of the lambda calculus. Inherent in this expressiveness is the possibility of writing programs that perform unreasonable or unbounded amounts of computation as each step, or that have subtle space leaks\cite{mitchell2013leaking}.

%Real-time FRP (RT-FRP) \cite{wan2001real} ensures that signals cannot be used in ways that do not have an efficient implementation. RT-FRP uses a two-tiered language: an unrestricted base language ($\lambda$-calculus with recursion) and a limited reactive language for manipulating signals, which supports recursion but not higher- order functions (making it less expressive than traditional FRP). RT-FRP ensures that reactive updates will terminate as long as the base language terms terminate, and memory will not grow unless it grows in the base language.

%Elm \cite{czaplicki2013asynchronous} uses two-tiered language, and event driven in that no changes need to be propagated unless the value of a signal has changed, which improves efficiency of the computation. Apart from that, the most important novelty of Elm is it permits inter-signal asynchrony: relaxing the order of events between multiple signals.

%Several languages have been proposed around the synchronous data-flow notion of computation. The general-purpose functional language Lucid\cite{wadge1985lucid} is an example of this style of language. More relevant to the present paper are the language Signal\cite{gautier1987signal}, Lustre\cite{pilaud1987lustre}, and Esterel\cite{berry1992esterel}, which were specifically designed for control of real-time systems. This is a analogous to the sequence of values generated in the execution of an RT-FRP program. However, none of these synchronous data flow language seem to have considered recursion.

\subsection{Specifications and Real-Time Verification}

%Formally, given a KA is \code{(A,+,\cdot, \star,  0, 1)}, a SKA over a finite set \code{A_B} is \code{(A,+, \cdot, \times, \star,  0, 1,  A_B)}, \code{A_B {\subseteq} A}. 
%Our \code{\bot} corresponds to the \code{0}; our \code{\empt} corresponds to the \code{1}; our \emph{time instance} containing simultaneous signals can be expressed via \code{\times};

Compositional specification for real-time systems based on timed process algebras has been extensively studied. Examples include the CCS\code{\text{+}}Time \cite{yi1991ccs} and Timed CSP \cite{dong2008timed}.  
The differences are: 
i) in CCS\code{\text{+}}Time, if there is no timed constraints specified, transitions takes no time; whereas in our effects logic, it means \code{true} (arbitrary time), which is more close to the real life context where the time bounds are often unpredictable.
ii) Timed CSP does not allow explicit representation of real-time through the manipulation of clock variables.

%relies on implicit clocks, which means it

There have been a number of translation-based approaches on building verification support for timed process algebras. For example, Timed CSP \cite{dong2008timed} is translated to Timed Automata (TA) so that the model checker Uppaal can be \cite{larsen1997uppaal} applied. 
TA are finite state automata equipped with clock variables. Models based on TA often have simple structures. For example, the input models of the Uppaal are networks of TA with no hierarchy.

%Given the well-established TA techniques,

In practice, system requirements are often structured into phases, which are then composed in many different ways, while TA is deficiency in modelling complex compositional systems. Users often need to manually cast high-level requirements into a set of clock variables with carefully calculated clock constraints, which is tedious and error-prone \cite{sun2013modeling}. 
%Also real-time system modelling based on timed process algebras often suffers from lack of language features or automated tool support. 
On the other hand, all the translation-based approaches share the common problem: 
%i) the worst-case complexity of any efficient  equivalences/inclusion checking algorithm \cite{de2006antichains} %based on such translation 
%goes  exponential in the number of automata states; and ii) 
the overhead introduced by
the complex translation makes it particularly inefficient when \emph{disproving} properties.

We believe in that the goal of verifying real-time systems, in particular safety-critical systems is to check logical temporal properties, which can be done without constructing the whole reachability graph or the full power of model-checking. We are of the opinion that our approach is simpler as it is based directly on constraint-solving techniques and can be fairly efficient in verifying systems consisting of many components as it avoids to explore the whole state-space \cite{song2020automated,yi1995automatic}.

%About that, between TRS and the construction of efficient automata, recent work \cite{song2020automated} has shown that the former has a minor performance advantage (over a
%benchmark suite) when it is compared with
%state-of-the-art PAT \cite{sun2009pat} model checker.
%Improvement came from the avoidance of the more
%expensive automata construction process.

Moreover, our timed synchronous effects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
%Antimirov and Mosses' algorithm \cite{antimirov1995rewriting} was designed for deciding the inclusion of regular expressions.   
Kleene algebra (KA) is a decades-old sound and complete equational theory of regular expressions. Among many extensions of KA,
 %timed synchronous 
  SKA is KA extended with a synchrony combinator for actions. In particularly, SKA's \emph{demanding relation} can be reflected by our \emph{instances subsumption} (\defref{Subsumption}), which contributes to the inductive unfolding process. 
Yet our timed effects further capture the time bounds constraints by adding the operator \code{\#}, adapting to real-time system modelling and verification, which is not covered by any existing KA variants/extensions.

%Presently, SKA allows the synchrony combinator \code{\times} to be expressed over any two SKA terms to support concurrency.
%We achieve a similar outcome in Synced Effects by supporting normalization operations during trace synchronization, via a \code{zip} function in the forward rule of \code{[FV\text{-}Par]}.
%This leads to one major difference in the inclusion/equivalence checking procedure, whereby a TRS for SKA would have to rely on
%\emph{nullable}, \emph{first}, and \emph{partial derivatives} for terms constructed by the added combinator \code{\times}, but
%carefully avoided by our TRS construction.

While the original equivalence checking algorithm for SKA terms in \cite{prisacariu2010synchronous} has
relied on well-studied decision procedures based on classical Thompson \code{\epsilon}-NFA construction, prior work \cite{broda2015deciding}  shows that the use of Antimirov's partial derivatives
could result in better average-case algorithms for automata construction. 
%Our present work avoided the consideration for the more general \code{\times} operation from SKA
%and customized the TRS for inclusion (instead of equivalence) checking. These decisions led to some opportunities for improvements.
Moreover, between TRS and the construction of efficient automata, prior work has recently shown in \cite{song2020automated} that the former has a minor performance advantage (over a benchmark suite) when it is compared with state-of-the-art PAT \cite{sun2009pat} model checker.
Improvement came from the avoidance of the more expensive automata construction process.

\subsection{Existing Traces-Based Effects Systems}

Combining program events with a temporal program logic for asserting properties of event traces yields a powerful and general engine for enforcing program properties. Results in \cite{skalka2008types,skalka2004history,marriott2003resource} have demonstrated that static approximations of program event traces can be generated by type and effect analyses \cite{talpin1994type,amtoft1999type}, in a form amenable to existing model-checking techniques for verification. We call these approximations trace-based effects.

Trace-based analyses have been shown capable of statically enforcing flow-sensitive security properties such as safe locking behaviour \cite{foster2002flow} and resource usage policies such as file usage protocols and memory management \cite{marriott2003resource}. In \cite{bartoletti2005enforcing}, a trace effect analysis is used to enforce secure service composition. 
 Stack-based security policies are also amenable to this form of analysis, as shown in \cite{skalka2004history}.

 %  has effects capturing sequences of events, including requirements about things that must have happened prior to executing a given block of code

More related to our work, prior research has been extending Hoare logic with event traces. The work \cite{malecha2011trace} focuses on finite traces (terminating runs) for web applications, leaving the divergent computation, which indicates \code{false}, verified for every specification. The work \cite{nakata2010hoare} focuses on infinite traces (non-terminating runs) by providing coinductively trace definitions. 
More recent works \cite{bubel2015dynamic,song2020automated} proposed dynamic logics and unified operators to reason about possibly finite and infinite traces at the same time.

Moreover, this paper draws similarities to \textit{contextual effects} \cite{neamtiu2008contextual}, which computes the effects that have already occurred as the prior effects. The effects of the computation yet to take place as the future effects. 
Besides, prior work \cite{nielson1998behaviour} proposes an annotated type and effect system and infers behaviours from CML \cite{reppy1993concurrent} programs for channel-based communications, though it did not provide any inclusion solving process.

However, none of the previous works have considered adding real-time abstractions into the modelling for a more extensive timed verification, which is our work's main contribution.
 %The purely algebraic TRS is flexible to accommodate possibly extended expressiveness for the effects logics. Furthermore, as an extension of prior work \cite{song2020automated}, this work is able to reason about both finite and infinite traces, using cyclic proof techniques established  from \cite{brotherston2005cyclic}.

%due to the reason that Hoare logic only captures partial correctness, 
%
%
% only captures partial correctness, 
%
%
%deploys a Hoare logics based on  while its  networking library does not capture timeout, making certain properties difficult or impossible to specify. And because 
%

%While  , , the reasoning on timed traces is new. Prior timed effects in precondition is also new, allowing greater safety to be applied to sequential reactive controlling systems such as web applications, communication protocols and IoT systems.

%
%
%compare to timed automata:
%modular and can plug in anywhere. 
%absolute time and relative time. 
%$
%//
%(lower_t, upper_time)
%lower_ti<=upper_t
%lower_t<5
%lower_t>8
%modular and can plug in anywhere. 
%absolote time and relative time. 
%it can be only for synchronous system, t.sync, 
%or or real time t.rt.dur. 
%$

\section{Conclusion}
\label{sec:conclusion}
%HipHop.js
We define the syntax and semantics of the novel timed synchronous effects, to capture reactive program behaviours and  temporal properties. We demonstrate how to give a rather axiomatic semantics to \code{\lambda_{HH}} by timed-trace processing functions. We use this semantic model to enable  a Hoare-style forward verifier,  which computes the program effects constructively.
We present an effects inclusion checker (the TRS) to prove the annotated temporal properties efficiently. We prototype the verification system and show its feasibility.
To the best of our knowledge, our work is the first that formulates semantics of a mixed Sync-Async concurrency paradigm; and that automates modular timed verification for reactive programs using an expressive effects logic.

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
%\begin{acks}
%To Robert, for the bagels and explaining CMYK and color spaces.
%\end{acks}

%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}
%% Citation style
%% Note: author/year citations are required for papers published as an
%% issue of PACMPL.

%%
%% If your work has an appendix, this is the place to put it.
\appendix

\section{Termination Proof}  \label{proof:TerminationProof}

\begin{proof}\label{proof:termination} 
Let Set[\inclusion] be a data structure representing the sets of inclusions.

We use \code{S} to denote the inclusions to be proved, and \code{H} to accumulate  "inductive hypotheses", i.e., \code{S,  H \in Set[\inclusion]}.

Consider the following partial ordering \code{\succ} on pairs \code{\langle S, H \rangle}:
\begin{gather*}
\code{\langle S_1, H_1 \rangle \succ \langle S_2, H_2 \rangle}\ \ \text{iff}\ \ \code{|H_1| < |H_2| \vee 
(|H_1| = |H_2| \wedge |S_1| > |S_2|)}. 
\end{gather*}
where \code{|X|} stands for the cardinality of a set \code{X}.  Let \code{\Rightarrow} donate the rewrite relation, then \code{\Rightarrow^*} denotes its reflexive transitive closure. For any given \code{S_0}, \code{H_0}, this ordering is well founded on the set of pairs \code{\{\langle S, H \rangle | \langle S_0, H_0 \rangle \Rightarrow^* \langle S, H \rangle \}}, due to the fact that \code{H} is a subset of the finite set of pairs of all possible derivatives in initial inclusion.

Inference rules in our TRS given in \secref{InferenceRules} transform current pairs \code{\langle S, H \rangle} to new pairs \code{\langle S^\prime, H^\prime \rangle}. 
And each rule either increases \code{|H|} (Unfolding) or, otherwise, reduces \code{|S|} (Axiom, Disprove, Prove), therefore the system is terminating.

 \end{proof}

\section{Soundness Proof} 
 \label{proof:SoundnessProof}

\begin{proof}
For each inference rules, if inclusions in their premises are valid, and their side conditions are satisfied, then goal inclusions in their conclusions are valid.

\begin{enumerate}
\item \textbf{Axiom Rules:} 
\input{rules/rule1}
- It is easy to verify that antecedent of goal entailments in the rule \codeme{[Bot\text{-}LHS]} is unsatisfiable. Therefore, these entailments are evidently valid.\\
- It is easy to verify that consequent of goal entailments in the rule \codeme{[Bot\text{-}RHS]} is unsatisfiable. Therefore, these entailments are evidently invalid.\\

\item \textbf{Disprove Rules:} 
\input{rules/rule2}
- It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.  Therefore, these entailments are evidently invalid.\\

\item \textbf{Prove Rules:} 
\input{rules/rule3}
- To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}. Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \es_1}}. When the \code{\m{fst}} set of \code{\es_1} is empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon}; and \code{\es_2} is nullable. For both cases, the inclusion is valid.

- To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}. Given the promises that  \codeme{\pi_1 : \es_1 \CONTAIN \pi_3 : \es_3}, we get \codeme{d,  \varphi \models {\pi_3 : \es_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \es_3 \CONTAIN  \pi_4 : \es_4}, we get \codeme{d,  \varphi \models {\pi_4 : \es_4}}; Given the promises that  \codeme{\pi_4 : \es_4 \CONTAIN \pi_2 : \es_2}, we get \codeme{d,  \varphi \models {\pi_2 : \es_2}}. Therefore,  the inclusion is valid. 
\\

\item \textbf{Unfolding Rule:} 
\input{rules/rule4}

- To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \es_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \es_2}}. For an arbitrary time instance \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and 
\codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \es_2 \rrbracket}.

Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bott}, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};

Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}.

By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\es_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}, the conclusion is valid. 
\\

\end{enumerate}
All the inference rules used in the TRS are sound, therefore the TRS is sound.
\end{proof}

% \section{Completeness Proof} 
% \label{proof:Completeness}

 \section{Execute the loop body twice to compute the invariant} 
 \label{proof:twice}

 \begin{theorem}[twice]\label{twice}
The deterministic loop invariant can be fixed after the second run of the loop body.

\end{theorem}

\begin{proof}

Let \code{ \langle H,C  \rangle} be the initial program state, where H is the history trace, and C is the current time instance.  Given any program \code{P}, we use \code{H_P} and \code{C_P} to denote the history trace and current time instance by executing \code{P}. Based on the semantics of synchronous programs, there are three possible kinds of loops:

\noindent\textbf{Case 1: loop \{Yield; P\},}

The first  run:    \code{ \langle \epsilon , C\rangle}    Yield; P   \code{ \langle C\cdot H_P, C_P\rangle}

The second run:    \code{ \langle\epsilon , C_P\rangle} Yield; P   \code{ \langle C_P \cdot H_P, C_P\rangle}

The final effects: \code{H \cdot C \cdot H_P \cdot (C_P \cdot H_P)^\star }

\noindent\textbf{Case 2: loop \{P; Yield\},}

The first  run:   \code{ \langle\code{\epsilon }, C\rangle}     P; Yield  \code{ \langle(C || H_P) \cdot C_P, \{\}\rangle}

The second run:    \code{ \langle\code{\epsilon }, \{\}\rangle}    P; Yield  \code{ \langle H_P \cdot C_P, \{\}\rangle}

The final effects: \code{H \cdot (C || H_P) \cdot C_P \cdot (H_P \cdot C_P)^\star}

\noindent\textbf{Case 3: loop \{P1; Yield; P2\},}

The first  run:    \code{ \langle\epsilon , C\rangle}        P1; Yield; P2  \code{ \langle(C || (H_{P1} \cdot C_{P1})) \cdot H_{P2}, C_{P2}\rangle}

The second run:    \code{ \langle\epsilon , C_{P2}\rangle}     P1; Yield; P2  \code{ \langle(C_{P2} || (H_{P1} \cdot C_{P1})) \cdot H_{P2}, C_{P2}\rangle}

The final effects: \code{H \cdot (C || (H_{P1} \cdot C_{P1})) \cdot H_{P2} \cdot ((C_{P2} || (H_{P1} \cdot C_{P1})) \cdot H_{P2})^\star}~\\

\noindent In all possible cases, the loop invariant can be fixed by the end of the second run. 
(cf. \figref{fig:loop1})
\end{proof}

\end{document}
\endinput
%%
%% End of file `sample-manuscript.tex'.

### 2022-02-27 popl2022.tex
added todo list
m

@@
 %\copyrightyear{2018}           %% If different from \acmYear
+
+\newcommand{\timedEffs}{\emph{TimedEffs}}
+\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Automated Timed Temporal Verification for a Mixed Sync-Async Concurrency Paradigm}
+\title{Automated Timed Temporal Verification
+% for a Mixed Sync-Async Concurrency Paradigm
+}
 
@@
 
-\begin{figure*}[h]
-  \vspace{0mm}
-\renewcommand{\arraystretch}{1.1}
+\begin{figure}[!ht]
+\renewcommand{\arraystretch}{1.2}
 \centering
@@
   \begin{array}{lrcl}
- \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }& \
+
+    \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }&
     \code{%{datat^*}  \  
-   \overrightarrow{module}} 
-\qquad  \ \ 
-    \m{(Basic\ Types)} \quad  \code{\tau\ } \code{  ::= } \
-     \code{IN\ |\ OUT\ |\ INOUT \ | \ int }
-    \\
-
-      \m{(Module\ Def.)} &  \code{module}&\code{  ::= }&
-  \code{ \ nm  \ \ {(\overrightarrow{\tau\ x}, \  \overrightarrow{\tau\ \textbf{S}} )}\ \ \langle\textbf{requires}\ \ \effect_{pre}\ \ \textbf{ensures}\ \  \effect_{post} \rangle\ \  {p} }
-  \\
-
-  \m{(Statement)} &  \code{{{p, \ q}}}&\code{  ::= }&
- \textcolor{purple} {  \code{ 
-    \ nothing
-         \ |\ yield
-      \ |\ emit \ \textbf{S}
-     \ |\ present \ \textbf{S} \ {p} \ {q}
-     \ |\ seq\  {p} \ {q}  
-          \  |\ fork\  {p}  \ {q}    
-   }}\\
-&&&  
- \textcolor{purple} {\code{ 
-        |\ loop \ {p} 
-%\  |\ run \ nm \ {( x ^*, \textbf{S}^*)}
-\ | \ run \ nm \ {( \overrightarrow{x}, \overrightarrow{ \textbf{S}})}
-%\  | \ every \  \textbf{S} \  {p}
-  \   |\ abort\ {p}\ when\ d  
-%  \ |\ trap \  \textbf{T} \ \textbf{p}
- % \  |\ exit \   \textbf{T}_k
-   } }
-   \\
-%&&&  
-% \textcolor{purple} {\code{ 
-% %  
-%%   |\ signal \ \textbf{S} \ {p}
-%
-%}}
+   {meth^*}} 
+\qquad   \qquad
+    \m{(Basic\ Types)} \quad  \code{\tau} \code{\ \ ::= \ \ }
+     \code{int\ 
+    % |\ bool\ 
+     |\ void}
+    \\
+
+%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
+ %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
  %   \\
-%   
-   &&&
-
-     \textcolor{ blue} {|\ async\ \textbf{S} \ {p} \ d
- \ |\ await\ \textbf{S}
- } 
- \ |\ assert\ \effect
-
-  \\~\\
+
+%     \m{(Types)} &  \code{t}&\code{  ::= }&
+% \code{d\ |\ \tau} 
+% \\    
+  \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
+  \code{\tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}}
+  \\
+  \code{(Values)} &  {v}&\code{  ::= }&
+  ()\ |\ c \ | \  x
+
+ \\
+  \m{(Expressions)} &  \code{e}&\code{  ::= }&
+    \code{ v\ 
+    |\ mn({x^*}) \ 
+    |\ \textbf{let}\ x{=}e_1\ \textbf{in} \ e_2
+    |\ \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 
+ }\\ %|\ \textbf{assert}\ \effect  }  \\
+ &   & & \code{
+  |\ \textbf{emit} [\anyevent{a}]\ 
+  | \  \textbf{timeout}\ e \ d \ | \ \textbf{abort} \ e \ d 
+  }  \\~\\
 
     \multicolumn{4}{c}{
-      \code{\textbf{S} \in \text{signal variables}}  
-      \qquad\quad \ 
-\code{\text{nm, x} \in \textbf{var}}
-   \qquad\quad \ 
-       \code{
-          \m{(Finite\ List) \ \overrightarrow{}}}
- \qquad\quad \ 
-\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{Z^+}}    
+      \code{c::\in \mathbb{Z}} \qquad\quad\ \ \
+\code{x, mn  ::\in \textbf{var}}  
+\qquad\quad\ \ \ \ \code{(Events)  \anyevent{A} ::\in \Sigma  } 
+\qquad\quad\ \ \ \  \code{d::\in  \mathbb{Z}^{+}}  
     }\\  
-
     \hline
@@
   $
-    \vspace{0mm}
- \caption{Syntax of \code{\lambda_{HH}}.} 
- \label{fig:Hiphop_Syntax}
-  \vspace{0mm}
-\end{figure*}
-}
-
-We here explain the intuitive semantics, while the axiomatic semantics model is defined in \secref{sec:Verification}.
-The statement \code{nothing} in \code{\lambda_{HH}} resets all the output signals into absent. 
-%is the Esterel equivalent of unit, void or skip in other languages. 
-A thread of execution suspends itself for the current time instance using the \code{yield}  construct, and resumes when the next time instance started.
-The statement $emit \ \textbf{S}$ broadcasts the signal {\textbf{S}} to be set as  present and terminates instantaneously.
-The emission of {\textbf{S}} is valid for the current instance only.
-
-The statement $present \ \textbf{S} \ p \ q$ immediately starts \code{p} if {\textbf{S}} is present in the current instance; otherwise it starts \code{q} when {\textbf{S}} is absent.
-The sequence statement \code{seq\  p \ q} immediately starts \code{p} and behaves 
-as \code{p} as long as \code{p} remains active.
-When \code{p} terminates, control is passed instantaneously to \code{q}, which determines the behaviour of the sequence from then on.
-\emph{(Notice that `$emit\ \textbf{S1};\ emit \  \textbf{S2}$' leads to $\{S1, S2\}$, which  emits {{\textbf{S1}}} and ${\textbf{S2}}$ simultaneously and terminates instantaneously.)}
-
-%If \code{p} exits a \code{trap}, so does the whole sequence,
-%  \code{q} being discarded in this case.
-
- %\code{q} is never started if \code{p} always pauses.
-
- The parallel statement \code{fork\  p  \ q} runs p  and q in parallel.
-It remains active as long as one of its branches remains active.
-The parallel statement terminates when both \code{p} and \code{q} are terminated.
-The branches can terminate in different instances, and the parallel waits for the last one to terminate.
-
- The statement \code{loop \ p} implements an infinite loop, but it is possible to be aborted or suspended by enclosing it within a preemptive statement.  
-% escape from the loop by enclosing it within a trap and executing an exit statement. 
- When \code{p} terminates, it is immediately restarted. 
- %If \code{p} exits a trap, so does the whole loop. 
- The body of a loop is not allowed to terminate instantaneously when started, i.e., it must execute a yield statement to avoid an `infinite instance'. 
-For example, `$loop \ emit\ \textbf{S}$' is not a correct program.
-
-%The statement \code{run \ nm \ {( x ^*, \textbf{S}^*)}} makes a function calls to \code{nm} with parameters.
-
-The statement $run \ nm \ {( \overrightarrow{x}, \overrightarrow{ \textbf{S}})}$ is a call to module \code{nm}, parametrising with values and signals.
-
-%providing the list of IO signals.
-
-%The statement \code{every \  \textbf{S} \  {p}} behaves as its body p once the \textbf{S} is present occurs, where the whole watchdog statement terminates without transferring control to p in this instant.
-The watchdog construct is used to abort the body when an event occurs.
-
-%To facilitate the preemptive concurrency, \code{\lambda_{HH}} includes two primitive statements: \code{every}  and \code{abort}.
-
-To facilitate a preemptive concurrency, as well as provide necessary  real-time bounds, \code{\lambda_{HH}} includes the primitive statement  \code{abort\ p\ when\ d}, which runs statement \code{p} to completion.
-If the execution  reached the time bound \code{d}, it terminates immediately.
-
-%Parallel branches may simultaneously exit traps.
-If one branch exits a trap \code{\textbf{T}} or both branches exit the same trap \code{\textbf{T}}, then the parallel exits \code{\textbf{T}}.
-If both statements exit distinct traps \code{\textbf{T}} and \code{\textbf{U}} in the same instant, then the parallel only exits the higher prioritized one.
-
-%The statement  \code{signal \ \textbf{S} \ p} starts p with a fresh signal \textbf{S}, overriding any that might already exist.
-
-%The statement \code{abort\ {p}\ when\ d  } is used to abort the body when an event occurs.
-It behaves as its body \code{p} until the first following instant where \code{\textbf{S}} occurs, where the whole statement terminates without transferring control to \code{p} in this instant.
-
-%In the \code{suspend \   {p}\  when \   \textbf{S}} suspension statement, \textbf{S} is called the guard.
-The guard controls execution of the body in each instant except for the first one, where it is ignored (masked in common terminology).
-In the initial instant, the body \code{p} is started; if p terminates or exits a trap, so does the suspend statement, and the guard is transparent.
-Interesting things only happen in the following instants if p paused in the first instant.
-Then, as long as p remains active, the guard signal \textbf{S} is tested for presence.
-%– If \textbf{S} is present, then p is not executed in the instant and it is kept frozen for the next instant.
-The whole suspend statement pauses.
-In this case, we say that p is suspended for the instant.
-%– If \textbf{S} is absent, then p receives the control for the instant.
-We say that p is activated for the instant.
-If p terminates or exits a trap, so does the suspend statement.
-If p pauses, then the suspend statement also pauses.
-
-\emph{Async statements implement long lasting background operations.
-They are the essential ingredient for mixing indeterministic asynchronous computation and deterministic synchronous computations.} In other words, the \code{async} statement enables well-behaving synchronous to regulate unsteady asynchronous computations.
-The statement  $async\ \textbf{S} \ p \ d$ is supposed to spawn a long lasting background computation, where \code{d} represents an execution delay.
-When it completes, the asynchronous block will resume the synchronous machine.
-%by calling the function that composes the async JavaScript API. 
-Therefore when a signal {\textbf{S}} is specified with the {async} call, it emits {\textbf{S}} when the asynchronous block completes.
-
-The statement $await\ \textbf{S}$ blocks the execution and waits for the signal {\textbf{S}} to be emitted across the threads. 
-%The assertion statement is parametrized with effects $\effect$.
-The statement assert \code{\effect} is used to guarantee the temporal property \code{\effect} asserted at a certain point of the programs.
-%Prior work
-\cite{kambona2013evaluation} shows that such a language combination makes reactive programming more powerful and flexible than the traditional web programming. % (cf. \secref{subsection:HipHop}).
-
-%
+ \caption{$\lambda^t$ Syntax.} 
+ \label{work3_fig:lambda_t}
+
+\end{figure}
+}
 
 \subsection{The Specification Language}
-\label{subsec:Specification_language}
-
-We plant the effects specifications into the Hoare-style verification system, using \code{ \effect_{pre}} and \code{  \effect_{post} }  to capture the temporal pre/post 
-condition. %\code{\effect_{pre}} and the postcondition \code{\effect_{post}}.
+\label{work3_subsec:Specification_language}
+
+The effects specifications are planted into the Hoare-style verification system, 
+using \code{ \effect_{pre}} and \code{  \effect_{post} }  to capture the temporal pre/post 
+condition.
 
@@
     \vspace{0mm}
-\begin{figure*}[h]
+\begin{figure*}[!ht]
 \renewcommand{\arraystretch}{1.1}
@@
 
-    \m{(Timed\ Effects)} &  \effect &\code{\  ::=\ }&
+    \m{(\timedEffs)} &  \effect &\code{\  ::=\ }&
     \code{
-          \pure{\pi} : \es  
+          {\pi} \wedge es  
    \ | \ \effect_1 \vee \effect_2
@@
     \\
- \m{(Timed \ Sequence)}  & \ \code{\es}   &\code{\ ::=\ }&
-
-   \code{ \bott
-   \  | \ \empt 
-    \ | \ I 
-    \ | \ \textbf{S}?
-    %   \ | \ \anyevent{a}
-   \  | \ \es_1 {\seq} \es_2
-    \ | \ \es_1 {\vee} \es_2
-      %    \  | \ \es_1 \times \es_2
-      \  | \ \es_1  ||  \es_2
-      \ | \ \es \# t 
- %  \  | \  \esn{\es}{t}    
-   \  | \  \esn{\es}{\star}    
-   \  | \ \esn{\es}{\omega} 
-    }
-            \\
-    \m{(Time \ Instance)} &  \code{I} &\code{::= }&
-
-    \code{
-    \{ \} \ | \ \{ \textbf{S} \} \ | \ \{ \overline{\textbf{S}} \} \ | \ I_1 \cup I_2
-    }
-%(\textbf{S} \mapsto \theta )^*
-
-%    \\
-%        \m{(Real\ Time)} &  \mathcal{O} &\code{::= }&
-%    
-%    \code{
-%   %n \ | \ 
-%   c \ | \ (c, {+}\infty) \ | \  [0, c) \ | \  \mathcal{O}_1 \wedge \mathcal{O}_2 \ | \  \mathcal{O}_1 \vee \mathcal{O}_2
-%    }
-
-    \\
-
-    \m{(Pure)}  & \code{\code{\pure{\pi}}}&\code{\  ::=\ }&
-\pure{ \pure{True}}
-   \ | \  \pure{False}
-   \ | \ \pure{A(}{t_1, t_2}\pure{)}
-  \   | \  \pure{\pure{\pi_1}} \wedge \code{\pure{\pi}}_2
-   \  | \ \pure{\pure{\pi_1}} \vee \code{\pure{\pi}}_2
-   \  | \ \neg\code{\pure{\pi}}
+ \m{(Timed \ Sequence)}  & \ \code{es}   &\code{\ ::=\ }&
+
+   \code{ \bot
+   \  | \ \epsilon 
+    \ | \ \anyevent{A}
+   \  | \ es_1 {\cdot} es_2
+    \ | \ es_1 {\vee} es_2
+      \ | \ es \mysharp  t 
+ %  \  | \  \esn{es}{t}    
+   \  | \  \esn{es}{\star}    
+   \  | \ \esn{es}{\omega} 
+    }
+
+    \\
+
+    \m{(Pure)}  & \code{\code{{\pi}}}&\code{\  ::=\ }&
+{ \m{True}}
+   \ | \  \m{False}
+   \ | \ {A(}{t_1, t_2}{)}
+  \   | \  {{\pi_1}} \wedge \code{{\pi}}_2
+   \  | \ {{\pi_1}} \vee \code{{\pi}}_2
+   \  | \ \neg\code{{\pi}}
 
@@
     & &&\code{
-       | \  \pure{\pure{\pi_1}} \Rightarrow \pure{\pure{\pi_2}}
-   \  | \ \forall x. \code{\pure{\pi}}
-   \  | \ \exists x. \code{\pure{\pi}}
+       | \  {{\pi_1}} \Rightarrow {{\pi_2}}
+   \  | \ \forall x. \code{{\pi}}
+   \  | \ \exists x. \code{{\pi}}
    }\\
@@
     \\~\\
-    \multicolumn{4}{l}{
-   \qquad   \code{\textbf{S} \in \text{signal variables}}   
+    \multicolumn{4}{c}{
+   \qquad   \code{\anyevent{A} \in \Sigma}   
    \qquad\qquad\qquad\quad
@@
 
-         \multicolumn{4}{l}{
-       \   \m{(Blocking)}\ \code{?}
-          \qquad  \qquad \ \
-     \m{(Real\ Time\ Bound)}\ \code{\#}
+         \multicolumn{4}{c}{
+     \m{(Real\ Time\ Bound)}\ \code{\mysharp }
      \qquad\qquad \ \
@@
   $ \\
-  \caption{Syntax of Timed Synchronous Effects.}
-  \label{fig:Syntax_of_Types_and_Effects}
+  \caption{Syntax of \timedEffs\ .}
+  \label{work3_fig:Syntax_of_Types_and_Effects}
   \vspace{0mm}

### 2022-03-23 tv.tex
m

--- 2022-02-27 popl2022.tex
@@
-\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
+\documentclass[acmsmall,10pt,review]{acmart}
 
@@
 \acmVolume{1}
-\acmNumber{POPL} % CONF = POPL or ICFP or OOPSLA
+\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
 \acmArticle{1}
@@
 %\copyrightyear{2018}           %% If different from \acmYear
-
-\newcommand{\timedEffs}{\emph{TimedEffs}}
-\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
 
@@
 
+\newcommand{\timedEffects}{\emph{TimEffs}}
 \usepackage{xcolor}
@@
 \newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
+\newcommand{\timedL}{\code{\lambda^{t}}}
 
@@
 \lstdefinelanguage{JavaScript}{
-  keywords={typeof, const, new, true, false, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
+  keywords={typeof, void, const, new, int, true, false, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
   keywordstyle=\color{blue}\bfseries,
-  ndkeywords={class, export, boolean, throw, implements, import, this},
+  ndkeywords={class, export, boolean,event, timeout, deadline, delay,  throw, implements, import, this},
   ndkeywordstyle=\color{darkgray}\bfseries,
@@
 \begin{abstract} 
-To make reactive programming more concise and flexible, it is promising to deploy a mixed concurrency paradigm \cite{berry2020hiphop} that
-integrates Esterel's synchrony and preemption \cite{berry1999constructive}  
-with JavaScript's asynchrony \cite{madsen2017model}. 
-%HipHop.js \cite{berry2020hiphop} is the first web language that 
-Existing temporal verification techniques have not been designed to handle such a blending of two concurrency
-models.
-We propose a novel solution via a 
-compositional 
-Hoare-style forward verifier and a term rewriting system (TRS) on \emph{Timed Synchronous Effects} (TSE).
-
-Firstly, we introduce TSE, a new effects logic, that extends \emph{Kleene Algebra} with value-dependent constraints, providing real-time bounds for logical-time synchronous traces \cite{von2017real}. 
-Secondly, we establish an axiomatic semantics  for a core language \code{\lambda_{HH}}, generalising the mixed paradigm. 
-% HipHop.js,  based on our effects logic. 
-%Secondly, we formalise a set of construction rules to infer the program effects based on a . using a set of inductive rules
-Thirdly, we present a purely algebraic TRS, to efficiently check language inclusions between expressive timed effects.  
-To demonstrate the feasibility of our proposals, we prototype the  verification system; prove its correctness; investigate how it can help to debug errors related to both synchronous and asynchronous programs.
+In this work, we study temporal verification of 
+compositional real-time systems, which are modeled 
+using mutable variables and timed processes.  
+Instead of explicitly manipulating clock variables, 
+a number of compositional timed behavioral patterns, 
+such as \emph{delay}, \emph{timeout}, \emph{deadline},  
+are introduced to capture quantitative timing constraints.
+The idea is to dynamically create clocks, 
+and solve constraints on the clocks.
+
+We propose a novel solution for timed verification via a 
+compositional Hoare-style forward verifier and a 
+term rewriting system (TRS) on \emph{Timed Effects} (\timedEffects).  
+More specifically, we formally define 
+a core language \timedL, generalizing the timed systems.
+Secondly, we introduce \timedEffects, a new effects logic, 
+that extends 
+\emph{Kleene Algebra} with value-dependent real-time constraints. 
+Thirdly,  we establish an  axiomatic semantics for  
+\timedL\  to infer temporal behaviors  of  given 
+programs, expressed in \timedEffects. 
+Lastly, we present a purely algebraic TRS, to 
+efficiently prove  language inclusions between 
+ \timedEffects.
+To demonstrate the feasibility of our proposals, 
+we prototype the verification system; prove its 
+correctness; report case studies and the experimental results. 
+%we prototype the  verification system in OCaml; then prove soundness of both the effects inference process and the term rewriting process. % in Coq.
 
@@
 \ccsdesc[300]{Theory of computation~Semantics and reasoning}
-\ccsdesc[100]{Models of computation~Concurrency}
+\ccsdesc[300]{Theory of computation~Finite Model Theory}
 
@@
 
-As it recently proposed,  reactive languages such as Hiphop.js\footnote{Hiphop.js is a JavaScript extension of Esterel \cite{berry1992esterel}
-(or vice versa)
-for reactive web applications: \url{https://www-sop.inria.fr/members/Colin.Vidal/hiphop/}.}   \cite{vidal2018hiphop,berry2020hiphop} are designed to be
-based on a smooth integration of (i) Asynchronous concurrent programs, which perform interactions between components or with the environment with uncontrollable timing, such as network-based communication; (ii) Synchronous reactive programs, which react to external events in a conceptually instantaneous and deterministic way; and (iii) Preemption, the explicit cancellation and resumption of an ongoing orchestration subactivity.
-
-%Recent research has
-
-%One of the major difficulties of reactive web programming is \emph{callback hell} \cite{kambona2013evaluation}, which is the problem of appropriately handling the asynchronous events appearing in program executions.
-To avoid using callbacks, efforts have been made:
-%%\cite{madsen2017model}
-%(i) JavaScript has provided  \emph{promises} and \emph{async/await} primitives, making it possible to chain asynchronous actions in a specific sequential order; (ii) High-level abstractions such as \emph{Functional Reactive Programming} has been carried up to the web applications \cite{czaplicki2013asynchronous}, which adopts the data flow declarative programming style: when a variable is modified, any expression that references it is implicitly reevaluated.
-%
-%To go further with this problem and achieve a better web orchestration,  the language Hiphop.js \cite{vidal2018hiphop,berry2020hiphop} is designed to be a JavaScript extension of Esterel \cite{berry1992esterel} (or vice versa) based on a smooth integration of (i) Asynchronous concurrent programs, which perform interactions between components or with the environment with uncontrollable timing, such as network-based communication; (ii) Synchronous reactive programs, which react to external events in a conceptually instantaneous and deterministic way; and (iii) Preemption, the explicit cancellation and resumption of an ongoing orchestration subactivity.
-
-\textit{"Such a combination makes reactive programming more powerful and flexible than plain JavaScript because it makes the temporal geometry of complex executions explicit instead of hidden in implicit relations between state variables." \cite{berry2020hiphop}}
-
-Given such a multi-paradigm (mixed Sync-Async) concurrency model, the verification of its temporal behaviour becomes engaging and challenging. 
-%which, however, has not been intensely exploited. 
 Existing techniques are based on a transformation to convert the asynchronous chunk into semantically equivalent synchronization\footnote{Usually the transformation is incomplete, i.e., not all the asynchronous programs can be translated into a semantically equivalent synchronization.}; then reason about the behaviours based on the synchronous semantics \cite{damian2019communication,gleissenthall2019pretend,tarawneh2018formal}.
@@
 \begin{enumerate}
-\item \textbf{The Timed Synchronous Effects:} We define the syntax ({\secref{subsec:Specification_language}}) and semantics ({\secref{subsec:Specification_Semantics}}) of timed synchronous effects, to be the specification language, which captures the target programs' behaviours and non-trivial temporal properties.
+\item \textbf{The Timed Effects:} We define the syntax ({\secref{subsec:Specification_language}}) and semantics ({\secref{subsec:Specification_Semantics}}) of timed synchronous effects, to be the specification language, which captures the target programs' behaviours and non-trivial temporal properties.
 
@@
 \end{enumerate}
-
-\noindent\textbf{\textit{Organization.}} 
-\secref{sec:Preliminaries} introduces the language features of synchronous Esterel programs, JavaScript promises, and the web reactive language HipHop.js. 
-\secref{sec:Overview} gives motivation examples to highlight the key methodologies and contributions. 
-\secref{sec:LanguageSpecifications} formally presents the core   language \code{\lambda_{HH}}, and the syntax and semantics of timed synchronous effects.
-\secref{sec:Verification} presents the forward verification rules.
-\secref{sec:Entailment_Prover} explains the TRS for effects inclusion checking, and displays the essential auxiliary functions. 
-\secref{sec:Evaluation} demonstrates the implementation and cases studies. % via a number of . 
-We discuss related works in \secref{sec:Related_work} and conclude in  \secref{sec:conclusion}. Omitted proofs can be found in the Appendix.
-
-\section{Background: Esterel, Async-Await, and Hiphop.js }
-\label{sec:Preliminaries}
-
-It has been an active research topic to build flexible programming paradigms for reactive systems in different domains.
-This section identifies: i) \emph{Synchronous programming}, represented by Esterel  \cite{berry1992esterel}, ii) \emph{Asynchronous programming}, represented by JavaScript promises \cite{madsen2017model}, and iii) A \emph{mixed Sync-Async} paradigm, recently proposed by HipHop.js  \cite{berry2020hiphop}.
-Meanwhile, we discuss the real-world programming challenges of each paradigm; and show how our proposal addresses them in the cases studies, \secref{subsec:Case_Studies}.
-
- %language abstractions
-
-\subsection{A Sense of Esterel: Synchronous and Preemptive}
-
-%Synchronous programming (also synchronous reactive programming or SRP) is a computer programming paradigm supported by synchronous programming languages.
-
-The principle of synchronous programming is to design a high-level abstraction where the timing characteristics of the electronic transistors are neglected \cite{esterel_wiki}.
-Such an abstraction makes reasoning about time a lot simpler, thanks to the notion of \emph{logical ticks}: a synchronous program reacts to its environment in a sequence of ticks, and computations within a tick are assumed to be instantaneous.
-As one of the first few well-known synchronous languages, Esterel's high-level imperative style allows the simple expression of parallelism and preemption, making it natural for programmers to specify and reason about control-dominated model designs.
-Esterel has found success in many safety-critical applications such as nuclear power plant control software.
-The success with real-time and embedded systems in domains that need strong guarantees can be partially attributed to its precise semantics and computational model  \cite{berry1992esterel,berry1999constructive, song2021synchronous}.
-
-Esterel treats computation as a series of deterministic reactions to external signals.
-All parts of a reaction complete in a single, discrete-time step called an \emph{instance}.
-Besides, instances exhibit deterministic concurrency; each reaction may contain concurrent threads without execution order affecting the computation result.
-Primitive constructs execute in zero time except for the \code{yield} (pause) statement.
-Hence, time flows as a sequence of logical instances separated by explicit pauses.
-In each instance, several elementary instantaneous computations take place simultaneously.
-
-\begin{lstlisting}
-fork {emit A; yield; emit B; emit C} par {emit E; yield; emit F; yield; emit G}
-\end{lstlisting}
-
-The synchronous parallelism in Esterel is constructed by the \code{\m{fork} \{...\} \m{par}  \{...\}  } statement. 
-It remains active as long as one of its branches remains active, 
-% unless some branch exits a trap, 
-and it terminates when both branches are terminated. The branches can terminate in different instances, and wait for the last one to terminate.
-As the above example shows, the first branch generates effects $\{\textbf{A}\} \cdot \{\textbf{B}, \textbf{C}\}$ while the second branch generates effects $\{\textbf{E}\} \cdot \{\textbf{F}\} \cdot \{\textbf{G}\}$; then the final effects should be $\{\textbf{A},\textbf{E}\}\cdot \{\textbf{B}, \textbf{C}, \textbf{F}\} \cdot \{\textbf{G}\}$.
-
-To maintain determinism and synchrony, evaluation in one thread of execution may affect code arbitrarily far away in the program.
-In other words, there is a strong relationship between signal status and control propagation: a signal status determines which branch of a \code{present} test is executed, which in turn determines which \code{emit} statements are executed (See \secref{subsec:Targetlanguage} for the language syntax).
-%For instance, selecting a particular branch of execution in one thread may immediately unblock a different thread of execution. 
-%The selection of the other branch may render the entire program invalid\citeref{florence2019calculus}. 
-The first semantic challenge of programming Esterel is the \emph{Logical Correctness} issue, caused by these non-local executions, which is simply the requirement that there exists precisely \textbf{one} status for each signal.
-For example, consider the program below:
-
-\begin{lstlisting}
-signal S1 in present S1 then nothing else emit S1 end present end signal
-\end{lstlisting}
-
-If the local signal {\textbf{S1}} were \emph{present}, the program would take the first branch of the condition, and the program would terminate without having emitted {\textbf{S1}} (\code{nothing} leaves \code{\textbf{S1}} with   \emph{absent}).
-If \code{\textbf{S1}} were absent, the program would choose the second branch and emit the signal.
-Both executions lead to a contradiction.
-Therefore there are no valid assignments of signals in this program.
-This program is logically incorrect.
-
-\begin{lstlisting}
-signal S1 in present S1 then emit S1 else nothing end present end signal
-\end{lstlisting}
-
-Consider the revised program above. If the local signal {\textbf{S1}} were present, the conditional would take the first branch, and  {\textbf{S1}} would be emitted, justifying
-the choice of signal value. 
-If {\textbf{S1}} were absent, the signal would not be emitted, and the choice of absence is also justified.
-Thus there are two possible assignments to the signals in this program, which is also logically incorrect.
-
-\begin{wrapfigure}{R}{0.41\columnwidth}
-    \vspace{-1mm}
-\centering
-\begin{lstlisting}
-module a_loop: output A,B,C;
-  emit A;
-  loop 
-  	emit B; yield; emit C
-  end loop  
-end module
-\end{lstlisting}  
-     \vspace{-1mm}
- \caption{A Loop Example in Esterel \cite{song2021synchronous}.} 
-  \label{fig:loop1}
-       \vspace{-1mm}
-\end{wrapfigure}
-
-Esterel's instantaneous nature requires a special distinction when it comes to loop statements, which increases the difficulty of the effects invariants inference.  
-As shown in \figref{fig:loop1}, the program firstly emits signal {\textbf{A}}, then enters into a loop which emits signal \code{\textbf{B}} followed by a \code{\m{yield}} followed by emitting signal {\textbf{C}} at the end.
-The effects of it is $ \{\textbf{A}, \textbf{B}\} \cdot \{ \textbf{B}, \textbf{C}\} \cdot \{ \textbf{B}, \textbf{C}\} \cdot \{ \textbf{B}, \textbf{C}\} ...$,
-which says that in the first time instance, signals {\textbf{A}} and {\textbf{B}} will be present, 
-as there is no explicit yield between $emit\ \textbf{A}$ and $emit\ \textbf{B}$; 
-then for the following instances (in an infinite trace), signals {\textbf{B}} and {\textbf{C}} are present all the time, because after executing $emit\ \textbf{C}$, it immediately executes from the beginning of the loop, which is $emit\ \textbf{B}$.
-
- %one deals with concurrent processes that coordinate with each other.
-
-Coordination in concurrent systems can result from information exchange, using messages circulating on channels with possible implied synchronization.
-In Esterel, it can also result from \emph{process preemption}  \cite{berry1993preemption}, which is a more implicit control mechanism that consists in denying the right to work to a process, either permanently (abortion, cf.
-\figref{fig:overview_eg1}) or temporarily (e.g.
-suspension).
-Preemption is particularly important in control-dominated reactive and real-time programming, where most of the works consist of handling interrupts and controlling computation.
-
-%
-%\begin{wrapfigure}{L}{0.4\columnwidth}
-%    \vspace{-1mm}
-%\centering
-%\begin{lstlisting}
-%suspend
-%	loop emit A; yield; yield;
-%	end loop
-%when B end suspend
-%\end{lstlisting}  
-%     \vspace{-1mm}
-% \caption{A Suspend Example in Esterel.} 
-%  \label{fig:Suspend}
-%       \vspace{5mm}
-%\includegraphics[width=0.39\columnwidth]{suspend.png}
-%        \vspace{-1mm}
-%\caption{\label{fig:Suspend}Graphical Illustration of \figref{fig:Suspend}}
-%        \vspace{0mm}
-%\end{wrapfigure}
-%
-%
-%\figref{fig:Suspend} presents a suspend statement, one of the preemptive operations in Esterel.
-When the preemption condition satisfied, it pauses the execution of a group of statements, and resume it from the next time instance.
-%As \figref{fig:Suspend_pbg} illustrates, without the preemption, the effects is a repeated pattern: \code{\{\textbf{A}\}\cdot\{\}\cdot\{\textbf{A}\}\cdot\{\} \cdot ...} .
-Due to the presence of signal \code{\textbf{B}}, it delays emission of \code{\textbf{A}} by one cycle (at {\textcircled{1}} and {\textcircled{2}}), and resumes from the next cycle.
-
-While the flexibility they provide us, preemption primitives often with loose or complex semantics, making abstract reasoning difficult. 
-Most existing languages offer a small set of preemption primitives, often insufficient to program reactive systems concisely.
-
-\subsection{Asynchrony from JavaScript Promises: Async–Await}
-
-\noindent \textit{"Who can wait quietly while the mud settles? Who can remain still until the moment of action?"}\\
-\textcolor{white}{.}\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad \textit{ -- Laozi, Tao Te Ching}
-
-A number of mainstream languages, such as C\code{\#}, JavaScript, Rust, and Swift, have recently added support for async–await and the accompanying promises abstraction\footnote{JavaScript's asynchrony arises in situations such as web-based user-interfaces, communicating with servers through HTTP requests, and non-blocking I/O.}, also known as \emph{futures} or \emph{tasks} \cite{bierman2012pause}.
-As an example, consider the JavaScript program in \figref{fig:json},
-it uses the {\ttfamily{fs}} module (line 1) to load the file into a variable (line 6) using async/await syntax.
-
-\begin{figure}[h]
-    \vspace{-2mm}
-\centering
-\begin{lstlisting}
-const fs = require('fs').promises;
-
-async function read (filePath) {
-	const task = fs.readFile(filePath);
-    ... // do things that do not depend on the result of the loading file
-    const data = await task; // block execution until the file is loaded
-	... // logging or data processing of the Json file 
-}
-\end{lstlisting}  
-     \vspace{-3mm}
- \caption{Using Async-Await in JavaScript.} 
-  \label{fig:json}
-       \vspace{-2mm}
-\end{figure}
-
-The function {\ttfamily{read}} accepts one argument, a string called {\ttfamily{filePath}}.
-As it is declared {\textbf{\color{blue}\ttfamily{async}}}, reading a file (line 4) does not block computations that do not depend on the result (line 5).
-The programmer {\textbf{\color{blue}\ttfamily{await}}}s the task when they need the result to be ready.
-Reading a file may raise exceptions (e.g., the file is non-existent), then the point for such an exception to emerge is where the tasks are awaited (lines 6).
-While await sends a signal to a task scheduler on the runtime stack, the exceptions appear to propagate in the opposite direction, from the runtime to the await sites.
-
-Unfortunately, existing languages that support async–await do not enforce at compile time that exceptions raised by asynchronous computations are handled.
-The lack of this static assurance makes asynchronous programming error-prone.
-For example, the JavaScript compiler accepts the program above without requiring that an exception handler to be provided, which leads to program crashes if the asynchronous computation results in an exception.
-%The worse situation is: an exception raised asynchronously is possibly silently swallowed if not otherwise caught. 
-Such unhandled exceptions have been identified as a common vulnerability in JavaScript programs \cite{madsen2017model,alimadadi2018finding}.
-Furthermore, \cite{madsen2017model,alimadadi2018finding} display a set of other \emph{anti-patterns} including: 
-attempting to settle a promise multiple times; unsettled promises; unreachable reactions; 
-%implicit returns in reactions; 
-and unnecessary promises, which are mostly caused by using promises without sufficient static checking.
-
-   \vspace{2mm}
-\subsection{HipHop.js -- A mixture of Esterel and JavaScript}
-\label{subsection:HipHop}
-
-\begin{figure}[h]
-\noindent
-   \vspace{-2mm}
-\begin{varwidth}{.5\textwidth}
-\begin{lstlisting}
-function enableLoginButton(){
-  return (Rname.length >= 2 
-	   && Rpasswd.length >= 2);}
-function nameKeypress(value){
-  Rname = value;
-  RenableLogin=enableLoginButton();}
-function passwdKeypress(value){ 
-  Rpasswd = value;
-  RenableLogin=enableLoginButton();}
-\end{lstlisting}
-\end{varwidth}%
-\begin{varwidth}{.5\textwidth}
-\begin{lstlisting}
-hiphop module Identity(
-			in name, in passwd, 
-			out enableLogin){
-  do{
-	  emit enableLogin(
-		  		name.length >= 2 
-		  	 && passwd.length >= 2); 
-  } every(name || passwd)
-}
-\end{lstlisting}  
-\end{varwidth}
-      \vspace{0mm}
-\caption{A comparison between JavaScript (left) and HipHop.js (right) for a same login button implementation \cite{berry2020hiphop}.
-(On the right, {\ttfamily{name}}, {\ttfamily{passwd}} and {\ttfamily{enableLogin}} are reactive input/output signals.)}
-  \label{fig:login_compare}  
-      \vspace{0mm}
-\end{figure}
-
-HipHop.js is a reactive web language that adds synchronous concurrency and preemption to JavaScript, which is compiled into plain  JavaScript and executes on runtime environments \cite{berry2020hiphop}.
-To show the advantages of such a mixture, \figref{fig:login_compare} presents a comparison between JavaScript and HipHop.js to achieve the same login button.
-Here, {\ttfamily{Rname}}, {\ttfamily{Rpasswd}}, {\ttfamily{RenableLogin}} are global variables to model the application's states.
-Dis/En-abling login is done by setting {\ttfamily{RenableLogin}}.
-However, while more and more features get added to the specification, state variable interactions can lead to a large number of implicit and  invisible global control states.
-
-Whereas, HipHop.js simplifies and modularizes designs, and synchronous signaling makes it possible to instantly communicate between concurrent statements to exchange data and coordination signals. 
-Second, powerful event-driven reactive preemption borrowed from Esterel finely controls the lifetime of the arbitrarily complex program statements they apply, instantly killing them when their control events occur.
-More examples are discussed in the following sections.
-
-%Third, an extension of async that synchronously signals termination completion to concurrent statements and automatically performs automatic resource cleaning when preempted.
-
-%
 
@@
 \begin{lstlisting}[columns=fullflexible]
-hiphop module authenticate(var d, var name, var passwd, in Tick, out Connecting, out Connected)
-/*@ requires d>3000 : {}^*.{Login} @*/
-/*@ ensures	(3000<t/\t<d : {Connecting}#t.{Connected}) \/ (t=d :  {Connecting}#t) @*/
+  void addSugar(int n)
+  // requires n>0 /\ Cup 
+  // ensures  t>=n /\ Sugar # t
   {
-   abort count(d, Tick) { // Abort the execution at d milliseconds
-      async Connected {
-         emit Connecting; 
-         // Execute authenticateSvc after a 3000 milliseconds' delay
-         setTimeout (authenticateSvc(name, passwd).post().then( v => this.notify(v)), 3000);}}}
+      if n == 0 then event[Sugar] 
+      else {
+          timeout (oneSugar(), 1);
+          addSugar (n-1);
+      }
+  }
+
+  void makeCoffee (int n)
+  // requires n>0 /\ emp 
+  // ensures  5>t>=n/\ t1<3 /\ Cup.(Sugar # t).(Coffee # t1).Done
+  {
+      event[Cup];
+      deadline (getSugar(n), 5);
+      deadline (event[Coffee], 3);
+      event[Done];
+  }
+
+  void main () 
+  // requires true /\ emp 
+  // ensures  t < 8 /\ (_^*.Done) # t
+  {
+      makeCoffee(3);
+  }
 \end{lstlisting}  
@@
 {
-
+ % \vspace{-2mm}
 \begin{figure}[!ht]
-\renewcommand{\arraystretch}{1.2}
-\centering
+\renewcommand{\arraystretch}{1.1}
+\centering%\small
   $
@@
 \qquad   \qquad
-    \m{(Basic\ Types)} \quad  \code{\tau} \code{\ \ ::= \ \ }
-     \code{int\ 
-    % |\ bool\ 
-     |\ void}
+    \m{(Basic\ Types)} \qquad  \code{\tau} \code{  ::= }
+     \code{int\ |\ bool\ |\ void}
     \\
@@
   \\
-  \code{(Values)} &  {v}&\code{  ::= }&
-  ()\ |\ c \ | \  x
-
- \\
   \m{(Expressions)} &  \code{e}&\code{  ::= }&
-    \code{ v\ 
-    |\ mn({x^*}) \ 
-    |\ \textbf{let}\ x{=}e_1\ \textbf{in} \ e_2
-    |\ \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 
- }\\ %|\ \textbf{assert}\ \effect  }  \\
+    \code{ ()\ |\ k^\tau\ |\ x\ |\ 
+    %v.f\ |\ 
+    %\textbf{new}\ d({v^*}) \ |\ 
+    \tau\ x;\ e \ |\ mn({x^*}) \ }
+  \code{|\ x{:=}e\ |\ 
+ % v.f:=e \ | 
+ \ e_1;e_2\ 
+  |\ {if}\ v\ {then}\ e_1\ {else}\ e_2 
+ }  \\
  &   & & \code{
-  |\ \textbf{emit} [\anyevent{a}]\ 
-  | \  \textbf{timeout}\ e \ d \ | \ \textbf{abort} \ e \ d 
-  }  \\~\\
+% |\ e_1}\ op\ \code{ e_2 \ 
+| \ \textbf{event} [\anyevent{A}]\
+  %|\ \textbf{assert}\ \effect \ 
+  | \ \textbf{timeout} \ e \ d \  
+  | \ \textbf{deadline} \ e \ d \  
+  | \ \textbf{delay}\ d 
+  }  \\
+  ~\\
 
     \multicolumn{4}{c}{
-      \code{c::\in \mathbb{Z}} \qquad\quad\ \ \
-\code{x, mn  ::\in \textbf{var}}  
-\qquad\quad\ \ \ \ \code{(Events)  \anyevent{A} ::\in \Sigma  } 
-\qquad\quad\ \ \ \  \code{d::\in  \mathbb{Z}^{+}}  
+  \code{k^\tau:constant\ of\ type\ \tau\ } 
+  \qquad\quad
+\code{    x, mn  ::\in \textbf{var}}  
+\qquad\quad
+ \code{(Events)  \anyevent{A} ::\in \Sigma 
+\qquad\quad
+\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{Z^+}}    
+}   
     }\\  
@@
   $
- \caption{$\lambda^t$ Syntax.} 
- \label{work3_fig:lambda_t}
-
+ \caption{A Core Imperative Language.} 
+ \label{fig:code_language}
+  \vspace{-1mm}
 \end{figure}
@@
 
+%
+
 \subsection{The Specification Language}
-\label{work3_subsec:Specification_language}
-
-The effects specifications are planted into the Hoare-style verification system, 
-using \code{ \effect_{pre}} and \code{  \effect_{post} }  to capture the temporal pre/post 
-condition.
+\label{subsec:Specification_language}
+
+We plant the effects specifications into the Hoare-style verification system, using \code{ \effect_{pre}} and \code{  \effect_{post} }  to capture the temporal pre/post 
+condition. %\code{\effect_{pre}} and the postcondition \code{\effect_{post}}.
 
@@
     \vspace{0mm}
-\begin{figure*}[!ht]
+\begin{figure*}[h]
 \renewcommand{\arraystretch}{1.1}
@@
 
-    \m{(\timedEffs)} &  \effect &\code{\  ::=\ }&
+    \m{(Timed\ Effects)} &  \effect &\code{\  ::=\ }&
     \code{
-          {\pi} \wedge es  
+          \pure{\pi} : \es  
    \ | \ \effect_1 \vee \effect_2
@@
     \\
- \m{(Timed \ Sequence)}  & \ \code{es}   &\code{\ ::=\ }&
-
-   \code{ \bot
-   \  | \ \epsilon 
+ \m{(Timed \ Sequence)}  & \ \code{\es}   &\code{\ ::=\ }&
+
+   \code{ \bott
+   \  | \ \empt 
     \ | \ \anyevent{A} 
-   \  | \ es_1 {\cdot} es_2
-    \ | \ es_1 {\vee} es_2
-      \ | \ es \mysharp  t 
- %  \  | \  \esn{es}{t}    
-   \  | \  \esn{es}{\star}    
-   \  | \ \esn{es}{\omega} 
-    }
-
-    \\
-
-    \m{(Pure)}  & \code{\code{{\pi}}}&\code{\  ::=\ }&
-{ \m{True}}
-   \ | \  \m{False}
-   \ | \ {A(}{t_1, t_2}{)}
-  \   | \  {{\pi_1}} \wedge \code{{\pi}}_2
-   \  | \ {{\pi_1}} \vee \code{{\pi}}_2
-   \  | \ \neg\code{{\pi}}
+    %   \ | \ \anyevent{a}
+   \  | \ \es_1 {\seq} \es_2
+    \ | \ \es_1 {\vee} \es_2
+      %    \  | \ \es_1 \times \es_2
+      \ | \ \es \# t 
+ %  \  | \  \esn{\es}{t}    
+   \  | \  \esn{\es}{\star}    
+  % \  | \ \esn{\es}{\omega} 
+    }
+
+%    \\
+%        \m{(Real\ Time)} &  \mathcal{O} &\code{::= }&
+%    
+%    \code{
+%   %n \ | \ 
+%   c \ | \ (c, {+}\infty) \ | \  [0, c) \ | \  \mathcal{O}_1 \wedge \mathcal{O}_2 \ | \  \mathcal{O}_1 \vee \mathcal{O}_2
+%    }
+
+    \\
+
+    \m{(Pure)}  & \code{\code{\pure{\pi}}}&\code{\  ::=\ }&
+\pure{ \pure{True}}
+   \ | \  \pure{False}
+   \ | \ \pure{A(}{t_1, t_2}\pure{)}
+  \   | \  \pure{\pure{\pi_1}} \wedge \code{\pure{\pi}}_2
+   \  | \ \pure{\pure{\pi_1}} \vee \code{\pure{\pi}}_2
+   \  | \ \neg\code{\pure{\pi}}
 
@@
     & &&\code{
-       | \  {{\pi_1}} \Rightarrow {{\pi_2}}
-   \  | \ \forall x. \code{{\pi}}
-   \  | \ \exists x. \code{{\pi}}
+       | \  \pure{\pure{\pi_1}} \Rightarrow \pure{\pure{\pi_2}}
+   \  | \ \forall x. \code{\pure{\pi}}
+   \  | \ \exists x. \code{\pure{\pi}}
    }\\
@@
     \code{ c
-    \ | \  n
+    \ | \  x
     \ | \  t_1{+}t_2
@@
     \\~\\
-    \multicolumn{4}{c}{
-   \qquad   \code{\anyevent{A} \in \Sigma}   
-   \qquad\qquad\qquad\quad
+    \multicolumn{4}{l}{
+      \code{(Events)  \anyevent{A} ::\in \Sigma}   
+   \qquad
     \code{c ::\in \mathbb{R}^{+}} 
-     \qquad \qquad\qquad \quad
-           \code{n  ::\in \textbf{var} }
-
-     }\\
-
-         \multicolumn{4}{c}{
-     \m{(Real\ Time\ Bound)}\ \code{\mysharp }
-     \qquad\qquad \ \
+     \qquad 
+           \code{x  ::\in \textbf{var} } 
+           \qquad
+
+     \m{(Real\ Time\ Bound)}\ \code{\#}
+     \qquad
         \m{(Kleene\ Star) \ \star}
-         \qquad\qquad \ \
-         \m{(Infinity) \ \omega}
 
@@
   $ \\
-  \caption{Syntax of \timedEffs\ .}
-  \label{work3_fig:Syntax_of_Types_and_Effects}
+  \caption{Syntax of Timed Synchronous Effects.}
+  \label{fig:Syntax_of_Types_and_Effects}
   \vspace{0mm}
@@
  We introduce a new operator \code{\#}, and the effects \code{\es \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
-A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace; or constructed by \code{\omega}, representing an definitely infinite repetition of a trace.
-
-There are two possible states for a signal: present \textbf{S}, or absent $\overline{\textbf{S}}$, 
-%or waiting \anyevent{S?}. 
-The default state of signals in a new time instance is absent. 
-A time instance \code{I} is a set of signals; and it can be possible empty sets \code{ \{ \}}, indicating that there is no signal constraints for the time instance.
+A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace.
 
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          waiting                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : \textbf{S}?}  &\m{iff}\quad 
-& d {\geq} 0  \ and\  {\tt{SAT}(\pi)}  \ and \
-\exists n {\geq} 0.\ \varphi {=} \code{\{ \overline{\textbf{S}} \}^{n} {+}{+} [\{ {\textbf{S}} \}] }
-  \\[0.2em]
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%                            CONCATE                            %%
@@
 d, \varphi \models \pi :  (\es \cdot \esn{\es}{\star} ) 
- \\[0.2em]
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            OMEGA                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d,  \varphi \models \pi : \esn{\es}{\omega}   }  
-&\m{iff}\quad 
-&
-d, \varphi \models \pi :  (\es \cdot \esn{\es}{\omega} )  
  \\[0.2em]
@@
 %how our proposal makes it flexible for different effects logics.
-
-\subsubsection{Logical Incorrect Catching}~\\
-\label{subsec:LogicalIncorrectCatching}
-
-      \vspace{-2mm}
-%We say that the program is logically reactive (resp. logically deterministic) w.r.t. the input event if there is at least (resp. at most) one logically coherent global status.
-
-%A program is logically correct if there exists precisely \textbf{one} status for each signal that respects the coherence law. 
-%it is both logically reactive and deterministic. 
-%To effectively check logical correctness, 
-We regard these programs, which have precisely one safe trace reacting to each input assignments, as logical correct. 
-To effectively check logical correctness, in this work, given a synchronous  program, after been applied to the forward rules, we compute the possible execution traces in a disjunctive form; then prune the traces contain contradictions, following these principles: (i) explicit present and absent; (ii) each local signal should have
-only one status; (iii) lookahead should work for both present and absent; (iv) signal emissions are idempotent; (v) signal status should not be contradictory.
-Finally, upon each assignment of inputs, programs have none or multiple output traces that will be rejected, corresponding to no-valid or multiple-valid assignments.
-
-\begin{table}[h]
-\centering
-\begin{tabular}{c|c|c}
-\footnotesize
-\begin{minipage}[t]{0.32\textwidth}
-\begin{enumerate}
-  \item  \code{\key{present}\ S1 } 
-  \\
- \code{\langle  \textcolor{darklavender}{true : \{\}} \rangle }
-
-  \item    \code{~\qquad \jskey{then}}
-   \\
- \code{\langle  \textcolor{darklavender}{true : \{S1\} } \rangle }
-   \item    \code{~\qquad~\qquad \key{nothing}}
-         \\
- \code{\langle  \textcolor{darklavender}{true : \{S1, \overline{S1}\}} \rangle }
-  \item \code{~\qquad  \jskey{else} }
-  \\
- \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}\} } \rangle }
-  \item    \code{~\qquad~\qquad \key{emit}\ S1 }
-     \\
- \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}, S1\}} \rangle }
-     \item    \code{  \key{end}\  \key{present} }
-     \\
- \code{\langle  \textcolor{darklavender}{true : \{S1, \overline{S1}\} \vee \{\overline{S1}, S1\}} \rangle }
-     \\
-      \code{\langle  \textcolor{darklavender}{false : \bot} \rangle }
-
-\end{enumerate}
-
-  \end{minipage}
-
-  &
-  \small
-  \begin{minipage}[t]{0.32\textwidth}
-   \begin{enumerate}
-  \item  \code{\key{present}\ S1 } 
-  \\
- \code{\langle  \textcolor{darklavender}{true : \{\}} \rangle }
-
-  \item    \code{~\qquad \jskey{then}}
-   \\
- \code{\langle  \textcolor{darklavender}{true : \{S1\} } \rangle }
-  \item    \code{~\qquad~\qquad \key{emit}\ S1 }
-     \\
- \code{\langle  \textcolor{darklavender}{true : \{{S1}, S1\}} \rangle }
-
-  \item \code{~\qquad  \jskey{else} }
-  \\
- \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}\} } \rangle }
-   \item    \code{~\qquad~\qquad \key{nothing}}
-         \\
- \code{\langle  \textcolor{darklavender}{true : \{\overline{S1}, \overline{S1}\}} \rangle }
-     \item    \code{  \key{end}\  \key{present} }
-     \\
- \code{\langle  \textcolor{darklavender}{true : \{{S1}, S1\} \vee \{\overline{S1}, \overline{S1}\}} \rangle }
-     \\
-      \code{\langle  \textcolor{darklavender}{true : \{{S1}\} \vee \{\overline{S1}\} }\rangle }
-
-\end{enumerate}
-
-  \end{minipage}
-
-    &
-  \small
-  \begin{minipage}[t]{0.32\textwidth}
-   \begin{enumerate}
-  \item  \code{\key{abort} } 
-    \\
- \code{\langle  \textcolor{darklavender}{true : emp} \rangle }     
-       \item  \code{~\qquad \key{yield}}  
-           \\
- \code{\langle  \textcolor{darklavender}{true : \{\}} \rangle }
- \item  \code{~\qquad \key{emit}\ A}  
-      \\
- \code{\langle  \textcolor{darklavender}{true : \{A\}} \rangle }
-
-            \item  \code{ \key{when}\  A} 
-      \\
- \code{\langle  \textcolor{darklavender}{true : \{A, \overline{A}\} \vee \{\overline{A}, A\} } \rangle }
-      \\
-      \code{\langle  \textcolor{darklavender}{false : \bot} \rangle }
-
-\end{enumerate}
-
-  \end{minipage}
-
-  \\
-&& 
- \\
-(a) 
-&
-(b)
-&
-(c)
-
-\end{tabular}
-
-       \vspace{5mm}
-      \caption{Logical incorrect examples, caught by the effect logic.}\label{fig:Logical_Incorrect}
-         \vspace{-4mm}
-\end{table}
-
-As shown in \figref{fig:Logical_Incorrect} (a), there are no valid assignments of signal {\textbf{S1}} in this program. 
-As shown in in \figref{fig:Logical_Incorrect} (b), it is also logical incorrect because there are two possible assignments of signal {\textbf{S1}} in this program. 
-As the example shows in \figref{fig:Logical_Incorrect} (c), it is logical incorrect because: if the abortion does not happen, indicating {\textbf{A}} is absent, then the program emits {\textbf{A}}.
-If the abortion does happen, indicating {\textbf{A}} is present, then the program does nothing leaving {\textbf{A}} absent.
-Both way lead to contradiction.
-
-\subsubsection{A Strange Logically Correct Program.}~\\
-
-\begin{wrapfigure}{R}{0.6\columnwidth}
-      \vspace{-6mm}
-\begin{lstlisting}[columns=fullflexible]
-fork { present S1 then emit S1 else nothing end present
-}par { present S1 
-				then	present S2 
-						then nothing 
-						else emit S2 end present 
-				else nothing 
-		end present}        
-\end{lstlisting}  
-      \vspace{-1mm}
-      \caption{Logical Correct.}\label{fig:A_Strange}
-         \vspace{-2mm}
-\end{wrapfigure}
-
-      \vspace{-2mm}
-Another example for synchronous languages shows that composing programs can lead to counter-intuitive phenomena. As the program shows in \figref{fig:A_Strange}, 
-the first parallel branch is the logical incorrect program \figref{fig:Logical_Incorrect} (b), while the second branch contains a non-reactive program enclosed in  "present {\textbf{S1}}" statement.
-Surprisingly, this program is logical correct, since there is only one logically coherent assumption: {\textbf{S1}} absent and {\textbf{S2}}  absent.
-With this assumption, the first present {{S1}}  statement takes its empty else branch, which justifies {{S1}}  absent.
-The second "present \code{\textbf{S1}}" statement also takes its empty else branch, and "emit {\textbf{S2}}" is not executed, which justifies {\textbf{S2}}  absent.
-And our effects logic is able to soundly detect above mentioned correctness checking.
-
-\subsubsection{Semantics of Await}~\\
-
-      \vspace{-2mm}
-We use 
-\tabref{tab:await} as an example to demonstrate the semantics of \code{A?}, i.e., "waiting for the signal \code{A}". 
-%of the \code{Await} language structure.
-%Awaiting an event \code{A} is represented as \code{A?}.
-Formally, we define, 
-%And the semantic of
-
-\vspace{-4mm}
-{\small
-\begin{align*}
-A? \equiv \exists n, n{\geq}0 \wedge \{\overline{A}\}^n \cdot\{A\}
-\end{align*}
-}
-\vspace{-4mm}
-
-\noindent where\code{\{\overline{A}\}} refers to all the time instances containing \code{A} to be absent.
-
-As shown in \tabref{tab:await},
-the LHS \code{\{A\}\cdot\{C\}\cdot B? \cdot \{D\}} entails the
-RHS \code{\{A\}\cdot B? \cdot \{D\}}, as intuitively \code{\{C\}\cdot B?} is a
-special case of \code{B?}.
-In step \code{\textcircled{1}}, \code{\{A\}} is eliminated.
-In step \code{\textcircled{3}}, \code{B?} is normalised into 
-\code{\{B\} \vee (\{\overline{B}\}\cdot B?)}, 
-%In step \code{\textcircled{3}}, \code{B?} is unfolded into 
-%\code{(\epsilon \vee \{\overline{B}\})\cdot B?}, and 
-By the step of \code{\textcircled{4}}, 
-\code{\{C\}} is eliminated 
-together with \code{\{\overline{B}\}} because \code{\{C\} \subseteq \{\overline{B}\}}.
-Now the rest part is \code{B? \cdot \{D\} \CONTAIN B? \cdot \{D\}}.
-Here, we further normalise \code{B?} from the LHS into a disjunction, leading to two proof sub-trees. 
-From the first sub-tree, we keep unfolding the inclusion with \code{\{B\}} (\code{\textcircled{6}}) and \code{\{D\}} (\code{\textcircled{7}}) till we can prove it. 
-Continue with the second sub-tree, we unfold it with \code{\{\overline{B}\}}; then in step \code{\textcircled{8}} we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}.
-We prove it using the \code{[REOCCUR]} rule and finish the whole writing process.
-%Finally from  to \code{\textcircled{7}},
-%we find the inclusion reoccurs, hence we prove this example.
-
-{
-\begin{table*}[h]
-\centering
-      \vspace{0mm}
-\caption{\label{tab:await} The example for Await.}
-
-\vspace{-2mm}
-\begin{adjustbox}{width=0.87\textwidth}
- \Large\begin{tabular}[t]{l}
-  \hline\\
-{
-
-\begin{prooftree}
-
-\Hypo{
-  \code{    
-     \empt
-    \CONTAIN    
-  \empt
-  }
-}
-
-\Infer[dashed]1[{\siderule{\textcircled{7}[PROVE]}}]{
-  \code{    
-   \cancel{ \{D\}}
-    \CONTAIN    
-   \cancel{ \{D\}}
-  }
-}
-
-\Infer[dashed]1[{\siderule{\textcircled{6}[UNFOLD]}}]{
-  \code{    
-    \cancel{\{ B\}} \cdot \{D\}
-    \CONTAIN   
-     (\cancel{\{B\}} \vee \bot) \cdot \{D\}
-  }
-}
-%%%%%%%%%%%
-
-\Hypo{
-  \code{    
-     B? \cdot \{D\}
-    \CONTAIN
-     B? \cdot \{D\} \quad  \textcolor{darklavender}{(\ddagger)}
-  }
-}
-
-\Infer[dashed]1[{\siderule{\textcircled{8}[REOCCUR]}}]{
-  \code{    
-     \cancel{\{\overline{B}\}} \cdot B? \cdot \{D\}
-    \CONTAIN    
-      (\bot \vee (\cancel{\{\overline{B}\}} \cdot B?)) \cdot \{D\}
-  }
-}
-
-\Infer[dashed]2[{\siderule{\textcircled{5}[Disj\text{-}L]}}]{
-  \code{    
-     B? \cdot \{D\}
-    \CONTAIN    
-     B? \cdot \{D\} \quad  \textcolor{darklavender}{(\ddagger)}
-  }
-}
-
-\Infer[dashed]1[{\siderule{\textcircled{4}[Normalisation]}}]{
-  \code{    
-     \cancel{\{C\}} \cdot B? \cdot \{D\}
-    \CONTAIN    
-     (\bot \vee (\cancel{\{\overline{B}\}} \cdot B?)) \cdot \{D\}
-  }
-}
-
-\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{
-  \code{
-     \{C\}\cdot B? \cdot \{D\}
-    \CONTAIN
-     (\{B\} \vee (\{\overline{B}\}\cdot B?)) \cdot \{D\}
-  }
-}
-
-\Infer[dashed]1[{\siderule{\textcircled{2}[Normalisation]}}]{
-  \code{
-     \cancel{\{A\}}\cdot\{C\}\cdot B? \cdot \{D\}
-    \CONTAIN
-     \cancel{\{A\}}\cdot B? \cdot \{D\}
-  }
-}
-\Infer[dashed]1[{\siderule{\textcircled{1}[UNFOLD]}}]{
-  \code{
-    \textcolor {darkred}{True} : \{A\}\cdot\{C\}\cdot B? \cdot \{D\}
-    \CONTAIN
-    \textcolor {darkred}{True} : \{A\}\cdot B? \cdot \{D\}
-  }
-}
-
-\end{prooftree}}
-\\~\\
-
-\hline
-
-\end{tabular}
-\end{adjustbox}
-            \vspace{-1mm}
-\end{table*}
-}
-
-\subsubsection{Broken Promises Chain} ~\\
-
-      \vspace{-2mm}
-As the prior work \cite{madsen2017model,alimadadi2018finding} present, one of the critical issues of using promise is the broken chain of the interdependent promises; and they propose the \emph{promise graph}, as a graphical aid, to understand and debug promise-based code.
-
-%provide solutions to detect such anti-patterns by constructing
-
-\begin{definition}[Well-Synchronised Traces]\label{WELL}
-Based on the syntax (\secref{subsec:Specification_Semantics}) and semantics (\secref{subsec:Specification_language}) defined for timed synchronous effects, in this paper, we call traces without any blocking signals well-synchronised traces.
-\end{definition}
-
-We here show that our algebraic effects can capture non well-synchronised traces during the   
-rewriting process by computing the derivative.   
- For example, the parallel composition of traces:
-\begin{align*}
-\{\textbf{A}\}\cdot\{\textbf{B}\}\cdot\{\textbf{C}\} \cdot\{\textbf{D}\}\  || \ \{\textbf{E}\}\cdot\ \textbf{C}? \cdot\{\textbf{F}\}
-\end{align*}
- leads to the final behaviour of $\{\textbf{A},\textbf{E} \}\cdot\{\textbf{B}\}\cdot\{\textbf{C}\}\cdot\{\textbf{D}, \textbf{F}\}$, which is well-synchronised for all the time instances.
-However, if we were composing traces:
- \begin{align*}
-\{\textbf{A}\}\cdot\{\textbf{B}\} \cdot\{\textbf{D}\}\  || \ \{\textbf{E}\}\cdot\ \textbf{C}? \cdot\{\textbf{F}\}
-\end{align*}
-due to the reasons that forgetting to emit {\textbf{C}} (In JavaScript, it could be the case that forgetting to explicitly return a promise result), it leads to a problematic trace  $\{\textbf{A},\textbf{E} \}\cdot\{\textbf{B}\}\cdot\{\textbf{D}\} \cdot \textbf{C}?
-\cdot \{\textbf{F}\}$.
-The final effects contain a dangling signal waiting of {\textbf{C}}, which  indicates the corresponding anti-pattern.
 
@@
 
-This work is related to i) semantics of synchronous languages and asynchronous promises; ii) research on real-time system modelling and verification; and iii) existing traces-based effects systems.
-
-\subsection{Semantics of Esterel and JavaScript's asynchrony} 
-% 
-The web orchestration language HipHop.js \cite{berry2020hiphop} integrates Esterel’s synchrony with JavaScript’s asynchrony, which provides the infrastructure for our work on mixed synchronous and asynchronous concurrency models.
-To the best of authors' knowledge, the inference rules in this work formally define the first axiomatic semantics for a core language of HipHop.js, which are established on top of the existing semantics of Esterel and JavaScript's asynchrony.
-
-For the pure Esterel, the communication kernel of the Esterel synchronous reactive language, 
-prior work gave two semantics, a macrostep logical semantics called the behavioural semantics \cite{berry1999constructive}, and a small-step semantics called execution/operational semantics \cite{berry1992esterel}.
-%A subsequent work \cite{} gave an update to the logical behavioural macrostep semantics to make it more \emph{constructive}. 
-%The logical behavioural semantics requires existence and uniqueness of a behaviour, while the constructive behavioural semantics introduces \emph{Can} function to determine execution paths in an effective but restricted way.
-Our timed synchronous effects of Esterel primitives closely follow the work of states-based semantics \cite{berry1999constructive}.
-In particular, we borrow the idea of internalizing state into effects using \emph{history} instance trace and \emph{current} time instance, that bind a partial store embedded at any level in a program.
-However, as the existing semantics are not ideal for compositional reasoning in terms of the source program, our forward verifier can help meet
-this requirement for better modularity.
-
-In JavaScript programs, the primitives \code{async} and \code{await} serve for \emph{promises}-based (supported in ECMAScript 6 \cite{ecma1999262}) asynchronous programs, which can be written in a synchronous style, leading to more scalable code.
-However, the ECMAScript 6 standard specifies the semantics of promises informally and in operational terms, which is not a suitable basis for formal reasoning or program analysis.
-Prior work \cite{madsen2017model,alimadadi2018finding}, in order to understand promise-related bugs, present the \code{\lambda_p} calculus, which provides a formal semantics for JavaScript promises.
-Based on these, our work defines the semantics of \code{async} and \code{await} in the event-driven synchronous concurrent context.
-In particular, the asynchronous primitive \code{setTimeout} provides the lower real-time bounds, cooperating with the preemptive primitive \code{abort} from Esterel,  which provides the upper real-time bounds for the program execution.
-
-%``Traditional" FRP was initially implemented as an embedded langauge in Haskell\cite{hudak1996building}, making assertions about the cost of a computation was non-trivial.
-Embedding a language into a higher-order language introduces all of the power of the lambda calculus.
-Inherent in this expressiveness is the possibility of writing programs that perform unreasonable or unbounded amounts of computation as each step, or that have subtle space leaks\cite{mitchell2013leaking}.
-
-%Real-time FRP (RT-FRP) \cite{wan2001real} ensures that signals cannot be used in ways that do not have an efficient implementation.
-RT-FRP uses a two-tiered language: an unrestricted base language ($\lambda$-calculus with recursion) and a limited reactive language for manipulating signals, which supports recursion but not higher- order functions (making it less expressive than traditional FRP).
-RT-FRP ensures that reactive updates will terminate as long as the base language terms terminate, and memory will not grow unless it grows in the base language.
-
-%Elm \cite{czaplicki2013asynchronous} uses two-tiered language, and event driven in that no changes need to be propagated unless the value of a signal has changed, which improves efficiency of the computation.
-Apart from that, the most important novelty of Elm is it permits inter-signal asynchrony: relaxing the order of events between multiple signals.
-
-%Several languages have been proposed around the synchronous data-flow notion of computation.
-The general-purpose functional language Lucid\cite{wadge1985lucid} is an example of this style of language.
-More relevant to the present paper are the language Signal\cite{gautier1987signal}, Lustre\cite{pilaud1987lustre}, and Esterel\cite{berry1992esterel}, which were specifically designed for control of real-time systems.
-This is a analogous to the sequence of values generated in the execution of an RT-FRP program.
-However, none of these synchronous data flow language seem to have considered recursion.
-
 \subsection{Specifications and Real-Time Verification}
@@
 
- \section{Execute the loop body twice to compute the invariant} 
- \label{proof:twice}
-
- \begin{theorem}[twice]\label{twice}
-The deterministic loop invariant can be fixed after the second run of the loop body.
-
-\end{theorem}
-
-\begin{proof}
-
-Let \code{ \langle H,C  \rangle} be the initial program state, where H is the history trace, and C is the current time instance.
-Given any program \code{P}, we use \code{H_P} and \code{C_P} to denote the history trace and current time instance by executing \code{P}.
-Based on the semantics of synchronous programs, there are three possible kinds of loops:
-
-\noindent\textbf{Case 1: loop \{Yield; P\},}
-
-The first  run:    \code{ \langle \epsilon , C\rangle}    Yield; P   \code{ \langle C\cdot H_P, C_P\rangle}
-
-The second run:    \code{ \langle\epsilon , C_P\rangle} Yield; P   \code{ \langle C_P \cdot H_P, C_P\rangle}
-
-The final effects: \code{H \cdot C \cdot H_P \cdot (C_P \cdot H_P)^\star }
-
-\noindent\textbf{Case 2: loop \{P; Yield\},}
-
-The first  run:   \code{ \langle\code{\epsilon }, C\rangle}     P; Yield  \code{ \langle(C || H_P) \cdot C_P, \{\}\rangle}
-
-The second run:    \code{ \langle\code{\epsilon }, \{\}\rangle}    P; Yield  \code{ \langle H_P \cdot C_P, \{\}\rangle}
-
-The final effects: \code{H \cdot (C || H_P) \cdot C_P \cdot (H_P \cdot C_P)^\star}
-
-\noindent\textbf{Case 3: loop \{P1; Yield; P2\},}
-
-The first  run:    \code{ \langle\epsilon , C\rangle}        P1; Yield; P2  \code{ \langle(C || (H_{P1} \cdot C_{P1})) \cdot H_{P2}, C_{P2}\rangle}
-
-The second run:    \code{ \langle\epsilon , C_{P2}\rangle}     P1; Yield; P2  \code{ \langle(C_{P2} || (H_{P1} \cdot C_{P1})) \cdot H_{P2}, C_{P2}\rangle}
-
-The final effects: \code{H \cdot (C || (H_{P1} \cdot C_{P1})) \cdot H_{P2} \cdot ((C_{P2} || (H_{P1} \cdot C_{P1})) \cdot H_{P2})^\star}~\\
-
-\noindent In all possible cases, the loop invariant can be fixed by the end of the second run. 
-(cf. \figref{fig:loop1})
-\end{proof}
-
 \end{document}

### 2022-03-24 tv.tex
m

@@
 \newcommand{\anyevent}[1]{{\textcolor{darkred}
-{\underline{\textbf{\footnotesize #1}}}}}
+{{\textbf{\footnotesize #1}}}}}
 \newcommand{\seq}{\cdot}
@@
 In this work, we study temporal verification of 
-compositional real-time systems, which are modeled 
+compositional real-time systems, modeled 
 using mutable variables and timed processes.  
 Instead of explicitly manipulating clock variables, 
-a number of compositional timed behavioral patterns, 
+several compositional timed behavioral patterns, 
 such as \emph{delay}, \emph{timeout}, \emph{deadline},  
 are introduced to capture quantitative timing constraints.
-The idea is to dynamically create clocks, 
+The idea is to dynamically create clocks  
 and solve constraints on the clocks.
@@
 term rewriting system (TRS) on \emph{Timed Effects} (\timedEffects).  
-More specifically, we formally define 
-a core language \timedL, generalizing the timed systems.
-Secondly, we introduce \timedEffects, a new effects logic, 
+We formally define 
+a core language \timedL, generalizing the timed processes.
+Secondly, to capture real-time specifications, 
+we introduce \timedEffects, a new effects logic, 
 that extends 
-\emph{Kleene Algebra} with value-dependent real-time constraints. 
-Thirdly,  we establish an  axiomatic semantics for  
-\timedL\  to infer temporal behaviors  of  given 
-programs, expressed in \timedEffects. 
+\emph{Kleene Algebra} with dependent
+values and arithmetic constraints.
+Thirdly,  the forward verifier infers temporal behaviors of given 
+\timedL\ programs, expressed in \timedEffects. 
 Lastly, we present a purely algebraic TRS, to 
@@
 we prototype the verification system; prove its 
-correctness; report case studies and the experimental results. 
+correctness; report on case studies and the experimental results. 
 %we prototype the  verification system in OCaml; then prove soundness of both the effects inference process and the term rewriting process. % in Coq.
@@
 
-Existing techniques are based on a transformation to convert the asynchronous chunk into semantically equivalent synchronization\footnote{Usually the transformation is incomplete, i.e., not all the asynchronous programs can be translated into a semantically equivalent synchronization.}; then reason about the behaviours based on the synchronous semantics \cite{damian2019communication,gleissenthall2019pretend,tarawneh2018formal}.
-This approach (i) suffers from the limited expressiveness, restricted by finite-state automata (FSA); (ii) lacks the modularity to reason about programs compositionally; (iii) loses time awareness due to the conversion to synchronous models; and (iv) has the \emph{state explosion problem}  when proving language inclusions between FSA.
- %finite-state automata
- % PSPACE-complete complexity
-
-To tackle the above issues and exploit the best of both synchronous and asynchronous concurrency models, we propose a novel temporal specification language, which enables a compositional verification via a  Hoare-style forward verifier and a term rewriting system (TRS).
-More specifically, we specify system behaviours in the form of \emph{Timed Synchronous Effects (TSE)}, which integrates the Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous,broda2015deciding} with dependent values and arithmetic constraints,
+Specification and verification of real-time systems are important 
+research topics which have practical implications. During the last 
+(more than) two decades, a popular approach for specifying real-time systems is 
+based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
+Timed Automata are powerful 
+in designing real-time models with explicit clock variables. Real-time 
+constraints are captured by explicitly setting/reseting clock variables. 
+A number of automatic verification support for Timed Automata have proven 
+to be successful, such as UPPAAL \cite{DBLP:journals/sttt/LarsenPY97}.
+
+Models based on Timed Automata often adapt a simple structure, e.g. a 
+network with no hierarchy. The benefit is that 
+efficient model checking is made feasible. Nonetheless, designing and 
+verifying compositional real-time systems is becoming an increasingly 
+difficult task due to the widespread applications and increasing complexity 
+of such systems. In industrial case studies of real-time system verification, system 
+requirements are often structured into phases, which are then composed 
+sequentially, in parallel and alternatively \cite{DBLP:conf/emsoft/LarsenMNS05}. 
+Unlike timed process algebras, Timed Automata lack high-level 
+compositional patterns for hierarchical design. As a result, users often 
+need to manually cast those terms into a set of clock variables with 
+carefully calculated clock constraints. The process is tedious and error-prone.
+
+We propose a novel temporal specification language, 
+which enables a compositional verification via a  Hoare-style 
+forward verifier and a term rewriting system (TRS). 
+More specifically, we specify system behaviours in the form of 
+{Timed Effects} (\timedEffects), which integrates the Kleene Algebra with dependent values and arithmetic constraints, 
 %gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
@@
 %capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
-provide real-time abstractions into traditional synchronous verification. 
+provide real-time abstractions into traditional linear temporal logics. 
 %Resource usages, provided by a \emph{dynamic ticks}\cite{von2017real}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
-For example, one safety property, \textit{"The event \anyevent{Done} will be triggered no later than one second"}\footnote{For simplicity, we  follow the convention of JavaScript, and use integer values to represent milliseconds in this paper, while it can be easily extended to real numbers and other time measurement units.}, is expressed in our effects logic as:
+For example, one safety property, \textit{"The event \anyevent{Done} 
+will be triggered no later than one second"}\footnote{For 
+simplicity, we use integer values to represent seconds in this 
+paper, while it can bes extended to real numbers and other 
+time measurement units.}, is expressed in \timedEffects\ as: 
 \begin{align*}
-&\code{\effect \defeq \  0 {\leq} t {<}1000 : (\{{\anyevent{}\}^\star} \cdot \{\anyevent{Done}\} ) \# t}.
+&\code{\effect \defeq \  0 {\leq} t {<}1 : ({\_^\star} \cdot \anyevent{Done} ) \# t}.
 \end{align*}  
@@
 %which replaces temporal operators by time-constrained versions from 
-Here, \code{\#} is the parallel operator specifying the \emph{real-time} constraints for the \emph{logical-time} sequences \cite{von2017real}; 
-curly braces \code{\{\}} enclose a single  logical-time instance\footnote{A time instance is a set of signals (possible empty) with status, logically concurring at the same time (cf.
-{\secref{subsec:Specification_language}}).};
+Here, \code{\#} is the novel operator specifying the \emph{real-time} 
+constraints for the \emph{logical-time} sequences \cite{von2017real}; 
+\code{\_} is a wildcard matching to any event; 
 Kleene star \code{\star} denotes trace repetition.
-The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1000)}\ }\anyevent{Done}' in metric temporal logic (MTL), reads \textit{"within one second, \anyevent{Done} finally happens"}.
-Moreover, the time bounds can be dependent on the program inputs.
-For example, we express, the effects of \code{send(d)} as:
+The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1)}\ }\anyevent{Done}' 
+in metric temporal logic (MTL), reads \textit{"within one second, 
+\anyevent{Done} finally happens"}. Moreover, the time bounds can be dependent on the program inputs. For example, we express, the effects of \code{send(d)} as:
 \begin{align*}
-&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5000 \wedge  0 {\leq} t {<} d) : (\{{\anyevent{Send}\} \# t)} \cdot \{\anyevent{Done}\}}.
+&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d) : ({\anyevent{Send} \# t)} \cdot \anyevent{Done}}.
 \end{align*}  
-The \code{send} method takes a parameter \code{d}, and \anyevent{Send}s out a message at time \code{t}.  
-The above formula  \code{\effect^{send (d)}} indicates that the input  \code{d} is positive and smaller or equal to \code{5000}; the method generates a finite trace, with the first time instance containing the event \anyevent{Send}, followed by a second time instance containing the event \anyevent{Done}; and the instance \code{\{}\anyevent{Send}\code{\}} takes a no more than \code{d} milliseconds delay to finish.
-Although these examples are simple, they show the benefits of deploying value-dependent time bounds.
-Intuitively, if traditional timed automata \cite{larsen1997uppaal} define an \emph{exact} transition system, our timed effects define a set (possibly infinite) of exact transition systems.
+The \code{send} method takes a parameter \code{d}, and \anyevent{Send}s 
+out a message at time \code{t}.  
+The above formula  \code{\effect^{send (d)}} indicates that the 
+input  \code{d} is positive and smaller or equal to \code{5}; the method 
+generates a finite trace, with the first event \anyevent{Send}, followed by 
+a second event \anyevent{Done}; and \anyevent{Send} takes a no more 
+than \code{d} milliseconds delay to finish. 
+Although these examples are simple, they show the benefits of deploying 
+value-dependent 
+time bounds. Intuitively, if traditional timed automata define an 
+\emph{exact} transition system, our timed effects define a set 
+(possibly infinite) of exact transition systems.
 
@@
 @*/}}}) for each program, which leads to a compositional verification strategy, where static checking and timed temporal verification can be done locally.
-%The set of signals to be present in one logical time instance are represented within one \code{\{\}}.
+%The set of signals to be present in one logical time instance are represented within one \code{\_}.
 
@@
 After emitting the signal \anyevent{Connecting}, it emits  \anyevent{Connected} if the connection succeeds before the  preemptive deadline; otherwise, no signal is emitted. 
-The precondition \code{d{>}3000 : \{
-\}^\star \cdot\{\m{Login}\} } requires that the input variable \code{d} is greater than 3000, and before entering into this module, the signal \anyevent{Login} should be emitted at the last time instance, indicating that a login request has been sent.
-The postcondition contains two parts and connected using the disjunction mark \code{{\vee}}: when \code{3000{<}t{<}d}, the effects contains two time instances, \code{\{\m{Connecting}\}} and \code{\{\m{Connected}\}}, while the first  time instance finishes at time \code{t}, %(assuming to reset the clock when executing the module),
+The precondition \code{d{>}3 : \{
+\}^\star \cdot\{\m{Login}\} } requires that the input variable \code{d} is greater than 3, and before entering into this module, the signal \anyevent{Login} should be emitted at the last time instance, indicating that a login request has been sent.
+The postcondition contains two parts and connected using the disjunction mark \code{{\vee}}: when \code{3{<}t{<}d}, the effects contains two time instances, \code{\{\m{Connecting}\}} and \code{\{\m{Connected}\}}, while the first  time instance finishes at time \code{t}, %(assuming to reset the clock when executing the module),
 which is no later than \code{\m{d}} milliseconds; otherwise, the effects contains one time instance \code{\{Connecting\}} which finishes at time \code{d}. \emph{(See a demo from \cite{CODE1})}
@@
 The precondition of {\ttfamily{main}} requires no arithmetic constraints on its input values (expressed as \code{\m{true}}), neither any pre-traces  (expressed as \code{\m{emp}} or \code{\epsilon}, indicating an empty trace).
-The postcondition ensures a trace, where the second time instance contains at least one signal \code{\anyevent{Cook}} and finishes within 3000 milliseconds after the completion of the first time instance.
-Then we do not care about the rest of the trace (\code{\{\}} is similar to a wildcard).
+The postcondition ensures a trace, where the second time instance contains at least one signal \code{\anyevent{Cook}} and finishes within 3 milliseconds after the completion of the first time instance.
+Then we do not care about the rest of the trace (\code{\_} is similar to a wildcard).
 %We omit the implementation of \code{cook} here, while provide the specifications of it. 
@@
 /*@ requires true : emp @*/
-/*@ ensures  0<=t/\t<3000 : {}.({Cook})#t.{}^* @*/
+/*@ ensures  0<=t/\t<3 : {}.({Cook})#t.{}^* @*/
 {
@@
 		await Ready; emit Go; 
-	}par{ // The effects of the second thread is 0<t<3000 : {Prep, Cook}#t.{Ready}
+	}par{ // The effects of the second thread is 0<t<3 : {Prep, Cook}#t.{Ready}
 		emit Prep;
-		async Ready { run cook (3000, Tick, Cook); }}}
-// The final effects for main is  0<=t/\t<3000 : ({Prep}.{Cook})#t.{Ready}.{Go}
+		async Ready { run cook (3, Tick, Cook); }}}
+// The final effects for main is  0<=t/\t<3 : ({Prep}.{Cook})#t.{Ready}.{Go}
 
 hiphop module cook (var d, in Tick, out Cook)
-/*@ requires d>2000  : {}^*.{Prep} @*/
+/*@ requires d>2  : {}^*.{Prep} @*/
 /*@ ensures  0<=t/\t<d : ({}.{Cook})#t @*/
@@
    \\
- \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\{\} } \rangle }
+ \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\_ } \rangle }
      \siderule{ [FV\text{-}Await]}
@@
  %     \\
-% \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\{\}} \rangle }
+% \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\_} \rangle }
  %    \siderule{ [FV\text{-}Yield]}
 %     \\
-  \item      \code{~\qquad \ \qquad \key{run}\ cook\ (3000, Cook) 
+  \item      \code{~\qquad \ \qquad \key{run}\ cook\ (3, Cook) 
      \}\}\}}
@@
                      \textcolor{mGray}{\emph{(-TRS: check the  precondition of module cook-) }} \\
-              \code{  \textcolor{darkred}{d{=}3000 : \{Prep\}  \CONTAIN  d{>}2000 \wedge \{Prep\}} }   \\
+              \code{  \textcolor{darkred}{d{=}3 : \{Prep\}  \CONTAIN  d{>}2 \wedge \{Prep\}} }   \\
 
@@
       \\
-     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3000 : (\{Prep\}\cdot \{Cook\})\# t}  \rangle } 
+     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\# t}  \rangle } 
      \siderule{ [FV\text{-}Call]}
       \\
-     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3000 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}}  \rangle } 
+     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}}  \rangle } 
      \siderule{ [FV\text{-}Async]}
      \\ \item
-                   \code{\langle \textcolor{huntergreen}{(true \wedge 0{\leq}t {<}3000) :  Ready?
+                   \code{\langle \textcolor{huntergreen}{(true \wedge 0{\leq}t {<}3) :  Ready?
 \cdot\{Go\}  \ || \  (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}} \rangle }   \siderule{ [FV\text{-}Fork]}
         \\ 
-         \code{\langle \textcolor{huntergreen}{0{\leq}t {<}3000 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}} \rangle }
+         \code{\langle \textcolor{huntergreen}{0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}} \rangle }
          \siderule{ [Effects\text{-}Normalization]} 
@@
                   \code{  \textcolor{darkred}{
-{0 {\leq} t {<}3000} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN {0 {\leq} t  {<}3000} : \{\}\cdot (\{Cook\})\# t \cdot\{\}^\star} 
+{0 {\leq} t {<}3} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
+ \CONTAIN {0 {\leq} t  {<}3} : \_\cdot (\{Cook\})\# t \cdot\_^\star} 
                   }    \\
@@
  satisfy the declared postcondition. 
-%property \code{\effect^\prime  {=} 0{\leq} t {<}3 : \{\}\cdot(\{Cook\}\# t)\cdot\{\}^\star}, 
-%where \code{\effect^\prime} simply indicates that the signal \anyevent{Cook} needs to happen at the second time instance, and takes no more than \code{3000} milliseconds after the first time instance has completed; and \code{\{\}^\star} means we do not care the rest of the traces.
+%property \code{\effect^\prime  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\# t)\cdot\_^\star}, 
+%where \code{\effect^\prime} simply indicates that the signal \anyevent{Cook} needs to happen at the second time instance, and takes no more than \code{3} milliseconds after the first time instance has completed; and \code{\_^\star} means we do not care the rest of the traces.
 We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.
@@
       \vspace{0mm}
-\caption{\label{tab:rewriting_tree_send} The inclusion proving example. (For simplicity, we use 3 seconds to replace the 3000 milliseconds.)}
+\caption{\label{tab:rewriting_tree_send} The inclusion proving example. (For simplicity, we use 3 seconds to replace the 3 milliseconds.)}
 
@@
 } \qquad
-\code{emp  \CONTAIN  \{\}^\star}
+\code{emp  \CONTAIN  \_^\star}
 }
@@
 } :  emp
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee \{\}^\star}}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee \_^\star}}
 \Infer[dashed]1[{\siderule{\textcircled{7}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
@@
 } :  \cancel{\{Go\}}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\{\}} \cdot \{\}^\star}}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\_} \cdot \_^\star}}
 \Infer[dashed]1[{\siderule{\textcircled{6}[Normalization]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
@@
 } :  \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee  \{\}^\star}}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee  \_^\star}}
 \Infer[dashed]1[{\siderule{\textcircled{5}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
@@
 :  \cancel{\{ Ready\}} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\{\}} \cdot \{\}^\star}}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\_} \cdot \_^\star}}
 \Infer[dashed]1[{\siderule{\textcircled{4}[UNFOLD{-}UNIFY]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L
  } : \cancel{\{Cook\} \# t_L^2} \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\# t_R}\cdot\{\}^\star}  }
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\# t_R}\cdot\_^\star}  }
 \Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L } : \cancel{\{Prep\}\# t_L^1} \cdot \{Cook\} \# t_L^2 \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\{\}}\cdot\{Cook\}\# t_R \cdot\{\}^\star}  }
+ \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\_}\cdot\{Cook\}\# t_R \cdot\_^\star}  }
 \Infer[dashed]1[{\siderule{\textcircled{2}[SPLIT]}}]{\code{ \textcolor {darkred}{t_L {<}3} : (\{Prep\}\cdot \{Cook\})\# t_L \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \{\}\cdot\{Cook\}\# t_R\cdot\{\}^\star}  }
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \_\cdot\{Cook\}\# t_R\cdot\_^\star}  }
  \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{ \textcolor {darkred}{t {<}3} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t {<}3} : \{\}\cdot\{Cook\}\# t\cdot\{\}^\star}  }
+ \CONTAIN \textcolor {darkred}{t {<}3} : \_\cdot\{Cook\}\# t\cdot\_^\star}  }
 \end{prooftree}}
@@
 
-Note that time instance \code{\{Prep\}} entails \code{\{\}} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
+Note that time instance \code{\{Prep\}} entails \code{\_} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
 Intuitively, we use \code{[DISPROVE]} wherever the left-hand side (LHS) is \emph{nullable}\footnote{If the event sequence is possibly empty, i.e.
@@
 Then \code{t_L^1} and \code{t_L^2} mark the real-time constraints for time instances  \code{\{Prep\}} and \code{\{Cook\}} respectively.
-Then in step \code{\textcircled{3}}, we eliminate \code{\{Prep\}} from the LHS and \code{\{\}} from the RHS, as the instances entailment  \code{\{Prep\} \subseteq \{\}} holds.  
+Then in step \code{\textcircled{3}}, we eliminate \code{\{Prep\}} from the LHS and \code{\_} from the RHS, as the instances entailment  \code{\{Prep\} \subseteq \_} holds.  
 In step \code{\textcircled{4}}, in order to conduct a further unfolding, we unify time variables \code{t_L^2} and \code{t_R} by adding the constraint \code{t_L^2 {=} t_R}. 
-In step \code{\textcircled{5}}, from the RHS, since \code{\{\}^\star {=} emp \vee \{\} \cdot \{\}^\star}, eliminating one time instance \code{\{Ready\}} from it will lead to \code{\bot \vee \{\}^\star}, which can be normalised into \code{\{\}^\star} in step \code{\textcircled{6}}.
+In step \code{\textcircled{5}}, from the RHS, since \code{\_^\star {=} emp \vee \_ \cdot \_^\star}, eliminating one time instance \code{\{Ready\}} from it will lead to \code{\bot \vee \_^\star}, which can be normalised into \code{\_^\star} in step \code{\textcircled{6}}.
 At the end of the rewriting, we manage to prove that \code{(t_L {<}3 {\wedge} t_L^1 {+} t_L^2 {=}t_L {\wedge}t_L^2 {=} t_R)  \Rightarrow  t_R {<} 3} \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
 
-%(\code{\{Go\} \Rightarrow \{\}})
-%(\code{\{Ready\} \Rightarrow \{\}}, \code{t_L^2 \Rightarrow true})
+%(\code{\{Go\} \Rightarrow \_})
+%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
 Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic} (cf.
@@
 which provides the infrastructure for mixing synchronous and asynchronous concurrency models. 
-We here formally define the syntax of \code{\lambda_{HH}}, as shown in \figref{fig:Hiphop_Syntax} The statements marked as \textcolor{purple} {purple} come from the  Esterel v5 \cite{berry1999constructive,berry2000esterel} endorsed by current academic compilers; while the statements marked as \textcolor{blue} {blue} provide the asynchrony coming from the usage of JavaScript promises.
+We here formally define the syntax of \code{\lambda_{HH}}, as shown in \figref{fig:Hiphop_Syntax} The statements marked as \textcolor{purple} {purple} come from the  Esterel v5 \cite{berry1999constructive,berry2esterel} endorsed by current academic compilers; while the statements marked as \textcolor{blue} {blue} provide the asynchrony coming from the usage of JavaScript promises.
 In this work, we are mainly interested in signal status and control propagation, which are not related to data, therefore the data variables and data-handling primitives are abstracted away.
@@
 
-%The signals shown in one time instance  represent the \emph{minimal} set of signals which are required/guaranteed to be there. An empty set \code{\{\}} represents any set of signals
+%The signals shown in one time instance  represent the \emph{minimal} set of signals which are required/guaranteed to be there. An empty set \code{\_} represents any set of signals
 
@@
 Note that \code{\Gamma}, \code{\effect} are derived during the inclusion proof. 
-The inclusion checking is initially invoked with \code{\Gamma{=}\{\}} and \code{\effect{=} True : \empt}.
+The inclusion checking is initially invoked with \code{\Gamma{=}\_} and \code{\effect{=} True : \empt}.
 
@@
  \begin{gather*} 
-\code{fst^\prime( \bott) {=} \{ \} } \qquad\ 
-\code{ fst^\prime(\empt) {=} \{ \}} \qquad\ 
+\code{fst^\prime( \bott) {=} \_ } \qquad\ 
+\code{ fst^\prime(\empt) {=} \_} \qquad\ 
 \code{fst^\prime( I) {=} \{ I \} }
@@
  \begin{gather*} 
-\code{fst_{\pure{\pi}}( \bott) {=} \{ \} } \qquad\quad
-\code{fst_{\pure{\pi}}(\empt) {=} \{ \} } \qquad\quad
+\code{fst_{\pure{\pi}}( \bott) {=} \_ } \qquad\quad
+\code{fst_{\pure{\pi}}(\empt) {=} \_ } \qquad\quad
 \code{fst_{\pure{\pi}}( I ) {=} \{ (I, \pi {\wedge} t{\geq}0, t) \}  \ (t\ is\ fresh)} 
@@
 
-%The core implementation is less than 3500 LOC, roughly, 1000{+} LOC for the verifier, and 2000{+} LOC for the TRS. We prove the soundness of the TRS. 
+%The core implementation is less than 3500 LOC, roughly, 1{+} LOC for the verifier, and 2{+} LOC for the TRS. We prove the soundness of the TRS. 
 %Next, we show case studies to demonstrate the feasibilities of our timed synchronous effects comparing to timed automata.
@@
 \code{
-\textcolor {darkred}{n{=}0} \Rightarrow \textcolor {darkred}{n{\geq}0} \qquad emp \subseteq \{\}^\star \qquad  \code{\siderule{[PROVE]}}
+\textcolor {darkred}{n{=}0} \Rightarrow \textcolor {darkred}{n{\geq}0} \qquad emp \subseteq \_^\star \qquad  \code{\siderule{[PROVE]}}
 }
@@
 \Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : emp
- \CONTAIN \textcolor {darkred}{n{\geq}0} :  \bot \vee \{\}^\star \vee emp }  
+ \CONTAIN \textcolor {darkred}{n{\geq}0} :  \bot \vee \_^\star \vee emp }  
  }
 \Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : {\{Done\}} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} }  
+ \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} }  
  }
 \Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : \{Done\} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} \vee
+ \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} \vee
  \textcolor {darkred}{n{<}0} :
@@
   \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} \vee
+ \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} \vee
  \textcolor {darkred}{n{<}0} :
@@
  \Infer[dashed]2[]{\code{ \textcolor {darkred}{n{=}0} : \{Done\} \vee  \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \{\}^\star \cdot\{Done\} \vee
+ \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} \vee
  \textcolor {darkred}{n{<}0} :
@@
       \vspace{-2mm}
-%(\code{\{Go\} \Rightarrow \{\}})
-%(\code{\{Ready\} \Rightarrow \{\}}, \code{t_L^2 \Rightarrow true})
+%(\code{\{Go\} \Rightarrow \_})
+%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
 Termination of TRS is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic}, i.e., the rule \code{[REOCCUR]}.
@@
 There have been a number of translation-based approaches on building verification support for timed process algebras.
-For example, Timed CSP \cite{dong2008timed} is translated to Timed Automata (TA) so that the model checker Uppaal can be \cite{larsen1997uppaal} applied.
+For example, Timed CSP \cite{dong2008timed} is translated to Timed Automata (TA) so that the model checker Uppaal can be \cite{DBLP:journals/sttt/LarsenPY97} applied.
 TA are finite state automata equipped with clock variables. Models based on TA often have simple structures. For example, the input models of the Uppaal are networks of TA with no hierarchy.

### 2022-03-24 tv.tex
m

@@
 
-We propose a novel temporal specification language, 
+We investigate an alternative approach for modeling and verifying 
+compositional real-time systems. In this work, 
+we propose a novel temporal specification language, 
 which enables a compositional verification via a  Hoare-style 
@@
 %which replaces temporal operators by time-constrained versions from 
-Here, \code{\#} is the novel operator specifying the \emph{real-time} 
+Here, \code{\#} is a novel operator specifying the \emph{real-time} 
 constraints for the \emph{logical-time} sequences \cite{von2017real}; 
@@
 time bounds. Intuitively, if traditional timed automata define an 
-\emph{exact} transition system, our timed effects define a set 
-(possibly infinite) of exact transition systems.
+\emph{exact} transition system, \timedEffects\ define 
+a set (possibly infinite) of exact transition systems.
 
@@
 
-Having the effects logic as the specification language, we are interested in the following verification problem: 
-Given a program \code{\mathcal{P}}, and a temporal property \code{\effect^{\prime}}, does \code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds? In a typical verification
-context, checking the inclusion/entailment between the program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.
-
-Traditional ways of temporal verification either (i) rely on a translation from specification languages, such as LTL or CSP, into finite state automata \cite{sun2009pat}, which potentially gives rise to an exponential blow-up; %such as NFAs or DFAs;
-or (ii) use expressive automata to model the program logic directly, such as timed automata, which fails to capture the bugs introduced by the real implementation.
-
-In this paper, we present a new solution of extensive temporal verification comprising: a front-end verifier computes the program's  temporal behaviour, to be the \code{\effect^{\mathcal{P}}}, via inference rules at the source level; %defining program evaluation syntactically;
-and a back-end TRS, to soundly check \code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}}.
-
-The TRS  is inspired by Antimirov and Mosses’ algorithm \cite{antimirov1995rewriting}\footnote{Antimirov and Mosses' algorithm was designed for deciding the inequalities of regular expressions based on an
+Having \timedEffects\ to be  the specification language, we are interested in the following verification problem: 
+Given a program \code{\mathcal{P}},
+% with the concrete temporal behavior \code{\effect^{\mathcal{P}}}, 
+and a temporal specification \code{\effect^{\prime}}, does 
+\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds? Typically, 
+checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.
+
+To efficiently solve the inclusions, i.e., without any translation into
+finite state automata, we develop a TRS
+which  is inspired by Antimirov and Mosses’ algorithm 
+\cite{antimirov1995rewriting}\footnote{Antimirov and Mosses' 
+algorithm was designed for deciding the inequalities of regular 
+expressions based on an 
 complete 
-axiomatic algorithm of the algebra of regular sets.} but solving the language inclusions between more expressive timed synchronous effects.
-A TRS is a refutation method that normalizes expressions in such a way that checking their inclusion corresponds to an iterated process of checking the inclusion of their \emph{partial derivatives} \cite{antimirov1995partial}.
+axiomatic algorithm of the algebra of regular sets.} but solving the 
+language inclusions between more expressive \timedEffects.
+
+\begin{comment}
+A TRS is a refutation method that normalizes expressions in such a way 
+that checking their inclusion corresponds to an iterated process of 
+checking the inclusion of their \emph{partial derivatives} 
+\cite{antimirov1995partial}. 
 Works based on such a TRS \cite{song2020automated,antimirov1995rewriting,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
-
-This work targets timed temporal verification, and to the best of the authors’ knowledge, it proposes the first axiomatic semantics and the first algebraic TRS (proven sound and complete) for the mixed synchronous and asynchronous concurrency model.
+\end{comment}
+
+This work targets timed temporal verification, and to the best of 
+the authors' knowledge, it proposes the first algebraic TRS 
+ for the real-time verification. 
   Our main contributions are:% as follows:
@@
 \begin{enumerate}
-\item \textbf{The Timed Effects:} We define the syntax ({\secref{subsec:Specification_language}}) and semantics ({\secref{subsec:Specification_Semantics}}) of timed synchronous effects, to be the specification language, which captures the target programs' behaviours and non-trivial temporal properties.
-
-\item \textbf{Automated Forward Verifier:} Targeting a core language \code{\lambda_{HH}} ({\secref{subsec:Targetlanguage}}), we 
-establish its axiomatic semantics via a set of inductive transition rules (\secref{sec:Verification}), enabling a compositional verifier to infer the program's effects.
-The verifier triggers the back-end solver TRS.
+\item \textbf{The Timed Effects:} We define the syntax 
+({\secref{subsec:Specification_language}}) and semantics 
+({\secref{subsec:Specification_Semantics}}) of \timedEffects, to be the 
+specification language, which captures the target programs' behaviours 
+and non-trivial temporal properties.
+
+\item \textbf{Automated Forward Verifier:} Targeting a core language 
+\code{\timedL} ({\secref{subsec:Targetlanguage}}), we 
+establish its axiomatic semantics via a set of constructive rules 
+(\secref{sec:Verification}), enabling a compositional verifier to 
+infer the program's effects. The verifier triggers the back-end 
+solver TRS.
 
@@
 We present the rewriting rules, to prove 
-the inferred effects against given temporal properties, both expressed by timed synchronous effects (\secref{sec:Entailment_Prover}).
-
-\item \textbf{Implementation and Evaluation:} We prototype the novel effects logic and the automated verification system, %on top of the HIP/SLEEK system\cite{chin2012automated}, 
+the inferred effects against given temporal properties. %, both expressed by \timedEffects (\secref{sec:Entailment_Prover}).
+
+\item \textbf{Implementation and Evaluation:} We prototype the novel 
+effects logic and the automated verification system, %on top of the HIP/SLEEK system\cite{chin2012automated}, 
 %which is available online\cite{Demo}, 
-prove the correctness, report on a case study investigating how it can help to debug errors related to both synchronous and asynchronous programs (\secref{subsec:Case_Studies}).
+prove the correctness, report on case studies and experimental results. 
+%investigating how it can help to debug errors related to both synchronous and asynchronous programs (\secref{subsec:Case_Studies}).
 
@@
 %\subsection{HipHop.js and Dependent Effects}
-\subsection{Timed Synchronous Effects}
+\subsection{\timedEffects}
 As shown in \figref{fig:overview_eg1}, we define Hoare-triple style specifications (enclosed in \textcolor{darklavender}{\ttfamily{{/*@ ...
@@
 \subsection{The TRS}
-Our TRS is obligated to check the inclusions between timed synchronous effects, which is an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{antimirov1995rewriting}  
+Our TRS is obligated to check the inclusions between \timedEffects, which is an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{antimirov1995rewriting}  
 %a TRS 
@@
 
-Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between timed synchronous effects, where \code{D_{I\# t}(\effect)} is the partial derivative of \code{\effect} w.r.t the time instance \code{I} and time bound \code{t}.
-
-\begin{definition}[Timed Synchronous Effects Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
-For timed synchronous effects \code{\effect_1 } and \code{\effect_2}, 
+Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\# t}(\effect)} is the partial derivative of \code{\effect} w.r.t the time instance \code{I} and time bound \code{t}.
+
+\begin{definition}[\timedEffects Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
+For \timedEffects \code{\effect_1 } and \code{\effect_2}, 
 \code{\effect_1  \CONTAIN \effect_2 \Leftrightarrow \forall I. \forall t {\geq} 0.\ D_{I\# t}(\effect_1)  \CONTAIN D_{I\# t}(\effect_2)}.
@@
 
-%Adapting to the context of checking inclusions between timed synchronous effects, we extend the Antimirov algorithm with
+%Adapting to the context of checking inclusions between \timedEffects, we extend the Antimirov algorithm with
 
@@
 
-To formulate the target language, we generalise the design of  Hiphop.js into a core language \code{\lambda_{HH}}, 
+To formulate the target language, we generalise the design of  Hiphop.js into a core language \code{\timedL}, 
 %Based on the design of , but not too specific to Hiphop.js, we summarise a core language to be our target language, 
 which provides the infrastructure for mixing synchronous and asynchronous concurrency models. 
-We here formally define the syntax of \code{\lambda_{HH}}, as shown in \figref{fig:Hiphop_Syntax} The statements marked as \textcolor{purple} {purple} come from the  Esterel v5 \cite{berry1999constructive,berry2esterel} endorsed by current academic compilers; while the statements marked as \textcolor{blue} {blue} provide the asynchrony coming from the usage of JavaScript promises.
+We here formally define the syntax of \code{\timedL}, as shown in \figref{fig:Hiphop_Syntax} The statements marked as \textcolor{purple} {purple} come from the  Esterel v5 \cite{berry1999constructive,berry2esterel} endorsed by current academic compilers; while the statements marked as \textcolor{blue} {blue} provide the asynchrony coming from the usage of JavaScript promises.
 In this work, we are mainly interested in signal status and control propagation, which are not related to data, therefore the data variables and data-handling primitives are abstracted away.
@@
   $ \\
-  \caption{Syntax of Timed Synchronous Effects.}
+  \caption{Syntax of \timedEffects.}
   \label{fig:Syntax_of_Types_and_Effects}
@@
 
-The  syntax of the timed synchronous effects is formally defined in \figref{fig:Syntax_of_Types_and_Effects} Effects is  a conditioned time  instance sequence \code{\pure{\pi} : \es} or a disjunction of two effects $\effect_1 \vee \effect_2$.
+The  syntax of the \timedEffects is formally defined in \figref{fig:Syntax_of_Types_and_Effects} Effects is  a conditioned time  instance sequence \code{\pure{\pi} : \es} or a disjunction of two effects $\effect_1 \vee \effect_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : I }  &\m{iff}\quad 
+&\code{d, \varphi \models  \pi : \anyevent{A} }  &\m{iff}\quad 
 & d {\geq} 0 \ and\ {\tt{SAT}(\pi)}  \ and \ 
-\varphi {=} \code{[I]}
+\varphi {=} \code{[\anyevent{A}]}
   \\[0.2em]
@@
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                       par                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1 || \es_2) }  
-&\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ and \ 
- \code{d, \varphi \models  \pi :  \es_2}  
-\\[0.2em]
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%                       timed                         %%
@@
     \vspace{-3mm}
-\caption{Semantics of Timed Synchronous Effects.}
+\caption{Semantics of \timedEffects.}
 \label{fig:Sementic}
@@
 
-As shown in \figref{fig:Sementic}, we define the semantics of timed synchronous effects. 
+As shown in \figref{fig:Sementic}, we define the semantics of \timedEffects. 
 We use 
@@
 \code{[I]} to represent the sequence only contains one time instance.
-
 \code{{\tt{SAT}(\pi)} } indicates the pure \code{\pi} is satisfiable, which is discharged by the constraint solver Z3 \cite{de2008z3}.
-\code{I} is a list of mappings from signals to status.
-For example, the time instance $\{\textbf{S}\}$ indicates that signal \textbf{S} is present regardless of the status of other non-mentioned signals, i.e.,  time instances which at least contain $\textbf{S}$ to be present.
-Any time instance contains contradictions, such as $\{\textbf{S}, \overline{\textbf{S}}\}$, will lead to \code{false}, as a signal {\textbf{S}} can not be both present and absent.
 
@@
 An overview of our automated verification system is given in \figref{fig:Verification_oberview} It consists of a Hoare-style forward verifier and a TRS. 
-The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in timed synchronous effects (cf. \figref{fig:overview_eg1}).
+The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in \timedEffects (cf. \figref{fig:overview_eg1}).
 
@@
 
-In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\lambda_{HH}}, by formalising a set of forward inductive rules.
+In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\timedL}, by formalising a set of forward inductive rules.
 These rules transfer program states and systematically accumulate the effects syntactically. 
@@
 
-%The main difficulty in giving a semantics to \code{\lambda_{HH}} consists in the idea of instantaneous reactions of ESTEREL programs to input signals.
+%The main difficulty in giving a semantics to \code{\timedL} consists in the idea of instantaneous reactions of ESTEREL programs to input signals.
 
@@
 
-The TRS  is an automated entailment checker to prove language inclusions among timed synchronous effects (cf.
+The TRS  is an automated entailment checker to prove language inclusions among \timedEffects (cf.
 \defref{Inclusion} and \tabref{tab:rewriting_tree_send}).
@@
 \begin{definition}[Partial Derivative\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bott}; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}.
-Here we come up with a new notion of partial derivative for timed synchronous effects.
+Here we come up with a new notion of partial derivative for \timedEffects.
 }]\label{Derivative}
@@
 %\vspace{0mm}
-%  \caption{Some Normalization Lemmas for timed synchronous effects.}
+%  \caption{Some Normalization Lemmas for \timedEffects.}
 %  \label{table:normalization}
@@
 \begin{table}[h]
-\caption{Normalization Axioms for Timed Synchronous Effects.}
+\caption{Normalization Axioms for \timedEffects.}
 \label{table:normalization}
@@
  \begin{theorem}[Completeness]\label{Completeness}
- The set of axioms (A1)-(A22) is complete for timed synchronous effects.
+ The set of axioms (A1)-(A22) is complete for \timedEffects.
 
@@
 
-Then for any ground timed synchronous effects \code{\es}, the expression \code{\epsilon || \es} can be reduced to either \code{\epsilon} or \code{\es} by the applications of (A15) and (A16).  
+Then for any ground \timedEffects \code{\es}, the expression \code{\epsilon || \es} can be reduced to either \code{\epsilon} or \code{\es} by the applications of (A15) and (A16).  
 The expression \code{\es^\omega} can be reduced to either \code{\bot} or \code{\es^\omega} by the applications of (A12) to (A14).
@@
 %The core implementation is less than 3500 LOC, roughly, 1{+} LOC for the verifier, and 2{+} LOC for the TRS. We prove the soundness of the TRS. 
-%Next, we show case studies to demonstrate the feasibilities of our timed synchronous effects comparing to timed automata.
+%Next, we show case studies to demonstrate the feasibilities of our \timedEffects comparing to timed automata.
 
@@
 
-As the examples show, our proposed effects logic and the abstract semantics for \code{\lambda_{HH}} not only tightly capture the behaviours of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm.
+As the examples show, our proposed effects logic and the abstract semantics for \code{\timedL} not only tightly capture the behaviours of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm.
 Meanwhile, the inferred temporal traces from a given reactive program enable a compositional timed temporal verification at the source level, which is not yet supported by existing temporal verification techniques.
@@
 
-Moreover, our timed synchronous effects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
+Moreover, our \timedEffects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
 %Antimirov and Mosses' algorithm \cite{antimirov1995rewriting} was designed for deciding the inclusion of regular expressions.   
@@
 %HipHop.js
-We define the syntax and semantics of the novel timed synchronous effects, to capture reactive program behaviours and  temporal properties.
-We demonstrate how to give a rather axiomatic semantics to \code{\lambda_{HH}} by timed-trace processing functions.
+We define the syntax and semantics of the novel \timedEffects, to capture reactive program behaviours and  temporal properties.
+We demonstrate how to give a rather axiomatic semantics to \code{\timedL} by timed-trace processing functions.
 We use this semantic model to enable  a Hoare-style forward verifier,  which computes the program effects constructively.

### 2022-03-28 tv.tex
m

@@
 {{\textbf{\footnotesize #1}}}}}
+\newcommand{\anynotevent}[1]{{\textcolor{darkred}
+{{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
 \newcommand{\seq}{\cdot}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
       \vspace{0mm}
@@
 void addSugar(int n)
-  // requires n>0 /\ Cup 
-  // ensures  t>=n /\ Sugar # t
-  {
-      if n == 0 then event[Sugar] 
+/* requires n>0,  _^*.Cup */
+/* ensures  t>=n, Sugar # t */
+{ if n == 0 then event[Sugar] 
   else {
     timeout (oneSugar(), 1);
-          addSugar (n-1);
-      }
-  }
+    addSugar (n-1);}}
 
 void makeCoffee (int n)
-  // requires n>0 /\ emp 
-  // ensures  5>t>=n/\ t1<3 /\ Cup.(Sugar # t).(Coffee # t1).Done
-  {
-      event[Cup];
+/* requires n>0, emp */
+/* ensures  t<5/\t>=n/\t1<3, 
+ Cup.(Sugar#t).(Coffee#t1).Done */
+{ event[Cup];
   deadline (getSugar(n), 5);
   deadline (event[Coffee], 3);
-      event[Done];
-  }
+  event[Done];}
 
 void main () 
-  // requires true /\ emp 
-  // ensures  t < 8 /\ (_^*.Done) # t
-  {
-      makeCoffee(3);
-  }
+/* requires true, emp */
+/* ensures  t<8, (_^*.Done)#t */
+{ makeCoffee(3);}
+// make coffee with 3 lumps of sugar
+
 \end{lstlisting}  
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
       \vspace{-2mm}
@@
 {
-\begin{figure}[h]
+\begin{figure}[ht]
       \vspace{0mm}
@@
 {
-\begin{table*}[h]
+\begin{table*}[ht]
 \centering
@@
     \vspace{0mm}
-\begin{figure*}[h]
+\begin{figure*}[ht]
 \renewcommand{\arraystretch}{1.1}
@@
     \code{
-          \pure{\pi} : \es  
+          (\pure{\pi}, \es)
    \ | \ \effect_1 \vee \effect_2
@@
     \ | \ \anyevent{A} 
+    \ | \ \anynotevent{A}
+    \ | \ \_  
     %   \ | \ \anyevent{a}
@@
     \ | \ \es_1 {\vee} \es_2
+    \ | \ \es_1 {||} \es_2
       %    \  | \ \es_1 \times \es_2
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \vspace{-1mm}
@@
 
-%\begin{table}[h]
+%\begin{table}[ht]
 %\vspace{0mm}
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 \caption{Normalization Axioms for \timedEffects.}
@@
 %
-%\begin{table}[h]
+%\begin{table}[ht]
 %        \vspace{-2mm}
@@
 {
-\begin{table}[h]
+\begin{table}[ht]
       \vspace{0mm}

### 2022-03-29 code/src/program/15_LED_and_Switch_Array.c
m

@@ -1,0 +1,247 @@
+//https://create.arduino.cc/projecthub/ejshea/led-bar-graph-and-switch-array-8467e0?ref=tag&ref_id=control&offset=19
+//Control LED bar graph function based on input from switch array
+//Last modified April 2019
+
+int LED0 = 0;
+int LED1 = 1;
+int LED2 = 2;
+int LED3 = 3;
+int LED4 = 4;
+int LED5 = 5;
+int LED6 = 6;
+int LED7 = 7;
+int LED8 = 8;
+
+int switch1 = 9;
+int switch2 = 10;
+int switch3 = 11;
+int switch4 = 12;
+int switch5 = 13;
+
+int s1status = 0;
+int s2status = 0;
+int s3status = 0;
+int s4status = 0;
+int s5status = 0;
+
+void setup() {
+  //set pins 0-8 as output
+  pinMode(LED0, OUTPUT);
+  pinMode(LED1, OUTPUT);
+  pinMode(LED2, OUTPUT);
+  pinMode(LED3, OUTPUT);
+  pinMode(LED4, OUTPUT);
+  pinMode(LED5, OUTPUT);
+  pinMode(LED6, OUTPUT);
+  pinMode(LED7, OUTPUT);
+  pinMode(LED8, OUTPUT);
+
+  //set pins 9-14 as input
+  pinMode(switch1, INPUT);
+  pinMode(switch2, INPUT);
+  pinMode(switch3, INPUT);
+  pinMode(switch4, INPUT);
+  pinMode(switch5, INPUT);
+
+}
+
+void loop() {
+  //check inputs from switches
+  s1status = digitalRead(switch1);
+  s2status = digitalRead(switch2);
+  s3status = digitalRead(switch3);
+  s4status = digitalRead(switch4);
+  s5status = digitalRead(switch5);
+  
+  if(s1status == 1){
+    //perform LED function 1 -- forward light
+    
+    digitalWrite(LED0, HIGH);
+    delay(200);
+    digitalWrite(LED0, LOW);
+    digitalWrite(LED1, HIGH);
+    delay(200);
+    digitalWrite(LED1, LOW);
+    digitalWrite(LED2, HIGH);
+    delay(200);
+    digitalWrite(LED2, LOW);
+    digitalWrite(LED3, HIGH);
+    delay(200);
+    digitalWrite(LED3, LOW);
+    digitalWrite(LED4, HIGH);
+    delay(200);
[…]

### 2022-03-29 code/src/program/16_Washing_Machine.c

@@ -1,0 +1,332 @@
+#include "arduino.c"
+/* 
+https://github.com/joshua-scott/arduino-washing-machine/blob/master/washingmachine.c
+ARDUINO WASHING MACHINE 
+TASK REQUIREMENTS:
+
+Implement a virtual washing machine with Arduino, relay, switches, led, seven segment display and motors.
+- Motor1 simulates the drum of the washing machine. It should rotate whenever the machine is washing, rinsing or centrifuging. Otherwise it should be stopped.
+- Motor2 simulates the water pump of the washing machine. It should rotate whenever water is pumped out of the machine. Otherwise it should be stopped.
+- Switch1 is turning the machine ON/OFF.
+- Switch2 simulates the sensor which is ‘1’ whenever there is enough water in the machine.
+- Switch3 simulates the sensor which is ‘1’ whenever all the water is pumped out of the machine.
+- Relay is ON when the machine takes water.
+
+The routine of the washing machine goes like this:
+1. Washing machine takes water for 3s
+2. Washing machine is washing for 9s (The speed of the motor should be moderate)
+3. Dirty water is pumped out of the machine for 3s
+4. Washing machine takes water for 3s
+5. Washing machine is rinsing for 5s
+6. Rinsing water is pumped out of the machine for 3s
+7. Washing machine is centrifuging for 5s (The speed of the motor should be high)
+8. Led is blinking when the washing program is finished.
+9. Washing machine can be turned OFF
+
+*/
+
+/* ----- OUTPUT MACROS ----- */
+
+
+
+
+const int all[7] = {A, B, C, D, E, F, G};
+
+/* ----- END OUTPUT MACROS ----- */
+
+/* ----- SETUP ----- */
+
+void setup() 
+    /*
+    require TRUE/\emp
+    ensure TRUE/\Ready
+    */
+{
+  // Display outputs
+  pinMode(A, OUTPUT);
+  pinMode(B, OUTPUT);
+  pinMode(C, OUTPUT);
[…]

### 2022-03-29 code/src/program/arduino.c

@@ -1,0 +1,76 @@
+#include "primitives.c"
+#include <time.h>
+
+#define INPUT 0
+#define OUTPUT 1
+#define HIGH 1
+#define LOW 1
+#define A0 0
+
+#define A 2
+#define B 8
+#define C 6
+#define D 5
+#define E 4
+#define F 3
+#define G 7
+#define RELAY 10
+#define YELLOW 12
+#define PUMP 9
+#define DRUM 11
+#define SWITCH2 0
+#define SWITCH3 1
+
+void pinMode (int a, int b){
+    return ;
+}
+
+void digitalWrite (int a, int b){
+    return ;
+}
+
+int  digitalRead (int a){
+    return 0;
+}
+
+void delay (int n) 
+    /*
+    require (n>=0)/\/\emp
+    ensure (n>=0)/\(Delay^n)
+    */
+{
+    if (n == 0) { 
+        return;
+    }
+    else {
+        event ("Delay"); 
+        delay (n - 1);
+    }
+} 
+
+void analogWrite(int a, int b)
+    /*
+    require (a>=0)/\/\emp
+    ensure (b=1/\HIGH) \/ (b=0/\LOW)
+    */
+{
+    return ;
+}
+
+
+int  analogRead(int a){
+    int lower = 210, upper = 220; 
+  
+    // Use current time as  
+    // seed for random generator 
+    /*srand(time(0)); 
+  
+    return (rand() % 
+           (upper - lower + 1)) + lower;
+           */
+    return 0;
+}
+
+int millis() {
+    return 0;
+}

### 2022-03-29 code/src/program/assertion_invalid.c

@@ -1,0 +1,18 @@
+#include "primitives.c"
+
+void send (int n) 
+    /*
+    require TRUE/\Ready.(_^*)
+    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
+    */
+{
+
+    if (n == 0) { 
+        event ("Done");
+    }
+    else {
+        assert (n > 0/\Ready.(_^*));
+        event ("Send"); 
+        send (n - 1);
+    }
+} 

### 2022-03-29 code/src/program/assertion_valid.c

@@ -1,0 +1,18 @@
+#include "primitives.c"
+
+void send (int n) 
+    /*
+    require TRUE/\Ready.(_^*)
+    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
+    */
+{
+
+    if (n == 0) { 
+        event ("Done");
+    }
+    else {
+        assert (TRUE/\Ready.(_^*));
+        event ("Send"); 
+        send (n - 1);
+    }
+} 

### 2022-03-29 code/src/program/primitives.c

@@ -1,0 +1,7 @@
+#include <stdio.h>
+
+void event (char * ev)
+
+{
+    printf ("%s\n",ev);
+}

### 2022-03-29 code/src/program/send1.c

@@ -1,0 +1,37 @@
+#include "primitives.c"
+
+void send (int n) 
+    /*
+    require TRUE/\Ready.(_^*)
+    ensure (n>=0)/\(Send#n).Done\/n<0/\(Send^*)
+    */
+{
+
+    if (n == 0) { 
+        event ("Done");
+    }
+    else {
+        event ("Send"); 
+        send (n - 1);
+    }
+} 
+
+void server (int n)
+    /*
+    require TRUE/\emp
+    ensure (n>=0)/\((Ready.(Send#n).Done)^*)
+    */
+{
+    event("Ready");
+    send(n);
+	server(n);
+}
+
+int main ()
+/*
+    require TRUE /\emp
+    ensure TRUE/\((Ready.(Send#n).Done)^*)
+    */
+{
+    server (5);
+}

### 2022-03-29 code/src/program/send2.c

@@ -1,0 +1,37 @@
+#include "primitives.c"
+
+void send (int n) 
+    /*
+    require TRUE/\Ready.(_^*)
+    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
+    */
+{
+
+    if (n == 0) { 
+        event ("Done");
+    }
+    else {
+        event ("Send"); 
+        send (n - 1);
+    }
+} 
+
+void server (int n)
+    /*
+    require TRUE/\emp
+    ensure (n>=0)/\((Ready.(Send^n).Done)^w) \/ n <0 /\ Ready.(Send^w)
+    */
+{
+    event("Ready");
+    send(n);
+	server(n);
+}
+
+int main ()
+/*
+    require TRUE /\emp
+    ensure TRUE/\((Ready.(Send^n).Done)^w)
+    */
+{
+    server (5);
+}

### 2022-03-29 code/src/program/send_valid.c

@@ -1,0 +1,37 @@
+#include "primitives.c"
+
+void send (int n) 
+    /*
+    require TRUE/\Ready.(_^*)
+    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
+    */
+{
+
+    if (n == 0) { 
+        event ("Done");
+    }
+    else {
+        event ("Send"); 
+        send (n - 1);
+    }
+} 
+
+void server (int n)
+    /*
+    require (n>=0)/\emp
+    ensure (n>=0)/\((Ready.(Send^n).Done)^w)
+    */
+{
+    event("Ready");
+    send(n);
+	server(n);
+}
+
+int main ()
+/*
+    require TRUE /\emp
+    ensure TRUE/\((Ready.(Send^n).Done)^w)
+    */
+{
+    server (1);
+}

### 2022-03-29 code/src/program/traffic_light1.c

@@ -1,0 +1,27 @@
+#include "traffic_primitives.c"
+ 
+void controller()
+    /*
+    require TRUE/\Ready.(_^*) 
+    ensure TRUE /\ (((_^*).Green)^w)
+    */
+{
+    turnGreen ();    
+    delay(4);
+    turnYellow ();
+    delay(2);
+    turnRed();
+    delay(6);
+    controller();
+}
+
+int main()
+    /*
+    require TRUE /\emp
+    ensure TRUE /\ Ready.(((_^*).Green)^w)
+    */
+{
+    event ("Ready");
+    controller();
+}
+

### 2022-03-29 code/src/program/traffic_light2.c

@@ -1,0 +1,27 @@
+#include "primitives.c"
+#include "traffic_primitives.c"
+ 
+void controller()
+    /*
+    require TRUE/\Ready.(_^*) 
+    ensure TRUE /\ ((Green._._)^w)  
+    */
+{
+    turnGreen ();    
+   
+    turnYellow ();
+    
+    turnRed();
+    
+    controller();
+}
+
+int main()
+    /*
+    require TRUE /\emp
+    ensure TRUE /\ Ready.((Green._._)^w)  
+    */
+{
+    event ("Ready");
+    controller();
+}

### 2022-03-29 code/src/program/traffic_light3.c

@@ -1,0 +1,27 @@
+#include "primitives.c"
+#include "traffic_primitives.c"
+
+
+void controller(int n, int m)
+    /*
+    require (n>0 /\ m > 0) /\ Ready.(_^*)
+    ensure (n>0 /\ m > 0)  /\ (((Red^n).(Yellow^m).(Green^n))^w) 
+    */
+{
+    red(n);
+    yellow (m);
+    green (n);
+    controller(n, m);
+}
+  
+   
+int main()
+    /*
+    require TRUE /\emp
+    ensure TRUE  /\ Ready.(((Red^5).(Yellow).(Green^5))^w) 
+    */
+    
+{
+    event ("Ready");
+    controller(5, 1);
+}

### 2022-03-29 code/src/program/traffic_light3_1.c

@@ -1,0 +1,27 @@
+#include "primitives.c"
+#include "traffic_primitives.c"
+
+
+void controller(int n, int m)
+    /*
+    require (n>0 /\ m > 0) /\ Ready.(_^*)
+    ensure (n>0 /\ m > 0)  /\ (((Red^n).(Yellow^n).(Green^n))^w) 
+    */
+{
+    red(n);
+    yellow (n);
+    green (n);
+    controller(n, n);
+}
+  
+   
+int main()
+    /*
+    require TRUE /\emp
+    ensure TRUE  /\ Ready.(((Red^5).(Yellow^5).(Green^5))^w) 
+    */
+    
+{
+    event ("Ready");
+    controller(5, 1);
+}

### 2022-03-29 code/src/program/traffic_light4.c

@@ -1,0 +1,24 @@
+#include "primitives.c"
+#include "traffic_primitives.c"
+
+void controller()
+    /*
+    require TRUE /\ Ready._*
+    ensure (TRUE/\ X \in {Yellow._*, Red._*, Green._*}) /\ (X.X.X)^w
+    */
+{
+    turnYellow ();
+    delay (2);
+    turnRed();
+    delay (2);
+    turnGreen (); 
+    delay (2);   
+    controller();
+}
+
+int main()
+{
+    event ("Ready");
+    controller();
+}
+

### 2022-03-29 code/src/program/traffic_primitives.c

@@ -1,0 +1,96 @@
+#include "primitives.c"
+
+void delay (int n) 
+    /*
+    require (n>=0)/\emp
+    ensure (n>=0)/\(Delay^n)
+    */
+{
+    if (n == 0) { 
+        return;
+    }
+    else {
+        event ("Delay"); 
+        delay (n - 1);
+    }
+} 
+
+void turnRed ()
+    /*
+    require TRUE/\emp
+    ensure TRUE /\ Red
+    */
+{
+    event ("Red"); 
+    printf("X Ave. - RED; Y Blvd. - RED\n");
+}
+
+void turnGreen ()
+    /*
+    require TRUE/\emp
+    ensure TRUE /\ Green
+    */
+{
+    event ("Green"); 
+}
+
+
+void turnYellow ()
+    /*
+    require TRUE/\emp
+    ensure TRUE /\ Yellow
+    */
+{
+    event ("Yellow"); 
+    printf("X Ave. - RED; Y Blvd. - YELLOW\n");
+}
+
+
+void red (int n) 
+    /*
+    require (n>=0)/\emp
+    ensure TRUE/\(Red^n)
+    */
+{
+    if (n == 0) { 
+        turnRed();
+        return;
+    }
+    else {
+        turnRed();
+        red (n - 1);
+    }
+} 
+
+void green (int n) 
+    /*
+    require (n>=0)/\emp
+    ensure TRUE/\(Green^n)
+    */
+{
+    if (n == 0) { 
+        turnGreen ();    
+        return;
+    }
+    else {
+        turnGreen ();    
+        green (n - 1);
+    }
+} 
+
+void yellow (int n) 
+    /*
+    require (n>=0)/\emp
+    ensure TRUE/\(Yellow^n)
+    */
+{
+    if (n == 0) { 
+        turnYellow ();
+        return;
+    }
+    else {
+        turnYellow ();
+        yellow (n - 1);
+    }
+} 
+

### 2022-03-29 paper/tv.tex
m

--- 2022-03-28 tv.tex
@@
 void addSugar(int n)
-/* requires n>0,  _^*.Cup */
-/* ensures  t>=n, Sugar # t */
+/* requires n>0,  _^*.Cup 
+   ensures  t>=n, Sugar # t */
 { if n == 0 then event[Sugar] 
@@
 void makeCoffee (int n)
-/* requires n>0, emp */
-/* ensures  t<5/\t>=n/\t1<3, 
+/* requires n>0, emp 
+ ensures  t<5/\t>=n/\t1<3, 
  Cup.(Sugar#t).(Coffee#t1).Done */
 { event[Cup];
-  deadline (getSugar(n), 5);
+  deadline (addSugar(n), 5);
   deadline (event[Coffee], 3);
@@
 void main () 
-/* requires true, emp */
-/* ensures  t<8, (_^*.Done)#t */
+/* requires true, emp 
+ ensures  t<8, (_^*.Done)#t */
 { makeCoffee(3);}

### 2022-03-29 code/src/program/11_Control_a_Solenoid.c
m

@@ -1,88 +1,0 @@
-//https://create.arduino.cc/projecthub/robotgeek-projects-team/control-a-solenoid-with-arduino-710bdc?ref=tag&ref_id=control&offset=13
-/*
-
-Controlling a Solenoid with Arduino
-
-This demo shows how to control a solenoid using pushbuttons and a relay with
-your Arduino compatable controller.
- 
- 
- The circuit:
- * RobotGeek Pushbutton - Digital Pin 2
- * RobotGeek Pushbutton - Digital Pin 4
- * RobotGeek Pushbutton - Digital Pin 7
- * RobotGeek Relay - Digital Pin 8
- * RobotGeek Relay - Digital Pin 12
- * RobotGeek Relay - Digital Pin 13
- */
-
-// constants won't change. They're used here to set pin numbers:
-const int button1Pin = 2;     // the number of the pushbutton1 pin
-const int button2Pin = 4;     // the number of the pushbutton2 pin
-const int button3Pin = 7;     // the number of the pushbutton3 pin
-const int relay1Pin =  8;      // the number of the Relay1 pin
-const int relay2Pin =  12;      // the number of the Relay2 pin
-const int relay3Pin =  13;      // the number of the Relay3 pin
-
-// variables will change:
-int button1State = 0;         // variable for reading the pushbutton status
-int button2State = 0;         // variable for reading the pushbutton status
-int button3State = 0;         // variable for reading the pushbutton status
-
-void setup() { 
-  
-  // initialize the pushbutton pin as an input:
-  pinMode(button1Pin, INPUT);     
-  pinMode(button2Pin, INPUT);     
-  pinMode(button3Pin, INPUT);    
-  // initialize the relay pin as an output:
-  pinMode(relay1Pin, OUTPUT);    
-  pinMode(relay2Pin, OUTPUT);    
-  pinMode(relay3Pin, OUTPUT);    
-   
-}
-
-void loop(){
-  
-  // read the state of the pushbutton values:
-  button1State = digitalRead(button1Pin);
-  button2State = digitalRead(button2Pin);
-  button3State = digitalRead(button3Pin);
-
-  // check if the pushbutton1 is pressed.
-  // if it is we turn on the small relay/solenoid
-  if (button1State == HIGH) {     
-    // turn relay on:    
-    digitalWrite(relay1Pin, HIGH);  
-  } 
-  // When we let go of the button, turn off the relay
[…]

### 2022-03-29 code/src/program/12_IoT_Stepper_Motor.c

@@ -1,122 +1,0 @@
-//https://create.arduino.cc/projecthub/vicentezavala/iot-stepper-motor-2db08f?ref=tag&ref_id=control&offset=14
-/*
-*	Author		: Zavala Ortiz Vicente Arturo.
-*	language	: .cpp
-*	Created		: 3/11/2015 11:56:57 AM
-*	Name		: ATmega32u4_WiFiStepperKnob.cpp
-*	Update		: 1/9/2017 02:29:15 PM
-*	Description : wifi Socket Client
-*/
-
-#include <util/delay.h>
-#include <stdlib.h>
-
-#include "CC3000.h"
-#include "CC3000_Client.h"
-#include "AFMotor.h"
-#include "common.h"
-
-/*****		wifi Global Variables		*****/
-// Connection info data lengths
-#define MAX_MSG_LEN							100
-#define DHT11_PIN							0
-// Constants
-
-char ap_ssid[]				= "SSID of network";	    // SSID of network
-char ap_password[]		= "Password of network";	// Password of network
-
-unsigned int ap_security	= WLAN_SEC_WPA2;	  // Security of network
-unsigned long timeout		  = 3000;            	// Milliseconds
-
-// Global Variables
-CC3000 wifi						= CC3000();
-CC3000_Client client  = CC3000_Client(wifi);
-
-char in_message[MAX_MSG_LEN]	= {0};
-
-/*****		Other Global Variables		*****/
-static char page[20], data[20];
-signed int option, value, out, stepper2_actual_value = 0;
-
-void setup()
-{
-	/* add setup code here */
- 	ConnectionInfo connection_info;
- 
- 	// Initialize CC3000 (configure SPI communications) 	
- 	Serial.begin(115200);
- 	 
- 	// Initialize CC3000 (configure SPI communications)
- 	if(!wifi.init(9)) {
- 			Serial.println("Initialize CC3000 FAIL!");
- 		return;
- 	}
-
-	else {
-		Serial.println"Initialize CC3000 OK");
-	}
-
-	if(!wifi.connect(ap_ssid, ap_security, ap_password, timeout)) {	
-		Serial.println("Error: Could not connect to AP!");
-	}
-
-	else
-		return;
-	
-	
-	_delay_ms(5000);
-	
-	// Gather connection details and print IP address
-	if(!wifi.getConnectionInfo(connection_info) )
-	{
[…]

### 2022-03-29 code/src/program/13_Aquariumatic_Management.c

@@ -1,95 +1,0 @@
-  
-  //https://create.arduino.cc/projecthub/basem/modified-aquariumatic-management-system-ams-iot-app-02ddfe?ref=tag&ref_id=control&offset=15
-  /*************
-  
-    The Islamic University of Gaza Faculty of Engineering
-    Electrical Engineering Department 
-    Aquariumatic management system (AMS - IoT App)
-
-    A graduation project is submitted to the Electrical Engineering Department in partial fulfillment of the requirements for the degree of B.Sc. in Electrical Engineering!
-    By : Basem M. Khalaf     basem.khalaf.1994@ieee.org
-         Hazem E. Abu Taha
-    Supervisor : Dr. Jawdat Abu Taha
-
-    Gaza, Palestine 
-    15 May 2017
-    You can find more about this project , just click on the Link : 
-    or you can contact with Basem by this email : basem.khalaf.1994@ieee.org
-    
-    Note :
-    Typical Ethernet Module wiring would be:
- *  VCC -- 5V
- *  GND -- GND
- *  CS  -- D10
- *  SI  -- D11
- *  SCK -- D13
- *  SO  -- D12
- *  INT -- D2
- 
- **************/
- 
-#define BLYNK_PRINT Serial           // Comment this out to disable prints and save space
-#include <SPI.h>
-#include <UIPEthernet.h>
-#include <BlynkSimpleUIPEthernet.h>
-#include <SimpleTimer.h>
-
-                                     // You should get Auth Token in the Blynk App.
-                                     // Go to the Project Settings (nut icon).
-char auth[] = "ef83d5daf43e406987fca44a0a90015d";
-#define echoPin 8                    // Echo Pin
-#define trigPin 9                    // Trigger Pin
-long duration, distance;             // Duration used to calculate distance
-float temp;
-int tempPin = 1;                     //analog pin 1
-SimpleTimer  timer;                  // http://playground.arduino.cc/Code/SimpleTimer , simply how to use timer in your code to send data over time intervals !
-
-    
-void setup()
-{
-  Serial.begin(9600);
-  Blynk.begin(auth);
-  pinMode(trigPin, OUTPUT);
-  pinMode(echoPin, INPUT);
-  timer.setInterval(1500, sendUptime);                    //i removed L from 1000L! more time to send less flood on to Blynk server !
-  timer.setInterval(1500, sendUpdestance);                // USonic sensor data sending!
-  
-                                                          //You can also specify server.
[…]

### 2022-03-29 code/src/program/14_Automatic_Train_Control.c

@@ -1,96 +1,0 @@
-//https://create.arduino.cc/projecthub/Steve_Massikker/automatic-train-control-a17c6f?ref=tag&ref_id=control&offset=17
-// L298 
-#define L298_ENA 5
-#define L298_IN1 6
-#define L298_IN2 7
-
-
-// SCRIPTS VARIABLES
-int counterScheduler;
-unsigned long timerScheduler = 0;
-unsigned long timerLocal = 0;
-byte speedAuto = 0;
-
-
-void setup() {
-
-// Initializing pins
-  pinMode(L298_ENA, OUTPUT);
-  pinMode(L298_IN1, OUTPUT);
-  pinMode(L298_IN2, OUTPUT);
-
-// Set default direction to FORWARD
-  digitalWrite(L298_IN1, HIGH);
-  digitalWrite(L298_IN2, LOW); 
-
-}
-
-void loop() {
-
-  	// Start Scheduler
-    if (millis() > (timerScheduler + 1000)) {  // Tick every 1 sec
-      counterScheduler++; 
-      timerScheduler = millis();
-    }  
-    
-    // ------------- SCRIPT SWING
-    int brakingDelta = 5;
-    int accelerateDelta = 6;
-
-    // 1  | 0 > Time < 5 sec
-    if (counterScheduler <= 5) {  
-        // Start train
-        if (millis() > (timerLocal + 100)) {
-          if (speedAuto < 240) speedAuto = speedAuto + accelerateDelta;
-          else speedAuto = 255;
-          analogWrite(L298_ENA, speedAuto); 
-          timerLocal = millis();
-        }   
-    }       
-    
-    // 2  | 10 sec > Time < 15 sec
-    if ((counterScheduler >= 10) && (counterScheduler <= 15)) {  // Stop train after 10 sec
-        // Stop train
-        if (millis() > (timerLocal + 100)) {
-          if (speedAuto > 30) speedAuto = speedAuto - brakingDelta;
-          else speedAuto = 0;
-          analogWrite(L298_ENA, speedAuto); 
-          timerLocal = millis();
-        } 
-    }  
-    
-    // 3  | Change direction
-    if (counterScheduler == 16) {  
-        digitalWrite(L298_IN1, LOW);
-        digitalWrite(L298_IN2, HIGH); 
-    }   
-    
-    // 4  | 20 sec > Time < 30 sec
-    if ((counterScheduler >= 20) && (counterScheduler <= 30)) {  
-        // Start train
[…]

### 2022-03-29 code/src/program/15_LED_and_Switch_Array.c

@@ -1,247 +1,0 @@
-//https://create.arduino.cc/projecthub/ejshea/led-bar-graph-and-switch-array-8467e0?ref=tag&ref_id=control&offset=19
-//Control LED bar graph function based on input from switch array
-//Last modified April 2019
-
-int LED0 = 0;
-int LED1 = 1;
-int LED2 = 2;
-int LED3 = 3;
-int LED4 = 4;
-int LED5 = 5;
-int LED6 = 6;
-int LED7 = 7;
-int LED8 = 8;
-
-int switch1 = 9;
-int switch2 = 10;
-int switch3 = 11;
-int switch4 = 12;
-int switch5 = 13;
-
-int s1status = 0;
-int s2status = 0;
-int s3status = 0;
-int s4status = 0;
-int s5status = 0;
-
-void setup() {
-  //set pins 0-8 as output
-  pinMode(LED0, OUTPUT);
-  pinMode(LED1, OUTPUT);
-  pinMode(LED2, OUTPUT);
-  pinMode(LED3, OUTPUT);
-  pinMode(LED4, OUTPUT);
-  pinMode(LED5, OUTPUT);
-  pinMode(LED6, OUTPUT);
-  pinMode(LED7, OUTPUT);
-  pinMode(LED8, OUTPUT);
-
-  //set pins 9-14 as input
-  pinMode(switch1, INPUT);
-  pinMode(switch2, INPUT);
-  pinMode(switch3, INPUT);
-  pinMode(switch4, INPUT);
-  pinMode(switch5, INPUT);
-
-}
-
-void loop() {
-  //check inputs from switches
-  s1status = digitalRead(switch1);
-  s2status = digitalRead(switch2);
-  s3status = digitalRead(switch3);
-  s4status = digitalRead(switch4);
-  s5status = digitalRead(switch5);
-  
-  if(s1status == 1){
-    //perform LED function 1 -- forward light
-    
-    digitalWrite(LED0, HIGH);
-    delay(200);
-    digitalWrite(LED0, LOW);
-    digitalWrite(LED1, HIGH);
-    delay(200);
-    digitalWrite(LED1, LOW);
-    digitalWrite(LED2, HIGH);
-    delay(200);
-    digitalWrite(LED2, LOW);
-    digitalWrite(LED3, HIGH);
-    delay(200);
-    digitalWrite(LED3, LOW);
-    digitalWrite(LED4, HIGH);
-    delay(200);
[…]

### 2022-03-29 code/src/program/16_Washing_Machine.c

@@ -1,332 +1,0 @@
-#include "arduino.c"
-/* 
-https://github.com/joshua-scott/arduino-washing-machine/blob/master/washingmachine.c
-ARDUINO WASHING MACHINE 
-TASK REQUIREMENTS:
-
-Implement a virtual washing machine with Arduino, relay, switches, led, seven segment display and motors.
-- Motor1 simulates the drum of the washing machine. It should rotate whenever the machine is washing, rinsing or centrifuging. Otherwise it should be stopped.
-- Motor2 simulates the water pump of the washing machine. It should rotate whenever water is pumped out of the machine. Otherwise it should be stopped.
-- Switch1 is turning the machine ON/OFF.
-- Switch2 simulates the sensor which is ‘1’ whenever there is enough water in the machine.
-- Switch3 simulates the sensor which is ‘1’ whenever all the water is pumped out of the machine.
-- Relay is ON when the machine takes water.
-
-The routine of the washing machine goes like this:
-1. Washing machine takes water for 3s
-2. Washing machine is washing for 9s (The speed of the motor should be moderate)
-3. Dirty water is pumped out of the machine for 3s
-4. Washing machine takes water for 3s
-5. Washing machine is rinsing for 5s
-6. Rinsing water is pumped out of the machine for 3s
-7. Washing machine is centrifuging for 5s (The speed of the motor should be high)
-8. Led is blinking when the washing program is finished.
-9. Washing machine can be turned OFF
-
-*/
-
-/* ----- OUTPUT MACROS ----- */
-
-
-
-
-const int all[7] = {A, B, C, D, E, F, G};
-
-/* ----- END OUTPUT MACROS ----- */
-
-/* ----- SETUP ----- */
-
-void setup() 
-    /*
-    require TRUE/\emp
-    ensure TRUE/\Ready
-    */
-{
-  // Display outputs
-  pinMode(A, OUTPUT);
-  pinMode(B, OUTPUT);
-  pinMode(C, OUTPUT);
[…]

### 2022-03-29 code/src/program/2_cradle_with_Joystick.c

@@ -1,50 +1,0 @@
-//This code is to use with dual axis fpv camera cradle that uses two servos, adding a joystick module
-//We control the position of the cradle by moving the analog stick, the cradle move to the direction where the stick is pointing
-//until the limits and stay there
-//Refer to surtrtech.com for more information
-//https://create.arduino.cc/projecthub/SurtrTech/control-dual-axis-fpv-camera-cradle-with-joystick-module-6ee514?ref=tag&ref_id=control&offset=1
-
-#include <Servo.h> //Servos library and declaration
-
-Servo myservo1;
-Servo myservo2;
-
-int a,b,X,Y; //Variables needed later
-int YAxis = 1; //Declaring where the X axis and Y axis of the joystick pins are wired
-int XAxis = 0; //Of course analog inputs
-
-void setup() {
- Serial.begin(9600); //Setting the Serial monitor baude rate and launching
- pinMode(XAxis, INPUT); //Declaring the pin modes and servo pins
- myservo1.attach(8);
- pinMode(YAxis, INPUT); 
- myservo2.attach(9);
-}
-
-void loop() {
- 
- a=myservo1.read(); //Reading the previous servos positions is an important step so we can know where they should position next
- b=myservo2.read();
- X=analogRead(XAxis);//Reading the joystick values
- Y=analogRead(YAxis);
- 
- if(X>550){ //Here we didn't do any calibration so the joystick has three positions (Left|Resting|Right)
- a=a-1; //it depends on the value we read we can know in which direction the stick is pointing and I left the resting position big actually it's just 1 value
- myservo1.write(a); //we inject the new value
- delay(50); //You can make the delay big or short or act on a=a-x to make big steps or short steps
- }
- if(X<450){
- a=a+1; //Here we did the opposit operation to move to the opposit direction
- myservo1.write(a);
- delay(50);
- }
- if(Y>600){ //Here we didn't do any calibration so the joystick has three positions (Up|Resting|Down) ditto
- b=b+1;
- myservo2.write(b);
- delay(50);
- }
- if(Y<450){
- b=b-1;
- myservo2.write(b);
- delay(50);
- }

### 2022-03-29 code/src/program/arduino.c

@@ -1,76 +1,0 @@
-#include "primitives.c"
-#include <time.h>
-
-#define INPUT 0
-#define OUTPUT 1
-#define HIGH 1
-#define LOW 1
-#define A0 0
-
-#define A 2
-#define B 8
-#define C 6
-#define D 5
-#define E 4
-#define F 3
-#define G 7
-#define RELAY 10
-#define YELLOW 12
-#define PUMP 9
-#define DRUM 11
-#define SWITCH2 0
-#define SWITCH3 1
-
-void pinMode (int a, int b){
-    return ;
-}
-
-void digitalWrite (int a, int b){
-    return ;
-}
-
-int  digitalRead (int a){
-    return 0;
-}
-
-void delay (int n) 
-    /*
-    require (n>=0)/\/\emp
-    ensure (n>=0)/\(Delay^n)
-    */
-{
-    if (n == 0) { 
-        return;
-    }
-    else {
-        event ("Delay"); 
-        delay (n - 1);
-    }
-} 
-
-void analogWrite(int a, int b)
-    /*
-    require (a>=0)/\/\emp
-    ensure (b=1/\HIGH) \/ (b=0/\LOW)
-    */
-{
-    return ;
-}
-
-
-int  analogRead(int a){
-    int lower = 210, upper = 220; 
-  
-    // Use current time as  
-    // seed for random generator 
-    /*srand(time(0)); 
-  
-    return (rand() % 
-           (upper - lower + 1)) + lower;
-           */
-    return 0;
-}
-
-int millis() {
-    return 0;
-}

### 2022-03-29 code/src/program/assertion_invalid.c

@@ -1,18 +1,0 @@
-#include "primitives.c"
-
-void send (int n) 
-    /*
-    require TRUE/\Ready.(_^*)
-    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
-    */
-{
-
-    if (n == 0) { 
-        event ("Done");
-    }
-    else {
-        assert (n > 0/\Ready.(_^*));
-        event ("Send"); 
-        send (n - 1);
-    }
-} 

### 2022-03-29 code/src/program/assertion_valid.c

@@ -1,18 +1,0 @@
-#include "primitives.c"
-
-void send (int n) 
-    /*
-    require TRUE/\Ready.(_^*)
-    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
-    */
-{
-
-    if (n == 0) { 
-        event ("Done");
-    }
-    else {
-        assert (TRUE/\Ready.(_^*));
-        event ("Send"); 
-        send (n - 1);
-    }
-} 

### 2022-03-29 code/src/program/linear_Actuator.c

@@ -1,83 +1,0 @@
-#include "arduino.c"
-/*
-Manual Linear Actuator Control using an Arduino and two pushbuttons
-This demo shows how to do basic manual control of a large linear
-actuator using an Arduino and two buttons. The first button extends
-the actuator and the second retracts the actuator.
- The circuit:
- * RobotGeek Pushbutton - Digital Pin 2
- * RobotGeek Pushbutton - Digital Pin 4
- * RobotGeek Relay - Digital Pin 7 
- * RobotGeek Relay - Digital Pin 8 
-Products Used in this demo:
- - http://www.robotgeek.com/linear-actuators
- - http://www.robotgeek.com/robotgeek-geekduino-sensor-kit
- - http://www.robotgeek.com/robotGeek-pushbutton
- - http://www.robotgeek.com/robotgeek-relay
- */
-// constants won't change. They're used here to set pin numbers:
-const int button1Pin = 2;     // the number of the pushbutton1 pin
-const int button2Pin = 4;     // the number of the pushbutton2 pin
-const int relay1Pin =  7;      // the number of the Realy1 pin
-const int relay2Pin =  8;      // the number of the Relay2 pin
-// variables will change:
-int button1State = 0;         // variable for reading the pushbutton status
-int button2State = 0;         // variable for reading the pushbutton status
-const int sensorPin = 0;    // select the input pin for the potentiometer
-int sensorValue = 0;  // variable to store the value coming from the sensor
-void setup() { 
-  
-  
-  //start serial connection
-  //Serial.begin(9600);  
-  
-  // initialize the pushbutton pin as an input:
-  pinMode(button1Pin, INPUT);     
-  pinMode(button2Pin, INPUT);    
-  // initialize the relay pin as an output:
-  pinMode(relay1Pin, OUTPUT);    
-  pinMode(relay2Pin, OUTPUT);    
-}
-
-void control(){
-  
-  
-  // read the value from the sensor:
-  sensorValue = analogRead(sensorPin); 
-  //print out the value of the pushbutton
-  //Serial.println(sensorValue);    
-  
-  // read the state of the pushbutton values:
-  button1State = digitalRead(button1Pin);
-  button2State = digitalRead(button2Pin);
-  // check if the pushbutton1 is pressed.
-  // if it is, the buttonState is HIGH:
-  // we also ensure tha the other button is not pushed to avoid conflict
[…]

### 2022-03-29 code/src/program/mutual.c

@@ -1,52 +1,0 @@
-#include "primitives.c"
-
-int is_odd (int n);
-
-int is_even(int n)
-    /*
-    require n>=0 /\ emp
-    ensure TRUE /\ (ODD.EVEN)^*._*
-    */
-    /*
-    require n>=0 /\ emp
-    ensure TRUE /\ (ODD.EVEN)^(n/2).ODD?
-    */
-{
-    if (n == 0) {
-        return 1;
-    }
-    else {
-        event ("ODD");
-        return is_odd(n-1);
-    }
-}
-    
-
-int is_odd(int n)
-    /*
-    require n>=0 /\ emp
-    ensure TRUE /\ (EVEN.ODD)^*._*
-    */
-
-    /*
-    require n>=0 /\ emp
-    ensure TRUE /\ (EVEN.ODD)^(n/2).EVEN?
-    */
-{
-    if (n == 0) {
-        return 0;
-    }
-    else{
-        event ("EVEN");
-        return is_even(n-1);
-    }      
-}
-
-int main () {
-    is_odd (4);
-}
-
-
-//TRUE /\ E.((O.E)^*).(_^*) |- TRUE /\ ((E.O)^*).(_^*)
-//
-    

### 2022-03-29 code/src/program/send1.c

@@ -1,37 +1,0 @@
-#include "primitives.c"
-
-void send (int n) 
-    /*
-    require TRUE/\Ready.(_^*)
-    ensure (n>=0)/\(Send#n).Done\/n<0/\(Send^*)
-    */
-{
-
-    if (n == 0) { 
-        event ("Done");
-    }
-    else {
-        event ("Send"); 
-        send (n - 1);
-    }
-} 
-
-void server (int n)
-    /*
-    require TRUE/\emp
-    ensure (n>=0)/\((Ready.(Send#n).Done)^*)
-    */
-{
-    event("Ready");
-    send(n);
-	server(n);
-}
-
-int main ()
-/*
-    require TRUE /\emp
-    ensure TRUE/\((Ready.(Send#n).Done)^*)
-    */
-{
-    server (5);
-}

### 2022-03-29 code/src/program/send2.c

@@ -1,37 +1,0 @@
-#include "primitives.c"
-
-void send (int n) 
-    /*
-    require TRUE/\Ready.(_^*)
-    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
-    */
-{
-
-    if (n == 0) { 
-        event ("Done");
-    }
-    else {
-        event ("Send"); 
-        send (n - 1);
-    }
-} 
-
-void server (int n)
-    /*
-    require TRUE/\emp
-    ensure (n>=0)/\((Ready.(Send^n).Done)^w) \/ n <0 /\ Ready.(Send^w)
-    */
-{
-    event("Ready");
-    send(n);
-	server(n);
-}
-
-int main ()
-/*
-    require TRUE /\emp
-    ensure TRUE/\((Ready.(Send^n).Done)^w)
-    */
-{
-    server (5);
-}

### 2022-03-29 code/src/program/send_invalid.c

@@ -1,38 +1,0 @@
-#include "primitives.c"
-
-void send (int n) 
-    /*
-    require TRUE/\Ready.(_^*)
-    ensure (n>0\/n=0)/\(Send^n).Done\/n<0/\(Send^w)
-    */
-{
-
-    if (n == 0) { 
-        event ("Done");
-    }
-    else {
-        event ("Send"); 
-        send (n - 1);
-    }
-} 
-
-void server (int n)
-    /*
-    require (n>0\/n=0)/\emp
-    ensure (n>0\/n=0)/\((Ready.(Send^n).Done)^w)
-    */
-{
-    event("Ready");
-    send(n);
-	server(n);
-}
-
-int main ()
-/*
-    require TRUE /\emp
-    ensure TRUE/\((Ready.(Send^n).Done)^w)
-    */
-{
-    server (-5);
-}
-

### 2022-03-29 code/src/program/send_valid.c

@@ -1,37 +1,0 @@
-#include "primitives.c"
-
-void send (int n) 
-    /*
-    require TRUE/\Ready.(_^*)
-    ensure (n>=0)/\(Send^n).Done\/n<0/\(Send^w)
-    */
-{
-
-    if (n == 0) { 
-        event ("Done");
-    }
-    else {
-        event ("Send"); 
-        send (n - 1);
-    }
-} 
-
-void server (int n)
-    /*
-    require (n>=0)/\emp
-    ensure (n>=0)/\((Ready.(Send^n).Done)^w)
-    */
-{
-    event("Ready");
-    send(n);
-	server(n);
-}
-
-int main ()
-/*
-    require TRUE /\emp
-    ensure TRUE/\((Ready.(Send^n).Done)^w)
-    */
-{
-    server (1);
-}

### 2022-03-29 code/src/program/traffic_light1.c

@@ -1,27 +1,0 @@
-#include "traffic_primitives.c"
- 
-void controller()
-    /*
-    require TRUE/\Ready.(_^*) 
-    ensure TRUE /\ (((_^*).Green)^w)
-    */
-{
-    turnGreen ();    
-    delay(4);
-    turnYellow ();
-    delay(2);
-    turnRed();
-    delay(6);
-    controller();
-}
-
-int main()
-    /*
-    require TRUE /\emp
-    ensure TRUE /\ Ready.(((_^*).Green)^w)
-    */
-{
-    event ("Ready");
-    controller();
-}
-

### 2022-03-29 code/src/program/traffic_light2.c

@@ -1,27 +1,0 @@
-#include "primitives.c"
-#include "traffic_primitives.c"
- 
-void controller()
-    /*
-    require TRUE/\Ready.(_^*) 
-    ensure TRUE /\ ((Green._._)^w)  
-    */
-{
-    turnGreen ();    
-   
-    turnYellow ();
-    
-    turnRed();
-    
-    controller();
-}
-
-int main()
-    /*
-    require TRUE /\emp
-    ensure TRUE /\ Ready.((Green._._)^w)  
-    */
-{
-    event ("Ready");
-    controller();
-}

### 2022-03-29 code/src/program/traffic_light3.c

@@ -1,27 +1,0 @@
-#include "primitives.c"
-#include "traffic_primitives.c"
-
-
-void controller(int n, int m)
-    /*
-    require (n>0 /\ m > 0) /\ Ready.(_^*)
-    ensure (n>0 /\ m > 0)  /\ (((Red^n).(Yellow^m).(Green^n))^w) 
-    */
-{
-    red(n);
-    yellow (m);
-    green (n);
-    controller(n, m);
-}
-  
-   
-int main()
-    /*
-    require TRUE /\emp
-    ensure TRUE  /\ Ready.(((Red^5).(Yellow).(Green^5))^w) 
-    */
-    
-{
-    event ("Ready");
-    controller(5, 1);
-}

### 2022-03-29 code/src/program/traffic_light3_1.c

@@ -1,27 +1,0 @@
-#include "primitives.c"
-#include "traffic_primitives.c"
-
-
-void controller(int n, int m)
-    /*
-    require (n>0 /\ m > 0) /\ Ready.(_^*)
-    ensure (n>0 /\ m > 0)  /\ (((Red^n).(Yellow^n).(Green^n))^w) 
-    */
-{
-    red(n);
-    yellow (n);
-    green (n);
-    controller(n, n);
-}
-  
-   
-int main()
-    /*
-    require TRUE /\emp
-    ensure TRUE  /\ Ready.(((Red^5).(Yellow^5).(Green^5))^w) 
-    */
-    
-{
-    event ("Ready");
-    controller(5, 1);
-}

### 2022-03-29 code/src/program/traffic_light4.c

@@ -1,24 +1,0 @@
-#include "primitives.c"
-#include "traffic_primitives.c"
-
-void controller()
-    /*
-    require TRUE /\ Ready._*
-    ensure (TRUE/\ X \in {Yellow._*, Red._*, Green._*}) /\ (X.X.X)^w
-    */
-{
-    turnYellow ();
-    delay (2);
-    turnRed();
-    delay (2);
-    turnGreen (); 
-    delay (2);   
-    controller();
-}
-
-int main()
-{
-    event ("Ready");
-    controller();
-}
-

### 2022-03-29 code/src/program/traffic_primitives.c

@@ -1,96 +1,0 @@
-#include "primitives.c"
-
-void delay (int n) 
-    /*
-    require (n>=0)/\emp
-    ensure (n>=0)/\(Delay^n)
-    */
-{
-    if (n == 0) { 
-        return;
-    }
-    else {
-        event ("Delay"); 
-        delay (n - 1);
-    }
-} 
-
-void turnRed ()
-    /*
-    require TRUE/\emp
-    ensure TRUE /\ Red
-    */
-{
-    event ("Red"); 
-    printf("X Ave. - RED; Y Blvd. - RED\n");
-}
-
-void turnGreen ()
-    /*
-    require TRUE/\emp
-    ensure TRUE /\ Green
-    */
-{
-    event ("Green"); 
-}
-
-
-void turnYellow ()
-    /*
-    require TRUE/\emp
-    ensure TRUE /\ Yellow
-    */
-{
-    event ("Yellow"); 
-    printf("X Ave. - RED; Y Blvd. - YELLOW\n");
-}
-
-
-void red (int n) 
-    /*
-    require (n>=0)/\emp
-    ensure TRUE/\(Red^n)
-    */
-{
-    if (n == 0) { 
-        turnRed();
-        return;
-    }
-    else {
-        turnRed();
-        red (n - 1);
-    }
-} 
-
-void green (int n) 
-    /*
-    require (n>=0)/\emp
-    ensure TRUE/\(Green^n)
-    */
-{
-    if (n == 0) { 
-        turnGreen ();    
-        return;
-    }
-    else {
-        turnGreen ();    
-        green (n - 1);
-    }
-} 
-
-void yellow (int n) 
-    /*
-    require (n>=0)/\emp
-    ensure TRUE/\(Yellow^n)
-    */
-{
-    if (n == 0) { 
-        turnYellow ();
-        return;
-    }
-    else {
-        turnYellow ();
-        yellow (n - 1);
-    }
-} 
-

### 2022-03-29 code/src/program/train.c

@@ -1,115 +1,0 @@
-#include "arduino.c"
-
-// L298 
-#define L298_ENA 5
-#define L298_IN1 6
-#define L298_IN2 7
-
-
-// SCRIPTS VARIABLES
-int counterScheduler =0;
-unsigned long timerScheduler = 0;
-unsigned long timerLocal = 0;
-int speedAuto = 0;
-
-
-void setup() 
-    /*
-    require TRUE/\emp
-    ensure TRUE/\Ready
-    */
-{
-
-// Initializing pins
-  pinMode(L298_ENA, OUTPUT);
-  pinMode(L298_IN1, OUTPUT);
-  pinMode(L298_IN2, OUTPUT);
-
-// Set default direction to FORWARD
-  digitalWrite(L298_IN1, HIGH);
-  digitalWrite(L298_IN2, LOW); 
-  event ("Reday");
-
-}
-
-void control(int counterScheduler) 
-    /*
-    require TRUE/\Ready._*
-    ensure TRUE/\
-    */
-{
-
-  	// Start Scheduler
-    if (millis() > (timerScheduler + 1000)) {  // Tick every 1 sec
-      counterScheduler++; 
-      timerScheduler = millis();
-    }  
-    
-    // ------------- SCRIPT SWING
-    int brakingDelta = 5;
-    int accelerateDelta = 6;
-
-    // 1  | 0 > Time < 5 sec
-    if (counterScheduler <= 5) {  
-        // Start train
-        if (millis() > (timerLocal + 100)) {
-          if (speedAuto < 240) speedAuto = speedAuto + accelerateDelta;
-          else speedAuto = 255;
-          analogWrite(L298_ENA, speedAuto); 
-          timerLocal = millis();
-        }   
-    }       
-    
-    // 2  | 10 sec > Time < 15 sec
-    else if ((counterScheduler >= 10) && (counterScheduler <= 15)) {  // Stop train after 10 sec
-        // Stop train
-        if (millis() > (timerLocal + 100)) {
-          if (speedAuto > 30) speedAuto = speedAuto - brakingDelta;
-          else speedAuto = 0;
-          analogWrite(L298_ENA, speedAuto); 
-          timerLocal = millis();
-        } 
-    }  
-    
-    // 3  | Change direction
-    else if (counterScheduler == 16) {  
-        digitalWrite(L298_IN1, LOW);
-        digitalWrite(L298_IN2, HIGH); 
-    }   
-    
-    // 4  | 20 sec > Time < 30 sec
[…]

### 2022-03-29 code/src/program/train_detect.c

@@ -1,46 +1,0 @@
-#include "arduino.c"
-
-#define LED_BUILTIN 0
-
-int trigger_s1, trigger_s2, latch_s1, latch_s2; 
-
-void setup() 
-    /*
-    require TRUE/\emp
-    ensure TRUE/\Ready
-    */
-{
-  pinMode(LED_BUILTIN, OUTPUT);
-  pinMode(9, INPUT);
-  pinMode(10, INPUT); 
-  event ("Reday");
-}
-
-void control() {
-
-  if (digitalRead(10) == HIGH) {
-    trigger_s1 = 1;
-    latch_s1 = 1;
-  }
-  else trigger_s1 = 0;
-    
-  if (digitalRead(9) == HIGH) {
-    trigger_s2 = 1;
-    latch_s2 = 1; 
-  }
-  else trigger_s2 = 0;  
-
-  if (latch_s1 && latch_s2 && !trigger_s1 && !trigger_s2) {
-    latch_s1 = 0;    
-    latch_s2 = 0;     
-  }
-
-  if (latch_s1 || latch_s2) digitalWrite(LED_BUILTIN, HIGH);
-  else digitalWrite(LED_BUILTIN, LOW);
-  control();
-}
-
-int main (){
-    control();
-}
-

### 2022-04-01 paper/tv.tex
m

@@
 \newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
-\newcommand{\timedL}{\code{\lambda^{t}}}
+\newcommand{\timedL}{\code{C^{t}}}
 
@@
 %% allowing the author to define a "short title" to be used in page headers.
-\title{Automated Timed Temporal Verification
-% for a Mixed Sync-Async Concurrency Paradigm
-}
+\title{Automated Verification for Real-Time Systems 
+using Implicit Clocks and an Extended Antimirov Algorithm}
 
@@
 \begin{abstract} 
-In this work, we study temporal verification of 
-compositional real-time systems, modeled 
-using mutable variables and timed processes.  
-Instead of explicitly manipulating clock variables, 
-several compositional timed behavioral patterns, 
-such as \emph{delay}, \emph{timeout}, \emph{deadline},  
-are introduced to capture quantitative timing constraints.
-The idea is to dynamically create clocks  
-and solve constraints on the clocks.
-
-We propose a novel solution for timed verification via a 
-compositional Hoare-style forward verifier and a 
-term rewriting system (TRS) on \emph{Timed Effects} (\timedEffects).  
+Real-time systems are systems where the correctness does not 
+only depend on their correct functioning but also on meeting 
+realtime constraints.
+Different from existing timed-automata based techniques, 
+we propose a novel solution that integrates a 
+modular Hoare-style forward verifier with a new term rewriting 
+system (TRS) on \emph{Timed Effects} (\timedEffects).
+The main purpose is to dynamically create clocks  
+and efficiently solve constraints on the clocks, 
 We formally define 
-a core language \timedL, generalizing the timed processes.
+a core language \timedL, generalizing the real-time systems, modeled 
+using mutable variables and timed behavioral patterns, 
+such as \emph{delay}, \emph{timeout}, \emph{deadline}. 
 Secondly, to capture real-time specifications, 
@@
 that extends 
-\emph{Kleene Algebra} with dependent
+\emph{Regular Expressions} with dependent
 values and arithmetic constraints.
@@
 \timedL\ programs, expressed in \timedEffects. 
-Lastly, we present a purely algebraic TRS, to 
+Lastly, we present a purely algebraic TRS, i.e., the extended Antimirov algorithm, to 
 efficiently prove language inclusions between 
@@
 correctness; report on case studies and the experimental results.
-%we prototype the  verification system in OCaml; then prove soundness of both the effects inference process and the term rewriting process. % in Coq.
 
@@
 \label{Introduction}
+
+several compositional ,  
+are introduced to capture quantitative timing constraints.
+The idea is to
+
+In this work, we study temporal verification of 
+compositional real-time systems,
+
+Existing automatic verification techniques massively rely on 
+the timed automata which requires manually cast of clock variables with 
+carefully calculated clock constraints.
 

### 2022-04-01 paper/tv.tex
m

@@
 realtime constraints.
-Different from existing timed-automata based techniques, 
+Different from existing Timed Automata based techniques, 
 we propose a novel solution that integrates a 
@@
 \timedL\ programs, expressed in \timedEffects. 
-Lastly, we present a purely algebraic TRS, i.e., the extended Antimirov algorithm, to 
+Lastly, we present a purely algebraic TRS, i.e., an extended Antimirov algorithm, to 
 efficiently prove language inclusions between 
@@
 
-several compositional ,  
-are introduced to capture quantitative timing constraints.
-The idea is to
-
-In this work, we study temporal verification of 
-compositional real-time systems,
-
-Existing automatic verification techniques massively rely on 
-the timed automata which requires manually cast of clock variables with 
-carefully calculated clock constraints.
-
 Specification and verification of real-time systems are important 
 research topics which have practical implications. During the last 
-(more than) two decades, a popular approach for specifying real-time systems is 
+more than two decades, a popular approach for specifying real-time systems is 
 based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
@@
 A number of automatic verification support for Timed Automata have proven 
-to be successful, such as UPPAAL \cite{DBLP:journals/sttt/LarsenPY97}.
+to be successful \cite{DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
 
@@
 \begin{comment}
+  several compositional ,  
+are introduced to capture quantitative timing constraints.
+The idea is to
+
+In this work, we study temporal verification of 
+compositional real-time systems,
+
+Existing automatic verification techniques massively rely on 
+the timed automata which requires manually cast of clock variables with 
+carefully calculated clock constraints.
+
 A TRS is a refutation method that normalizes expressions in such a way 
@@
 
-\begin{figure}[ht]
-      \vspace{-2mm}
-\begin{lstlisting}[columns=fullflexible]
-hiphop module main (out Prep, in Tick, out Ready, out Go, out Cook)
-/*@ requires true : emp @*/
-/*@ ensures  0<=t/\t<3 : {}.({Cook})#t.{}^* @*/
-{
-	fork{ // The effects of the first thread is true : Ready?.{Go}
-		await Ready; emit Go; 
-	}par{ // The effects of the second thread is 0<t<3 : {Prep, Cook}#t.{Ready}
-		emit Prep;
-		async Ready { run cook (3, Tick, Cook); }}}
-// The final effects for main is  0<=t/\t<3 : ({Prep}.{Cook})#t.{Ready}.{Go}
-
-hiphop module cook (var d, in Tick, out Cook)
-/*@ requires d>2  : {}^*.{Prep} @*/
-/*@ ensures  0<=t/\t<d : ({}.{Cook})#t @*/
-{	abort count(d, Tick) { yield; emit Cook; }}
-\end{lstlisting}  
-      \vspace{-1mm}
-      \caption{Mixed Synchronous and Asynchronous Concurrency with Function Calls.}\label{fig:overview_eg2}
-            \vspace{-1mm}
-\end{figure}
-
-%We demonstrate
-
-%%, and a function call from module \code{main} to \code{cook}.
-
-      \vspace{-2mm}
 \subsection{Forward Verification}
@@
 
-To formulate the target language, we generalise the design of  Hiphop.js into a core language \code{\timedL}, 
-%Based on the design of , but not too specific to Hiphop.js, we summarise a core language to be our target language, 
-which provides the infrastructure for mixing synchronous and asynchronous concurrency models. 
-We here formally define the syntax of \code{\timedL}, as shown in \figref{fig:Hiphop_Syntax} The statements marked as \textcolor{purple} {purple} come from the  Esterel v5 \cite{berry1999constructive,berry2esterel} endorsed by current academic compilers; while the statements marked as \textcolor{blue} {blue} provide the asynchrony coming from the usage of JavaScript promises.
-In this work, we are mainly interested in signal status and control propagation, which are not related to data, therefore the data variables and data-handling primitives are abstracted away.
+To formulate the target language, we generalize the design of the real-time systems
+ into a core language \code{\timedL}, 
+ which provides the infrastructure for mutable variables and timed behavioral patterns, 
+ such as \emph{delay}, \emph{timeout}, \emph{deadline}. 
+We here formally define the syntax of \code{\timedL}, as shown in \figref{fig:code_language}
 
@@
 % |\ e_1}\ op\ \code{ e_2 \ 
-| \ \textbf{event} [\anyevent{A}]\
+| \ \textbf{event} [ev]\
   %|\ \textbf{assert}\ \effect \ 
@@
 \qquad\quad
- \code{(Events)  \anyevent{A} ::\in \Sigma 
+ \code{(Events)  ev ::\in \Sigma 
 \qquad\quad
@@
    \  | \ \empt 
-    \ | \ \anyevent{A} 
-    \ | \ \anynotevent{A}
-    \ | \ \_  
+    \ | \ ev 
     %   \ | \ \anyevent{a}
@@
 
+\\
+\m{(Events)} & ev  & \ ::= \ & 
+\code{
+    \anyevent{A} (c)
+    \ | \ \anynotevent{A} (c)
+    \ | \ \_  
+}
+
 %    \\
@@
     \\~\\
-    \multicolumn{4}{l}{
-      \code{(Events)  \anyevent{A} ::\in \Sigma}   
-   \qquad
+    \multicolumn{4}{c}{
+     % \code{(Events)  \anyevent{A} ::\in \Sigma}   
+   %\qquad
     \code{c ::\in \mathbb{R}^{+}} 

### 2022-04-02 paper/tv.tex
m

@@
 
-%as our target language because it Given that Hiphop.js is an integration of Esterel and JavaScript,
-
-Meta-variables are {\textbf{S}}, \code{x} and \code{nm} .
-Basic signal types include \code{IN} for input signals, \code{OUT} for output signals, \code{INOUT} for both and \code{int} for integer variables.
-{\textbf{var}} represents the countably infinite set of arbitrary distinct identifiers.
-We assume that programs are well-typed conforming to basic types \code{\tau}.
-
-A program \code{\mathcal{P} } comprises a list of module definitions \code{ \overrightarrow{module}}.
-Here, we use the \code{ \overrightarrow{}} script to denote a finite vector (possibly empty) of items.
-Each \code{module} has a name \code{nm}, a list of well-typed arguments \code{ \overrightarrow{\tau\ x} } and $ \overrightarrow{\tau\ \textbf{S}}$, a statement-oriented body \code{{p}}, associated with a precondition \code{\effect_{pre}} and a postcondition \code{\effect_{post}}.
-(The syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects})
+Here, we regard \code{k} and \code{x} are meta-variables.
+\code{k^\tau} represents a constant of basic type \code{\tau}.
+\textbf{var} represents the countably infinite set of arbitrary distinct identifiers.
+\anyevent{a} refers to a singleton event coming from the finite set of events \code{\Sigma}. 
+%Without loss of generality, any event can be further parametrized with constant values, e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events, leading to infinite alphabet.
+We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
+%Each events raising expression \code{\textbf{event}} is parametrized with an event, to trigger such a single event. 
+A program \code{\mathcal{P}} comprises a list of 
+%data type declarations \code{{datat^*}} and a list of 
+method declarations \code{{meth^*}}. 
+Here, we use the \code{*} superscript to denote a finite list (possibly empty) of items, for example, \code{{x^*}} refers to a list of variables, \code{x_1, ...,\ x_n}. 
+%Besides, \code{d} denotes the name of a user-defined data type, \code{f} denotes a field name.
+
+Each method \code{meth} has a name \code{mn}, an expression-oriented body \code{e}, also is associated with a precondition  \code{\effect_{pre}} and a postcondition \code{\effect_{post}} (the syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects}).
+The language allows each iterative loop to be optimized to an equivalent tail-recursive method, where mutation on parameters is made visible to the caller.
+The technique of translating away iterative loops is standard
+%\citeref{insa2015automatic} 
+and is helpful
+in further minimising our core language. Expressions comprise unit (), 
+constants \code{k}, 
+variables \code{x}, 
+%one-level field access \code{v.f} (rather than \code{v.f1.f2...} for the sake of simplicity), 
+%data structure allocation \code{\textbf{new}\ d({v^*})},  
+local variable declaration \code{\tau\ x;\ e}, method calls \code{mn({x^*}) }, 
+variable assignments \code{x{:=}e}, 
+%field update \code{v.f:=e}, 
+expression sequences \code{e_1;e_2},
+conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2},
+event raises expression \code{ \textbf{event} [ev] },
 
@@
    {meth^*}} 
-\qquad   \qquad
-    \m{(Basic\ Types)} \qquad  \code{\tau} \code{  ::= }
+\qquad   \qquad\quad 
+    \m{(Basic\ Types)} \qquad  \code{\tau} \code{\quad  ::= \quad }
      \code{int\ |\ bool\ |\ void}
@@
 | \ \textbf{event} [ev]\ 
-  %|\ \textbf{assert}\ \effect \ 
-  | \ \textbf{timeout} \ e \ d \  
-  | \ \textbf{deadline} \ e \ d \  
-  | \ \textbf{delay}\ d 
+  | \ \textbf{delay}\ [d] \ 
+  | \ e_1\ \textbf{timeout}\  [d] \  e_2 \ 
+  | \ \textbf{deadline}  \ [d] \ e \  
   }  \\
@@
 
-%
+A number of timed process constructs can be used to capture common 
+real-time system behavior patterns. Without loss of generality, we 
+assume d is an integer constant.  $\textbf{delay}\ [d]$ idles for exactly $d$ 
+time units. In process $e_1\ \textbf{timeout}\ [d] e_2$, the first observable event of 
+$e_1$ shall occur before d time units elapse (since the process starts). 
+Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
+Process $\textbf{deadline}\ [d]\ e$ constrains $e$ to terminate before $d$ time units. 
+In this setting, clock variables are 
+made implicit and hence they cannot be compared with each other 
+directly, which potentially allows efficient clock manipulation and 
+hence system verification.
+
+%
+
+\subsection{Semantics}
+\label{subsec:Targetlanguage_Semantics}
+
+In order to define the operational semantics of a system model, 
+we define the notion of a configuration to capture the global 
+system state during system execution.
+
+\begin{definition}[System configuration]
+A system configuration is a pair $c = (V , e)$ where $V$ is a variable valuation function and $e$ is an expression.
+\end{definition}
+
+A transition of the system is of the form $c \xrightarrow[]{\text{x}} c^\prime$ where $c$ and $c^\prime$ are 
+the system configurations before and after the transition respectively. 
+We adopt the following naming convention for transition labels: 
+$t$ denotes a non-negative real number; $\tau$ denotes an invisible event;
+For instance, $c \xrightarrow[]{\text{t}} c^\prime$ denotes a transition of $t$ time units elapsing. 
+In the following, we present the firing rules which are associated with 
+the timed process constructs. 
+\begin{flalign*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%   Wait                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\code{\frac{
+  t {\leq} d 
+}{(V, \textbf{delay}\ [d]) \xrightarrow[]{\text{t}} (V, \textbf{delay}\ [d \text{-}t])}\ [de1]} 
+\qquad \qquad 
+\code{\frac{
+}{(V, \textbf{delay}\ [0]) \xrightarrow[]{\tau} (V, ())}\ [de2]} 
+\end{flalign*}
+
+\begin{flalign*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%   timeout                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\code{\frac{
+  (V,e_1) \xrightarrow[]{\text{e}} (V^\prime,e_1^\prime)
+}{(V, e_1\ \textbf{timeout} \  [d] \ e_2) \xrightarrow[]{\text{e}} (V^\prime,e^\prime)}\ [to1]} 
+\quad  
+\code{\frac{
+  (V,e) \xrightarrow[]{\tau} (V^\prime,e^\prime)  \quad (t {\leq} d)
+}{(V, e_1\ \textbf{timeout} \  [d] \ e_2) \xrightarrow[]{\text{t}} (V, \textbf{timeout}\ e^\prime \ [d \text{-}t])}\ [to2]} 
+\\
+\code{\frac{
+  (V,e_1) \xrightarrow[]{\text{t}} (V,e_1^\prime)  \quad (t {\leq} d) 
+}{(V, e_1\ \textbf{timeout} \ [d] \ e_2) \xrightarrow[]{\text{t}} (V,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [to3]} 
+\quad  
+\code{\frac{
+}{(V, e_1\ \textbf{timeout} \  [0] \ e_2) \xrightarrow[]{\tau} (V, e_2)}\ [to4]} 
+\end{flalign*}
+
+\begin{flalign*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%   deadline                 %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\code{\frac{
+  (V,e) \xrightarrow[]{\text{x}} (V^\prime,e^\prime)
+}{(V, \textbf{deadline}\  [d] \ e ) \xrightarrow[]{\text{x}} (V^\prime, \textbf{deadline} \ [d] \ e^\prime)}\ [dl1]} 
+\quad  
+\code{\frac{
+  (V,e) \xrightarrow[]{\text{t}} (V,e^\prime)  \quad (t {\leq} d)
+}{(V, \textbf{deadline} \  [d]\ e ) \xrightarrow[]{\text{t}} (V, \textbf{deadline} \ [d \text{-}t] \ e^\prime )}\ [dl2]} 
+\end{flalign*}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : \anyevent{A} }  &\m{iff}\quad 
+&\code{d, \varphi \models  \pi : ev }  &\m{iff}\quad 
 & d {\geq} 0 \ and\ {\tt{SAT}(\pi)}  \ and \ 
-\varphi {=} \code{[\anyevent{A}]}
+\varphi {=} \code{[ev]}
   \\[0.2em]

### 2022-04-02 paper/tv.tex
m

@@
 \label{Forward_Rules}
-To help with reasoning logical errors (cf.
-\secref{subsec:LogicalIncorrectCatching}), the rule \code{[FV\text{-}Nothing]} extends the current time instance with all the signals in the environment pointing to absent.
-%is the Esterel equivalent of unit, void or skip in other languages, 
-% obtains the next program state by inheriting the current program state.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          NOTHING                              %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{\frac{
-%\forall \textbf{S} \in \env.\  C[ \textbf{S}\mapsto  Absent]
-C^\prime {=} \{\textbf{S}\mapsto  Absent\ |\  \forall \textbf{S} \in \env\}
-}{\env \vdash \langle \Pi, H, C, T \rangle\  nothing \ \langle
- \Pi, H, C {+}{+} C^\prime, T \rangle}\ [FV\text{-}Nothing]} 
-\end{flalign*}
-The rule \code{[FV\text{-}Emit]} extends the current time instance with signal {\textbf{S}}  pointing to \code{Present}.
-%status of signal \code{\textbf{S}} (from \code{Undef}) to \code{Present}; keeps the pure constraints, the history trace and the current term unchanged.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                              EMIT                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-C^\prime {=} C {+}{+} [ (\textbf{S}\mapsto  Present)]
-}{\env \vdash \langle \Pi, H, C, T \rangle\  emit \ \textbf{S} \ \langle  \Pi, H, C^\prime, T \rangle}\ [FV\text{-}Emit] } 
-\end{flalign*}
-The rule \code{[FV\text{-}Yield]} archives the current time instance to the history trace; then initializes a new time instance where all the signals from \code{\env} are set to be undefined.
-Then the new \emph{current} is bound with a fresh non-negative term \code{ T^\prime}.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            PAUSE                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\Pi^\prime {=} \Pi \wedge  T^\prime {\geq}0 \qquad 
-C^\prime {=} \{\textbf{S}\mapsto  Undef\ |\  \forall \textbf{S} \in \env\} \qquad
-H^\prime {=} H \cdot (C\# T) \qquad
-( T^\prime\ is\ fresh)
-}{\env \vdash 
-\langle  \Pi, H, C, T  \rangle\  yield \ \langle 
- \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle}\ [FV\text{-}Yield]} 
-\end{flalign*}
-
-The rule \code{[FV\text{-}Present]} 
-enters into branches \code{p} and \code{q} after setting the status of  {\textbf{S}} in the current time instance to \code{Present} and \code{Absent} respectively.
-We deploy the \code{cut} function to reallocate the next program state.
-{Each signal can be reset from \code{\m{Undef}} to \code{\m{Present}} or \code{\m{Absent}} maximum once.}
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          PRESENT                              %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\begin{matrix}
-\text{\code{
- \env \vdash \langle  \Pi, H, C[ \textbf{S}\mapsto  Present], T  \rangle\  {p} \ \langle 
- \Pi_1, H_1, C_1,  T_1 
- \rangle
-}}\\
- \text{\code{
-\env \vdash \langle  \Pi, H, C[ \textbf{S}\mapsto  Absent], T  \rangle\  {q} \ \langle 
- \Pi_2, H_2, C_2,  T_2 
-\rangle 
-}}
-\\
- \text{
-\code{
-\langle   \Pi^\prime , H^\prime, C^\prime,  T^\prime \rangle {=} cut \ (\Pi_1 \wedge \Pi_2 : H_1 \cdot (C_1\#T_1) \vee H_2 \cdot (C_2\#T_2) )
-} 
- }
-\end{matrix}
-}{\env \vdash \langle  \Pi, H, C, T  \rangle\  present \ \textbf{S} \ {p} \ {q}  \ \langle  \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle}\ [FV\text{-}Present] } 
-\end{flalign*}
-}
-%Intuitively, Cut is defined in, with the intuition of cutting a trace es into a history trace H and a current time instance \code{C\#T}.
-\begin{definition}[Cut]\label{Def_cut} 
-Given any \code{\pi} and \code{\es}, we define: 
-\code{cut(\pi{:} \es)} computes \code{\langle \Pi, H, C, T \rangle. 
-} In particular, 
-{ 
-\begin{gather*}
-\code{cut(\pi:\es^\prime \cdot I){=} \langle \pi\wedge T{\geq}0, \es^\prime, I, T \rangle}    \qquad  (\es{=}\es^\prime \cdot I, \ T\ is\ \m{fresh})
-\\
- \code{cut(\pi:(\es^\prime \cdot I) \# t) {=} \langle \pi\wedge T_1{\geq}0\wedge T_2{\geq}0 \wedge T_1{+}T_2{=}t, \es^\prime \#T_1, I, T_2 \rangle} \quad \ 
- (\es{=}(\es^\prime \cdot I)\# t, \ T_1, \ T_2 \ are\ \m{fresh})
-\end{gather*}}
-\end{definition}
-
-The rule \code{[FV\text{-}Fork]} gets \code{\langle \Pi_1, H_1, C_1, k_1   \rangle} and 
-\code{\langle \Pi_2, H_2, C_2, k_2 \rangle} by executing \code{{p}} and \code{{q}} independently. 
-We parallel synchronise the effects from these two branches; and use the \code{cut} function to reallocate the next program state. 
-\begin{flalign*}
-&
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                             PAR                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\code{\frac{
-\begin{matrix}
-\text{\code{
-\env \vdash \langle  \Pi, H, C, T  \rangle\  {p} \ \langle  \Pi_1, H_1, C_1, T_1 
- \rangle 
-}}\qquad\quad
- \text{\code{
-\env \vdash \langle  \Pi, H, C, T  \rangle\  {q} \ \langle \Pi_2, H_2, C_2, T_2 
-\rangle 
- }}\\
- \text{\code{
-\langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle {=} cut\ (
-\Pi_1 \wedge \Pi_2 :  H_1 \cdot (C_1\#T_1) \ || \ H_2 \cdot (C_2\#T_2))
- }}
-\end{matrix}
-}{\env \vdash \langle  \Pi, H, C, T  \rangle\  fork\  {p}  \ {q} \ \langle   \Pi^\prime , H^\prime, C^\prime,  T^\prime \rangle} \ [FV\text{-}Fork] } 
-\end{flalign*}
-The rule \code{[FV\text{-}Seq]} firstly gets \code{ \langle \Pi_1, H_1, C_1, T_1  \rangle} by executing \code{{p}}.
-Then it further gets  \code{ \langle \Pi_2, H_2, C_2, T_2 \rangle}  by continuously executing \code{{q}}, to be the final program state.
-%and returns \code{\effect_1^{k_1}} to be the final effects. 
-%the rule splits \code{\effect_1} into \code{\tau^{\prime}} and  \code{ (\Pi^\prime {\wedge}  \phi^\prime )}; constructs the final effect \code{\effect_2^{k_2}} by  executing \code{\textbf{p}_2}.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                             SEQ                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\begin{matrix}
-\text{\code{
-\env \vdash \langle  \Pi, H, C, T  \rangle\  {p} \ \langle  \Pi_1, H_1, C_1, T_1 
- \rangle 
-}}\qquad\quad
- \text{\code{
-\env \vdash \langle \Pi_1, H_1, C_1, T_1  \rangle\  {q} \ \langle \Pi_2, H_2, C_2, T_2 
-\rangle 
- }}
-\end{matrix}
-}{\varrho \vdash \langle \Pi, H, C, T \rangle \  seq\  {p} \ {q}  \ \langle \Pi_2, H_2, C_2, T_2 
-\rangle  }\ [FV\text{-}Seq]  } 
-\end{flalign*}
-
-The rule \code{[FV\text{-}Loop]} computes a fixpoint (as the invariant effects of the loop body) \code{\langle \Pi_2, H_2, C_2, T_2 \rangle} by continuously executing \code{p} twice\footnote{The deterministic loop invariant can be fixed after the second run of the loop body, cf.
-\appref{proof:twice} for the proof.}, starting from temporary initialised program states \code{\langle \Pi, \empt,  C , T \rangle} and
-\code{\langle \Pi_1, \empt,  C_1 , T_1  \rangle} respectively. 
-The final state will contain a repeated trace \code{(H_2 \cdot C_2\# T_2 )^\star}.
-% Then anything following an infinite trace will be abandoned. (cf. \tabref{table:normalization})
-%gets \code{\langle\effect^k \rangle} by initializing the precondition with \code{\empt} to be the history trace and the current instant by mapping all the local signals to \code{absent} before executing \code{ \textbf{p}}.
-When there is no exit from the loop body (\code{k{=}0}), the final effects is an infinite trace constructed by \code{(\tau \cdot (\Pi \wedge  \phi) \cdot \effect^\omega)^0}.
-Otherwise, when there is an exit in the loop body, the final effects is a finite trace \code{(\tau \cdot (\Pi \wedge  \phi) \cdot \effect)^k}, reflecting the completion code \code{k}.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                             LOOP                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\begin{matrix}
-\text{\code{
-\env \vdash  \langle \Pi, \empt,  C , T  \rangle\  {p} \ \langle \Pi_1, H_1, C_1, T_1 \rangle \qquad\quad 
-\env \vdash  \langle \Pi_1, \empt,  C_1 , T_1  \rangle\  {p} \ \langle \Pi_2, H_2, C_2, T_2\rangle  
- }}\\
- \text{
-\code{
-H^\prime {=} H \cdot H_1 \cdot (H_2 \cdot C_2\# T_2 )^\star \cdot H_2
-} 
- }
- %\qquad \code{C^\prime = \{\textbf{S}\mapsto  absent\ |\  \forall \textbf{S} \in \varrho\}}
-\end{matrix}
-}{\env \vdash \langle \Pi, H, C, T \rangle\  loop \ {p} \ \langle  \Pi_2, H^\prime, C_2 , T_2 \rangle} \ [FV\text{-}Loop]} 
-\end{flalign*}
-
-%The rule \code{[FV\text{-}Trap]} gets \code{\langle \Pi^\prime, H^\prime, C^\prime, k^\prime \rangle} by executing the trap body \code{ \textbf{p}}.
-%When there is no exit from the trap body (\code{k{=}0}), or there is an exit which can be exactly catched by the current trap (\code{k{=}1}), we leave the final completion code to be 0.
-When there is an exit with a higher priority, (\code{k{>}1}), indicating to exit from a outer trap, we get the final \code{k_f} by decreasing  the completion code by one.
-
-%\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%                             TRAP                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%&
-%\code{\frac{
-%\begin{matrix}
-%\text{\code{
-% \env \vdash \langle \Pi, H, C, k  \rangle\  \textbf{p} \ \langle \Pi^\prime, H^\prime, C^\prime, k^\prime 
-%   \rangle
-% }}\\
-% \text{\code{
-%k_f  = 0  \qquad\qquad\   when \quad k^\prime {\leq} 1 }}\\
-%\text{\code{
-%k_f  = k^\prime\text{-}1  \qquad\quad\   when \quad k^\prime {>} 1 }}
-%\end{matrix}
-%}{\env \vdash \langle \Pi, H, C, k  \rangle\  trap\ \textbf{T} \ \textbf{p} \ \langle   \Pi^\prime, H^\prime, C^\prime, k_f \rangle}\ [FV\text{-}Trap]} 
-%\end{flalign*}
-%
-%As \code{exit \ \textbf{T}_{k^\prime}} will abort execution up to the \code{(k^\prime{+}1)}th enclosing of the trap \code{\textbf{T}}.
-%%reducing it to nothing. It can be used for exception handling, but also for non-exceptional control flow. 
-%The rule \code{[FV\text{-}Exit]} sets the value of \code{k} using \code{k^\prime{+}1}. %and keeps the history trace and the current time instant unchanged. 
-%\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%                             EXIT                                %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%&
-%\code{\frac{
-%}{\env \vdash \langle \Pi, H, C, k \rangle\  exit \ \textbf{T}_{k^\prime} \  \langle  \Pi, H, C, k^\prime{+}1 \rangle}\ [FV\text{-}Exit]} 
-%\end{flalign*}
-%
-The rule \code{[FV\text{-}Call]} triggers the back-end solver TRS to  check if the precondition of the callee, \code{\effect_{pre}}, is satisfied by the current effects state or not.
-If it holds, the rule obtains the next program state by concatenating the postcondition \code{\effect_{post}} to the current effects state.
-(cf.
-\figref{fig:forward_example})
-\begin{flalign*}
-&
-\code{\frac{
-\begin{matrix}
-\code{nm  \ \ {(\overrightarrow{\tau\ x}, \  \overrightarrow{\tau\ \textbf{S}} )}\ \langle\textbf{requires}\  \effect_{pre}\ \ \textbf{ensures}\ \effect_{post} \rangle\ {p} \in \mathcal{P}}\\
-\code{\textit{TRS}  \vdash  \Pi : H \cdot (C\# T)  \CONTAIN \effect_{pre} }
-\qquad\quad
-\code{
-\langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle {=} cut\ (\Pi :  H \cdot (C\#T) \cdot \effect_{post})
-}
-\end{matrix}
-}{\env \vdash \langle \Pi, H, C, T \rangle\  run \ nm \ {( \overrightarrow{x}, \overrightarrow{ \textbf{S}})} \ \langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle } \ [FV\text{-}Call]  } 
-\end{flalign*}
-
-The rule \code{[FV\text{-}Abort]} initialises the state using \code{\langle  \Pi, \epsilon, C, T  \rangle} before entering into \code{ {p}}, and  obtains \code{\langle \Pi^\prime, H^\prime, C^\prime,  T^\prime \rangle} after the execution; then uses a fresh time variable  \code{T_d} to set an upper-bound for the execution \code{H^\prime \cdot (C^\prime \# T^\prime)}, where the constraint on \code{T_d} is \code{0{\leq}T_d{\leq} d}.
-Lastly, it sets the new current time instance \code{C^{\prime\prime}} by setting all the existing signals to undefined, which is bound with a fresh non-negative term \code{ T_f}.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                              ABORT                              %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\begin{matrix}
-\text{
-\code{
-\env \vdash \langle  \Pi, \epsilon, C, T  \rangle\   {p} \ \langle \Pi^\prime, H^\prime, C^{\prime},  T^\prime  \rangle
-\qquad\quad
-\Pi^{\prime\prime} {=} \Pi^{\prime} \wedge (0 {\leq}T_d{<} d) \wedge (T_f {\geq}0)
-}}
- \\
-\text{
-\code{
-H^{\prime\prime} {=} (H^\prime \cdot (C^{\prime}\#  T^\prime)) \# T_d
-}}\qquad
-\text{\code{
-C^{\prime\prime} {=} \{\textbf{S}\mapsto  \m{Undef}\ |\  \forall \textbf{S} \in \env\}
-\qquad\quad \m{(T_d, T_f\ are\ fresh)}
-}}
-\end{matrix}
-}{\env \vdash \langle \Pi, H, C, T \rangle\  abort\ {p}\ when\ d \ \langle \Pi^{\prime\prime}, H\cdot H^{\prime\prime}, C^{\prime\prime}, T_f  \rangle} \ [FV\text{-}Abort]} 
-\end{flalign*}
-
-Dually, the rule \code{[FV\text{-}Async]} initialises the states using \code{\langle  \Pi, \epsilon, C, k  \rangle} before entering into \code{ {p}}, and  obtains \code{\langle \Pi^\prime, H^\prime, C^\prime, k^\prime \rangle} after the execution; then uses a fresh time variable  \code{T_d} to set a lower-bound for the execution \code{H^\prime \cdot (C^{\prime} \# T^\prime)}, where the constraint on \code{T_d} is \code{T_d{\geq} d}.
-Lastly, it creates the new current time instance  \code{C^{\prime\prime}}  by
-setting \textbf{S} to present instantaneously, and the rest of the signals in \code{\env}  to undefined (as it emits \textbf{S} once the asynchronous execution is completed), which is bound with a fresh non-negative term \code{ T_f}.
-%[ \textbf{S} \mapsto  present]
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                              ASYNC                              %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\begin{matrix}
-\text{\code{\env \vdash \langle  \Pi, \epsilon, C, T  \rangle\   {p} \ \langle \Pi^\prime, H^\prime, C^{\prime},  T^\prime  \rangle
-\qquad\quad \m{(T_d, T_f\ are\ fresh)}
-}}
- \\
-\text{
-\code{
-\Pi^{\prime\prime} {=} \Pi^{\prime} \wedge (T_d{\geq} d)  \wedge (T_f {\geq} 0)
-\qquad \qquad
-H^{\prime\prime} {=}  (H^{\prime} \cdot (C^{\prime}\#  T^\prime)) \# T_d
-}}\\
-\text{\code{
-C^{\prime\prime} {=} \{\textbf{S}^\prime \mapsto  \m{Undef}\ |\  \forall \textbf{S}^\prime \in (\env \symbol{92} \textbf{S}) \} \cup \{ \textbf{S} \mapsto  Present\}
-}}
-\end{matrix}
-}{\env \vdash \langle \Pi, H, C, T \rangle\  async\ \textbf{S} \ {p} \  d \  \langle \Pi^{\prime\prime}, H \cdot H^{\prime\prime}, C^{\prime\prime}, T_f \rangle}\ [FV\text{-}Async]} 
-\end{flalign*}
-
-The rule \code{[FV\text{-}Await]} archives the current time instance to the history trace, then sets a new current instance as a waiting for signal {\textbf{S}}, bound with a fresh non-negative term \code{ T^\prime}.
-%updates the current status of signal \code{\textbf{S}} to \code{waiting}; keeps the pure constraints, history trace and completion code unchanged.
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                              AWAIT                                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{\frac{
-\Pi^\prime {=} \Pi \wedge  T^\prime {\geq}0 \qquad  
-H^\prime {=} H \cdot (C\# t) \qquad ( T^\prime\ is\ fresh)
-}{\env \vdash \langle \Pi, H, C, T \rangle\  await \ \textbf{S} \ \langle  \Pi^\prime, H^\prime, \textbf{S}?,  T^\prime \rangle}\ [FV\text{-}Await] } 
-\end{flalign*}
-
-The rule \code{[FV\text{-}Assert]} simply checks if the asserted property \code{\effect} is satisfied by the current effects state. If not, a compilation error will be raised. 
-\begin{flalign*}
-&
-\code{\frac{
-\begin{matrix}
-\code{\textit{TRS}  \vdash  \Pi \wedge (H \cdot (C\#T ) \CONTAIN \effect }
-\end{matrix}
-}{\env \vdash \langle \Pi, H, C, T  \rangle\  assert\ \effect  \ \langle \Pi, H, C, T  \rangle}\ [FV\text{-}Assert]} 
-\end{flalign*}
 
@@
 
-\subsubsection{Handling Finite and Infinite Effects Simultaneously}~\\
-\label{rec:finit_infinite}
-
-      \vspace{-2mm}
-To further demonstrate the expressiveness of our timed effects, we use an example shows in \figref{fig:case_study_finit_infinit}
-It declares a recursive module named \code{send}, making a deterministic choice depending on input \code{n}: in one case it emits one  signal  \anyevent{Done}; otherwise it emits a signal 
-\anyevent{Send}, then makes a recursive call with parameter \code{n{-}1}.
-Note that the post condition contains both finite effects and infinite effects in one single formula, separated by arithmetic constrains.
-
-\begin{wrapfigure}{R}{0.5\columnwidth}
-      \vspace{-2mm}
-\begin{lstlisting}[columns=fullflexible]
-hiphop module send (var n, out Send, out Done)
-/*@ requires true : emp @*/
-/*@ ensures	(n>=0 : {}^*. {Done}) 
-          \/ (n<0   : {Send}^w)  @*/
-{
-	if (n==0) { emit Done; }
-	else {
-		emit Send;
-		yield;
-		send (d, n-1, Send, Done); }}
-\end{lstlisting}  
-      \vspace{-1mm}
-      \caption{A recursive \ttfamily{Send} module.}\label{fig:case_study_finit_infinit}
-         \vspace{-2mm}
-\end{wrapfigure}
-
-We here bring up the discussion distinguishing our work from the closely related prior work,  which deploys an effects tuple (\code{\effect_{u},\effect_{v}}) \cite{nanjo2018fixpoint},  separating the finite (\code{\effect_{u}}) and infinite (\code{\effect_{v}}) effects, therefore it leads to separated sets of effects semantics, and a separated reasoning on inductive and co-inductive definitions.
-%The paper cites a piece of work by Nanjo et al.
-[27] which is very closely related to this paper.
-They also define an effect system capturing finite and infinite temporal behaviours, including contexts and effects that can depend on program variables.
-They also give a proof system for discharging obligations that come up in type checking.
-Yet the present paper does not discuss them in any detail.
-The only mention is an off-hand comment about this work handling finite and infinite behaviors together while Nanjo et al.
-do not, which seems completely incorrect to me.
-In our work, by merging finite and infinite effects into a single disjunctive form, it not only eliminates duplicate operators, but also enables an effective reasoning of both effects logics simultaneously.
-The inclusion checking process on the \code{send}'s postcondition is demonstrated in \tabref{tab:rewriting_tree_case_study_finit_infinit} [REOCCUR], which finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{brotherston2005cyclic}.
-
-{
-\begin{table*}[ht]
-\centering
-      \vspace{0mm}
-\caption{\label{tab:rewriting_tree_case_study_finit_infinit} Term Rewriting for \figref{fig:case_study_finit_infinit} (We use \code{(\dagger)} to indicate the pairing of buds with companions.)}
-
-\vspace{0mm}
-\begin{adjustbox}{width=1\textwidth}
- \Large\begin{tabular}[t]{l}
-  \hline\\
-{
-
-\begin{prooftree}
-\Hypo{
-\code{
-\textcolor {darkred}{n{=}0} \Rightarrow \textcolor {darkred}{n{\geq}0} \qquad emp \subseteq \_^\star \qquad  \code{\siderule{[PROVE]}}
-}
-}
-\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : emp
- \CONTAIN \textcolor {darkred}{n{\geq}0} :  \bot \vee \_^\star \vee emp }  
- }
-\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : {\{Done\}} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} }  
- }
-\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : \{Done\} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} \vee
- \textcolor {darkred}{n{<}0} :
-  \{Send\}^\omega}  }
-  \Hypo{
-\code{ \textcolor {darkred}{n {\neq} 0} {:}  \{Send\}^\omega 
- \CONTAIN 
- \textcolor {darkred}{n{<}0} {:}
-  \{Send\}^\omega  (\dagger) } 
-}
-  \Infer[dashed]1[\code{\siderule{[REOCCUR]}}]{\code{ \textcolor {darkred}{n {\neq} 0} {:}  \{Send\}^\omega 
- \CONTAIN 
- \textcolor {darkred}{n{<}0} {:}
-  \{Send\}^\omega}  (\dagger)
-  }
-  \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \{Send\}^\omega 
- \CONTAIN 
- \textcolor {darkred}{n{<}0} :
-  \{Send\}^\omega}  
-  }
-  \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post}
- \CONTAIN 
- \textcolor {darkred}{n{<}0} :
-  \{Send\}^\omega}  
-  }
-  \Infer[dashed]1[]{\code{ \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} \vee
- \textcolor {darkred}{n{<}0} :
-  \{Send\}^\omega}  }
- \Infer[dashed]2[]{\code{ \textcolor {darkred}{n{=}0} : \{Done\} \vee  \textcolor {darkred}{n {\neq} 0} : \{Send\} \cdot \effect^{send}_{post} 
- \CONTAIN \textcolor {darkred}{n{\geq}0} : \_^\star \cdot\{Done\} \vee
- \textcolor {darkred}{n{<}0} :
-  \{Send\}^\omega}  }
-\end{prooftree}}
-\\~\\
-
-\hline
-
-\end{tabular}
-\end{adjustbox}
-            \vspace{0mm}
-\end{table*}
-}
-
 \subsubsection{Prove it when Reoccur}~\\
 
-      \vspace{-2mm}
+   %   \vspace{-2mm}
 %(\code{\{Go\} \Rightarrow \_})

### 2022-04-03 paper/tv.tex
m

@@
 
-Here, we regard \code{k} and \code{x} are meta-variables.
-\code{k^\tau} represents a constant of basic type \code{\tau}.
+Here, \code{c} is for integer constants, \code{b} is for boolean values, 
+ \code{mn} and \code{x} are for meta-variables.  
  \textbf{var} represents the countably infinite set of arbitrary distinct identifiers. 
-\anyevent{a} refers to a singleton event coming from the finite set of events \code{\Sigma}. 
-%Without loss of generality, any event can be further parametrized with constant values, e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events, leading to infinite alphabet.
+\code{ev} refers to a singleton event coming from the finite 
+set of events \code{\Sigma}. 
+%Without loss of generality, any event can be further parametrized with 
+%constant values, e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events. 
+%leading to infinite alphabet.
 We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
@@
 A program \code{\mathcal{P}} comprises a list of 
-%data type declarations \code{{datat^*}} and a list of 
+global values initializations \code{(x:=v)^*} and 
+a list of 
 method declarations \code{{meth^*}}. 
@@
 Each method \code{meth} has a name \code{mn}, an expression-oriented body \code{e}, also is associated with a precondition  \code{\effect_{pre}} and a postcondition \code{\effect_{post}} (the syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects}).
-The language allows each iterative loop to be optimized to an equivalent tail-recursive method, where mutation on parameters is made visible to the caller.
-The technique of translating away iterative loops is standard
+The language allows each iterative loop to be optimized to an equivalent 
+tail-recursive method, where mutation on parameters is made visible 
+to the caller. 
+%The technique of translating away iterative loops is standard
 %\citeref{insa2015automatic} 
-and is helpful
-in further minimising our core language. Expressions comprise unit (), 
-constants \code{k}, 
-variables \code{x}, 
+%and is helpful
+%in further minimising our core language.
+
+Expressions comprise simple values \code{v};
+a guarded process is written as \code{[b]e} where if b is true, 
+then it behaves as \code{e}, else it idles until \code{b} becomes true; 
 %one-level field access \code{v.f} (rather than \code{v.f1.f2...} for the sake of simplicity), 
 %data structure allocation \code{\textbf{new}\ d({v^*})},  
-local variable declaration \code{\tau\ x;\ e}, method calls \code{mn({x^*}) }, 
-variable assignments \code{x{:=}e}, 
+%local variable declaration \code{\tau\ x;\ e}, 
+method calls \code{mn({x^*})}; 
+variable assignments \code{x{:=}e}; 
 %field update \code{v.f:=e}, 
-expression sequences \code{e_1;e_2},
-conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2},
-event raises expression \code{ \textbf{event} [ev] },
+expression sequences \code{e_1;e_2};
+parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
+may communicate via multi-party event synchronization or shared variables; 
+conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}.
 
@@
     \code{%{datat^*}  \  
-   {meth^*}} 
-\qquad   \qquad\quad 
-    \m{(Basic\ Types)} \qquad  \code{\tau} \code{\quad  ::= \quad }
-     \code{int\ |\ bool\ |\ void}
+   ((x:=v)^*, {meth^*})} 
+%\qquad   \qquad\quad 
+ %   \m{(Basic\ Types)} \qquad  \code{b} \code{\quad  ::= \quad }
+  %   \code{int\ |\ bool\ |\ void}
     \\
@@
   \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
-  \code{\tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}}
+  \code{ mn  \ {(x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}}
+  \\
+  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
   \\
   \m{(Expressions)} &  \code{e}&\code{  ::= }&
-    \code{ ()\ |\ k^\tau\ |\ x\ |\ 
-    %v.f\ |\ 
-    %\textbf{new}\ d({v^*}) \ |\ 
-    \tau\ x;\ e \ |\ mn({x^*}) \ }
+    \code{ v \ | \ 
+    [b]\ e \ |\ mn({v^*}) \ }
   \code{|\ x{:=}e\ |\ 
  % v.f:=e \ | 
- \ e_1;e_2\ 
-  |\ {if}\ v\ {then}\ e_1\ {else}\ e_2 
+ \ e_1;e_2\ | \ e_1 || e_2 \ 
+  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 
  }  \\
@@
 | \ \textbf{event} [ev]\ 
-  | \ \textbf{delay}\ [d] \ 
-  | \ e_1\ \textbf{timeout}\  [d] \  e_2 \ 
-  | \ \textbf{deadline}  \ [d] \ e \  
+  | \ \textbf{delay} [d] \ 
+  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
+  | \ \textbf{deadline}  [d] \ e \  
   }  \\
@@
     \multicolumn{4}{c}{
-  \code{k^\tau:constant\ of\ type\ \tau\ } 
-  \qquad\quad
-\code{    x, mn  ::\in \textbf{var}}  
-\qquad\quad
- \code{(Events)  ev ::\in \Sigma 
-\qquad\quad
-\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{Z^+}}    
+ % \code{k^\tau:constant\ of\ type\ \tau\ } 
+ % \qquad\quad
+\code{c  \in \mathbb{Z}}
+\qquad \ \ 
+\code{b  \in \mathbb{B}}
+\qquad \ \ 
+\code{x, mn  ::\in \textbf{var}}  
+\qquad\ \ 
+ \code{(Events)  ev \in \Sigma 
+\qquad\ \ 
+\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
 }   
@@
   $
- \caption{A Core Imperative Language.} 
+ \caption{A Core First-Order Timed Imperative Language, \timedL.} 
  \label{fig:code_language}
-  \vspace{-1mm}
+
 \end{figure}
@@
 
-A number of timed process constructs can be used to capture common 
+Apart for the event raising expression \code{ \textbf{event} [ev] }, 
+a number of timed process constructs can be used to capture common 
 real-time system behavior patterns. Without loss of generality, we 
-assume d is an integer constant.  $\textbf{delay}\ [d]$ idles for exactly $d$ 
-time units. In process $e_1\ \textbf{timeout}\ [d] e_2$, the first observable event of 
+assume d is a non-negative integer constant.  $\textbf{delay} [d]$ idles for exactly $d$ 
+time units. In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
 $e_1$ shall occur before d time units elapse (since the process starts). 
 Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
-Process $\textbf{deadline}\ [d]\ e$ constrains $e$ to terminate before $d$ time units. 
+Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units. 
 In this setting, clock variables are 
@@
 
-\subsection{Semantics}
+\subsection{Semantics of the target language}
 \label{subsec:Targetlanguage_Semantics}

### 2022-04-03 paper/tv.tex
m

@@
 %We now give a summary of our techniques using running examples.
+
+\begin{figure}[ht]
+  \vspace{0mm}
+\begin{lstlisting}[columns=fullflexible]
+var x := -1; 
+var ct := 0;
+
+void process (int i)
+/* requires d1<d2,  emp 
+   ensures  true, (Update(i)#d1.emp#d2.([x=i]Critical(i).Exit(i) \/ emp))^* */
+{
+  [x=-1] active (i, 2, 3); 
+  deadline (event[Update(i)]{x := i}, d1);
+  delay (d2);
+  if (x=i) {
+    event[Critical(i)]{ct := ct +1};
+    event[Exit(i)]{ct := ct -1; x := -1};
+    process (i);
+  } else {
+    process (i);
+}
+
+void main () 
+/* requires true /\ emp 
+   ensures  true, (!Critical \/ (Critical(i) /\ i=x))^* */
+{ process(0) || process(1) || process(2); }
+\end{lstlisting}  
+  \vspace{0mm}
+  \caption{Dependent Values for Time Bounds).}\label{fig:overview_ficher}
+     \vspace{0mm}
+\end{figure}
 

### 2022-04-03 paper/tv.tex
no bugs after changing type

@@
 method calls \code{mn({x^*})}; 
-variable assignments \code{x{:=}e}; 
+%variable assignments \code{x{:=}e}; 
 %field update \code{v.f:=e}, 
@@
 conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}. 
+The expression \code{ \textbf{event} [\anyevent{A}(v)]\{(x:=v)^*\} } 
+raises an event \anyevent{A} parametrized with \code{v}, and takes a set of 
+assignment actions \code{(x:=v)^*}.
 
@@
     [b]\ e \ |\ mn({v^*}) \ }
-  \code{|\ x{:=}e\ |\ 
+  \code{| 
  % v.f:=e \ | 
  \ e_1;e_2\ | \ e_1 || e_2 \ 
-  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 
+  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
  }  \\
+&&& \code{ |\ \textbf{event} [\anyevent{A}(v)] \{(x{:=}v)^*\} }
+ \\
  &   & & \code{
-% |\ e_1}\ op\ \code{ e_2 \ 
-| \ \textbf{event} [ev]\ 
   | \ \textbf{delay} [d] \ 
@@
 \qquad\ \ 
- \code{(Events)  ev \in \Sigma 
+ \code{(Action\ labels)\ \anyevent{A}  \in \Sigma 
 \qquad\ \ 
@@
 
-Apart for the event raising expression \code{ \textbf{event} [ev] }, 
-a number of timed process constructs can be used to capture common 
+Furthermore, a number of timed process constructs can be used to capture common 
 real-time system behavior patterns. Without loss of generality, we 
@@
 \code{
-    \anyevent{A} (c)
-    \ | \ \anynotevent{A} (c)
+  \anyevent{A}(c, \pi, (x:=v)^*)
+    \ | \ \anynotevent{A} 
     \ | \ \_  
@@
    %\qquad
-    \code{c ::\in \mathbb{R}^{+}} 
+    \code{c ::\in \mathbb{Z}^{+}} 
      \qquad 

### 2022-04-04 paper/tv.tex
changed the type

@@
 {
-  [x=-1] active (i, 2, 3); 
+  [x=-1] 
   deadline (event[Update(i)]{x := i}, d1);
@@
     event[Critical(i)]{ct := ct +1};
-    event[Exit(i)]{ct := ct -1; x := -1};
+    event[Exit(i)]{ct := ct-1; x := -1};
     process (i);
@@
    ensures  true, (!Critical \/ (Critical(i) /\ i=x))^* */
+// ensures  true, (ct <= 1)^*
 { process(0) || process(1) || process(2); }
@@
   \vspace{0mm}
-  \caption{Dependent Values for Time Bounds).}\label{fig:overview_ficher}
+  \caption{Fischer's mutual exclusion algorithm.}\label{fig:overview_ficher}
      \vspace{0mm}

### 2022-04-05 code/src/program/coffee.c
no compilation errors

@@ -11,13 +11,13 @@ void oneSugar()
 
 void addSugar (int n) 
     /*
-    require TRUE/\(_^*).emp
+    require TRUE/\(_^*)
     ensure  (t>=n)/\ (Sugar #t)
     */
 {
 
     if (n == 0) { 
-        event ("Sugar");
+        event ["Sugar"];
     }
     else {
         timeout (oneSugar() , 1);
@@ -31,10 +31,10 @@ void makeCoffee (int n)
     ensure (t<=5/\t>=n/\t1<=3)/\Cup.(Sugar#t).(Coffee#t1).Done
     */
 {
-    event("Cup");
+    event["Cup"];
     deadline (addSugar(n), 5);
-    deadline (event("Coffee"), 3);
-    event("Done");
+    deadline (event["Coffee"], 3);
+    event["Done"];
 }
 
 

### 2022-04-05 paper/tv.tex
no compilation errors
m

@@
 For example, one safety property, \textit{"The event \anyevent{Done} 
-will be triggered no later than one second"}\footnote{For 
-simplicity, we use integer values to represent seconds in this 
+will be triggered no later than one time unit"}\footnote{Without loss of generality, 
+we use integer values to represent time units in this 
 paper, while it can bes extended to real numbers and other 
@@
 \begin{align*}
-&\code{\effect \defeq \  0 {\leq} t {<}1 : ({\_^\star} \cdot \anyevent{Done} ) \# t}.
+&\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \# t}.
 \end{align*}  
@@
 in metric temporal logic (MTL), reads \textit{"within one second, 
-\anyevent{Done} finally happens"}. Moreover, the time bounds can be dependent on the program inputs. For example, we express, the effects of \code{send(d)} as:
-\begin{align*}
-&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d) : ({\anyevent{Send} \# t)} \cdot \anyevent{Done}}.
-\end{align*}  
-The \code{send} method takes a parameter \code{d}, and \anyevent{Send}s 
-out a message at time \code{t}.  
-The above formula  \code{\effect^{send (d)}} indicates that the 
-input  \code{d} is positive and smaller or equal to \code{5}; the method 
-generates a finite trace, with the first event \anyevent{Send}, followed by 
-a second event \anyevent{Done}; and \anyevent{Send} takes a no more 
+\anyevent{Done} finally happens"}. Moreover, the time bounds 
+can be dependent on the program inputs. For example, as the program 
+shown in \autoref{fig:Value_dependent_intro}, we mark the precondition and postcondition
+using keywords \code{\emph{require}} and \code{\emph{ensure}} respectively.
+
+\newcommand{\codem}[1]{{\code{\emph{#1}}}}
+
+\begin{wrapfigure}{L}{0.4\columnwidth}
+  \vspace{-2mm}
+\begin{lstlisting}
+void addSugar (int n) 
+/*require n>=0 , _^*
+  ensure  t>=n, Sugar#t */
+{ if (n == 0) { 
+    event ["Sugar"];} 
+  else {
+    timeout (oneSugar() , 1);
+    addSugar (n-1);}} 
+\end{lstlisting}
+\vspace{-1mm}
+\caption{Value-dependent specification.} 
+\label{fig:Value_dependent_intro}
+\vspace{-1mm}
+\end{wrapfigure}
+
+The function 
+\code{\emph{addSugar}} is intended to takes a parameter \codem{n}, representing 
+the portion of the sugar we need to add. When \codem{n} decreases to \codem{0}, 
+it simply raises an event \anyevent{Sugar} to mark the end of the process. 
+Otherwise, it adds one portion of the sugar then recursively calls \code{\emph{addSugar}} with parameter \codem{n-1}. 
+Statement \codem{timeout(e, d)} sets a timer which executes code \codem{e} once the timer expires at time \codem{d}. 
+Therefore, the time spent on adding one portion of the sugar is no less than 1 time unit.
+
+The specifications of  \codem{addSugar(n)} indicates that the 
+input  \code{n} is non-negative; the method 
+generates a finite trace where \anyevent{Sugar} takes a no less 
 than \code{d} milliseconds delay to finish. 
@@
 value-dependent 
-time bounds. Intuitively, if traditional timed automata define an 
+time bounds, which is beyond the capability of Timed Automata. Intuitively, if traditional Timed Automata define an 
 \emph{exact} transition system, \timedEffects\ define 
@@
 
-   %they already illustrate the gain of expressiveness from  existing temporal logics and traditional timed automata.
-
-%properties beyond
+\begin{comment}
+  we express, the effects of \code{send(d)} as:
+\begin{align*}
+&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \# t)} \cdot \anyevent{Done}}.
+\end{align*}  
+effects of \code{addSugar(n)} as:
+\code{(n{>}0  \wedge  t {\geq} n) : ({\anyevent{Sugar} \# t)}}
+
+\end{comment}
+
+   %they already illustrate the gain of expressiveness from  existing temporal logics and traditional Timed Automata.
+
+%properties
 
@@
 Existing automatic verification techniques massively rely on 
-the timed automata which requires manually cast of clock variables with 
+the Timed Automata which requires manually cast of clock variables with 
 carefully calculated clock constraints.
@@
     \code{%{datat^*}  \  
-   ((x:=v)^*, {meth^*})} 
+   (\alpha^*, {meth^*})} 
 %\qquad   \qquad\quad 
@@
   %   \code{int\ |\ bool\ |\ void}
+    \\
+    \m{(Assignment)} &  \code{\alpha }&\code{  ::= }&
+    \code{x:=v} 
    \\
@@
  \ e_1;e_2\ | \ e_1 || e_2 \ 
-  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
+ % |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
+ |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
  }  \\
-&&& \code{ |\ \textbf{event} [\anyevent{A}(v)] \{(x{:=}v)^*\} }
- \\
+
  &   & & \code{
@@
 \code{
-  \anyevent{A}(c, \pi, (x:=v)^*)
+  \anyevent{A}(v, \pi, \alpha^*)
     \ | \ \anynotevent{A} 
@@
 }
-
-%    \\
-%        \m{(Real\ Time)} &  \mathcal{O} &\code{::= }&
-%    
-%    \code{
-%   %n \ | \ 
-%   c \ | \ (c, {+}\infty) \ | \  [0, c) \ | \  \mathcal{O}_1 \wedge \mathcal{O}_2 \ | \  \mathcal{O}_1 \vee \mathcal{O}_2
-%    }
 
@@
 %The core implementation is less than 3500 LOC, roughly, 1{+} LOC for the verifier, and 2{+} LOC for the TRS. We prove the soundness of the TRS. 
-%Next, we show case studies to demonstrate the feasibilities of our \timedEffects comparing to timed automata.
+%Next, we show case studies to demonstrate the feasibilities of our \timedEffects comparing to Timed Automata.
 
@@
 
-Our implementation is the first that solves the  inclusion problem of symbolic timed automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i.
-e., whose timing constants are not known yet), and hence cannot be used in early design phases; ii) verifying a system for a set of timing constants usually requires to enumerate all of them one by one if they are supposed to be integer-valued; in addition, timed automata cannot be used to verify a system for a set of timing constants that are to be taken in a real-valued dense interval.
+Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i.
+e., whose timing constants are not known yet), and hence cannot be used in early design phases; ii) verifying a system for a set of timing constants usually requires to enumerate all of them one by one if they are supposed to be integer-valued; in addition, Timed Automata cannot be used to verify a system for a set of timing constants that are to be taken in a real-valued dense interval.
 
@@
 %
-%compare to timed automata:
+%compare to Timed Automata:
 %modular and can plug in anywhere. 

### 2022-04-05 paper/tv.tex
m

@@
 time measurement units.}, is expressed in \timedEffects\ as: 
-\begin{align*}
-&\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \# t}.
-\end{align*}  
+\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \# t}.
+%\begin{align*}
+%&\end{align*}  
 %The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
@@
 
-\begin{wrapfigure}{L}{0.4\columnwidth}
+\begin{wrapfigure}{L}{0.39\columnwidth}
   \vspace{-2mm}
@@
 void addSugar (int n) 
-/*require n>=0 , _^*
+/*require n>=0, _^*
   ensure  t>=n, Sugar#t */
@@
 Otherwise, it adds one portion of the sugar then recursively calls \code{\emph{addSugar}} with parameter \codem{n-1}. 
-Statement \codem{timeout(e, d)} sets a timer which executes code \codem{e} once the timer expires at time \codem{d}. 
-Therefore, the time spent on adding one portion of the sugar is no less than 1 time unit.
+The use of statement \codem{timeout(e, d)} is standard, 
+which sets a timer which executes code \codem{e} once the timer 
+expires at time \codem{d}. 
+Therefore, the time spent on adding one portion of the sugar is 
+no less than 1 time unit.
 
@@
 %leading to infinite alphabet.
-We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
+%We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
 %Each events raising expression \code{\textbf{event}} is parametrized with an event, to trigger such a single event. 
 A program \code{\mathcal{P}} comprises a list of 
-global values initializations \code{(x:=v)^*} and 
+global values initializations \code{\alpha^*} and 
 a list of 
@@
 %data structure allocation \code{\textbf{new}\ d({v^*})},  
-%local variable declaration \code{\tau\ x;\ e}, 
+%local variable declaration \code{\alpha; e}, 
 method calls \code{mn({x^*})}; 
-%variable assignments \code{x{:=}e}; 
+variable assignments \code{\alpha}; 
 %field update \code{v.f:=e}, 
@@
 parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
-may communicate via multi-party event synchronization or shared variables; 
-conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}. 
-The expression \code{ \textbf{event} [\anyevent{A}(v)]\{(x:=v)^*\} } 
-raises an event \anyevent{A} parametrized with \code{v}, and takes a set of 
-assignment actions \code{(x:=v)^*}.
+may communicate via multi-party event synchronization or shared variables. 
+%conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}. 
+The expression \code{ \textbf{event} [\anyevent{A}(v)] } 
+raises an event \anyevent{A} parametrized with \code{v}. 
+%and takes a set of 
+%assignment actions \code{(x:=v)^*}. 
+Furthermore, a number of timed process constructs can be used to capture common 
+real-time system behavior patterns. Without loss of generality, we 
+assume d is a non-negative integer constant.  $\textbf{delay} [d]$ idles for exactly $d$ 
+time units. In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
+$e_1$ shall occur before d time units elapse (since the process starts). 
+Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
+Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units.
 
@@
     \code{ v \ | \ 
+    \alpha  \ | \ 
     [b]\ e \ |\ mn({v^*}) \ }
@@
  % |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
- |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
+ |\ \textbf{event} [\anyevent{A}(v)] 
  }  \\
@@
   $
- \caption{A Core First-Order Timed Imperative Language, \timedL.} 
+ \caption{A core first-order imperative language with timed constructs, \timedL.} 
  \label{fig:code_language}
@@
 
-Furthermore, a number of timed process constructs can be used to capture common 
-real-time system behavior patterns. Without loss of generality, we 
-assume d is a non-negative integer constant.  $\textbf{delay} [d]$ idles for exactly $d$ 
-time units. In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
-$e_1$ shall occur before d time units elapse (since the process starts). 
-Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
-Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units. 
-In this setting, clock variables are 
+We remark additional process constructs (e.g. if-then-else, while, etc.) 
+can be defined using the above. In this setting, clock variables are 
 made implicit and hence they cannot be compared with each other 
@@
 
-A transition of the system is of the form $c \xrightarrow[]{\text{x}} c^\prime$ where $c$ and $c^\prime$ are 
+A transition of the system is of the form $c \xrightarrow[]{l} c^\prime$ where $c$ and $c^\prime$ are 
 the system configurations before and after the transition respectively. 
-We adopt the following naming convention for transition labels: 
-$t$ denotes a non-negative real number; $\tau$ denotes an invisible event;
-For instance, $c \xrightarrow[]{\text{t}} c^\prime$ denotes a transition of $t$ time units elapsing. 
+Transition labels \code{l} consist: 
+%We adopt the following naming convention for transition labels: 
+$t$, denoting a non-negative real integer; 
+$\tau$, denoting an invisible event;
+$\anyevent{A} \in \Sigma $ is an observable 
+event; and $\sigma \in \Sigma\cup \{\tau\}$. 
+For instance, $c \xrightarrow[]{\text{t}} c^\prime$ denotes a transition of \codem{t} time units elapsing. 
 In the following, we present the firing rules which are associated with 
 the timed process constructs.
+
 \begin{flalign*}
@@
   t {\leq} d 
-}{(V, \textbf{delay}\ [d]) \xrightarrow[]{\text{t}} (V, \textbf{delay}\ [d \text{-}t])}\ [de1]} 
+}{(V, \textbf{delay}[d]) \xrightarrow[]{\text{t}} (V, \textbf{delay} [d \text{-}t])}\ [de_1]} 
 \qquad \qquad 
 \code{\frac{
-}{(V, \textbf{delay}\ [0]) \xrightarrow[]{\tau} (V, ())}\ [de2]} 
+}{(V, \textbf{delay} [0]) \xrightarrow[]{\tau} (V, ())}\ [de_2]} 
 \end{flalign*}
 
+The above captures behaviors of process \code{\textbf{delay}[d]}. 
+Rule \code{de_1} states that the process may idle for 
+any amount of time as long as it is less than or equal to \codem{d} time units; 
+Rule \code{de_2} states that the process terminates immediately after 
+\codem{d} becomes \codem{0}.
 \begin{flalign*}
@@
 \code{\frac{
-  (V,e_1) \xrightarrow[]{\text{e}} (V^\prime,e_1^\prime)
-}{(V, e_1\ \textbf{timeout} \  [d] \ e_2) \xrightarrow[]{\text{e}} (V^\prime,e^\prime)}\ [to1]} 
+  (V,e_1) \xrightarrow[]{\anyevent{A}} (V^\prime,e_1^\prime)
+}{(V, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\anyevent{A}} (V^\prime,e^\prime)}\ [to_1]} 
 \quad  
 \code{\frac{
-  (V,e) \xrightarrow[]{\tau} (V^\prime,e^\prime)  \quad (t {\leq} d)
-}{(V, e_1\ \textbf{timeout} \  [d] \ e_2) \xrightarrow[]{\text{t}} (V, \textbf{timeout}\ e^\prime \ [d \text{-}t])}\ [to2]} 
+  (V,e_1) \xrightarrow[]{\tau} (V^\prime,e_1^\prime)  
+}{(V, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (V^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [to_2]} 
 \\
@@
   (V,e_1) \xrightarrow[]{\text{t}} (V,e_1^\prime)  \quad (t {\leq} d) 
-}{(V, e_1\ \textbf{timeout} \ [d] \ e_2) \xrightarrow[]{\text{t}} (V,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [to3]} 
+}{(V, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (V,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [to_3]} 
 \quad  
 \code{\frac{
-}{(V, e_1\ \textbf{timeout} \  [0] \ e_2) \xrightarrow[]{\tau} (V, e_2)}\ [to4]} 
+}{(V, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (V, e_2)}\ [to_4]} 
 \end{flalign*}
-
+If an observable event \anyevent{A} can be engaged by \code{e_1}, 
+then \code{e_1\ \textbf{timeout}[d]\ e_2} becomes \code{e_1^\prime} (rule \code{[to_1]}). 
+An invisible transition does 
+not solve the choice (rule \code{[to_2]}). 
+If \code{e_1} may idle for less than or equal 
+to \codem{d} time units, so is the composition (rule \code{[to_3]}). 
+When \codem{d} becomes \codem{0}, 
+\code{e_2} takes over control by a silent transition (rule \code{[to_4]}).
 \begin{flalign*}
@@
 \code{\frac{
-  (V,e) \xrightarrow[]{\text{x}} (V^\prime,e^\prime)
-}{(V, \textbf{deadline}\  [d] \ e ) \xrightarrow[]{\text{x}} (V^\prime, \textbf{deadline} \ [d] \ e^\prime)}\ [dl1]} 
-\quad  
+  (V,e) \xrightarrow[]{\anyevent{A}} (V^\prime,e^\prime)
+}{(V, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (V^\prime, \textbf{deadline}  [d] \ e^\prime)}\ [dl_1]} 
+\  
 \code{\frac{
   (V,e) \xrightarrow[]{\text{t}} (V,e^\prime)  \quad (t {\leq} d)
-}{(V, \textbf{deadline} \  [d]\ e ) \xrightarrow[]{\text{t}} (V, \textbf{deadline} \ [d \text{-}t] \ e^\prime )}\ [dl2]} 
+}{(V, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (V, \textbf{deadline}  [d \text{-}t] \ e^\prime )}\ [dl_2]} 
 \end{flalign*}
+
+Intuitively, \code{\textbf{deadline}\  [d] \ e} behaves exactly as 
+\code{e} except that it must terminate before \codem{d} time units.
 

### 2022-04-05 paper/tv.tex
m

@@
 \acmMonth{1}
+
 \acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
@@
 \newcommand{\m}{\mathit} 
+\newcommand{\lappend}{\mathrel{\texttt{++}}}
+
 \newcommand{\toolName}{Tvide}
@@
 generates a finite trace where \anyevent{Sugar} takes a no less 
-than \code{d} milliseconds delay to finish. 
+than \code{d} time units delay to finish. 
 Although these examples are simple, they show the benefits of deploying 
@@
 @*/}}}) for each program, which leads to a compositional verification strategy, where static checking and timed temporal verification can be done locally.
-%The set of signals to be present in one logical time instance are represented within one \code{\_}.
+%The set of signals to be present in one logical event are represented within one \code{\_}.
 
@@
 The precondition \code{d{>}3 : \{
-\}^\star \cdot\{\m{Login}\} } requires that the input variable \code{d} is greater than 3, and before entering into this module, the signal \anyevent{Login} should be emitted at the last time instance, indicating that a login request has been sent.
-The postcondition contains two parts and connected using the disjunction mark \code{{\vee}}: when \code{3{<}t{<}d}, the effects contains two time instances, \code{\{\m{Connecting}\}} and \code{\{\m{Connected}\}}, while the first  time instance finishes at time \code{t}, %(assuming to reset the clock when executing the module),
-which is no later than \code{\m{d}} milliseconds; otherwise, the effects contains one time instance \code{\{Connecting\}} which finishes at time \code{d}. \emph{(See a demo from \cite{CODE1})}
+\}^\star \cdot\{\m{Login}\} } requires that the input variable \code{d} is greater than 3, and before entering into this module, the signal \anyevent{Login} should be emitted at the last event, indicating that a login request has been sent.
+The postcondition contains two parts and connected using the disjunction mark \code{{\vee}}: when \code{3{<}t{<}d}, the effects contains two time instances, \code{\{\m{Connecting}\}} and \code{\{\m{Connected}\}}, while the first  event finishes at time \code{t}, %(assuming to reset the clock when executing the module),
+which is no later than \code{\m{d}} time units; otherwise, the effects contains one event \code{\{Connecting\}} which finishes at time \code{d}. \emph{(See a demo from \cite{CODE1})}
 
@@
 The precondition of {\ttfamily{main}} requires no arithmetic constraints on its input values (expressed as \code{\m{true}}), neither any pre-traces  (expressed as \code{\m{emp}} or \code{\epsilon}, indicating an empty trace).
-The postcondition ensures a trace, where the second time instance contains at least one signal \code{\anyevent{Cook}} and finishes within 3 milliseconds after the completion of the first time instance.
+The postcondition ensures a trace, where the second event contains at least one signal \code{\anyevent{Cook}} and finishes within 3 time units after the completion of the first event.
 Then we do not care about the rest of the trace (\code{\_} is similar to a wildcard).
@@
 %(with a question mark) 
-%followed by a new empty time instance
+%followed by a new empty event
  to the current effects. 
-%The effects state (3) is obtained by [FV-Emit], which simply adds  %concatenates an empty time instance to the current effects. %to be the new current state. 
-The effects states (3) and (5) are obtained by [FV-Emit], which simply adds the emitted  signal to the current time instance. The intermediate effects state of (7) is obtained by [FV-Call]. 
+%The effects state (3) is obtained by [FV-Emit], which simply adds  %concatenates an empty event to the current effects. %to be the new current state. 
+The effects states (3) and (5) are obtained by [FV-Emit], which simply adds the emitted  signal to the current event. The intermediate effects state of (7) is obtained by [FV-Call]. 
 Before each function call, it invokes the TRS to check whether the current effects state satisfies the precondition of the callee module.
 If it is not satisfied, the verification fails, otherwise it concatenates the callee's postcondition to the current effects state.
-The final effects state of (7) is obtained by [FV-Async], which adds a new time instance \code{\{Ready\}} to the current effects state, indicating that the asynchronous program has been resolved.
+The final effects state of (7) is obtained by [FV-Async], which adds a new event \code{\{Ready\}} to the current effects state, indicating that the asynchronous program has been resolved.
 In step (8), we parallel compose the effects from both of the branches, and normalize the final effects. 
@@
 
-Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\# t}(\effect)} is the partial derivative of \code{\effect} w.r.t the time instance \code{I} and time bound \code{t}.
+Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\# t}(\effect)} is the partial derivative of \code{\effect} w.r.t the event \code{I} and time bound \code{t}.
 
@@
 %property \code{\effect^\prime  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\# t)\cdot\_^\star}, 
-%where \code{\effect^\prime} simply indicates that the signal \anyevent{Cook} needs to happen at the second time instance, and takes no more than \code{3} milliseconds after the first time instance has completed; and \code{\_^\star} means we do not care the rest of the traces.
+%where \code{\effect^\prime} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces.
 We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.
@@
       \vspace{0mm}
-\caption{\label{tab:rewriting_tree_send} The inclusion proving example. (For simplicity, we use 3 seconds to replace the 3 milliseconds.)}
+\caption{\label{tab:rewriting_tree_send} The inclusion proving example. }
 
@@
 
-Note that time instance \code{\{Prep\}} entails \code{\_} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
+Note that event \code{\{Prep\}} entails \code{\_} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
 Intuitively, we use \code{[DISPROVE]} wherever the left-hand side (LHS) is \emph{nullable}\footnote{If the event sequence is possibly empty, i.e.
@@
 In step \code{\textcircled{4}}, in order to conduct a further unfolding, we unify time variables \code{t_L^2} and \code{t_R} by adding the constraint \code{t_L^2 {=} t_R}. 
-In step \code{\textcircled{5}}, from the RHS, since \code{\_^\star {=} emp \vee \_ \cdot \_^\star}, eliminating one time instance \code{\{Ready\}} from it will lead to \code{\bot \vee \_^\star}, which can be normalised into \code{\_^\star} in step \code{\textcircled{6}}.
+In step \code{\textcircled{5}}, from the RHS, since \code{\_^\star {=} emp \vee \_ \cdot \_^\star}, eliminating one event \code{\{Ready\}} from it will lead to \code{\bot \vee \_^\star}, which can be normalised into \code{\_^\star} in step \code{\textcircled{6}}.
 At the end of the rewriting, we manage to prove that \code{(t_L {<}3 {\wedge} t_L^1 {+} t_L^2 {=}t_L {\wedge}t_L^2 {=} t_R)  \Rightarrow  t_R {<} 3} \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
@@
 event; and $\sigma \in \Sigma\cup \{\tau\}$. 
-For instance, $c \xrightarrow[]{\text{t}} c^\prime$ denotes a transition of \codem{t} time units elapsing. 
+For event, $c \xrightarrow[]{\text{t}} c^\prime$ denotes a transition of \codem{t} time units elapsing. 
 In the following, we present the firing rules which are associated with 
@@
 
-    \m{(Timed\ Effects)} &  \effect &\code{\  ::=\ }&
+    \m{(Timed\ Effects)} &  \effect &\code{  ::= }&
     \code{
@@
     \\
- \m{(Timed \ Sequence)}  & \ \code{\es}   &\code{\ ::=\ }&
+ \m{(Timed \ Sequence)}  & \ \code{\es}   &\code{ ::=}&
 
@@
 \\
-\m{(Events)} & ev  & \ ::= \ & 
+\m{(Events)} & ev  &  ::=  & 
 \code{
@@
 
-    \m{(Pure)}  & \code{\code{\pure{\pi}}}&\code{\  ::=\ }&
+    \m{(Pure)}  & \code{\code{\pure{\pi}}}&\code{  ::= }&
 \pure{ \pure{True}}
@@
    \ | \ \pure{A(}{t_1, t_2}\pure{)}
-  \   | \  \pure{\pure{\pi_1}} \wedge \code{\pure{\pi}}_2
-   \  | \ \pure{\pure{\pi_1}} \vee \code{\pure{\pi}}_2
-   \  | \ \neg\code{\pure{\pi}}
-
-    \\
-
-    & &&\code{
-       | \  \pure{\pure{\pi_1}} \Rightarrow \pure{\pure{\pi_2}}
-   \  | \ \forall x. \code{\pure{\pi}}
-   \  | \ \exists x. \code{\pure{\pi}}
-   }\\
-
-    \m{(Real\text{-}Time\ Term)}  & \code{t} &\code{\  ::=\ }&
+  \  |   \pure{\pure{\pi_1}} {\wedge} \code{\pure{\pi}}_2
+   \ |  \pure{\pure{\pi_1}} {\vee} \code{\pure{\pi}}_2
+   \ |  \neg\code{\pure{\pi}}
+  \  |   \pure{\pure{\pi_1}} {\Rightarrow} \pure{\pure{\pi_2}}
+   \ |  \forall x. \code{\pure{\pi}}
+   \ |  \exists x. \code{\pure{\pi}}
+
+    \\
+
+    \m{(Real\text{-}Time\ Term)}  & \code{t} &\code{  ::= }&
     \code{ c
@@
    %\qquad
-    \code{c ::\in \mathbb{Z}^{+}} 
-     \qquad 
+    \code{c ::\in \mathbb{Z}} 
+     \qquad \qquad 
            \code{x  ::\in \textbf{var} } 
-           \qquad
+           \qquad\qquad
 
      \m{(Real\ Time\ Bound)}\ \code{\#}
-     \qquad
+     \qquad \qquad 
         \m{(Kleene\ Star) \ \star}
@@
 
-The  syntax of the \timedEffects is formally defined in \figref{fig:Syntax_of_Types_and_Effects} Effects is  a conditioned time  instance sequence \code{\pure{\pi} : \es} or a disjunction of two effects $\effect_1 \vee \effect_2$.
+The  syntax of the \timedEffects is formally defined in 
+\figref{fig:Syntax_of_Types_and_Effects} Effects is 
+ a conditioned time  event sequence \code{\pure{\pi},  \es} or a disjunction of two effects $\effect_1 \vee \effect_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
  an empty trace $\empt$;
-a single time instance represented by \code{I};
-a waiting for a single signal \code{\textbf{S}?};
+a single event \code{ev};
   %where \anyevent{a} is an element from a finite set of events, donated by \code{\Sigma};
@@
 disjunction  \code{\es_1\vee \es_2};
-synchronous parallelism   \code{\es_1 || \es_2}.
-%negation \code{\neg \es};
- %
-
+parallel composition of two processes is written as \code{\es_1 || \es_2}, where \code{es_1} and \code{es_2} 
+may communicate via multi-party event synchronization or shared variables. 
 We introduce a new operator \code{\#}, and the effects \code{\es \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
 A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace.
+
+\code{\anyevent{A}(v, \pi, \alpha^*)} stands for an event labeled 
+as \anyevent{A} with parameter \code{v}, guard \code{\pi} and assignment operations \code{\alpha^*}. 
+To make the specification more expressive, events can also be 
+\code{\anynotevent{A}}, representing  events which are not 
+labeled using \anyevent{A}; and a wildcard \code{\_}, which matches to all the events.
 
@@
 
+To define the model, 
+\code{var} is the set of program variables, 
+\code{val} is the set of primitive values, 
+\code{\es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
+Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
+the effects \code{\effect} take exactly \code{d} time units to complete; 
+the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
+temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
+from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
+\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{[ev]} \ .
+
+As shown in \figref{fig:Sementic}, we define the semantics of our effects. 
+We use $\lappend$ to represent the append operation of two event sequences. 
+We use $[]$ to represent the empty sequence, \code{[ev]} to represent 
+the sequence only contains a singleton event.
+
+\begin{figure}[]
+  \vspace{-1mm}
+  \renewcommand{\arraystretch}{1.1}
+\small\begin{align*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%     Disjunction        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \effect_1 \vee \effect_2}  
+&\m{iff}\quad & \code{d, s, \varphi \models \effect_1 } \ 
+or\ \code{d, s, \varphi \models \effect_2 }  \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%         Empty          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s,  \varphi \models \pure{\pi}  , \empt}  
+&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
+\pure{True} } \ and\  \code{ \varphi {=} [] }\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%         Event          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi}  , ev }  
+&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
+\pure{True} }\ and \ \varphi {=} [ev]  \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%   s  Concatenate        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi}, (\es_1\cdot\es_2)}  
+&\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
+\code{ \varphi_1 {\lappend} \varphi_2 {=} \varphi}\ and\ 
+\exists \code{d_1,d_2}. \  
+\code{ d_1 {+} d_2 {=} d} \ 
+  and \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
+\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    disjunction         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi}  , (\es_1\vee\es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , \es_2 } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    t times         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&
+\code{d, s, \varphi \models \pure{\pi}  ,\es\# t}  &\m{iff}\quad &
+ \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
+ \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or  \\
+& & &  \code{\llbracket \pure{\pi}  , t {>} 0 \rrbracket_{s} {=}  
+\pure{True} }, 
+\  \exists \code{\varphi_1,\varphi_2}. \  \code{ \varphi_1 \lappend  \varphi_2 {=} \varphi}
+\  and \ \code{d, s, \varphi_1 \models \pure{\pi}  , \es } \\
+& & & \quad and \ \code{d, s, \varphi_2  \models (\pure{\pi}  , t {>} 0) \wedge  \es^{t\text{-}1} } \\
+&\code{d, s, \varphi \models \pure{\pi}, \es^\star}  &\m{iff}\quad & there\ exist\ \code{\varphi_1,\varphi_2}
+\   and \  \code{ \varphi_1 {+}{+} \varphi_2 {=} \varphi} 
+ \  and \ \code{d, s, \varphi_1 \models \pure{\pi} , \es } 
+ \   and \ \code{d, s, \varphi_2 \models \pure{\pi} , \es^\star }\\
+& \code{d, s, \varphi \models false}  &\m{iff}\quad &
+ \code{\llbracket \pure{\pi}  \rrbracket_{s} {=} \pure{False} } \ or \ \code{\varphi {=} \bott}
+\end{align*}
+  \vspace{-2mm}
+\caption{Semantics of \timedEffects .}
+\label{fig:Sementic}
+\vspace{-2mm}
+\end{figure}
+
+\begin{comment}
+
 \begin{figure}[ht]
@@
 & {\tt{SAT}(\pi)}  \ and \ \exists \code{\varphi_1, \varphi_2, d_1, d_2}\ and\ \code{
-\varphi {=} \varphi_1 {+}{+} \varphi_2, d {=} d_1 {+} d_2 \ and 
+\varphi {=} \varphi_1 \lappend \varphi_2, d {=} d_1 {+} d_2 \ and 
 }\\
@@
 To define the semantic model, 
-we use \code{\varphi} (\emph{a trace of sets of signals})  to represent the computation execution (or time-instance multi-trees, per se), indicating the sequential constraint of the temporal behaviour; and we use \code{d} to record the computation duration of given effects.
+we use \code{\varphi} (\emph{a trace of events}) to represent 
+the computation execution (or events multi-trees, per se), indicating 
+the sequential constraint of the temporal behaviour; and we use \code{d} 
+to record the computation duration of given effects. 
 Let \code{d, \varphi \models \effect} denote the model relation, i.e., 
-the effects \code{\effect} take exactly \code{d} milliseconds to complete; and 
+the effects \code{\effect} take exactly \code{d} time units to complete; and 
 the linear temporal sequence \code{\varphi} satisfies the sequential time  instances defined from \code{\effect}, with \code{d}, \code{\varphi} from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{Z^+}} and \code{\varphi}   {\defeq}\ \code{list\ of\ I} (a sequence of time instances).
@@
 $[]$ to represent the empty sequence;
-${+}{+}$ to represent the append operation of two traces;
-\code{[I]} to represent the sequence only contains one time instance.
+$\lappend$ to represent the append operation of two traces;
+\code{[I]} to represent the sequence only contains one event.
 \code{{\tt{SAT}(\pi)} } indicates the pure \code{\pi} is satisfiable, which is discharged by the constraint solver Z3 \cite{de2008z3}.
 
-%The signals shown in one time instance  represent the \emph{minimal} set of signals which are required/guaranteed to be there. An empty set \code{\_} represents any set of signals
+%The signals shown in one event  represent the \emph{minimal} set of signals which are required/guaranteed to be there. An empty set \code{\_} represents any set of signals
+
+\end{comment}
 
@@
 
-Let \code{\Pi} represents the pure constraints for all the terms; \code{H} represents the trace of \emph{history}; \code{C} represents the \emph{current} time instance or a waiting signal; 
+Let \code{\Pi} represents the pure constraints for all the terms; \code{H} represents the trace of \emph{history}; \code{C} represents the \emph{current} event or a waiting signal; 
 \code{T} is a term binding \code{C}; 
@@
 Next we provide the definitions and implementations of auxiliary functions \emph{Nullable}(\code{\delta}), \emph{First}(\code{fst}) and \emph{Derivative}(\code{D}) respectively.
-Intuitively, the Nullable function \code{\delta(\es)} returns a boolean value indicating whether \code{\es} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \es)} computes a set of possible initial time instances of \code{\pure{\pi} : \es}; and the Derivative function \code{D_{I\# t}^{\pure{\pi}}(\es)} computes a next-state effects after eliminating one time instance \code{I} w.r.t.
+Intuitively, the Nullable function \code{\delta(\es)} returns a boolean value indicating whether \code{\es} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \es)} computes a set of possible initial time instances of \code{\pure{\pi} : \es}; and the Derivative function \code{D_{I\# t}^{\pure{\pi}}(\es)} computes a next-state effects after eliminating one event \code{I} w.r.t.
 the execution time \code{t} from the current effects \code{\pure{\pi} : \es}.
@@
 w.r.t.
-a time instance \code{(I, \pi^\prime, t^\prime)} computes the  effects for the left quotient \code{(I, \pi^\prime, t^\prime)^{\text{-}1}\llbracket \pi : \es \rrbracket}.
+a event \code{(I, \pi^\prime, t^\prime)} computes the  effects for the left quotient \code{(I, \pi^\prime, t^\prime)^{\text{-}1}\llbracket \pi : \es \rrbracket}.
 \footnote{For understanding of the derivative rule for \code{es\# t} (cf.
@@
 %        \vspace{-2mm}
-%\caption{\label{tab:Experimental} The experiments are based on 16 real world C programs, we record the lines of code (LOC), the number of testing temporal properties ($\#$Prop.), and the (dis-) proving times (in milliseconds) using PAT and our T.r.s respectively.
+%\caption{\label{tab:Experimental} The experiments are based on 16 real world C programs, we record the lines of code (LOC), the number of testing temporal properties ($\#$Prop.), and the (dis-) proving times (in time units) using PAT and our T.r.s respectively.
 }
@@
 %in . 
-In step \code{\textcircled{2}} of the first sub-tree, in order to eliminate the first instance \code{\{B\}}, \code{\{A\}^\star \# t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
+In step \code{\textcircled{2}} of the first sub-tree, in order to eliminate the first event \code{\{B\}}, \code{\{A\}^\star \# t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
 % is 
@@
 %Formally, given a KA is \code{(A,+,\cdot, \star,  0, 1)}, a SKA over a finite set \code{A_B} is \code{(A,+, \cdot, \times, \star,  0, 1,  A_B)}, \code{A_B {\subseteq} A}. 
-%Our \code{\bot} corresponds to the \code{0}; our \code{\empt} corresponds to the \code{1}; our \emph{time instance} containing simultaneous signals can be expressed via \code{\times};
+%Our \code{\bot} corresponds to the \code{0}; our \code{\empt} corresponds to the \code{1}; our \emph{event} containing simultaneous signals can be expressed via \code{\times};
 
@@
 - To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \es_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \es_2}}.
-For an arbitrary time instance \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and
+For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and
 \codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \es_2 \rrbracket}.

### 2022-04-05 paper/tv.tex
m

@@
 \usepackage{cancel}
-\newcommand{\env}{\code{\mathcal{E}}}
+\newcommand{\env}{\code{\mathcal{S}}}
 
@@
   \vspace{-1mm}
-  \renewcommand{\arraystretch}{1.1}
+  \renewcommand{\arraystretch}{1.2}
 \small\begin{align*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%   s  Concatenate        %%
+%%     Concatenate        %%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \exists \code{d_1,d_2}. \  
-\code{ d_1 {+} d_2 {=} d} \ 
-  and \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
+\code{ d_1 {+} d_2 {=} d} \\
+&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
 \ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  , (\es_1\vee\es_2)}  
+&\code{d, s, \varphi \models \pure{\pi}  , (\es_1{\vee}\es_2)}  
 &\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    parallel         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}\es_1)||(ev_2{\cdot}\es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (\es_1||(ev_2{\cdot}\es_2)) } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}\es_1)||es_2)  } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    parallel  2        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi} , (ev\#t_1) || (\epsilon \# t_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {\geq}t_2)}, (ev\#t_1) } 
+\ or\ \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {<}t_2)}  , (ev\#t_1){\cdot}(\epsilon \# (t_2\text{-}t_1))  } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%    t times         %%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&
-\code{d, s, \varphi \models \pure{\pi}  ,\es\# t}  &\m{iff}\quad &
+&\code{d, s, \varphi \models \pure{\pi}  ,\es\# t}  &\m{iff}\quad &
  \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
  \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or  \\
-& & &  \code{\llbracket \pure{\pi}  , t {>} 0 \rrbracket_{s} {=}  
+& & &  \code{\llbracket \pure{\pi}, t {>} 0 \rrbracket_{s} {=}  
 \pure{True} }, 
-\  \exists \code{\varphi_1,\varphi_2}. \  \code{ \varphi_1 \lappend  \varphi_2 {=} \varphi}
-\  and \ \code{d, s, \varphi_1 \models \pure{\pi}  , \es } \\
-& & & \quad and \ \code{d, s, \varphi_2  \models (\pure{\pi}  , t {>} 0) \wedge  \es^{t\text{-}1} } \\
-&\code{d, s, \varphi \models \pure{\pi}, \es^\star}  &\m{iff}\quad & there\ exist\ \code{\varphi_1,\varphi_2}
-\   and \  \code{ \varphi_1 {+}{+} \varphi_2 {=} \varphi} 
- \  and \ \code{d, s, \varphi_1 \models \pure{\pi} , \es } 
- \   and \ \code{d, s, \varphi_2 \models \pure{\pi} , \es^\star }\\
+\  \exists \code{\es_1,\es_2}. \  \code{ es_1 {\cdot}  es_2 {=} es}\\
+&&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi {\wedge}t_1{+} t_2{=}t)}  , 
+(es_1\#t_1) {\cdot} (es_2\#t_2) } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    star         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi}, \es^\star}  &\m{iff}\quad & 
+\code{d, s, \varphi \models \pure{\pi}  , \empt}\ or \ 
+\code{d, s, \varphi \models \pure{\pi}  , es {\cdot} \es^\star}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    FALSE         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 & \code{d, s, \varphi \models false}  &\m{iff}\quad &
@@
 These rules transfer program states and systematically accumulate the effects syntactically. 
-To define the model, we introduce an environment \env\ and describe a program state in a four-elements tuple \code{\langle \Pi, H, C, T \rangle}, with the following concrete domains:
+To define the model, we introduce a stack \env\ and describe a program state in a four-elements tuple \code{\langle \Pi, H, T \rangle}, with the following concrete domains:
 \begin{flalign*}
-\Pi {\defeq} t {\rightarrow} \pi, \qquad
-H  {\defeq} es, \qquad
-C {\defeq} \overrightarrow{\textbf{S} {\rightarrow} \Delta}\  | \ \textbf{S}?, \qquad
-T {\defeq} t, \qquad 
-\env {\defeq} \overrightarrow{\textbf{S}}, \qquad
-\Delta {\defeq} \m{Present} \ | \ \m{Absent}  \ | \  \m{Undef}
+\Pi {\defeq} t {\rightarrow} \pi, \qquad\qquad
+H  {\defeq} es, \qquad\qquad
+T {\defeq} t, \qquad\qquad
+\env {\defeq} \code{var {\rightarrow} val }
 \end{flalign*}
@@
 \env\ be the environment containing all the local and output signals;
-\code{\Delta} marks the signal status.
 
@@
 \appref{proof:SoundnessProof}.
-\end{proof}
-
-%\begin{lemma}
-%The set of axioms (A1)-(A11) and (A15)-(A22) are complete for timed effects.
-%\begin{proof} 
-%
-%\end{proof}
-%\end{lemma}
-
- \begin{theorem}[Completeness]\label{Completeness}
- The set of axioms (A1)-(A22) is complete for \timedEffects.
-
-%Given an inclusion \code{\effect_1 \CONTAIN \effect_2}, if \code{\effect_1 \CONTAIN \effect_2} is valid, then the TRS returns  \code{TRUE} by providing a proof.
-
-\end{theorem}
-
-\begin{proof} 
-One can observe that by succinct applications of (A17) to (A22), we have a normal form, 
-\begin{align}
-\pi_1 : (I\# t_1) \cdot \es_1\ ||\ \pi_2 :  (J\# t_2) \cdot\es_2 \rightarrow  (\pi_1 \wedge \pi_2 \wedge t_1{=}t_2) :  ((I  {\cup} J) \# t_1) \cdot (\es_1\ ||\ \es_2)
-\end{align}
-
-Then for any ground \timedEffects \code{\es}, the expression \code{\epsilon || \es} can be reduced to either \code{\epsilon} or \code{\es} by the applications of (A15) and (A16).  
-The expression \code{\es^\omega} can be reduced to either \code{\bot} or \code{\es^\omega} by the applications of (A12) to (A14).
-
-Then, by the semantics defined in \figref{fig:Sementic}, effects constructed by Kleene star \code{\star} (possibly finite and possibly infinite) are supersets of effects constructed by \code{\omega} (definite infinite).
-
-Then one can apply literally all the constructions of \cite{salomaa1966two} used in the completeness proof of \code{F_1} (A1) to (A11).
-
 \end{proof}

### 2022-04-06 paper/tv.tex
m

@@
 \usepackage{cancel}
-\newcommand{\env}{\code{\mathcal{S}}}
+\newcommand{\env}{\code{\mathcal{V}}}
 
@@
 method calls \code{mn({x^*})}; 
-variable assignments \code{\alpha}; 
+%variable assignments \code{\alpha}; 
 %field update \code{v.f:=e}, 
@@
 parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
-may communicate via multi-party event synchronization or shared variables. 
-%conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}. 
-The expression \code{ \textbf{event} [\anyevent{A}(v)] } 
-raises an event \anyevent{A} parametrized with \code{v}. 
-%and takes a set of 
-%assignment actions \code{(x:=v)^*}. 
+may communicate via multi-party event synchronization or shared variables; 
+conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}.
+
+The expression \code{ \textbf{event} [\anyevent{A}(v,  \alpha^*)] } 
+raises an event \anyevent{A} parametrized with \code{v}, 
+and takes a set of 
+assignment actions \code{\alpha^*}. 
 Furthermore, a number of timed process constructs can be used to capture common 
@@
     \code{ v \ | \ 
-    \alpha  \ | \ 
     [b]\ e \ |\ mn({v^*}) \ }
@@
  \ e_1;e_2\ | \ e_1 || e_2 \ 
- % |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
- |\ \textbf{event} [\anyevent{A}(v)] 
+  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
  }  \\
@@
  &   & & \code{
+  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
   | \ \textbf{delay} [d] \ 
@@
 
-We remark additional process constructs (e.g. if-then-else, while, etc.) 
-can be defined using the above. In this setting, clock variables are 
+In this setting, clock variables are 
 made implicit and hence they cannot be compared with each other 
@@
 \code{e} except that it must terminate before \codem{d} time units.
+
+\begin{flalign*}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%   deadline                 %%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \code{\frac{
+    V \not\models  b 
+  }{(V, [b] \ e ) \xrightarrow[]{t} (V, [b] \ e)}\ [gu_1]} 
+  \quad
+  \code{\frac{
+    V \models  b 
+  }{(V, [b] \ e ) \xrightarrow[]{\tau} (V, e)}\ [gu_2]} 
+  \quad
+  \code{\frac{
+  }{(V, \alpha ) \xrightarrow[]{\tau} (\alpha(V), ())}\ [assign]} 
+\end{flalign*}
+
+\begin{flalign*}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%   deadline                 %%
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \code{\frac{
+    (V,e_1) \xrightarrow[]{\anyevent{A}} (V^\prime,e_1^\prime) 
+  }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1^\prime || e_2)}\ [pa_1]} 
+  \quad  
+  \code{\frac{
+    (V,e_2) \xrightarrow[]{\anyevent{A}} (V^\prime,e_2^\prime) 
+  }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
+\quad
+\code{\frac{
+  (V,e_1) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime,e_1^\prime) 
+}{(V, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime, e_1^\prime ; e_2)}\ [se]} 
+\end{flalign*}
 
@@
 from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
-\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{[ev]} \ .
+\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{ev^*} \ .
 
@@
 \  \exists \code{\es_1,\es_2}. \  \code{ es_1 {\cdot}  es_2 {=} es}\\
-&&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi {\wedge}t_1{+} t_2{=}t)}  , 
+&&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi 
+{\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
 (es_1\#t_1) {\cdot} (es_2\#t_2) } \\
@@
 
+\newcommand{\s}[1]{\code{\{ #1\}}}
+
+\subsection{Forward Inference Rules}
+\label{Forward_Rules}
+
+We here present the forward verification rules, s
+which are used to systematically accumulate the effects based on 
+the syntax of each statement.
+\code{\mathcal{P}} denotes the program being checked. 
+With pre/post conditions declared for each method in \code{\mathcal{P}}, 
+we can apply modular verification to a method's body using Hoare-style 
+triples \code{ \Pi, \env \vdash \s{ \effect_c} \ e\ \s{\effect_c^\prime}}
+where 
+\code{\Pi} is the current guard, 
+\code{\env} is the current valuation of the variables;
+\code{\effect_c} is the current effects, 
+and \code{ \effect_C^\prime}
+is the resulting effects by executing \code{e}.
+
+\begin{comment}
   In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\timedL}, by formalising a set of forward inductive rules.
 These rules transfer program states and systematically accumulate the effects syntactically.
-To define the model, we introduce a stack \env\ and describe a program state in a four-elements tuple \code{\langle \Pi, H, T \rangle}, with the following concrete domains:
+
+To define the model, we introduce a stack \env\ and describe 
+a program state in a four-elements tuple \s{H, G}, with the following concrete domains:
 \begin{flalign*}
-\Pi {\defeq} t {\rightarrow} \pi, \qquad\qquad
+G {\defeq} \pi, \qquad\qquad
 H  {\defeq} es, \qquad\qquad
-T {\defeq} t, \qquad\qquad
 \env {\defeq} \code{var {\rightarrow} val }
@@
 
-%We describe the input and output histories of ESTEREL programs by streams carrying sets of signals.
-
-%which is used for the description of a reactive program.
-
-%The main difficulty in giving a semantics to \code{\timedL} consists in the idea of instantaneous reactions of ESTEREL programs to input signals.
-
-%We base this semantics on a functional model of behaviour. We describe the input and output histories of ESTEREL programs by streams carrying sets of signals.
-
-%we mainly present the forward verifier
-% based on the syntax of each statement.
-
-%We present the intermediate representation of program states in \figref{fig:intermediate_representation}
-
-%\noindent   the second element represents the  containing the path constraints (\code{\pi}) and signal assignments (\code{\phi})\footnote{The difference between \code{\textbf{S} = \theta} and \code{\textbf{S} \mapsto \theta } is: the former one denotes the constraints along the execution path, which creates \emph{false} if there are two different status assignments to the same signal; while the latter one records the current status of one signal, and will be overwritten when the presence of a signal had been determined.};
-
-\subsection{Forward Inference Rules}
-\label{Forward_Rules}
+  v \ | \ 
+    [b]\ e \ |\ mn({v^*}) \ }
+  \code{| 
+ % v.f:=e \ | 
+ \ e_1;e_2\ | \ e_1 || e_2 \ 
+  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
+ }  \\
+
+ &   & & \code{
+  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
+  | \ \textbf{delay} [d] \ 
+  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
+  | \ \textbf{deadline}  [d] \ e \  
+\end{comment}
+
+\begin{gather*}
+  \code{\frac{\effect_C^\prime {=} \effect_C\cdot \anyevent{a}}{\vdash \{  \effect_C \}\  \textbf{event} [\anyevent{a}] \ \{ \effect_C^\prime \}} \   {[FV\text{-}Event]}} 
+  \qquad
+  \code{\frac{\vdash \{ \effect_C\}\ e_1 \ \{  \effect_C^\prime\} \qquad \vdash \{  \effect_C^\prime\}\ e_2 \ \{  \effect_C^{\prime\prime}\} }{\vdash \{  \effect_C\}\  e_1;e_2 \ \{  \effect_C^{\prime\prime}\}} \  {[FV\text{-}Seq]}}
+\end{gather*}
+
+\begin{gather*}
+\code{\frac{ \vdash \{  v \wedge \effect_C  \} \ e_1 \ \{  \effect_C^{\prime}\} \qquad \vdash \{ \neg v \wedge \effect_C \} \ e_2 \ \{  \effect_C^{\prime\prime}\}  }
+{\vdash \{  \effect_C\}\  \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 \ \{  \effect_C^{\prime} \vee\effect_C^{\prime\prime} \} } \  {[FV\text{-}If\text{-}Else]}} 
+\end{gather*}
+
+\begin{gather*}
+\code{\frac{
+\begin{matrix}
+\text{\code{  \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
+\\
+\text{\code{\vdash rev( \effect_C) \CONTAIN rev([y^*/x^*] \effect_{pre})   \qquad   \effect_C^\prime =  \effect_C \cdot  [y^*/x^*]\effect_{post}}}
+\end{matrix}}
+{\vdash \{  \effect_C \} \  mn({y^*})  \ \{  \effect_C^\prime\}} \ {[FV\text{-}Call]}}
+\end{gather*}
+
+\begin{gather*}
+\code{\frac{  \vdash \{  \empt \}  \ e \  \{ \effect_C \} \qquad\qquad  \vdash\effect_C \CONTAIN   \effect_{post}}{  \vdash \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}
+\end{gather*}
 

### 2022-04-06 paper/tv.tex
m

@@
 \newcommand{\jskey}[1]{\textcolor{blue}{\code{#1}}}
-\newcommand{\es}{\textcolor{black}{\ensuremath{{es}}}}
 \definecolor{palered-violet}{rgb}{0.86, 0.44, 0.58}
@@
 \newcommand{\codeme}[1]{{\tt{\ensuremath{#1}}}}
-\newcommand{\esn}[2]{\ensuremath{#1^{#2}}}
 \newcommand{\empt}{\textcolor{black}{\ensuremath{\epsilon}}}
@@
 
-    \m{(Timed\ Effects)} &  \effect &\code{  ::= }&
-    \code{
-          (\pure{\pi}, \es)
-   \ | \ \effect_1 \vee \effect_2
-}
-    \\
- \m{(Timed \ Sequence)}  & \ \code{\es}   &\code{ ::=}&
+ \m{(Timed\ Effects)}  & \ \code{\effect}   &\code{ ::=}&
 
@@
     %   \ | \ \anyevent{a}
-   \  | \ \es_1 {\seq} \es_2
-    \ | \ \es_1 {\vee} \es_2
-    \ | \ \es_1 {||} \es_2
-      %    \  | \ \es_1 \times \es_2
-      \ | \ \es \# t 
- %  \  | \  \esn{\es}{t}    
-   \  | \  \esn{\es}{\star}    
-  % \  | \ \esn{\es}{\omega} 
+   \  | \ \effect_1 {\seq} \effect_2
+    \ | \ \effect_1 {\vee} \effect_2
+    \ | \ \effect_1 {||} \effect_2
+      %    \  | \ \effect_1 \times \effect_2
+      \ | \ \effect \# t 
+   \  | \  \effect^\star
 }
@@
 \pure{ \pure{True}}
-   \ | \  \pure{False}
-   \ | \ \pure{A(}{t_1, t_2}\pure{)}
+   \ |  \pure{False}
+   \ |  \pure{A(}{t_1, t_2}\pure{)}
   \  |   \pure{\pure{\pi_1}} {\wedge} \code{\pure{\pi}}_2
@@
 \figref{fig:Syntax_of_Types_and_Effects} Effects is 
- a conditioned time  event sequence \code{\pure{\pi},  \es} or a disjunction of two effects $\effect_1 \vee \effect_2$.
+ a conditioned time  event sequence \code{\pure{\pi},  \effect} or a disjunction of two effects $\effect_1 \vee \effect_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
@@
 %while \code{\anyevent{a}.[1 ..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot}..., and \code{\anyevent{a}.[1, 3..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.3 \cdot \anyevent{a}.5\cdot}...);
- sequences concatenation \code{\es_1\cdot \es_2};
-disjunction  \code{\es_1\vee \es_2};
-parallel composition of two processes is written as \code{\es_1 || \es_2}, where \code{es_1} and \code{es_2} 
+ sequences concatenation \code{\effect_1\cdot \effect_2};
+disjunction  \code{\effect_1\vee \effect_2};
+parallel composition of two processes is written as \code{\effect_1 || \effect_2}, where \code{\effect_1} and \code{\effect_2} 
 may communicate via multi-party event synchronization or shared variables. 
-We introduce a new operator \code{\#}, and the effects \code{\es \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
+We introduce a new operator \code{\#}, and the effects \code{\effect \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
 A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace.
@@
 \code{val} is the set of primitive values, 
-\code{\es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
+\code{\effect} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
 Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, (\es_1\cdot\es_2)}  
+&\code{d, s, \varphi \models \pure{\pi}, (\effect_1\cdot\effect_2)}  
 &\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
@@
 \code{ d_1 {+} d_2 {=} d} \\
-&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
-\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
+&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \effect_1 }
+\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \effect_2 }\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  , (\es_1{\vee}\es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , \es_2 } \\
+&\code{d, s, \varphi \models \pure{\pi}  , (\effect_1{\vee}\effect_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \effect_1 } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , \effect_2 } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}\es_1)||(ev_2{\cdot}\es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (\es_1||(ev_2{\cdot}\es_2)) } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}\es_1)||es_2)  } \\
+&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}\effect_1)||(ev_2{\cdot}\effect_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (\effect_1||(ev_2{\cdot}\effect_2)) } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}\effect_1)||\effect_2)  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  ,\es\# t}  &\m{iff}\quad &
+&\code{d, s, \varphi \models \pure{\pi}  ,\effect\# t}  &\m{iff}\quad &
  \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
@@
 \pure{True} }, 
-\  \exists \code{\es_1,\es_2}. \  \code{ es_1 {\cdot}  es_2 {=} es}\\
+\  \exists \code{\effect_1,\effect_2}. \  \code{\effect_1 {\cdot} \effect_2 {=} \effect}\\
 &&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi 
 {\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
-(es_1\#t_1) {\cdot} (es_2\#t_2) } \\
+(\effect_1\#t_1) {\cdot} (\effect_2\#t_2) } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, \es^\star}  &\m{iff}\quad & 
+&\code{d, s, \varphi \models \pure{\pi}, \effect^\star}  &\m{iff}\quad & 
 \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or \ 
-\code{d, s, \varphi \models \pure{\pi}  , es {\cdot} \es^\star}\\
+\code{d, s, \varphi \models \pure{\pi}  , \effect {\cdot} \effect^\star}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \vspace{-2mm}
-\caption{Semantics of \timedEffects .}
+\caption{Semantics of \timedEffects.}
 \label{fig:Sementic}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1{\cdot}\es_2)}  
+&\code{d, \varphi \models  \pi : (\effect_1{\cdot}\effect_2)}  
 &\m{iff}\quad 
@@
 & & &
-\code{d_1, \varphi_1 \models  \pi : \es_1}  \ and \ 
-\code{d_2, \varphi_2 \models  \pi : \es_2}  
+\code{d_1, \varphi_1 \models  \pi : \effect_1}  \ and \ 
+\code{d_2, \varphi_2 \models  \pi : \effect_2}  
  \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1 {\vee} \es_2)}  
+&\code{d, \varphi \models  \pi : (\effect_1 {\vee} \effect_2)}  
 &\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ or \ 
- \code{d, \varphi \models  \pi :  \es_2}  
+& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \effect_1 } \ or \ 
+ \code{d, \varphi \models  \pi :  \effect_2}  
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : \es \# t }  
+&\code{d, \varphi \models  \pi : \effect \# t }  
 &\m{iff}\quad 
-& d, \varphi \models  (\pi \wedge t{=}d) : \es
+& d, \varphi \models  (\pi \wedge t{=}d) : \effect
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d,  \varphi \models \pi : \esn{\es}{\star}  }  
-&\m{iff}\quad 
-&d, \varphi \models \pi :  \empt \ or \ 
-d, \varphi \models \pi :  (\es \cdot \esn{\es}{\star} ) 
- \\[0.2em]
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-We here present the forward verification rules, s
+We here present the forward verification rules, 
 which are used to systematically accumulate the effects based on 
@@
 we can apply modular verification to a method's body using Hoare-style 
-triples \code{ \Pi, \env \vdash \s{ \effect_c} \ e\ \s{\effect_c^\prime}}
+triples \code{\ \vdash \s{ \effect, \Pi, \env } \ e\ \s{\effect^\prime, \Pi^\prime, \env^\prime}}
 where 
+\code{\effect} is the current effects, 
 \code{\Pi} is the current guard, 
 \code{\env} is the current valuation of the variables;
-\code{\effect_c} is the current effects, 
-and \code{ \effect_C^\prime}
-is the resulting effects by executing \code{e}.
+and \s{\effect^\prime, \Pi^\prime, \env^\prime}  
+is the resulting state by executing \code{e}. 
+The program state is initialized using \s{\epsilon, True, []}.
 
@@
 G {\defeq} \pi, \qquad\qquad
-H  {\defeq} es, \qquad\qquad
+H  {\defeq} \effect, \qquad\qquad
 \env {\defeq} \code{var {\rightarrow} val }
@@
 
-  v \ | \ 
-    [b]\ e \ |\ mn({v^*}) \ }
-  \code{| 
- % v.f:=e \ | 
- \ e_1;e_2\ | \ e_1 || e_2 \ 
+     \ |\ mn({v^*}) \ }
+
   |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
@@
 \begin{gather*}
-  \code{\frac{\effect_C^\prime {=} \effect_C\cdot \anyevent{a}}{\vdash \{  \effect_C \}\  \textbf{event} [\anyevent{a}] \ \{ \effect_C^\prime \}} \   {[FV\text{-}Event]}} 
+  \code{\frac{
+  }
+{  \vdash \{  \effect,\Pi, \env \}\  v \ 
+\{ \effect, \Pi, \env \}} \  
+ {[FV\text{-}Value]}} 
  \qquad
-  \code{\frac{\vdash \{ \effect_C\}\ e_1 \ \{  \effect_C^\prime\} \qquad \vdash \{  \effect_C^\prime\}\ e_2 \ \{  \effect_C^{\prime\prime}\} }{\vdash \{  \effect_C\}\  e_1;e_2 \ \{  \effect_C^{\prime\prime}\}} \  {[FV\text{-}Seq]}}
+ \code{\frac{
+  }
+{  \vdash \{  \effect, \Pi, \env \}\  [b]\ e \ 
+\{ \effect, \Pi{\wedge} b, \env  \}} \  
+ {[FV\text{-}Guard]}} 
 \end{gather*}
@@
 \begin{gather*}
-\code{\frac{ \vdash \{  v \wedge \effect_C  \} \ e_1 \ \{  \effect_C^{\prime}\} \qquad \vdash \{ \neg v \wedge \effect_C \} \ e_2 \ \{  \effect_C^{\prime\prime}\}  }
-{\vdash \{  \effect_C\}\  \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 \ \{  \effect_C^{\prime} \vee\effect_C^{\prime\prime} \} } \  {[FV\text{-}If\text{-}Else]}} 
+  \code{\frac{ 
+ \vdash \{ \effect, \Pi, \env\}\ e_1 \ \{  \effect^\prime, \Pi^\prime, \env^\prime\} 
+\qquad 
+\vdash \{ \effect^\prime, \Pi^\prime, \env^\prime\}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime}, \env^{\prime\prime} \} 
+}{
+  \vdash \{  \effect, \Pi, \env \}\  
+  e_1;e_2 \ \{ \effect^{\prime\prime}, \Pi^{\prime\prime}, 
+  \env^{\prime\prime}\}} \ 
+   {[FV\text{-}Seq]}}  
+\end{gather*}
+
+\begin{gather*}
+  \code{\frac{
+ \vdash \{ \effect, \Pi, \env \}\ e_1 \ \{  \effect^\prime, \Pi^\prime, \env^\prime\} 
+\qquad 
+\vdash \{  \effect, \Pi, \env \}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime}, \env^{\prime\prime} \} 
+    }{
+\vdash \{   \effect, \Pi, \env \}\  e_1 || e_2 \ \{ \effect^\prime || \effect^{\prime\prime}, 
+\Pi^{\prime} {\wedge}\Pi^{\prime\prime}, 
+\}} \   
+{[FV\text{-}Par]}} 
+\end{gather*}
+
+\begin{gather*}
+  \code{\frac{\effect^\prime {=} \effect\cdot \anyevent{a}}{\vdash \{  \effect \}\  \textbf{event} [\anyevent{a}] \ \{ \effect^\prime \}} \   {[FV\text{-}Event]}} 
+\end{gather*}
+
+\begin{gather*}
+\code{\frac{ \vdash \{  v \wedge \effect  \} \ e_1 \ \{  \effect^{\prime}\} \qquad \vdash \{ \neg v \wedge \effect \} \ e_2 \ \{  \effect^{\prime\prime}\}  }
+{\vdash \{  \effect\}\  \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 \ \{  \effect^{\prime} \vee\effect^{\prime\prime} \} } \  {[FV\text{-}If\text{-}Else]}} 
 \end{gather*}
@@
 \\
-\text{\code{\vdash rev( \effect_C) \CONTAIN rev([y^*/x^*] \effect_{pre})   \qquad   \effect_C^\prime =  \effect_C \cdot  [y^*/x^*]\effect_{post}}}
+\text{\code{\vdash rev( \effect) \CONTAIN rev([y^*/x^*] \effect_{pre})   \qquad   \effect^\prime =  \effect \cdot  [y^*/x^*]\effect_{post}}}
 \end{matrix}}
-{\vdash \{  \effect_C \} \  mn({y^*})  \ \{  \effect_C^\prime\}} \ {[FV\text{-}Call]}}
+{\vdash \{  \effect \} \  mn({y^*})  \ \{  \effect^\prime\}} \ {[FV\text{-}Call]}}
 \end{gather*}
@@
 \begin{gather*}
-\code{\frac{  \vdash \{  \empt \}  \ e \  \{ \effect_C \} \qquad\qquad  \vdash\effect_C \CONTAIN   \effect_{post}}{  \vdash \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}
+\code{\frac{  \vdash \{  \empt \}  \ e \  \{ \effect \} \qquad\qquad  \vdash\effect \CONTAIN   \effect_{post}}{  \vdash \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}
 \end{gather*}
@@
 Next we provide the definitions and implementations of auxiliary functions \emph{Nullable}(\code{\delta}), \emph{First}(\code{fst}) and \emph{Derivative}(\code{D}) respectively.
-Intuitively, the Nullable function \code{\delta(\es)} returns a boolean value indicating whether \code{\es} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \es)} computes a set of possible initial time instances of \code{\pure{\pi} : \es}; and the Derivative function \code{D_{I\# t}^{\pure{\pi}}(\es)} computes a next-state effects after eliminating one event \code{I} w.r.t.
-the execution time \code{t} from the current effects \code{\pure{\pi} : \es}.
+Intuitively, the Nullable function \code{\delta(\effect)} returns a boolean value indicating whether \code{\effect} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \effect)} computes a set of possible initial time instances of \code{\pure{\pi} : \effect}; and the Derivative function \code{D_{I\# t}^{\pure{\pi}}(\effect)} computes a next-state effects after eliminating one event \code{I} w.r.t.
+the execution time \code{t} from the current effects \code{\pure{\pi} : \effect}.
 
@@
 \begin{definition}[Nullable]\label{Nullable}
-Given any time sequence \code{\es}, we recursively define \code{\delta(\es)} as:\\
+Given any time sequence \code{\effect}, we recursively define \code{\delta(\effect)} as:\\
 {
-\code{\delta(\es) :bool {=}
+\code{\delta(\effect) :bool {=}
 \begin{cases}
-      \code{true} & \code{if\ \empt \in \es}\\
-      \code{false} & \code{if\ \empt \notin \es}
+      \code{true} & \code{if\ \empt \in \effect}\\
+      \code{false} & \code{if\ \empt \notin \effect}
     \end{cases} }
@@
 \qquad\quad\
-    \code{\delta(\esn{\es}{\star} ) {=} true}   
-\\ 
-\code{\delta(\es_1 \seq \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
+    \code{\delta({\effect^\star} ) {=} true}   
+\\ 
+\code{\delta(\effect_1 \seq \effect_2) {=} \delta(\effect_1) \wedge \delta(\effect_2)}
 \qquad\qquad
-  \code{\delta(\es_1 \choice \es_2) {=} \delta(\es_1) \vee \delta(\es_2)}   
-  \qquad\quad
-  \code{\delta(\esn{\es}{\omega} ) {=} false}     
-  \\
-\code{\delta(\es_1 || \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
+  \code{\delta(\effect_1 \choice \effect_2) {=} \delta(\effect_1) \vee \delta(\effect_2)}   
+  \\
+\code{\delta(\effect_1 || \effect_2) {=} \delta(\effect_1) \wedge \delta(\effect_2)}
 \qquad\qquad\quad
- \code{\delta(\es \# t) {=} \delta(\es)}
+ \code{\delta(\effect \# t) {=} \delta(\effect)}
 \end{gather*}}
@@
 \begin{definition}[Antimirov's First]\label{First1}
-Let \code{fst^\prime(\es){:=}\{ I\ |\  (I \cdot \es^\prime) \in \llbracket  \es \rrbracket  \}} be the set of initial instances derivable from  sequence \code{\es}.
-(\code{\llbracket  \es \rrbracket } represents all the traces contained in \code{\es}.)
+Let \code{fst^\prime(\effect){:=}\{ I\ |\  (I \cdot \effect^\prime) \in \llbracket  \effect \rrbracket  \}} be the set of initial instances derivable from  sequence \code{\effect}.
+(\code{\llbracket  \effect \rrbracket } represents all the traces contained in \code{\effect}.)
 { 
@@
  \qquad\ 
-\code{fst^\prime(  \es_1 {\vee} \es_2) {=} fst^\prime(  \es_1) \cup fst^\prime(  \es_2)}
+\code{fst^\prime(  \effect_1 {\vee} \effect_2) {=} fst^\prime(  \effect_1) \cup fst^\prime(  \effect_2)}
 \\
 {
-\code{fst^\prime( \esn{\es}{\star} ) {=} fst^\prime({ \es})} 
+\code{fst^\prime( {\effect^\star} ) {=} fst^\prime({ \effect})} 
 \qquad\quad\
-\code{fst^\prime(\es_1 {\seq} \es_2) {=} } 
+\code{fst^\prime(\effect_1 {\seq} \effect_2) {=} } 
 \begin{cases}
-      \code{\code{fst^\prime(  \es_1)} \cup \code{fst^\prime(  \es_2)} } \quad & \code{ if\ \delta(\es_1) {=} true}\\
-      \code{\code{fst^\prime(  \es_1)}} & \code{  if\ \delta(\es_1) {=} false}
+      \code{\code{fst^\prime(  \effect_1)} \cup \code{fst^\prime(  \effect_2)} } \quad & \code{ if\ \delta(\effect_1) {=} true}\\
+      \code{\code{fst^\prime(  \effect_1)}} & \code{  if\ \delta(\effect_1) {=} false}
     \end{cases} 
@@
 \begin{definition}[First]\label{First}
-Let \code{fst_{\pure{\pi}}(\es){:=}\{ (I,  \pi, t) \ |\  \pi {\wedge} t{\geq}0 : (I\# t) \cdot \es^\prime \in \llbracket  \pi {:} \es \rrbracket \}} be the set of initial time instances derivable from effects \code{\pi {:} \es}.
-(\code{\llbracket  \pi {:} \es \rrbracket } represents all the time  traces contained in \code{\pi {:} \es})
+Let \code{fst_{\pure{\pi}}(\effect){:=}\{ (I,  \pi, t) \ |\  \pi {\wedge} t{\geq}0 : (I\# t) \cdot \effect^\prime \in \llbracket  \pi {:} \effect \rrbracket \}} be the set of initial time instances derivable from effects \code{\pi {:} \effect}.
+(\code{\llbracket  \pi {:} \effect \rrbracket } represents all the time  traces contained in \code{\pi {:} \effect})
 { 
@@
 \qquad\quad
-   \code{fst_{\pure{\pi}}(  \es \# t) {=}  fst_{pi}(\es)}
- \\
-\code{fst_{\pure{\pi}}( \esn{\es}{\star} ) {=} fst_{\pure{\pi}}({ \es})}
+   \code{fst_{\pure{\pi}}(  \effect \# t) {=}  fst_{pi}(\effect)}
+ \\
+\code{fst_{\pure{\pi}}( {\effect^\star} ) {=} fst_{\pure{\pi}}({ \effect})}
 \qquad\quad
-\code{fst_{\pure{\pi}}( \esn{\es}{\omega} ) {=} fst_{\pure{\pi}}({ \es})} 
 \qquad\quad
-\code{fst_{\pure{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{\pure{\pi}}(  \es_1) \cup fst_{\pure{\pi}}(  \es_2)  }  \\
+\code{fst_{\pure{\pi}}(  \effect_1 {\vee} \effect_2) {=} fst_{\pure{\pi}}(  \effect_1) \cup fst_{\pure{\pi}}(  \effect_2)  }  \\
 \code{fst_{\pure{\pi}}( \textbf{S}? ) {=} fst_{\pure{\pi}}( \{\textbf{S}\} ) \cup fst_{\pure{\pi}}( \{ \overline{\textbf{S}} \} ) }
     \qquad\qquad\quad
-   \code{fst_{\pure{\pi}}(  \es_1 {||} \es_2) {=} unify \ 
-    (fst_{\pure{\pi}}(  \es_1)) \  (fst_{\pure{\pi}}(  \es_2))  }  
+   \code{fst_{\pure{\pi}}(  \effect_1 {||} \effect_2) {=} unify \ 
+    (fst_{\pure{\pi}}(  \effect_1)) \  (fst_{\pure{\pi}}(  \effect_2))  }  
    \\
 {
-\code{fst_{\pure{\pi}}(\es_1 {\seq} \es_2) {=} } 
+\code{fst_{\pure{\pi}}(\effect_1 {\seq} \effect_2) {=} } 
 \begin{cases}
-      \code{\code{fst_{\pure{\pi}}(  \es_1)} \cup \code{fst_{\pure{\pi}}(  \es_2)} } & \code{ if\ \delta(\es_1) {=} true}\\
-      \code{\code{fst_{\pure{\pi}}(  \es_1)}} & \code{  if\ \delta(\es_1) {=} false}
+      \code{\code{fst_{\pure{\pi}}(  \effect_1)} \cup \code{fst_{\pure{\pi}}(  \effect_2)} } & \code{ if\ \delta(\effect_1) {=} true}\\
+      \code{\code{fst_{\pure{\pi}}(  \effect_1)}} & \code{  if\ \delta(\effect_1) {=} false}
     \end{cases} 
@@
 }]\label{Derivative}
-The partial derivative \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\es)} 
-of effects \code{\pi : \es} 
+The partial derivative \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect)} 
+of effects \code{\pi : \effect} 
 w.r.t.
-a event \code{(I, \pi^\prime, t^\prime)} computes the  effects for the left quotient \code{(I, \pi^\prime, t^\prime)^{\text{-}1}\llbracket \pi : \es \rrbracket}.
-\footnote{For understanding of the derivative rule for \code{es\# t} (cf.
-\tabref{tab:rewriting_tree_send}  step \textcircled{3}), it is essentially splitting \code{\es} with a head and a tail, bound with fresh terms \code{t_1} and \code{t_2} respectively.
+a event \code{(I, \pi^\prime, t^\prime)} computes the  effects for the left quotient \code{(I, \pi^\prime, t^\prime)^{\text{-}1}\llbracket \pi : \effect \rrbracket}.
+\footnote{For understanding of the derivative rule for \code{\effect\# t} (cf.
+\tabref{tab:rewriting_tree_send}  step \textcircled{3}), it is essentially splitting \code{\effect} with a head and a tail, bound with fresh terms \code{t_1} and \code{t_2} respectively.
 Meanwhile it unifies \code{t_1} with \code{t^\prime} and  adds the constraint \code{t_1 {+} t_2 {=} t}.}
@@
 \qquad \ 
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(es_1 || es_2)} {=} \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(es_1)} || \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}( es_2)} 
-    \\
-        \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \esn{\es}{\star}) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\es}) \cdot (\esn{\es}{\star})}  
+\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect_1 ||\effect_2)} {=} \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect_1)} || \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect_2)} 
+    \\
+        \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\effect^\star}) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\effect}) \cdot ({\effect^\star})}  
         \qquad\qquad
-                \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \esn{\es}{\omega}) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\es}) \cdot (\esn{\es}{\omega})}  
 \\
 {
- \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \es_1 \seq \es_2) {=} }
+ \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \effect_1 \seq \effect_2) {=} }
 \begin{cases}
-      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \es_1) \cdot  \es_2 \vee  D^{\pi}_{(I, \pi^\prime, t^\prime)}( \es_2)} \quad &\code{if\ \delta(\es_1) {=} true}   \\
-      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}  ( \es_1) \cdot  \es_2} & \code{if\ \delta(\es_1) {=} false} 
+      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \effect_1) \cdot  \effect_2 \vee  D^{\pi}_{(I, \pi^\prime, t^\prime)}( \effect_2)} \quad &\code{if\ \delta(\effect_1) {=} true}   \\
+      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}  ( \effect_1) \cdot  \effect_2} & \code{if\ \delta(\effect_1) {=} false} 
     \end{cases} 
@@
  \\
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1 \choice \es_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1) \choice D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_2)} 
+\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1 \choice \effect_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1) \choice D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_2)} 
 %\\
-%\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1 \ ||\  \es_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_1) \ ||\ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es_2)} 
-\\
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \es \# t) } {=}
+%\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1 \ ||\  \effect_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1) \ ||\ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_2)} 
+\\
+\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect \# t) } {=}
 \code{
-\pi \wedge(t_1{+} t_2 {=}t) \wedge (t_1{=}t^\prime) : (D^{\pi}_{(I, \pi^\prime, t^\prime)}(\es))\# t_2} \ \ \ 
+\pi \wedge(t_1{+} t_2 {=}t) \wedge (t_1{=}t^\prime) : (D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect))\# t_2} \ \ \ 
 \code{(fresh \ t_1\ t_2 )}
@@
 %\hline
-%  \code{\es \choice \es \rightarrow \es} 
-%  &\code{\bott \cdot \es \rightarrow \bott }  
+%  \code{\effect \choice \effect \rightarrow \effect} 
+%  &\code{\bott \cdot \effect \rightarrow \bott }  
 %  &
@@
 %
-%  \code{\bott \choice \es \rightarrow \es } & \code{ \es  \cdot \bott \rightarrow \bott }  &
-%
-%\code{ (\es_1 \cdot \es_2) \cdot \es_3 \rightarrow \es_1 \cdot (\es_2 \cdot \es_3)}
+%  \code{\bott \choice \effect \rightarrow \effect } & \code{ \effect  \cdot \bott \rightarrow \bott }  &
+%
+%\code{ (\effect_1 \cdot \effect_2) \cdot \effect_3 \rightarrow \effect_1 \cdot (\effect_2 \cdot \effect_3)}
 %\\ \hline
 %
-%\code{ \es \choice \bott \rightarrow \es }
+%\code{ \effect \choice \bott \rightarrow \effect }
 %&\code{\bott ^\star \rightarrow \empt}
@@
 %
-% \code{\empt \cdot \es  \rightarrow \es }
+% \code{\empt \cdot \effect  \rightarrow \effect }
 % &  \code{\epsilon^\star \rightarrow \epsilon}
@@
 %
-%\code{ \es \cdot \empt \rightarrow \es}
-%& \code{(\empt \vee \es)^\star \rightarrow \es^\star}
+%\code{ \effect \cdot \empt \rightarrow \effect}
+%& \code{(\empt \vee \effect)^\star \rightarrow \effect^\star}
 %& \code{ }
@@
 (A1)  &
-\code{\es_1 \vee (\es_2 \vee \es_3) \rightarrow   (\es_1 \vee \es_2) \vee \es_3 }\\
+\code{\effect_1 \vee (\effect_2 \vee \effect_3) \rightarrow   (\effect_1 \vee \effect_2) \vee \effect_3 }\\
 \hline
 (A2)  &
-\code{\es_1 \cdot (\es_2 \cdot \es_3)\rightarrow     (\es_1 \cdot \es_2) \cdot \es_3 }\\
+\code{\effect_1 \cdot (\effect_2 \cdot \effect_3)\rightarrow     (\effect_1 \cdot \effect_2) \cdot \effect_3 }\\
 \hline
 (A3)  &
-\code{\es_1 \vee \es_2 \rightarrow   \es_2 \vee \es_1 }\\
+\code{\effect_1 \vee \effect_2 \rightarrow   \effect_2 \vee \effect_1 }\\
 \hline
 (A4)  &
-\code{\es \cdot (\es_1 \vee \es_2)  \rightarrow \es \cdot \es_1  \vee \es \cdot \es_2 }\\
+\code{\effect \cdot (\effect_1 \vee \effect_2)  \rightarrow \effect \cdot \effect_1  \vee \effect \cdot \effect_2 }\\
 \hline
 (A5)  &
- \code{(\es_1 \vee \es_2)\cdot \es   \rightarrow \es_1 \cdot \es   \vee  \es_2 \cdot \es}\\
+ \code{(\effect_1 \vee \effect_2)\cdot \effect   \rightarrow \effect_1 \cdot \effect   \vee  \effect_2 \cdot \effect}\\
 \hline
 (A6)  &
- \code{\es \vee \es   \rightarrow \es}\\
+ \code{\effect \vee \effect   \rightarrow \effect}\\
 \hline
 (A7)  &
- \code{  \es \cdot \epsilon   \rightarrow \es}\\
+ \code{  \effect \cdot \epsilon   \rightarrow \effect}\\
 \hline
 (A8)  &
- \code{  \es \cdot  \bot \rightarrow \bot}\\
+ \code{  \effect \cdot  \bot \rightarrow \bot}\\
 \hline
 (A9)  &
- \code{\es \vee \bot   \rightarrow \es}\\
+ \code{\effect \vee \bot   \rightarrow \effect}\\
 \hline
 (A10)  &
- \code{\epsilon \vee (\es \cdot \es^\star)   \rightarrow  \es^\star}\\
+ \code{\epsilon \vee (\effect \cdot \effect^\star)   \rightarrow  \effect^\star}\\
 \hline
 (A11)  &
- \code{(\epsilon \vee \es)^\star   \rightarrow  \es^\star}\\
+ \code{(\epsilon \vee \effect)^\star   \rightarrow  \effect^\star}\\
 \hline
@@
 (A13)  &
-\code{\es^\omega \cdot \es_1 \rightarrow \es^\omega }\\
+\code{\effect^\omega \cdot \effect_1 \rightarrow \effect^\omega }\\
 \hline
@@
 (A15)  &
-\code{ \es\ ||\ \empt \rightarrow \es}\\
+\code{ \effect\ ||\ \empt \rightarrow \effect}\\
 \hline
 (A16)  &
-\code{ \es\ ||\ \bott \rightarrow \bott}\\
+\code{ \effect\ ||\ \bott \rightarrow \bott}\\
 \hline
 (A17)  &
- \code{(I\# t) \cdot \es_1\ ||\ J \cdot\es_2 \rightarrow ((I  {\cup} J) \# t) \cdot (\es_1 || \es_2)}\\
+ \code{(I\# t) \cdot \effect_1\ ||\ J \cdot\effect_2 \rightarrow ((I  {\cup} J) \# t) \cdot (\effect_1 || \effect_2)}\\
 \hline
 (A18)  &
-\code{\pi : (\es \# t_1 ) \# t_2 \rightarrow \pi  \wedge (t_1 {=} t_2) : \es \# t_1 }\\
+\code{\pi : (\effect \# t_1 ) \# t_2 \rightarrow \pi  \wedge (t_1 {=} t_2) : \effect \# t_1 }\\
 \hline
@@
 (A21)  &
- \code{{\pure{False}} : \es \rightarrow {\pure{False}} : \bott}\\
+ \code{{\pure{False}} : \effect \rightarrow {\pure{False}} : \bott}\\
 \hline
@@
 \hline
- %\code{\es \choice \es \rightarrow \es} 
-%  &\code{\bott \cdot \es \rightarrow \bott }  
+ %\code{\effect \choice \effect \rightarrow \effect} 
+%  &\code{\bott \cdot \effect \rightarrow \bott }  
 %  &
@@
 \input{rules/rule2}
-- It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
+- It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \effect1} is nullable, while \codeme{ \effect_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
 Therefore, these entailments are evidently invalid.\\
@@
 \input{rules/rule3}
-- To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}.
-Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \es_1}}.
-When the \code{\m{fst}} set of \code{\es_1} is empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon}; and \code{\es_2} is nullable.
+- To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \effect_1}}.
+Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \effect_1}}.
+When the \code{\m{fst}} set of \code{\effect_1} is empty, \code{\effect_1} is possible \code{\bot} or \code{\epsilon}; and \code{\effect_2} is nullable.
 For both cases, the inclusion is valid.
 
-- To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}.
-Given the promises that  \codeme{\pi_1 : \es_1 \CONTAIN \pi_3 : \es_3}, we get \codeme{d,  \varphi \models {\pi_3 : \es_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \es_3 \CONTAIN  \pi_4 : \es_4}, we get \codeme{d,  \varphi \models {\pi_4 : \es_4}}; Given the promises that  \codeme{\pi_4 : \es_4 \CONTAIN \pi_2 : \es_2}, we get \codeme{d,  \varphi \models {\pi_2 : \es_2}}.
+- To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \effect_1}}.
+Given the promises that  \codeme{\pi_1 : \effect_1 \CONTAIN \pi_3 : \effect_3}, we get \codeme{d,  \varphi \models {\pi_3 : \effect_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \effect_3 \CONTAIN  \pi_4 : \effect_4}, we get \codeme{d,  \varphi \models {\pi_4 : \effect_4}}; Given the promises that  \codeme{\pi_4 : \effect_4 \CONTAIN \pi_2 : \effect_2}, we get \codeme{d,  \varphi \models {\pi_2 : \effect_2}}.
 Therefore,  the inclusion is valid.
@@
 
-- To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \es_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \es_2}}.
-For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and
-\codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \es_2 \rrbracket}.
-
-Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bott}, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};
-
-Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}.
-
-By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\es_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}, the conclusion is valid. 
+- To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \effect_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \effect_2}}.
+For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \effect_1 \rrbracket}; and
+\codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \effect_2 \rrbracket}.
+
+Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bott}, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \effect_2)};
+
+Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \effect_2)}.
+
+By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\effect_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \effect_2)}, the conclusion is valid. 
 \\

### 2022-04-06 paper/tv.tex
m

@@
 we can apply modular verification to a method's body using Hoare-style 
-triples \code{\ \vdash \s{ \effect, \Pi, \env } \ e\ \s{\effect^\prime, \Pi^\prime, \env^\prime}}
+triples \code{\ \vdash \s{ \effect, \Pi } \ e\ 
+\s{\effect^\prime, \Pi^\prime}}
 where 
@@
 \code{\Pi} is the current guard, 
-\code{\env} is the current valuation of the variables;
-and \s{\effect^\prime, \Pi^\prime, \env^\prime}  
+%\code{\env} is the current valuation of the variables;
+and \s{\effect^\prime, \Pi^\prime}  
 is the resulting state by executing \code{e}. 
-The program state is initialized using \s{\epsilon, True, []}.
+The program state is initialized using \s{\epsilon, True}.
 
@@
 
-     \ |\ mn({v^*}) \ }
-
-  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
- }  \\
-
- &   & & \code{
-  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
-  | \ \textbf{delay} [d] \ 
-  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
-  | \ \textbf{deadline}  [d] \ e \  
 \end{comment}
@@
   }
-{  \vdash \{  \effect,\Pi, \env \}\  v \ 
-\{ \effect, \Pi, \env \}} \  
+{  \vdash \{  \effect,\Pi \}\  v \ 
+\{ \effect, \Pi \}} \  
  {[FV\text{-}Value]}} 
@@
   }
-{  \vdash \{  \effect, \Pi, \env \}\  [b]\ e \ 
-\{ \effect, \Pi{\wedge} b, \env  \}} \  
+{  \vdash \{  \effect, \Pi \}\  [b]\ e \ 
+\{ \effect, \Pi{\wedge} b  \}} \  
  {[FV\text{-}Guard]}} 
@@
   \code{\frac{ 
- \vdash \{ \effect, \Pi, \env\}\ e_1 \ \{  \effect^\prime, \Pi^\prime, \env^\prime\} 
+ \vdash \{ \effect, \Pi\}\ e_1 \ \{  \effect^\prime, \Pi^\prime\} 
 \qquad 
-\vdash \{ \effect^\prime, \Pi^\prime, \env^\prime\}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime}, \env^{\prime\prime} \} 
+\vdash \{ \effect^\prime, \Pi^\prime\}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
 }{
-  \vdash \{  \effect, \Pi, \env \}\  
-  e_1;e_2 \ \{ \effect^{\prime\prime}, \Pi^{\prime\prime}, 
-  \env^{\prime\prime}\}} \ 
+  \vdash \{  \effect, \Pi \}\  
+  e_1;e_2 \ \{ \effect^{\prime\prime}, \Pi^{\prime\prime}
+  \}} \ 
    {[FV\text{-}Seq]}}  
@@
   \code{\frac{
- \vdash \{ \effect, \Pi, \env \}\ e_1 \ \{  \effect^\prime, \Pi^\prime, \env^\prime\} 
+ \vdash \{ \effect, \Pi \}\ e_1 \ \{  \effect^\prime, \Pi^\prime\} 
 \qquad 
-\vdash \{  \effect, \Pi, \env \}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime}, \env^{\prime\prime} \} 
+\vdash \{  \effect, \Pi \}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
     }{
-\vdash \{   \effect, \Pi, \env \}\  e_1 || e_2 \ \{ \effect^\prime || \effect^{\prime\prime}, 
-\Pi^{\prime} {\wedge}\Pi^{\prime\prime}, 
+\vdash \{   \effect, \Pi \}\  e_1 || e_2 \ \{ \effect^\prime || \effect^{\prime\prime}, 
+\Pi^{\prime} {\wedge}\Pi^{\prime\prime}
 \}} \   
@@
 \begin{gather*}
-  \code{\frac{\effect^\prime {=} \effect\cdot \anyevent{a}}{\vdash \{  \effect \}\  \textbf{event} [\anyevent{a}] \ \{ \effect^\prime \}} \   {[FV\text{-}Event]}} 
+  \code{\frac{ 
+    \begin{matrix}
+\vdash \{ \effect, \Pi {\wedge}  v   \} \ e_1 \ \{  \effect^{\prime} , \Pi^\prime \} 
+\qquad \vdash \{ \effect, \Pi {\wedge} \neg v  \} \ e_2 \ 
+\{  \effect^{\prime\prime}, \Pi^{\prime\prime} \}  
+\\ \{  \effect_f, \Pi_f \} {=} \s{ \effect^{\prime} , \Pi^\prime} \cup \s{\effect^{\prime\prime}, \Pi^{\prime\prime}}
+\end{matrix}}
+  {\vdash \s{ \effect, \Pi}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
+  \textbf{else}\ e_2 \ \{  \effect_f, \Pi_f \} } \  
+  {[FV\text{-}If\text{-}Else]}} 
   \end{gather*}
@@
 \begin{gather*}
-\code{\frac{ \vdash \{  v \wedge \effect  \} \ e_1 \ \{  \effect^{\prime}\} \qquad \vdash \{ \neg v \wedge \effect \} \ e_2 \ \{  \effect^{\prime\prime}\}  }
-{\vdash \{  \effect\}\  \textbf{if}\ v\ \textbf{then}\ e_1\ \textbf{else}\ e_2 \ \{  \effect^{\prime} \vee\effect^{\prime\prime} \} } \  {[FV\text{-}If\text{-}Else]}} 
+  \code{\frac{
+    \effect^\prime {=} \effect\cdot \anyevent{A}(v, \Pi, \alpha^*) 
+    }
+  {\vdash \s{ \effect, \Pi} \  
+  \textbf{event} [\anyevent{A}(v, \alpha^*)] 
+   \ \{ \effect^\prime, True \}} \   {[FV\text{-}Event]}} 
+   \qquad
+  \code{\frac{
+    \effect^\prime {=} \effect\cdot \epsilon\#t \quad (t\ is\ fresh) 
+    }
+  {\vdash \s{ \effect, \Pi} \  
+  \textbf{delay} [d] 
+   \ \{ \effect^\prime, True \}} \   {[FV\text{-}Delay]}} 
 \end{gather*}
@@
     \begin{matrix}
-\text{\code{  \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
-\\
-\text{\code{\vdash rev( \effect) \CONTAIN rev([y^*/x^*] \effect_{pre})   \qquad   \effect^\prime =  \effect \cdot  [y^*/x^*]\effect_{post}}}
+      \vdash \{ \epsilon, \Pi \}\ e_1 \ \{  \effect^\prime, \Pi^\prime\} 
+      \qquad 
+      \vdash \{  \epsilon, \Pi \}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
+      \\
+      \s{\effect_f, \Pi_f} {=} \s{\effect {\cdot}(\effect^\prime\#t), \Pi^\prime {\wedge}t{\leq}d}
+      \cup 
+  \s{\effect {\cdot}(\effect^{\prime\prime}\#t), \Pi^{\prime\prime} {\wedge}t{>}d}   
+  \quad (t\ is\ fresh)     
+\end{matrix}
+  }
+  {\vdash \s{ \effect, \Pi} \  
+  e_1\ \textbf{timeout} [d] \  e_2
+   \ \s{\effect_f, \Pi_f} } \   {[FV\text{-}Timeout]}} 
+\end{gather*}
+
+\begin{gather*}
+  \code{\frac{
+    \begin{matrix}
+      \vdash \{ \epsilon, \Pi \}\ e \ \{  \effect^\prime, \Pi^\prime\} 
+      \qquad 
+      \s{\effect_f, \Pi_f} {=} \s{\effect {\cdot}(\effect^\prime\#t), \Pi^\prime {\wedge}t{\leq}d}
+  \quad (t\ is\ fresh)     
+\end{matrix}
+  }
+  {\vdash \s{ \effect, \Pi} \  
+  \textbf{deadline}  [d] \ e 
+   \ \s{\effect_f, \Pi_f} } \   {[FV\text{-}Deadline]}} 
+\end{gather*}
+
+\begin{gather*}
+\code{\frac{
+\begin{matrix}
+\text{\code{  mn  \ {x^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
+\\
+\text{\code{\vdash  \effect \CONTAIN [v^*/x^*] \effect_{pre}   \qquad   \effect^\prime =  \effect \cdot  [y^*/x^*]\effect_{post}}}
 \end{matrix}}
-{\vdash \{  \effect \} \  mn({y^*})  \ \{  \effect^\prime\}} \ {[FV\text{-}Call]}}
+{\vdash \s{ \effect, \Pi} \ mn({v^*})  \ 
+\{  \effect^\prime,  \Pi\}} \ {[FV\text{-}Call]}}
 \end{gather*}
@@
 \begin{gather*}
-\code{\frac{  \vdash \{  \empt \}  \ e \  \{ \effect \} \qquad\qquad  \vdash\effect \CONTAIN   \effect_{post}}{  \vdash \tau \ mn  \ {( \tau\ x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}
+\code{\frac{  \vdash \{  \empt, True \} 
+ \ e \  \{ \effect, \Pi \} \qquad\qquad  \vdash\effect \CONTAIN  
+  \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}  
 \end{gather*}

### 2022-04-07 paper/tv.tex
m

@@
 void process (int i)
-/* requires d1<d2,  emp 
-   ensures  true, (Update(i)#d1.emp#d2.([x=i]Critical(i).Exit(i) \/ emp))^* */
+/* req  d1<d2,  emp 
+   ens  true, (Update(i)#d1.emp#d2.([x=i]Critical(i).Exit(i) \/ emp))^* */
 {
@@
 void main () 
-/* requires true /\ emp 
-   ensures  true, (!Critical \/ (Critical(i) /\ i=x))^* */
-// ensures  true, (ct <= 1)^*
+/* req true /\ emp 
+   ens  true, (!Critical \/ (Critical(i) /\ i=x))^* */
+// ens  true, (ct <= 1)^*
 { process(0) || process(1) || process(2); }
@@
 void addSugar(int n)
-/* requires n>0,  _^*.Cup 
-   ensures  t>=n, Sugar # t */
+/* req n>0,  _^*.Cup 
+   ens  t>=n, Sugar # t */
 { if n == 0 then event[Sugar] 
@@
 void makeCoffee (int n)
-/* requires n>0, emp 
- ensures  t<5/\t>=n/\t1<3, 
+/* req n>0, emp 
+ ens  t<5/\t>=n/\t1<3, 
  Cup.(Sugar#t).(Coffee#t1).Done */
@@
 void main () 
-/* requires true, emp 
- ensures  t<8, (_^*.Done)#t */
+/* req true, emp 
+ ens  t<8, (_^*.Done)#t */
 { makeCoffee(3);}
@@
   \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
-  \code{ mn  \ {(x)^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}}
+  \code{ mn  \ {(x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
   \\
@@
 
+{{\small
 \begin{flalign*}
@@
 }{(V, \textbf{delay} [0]) \xrightarrow[]{\tau} (V, ())}\ [de_2]} 
-\end{flalign*}
+\end{flalign*}}}
 
@@
 \codem{d} becomes \codem{0}.
-\begin{flalign*}
+{{\small\begin{flalign*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 }{(V, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (V, e_2)}\ [to_4]} 
-\end{flalign*}
+\end{flalign*}}}
 If an observable event \anyevent{A} can be engaged by \code{e_1}, 
@@
 \code{e_2} takes over control by a silent transition (rule \code{[to_4]}).
-\begin{flalign*}
+{{\small\begin{flalign*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   (V,e) \xrightarrow[]{\anyevent{A}} (V^\prime,e^\prime)
-}{(V, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (V^\prime, \textbf{deadline}  [d] \ e^\prime)}\ [dl_1]} 
-\  
+}{(V, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (V^\prime, \textbf{deadline}  [d] \ e^\prime)} [dl_1]} 
+\quad 
 \code{\frac{
   (V,e) \xrightarrow[]{\text{t}} (V,e^\prime)  \quad (t {\leq} d)
-}{(V, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (V, \textbf{deadline}  [d \text{-}t] \ e^\prime )}\ [dl_2]} 
-\end{flalign*}
+}{(V, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (V, \textbf{deadline}  [d \text{-}t] \ e^\prime )} [dl_2]} 
+\end{flalign*}}}
 
@@
 
-\begin{flalign*}
+{{\small\begin{flalign*}
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   }{(V, [b] \ e ) \xrightarrow[]{t} (V, [b] \ e)}\ [gu_1]} 
-  \quad
+  \ \ \qquad
   \code{\frac{
@@
   }{(V, [b] \ e ) \xrightarrow[]{\tau} (V, e)}\ [gu_2]} 
-  \quad
+  \ \ \qquad 
   \code{\frac{
   }{(V, \alpha ) \xrightarrow[]{\tau} (\alpha(V), ())}\ [assign]} 
-\end{flalign*}
-
-\begin{flalign*}
+\end{flalign*}}}
+
+{{\small\begin{flalign*}
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1^\prime || e_2)}\ [pa_1]} 
-  \quad  
+  \ \   
   \code{\frac{
@@
   }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
-\quad
+\ \ 
 \code{\frac{
@@
 }{(V, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime, e_1^\prime ; e_2)}\ [se]} 
-\end{flalign*}
+\end{flalign*}}}
 
@@
 
-We plant the effects specifications into the Hoare-style verification system, using \code{ \effect_{pre}} and \code{  \effect_{post} }  to capture the temporal pre/post 
-condition. %\code{\effect_{pre}} and the postcondition \code{\effect_{post}}.
+We plant the effects specifications into the Hoare-style verification system, using \code{ es_{pre}} and \code{  es_{post} }  to capture the temporal pre/post 
+condition. %\code{es_{pre}} and the postcondition \code{es_{post}}.
 
@@
 
- \m{(Timed\ Effects)}  & \ \code{\effect}   &\code{ ::=}&
+    \m{(Timed\ Effects)} &  \effect &\code{  ::= }&
+    \code{
+          (\pure{\pi}, es)
+   \ | \ \effect_1 \vee \effect_2
+}
+    \\
+ \m{(Event \ Sequences)}  & \ \code{es}   &\code{ ::=}&
 
@@
     %   \ | \ \anyevent{a}
-   \  | \ \effect_1 {\seq} \effect_2
-    \ | \ \effect_1 {\vee} \effect_2
-    \ | \ \effect_1 {||} \effect_2
-      %    \  | \ \effect_1 \times \effect_2
-      \ | \ \effect \# t 
-   \  | \  \effect^\star
+   \  | \ es_1 {\seq} es_2
+    \ | \ es_1 {\vee} es_2
+    \ | \ es_1 {||} es_2
+      %    \  | \ es_1 \times es_2
+      \ | \ es \# t 
+   \  | \  es^\star
 }
@@
 \figref{fig:Syntax_of_Types_and_Effects} Effects is 
- a conditioned time  event sequence \code{\pure{\pi},  \effect} or a disjunction of two effects $\effect_1 \vee \effect_2$.
+ a conditioned time  event sequence \code{\pure{\pi},  es} or a disjunction of two effects $es_1 \vee es_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
@@
 %while \code{\anyevent{a}.[1 ..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot}..., and \code{\anyevent{a}.[1, 3..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.3 \cdot \anyevent{a}.5\cdot}...);
- sequences concatenation \code{\effect_1\cdot \effect_2};
-disjunction  \code{\effect_1\vee \effect_2};
-parallel composition of two processes is written as \code{\effect_1 || \effect_2}, where \code{\effect_1} and \code{\effect_2} 
+ sequences concatenation \code{es_1\cdot es_2};
+disjunction  \code{es_1\vee es_2};
+parallel composition of two processes is written as \code{es_1 || es_2}, where \code{es_1} and \code{es_2} 
 may communicate via multi-party event synchronization or shared variables. 
-We introduce a new operator \code{\#}, and the effects \code{\effect \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
+We introduce a new operator \code{\#}, and the effects \code{es \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
 A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace.
@@
 \code{val} is the set of primitive values, 
-\code{\effect} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
-Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
-the effects \code{\effect} take exactly \code{d} time units to complete; 
+\code{es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
+Let \code{d, s, \varphi \models es} denote the model relation, i.e., 
+the effects \code{es} take exactly \code{d} time units to complete; 
 the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
-temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
+temporal effects \code{es}, with \code{d}, \code{s}, \code{\varphi} 
 from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, (\effect_1\cdot\effect_2)}  
+&\code{d, s, \varphi \models \pure{\pi}, (es_1\cdot es_2)}  
 &\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
@@
 \code{ d_1 {+} d_2 {=} d} \\
-&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \effect_1 }
-\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \effect_2 }\\
+&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , es_1 }
+\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , es_2 }\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  , (\effect_1{\vee}\effect_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \effect_1 } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , \effect_2 } \\
+&\code{d, s, \varphi \models \pure{\pi}  , (es_1{\vee}es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , es_1 } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , es_2 } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}\effect_1)||(ev_2{\cdot}\effect_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (\effect_1||(ev_2{\cdot}\effect_2)) } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}\effect_1)||\effect_2)  } \\
+&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}es_1)||(ev_2{\cdot}es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (es_1||(ev_2{\cdot}es_2)) } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}es_1)||es_2)  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  ,\effect\# t}  &\m{iff}\quad &
+&\code{d, s, \varphi \models \pure{\pi}  ,es\# t}  &\m{iff}\quad &
  \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
@@
 \pure{True} }, 
-\  \exists \code{\effect_1,\effect_2}. \  \code{\effect_1 {\cdot} \effect_2 {=} \effect}\\
+\  \exists \code{es_1,es_2}. \  \code{es_1 {\cdot} es_2 {=} es}\\
 &&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi 
 {\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
-(\effect_1\#t_1) {\cdot} (\effect_2\#t_2) } \\
+(es_1\#t_1) {\cdot} (es_2\#t_2) } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, \effect^\star}  &\m{iff}\quad & 
+&\code{d, s, \varphi \models \pure{\pi}, es^\star}  &\m{iff}\quad & 
 \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or \ 
-\code{d, s, \varphi \models \pure{\pi}  , \effect {\cdot} \effect^\star}\\
+\code{d, s, \varphi \models \pure{\pi}  , es {\cdot} es^\star}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models \effect_1 {\vee} \effect_2}  
+&\code{d, \varphi \models es_1 {\vee} es_2}  
 &\m{iff}\quad 
-&  d, \varphi \models \effect_1 \ or \ d, \varphi \models \effect_2
+&  d, \varphi \models es_1 \ or \ d, \varphi \models es_2
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\effect_1{\cdot}\effect_2)}  
+&\code{d, \varphi \models  \pi : (es_1{\cdot}es_2)}  
 &\m{iff}\quad 
@@
 & & &
-\code{d_1, \varphi_1 \models  \pi : \effect_1}  \ and \ 
-\code{d_2, \varphi_2 \models  \pi : \effect_2}  
+\code{d_1, \varphi_1 \models  \pi : es_1}  \ and \ 
+\code{d_2, \varphi_2 \models  \pi : es_2}  
  \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\effect_1 {\vee} \effect_2)}  
+&\code{d, \varphi \models  \pi : (es_1 {\vee} es_2)}  
 &\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \effect_1 } \ or \ 
- \code{d, \varphi \models  \pi :  \effect_2}  
+& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  es_1 } \ or \ 
+ \code{d, \varphi \models  \pi :  es_2}  
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : \effect \# t }  
+&\code{d, \varphi \models  \pi : es \# t }  
 &\m{iff}\quad 
-& d, \varphi \models  (\pi \wedge t{=}d) : \effect
+& d, \varphi \models  (\pi \wedge t{=}d) : es
 \\[0.2em]
@@
 to record the computation duration of given effects. 
-Let \code{d, \varphi \models \effect} denote the model relation, i.e., 
-the effects \code{\effect} take exactly \code{d} time units to complete; and 
-the linear temporal sequence \code{\varphi} satisfies the sequential time  instances defined from \code{\effect}, with \code{d}, \code{\varphi} from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{Z^+}} and \code{\varphi}   {\defeq}\ \code{list\ of\ I} (a sequence of time instances).
+Let \code{d, \varphi \models es} denote the model relation, i.e., 
+the effects \code{es} take exactly \code{d} time units to complete; and 
+the linear temporal sequence \code{\varphi} satisfies the sequential time  instances defined from \code{es}, with \code{d}, \code{\varphi} from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{Z^+}} and \code{\varphi}   {\defeq}\ \code{list\ of\ I} (a sequence of time instances).
 
@@
 
-\begin{gather*}
+{{\small\begin{gather*}
   \code{\frac{
@@
  {[FV\text{-}Guard]}} 
-\end{gather*}
-
-\begin{gather*}
+\end{gather*}}}
+
+{{\small\begin{gather*}
   \code{\frac{ 
- \vdash \{ \effect, \Pi\}\ e_1 \ \{  \effect^\prime, \Pi^\prime\} 
-\qquad 
-\vdash \{ \effect^\prime, \Pi^\prime\}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
+ \vdash \{ \effect, \Pi\} e_1  \{  \effect^\prime, \Pi^\prime\} 
+\ \  \ 
+\vdash \{ \effect^\prime, \Pi^\prime\} e_2  \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
 }{
@@
   e_1;e_2 \ \{ \effect^{\prime\prime}, \Pi^{\prime\prime}
-  \}} \ 
+  \}} 
    {[FV\text{-}Seq]}}  
-\end{gather*}
-
-\begin{gather*}
+\  \ 
   \code{\frac{
- \vdash \{ \effect, \Pi \}\ e_1 \ \{  \effect^\prime, \Pi^\prime\} 
-\qquad 
-\vdash \{  \effect, \Pi \}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
+ \vdash \{ \effect, \Pi \} e_1  \{  \effect^\prime, \Pi^\prime\} 
+\ \  \
+\vdash \{  \effect, \Pi \} e_2  \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
     }{
@@
 \Pi^{\prime} {\wedge}\Pi^{\prime\prime}
-\}} \   
+\}}  
 {[FV\text{-}Par]}} 
-\end{gather*}
-
-\begin{gather*}
+\end{gather*}}}
+
+{{\small\begin{gather*}
   \code{\frac{ 
@@
 \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \}  
-\\ \{  \effect_f, \Pi_f \} {=} \s{ \effect^{\prime} , \Pi^\prime} \cup \s{\effect^{\prime\prime}, \Pi^{\prime\prime}}
+\qquad 
+ \{  \effect_f, \Pi_f \} {=} \s{ \effect^{\prime} , \Pi^\prime} \cup \s{\effect^{\prime\prime}, \Pi^{\prime\prime}}
 \end{matrix}}
@@
   {[FV\text{-}If\text{-}Else]}} 
-  \end{gather*}
-
-\begin{gather*}
+  \end{gather*}}}
+
+  {{\small\begin{gather*}
   \code{\frac{
@@
    \ \{ \effect^\prime, True \}} \   {[FV\text{-}Delay]}} 
-\end{gather*}
-
-\begin{gather*}
+\end{gather*}}}
+
+{{\small\begin{gather*}
   \code{\frac{
@@
    \ \s{\effect_f, \Pi_f} } \   {[FV\text{-}Timeout]}} 
-\end{gather*}
-
-\begin{gather*}
+\end{gather*}}}
+
+{{\small\begin{gather*}
   \code{\frac{
@@
    \ \s{\effect_f, \Pi_f} } \   {[FV\text{-}Deadline]}} 
-\end{gather*}
-
-\begin{gather*}
+\end{gather*}}}
+
+{{\small\begin{gather*}
 \code{\frac{
 \begin{matrix}
-\text{\code{  mn  \ {x^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
+{\code{  mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
 \\
@@
 \{  \effect^\prime,  \Pi\}} \ {[FV\text{-}Call]}}
-\end{gather*}
-
-\begin{gather*}
+\ \quad 
 \code{\frac{  \vdash \{  \empt, True \} 
- \ e \  \{ \effect, \Pi \} \qquad\qquad  \vdash\effect \CONTAIN  
-  \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{requires}\ \effect_{pre}\ \textbf{ensures}\  \effect_{post}\} \ \{ e \}} \ {[FV\text{-}Meth]}}  
-\end{gather*}
+ \ e \  \{ \effect, \Pi \} \quad  \vdash\effect \CONTAIN  
+  \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ 
+  \textbf{ens}\  \effect_{post}\} \ \{ e \}} \  {[FV\text{-}Meth]}}  
+\end{gather*}}}
 

### 2022-04-07 paper/tv.tex
m

@@
                         %% http://ctan.org/pkg/subcaption
+
+\newcommand{\wbigcup}{\mathop{\widetilde{\bigcup}}\displaylimits}
 
@@
 \newcommand{\env}{\code{\mathcal{V}}}
+
+\newcommand{\es}{\theta}
+\newcommand{\ev}{\iota}
 
@@
 
+\newcommand{\mysharp}{\mathrel{\texttt{\#}}}
+
 \newcommand{\toolName}{Tvide}
@@
 time measurement units.}, is expressed in \timedEffects\ as: 
-\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \# t}.
+\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}.
 %\begin{align*}
@@
 %which replaces temporal operators by time-constrained versions from 
-Here, \code{\#} is a novel operator specifying the \emph{real-time} 
+Here, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
 constraints for the \emph{logical-time} sequences \cite{von2017real}; 
@@
 \begin{align*}
-&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \# t)} \cdot \anyevent{Done}}.
+&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
 \end{align*}  
 effects of \code{addSugar(n)} as:
-\code{(n{>}0  \wedge  t {\geq} n) : ({\anyevent{Sugar} \# t)}}
+\code{(n{>}0  \wedge  t {\geq} n) : ({\anyevent{Sugar} \mysharp  t)}}
 
@@
 /* req  d1<d2,  emp 
-   ens  true, (Update(i)#d1.emp#d2.([x=i]Critical(i).Exit(i) \/ emp))^* */
+   ens  true, [x=-1](Update(i)#d1.emp#d2.
+   ([x=i]Critical(i).Exit(i) \/ [x!=i]emp))^* */
 {
@@
       \\
-     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\# t}  \rangle } 
+     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\mysharp  t}  \rangle } 
      \siderule{ [FV\text{-}Call]}
       \\
-     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}}  \rangle } 
+     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\}}  \rangle } 
      \siderule{ [FV\text{-}Async]}
@@
                    \code{\langle \textcolor{huntergreen}{(true \wedge 0{\leq}t {<}3) :  Ready?
-\cdot\{Go\}  \ || \  (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\}} \rangle }   \siderule{ [FV\text{-}Fork]}
-        \\ 
-         \code{\langle \textcolor{huntergreen}{0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}} \rangle }
+\cdot\{Go\}  \ || \  (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\}} \rangle }   \siderule{ [FV\text{-}Fork]}
+        \\ 
+         \code{\langle \textcolor{huntergreen}{0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}} \rangle }
          \siderule{ [Effects\text{-}Normalization]} 
@@
                   \code{  \textcolor{darkred}{
-{0 {\leq} t {<}3} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN {0 {\leq} t  {<}3} : \_\cdot (\{Cook\})\# t \cdot\_^\star} 
+{0 {\leq} t {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}
+ \CONTAIN {0 {\leq} t  {<}3} : \_\cdot (\{Cook\})\mysharp  t \cdot\_^\star} 
                   }    \\
@@
 
-Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\# t}(\effect)} is the partial derivative of \code{\effect} w.r.t the event \code{I} and time bound \code{t}.
+Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\mysharp  t}(\effect)} is the partial derivative of \code{\effect} w.r.t the event \code{I} and time bound \code{t}.
 
@@
 For \timedEffects \code{\effect_1 } and \code{\effect_2}, 
-\code{\effect_1  \CONTAIN \effect_2 \Leftrightarrow \forall I. \forall t {\geq} 0.\ D_{I\# t}(\effect_1)  \CONTAIN D_{I\# t}(\effect_2)}.
+\code{\effect_1  \CONTAIN \effect_2 \Leftrightarrow \forall I. \forall t {\geq} 0.\ D_{I\mysharp  t}(\effect_1)  \CONTAIN D_{I\mysharp  t}(\effect_2)}.
 \end{definition}
@@
  satisfy the declared postcondition. 
-%property \code{\effect^\prime  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\# t)\cdot\_^\star}, 
-%where \code{\effect^\prime} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces.
+%property \code{\effect_1  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\mysharp  t)\cdot\_^\star}, 
+%where \code{\effect_1} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces.
 We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.
@@
 \Infer[dashed]1[{\siderule{\textcircled{4}[UNFOLD{-}UNIFY]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L
- } : \cancel{\{Cook\} \# t_L^2} \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\# t_R}\cdot\_^\star}  }
-\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L } : \cancel{\{Prep\}\# t_L^1} \cdot \{Cook\} \# t_L^2 \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\_}\cdot\{Cook\}\# t_R \cdot\_^\star}  }
-\Infer[dashed]1[{\siderule{\textcircled{2}[SPLIT]}}]{\code{ \textcolor {darkred}{t_L {<}3} : (\{Prep\}\cdot \{Cook\})\# t_L \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \_\cdot\{Cook\}\# t_R\cdot\_^\star}  }
- \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{ \textcolor {darkred}{t {<}3} : (\{Prep\}\cdot \{Cook\})\# t \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t {<}3} : \_\cdot\{Cook\}\# t\cdot\_^\star}  }
+ } : \cancel{\{Cook\} \mysharp  t_L^2} \cdot \{ Ready\} \cdot \{Go\}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\mysharp  t_R}\cdot\_^\star}  }
+\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L } : \cancel{\{Prep\}\mysharp  t_L^1} \cdot \{Cook\} \mysharp  t_L^2 \cdot \{ Ready\} \cdot \{Go\}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\_}\cdot\{Cook\}\mysharp  t_R \cdot\_^\star}  }
+\Infer[dashed]1[{\siderule{\textcircled{2}[SPLIT]}}]{\code{ \textcolor {darkred}{t_L {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t_L \cdot \{ Ready\} \cdot \{Go\}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \_\cdot\{Cook\}\mysharp  t_R\cdot\_^\star}  }
+ \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{ \textcolor {darkred}{t {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}
+ \CONTAIN \textcolor {darkred}{t {<}3} : \_\cdot\{Cook\}\mysharp  t\cdot\_^\star}  }
 \end{prooftree}}
@@
     \code{
-          (\pure{\pi}, es)
+          (\pure{\pi}, \es)
    \ | \ \effect_1 \vee \effect_2
@@
     \\
- \m{(Event \ Sequences)}  & \ \code{es}   &\code{ ::=}&
+ \m{(Event \ Sequences)}  & \ \code{\es}   &\code{ ::=}&
 
@@
    \  | \ \empt 
-    \ | \ ev 
-    %   \ | \ \anyevent{a}
-   \  | \ es_1 {\seq} es_2
-    \ | \ es_1 {\vee} es_2
-    \ | \ es_1 {||} es_2
-      %    \  | \ es_1 \times es_2
-      \ | \ es \# t 
-   \  | \  es^\star
-}
-
-\\
-\m{(Events)} & ev  &  ::=  & 
+    \ | \ \ev
+   \  | \ \es_1 {\seq} \es_2
+    \ | \ \pi. (\es_1 {\vee} \es_2)
+    \ | \ \es_1 {||} \es_2
+    \ | \ \pi ?  \es
+      %    \  | \ \es_1 \times \es_2
+      \ | \ \es \mysharp  t 
+   \  | \  \es^\star
+}
+
+\\
+\m{(Events)} & \ev  &  ::=  & 
 \code{
-  \anyevent{A}(v, \pi, \alpha^*)
+  \anyevent{A}(v, \alpha^*)
     \ | \ \anynotevent{A} 
@@
 
-     \m{(Real\ Time\ Bound)}\ \code{\#}
+     \m{(Real\ Time\ Bound)}\ \code{\mysharp }
      \qquad \qquad 
@@
 \figref{fig:Syntax_of_Types_and_Effects} Effects is 
- a conditioned time  event sequence \code{\pure{\pi},  es} or a disjunction of two effects $es_1 \vee es_2$.
+ a conditioned time  event sequence \code{\pure{\pi},  es} or a disjunction of two effects $\es_1 \vee \es_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
@@
 %while \code{\anyevent{a}.[1 ..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot}..., and \code{\anyevent{a}.[1, 3..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.3 \cdot \anyevent{a}.5\cdot}...);
- sequences concatenation \code{es_1\cdot es_2};
-disjunction  \code{es_1\vee es_2};
-parallel composition of two processes is written as \code{es_1 || es_2}, where \code{es_1} and \code{es_2} 
+ sequences concatenation \code{\es_1\cdot \es_2};
+disjunction  \code{\es_1\vee \es_2};
+parallel composition of two processes is written as \code{\es_1 || \es_2}, where \code{\es_1} and \code{\es_2} 
 may communicate via multi-party event synchronization or shared variables. 
-We introduce a new operator \code{\#}, and the effects \code{es \# t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
+We introduce a new operator \code{\mysharp }, and the effects \code{es \mysharp  t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
 A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  , ev }  
+&\code{d, s, \varphi \models \pure{\pi}  , \ev }  
 &\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
-\pure{True} }\ and \ \varphi {=} [ev]  \\
+\pure{True} }\ and \ \varphi {=} [\ev]  \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, (es_1\cdot es_2)}  
+&\code{d, s, \varphi \models \pure{\pi}, (\es_1\cdot \es_2)}  
 &\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
@@
 \code{ d_1 {+} d_2 {=} d} \\
-&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , es_1 }
-\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , es_2 }\\
+&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
+\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  , (es_1{\vee}es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , es_1 } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , es_2 } \\
+&\code{d, s, \varphi \models \pure{\pi}, \Pi_1.(\es_1{\vee}\es_2)}  
+&\m{iff}\quad & 
+\code{\llbracket \Pi_1  \rrbracket_{s} {=}  
+ \pure{True} },\code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
+\ or\ 
+\code{\llbracket \Pi_1  \rrbracket_{s} {=}  
+ \pure{False} },
+\code{d, s, \varphi \models \pure{\pi}  , \es_2 } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi} , (ev_1{\cdot}es_1)||(ev_2{\cdot}es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , ev_1{\cdot} (es_1||(ev_2{\cdot}es_2)) } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , ev_2{\cdot}((ev_1{\cdot}es_1)||es_2)  } \\
+&\code{d, s, \varphi \models \pure{\pi} , (\ev_1{\cdot}\es_1)||(\ev_2{\cdot}\es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \ev_1{\cdot} (\es_1||(\ev_2{\cdot}\es_2)) } 
+\ or\ \code{d, s, \varphi \models \pure{\pi}  , \ev_2{\cdot}((\ev_1{\cdot}\es_1)||\es_2)  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi} , (ev\#t_1) || (\epsilon \# t_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {\geq}t_2)}, (ev\#t_1) } 
-\ or\ \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {<}t_2)}  , (ev\#t_1){\cdot}(\epsilon \# (t_2\text{-}t_1))  } \\
+&\code{d, s, \varphi \models \pure{\pi} , (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {\geq}t_2)}, (\ev\mysharp t_1) } 
+\ or\ \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {<}t_2)}  , (\ev\mysharp t_1){\cdot}(\epsilon \mysharp  (t_2\text{-}t_1))  } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    block         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \pure{\pi}, \Pi_1 ? es}  &\m{iff}\quad & 
+\code{\llbracket \Pi_1  \rrbracket_{s} {=}  
+ \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , es}\ or  \ 
+  \code{\llbracket \Pi_1 \rrbracket_{s} {=}  
+\pure{False} }, 
+\  \code{d, s, \varphi \models \pure{\pi}, \Pi_1 ? es}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  ,es\# t}  &\m{iff}\quad &
+&\code{d, s, \varphi \models \pure{\pi}  ,es\mysharp  t}  &\m{iff}\quad &
  \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
@@
 \pure{True} }, 
-\  \exists \code{es_1,es_2}. \  \code{es_1 {\cdot} es_2 {=} es}\\
+\  \exists \code{\es_1,\es_2}. \  \code{\es_1 {\cdot} \es_2 {=} es}\\
 &&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi 
 {\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
-(es_1\#t_1) {\cdot} (es_2\#t_2) } \\
+(\es_1\mysharp t_1) {\cdot} (\es_2\mysharp t_2) } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models es_1 {\vee} es_2}  
+&\code{d, \varphi \models \es_1 {\vee} \es_2}  
 &\m{iff}\quad 
-&  d, \varphi \models es_1 \ or \ d, \varphi \models es_2
+&  d, \varphi \models \es_1 \ or \ d, \varphi \models \es_2
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (es_1{\cdot}es_2)}  
+&\code{d, \varphi \models  \pi : (\es_1{\cdot}\es_2)}  
 &\m{iff}\quad 
@@
 & & &
-\code{d_1, \varphi_1 \models  \pi : es_1}  \ and \ 
-\code{d_2, \varphi_2 \models  \pi : es_2}  
+\code{d_1, \varphi_1 \models  \pi : \es_1}  \ and \ 
+\code{d_2, \varphi_2 \models  \pi : \es_2}  
  \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (es_1 {\vee} es_2)}  
+&\code{d, \varphi \models  \pi : (\es_1 {\vee} \es_2)}  
 &\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  es_1 } \ or \ 
- \code{d, \varphi \models  \pi :  es_2}  
+& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ or \ 
+ \code{d, \varphi \models  \pi :  \es_2}  
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : es \# t }  
+&\code{d, \varphi \models  \pi : es \mysharp  t }  
 &\m{iff}\quad 
@@
 \code{\mathcal{P}} denotes the program being checked. 
-With pre/post conditions declared for each method in \code{\mathcal{P}}, 
-we can apply modular verification to a method's body using Hoare-style 
-triples \code{\ \vdash \s{ \effect, \Pi } \ e\ 
-\s{\effect^\prime, \Pi^\prime}}
+The rules are in the Hoare-style triples: 
+\code{\ \vdash \s{ \Pi, \Theta } \ e\ 
+\s{\Pi^\prime, \Theta^\prime}},  where 
+$e$ is the given statement;
+\s{ \Pi, \Theta } refers to a set of program states. 
+The meaning of the transition rules, can be described as:
+
+\vspace{2mm}
+\qquad\qquad\quad \code{\s{ \Pi^\prime, \Theta^\prime } = 
+\wbigcup_{i{=}0}^{|\s{ \Pi, \Theta }| \text{-} 1}  
+\s{\pi_i^\prime, \es_i^\prime} \ \ where\ \ 
+ \vdash  \s{\pi_i, \es_i} \ p \ \s{\pi_i^\prime, \es_i^\prime}.} 
+\footnote{\code{|\s{ \Pi, \Theta }|} is the 
+size of \code{\s{ \Pi, \Theta }}.}
+\vspace{3mm}
+
+\begin{comment}
+
 where 
-\code{\effect} is the current effects, 
+\code{\Theta} is the current effects, 
 \code{\Pi} is the current guard, 
 %\code{\env} is the current valuation of the variables;
-and \s{\effect^\prime, \Pi^\prime}  
+and \s{\Pi_1, \Theta_1}  
 is the resulting state by executing \code{e}. 
 The program state is initialized using \s{\epsilon, True}. 
-
-\begin{comment}
   In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\timedL}, by formalising a set of forward inductive rules.
@@
 G {\defeq} \pi, \qquad\qquad
-H  {\defeq} \effect, \qquad\qquad
+H  {\defeq} \Theta, \qquad\qquad
 \env {\defeq} \code{var {\rightarrow} val }
@@
   }
-{  \vdash \{  \effect,\Pi \}\  v \ 
-\{ \effect, \Pi \}} \  
+{  \vdash \{  \Theta,\Pi \}\  v \ 
+\{ \Pi, \Theta \}} \  
  {[FV\text{-}Value]}} 
@@
   }
-{  \vdash \{  \effect, \Pi \}\  [b]\ e \ 
-\{ \effect, \Pi{\wedge} b  \}} \  
+{  \vdash \{  \Pi, \Theta \}\  [b]\ e \ 
+\{ \Pi, \Theta \}} \  
  {[FV\text{-}Guard]}} 
@@
   \code{\frac{ 
- \vdash \{ \effect, \Pi\} e_1  \{  \effect^\prime, \Pi^\prime\} 
-\ \  \ 
-\vdash \{ \effect^\prime, \Pi^\prime\} e_2  \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
+ \vdash \{ \Pi, \Theta\} \ e_1 \ \{  \Pi_1, \Theta_1\} 
+\ \  
+\vdash \{ \Pi_1, \Theta_1\} \ e_2 \  \{  \Pi_2, \Theta_2 \} 
 }{
-  \vdash \{  \effect, \Pi \}\  
-  e_1;e_2 \ \{ \effect^{\prime\prime}, \Pi^{\prime\prime}
+  \vdash \{  \Pi, \Theta \}\  
+  e_1;e_2 \ \{ \Pi_2, \Theta_2
   \}} 
    {[FV\text{-}Seq]}}  
+\  
+  \code{\frac{
+ \vdash \{ \Pi, \Theta \} \ e_1 \  \{  \Pi_1, \Theta_1\} 
 \ \  
-  \code{\frac{
- \vdash \{ \effect, \Pi \} e_1  \{  \effect^\prime, \Pi^\prime\} 
-\ \  \
-\vdash \{  \effect, \Pi \} e_2  \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
+\vdash \{  \Pi, \Theta \} \ e_2 \  \{  \Pi_2, \Theta_2 \} 
     }{
-\vdash \{   \effect, \Pi \}\  e_1 || e_2 \ \{ \effect^\prime || \effect^{\prime\prime}, 
-\Pi^{\prime} {\wedge}\Pi^{\prime\prime}
+\vdash \{   \Pi, \Theta \}\  e_1 || e_2 \ \{ \Theta_1 || \Theta_2, 
+\Pi^{\prime} {\wedge}\Pi_2
 \}}  
@@
     \begin{matrix}
-\vdash \{ \effect, \Pi {\wedge}  v   \} \ e_1 \ \{  \effect^{\prime} , \Pi^\prime \} 
-\qquad \vdash \{ \effect, \Pi {\wedge} \neg v  \} \ e_2 \ 
-\{  \effect^{\prime\prime}, \Pi^{\prime\prime} \}  
+\vdash \{ \Pi, \Theta {\wedge}  v   \} \ e_1 \ \{  \Theta^{\prime} , \Pi_1 \} 
+\qquad \vdash \{ \Pi, \Theta {\wedge} \neg v  \} \ e_2 \ 
+\{  \Pi_2, \Theta_2 \}  
 \qquad 
- \{  \effect_f, \Pi_f \} {=} \s{ \effect^{\prime} , \Pi^\prime} \cup \s{\effect^{\prime\prime}, \Pi^{\prime\prime}}
+ \{  \Theta_f, \Pi_f \} {=} \s{ \Theta^{\prime} , \Pi_1} \cup \s{\Pi_2, \Theta_2}
 \end{matrix}}
-  {\vdash \s{ \effect, \Pi}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
-  \textbf{else}\ e_2 \ \{  \effect_f, \Pi_f \} } \  
+  {\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
+  \textbf{else}\ e_2 \ \{  \Theta_f, \Pi_f \} } \  
   {[FV\text{-}If\text{-}Else]}} 
@@
   \code{\frac{
-    \effect^\prime {=} \effect\cdot \anyevent{A}(v, \Pi, \alpha^*) 
-    }
-  {\vdash \s{ \effect, \Pi} \  
+    \Theta_1 {=} \Theta\cdot \anyevent{A}(v, \Pi, \alpha^*) 
+    }
+  {\vdash \s{ \Pi, \Theta} \  
   \textbf{event} [\anyevent{A}(v, \alpha^*)] 
-   \ \{ \effect^\prime, True \}} \   {[FV\text{-}Event]}} 
+   \ \{ \Theta_1, True \}} \   {[FV\text{-}Event]}} 
    \qquad
   \code{\frac{
-    \effect^\prime {=} \effect\cdot \epsilon\#t \quad (t\ is\ fresh) 
-    }
-  {\vdash \s{ \effect, \Pi} \  
+    \Theta_1 {=} \Theta\cdot \epsilon\mysharp t \quad (t\ is\ fresh) 
+    }
+  {\vdash \s{ \Pi, \Theta} \  
   \textbf{delay} [d] 
-   \ \{ \effect^\prime, True \}} \   {[FV\text{-}Delay]}} 
+   \ \{ \Theta_1, True \}} \   {[FV\text{-}Delay]}} 
 \end{gather*}}}
@@
     \begin{matrix}
-      \vdash \{ \epsilon, \Pi \}\ e_1 \ \{  \effect^\prime, \Pi^\prime\} 
+      \vdash \{ \epsilon, \Pi \}\ e_1 \ \{  \Pi_1, \Theta_1\} 
       \qquad 
-      \vdash \{  \epsilon, \Pi \}\ e_2 \ \{  \effect^{\prime\prime}, \Pi^{\prime\prime} \} 
-      \\
-      \s{\effect_f, \Pi_f} {=} \s{\effect {\cdot}(\effect^\prime\#t), \Pi^\prime {\wedge}t{\leq}d}
+      \vdash \{  \epsilon, \Pi \}\ e_2 \ \{  \Pi_2, \Theta_2 \} 
+      \\
+      \s{\Theta_f, \Pi_f} {=} \s{\Theta {\cdot}(\Theta_1\mysharp t), \Pi_1 {\wedge}t{\leq}d}
       \cup 
-  \s{\effect {\cdot}(\effect^{\prime\prime}\#t), \Pi^{\prime\prime} {\wedge}t{>}d}   
+  \s{\Theta {\cdot}(\Theta_2\mysharp t), \Pi_2 {\wedge}t{>}d}   
   \quad (t\ is\ fresh)     
@@
   }
-  {\vdash \s{ \effect, \Pi} \  
+  {\vdash \s{ \Pi, \Theta} \  
   e_1\ \textbf{timeout} [d] \  e_2
-   \ \s{\effect_f, \Pi_f} } \   {[FV\text{-}Timeout]}} 
+   \ \s{\Theta_f, \Pi_f} } \   {[FV\text{-}Timeout]}} 
 \end{gather*}}}
@@
     \begin{matrix}
-      \vdash \{ \epsilon, \Pi \}\ e \ \{  \effect^\prime, \Pi^\prime\} 
+      \vdash \{ \epsilon, \Pi \}\ e \ \{  \Pi_1, \Theta_1\} 
       \qquad 
-      \s{\effect_f, \Pi_f} {=} \s{\effect {\cdot}(\effect^\prime\#t), \Pi^\prime {\wedge}t{\leq}d}
+      \s{\Theta_f, \Pi_f} {=} \s{\Theta {\cdot}(\Theta_1\mysharp t), \Pi_1 {\wedge}t{\leq}d}
   \quad (t\ is\ fresh)     
@@
   }
-  {\vdash \s{ \effect, \Pi} \  
+  {\vdash \s{ \Pi, \Theta} \  
   \textbf{deadline}  [d] \ e 
-   \ \s{\effect_f, \Pi_f} } \   {[FV\text{-}Deadline]}} 
+   \ \s{\Theta_f, \Pi_f} } \   {[FV\text{-}Deadline]}} 
 \end{gather*}}}
@@
 \begin{matrix}
-{\code{  mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
-\\
-\text{\code{\vdash  \effect \CONTAIN [v^*/x^*] \effect_{pre}   \qquad   \effect^\prime =  \effect \cdot  [y^*/x^*]\effect_{post}}}
+{\code{  mn  \ {x^*}\ \{\textbf{req}\ \Theta_{pre}\ \textbf{ens}\  \Theta_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
+\\
+\text{\code{\vdash  \Theta \CONTAIN [v^*/x^*] \Theta_{pre}   \qquad   \Theta_1 =  \Theta \cdot  [y^*/x^*]\Theta_{post}}}
 \end{matrix}}
-{\vdash \s{ \effect, \Pi} \ mn({v^*})  \ 
-\{  \effect^\prime,  \Pi\}} \ {[FV\text{-}Call]}}
+{\vdash \s{ \Pi, \Theta} \ mn({v^*})  \ 
+\{  \Theta_1,  \Pi\}} \ {[FV\text{-}Call]}}
 \ \quad 
 \code{\frac{  \vdash \{  \empt, True \} 
- \ e \  \{ \effect, \Pi \} \quad  \vdash\effect \CONTAIN  
-  \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ 
-  \textbf{ens}\  \effect_{post}\} \ \{ e \}} \  {[FV\text{-}Meth]}}  
+ \ e \  \{ \Pi, \Theta \} \quad  \vdash\Theta \CONTAIN  
+  \Theta_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \Theta_{pre}\ 
+  \textbf{ens}\  \Theta_{post}\} \ \{ e \}} \  {[FV\text{-}Meth]}}  
 \end{gather*}}}
@@
 Next we provide the definitions and implementations of auxiliary functions \emph{Nullable}(\code{\delta}), \emph{First}(\code{fst}) and \emph{Derivative}(\code{D}) respectively.
-Intuitively, the Nullable function \code{\delta(\effect)} returns a boolean value indicating whether \code{\effect} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \effect)} computes a set of possible initial time instances of \code{\pure{\pi} : \effect}; and the Derivative function \code{D_{I\# t}^{\pure{\pi}}(\effect)} computes a next-state effects after eliminating one event \code{I} w.r.t.
+Intuitively, the Nullable function \code{\delta(\effect)} returns a boolean value indicating whether \code{\effect} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \effect)} computes a set of possible initial time instances of \code{\pure{\pi} : \effect}; and the Derivative function \code{D_{I\mysharp  t}^{\pure{\pi}}(\effect)} computes a next-state effects after eliminating one event \code{I} w.r.t.
 the execution time \code{t} from the current effects \code{\pure{\pi} : \effect}.
@@
 \qquad\qquad\quad
- \code{\delta(\effect \# t) {=} \delta(\effect)}
+ \code{\delta(\effect \mysharp  t) {=} \delta(\effect)}
 \end{gather*}}
@@
 \begin{definition}[Antimirov's First]\label{First1}
-Let \code{fst^\prime(\effect){:=}\{ I\ |\  (I \cdot \effect^\prime) \in \llbracket  \effect \rrbracket  \}} be the set of initial instances derivable from  sequence \code{\effect}.
+Let \code{fst^\prime(\effect){:=}\{ I\ |\  (I \cdot \effect_1) \in \llbracket  \effect \rrbracket  \}} be the set of initial instances derivable from  sequence \code{\effect}.
 (\code{\llbracket  \effect \rrbracket } represents all the traces contained in \code{\effect}.)
@@
 any arithmetic constraints, nor 
-the real-time bounds constructor \code{\#}. Next, we define the novel  \emph{First} function used in this work, denoted using \code{fst}. 
+the real-time bounds constructor \code{\mysharp }. Next, we define the novel  \emph{First} function used in this work, denoted using \code{fst}. 
 %but helps to build up our \emph{First} function \code{fst}.
@@
 \begin{definition}[First]\label{First}
-Let \code{fst_{\pure{\pi}}(\effect){:=}\{ (I,  \pi, t) \ |\  \pi {\wedge} t{\geq}0 : (I\# t) \cdot \effect^\prime \in \llbracket  \pi {:} \effect \rrbracket \}} be the set of initial time instances derivable from effects \code{\pi {:} \effect}.
+Let \code{fst_{\pure{\pi}}(\effect){:=}\{ (I,  \pi, t) \ |\  \pi {\wedge} t{\geq}0 : (I\mysharp  t) \cdot \effect_1 \in \llbracket  \pi {:} \effect \rrbracket \}} be the set of initial time instances derivable from effects \code{\pi {:} \effect}.
 (\code{\llbracket  \pi {:} \effect \rrbracket } represents all the time  traces contained in \code{\pi {:} \effect})
@@
 \qquad\quad
-   \code{fst_{\pure{\pi}}(  \effect \# t) {=}  fst_{pi}(\effect)}
+   \code{fst_{\pure{\pi}}(  \effect \mysharp  t) {=}  fst_{pi}(\effect)}
  \\
@@
 }]\label{Derivative}
-The partial derivative \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect)} 
+The partial derivative \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect)} 
 of effects \code{\pi : \effect} 
 w.r.t.
-a event \code{(I, \pi^\prime, t^\prime)} computes the  effects for the left quotient \code{(I, \pi^\prime, t^\prime)^{\text{-}1}\llbracket \pi : \effect \rrbracket}.
-\footnote{For understanding of the derivative rule for \code{\effect\# t} (cf.
+a event \code{(I, \Pi_1, t^\prime)} computes the  effects for the left quotient \code{(I, \Pi_1, t^\prime)^{\text{-}1}\llbracket \pi : \effect \rrbracket}.
+\footnote{For understanding of the derivative rule for \code{\effect\mysharp  t} (cf.
 \tabref{tab:rewriting_tree_send}  step \textcircled{3}), it is essentially splitting \code{\effect} with a head and a tail, bound with fresh terms \code{t_1} and \code{t_2} respectively.
@@
 \begin{gather*}
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\bott) {=}}  
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\bott) {=}}  
  \code{False : \bott} 
 \qquad\ 
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \empt) {=}}   
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \empt) {=}}   
 \code{False : \bott} 
 \qquad \ 
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect_1 ||\effect_2)} {=} \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect_1)} || \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect_2)} 
-    \\
-        \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\effect^\star}) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  {\effect}) \cdot ({\effect^\star})}  
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect_1 ||\effect_2)} {=} \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect_1)} || \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect_2)} 
+    \\
+        \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  {\effect^\star}) } {=} \code{ D^{\pi}_{(I, \Pi_1, t^\prime)}(  {\effect}) \cdot ({\effect^\star})}  
         \qquad\qquad
@@
 {
- \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \effect_1 \seq \effect_2) {=} }
+ \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(   \effect_1 \seq \effect_2) {=} }
 \begin{cases}
-      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(   \effect_1) \cdot  \effect_2 \vee  D^{\pi}_{(I, \pi^\prime, t^\prime)}( \effect_2)} \quad &\code{if\ \delta(\effect_1) {=} true}   \\
-      \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}  ( \effect_1) \cdot  \effect_2} & \code{if\ \delta(\effect_1) {=} false} 
+      \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(   \effect_1) \cdot  \effect_2 \vee  D^{\pi}_{(I, \Pi_1, t^\prime)}( \effect_2)} \quad &\code{if\ \delta(\effect_1) {=} true}   \\
+      \code{D^{\pi}_{(I, \Pi_1, t^\prime)}  ( \effect_1) \cdot  \effect_2} & \code{if\ \delta(\effect_1) {=} false} 
     \end{cases} 
@@
  \\
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1 \choice \effect_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1) \choice D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_2)} 
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1 \choice \effect_2) } {=} \code{ D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1) \choice D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_2)} 
 %\\
-%\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1 \ ||\  \effect_2) } {=} \code{ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_1) \ ||\ D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect_2)} 
-\\
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(  \effect \# t) } {=}
+%\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1 \ ||\  \effect_2) } {=} \code{ D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1) \ ||\ D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_2)} 
+\\
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect \mysharp  t) } {=}
 \code{
-\pi \wedge(t_1{+} t_2 {=}t) \wedge (t_1{=}t^\prime) : (D^{\pi}_{(I, \pi^\prime, t^\prime)}(\effect))\# t_2} \ \ \ 
+\pi \wedge(t_1{+} t_2 {=}t) \wedge (t_1{=}t^\prime) : (D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect))\mysharp  t_2} \ \ \ 
 \code{(fresh \ t_1\ t_2 )}
 \\
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} \{\textbf{S}\})}
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} \{\textbf{S}\})}
 \qquad
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \textbf{S}?\ (}\code{ I {\not\subseteq} \{\textbf{S}\})}
-\\
-\code{D^{\pi}_{(I, \pi^\prime, t^\prime)}(J)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} J)}
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \textbf{S}?\ (}\code{ I {\not\subseteq} \{\textbf{S}\})}
+\\
+\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(J)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} J)}
 \qquad\ 
-    \code{D^{\pi}_{(I, \pi^\prime, t^\prime)}( J)} {=} \code{False : \bott \ (}\code{I {\not\subseteq} J)} 
+    \code{D^{\pi}_{(I, \Pi_1, t^\prime)}( J)} {=} \code{False : \bott \ (}\code{I {\not\subseteq} J)} 
 \end{gather*}
@@
 We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A11), suggested by \cite{salomaa1966two}, which was designed for regular languages.
-We develop axioms (A12) to (A22) to further accommodate effects constructed by \code{||},   \code{\#} and \code{\omega}.
+We develop axioms (A12) to (A22) to further accommodate effects constructed by \code{||},   \code{\mysharp } and \code{\omega}.
 
@@
 (A17)  &
- \code{(I\# t) \cdot \effect_1\ ||\ J \cdot\effect_2 \rightarrow ((I  {\cup} J) \# t) \cdot (\effect_1 || \effect_2)}\\
+ \code{(I\mysharp  t) \cdot \effect_1\ ||\ J \cdot\effect_2 \rightarrow ((I  {\cup} J) \mysharp  t) \cdot (\effect_1 || \effect_2)}\\
 \hline
 (A18)  &
-\code{\pi : (\effect \# t_1 ) \# t_2 \rightarrow \pi  \wedge (t_1 {=} t_2) : \effect \# t_1 }\\
+\code{\pi : (\effect \mysharp  t_1 ) \mysharp  t_2 \rightarrow \pi  \wedge (t_1 {=} t_2) : \effect \mysharp  t_1 }\\
 \hline
 (A19)  &
- \code{\empt \# t \rightarrow \empt}\\
+ \code{\empt \mysharp  t \rightarrow \empt}\\
 \hline
 (A20)  &
- \code{\bot \# t \rightarrow  \bott}\\
+ \code{\bot \mysharp  t \rightarrow  \bott}\\
 \hline
@@
 %        \vspace{-2mm}
-%\caption{\label{tab:Experimental} The experiments are based on 16 real world C programs, we record the lines of code (LOC), the number of testing temporal properties ($\#$Prop.), and the (dis-) proving times (in time units) using PAT and our T.r.s respectively.
+%\caption{\label{tab:Experimental} The experiments are based on 16 real world C programs, we record the lines of code (LOC), the number of testing temporal properties ($\mysharp $Prop.), and the (dis-) proving times (in time units) using PAT and our T.r.s respectively.
 }
@@
 %\hline
-%\textbf{Programs} & \textbf{LOC} & \textbf{$\#$Prop.}  & \textbf{PAT(ms)} & \textbf{T.r.s(ms)} \\ \hline\hline
+%\textbf{Programs} & \textbf{LOC} & \textbf{$\mysharp $Prop.}  & \textbf{PAT(ms)} & \textbf{T.r.s(ms)} \\ \hline\hline
 %1. Chrome\_Dino\_Game    &      80    &    12  &  32.09 &  7.66  \\ \hline
@@
 %  \code{
-%    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \# t_L \cdot \{B\}
+%    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
 %    \CONTAIN
-%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
+%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
 %  }
@@
 %    \textcolor {darkred}{True} : {B} \CONTAIN
-%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
+%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
 %  }.
@@
 %in . 
-In step \code{\textcircled{2}} of the first sub-tree, in order to eliminate the first event \code{\{B\}}, \code{\{A\}^\star \# t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
+In step \code{\textcircled{2}} of the first sub-tree, in order to eliminate the first event \code{\{B\}}, \code{\{A\}^\star \mysharp  t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
 % is 
@@
 Then in step \code{\textcircled{6}}, 
-\code{\{A\} \# t_L^1} together with \code{\{A\} \# t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
+\code{\{A\} \mysharp  t_L^1} together with \code{\{A\} \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
 %, also
@@
     \textcolor {darkred}{True} : \{B\} \CONTAIN
-    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
+    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
   }
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \# t_L {\cdot} \{B\}
+    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \mysharp  t_L {\cdot} \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \# t_R {\cdot} \{B\}
+    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \mysharp  t_R {\cdot} \{B\}
   }
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \# t_L \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
     \vee \textcolor {darkred}{True} : \{B\} \CONTAIN
-    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}
+    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
   }
@@
     } :
-     \{A\}^\star \# t_L^2 \cdot \{B\}
+     \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} :
-     \{A\}^\star \# t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
+     \{A\}^\star \mysharp  t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
   }
@@
     } :
-     \cancel{\{A\} \# t_L^1} {\cdot} \{A\}^\star \# t_L^2 \cdot \{B\}
+     \cancel{\{A\} \mysharp  t_L^1} {\cdot} \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} :
-     \cancel{\{A\} \# t_R^1} {\cdot} \{A\}^\star \# t_R^2 \cdot \{B\}
+     \cancel{\{A\} \mysharp  t_R^1} {\cdot} \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
   }
@@
     \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L {\wedge} t_R{=}t_R^1{+}t_R^2} :
-     ( \{A\} \# t_L^1 {\cdot} \{A\}^\star \# t_L^2) \cdot \{B\}
+     ( \{A\} \mysharp  t_L^1 {\cdot} \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} :
-     ( \{A\} \# t_R^1 {\cdot} \{A\}^\star \# t_R^2) \cdot \{B\}
+     ( \{A\} \mysharp  t_R^1 {\cdot} \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
   }
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \# t_L \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \# t_R \cdot \{B\}  \quad \textcolor{darklavender}{(\ddagger)}
+    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}  \quad \textcolor{darklavender}{(\ddagger)}
   }
@@
 In particularly, SKA's \emph{demanding relation} can be reflected by our \emph{instances subsumption} (\defref{Subsumption}), which contributes to the inductive unfolding process.
-Yet our timed effects further capture the time bounds constraints by adding the operator \code{\#}, adapting to real-time system modelling and verification, which is not covered by any existing KA variants/extensions.
+Yet our timed effects further capture the time bounds constraints by adding the operator \code{\mysharp }, adapting to real-time system modelling and verification, which is not covered by any existing KA variants/extensions.
 

### 2022-04-07 paper/tv.tex
m

@@
 
-\newcommand{\mysharp}{\mathrel{\texttt{\#}}}
+\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
 
@@
 \s{\pi_i^\prime, \es_i^\prime} \ \ where\ \ 
- \vdash  \s{\pi_i, \es_i} \ p \ \s{\pi_i^\prime, \es_i^\prime}.} 
+ \vdash  \s{\pi_i, \es_i} \ e \ \s{\pi_i^\prime, \es_i^\prime}.} 
 \footnote{\code{|\s{ \Pi, \Theta }|} is the 
@@
 
+$[FV\text{-}\m{Value}]$  obtains the next program state by 
+inheriting the current program state.
+$[FV\text{-}Guard]$ updates the event sequences with with
+the guard \code{b}. 
 {{\small\begin{gather*}
@@
   }
-{  \vdash \{  \Theta,\Pi \}\  v \ 
+{  \vdash \{  \Pi, \Theta \}\  v \ 
 \{ \Pi, \Theta \}} \  
@@
  \code{\frac{
+  \vdash \{  \Pi, \Theta \}\  e \ 
+  \{ \Pi^\prime, \Theta^\prime \}
   }
 {  \vdash \{  \Pi, \Theta \}\  [b]\ e \ 
-\{ \Pi, \Theta \}} \  
+\{  \Pi^\prime, b? \Theta^\prime \}} \  
  {[FV\text{-}Guard]}} 
@@
 
+$[FV\text{-}Seq]$ infers  \code{ \{  \Pi_1, \Theta_1\} } 
+from \code{e_1}, 
+then further computes  \code{ \{  \Pi_2, \Theta_2 \} } by 
+continuously infer the behaviors of \code{e_2}, to be the final state.
+$[FV\text{-}Par]$ infers behaviors for  \code{e_1} and \code{e_2} independently,
+then parallel merges the effects from these two branches.  
 {{\small\begin{gather*}
@@
     }{
-\vdash \{   \Pi, \Theta \}\  e_1 || e_2 \ \{ \Theta_1 || \Theta_2, 
-\Pi^{\prime} {\wedge}\Pi_2
+\vdash \{   \Pi, \Theta \}\  e_1 || e_2 \ \{ 
+\Pi_1 {\wedge}\Pi_2 , \Theta_1 || \Theta_2
 \}}  
@@
     \begin{matrix}
-\vdash \{ \Pi, \Theta {\wedge}  v   \} \ e_1 \ \{  \Theta^{\prime} , \Pi_1 \} 
-\qquad \vdash \{ \Pi, \Theta {\wedge} \neg v  \} \ e_2 \ 
+\vdash \{ \Pi{\wedge} v, \Theta    \} \ e_1 \ \{  \Theta^{\prime} , \Pi_1 \} 
+\qquad 
+\vdash \{ \Pi{\wedge} \neg v , \Theta  \} \ e_2 \ 
 \{  \Pi_2, \Theta_2 \}  
-\qquad 
- \{  \Theta_f, \Pi_f \} {=} \s{ \Theta^{\prime} , \Pi_1} \cup \s{\Pi_2, \Theta_2}
+\qquad (v\ is\ local)
 \end{matrix}}
   {\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
-  \textbf{else}\ e_2 \ \{  \Theta_f, \Pi_f \} } \  
-  {[FV\text{-}If\text{-}Else]}} 
+  \textbf{else}\ e_2 \ \s{ \Theta^{\prime} , \Pi_1} {\cup} \s{\Pi_2, \Theta_2} } \  
+  {[FV\text{-}If\text{-}Else\text{-}Local]}} 
+\\
+\code{\frac{ 
+  \begin{matrix}
+\vdash \{ \Pi, \Theta    \} \ e_1 \ \{  \Theta^{\prime} , \Pi_1 \} 
+\qquad 
+\vdash \{ \Pi , \Theta  \} \ e_2 \ 
+\{  \Pi_2, \Theta_2 \}  
+\qquad (v\ is\ global)
+\end{matrix}}
+{\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
+\textbf{else}\ e_2 \ \s{\Pi, v. \Theta_1 \vee \Theta_2 }} \  
+{[FV\text{-}If\text{-}Else\text{-}Global]}} 
   \end{gather*}}}
@@
   \code{\frac{
-    \Theta_1 {=} \Theta\cdot \anyevent{A}(v, \Pi, \alpha^*) 
+    \Theta^\prime {=} \Theta\cdot \anyevent{A}(v, \alpha^*) 
     }
@@
   \textbf{event} [\anyevent{A}(v, \alpha^*)] 
-   \ \{ \Theta_1, True \}} \   {[FV\text{-}Event]}} 
+   \ \{\Pi, \Theta^\prime \}} \   {[FV\text{-}Event]}} 
    \qquad
   \code{\frac{
-    \Theta_1 {=} \Theta\cdot \epsilon\mysharp t \quad (t\ is\ fresh) 
+    \Theta^\prime {=} \Theta\cdot \epsilon\mysharp t \quad (t\ is\ fresh) 
     }
@@
   \textbf{delay} [d] 
-   \ \{ \Theta_1, True \}} \   {[FV\text{-}Delay]}} 
+   \ \{ \Pi{\wedge} t {=}d,  \Theta^\prime \}} \   {[FV\text{-}Delay]}} 
 \end{gather*}}}
@@
       \\
-      \s{\Theta_f, \Pi_f} {=} \s{\Theta {\cdot}(\Theta_1\mysharp t), \Pi_1 {\wedge}t{\leq}d}
+      \s{\Theta_f, \Pi_f} {=} \s{\Pi_1 {\wedge}t{\leq}d, \Theta {\cdot}(\Theta_1\mysharp t)}
       \cup 
-  \s{\Theta {\cdot}(\Theta_2\mysharp t), \Pi_2 {\wedge}t{>}d}   
+  \s{\Pi_2 {\wedge}t{>}d, \Theta {\cdot}(\Theta_2\mysharp t)}   
   \quad (t\ is\ fresh)     
@@
       \vdash \{ \epsilon, \Pi \}\ e \ \{  \Pi_1, \Theta_1\} 
-      \qquad 
-      \s{\Theta_f, \Pi_f} {=} \s{\Theta {\cdot}(\Theta_1\mysharp t), \Pi_1 {\wedge}t{\leq}d}
   \quad (t\ is\ fresh)     
@@
   \textbf{deadline}  [d] \ e 
-   \ \s{\Theta_f, \Pi_f} } \   {[FV\text{-}Deadline]}} 
+   \ \s{\Pi_1 {\wedge}t{\leq}d, \Theta {\cdot}(\Theta_1\mysharp t)} }   
+    {[FV\text{-}Deadline]}} 
+\ 
+\code{\frac{  \vdash \effect_{pre} 
+ \ e \  \{ \Pi, \Theta \} \quad   \{ \Pi, \Theta \} \CONTAIN  
+  \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ 
+  \textbf{ens}\  \effect_{post}\} \ \{ e \}}   {[FV\text{-}Meth]}}  
   \end{gather*}}}
@@
 \begin{matrix}
-{\code{  mn  \ {x^*}\ \{\textbf{req}\ \Theta_{pre}\ \textbf{ens}\  \Theta_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
-\\
-\text{\code{\vdash  \Theta \CONTAIN [v^*/x^*] \Theta_{pre}   \qquad   \Theta_1 =  \Theta \cdot  [y^*/x^*]\Theta_{post}}}
+{\code{  mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
+\\
+\text{\code{ \s{ \Pi, \Theta} \CONTAIN [v^*/x^*] \effect_{pre}   
+\qquad   \effect_f =  \s{ \Pi, \Theta} \cdot  [y^*/x^*]\effect_{post}}}
 \end{matrix}}
 {\vdash \s{ \Pi, \Theta} \ mn({v^*})  \ 
-\{  \Theta_1,  \Pi\}} \ {[FV\text{-}Call]}}
-\ \quad 
-\code{\frac{  \vdash \{  \empt, True \} 
- \ e \  \{ \Pi, \Theta \} \quad  \vdash\Theta \CONTAIN  
-  \Theta_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \Theta_{pre}\ 
-  \textbf{ens}\  \Theta_{post}\} \ \{ e \}} \  {[FV\text{-}Meth]}}  
+\effect_f} \ {[FV\text{-}Call]}}
 \end{gather*}}}

### 2022-04-08 paper/tv.tex
m

@@
 \definecolor{color_pure}{RGB}{3,35,14}
-\newcommand\pure[1]{ \textcolor{black}{#1}}
 \usepackage{epigraph}
@@
     \code{
-          (\pure{\pi}, \es)
+          {\pi} \wedge \es
    \ | \ \effect_1 \vee \effect_2
@@
 
-    \m{(Pure)}  & \code{\code{\pure{\pi}}}&\code{  ::= }&
-\pure{ \pure{True}}
-   \ |  \pure{False}
-   \ |  \pure{A(}{t_1, t_2}\pure{)}
-  \  |   \pure{\pure{\pi_1}} {\wedge} \code{\pure{\pi}}_2
-   \ |  \pure{\pure{\pi_1}} {\vee} \code{\pure{\pi}}_2
-   \ |  \neg\code{\pure{\pi}}
-  \  |   \pure{\pure{\pi_1}} {\Rightarrow} \pure{\pure{\pi_2}}
-   \ |  \forall x. \code{\pure{\pi}}
-   \ |  \exists x. \code{\pure{\pi}}
+    \m{(Pure)}  & \code{\code{{\pi}}}&\code{  ::= }&
+{ {True}}
+   \ |  {False}
+   \ |  {A(}{t_1, t_2}{)}
+  \  |   {{\pi_1}} {\wedge} \code{{\pi}}_2
+   \ |  {{\pi_1}} {\vee} \code{{\pi}}_2
+   \ |  \neg\code{{\pi}}
+  \  |   {{\pi_1}} {\Rightarrow} {{\pi_2}}
+   \ |  \forall x. \code{{\pi}}
+   \ |  \exists x. \code{{\pi}}
 
@@
 \figref{fig:Syntax_of_Types_and_Effects} Effects is 
- a conditioned time  event sequence \code{\pure{\pi},  es} or a disjunction of two effects $\es_1 \vee \es_2$.
+ a conditioned time  event sequence \code{{\pi},  es} or a disjunction of two effects $\es_1 \vee \es_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
@@
 
-We use \code{\pure{\pi}} to donate a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
-We use \code{\pure{A(}{t_1, t_2}\pure{)}} to represent atomic formulas of two terms (including $  {=},
+We use \code{{\pi}} to donate a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
+We use \code{{A(}{t_1, t_2}{)}} to represent atomic formulas of two terms (including $  {=},
    \ {>},
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s,  \varphi \models \pure{\pi}  , \empt}  
-&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
-\pure{True} } \ and\  \code{ \varphi {=} [] }\\
+&\code{d, s,  \varphi \models {\pi} \wedge \empt}  
+&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
+{True} } \ and\  \code{ \varphi {=} [] }\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  , \ev }  
-&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket \pure{\pi} \rrbracket_s {=}  
-\pure{True} }\ and \ \varphi {=} [\ev]  \\
+&\code{d, s, \varphi \models {\pi} \wedge \ev }  
+&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
+{True} }\ and \ \varphi {=} [\ev]  \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, (\es_1\cdot \es_2)}  
+&\code{d, s, \varphi \models {\pi} \wedge (\es_1\cdot \es_2)}  
 &\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
@@
 \code{ d_1 {+} d_2 {=} d} \\
-&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} \pure{\pi}  , \es_1 }
-\ and \ \code{d_2, s, \varphi_2 {\models} \pure{\pi}  , \es_2 }\\
+&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} {\pi}  \wedge \es_1 }
+\ and \ \code{d_2, s, \varphi_2 {\models} {\pi}  \wedge \es_2 }\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, \Pi_1.(\es_1{\vee}\es_2)}  
+&\code{d, s, \varphi \models {\pi} \wedge \pi_1.(\es_1{\vee}\es_2)}  
 &\m{iff}\quad & 
-\code{\llbracket \Pi_1  \rrbracket_{s} {=}  
- \pure{True} },\code{d, s, \varphi \models \pure{\pi}  , \es_1 } 
+\code{\llbracket \pi_1  \rrbracket_{s} {=}  
+ {True} },\code{d, s, \varphi \models {\pi}  \wedge \es_1 } 
 \ or\ 
-\code{\llbracket \Pi_1  \rrbracket_{s} {=}  
- \pure{False} },
-\code{d, s, \varphi \models \pure{\pi}  , \es_2 } \\
+\code{\llbracket \pi_1  \rrbracket_{s} {=}  
+ {False} },
+\code{d, s, \varphi \models {\pi}  \wedge \es_2 } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi} , (\ev_1{\cdot}\es_1)||(\ev_2{\cdot}\es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{\pi}  , \ev_1{\cdot} (\es_1||(\ev_2{\cdot}\es_2)) } 
-\ or\ \code{d, s, \varphi \models \pure{\pi}  , \ev_2{\cdot}((\ev_1{\cdot}\es_1)||\es_2)  } \\
+&\code{d, s, \varphi \models {\pi} \wedge (\ev_1{\cdot}\es_1)||(\ev_2{\cdot}\es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models {\pi}  \wedge \ev_1{\cdot} (\es_1||(\ev_2{\cdot}\es_2)) } 
+\ or\ \code{d, s, \varphi \models {\pi}  \wedge \ev_2{\cdot}((\ev_1{\cdot}\es_1)||\es_2)  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi} , (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {\geq}t_2)}, (\ev\mysharp t_1) } 
-\ or\ \code{d, s, \varphi \models \pure{(\pi{\wedge}t_1 {<}t_2)}  , (\ev\mysharp t_1){\cdot}(\epsilon \mysharp  (t_2\text{-}t_1))  } \\
+&\code{d, s, \varphi \models {\pi} \wedge (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models {(\pi{\wedge}t_1 {\geq}t_2)}, (\ev\mysharp t_1) } 
+\ or\ \code{d, s, \varphi \models {(\pi{\wedge}t_1 {<}t_2)}  , (\ev\mysharp t_1){\cdot}(\epsilon \mysharp  (t_2\text{-}t_1))  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, \Pi_1 ? es}  &\m{iff}\quad & 
-\code{\llbracket \Pi_1  \rrbracket_{s} {=}  
- \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , es}\ or  \ 
-  \code{\llbracket \Pi_1 \rrbracket_{s} {=}  
-\pure{False} }, 
-\  \code{d, s, \varphi \models \pure{\pi}, \Pi_1 ? es}\\
+&\code{d, s, \varphi \models {\pi} \wedge \pi_1 ? es}  &\m{iff}\quad & 
+\code{\llbracket \pi_1  \rrbracket_{s} {=}  
+ {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge es}\ or  \ 
+  \code{\llbracket \pi_1 \rrbracket_{s} {=}  
+{False} }, 
+\  \code{d, s, \varphi \models {\pi} \wedge \pi_1 ? es}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}  ,es\mysharp  t}  &\m{iff}\quad &
- \code{\llbracket \pure{\pi}  , t {=} 0 \rrbracket_{s} {=}  
- \pure{True} }, \ \code{d, s, \varphi \models \pure{\pi}  , \empt}\ or  \\
-& & &  \code{\llbracket \pure{\pi}, t {>} 0 \rrbracket_{s} {=}  
-\pure{True} }, 
+&\code{d, s, \varphi \models {\pi}  \wedge es\mysharp  t}  &\m{iff}\quad &
+ \code{\llbracket {\pi}  \wedge t {=} 0 \rrbracket_{s} {=}  
+ {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge \empt}\ or  \\
+& & &  \code{\llbracket {\pi}\wedge t {>} 0 \rrbracket_{s} {=}  
+{True} }, 
 \  \exists \code{\es_1,\es_2}. \  \code{\es_1 {\cdot} \es_2 {=} es}\\
-&&& \qquad  s.t. \ \code{d, s, \varphi {\models} \pure{(\pi 
+&&& \qquad  s.t. \ \code{d, s, \varphi {\models} {(\pi 
 {\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \pure{\pi}, es^\star}  &\m{iff}\quad & 
-\code{d, s, \varphi \models \pure{\pi}  , \empt}\ or \ 
-\code{d, s, \varphi \models \pure{\pi}  , es {\cdot} es^\star}\\
+&\code{d, s, \varphi \models {\pi}\wedge es^\star}  &\m{iff}\quad & 
+\code{d, s, \varphi \models {\pi}  \wedge \empt}\ or \ 
+\code{d, s, \varphi \models {\pi}  \wedge es {\cdot} es^\star}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 & \code{d, s, \varphi \models false}  &\m{iff}\quad &
- \code{\llbracket \pure{\pi}  \rrbracket_{s} {=} \pure{False} } \ or \ \code{\varphi {=} \bott}
+ \code{\llbracket {\pi}  \rrbracket_{s} {=} {False} } \ or \ \code{\varphi {=} \bott}
 \end{align*}
@@
 %{\tt{UNSAT}(\pi)}  \ or \  \varphi  {=} \bot
-%\exists t, d(t) \not\models \llbracket \pure{\pi} \rrbracket_{t}
+%\exists t, d(t) \not\models \llbracket {\pi} \rrbracket_{t}
 \end{align*}
@@
 Now, the inclusions are disjunction-free formulas.
+
 Next we provide the definitions and implementations of auxiliary functions \emph{Nullable}(\code{\delta}), \emph{First}(\code{fst}) and \emph{Derivative}(\code{D}) respectively.
-Intuitively, the Nullable function \code{\delta(\effect)} returns a boolean value indicating whether \code{\effect} contains the empty trace; the First function \code{fst_{\pure{\pi}}( \effect)} computes a set of possible initial time instances of \code{\pure{\pi} : \effect}; and the Derivative function \code{D_{I\mysharp  t}^{\pure{\pi}}(\effect)} computes a next-state effects after eliminating one event \code{I} w.r.t.
-the execution time \code{t} from the current effects \code{\pure{\pi} : \effect}.
+Intuitively, the Nullable function \code{\delta(\effect)} returns a boolean value indicating whether \code{\effect} contains the empty trace; the First function \code{fst_{{\pi}}( \effect)} computes a set of possible initial time instances of \code{{\pi} : \effect}; and the Derivative function \code{D_{I\mysharp  t}^{{\pi}}(\effect)} computes a next-state effects after eliminating one event \code{I} w.r.t.
+the execution time \code{t} from the current effects \code{{\pi} : \effect}.
+
+Next we provide the definitions and the key implementations\footnote{As 
+the implementations according to basic regular expressions can be found 
+in prior work \cite{keil2014symbolic}. 
+%Here, we focus on presenting 
+%the definitions and how do we deal with dependent values in the effects, 
+%as the key novelties of this work. 
+%More detail implementations can be found in the extended technical report\citeref{Demo}.
+} of Nullable, First and Derivative respectively. Intuitively, 
+the Nullable function \code{\delta_{{\pi}}(\es)} returns a boolean 
+value indicating whether \code{{\pi} \wedge \es} contains the empty 
+trace; the First function \code{fst_{{\pi}}( \es)} computes a set of 
+possible initial events of \code{{\pi} \wedge \es}; and the Derivative 
+function \code{D_{\anyevent{a}}^{{\pi}}(\es)} computes a next-state 
+effects after eliminating one event \code{\anyevent{a}} from the current 
+effects \code{{\pi} \wedge \es}.
 
@@
 \begin{definition}[Nullable]\label{Nullable}
-Given any time sequence \code{\effect}, we recursively define \code{\delta(\effect)} as:\\
+Given any timed sequence \code{\es} under condition \code{{\pi}}, we define \code{\delta_{{\pi}}(\es)} to be:\\
 {
-\code{\delta(\effect) :bool {=}
+\code{\delta_{{\pi}}(\es) :bool {=}
 \begin{cases}
-      \code{true} & \code{if\ \empt \in \effect}\\
-      \code{false} & \code{if\ \empt \notin \effect}
+      \code{true} & \code{if\ \empt \in \llbracket {\pi} \wedge \es \rrbracket_{\varphi}}\\
+      \code{false} & \code{if\ \empt \notin \llbracket {\pi} \wedge \es \rrbracket_{\varphi}}
     \end{cases} }
-    }, where   
+    }, where\   
 { 
 \begin{gather*}
-\code{\delta(\bott) {=} false} 
+\code{\delta_{\pi}(\bott) {=} false} 
 \qquad\quad
-\code{\delta(\empt) {=} true} 
+\code{\delta_{\pi}(\empt) {=} true} 
 \qquad\quad
-\code{\delta(I){=} false}   
+\code{\delta_{\pi}(\ev){=} false}   
 \qquad\quad
-\code{\delta(\textbf{S}?){=} false}   
+\code{\delta_{\pi}(\pi^\prime? \es){=} \delta_{\pi}(\es)}   
 \qquad\quad\
-    \code{\delta({\effect^\star} ) {=} true}   
-\\ 
-\code{\delta(\effect_1 \seq \effect_2) {=} \delta(\effect_1) \wedge \delta(\effect_2)}
-\qquad\qquad
-  \code{\delta(\effect_1 \choice \effect_2) {=} \delta(\effect_1) \vee \delta(\effect_2)}   
-  \\
-\code{\delta(\effect_1 || \effect_2) {=} \delta(\effect_1) \wedge \delta(\effect_2)}
+    \code{\delta({\es^\star} ) {=} true}   
+\\ 
+\code{\delta_{\pi}(\es \seq \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
 \qquad\qquad\quad
- \code{\delta(\effect \mysharp  t) {=} \delta(\effect)}
+  \code{\delta_{\pi}(\es_1 \choice \es_2) {=} \delta(\es_1) \vee \delta(\es_2)}   
+  \\
+\code{\delta_{\pi}(\es_1 || \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
+\qquad\qquad\quad
+ \code{\delta_{\pi}(\es \mysharp  t) {=} SAT ({\pi} \wedge (t {=} 0) )}
 \end{gather*}}
@@
 
-To better outline our contribution, we first present the original \emph{First} function used in  Antimirov's rewriting system, denoted using \code{fst^\prime}, defined as follows:
-
-\begin{definition}[Antimirov's First]\label{First1}
-Let \code{fst^\prime(\effect){:=}\{ I\ |\  (I \cdot \effect_1) \in \llbracket  \effect \rrbracket  \}} be the set of initial instances derivable from  sequence \code{\effect}.
-(\code{\llbracket  \effect \rrbracket } represents all the traces contained in \code{\effect}.)
+%Next, we define the novel  \emph{First} function used in this work, denoted using \code{fst}. 
+%but helps to build up our \emph{First} function \code{fst}.
+
+\begin{definition}[First]\label{First}
+  Let \code{fst_{{\pi}}(\es): \{ (\ev,  t)  | 
+  \pi {\wedge} t{\geq}0 \wedge (\ev \mysharp  t) {\cdot} \es_1 \in \llbracket  
+  \pi \wedge \es \rrbracket \}} be the set of initial timed events  
+  derivable from effects \code{\pi \wedge \es}. (\code{\llbracket  \pi \wedge
+   \es \rrbracket } represents all the timed  traces contained in 
+   \code{\pi \wedge \es}) 
   { 
    \begin{gather*} 
-\code{fst^\prime( \bott) {=} \_ } \qquad\ 
-\code{ fst^\prime(\empt) {=} \_} \qquad\ 
-\code{fst^\prime( I) {=} \{ I \} }
- \qquad\ 
-\code{fst^\prime(  \effect_1 {\vee} \effect_2) {=} fst^\prime(  \effect_1) \cup fst^\prime(  \effect_2)}
+  \code{fst_{{\pi}}( \bott) {=} \{\} } \qquad\quad
+  \code{fst_{{\pi}}(\empt) {=}  \{\} } \qquad\quad
+  \code{fst_{{\pi}}( \ev) {=} \{ (\ev, t) \}  \ (t\ is\ fresh)} 
+  \qquad\quad
+     \code{fst_{{\pi}}(  \es \mysharp  t) {=}  fst_{\pi}(\es)}
+   \\
+  \code{fst_{{\pi}}( {\es^\star} ) {=} fst_{{\pi}}({ \es})}
+  \qquad\ \ \  
+  \qquad\quad
+  \code{fst_{{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }  \\
+  \code{fst_{{\pi}}( \pi^\prime? \es ) {=} fst_{\pi}(\es)  }
+      \qquad\qquad\quad
+     \code{fst_{{\pi}}(  \es_1 {||} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }   
      \\
   {
-\code{fst^\prime( {\effect^\star} ) {=} fst^\prime({ \effect})} 
-\qquad\quad\
-\code{fst^\prime(\effect_1 {\seq} \effect_2) {=} } 
+  \code{fst_{{\pi}}(\es_1 {\seq} \es_2) {=} } 
   \begin{cases}
-      \code{\code{fst^\prime(  \effect_1)} \cup \code{fst^\prime(  \effect_2)} } \quad & \code{ if\ \delta(\effect_1) {=} true}\\
-      \code{\code{fst^\prime(  \effect_1)}} & \code{  if\ \delta(\effect_1) {=} false}
-    \end{cases} 
-    }
-\end{gather*}
-}
-\end{definition}
-
-As shown, \code{fst^\prime} does not handle 
-%the concurrent operator \code{||} nor contains 
-any arithmetic constraints, nor 
-the real-time bounds constructor \code{\mysharp }. Next, we define the novel  \emph{First} function used in this work, denoted using \code{fst}. 
-%but helps to build up our \emph{First} function \code{fst}.
-
-\begin{definition}[First]\label{First}
-Let \code{fst_{\pure{\pi}}(\effect){:=}\{ (I,  \pi, t) \ |\  \pi {\wedge} t{\geq}0 : (I\mysharp  t) \cdot \effect_1 \in \llbracket  \pi {:} \effect \rrbracket \}} be the set of initial time instances derivable from effects \code{\pi {:} \effect}.
-(\code{\llbracket  \pi {:} \effect \rrbracket } represents all the time  traces contained in \code{\pi {:} \effect})
-{ 
- \begin{gather*} 
-\code{fst_{\pure{\pi}}( \bott) {=} \_ } \qquad\quad
-\code{fst_{\pure{\pi}}(\empt) {=} \_ } \qquad\quad
-\code{fst_{\pure{\pi}}( I ) {=} \{ (I, \pi {\wedge} t{\geq}0, t) \}  \ (t\ is\ fresh)} 
-\qquad\quad
-   \code{fst_{\pure{\pi}}(  \effect \mysharp  t) {=}  fst_{pi}(\effect)}
- \\
-\code{fst_{\pure{\pi}}( {\effect^\star} ) {=} fst_{\pure{\pi}}({ \effect})}
-\qquad\quad
-\qquad\quad
-\code{fst_{\pure{\pi}}(  \effect_1 {\vee} \effect_2) {=} fst_{\pure{\pi}}(  \effect_1) \cup fst_{\pure{\pi}}(  \effect_2)  }  \\
-\code{fst_{\pure{\pi}}( \textbf{S}? ) {=} fst_{\pure{\pi}}( \{\textbf{S}\} ) \cup fst_{\pure{\pi}}( \{ \overline{\textbf{S}} \} ) }
-    \qquad\qquad\quad
-   \code{fst_{\pure{\pi}}(  \effect_1 {||} \effect_2) {=} unify \ 
-    (fst_{\pure{\pi}}(  \effect_1)) \  (fst_{\pure{\pi}}(  \effect_2))  }  
-   \\
-{
-\code{fst_{\pure{\pi}}(\effect_1 {\seq} \effect_2) {=} } 
-\begin{cases}
-      \code{\code{fst_{\pure{\pi}}(  \effect_1)} \cup \code{fst_{\pure{\pi}}(  \effect_2)} } & \code{ if\ \delta(\effect_1) {=} true}\\
-      \code{\code{fst_{\pure{\pi}}(  \effect_1)}} & \code{  if\ \delta(\effect_1) {=} false}
+        \code{\code{fst_{{\pi}}(  \es_1)} \cup \code{fst_{{\pi}}(  \es_2)} } & \code{ if\ \delta(\es_1) {=} true}\\
+        \code{\code{fst_{{\pi}}(  \es_1)}} & \code{  if\ \delta(\es_1) {=} false}
       \end{cases} 
@@
 (A21)  &
- \code{{\pure{False}} : \effect \rightarrow {\pure{False}} : \bott}\\
+ \code{{{False}} : \effect \rightarrow {{False}} : \bott}\\
 \hline
 (A22)  &
- \code{{\pi} : \bott \rightarrow {\pure{False}} : \bott}\\
+ \code{{\pi} : \bott \rightarrow {{False}} : \bott}\\
 \hline

### 2022-04-08 paper/tv.tex
m

@@
 Now, the inclusions are disjunction-free formulas. 
-
-Next we provide the definitions and implementations of auxiliary functions \emph{Nullable}(\code{\delta}), \emph{First}(\code{fst}) and \emph{Derivative}(\code{D}) respectively.
-Intuitively, the Nullable function \code{\delta(\effect)} returns a boolean value indicating whether \code{\effect} contains the empty trace; the First function \code{fst_{{\pi}}( \effect)} computes a set of possible initial time instances of \code{{\pi} : \effect}; and the Derivative function \code{D_{I\mysharp  t}^{{\pi}}(\effect)} computes a next-state effects after eliminating one event \code{I} w.r.t.
-the execution time \code{t} from the current effects \code{{\pi} : \effect}.
-
 Next we provide the definitions and the key implementations\footnote{As 
@@
 trace; the First function \code{fst_{{\pi}}( \es)} computes a set of 
-possible initial events of \code{{\pi} \wedge \es}; and the Derivative 
-function \code{D_{\anyevent{a}}^{{\pi}}(\es)} computes a next-state 
-effects after eliminating one event \code{\anyevent{a}} from the current 
+ initial \emph{heads}, denoted as \code{h},  of \code{{\pi} \wedge \es}; and the Derivative 
+function \code{D_{h}^{{\pi}}(\es)} computes a next-state 
+effects after eliminating the head  \code{h} from the current 
 effects \code{{\pi} \wedge \es}.
@@
 \begin{definition}[Nullable]\label{Nullable}
-Given any timed sequence \code{\es} under condition \code{{\pi}}, we define \code{\delta_{{\pi}}(\es)} to be:\\
+Given any \code{\effect {=} \pi {\wedge} \es}, %we define 
+%\code{\delta_{{\pi}}(\es)} to be \\
 {
@@
   \begin{cases}
-      \code{true} & \code{if\ \empt \in \llbracket {\pi} \wedge \es \rrbracket_{\varphi}}\\
-      \code{false} & \code{if\ \empt \notin \llbracket {\pi} \wedge \es \rrbracket_{\varphi}}
+        \code{true} & \code{if\ \empt \in \llbracket {\pi} {\wedge} \es \rrbracket_{\varphi}}\\
+        \code{false} & \code{if\ \empt \notin \llbracket {\pi} {\wedge} \es \rrbracket_{\varphi}}
       \end{cases} }
-    }, where\   
+      }, where:  
+\begin{comment}
+ a boolean value, indicating whether \code{\effect} contains the empty trace, i.e., $\epsilon$. 
+We define recursively:  
+\end{comment} 
 { 
@@
 
+\begin{definition}[Heads]\label{Heads}
+If \code{h} is a head of \code{\pi \wedge \es}, then there exists 
+\code{\pi^\prime} and \code{\es^\prime}, 
+such that \code{\pi \wedge \es} {=} \code{\pi^\prime \wedge h \cdot \es^\prime}. 
+   %We adopt the following naming convention for transition labels: 
+A head can be  $t$, denoting a pure time passing; 
+  $\ev $, denoting a pure event passing; 
+  $(\ev, t)$, denoting an event passing which takes time \code{t}. 
+\end{definition}
+
 \begin{definition}[First]\label{First}
-  Let \code{fst_{{\pi}}(\es): \{ (\ev,  t)  | 
-  \pi {\wedge} t{\geq}0 \wedge (\ev \mysharp  t) {\cdot} \es_1 \in \llbracket  
-  \pi \wedge \es \rrbracket \}} be the set of initial timed events  
-  derivable from effects \code{\pi \wedge \es}. (\code{\llbracket  \pi \wedge
-   \es \rrbracket } represents all the timed  traces contained in 
-   \code{\pi \wedge \es}) 
+  Given any \code{\effect {=} \pi \wedge \es},
+  \code{fst_{{\pi}}(\es)} return a set of heads, be the set of initial elements   
+  derivable from effects \code{\pi \wedge \es}, where: 
     { 
    \begin{gather*} 
-  \code{fst_{{\pi}}( \bott) {=} \{\} } \qquad\quad
-  \code{fst_{{\pi}}(\empt) {=}  \{\} } \qquad\quad
-  \code{fst_{{\pi}}( \ev) {=} \{ (\ev, t) \}  \ (t\ is\ fresh)} 
+  \code{fst_{{\pi}}( \bott) {=} \{\} } \qquad\ \ 
+  \code{fst_{{\pi}}(\empt) {=}  \{\} } \qquad\ \ 
+  \code{fst_{{\pi}}( \ev) {=} \{ \ev \}  }
+  \qquad\ \ 
+  \code{fst_{{\pi}}(  \epsilon \mysharp  t) {=}  \{ t \}}
+  \qquad\ \ 
+  \code{fst_{{\pi}}( {\es^\star} ) {=} fst_{{\pi}}({ \es})}
+   \\
+   \code{fst_{{\pi}}(\es \mysharp  t) {=}  \{(\ev, t) \ | \ \ev \in fst_{\pi}(\es) \}} 
+   \ \ \  \emph{(t\ is\ fresh)}
   \qquad\quad 
-     \code{fst_{{\pi}}(  \es \mysharp  t) {=}  fst_{\pi}(\es)}
-   \\
-  \code{fst_{{\pi}}( {\es^\star} ) {=} fst_{{\pi}}({ \es})}
-  \qquad\ \ \  
   \qquad\quad
@@
 
-\begin{definition}[First-Tuples Unification]\label{unify} Given two first tuples \code{(I_1, \pi_1, t_1)} and \code{(I_2, \pi_2, t_2) }, we define that: 
-%We deploy a \code{unify} function to merge two time instances, where \\ 
-\code{unify\ (I_1, \pi_1, t_1)\  (I_2, \pi_2, t_2) = (I_1 \cup I_2, \pi_1 \wedge \pi_2 \wedge (t1 {=} t2), t_1)}.
-\end{definition}
-
-\begin{definition}[Instances Subsumption]\label{Subsumption}
+\begin{definition}[Timed Event Subsumption]\label{Subsumption}
 Given two instances \code{I} and \code{J}, we define the subset relation \code{I {\subseteq} J} as: the set of present signals in \code{J} is a subset of the set of present signals in \code{I}, and the set of absent signals in \code{J} is a subset of the set of absent signals in \code{I}\footnote{As in having more constraints refers to a smaller set of satisfying instances.}.

### 2022-04-08 paper/tv.tex
m

@@
 \begin{definition}[System configuration]
-A system configuration is a pair $c = (V , e)$ where $V$ is a variable valuation function and $e$ is an expression.
+A system configuration is a pair $c = (\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
 \end{definition}
@@
   t {\leq} d 
-}{(V, \textbf{delay}[d]) \xrightarrow[]{\text{t}} (V, \textbf{delay} [d \text{-}t])}\ [de_1]} 
+}{(\env, \textbf{delay}[d]) \xrightarrow[]{\text{t}} (\env, \textbf{delay} [d \text{-}t])}\ [de_1]} 
 \qquad \qquad 
 \code{\frac{
-}{(V, \textbf{delay} [0]) \xrightarrow[]{\tau} (V, ())}\ [de_2]} 
+}{(\env, \textbf{delay} [0]) \xrightarrow[]{\tau} (\env, ())}\ [de_2]} 
 \end{flalign*}}}
@@
 \code{\frac{
-  (V,e_1) \xrightarrow[]{\anyevent{A}} (V^\prime,e_1^\prime)
-}{(V, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\anyevent{A}} (V^\prime,e^\prime)}\ [to_1]} 
+  (\env,e_1) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_1^\prime)
+}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)}\ [to_1]} 
 \quad  
 \code{\frac{
-  (V,e_1) \xrightarrow[]{\tau} (V^\prime,e_1^\prime)  
-}{(V, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (V^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [to_2]} 
+  (\env,e_1) \xrightarrow[]{\tau} (\env^\prime,e_1^\prime)  
+}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [to_2]} 
 \\
 \code{\frac{
-  (V,e_1) \xrightarrow[]{\text{t}} (V,e_1^\prime)  \quad (t {\leq} d) 
-}{(V, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (V,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [to_3]} 
+  (\env,e_1) \xrightarrow[]{\text{t}} (\env,e_1^\prime)  \quad (t {\leq} d) 
+}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [to_3]} 
 \quad  
 \code{\frac{
-}{(V, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (V, e_2)}\ [to_4]} 
+}{(\env, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (\env, e_2)}\ [to_4]} 
 \end{flalign*}}}
@@
 \code{\frac{
-  (V,e) \xrightarrow[]{\anyevent{A}} (V^\prime,e^\prime)
-}{(V, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (V^\prime, \textbf{deadline}  [d] \ e^\prime)} [dl_1]} 
+  (\env,e) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)
+}{(\env, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (\env^\prime, \textbf{deadline}  [d] \ e^\prime)} [dl_1]} 
 \quad 
 \code{\frac{
-  (V,e) \xrightarrow[]{\text{t}} (V,e^\prime)  \quad (t {\leq} d)
-}{(V, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (V, \textbf{deadline}  [d \text{-}t] \ e^\prime )} [dl_2]} 
+  (\env,e) \xrightarrow[]{\text{t}} (\env,e^\prime)  \quad (t {\leq} d)
+}{(\env, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (\env, \textbf{deadline}  [d \text{-}t] \ e^\prime )} [dl_2]} 
 \end{flalign*}}}
@@
   \code{\frac{
-    V \not\models  b 
-  }{(V, [b] \ e ) \xrightarrow[]{t} (V, [b] \ e)}\ [gu_1]} 
+    \env \not\models  b 
+  }{(\env, [b] \ e ) \xrightarrow[]{t} (\env, [b] \ e)}\ [gu_1]} 
   \ \ \qquad
   \code{\frac{
-    V \models  b 
-  }{(V, [b] \ e ) \xrightarrow[]{\tau} (V, e)}\ [gu_2]} 
+    \env \models  b 
+  }{(\env, [b] \ e ) \xrightarrow[]{\tau} (\env, e)}\ [gu_2]} 
   \ \ \qquad 
   \code{\frac{
-  }{(V, \alpha ) \xrightarrow[]{\tau} (\alpha(V), ())}\ [assign]} 
+  }{(\env, \alpha ) \xrightarrow[]{\tau} (\alpha(\env), ())}\ [assign]} 
 \end{flalign*}}}
@@
   \code{\frac{
-    (V,e_1) \xrightarrow[]{\anyevent{A}} (V^\prime,e_1^\prime) 
-  }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1^\prime || e_2)}\ [pa_1]} 
+    (\env,e_1) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_1^\prime) 
+  }{(\env, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (\env^\prime, e_1^\prime || e_2)}\ [pa_1]} 
   \ \   
   \code{\frac{
-    (V,e_2) \xrightarrow[]{\anyevent{A}} (V^\prime,e_2^\prime) 
-  }{(V, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (V^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
+    (\env,e_2) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_2^\prime) 
+  }{(\env, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (\env^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
 \ \ 
 \code{\frac{
-  (V,e_1) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime,e_1^\prime) 
-}{(V, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (V^\prime, e_1^\prime ; e_2)}\ [se]} 
+  (\env,e_1) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime,e_1^\prime) 
+}{(\env, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime, e_1^\prime ; e_2)}\ [se]} 
 \end{flalign*}}}
@@
  initial \emph{heads}, denoted as \code{h},  of \code{{\pi} \wedge \es}; and the Derivative 
-function \code{D_{h}^{{\pi}}(\es)} computes a next-state 
+function \code{D^{\env}_{h}(\pi \wedge \es)} computes a next-state 
 effects after eliminating the head  \code{h} from the current 
-effects \code{{\pi} \wedge \es}.
+effects \code{{\pi} \wedge \es}, w.r.t \code{\env}.
 
@@
 
-\begin{definition}[Timed Event Subsumption]\label{Subsumption}
-Given two instances \code{I} and \code{J}, we define the subset relation \code{I {\subseteq} J} as: the set of present signals in \code{J} is a subset of the set of present signals in \code{I}, and the set of absent signals in \code{J} is a subset of the set of absent signals in \code{I}\footnote{As in having more constraints refers to a smaller set of satisfying instances.}.
-Formally, 
- \begin{gather*} 
- \code{I {\subseteq} J \Leftrightarrow  \{\textbf{S}\ |\ (\textbf{S} {\mapsto} Present) \in J \}  \subseteq  \{\textbf{S}\ |\ (\textbf{S} {\mapsto} Present) \in I \}} \\
-  \code{ \quad\  and  \ 
- \{\textbf{S}\ |\ (\textbf{S} \mapsto Absent) \in J \}  \subseteq  \{\textbf{S}\ |\ (\textbf{S} \mapsto Absent) \in I \}
- }
-\end{gather*}
+\begin{comment}
+  \begin{definition}[Heads Subsumption]\label{Subsumption1}
+Given two time instances \code{(I, \pi_1, t_1)} and \code{(J, \pi_2, t_2)}, we define the subset relation \code{(I, \pi_1, t_1) {\subseteq} (J, \pi_2, t_2)} as:  \code{I {\subseteq} J} and \code{\pi_1[t_2/t_1]  {\Rightarrow}   \pi_2  }.
 
 \end{definition}
-
-\begin{definition}[Time Instances Subsumption]\label{Subsumption1}
-Given two time instances \code{(I, \pi_1, t_1)} and \code{(J, \pi_2, t_2)}, we define the subset relation \code{(I, \pi_1, t_1) {\subseteq} (J, \pi_2, t_2)} as:  \code{I {\subseteq} J} and \code{\pi_1[t_2/t_1]  {\Rightarrow}   \pi_2  }.
-
-\end{definition}
+\end{comment}
 
@@
 }]\label{Derivative}
-The partial derivative \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect)} 
-of effects \code{\pi : \effect} 
-w.r.t.
-a event \code{(I, \Pi_1, t^\prime)} computes the  effects for the left quotient \code{(I, \Pi_1, t^\prime)^{\text{-}1}\llbracket \pi : \effect \rrbracket}.
-\footnote{For understanding of the derivative rule for \code{\effect\mysharp  t} (cf.
-\tabref{tab:rewriting_tree_send}  step \textcircled{3}), it is essentially splitting \code{\effect} with a head and a tail, bound with fresh terms \code{t_1} and \code{t_2} respectively.
-Meanwhile it unifies \code{t_1} with \code{t^\prime} and  adds the constraint \code{t_1 {+} t_2 {=} t}.}
+Given any \code{\effect {=} \pi \wedge \es}, and a variable valuation function \code{\env}, 
+the partial derivative \code{D^{\env}_{h}(\pi \wedge \es)} 
+ computes the  effects for the 
+left quotient \code{(h)^{\text{-}1}\llbracket \pi \wedge \es 
+\rrbracket_{\env}}. 
 %\footnote{As the reader may notice, our First and Derivative function does not handle the timed sequences constructed by \code{||}, as the synchronous parallel is reduced during the normalization phase.}

### 2022-04-08 paper/tv.tex
m

@@
 \newcommand{\es}{\theta}
-\newcommand{\ev}{\iota}
+\newcommand{\ev}{ev}
 
@@
 
+\begin{comment}
+
+/*require n>=0, _^*
+  ensure  t>=n, Sugar#t */
 {
-\begin{figure}[ht]
-      \vspace{0mm}
+
+\end{comment}
+
+{
+\begin{figure}[!ht]
+    %  \vspace{-4mm}
      \begin{minipage}[c]{\columnwidth}
-      \vspace{0mm}
          \centering
@@
          \begin{enumerate}
-  \item  \code{\key{fork}\{    } 
-                 \textcolor{mGray}{  \emph{(– initialize the current effects state using the module precondition –)}}
+\item \lstinline|void addSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
+     \textcolor{darkpastelred}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
+      \siderule{\scriptsize[FV\text{-}Meth] } \\
+     \item ~\qquad \lstinline|if (n == 0) {| \\
+     \textcolor{darkpastelred}{\code{\{ n{=}0 \wedge \anyevent{Ready} \cdot \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
+      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
+     \textcolor{darkpastelred}{\code{\{n{=}0 \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Done}\} }} \siderule{\scriptsize [FV\text{-}Event]}
+     \item 
+     ~\qquad \lstinline|else {| \\
+     \textcolor{darkpastelred}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
+    \item 
+     ~\qquad~\qquad \lstinline|timeout (oneSugar() , 1);| \\
+     \textcolor{darkpastelred}{\code{\{n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send}  }\}} \siderule {\scriptsize [FV\text{-}Event]}
+     \item 
+     ~\qquad~\qquad \lstinline|addSugar (n-1);}}|  \\
+      \code{rev(n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send})  \CONTAIN rev(\effect_{pre}^{send(n\text{-}1)}) }
+      \textcolor{mGray}{  \emph{(-check precondition-) }}\\
+     \textcolor{darkpastelred}{\code{\{ n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send}\cdot \effect_{post}^{send(n\text{-}1)} }\}} \siderule {\scriptsize [FV\text{-}Call]}
+      \item \textcolor{darkpastelred}{\code{\effect_C^\prime {=} (n{=}0 \wedge \anyevent{Ready} \cdot \_^\star \cdot  \anyevent{Done})\ \vee\ }\code{ (n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send}\cdot \effect_{post}^{send(n\text{-}1)}) }}
       \\
- \code{\langle  \textcolor{darklavender}{true : emp} \rangle }
-                  \textcolor{mGray}{  \emph{(– emp indicates an empty trace –)}}
-  \item    \code{~\qquad \key{await}\ Ready;}
-   \\
- \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\_ } \rangle }
-     \siderule{ [FV\text{-}Await]}
-     \\
-   \item    \code{~\qquad \key{emit}\ Go;}
-         \\
- \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\{Go\}} \rangle }
-     \siderule{ [FV\text{-}Emit]}
-     \\
-  \item \code{ \} \key{par}\{ }
-       \textcolor{mGray}{  \emph{(– initialize the current effects state using the module precondition –)}}
-  \\
- \code{\langle  \textcolor{darklavender}{true : emp} \rangle }
-  \item    \code{~\qquad \key{emit}\ Prep; }
-     \\
- \code{\langle  \textcolor{darklavender}{true : \{Prep\}} \rangle }
-     \siderule{ [FV\text{-}Emit]}
-     \\
-  \item    \code{~\qquad \key{async}\ Ready\{}
-  %   \item    \code{~\qquad \key{yield}; }
- %     \\
-% \code{\langle  \textcolor{darklavender}{true : Ready? \cdot\_} \rangle }
- %    \siderule{ [FV\text{-}Yield]}
-%     \\
-  \item      \code{~\qquad \ \qquad \key{run}\ cook\ (3, Cook) 
-     \}\}\}}
-      \\
-                     \textcolor{mGray}{\emph{(-TRS: check the  precondition of module cook-) }} \\
-              \code{  \textcolor{darkred}{d{=}3 : \{Prep\}  \CONTAIN  d{>}2 \wedge \{Prep\}} }   \\
-
-               \textcolor{mGray}{\emph{(-TRS: succeed-) }}
-      \\
-     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\mysharp  t}  \rangle } 
-     \siderule{ [FV\text{-}Call]}
-      \\
-     \code{\langle  \textcolor{darklavender}{ 0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\}}  \rangle } 
-     \siderule{ [FV\text{-}Async]}
-     \\ \item
-                   \code{\langle \textcolor{huntergreen}{(true \wedge 0{\leq}t {<}3) :  Ready?
-\cdot\{Go\}  \ || \  (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\}} \rangle }   \siderule{ [FV\text{-}Fork]}
-        \\ 
-         \code{\langle \textcolor{huntergreen}{0{\leq}t {<}3 : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}} \rangle }
-         \siderule{ [Effects\text{-}Normalization]} 
-         \\
-              \item 
-               \textcolor{mGray}{  \emph{(-TRS: check the  postcondition of module main; Succeed, cf. \tabref{tab:rewriting_tree_send}-) }}\\
-                  \code{  \textcolor{darkred}{
-{0 {\leq} t {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN {0 {\leq} t  {<}3} : \_\cdot (\{Cook\})\mysharp  t \cdot\_^\star} 
-                  }    \\
+       \item \code{
+       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{send(n-1)}) } 
+       \effect_C^\prime \CONTAIN \effect_{pre}^{send(n)} \cdot \effect_{post}^{send(n)} \Leftrightarrow   \textcolor{mGray}{  \emph{(-- check postcondition --) }}}
+        \\ \code{\code{\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  {\neq} 0  \wedge \anyevent{Send}\cdot \effect_{post}^{send(n\text{-}1)}) } \CONTAIN \effect_{post}^{send(n)}}}\\
 
@@
      \end{minipage}
-      \vspace{0mm}
-      \caption{The forward verification example for the module {\ttfamily{main}}. }\label{fig:forward_example}
-      \vspace{-1mm}
+
+      \caption{The forward verification example for method \code{send}. }\label{fig:forward_example}
+      \vspace{-4mm}
 \end{figure}
@@
   \code{fst_{{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }  \\
+  \code{fst_{{\pi}}(\epsilon \mysharp  t) {=}  \{t\}} 
+   \qquad \qquad
   \code{fst_{{\pi}}( \pi^\prime? \es ) {=} fst_{\pi}(\es)  }
-      \qquad\qquad\quad
+      \qquad\qquad
      \code{fst_{{\pi}}(  \es_1 {||} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }   
@@
 \begin{gather*}
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\bott) {=}}  
- \code{False : \bott} 
-\qquad\ 
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \empt) {=}}   
-\code{False : \bott} 
-\qquad \ 
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect_1 ||\effect_2)} {=} \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect_1)} || \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect_2)} 
-    \\
-        \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  {\effect^\star}) } {=} \code{ D^{\pi}_{(I, \Pi_1, t^\prime)}(  {\effect}) \cdot ({\effect^\star})}  
-        \qquad\qquad
+\code{D^{\env}_{h}(\pi \wedge \bott) {=}}  \code{False \wedge \bott} 
+\qquad\ \ \  
+\code{D^{\env}_{h}( \pi \wedge \empt) {=}}  \code{False \wedge \bott} 
+\qquad\ \ \ 
+\code{D^{\env}_{h}( \pi \wedge {\es^\star}) } {=} \code{ D^{\env}_{h}(\pi \wedge  {\es}) \cdot {\es^\star}}  
 \\
 {
- \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(   \effect_1 \seq \effect_2) {=} }
+ \code{\code{D^{\env}_{h}(\pi \wedge \pi^\prime? \es)} {=}}
 \begin{cases}
-      \code{D^{\pi}_{(I, \Pi_1, t^\prime)}(   \effect_1) \cdot  \effect_2 \vee  D^{\pi}_{(I, \Pi_1, t^\prime)}( \effect_2)} \quad &\code{if\ \delta(\effect_1) {=} true}   \\
-      \code{D^{\pi}_{(I, \Pi_1, t^\prime)}  ( \effect_1) \cdot  \effect_2} & \code{if\ \delta(\effect_1) {=} false} 
+      \code{\pi \wedge \pi^\prime? \es} \quad &\code{if\ \llbracket \pi^\prime  \rrbracket_{\env} {=} false}   \\
+      \code{D^{\env}_{h}(\pi \wedge \es)} & \code{if\ \llbracket \pi^\prime  \rrbracket_{\env} {=} true} 
     \end{cases} 
@@
     \\ 
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1 \choice \effect_2) } {=} \code{ D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1) \choice D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_2)} 
-%\\
-%\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1 \ ||\  \effect_2) } {=} \code{ D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_1) \ ||\ D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect_2)} 
+{
+ \code{D^{\env}_{h}(\pi \wedge \es_1 {\cdot} \es_2) {=} }
+\begin{cases}
+      \code{D^{\env}_{h}(\pi \wedge \es_1) \cdot  \es_2\ \vee \  D^{\env}_{h}(\pi \wedge \es_2)} \quad &\code{if\ \delta_{\pi}(\es_1) {=} true}   \\
+      \code{D^{\env}_{h}(\pi \wedge \es_2) \cdot  \es_2} & \code{if\ \delta_{\pi}(\es_1) {=} false} 
+    \end{cases} 
+    }
 \\
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(  \effect \mysharp  t) } {=}
-\code{
-\pi \wedge(t_1{+} t_2 {=}t) \wedge (t_1{=}t^\prime) : (D^{\pi}_{(I, \Pi_1, t^\prime)}(\effect))\mysharp  t_2} \ \ \ 
-\code{(fresh \ t_1\ t_2 )}
+\code{D^{\env}_{h}(\pi \wedge  \es_1 {\choice} \es_2) } {=} \code{ D^{\env}_{h}(\pi \wedge  \es_1) \choice D^{\env}_{h}( \pi \wedge \es_2)} 
+\qquad 
+\code{D^{\env}_{h}(\pi \wedge \es_1 {||}\es_2)} {=} \code{PD^{\env}_{h}(\pi \wedge \es_1)} || \code{PD^{\env}_{h}(\pi \wedge \es_2)} 
+ \\~\\
+ \hline
+ ~\\
+ \code{D^{\env}_{t}(\pi \wedge  \ev) } {=} \code{False \wedge \bott} 
+ \qquad\qquad 
+ \code{D^{\env}_{t}(\pi \wedge  \epsilon \mysharp t^\prime) } {=}  
+ \code{\pi{\wedge}(t{=}t^\prime) \wedge \epsilon}
  \\
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} \{\textbf{S}\})}
-\qquad
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(\textbf{S}?)} {=} \code{\pi: \textbf{S}?\ (}\code{ I {\not\subseteq} \{\textbf{S}\})}
+ \code{D^{\env}_{t}(\pi \wedge  \es \mysharp t^\prime) } {=} 
+ \code{\pi{\wedge}(t{+}t^{\prime\prime}{=}t^\prime) \wedge  
+ \es \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)} } 
+\\~\\
+\hline
+~\\
+\code{D^{\env}_{\ev}(\pi \wedge  \ev^\prime) } {=} 
+\code{\pi{\wedge}(\ev{=}\ev^\prime) \wedge \epsilon} 
+\qquad \quad 
+\code{D^{\env}_{\ev}(\pi \wedge  \es \mysharp t^\prime) } {=} 
+\code{\{(\pi^\prime \wedge \es^\prime \mysharp t^\prime) \ | \ (\pi^\prime \wedge \es^\prime) \in D^{\env}_{\ev}(\pi \wedge  \es)\}} 
+\\~\\
+\hline
+~\\
+\code{D^{\env}_{(\ev, t)}(\pi \wedge  \ev^\prime) } {=} 
+\code{False \wedge \bott}  
+\qquad \ \ \  
+\code{D^{\env}_{(\ev, t)}(\pi \wedge  \es \mysharp t^\prime) } {=} 
+\code{\pi{\wedge}(t{+}t^{\prime\prime}{=}t^\prime) \wedge  
+(D^{\env}_{\ev}(\pi \wedge  \es)) \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)}} 
 \\
-\code{D^{\pi}_{(I, \Pi_1, t^\prime)}(J)} {=} \code{\pi: \empt\ (}\code{ I {\subseteq} J)}
-\qquad\ 
-    \code{D^{\pi}_{(I, \Pi_1, t^\prime)}( J)} {=} \code{False : \bott \ (}\code{I {\not\subseteq} J)} 
 \end{gather*}
+\end{definition}
+
+\begin{definition}[Parallel Derivative]\label{Derivative_maybe}
+  Given any \code{\effect {=} \pi \wedge \es}, and a variable valuation function \code{\env}, 
+  the parallel derivative is defined as: {
+    \code{PD^{\env}_{h}(\pi \wedge \es) {=}
+    \begin{cases}
+          \code{\pi \wedge \es} & \code{if\ D^{\env}_{h}(\pi \wedge \es) = (False \wedge \bott)}\\
+          \code{D^{\env}_{h}(\pi \wedge \es)} & \code{otherwise}
+        \end{cases} }
+        }
+
 \end{definition}

### 2022-04-08 paper/tv.tex
m

@@
 
-\definecolor{darkpastelred}{rgb}{0, 0, 0}
+\definecolor{darklavender}{rgb}{0, 0, 0}
 \definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}
@@
 \usepackage{wrapfig}
-\newcommand{\effect}{\textcolor{black}{\ensuremath{\mathrm{\Phi}}}}
+\newcommand{\effect}{{\ensuremath{\mathrm{\Phi}}}}
 \definecolor{color_pure}{RGB}{3,35,14}
@@
 the portion of the sugar we need to add. When \codem{n} decreases to \codem{0}, 
-it simply raises an event \anyevent{Sugar} to mark the end of the process. 
+it simply raises an event Sugar to mark the end of the process. 
 Otherwise, it adds one portion of the sugar then recursively calls \code{\emph{addSugar}} with parameter \codem{n-1}. 
@@
 input  \code{n} is non-negative; the method 
-generates a finite trace where \anyevent{Sugar} takes a no less 
+generates a finite trace where Sugar takes a no less 
 than \code{d} time units delay to finish. 
@@
 effects of \code{addSugar(n)} as:
-\code{(n{>}0  \wedge  t {\geq} n) : ({\anyevent{Sugar} \mysharp  t)}}
+\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}
 
@@
 \item \lstinline|void addSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
-     \textcolor{darkpastelred}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
+     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
       \siderule{\scriptsize[FV\text{-}Meth] } \\
      \item ~\qquad \lstinline|if (n == 0) {| \\
-     \textcolor{darkpastelred}{\code{\{ n{=}0 \wedge \anyevent{Ready} \cdot \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
+     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
       \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
-     \textcolor{darkpastelred}{\code{\{n{=}0 \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Done}\} }} \siderule{\scriptsize [FV\text{-}Event]}
+     \textcolor{darklavender}{\code{\{n{=}0 \wedge  \_^\star \cdot Sugar\} }} \siderule{\scriptsize [FV\text{-}Event]}
      \item 
      ~\qquad \lstinline|else {| \\
-     \textcolor{darkpastelred}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
+     \textcolor{darklavender}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
     \item 
      ~\qquad~\qquad \lstinline|timeout (oneSugar() , 1);| \\
-     \textcolor{darkpastelred}{\code{\{n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send}  }\}} \siderule {\scriptsize [FV\text{-}Event]}
+     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
      \item 
      ~\qquad~\qquad \lstinline|addSugar (n-1);}}|  \\
-      \code{rev(n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send})  \CONTAIN rev(\effect_{pre}^{send(n\text{-}1)}) }
+     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addSugar(n\text{-}1)} }}
       \textcolor{mGray}{  \emph{(-check precondition-) }}\\
-     \textcolor{darkpastelred}{\code{\{ n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send}\cdot \effect_{post}^{send(n\text{-}1)} }\}} \siderule {\scriptsize [FV\text{-}Call]}
-      \item \textcolor{darkpastelred}{\code{\effect_C^\prime {=} (n{=}0 \wedge \anyevent{Ready} \cdot \_^\star \cdot  \anyevent{Done})\ \vee\ }\code{ (n  {\neq} 0  \wedge \anyevent{Ready} \cdot \_^\star \cdot \anyevent{Send}\cdot \effect_{post}^{send(n\text{-}1)}) }}
+     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
+     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} }\}} 
+     \siderule {\scriptsize [FV\text{-}Call]}
+      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
+      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} ) }}
       \\
-       \item \code{
+       \item 
+       \textcolor{darkred}{\code{
        %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{send(n-1)}) } 
-       \effect_C^\prime \CONTAIN \effect_{pre}^{send(n)} \cdot \effect_{post}^{send(n)} \Leftrightarrow   \textcolor{mGray}{  \emph{(-- check postcondition --) }}}
-        \\ \code{\code{\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  {\neq} 0  \wedge \anyevent{Send}\cdot \effect_{post}^{send(n\text{-}1)}) } \CONTAIN \effect_{post}^{send(n)}}}\\
+       \effect_C^\prime \CONTAIN \effect_{pre}^{addSugar(n)} \cdot \effect_{post}^{addSugar(n)} \Leftrightarrow  }}
+        \textcolor{mGray}{  \emph{(-- check postcondition --) }}
+        \\ 
+        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
+        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{send(n)}}}}\\
 

### 2022-04-09 paper/tv.tex
m

@@
 \begin{comment}
-  we express, the effects of \code{send(d)} as:
+  we express, the effects of \code{addSugar(d)} as:
 \begin{align*}
@@
        \textcolor{darkred}{\code{
-       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{send(n-1)}) } 
+       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addSugar(n-1)}) } 
        \effect_C^\prime \CONTAIN \effect_{pre}^{addSugar(n)} \cdot \effect_{post}^{addSugar(n)} \Leftrightarrow  }}
@@
         \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
-        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{send(n)}}}}\\
+        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addSugar(n)}}}}\\
 
@@
 \Hypo{
-\code{\textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
-{\wedge}   t_L^2 {=} t_R
-}  \Rightarrow 
-\textcolor {darkred}{t_R {<}3}
-} \qquad
-\code{emp  \CONTAIN  \_^\star}
-}
-\Infer[dashed]1[{\siderule{\textcircled{8}[PROVE]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
-{\wedge}   t_L^2 {=} t_R
-} :  emp
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee \_^\star}}
-\Infer[dashed]1[{\siderule{\textcircled{7}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
-{\wedge}   t_L^2 {=} t_R
-} :  \cancel{\{Go\}}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\_} \cdot \_^\star}}
-\Infer[dashed]1[{\siderule{\textcircled{6}[Normalization]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
-{\wedge}   t_L^2 {=} t_R
-} :  \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee  \_^\star}}
-\Infer[dashed]1[{\siderule{\textcircled{5}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
-{\wedge}   t_L^2 {=} t_R
-} 
-:  \cancel{\{ Ready\}} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\_} \cdot \_^\star}}
-\Infer[dashed]1[{\siderule{\textcircled{4}[UNFOLD{-}UNIFY]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L
- } : \cancel{\{Cook\} \mysharp  t_L^2} \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{\{Cook\}\mysharp  t_R}\cdot\_^\star}  }
-\Infer[dashed]1[{\siderule{\textcircled{3}[UNFOLD]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L } : \cancel{\{Prep\}\mysharp  t_L^1} \cdot \{Cook\} \mysharp  t_L^2 \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} :  \cancel{\_}\cdot\{Cook\}\mysharp  t_R \cdot\_^\star}  }
-\Infer[dashed]1[{\siderule{\textcircled{2}[SPLIT]}}]{\code{ \textcolor {darkred}{t_L {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t_L \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \_\cdot\{Cook\}\mysharp  t_R\cdot\_^\star}  }
- \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{ \textcolor {darkred}{t {<}3} : (\{Prep\}\cdot \{Cook\})\mysharp  t \cdot \{ Ready\} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t {<}3} : \_\cdot\{Cook\}\mysharp  t\cdot\_^\star}  }
+  \code{\siderule{[Prove]}}
+}
+
+\Infer[dashed]1[]{ \code{ n{=}0 \wedge \epsilon 
+\CONTAIN t_r{\geq}0 \wedge \epsilon \mysharp t_r}}
+
+\Infer[dashed]1[]{ \code{ n{=}0 \wedge Sugar
+\CONTAIN t_r{\geq}0 \wedge Sugar \mysharp t_r}}
+
+\Hypo{
+  \code{\textcolor {darkred}{  t{>}1 {\wedge} t_l{\geq}(n\text{-}1) 
+   {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1  \Rightarrow t_r{\geq}n
+}  } 
+\code{\siderule{[Prove]}}
+ }
+
+ \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
+ \epsilon
+\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1 
+\wedge \epsilon}}
+
+ \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
+ Sugar \mysharp t_l
+\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t
+\wedge Sugar \mysharp t_r^1}}
+
+ \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
+ Sugar \mysharp t_l
+\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r}}
+
+\Infer[dashed]2[]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
+\code{ (n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
+ Sugar \mysharp t_l) } 
+\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r  }
+
+\Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
+\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } 
+\CONTAIN \effect_{post}^{addSugar(n)}  }
 \end{prooftree}}

### 2022-04-10 paper/tv.tex
m

@@
 \begin{abstract} 
-Real-time systems are systems where the correctness does not 
-only depend on their correct functioning but also on meeting 
-realtime constraints.
-Different from existing Timed Automata based techniques, 
+The correctness of real-time systems 
+depends both on the correct functionalities and the realtime constraints.
+To go beyond the existing Timed Automata based techniques, 
 we propose a novel solution that integrates a 
@@
 system (TRS) on \emph{Timed Effects} (\timedEffects).
-The main purpose is to dynamically create clocks  
-and efficiently solve constraints on the clocks, 
+The main purposes are to increase the expressiveness,  
+dynamically create clocks, 
+and efficiently solve constraints on the clocks.  
 We formally define 
@@
 \timedL\ programs, expressed in \timedEffects. 
-Lastly, we present a purely algebraic TRS, i.e., an extended Antimirov algorithm, to 
+Lastly, we present a purely algebraic TRS, i.e., an extended \emph{Antimirov algorithm}, to 
 efficiently prove language inclusions between 
@@
 Term Rewriting System,
-Reactive System Design}
+Timed Verification}
 

### 2022-04-10 paper/tv.tex
m

@@
 \begin{lstlisting}
+void oneSugar() 
+/*req: TRUE/\ (_^*).emp
+  ens: t>1 /\ emp#t */ 
+{ timeout ((), 1); }
+
 void addSugar (int n) 
-/*require n>=0, _^*
-  ensure  t>=n, Sugar#t */
+/*req: n>=0 /\ _^*
+  ens: t>=n /\ Sugar#t */
 { if (n == 0) { 
@@
   else {
-    timeout (oneSugar() , 1);
+      oneSugar();
       addSugar (n-1);}} 
@@
    \  | \ \es_1 {\seq} \es_2
-    \ | \ \pi. (\es_1 {\vee} \es_2)
+    \ | \ \es_1 {\vee} \es_2
     \ | \ \es_1 {||} \es_2
@@
   \anyevent{A}(v, \alpha^*)
+    \ | \ \tau (\pi)
     \ | \ \anynotevent{A} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge \pi_1.(\es_1{\vee}\es_2)}  
+&\code{d, s, \varphi \models {\pi} \wedge \es_1{\vee}\es_2}  
 &\m{iff}\quad & 
-\code{\llbracket \pi_1  \rrbracket_{s} {=}  
- {True} },\code{d, s, \varphi \models {\pi}  \wedge \es_1 } 
+\code{d, s, \varphi \models {\pi}  \wedge \es_1 } 
 \ or\  
-\code{\llbracket \pi_1  \rrbracket_{s} {=}  
- {False} },
 \code{d, s, \varphi \models {\pi}  \wedge \es_2 } \\

### 2022-04-10 code/src/program/coffee.c

@@ -1,35 +1,35 @@
 #include "primitives.c"
 
 void oneSugar() 
-    /*
-    req: TRUE/\(_^*).emp
-    ens: TRUE/\emp
-    */
+/*
+req: TRUE/\(_^*).emp
+ens: (t1>1)/\ (emp # t1)
+*/
 {
-    1
+    timeout (() , 1);
 }
 
 void addSugar (int n) 
-    /*
-    req: TRUE/\(_^*)
-    ens:  (t>=n)/\ (Sugar #t)
-    */
+/*
+req: TRUE/\(_^*)
+ens:  (t>=n)/\ (Sugar #t)
+*/
 {
 
     if (n == 0) { 
         event ["Sugar"];
     }
     else {
-        timeout (oneSugar() , 1);
+        oneSugar();
         addSugar (n - 1);
     }
 } 
 
 void makeCoffee (int n)
-    /*
-    req: TRUE/\emp
-    ens: (t<=5/\t>=n/\t1<=3)/\Cup.(Sugar#t).(Coffee#t1).Done
-    */
+/*
+req: TRUE/\emp
+ens: (t<=5/\t>=n/\t1<=3)/\Cup.(Sugar#t).(Coffee#t1).Done
+*/
 {
     event["Cup"];
     deadline (addSugar(n), 5);

### 2022-04-10 code/src/program/fischer.c

@@ -21,5 +21,5 @@ void process (int i)
 void main () 
 /* req: TRUE /\ emp 
    ens: TRUE /\ (_^*)  */
-{ process(0) || process(1) || process(2); }
+{ process(0) || process(1); }
 

### 2022-04-10 code/src/program/fischer.c
m

@@ -3,8 +3,7 @@ ct := 0;
 
 void process (int i)
 /* req: TRUE /\ (_^*) 
-   ens: (t1=d2/\t0<=d1)/\ (((?[x=-1](Update(i){x := i}#t0)) . 
-   (emp#t1) . [x=i]((Critical(i){ct := (ct+1)} . Exit(i){ct :=( ct-1);x := -1}) + emp )) ^*) */
+   ens: TRUE /\ (_^*) */
 {
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);

### 2022-04-10 code/src/program/fischer.c
m

@@ -8,13 +8,7 @@ void process (int i)
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);
   delay (d2);
-  if (x==i) {
-    event["Critical"(i)]{ct := (ct + 1)};
-    event["Exit"(i)]{ct := (ct-1); x := -1};
-    process (i);
-  } else {
-    process (i);
-  }
+
 }
 
 void main () 

### 2022-04-11 code/src/program/fischer.c
m

@@ -8,7 +8,13 @@ void process (int i)
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);
   delay (d2);
-
+  if (x==i) {
+    event["Critical"(i)]{ct := (ct + 1)};
+    event["Exit"(i)]{ct := (ct-1); x := -1};
+    process (i);
+  } else {
+    process (i);
+  }
 }
 
 void main () 

### 2022-04-11 paper/tv.tex
m

@@
 \newcommand{\ev}{ev}
+\newcommand{\codem}[1]{{\lstinline[basicstyle=\small\ttfamily]|#1|}}
 
@@
 
-Specification and verification of real-time systems are important 
-research topics which have practical implications. During the last 
-more than two decades, a popular approach for specifying real-time systems is 
+Specification and verification of real-time systems are essential 
+to research topics with practical implications. During the last 
+more than two decades, a popular approach for specifying real-time systems has been 
 based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
@@
 in designing real-time models with explicit clock variables. Real-time 
-constraints are captured by explicitly setting/reseting clock variables. 
+constraints are captured by explicitly setting/resetting clock variables. 
 A number of automatic verification support for Timed Automata have proven 
-to be successful \cite{DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
-
-Models based on Timed Automata often adapt a simple structure, e.g. a 
+to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
+
+Models based on Timed Automata often adopt a simple structure, e.g., a 
 network with no hierarchy. The benefit is that 
@@
 forward verifier and a term rewriting system (TRS). 
-More specifically, we specify system behaviours in the form of 
-{Timed Effects} (\timedEffects), which integrates the Kleene Algebra with dependent values and arithmetic constraints, 
+More specifically, we specify system behaviors in the form of 
+{Timed Effects} (\timedEffects), which integrates the Kleene Algebra 
+with dependent values and arithmetic constraints, 
 %gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
@@
 we use integer values to represent time units in this 
-paper, while it can bes extended to real numbers and other 
-time measurement units.}, is expressed in \timedEffects\ as: 
-\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}.
-%\begin{align*}
-%&\end{align*}  
+paper.% while it can bes extended to real numbers and other 
+%time measurement units.
+}, is expressed in \timedEffects\ as: 
+\begin{align*}
+  \code{\effect \defeq \  0 {\leq} t {<}1 \wedge ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}
+\end{align*}  
 %The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
@@
 %which replaces temporal operators by time-constrained versions from 
-Here, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
+Here, \code{\wedge} connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
 constraints for the \emph{logical-time} sequences \cite{von2017real}; 
@@
 in metric temporal logic (MTL), reads \textit{"within one second, 
-\anyevent{Done} finally happens"}. Moreover, the time bounds 
-can be dependent on the program inputs. For example, as the program 
-shown in \autoref{fig:Value_dependent_intro}, we mark the precondition and postcondition
-using keywords \code{\emph{require}} and \code{\emph{ensure}} respectively.
-
-\newcommand{\codem}[1]{{\code{\emph{#1}}}}
+\anyevent{Done} finally happens"}.
+
+Moreover, the time bounds 
+can be dependent on the program inputs, demonstrated in \autoref{fig:Value_dependent_intro}, we mark the precondition and postcondition
+using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.
 
@@
 \begin{lstlisting}
-void oneSugar() 
-/*req: TRUE/\ (_^*).emp
+void addOneSugar() 
+/*req: TRUE/\ _^*
   ens: t>1 /\ emp#t */ 
@@
 
-void addSugar (int n) 
+void addNSugar (int n) 
 /*req: n>=0 /\ _^*
-  ens: t>=n /\ Sugar#t */
+  ens: d>=n /\ Sugar#d */
 { if (n == 0) { 
@@
   else {
-      oneSugar();
-      addSugar (n-1);}} 
+      addOneSugar();
+      addNSugar (n-1);}} 
 \end{lstlisting}
@@
 
-The function 
-\code{\emph{addSugar}} is intended to takes a parameter \codem{n}, representing 
-the portion of the sugar we need to add. When \codem{n} decreases to \codem{0}, 
-it simply raises an event Sugar to mark the end of the process. 
-Otherwise, it adds one portion of the sugar then recursively calls \code{\emph{addSugar}} with parameter \codem{n-1}. 
-The use of statement \codem{timeout(e, d)} is standard, 
-which sets a timer which executes code \codem{e} once the timer 
-expires at time \codem{d}. 
+The function \codem{addNSugar} takes a parameter \codem{n}, representing 
+the portion of the sugar we need to add. When \codem{n} 
+equals to \codem{0}, 
+it simply raises an event \anyevent{Sugar} to mark the end of the process. 
+Otherwise, it adds one portion of the sugar by calling
+\codem{addOneSugar()}, then recursively calls 
+\codem{addNSugar} with parameter \codem{n-1}. 
+The use of statement \lstinline|timeout(e, d)| is standard \cite{JSTO}, 
+which executes a block of code \codem{e} after the specified time \codem{d}.
 Therefore, the time spent on adding one portion of the sugar is 
-no less than 1 time unit.
-
-The specifications of  \codem{addSugar(n)} indicates that the 
-input  \code{n} is non-negative; the method 
-generates a finite trace where Sugar takes a no less 
-than \code{d} time units delay to finish. 
+no less than one time unit. Note that {\color{darklavender}\code{\emph{emp\#t}}} 
+refers to an empty trace which takes time \codem{t}.
+
+Both preconditions of \codem{addNSugar(n)} requies the 
+input  \codem{n} is non-negative, and has no temporal constrains upon 
+the history traces. 
+The postcondition of \codem{addNSugar(n)} indicates that  the method 
+generates a finite trace where \anyevent{Sugar} takes a no 
+less 
+than \codem{d} time-units delay to finish.
+
 Although these examples are simple, they show the benefits of deploying 
@@
 \begin{comment}
-  we express, the effects of \code{addSugar(d)} as:
+  we express, the effects of \code{addNSugar(d)} as:
 \begin{align*}
@@
 \end{align*}  
-effects of \code{addSugar(n)} as:
+effects of \code{addNSugar(n)} as:
 \code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}
@@
 ({\secref{subsec:Specification_Semantics}}) of \timedEffects, to be the 
-specification language, which captures the target programs' behaviours 
+specification language, which captures the target programs' behaviors 
 and non-trivial temporal properties.
@@
 \begin{lstlisting}[columns=fullflexible]
-void addSugar(int n)
+void addNSugar(int n)
 /* req n>0,  _^*.Cup 
@@
   else {
-    timeout (oneSugar(), 1);
-    addSugar (n-1);}}
+    timeout ( addOneSugar(), 1);
+    addNSugar (n-1);}}
 
@@
 { event[Cup];
-  deadline (addSugar(n), 5);
+  deadline (addNSugar(n), 5);
   deadline (event[Coffee], 3);
@@
          \begin{enumerate}
-\item \lstinline|void addSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
-     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
+\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
+     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
       \siderule{\scriptsize[FV\text{-}Meth] } \\
@@
     \item 
-     ~\qquad~\qquad \lstinline|timeout (oneSugar() , 1);| \\
+     ~\qquad~\qquad \lstinline|timeout ( addOneSugar() , 1);| \\
      \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
      \item 
-     ~\qquad~\qquad \lstinline|addSugar (n-1);}}|  \\
-     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addSugar(n\text{-}1)} }}
+     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
+     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
       \textcolor{mGray}{  \emph{(-check precondition-) }}\\
      \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
-     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} }\}} 
+     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
      \siderule {\scriptsize [FV\text{-}Call]}
       \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
-      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} ) }}
+      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }}
       \\
@@
        \textcolor{darkred}{\code{
-       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addSugar(n-1)}) } 
-       \effect_C^\prime \CONTAIN \effect_{pre}^{addSugar(n)} \cdot \effect_{post}^{addSugar(n)} \Leftrightarrow  }}
+       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
+       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}
         \textcolor{mGray}{  \emph{(-- check postcondition --) }}
@@
         \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
-        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addSugar(n)}}}}\\
+        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\
 
@@
 \Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
-\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } 
-\CONTAIN \effect_{post}^{addSugar(n)}  }
+\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
+\CONTAIN \effect_{post}^{addNSugar(n)}  }
 \end{prooftree}}
@@
     \ | \ \es_1 {||} \es_2
-    \ | \ \pi ?  \es
+    \ | \ \pi ? 
       %    \  | \ \es_1 \times \es_2
@@
 
-As the examples show, our proposed effects logic and the abstract semantics for \code{\timedL} not only tightly capture the behaviours of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm.
+As the examples show, our proposed effects logic and the abstract semantics for \code{\timedL} not only tightly capture the behaviors of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm.
 Meanwhile, the inferred temporal traces from a given reactive program enable a compositional timed temporal verification at the source level, which is not yet supported by existing temporal verification techniques.
@@
 The effects of the computation yet to take place as the future effects.
-Besides, prior work \cite{nielson1998behaviour} proposes an annotated type and effect system and infers behaviours from CML \cite{reppy1993concurrent} programs for channel-based communications, though it did not provide any inclusion solving process.
+Besides, prior work \cite{nielson1998behaviour} proposes an annotated type and effect system and infers behaviors from CML \cite{reppy1993concurrent} programs for channel-based communications, though it did not provide any inclusion solving process.
 
@@
 %HipHop.js
-We define the syntax and semantics of the novel \timedEffects, to capture reactive program behaviours and  temporal properties.
+We define the syntax and semantics of the novel \timedEffects, to capture reactive program behaviors and  temporal properties.
 We demonstrate how to give a rather axiomatic semantics to \code{\timedL} by timed-trace processing functions.

### 2022-04-11 code/src/program/fischer.c

@@ -3,7 +3,8 @@ ct := 0;
 
 void process (int i)
 /* req: TRUE /\ (_^*) 
-   ens: TRUE /\ (_^*) */
+   ens: (t0<=d1/\t1=d2) /\ ([x=-1]? . (Update(i)#t0) . (emp#t1) . (([x=i] . Critical(i) . Exit(i) ) + [(~(x=i))]) ^*) */
+
 {
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);
@@ -11,9 +12,9 @@ void process (int i)
   if (x==i) {
     event["Critical"(i)]{ct := (ct + 1)};
     event["Exit"(i)]{ct := (ct-1); x := -1};
-
+    process (i);
   } else {
-    1
+    process (i);
   }
 }
 

### 2022-04-12 paper/tv.tex
m

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Note: Authors migrating a paper from PACMPL format to traditional
-%% SIGPLAN proceedings format must update the '\documentclass' and
-%% topmatter commands above; see 'acmart-sigplanproc-template.tex'.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 %% Some recommended packages.
@@
                         %% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
+\usepackage{subcaption} 
                         %% http://ctan.org/pkg/subcaption
@@
 \definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
-\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc
+\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} 
 \definecolor{mGray}{rgb}{0.4,0.4,0.4}
@@
 %  tabsize=2,
-%  emphstyle={\bf},
-%  stringstyle=\mdseries\rmfamily,
-%  showspaces=false,
-%  keywordstyle=\bfseries\rmfamily\color{deepcerise},
-%  columns=flexible,
-%  basicstyle=\small\sffamily,
-%  showstringspaces=false,
-%  morecomment=[l]\%,
-%  keywordstyle=[2]\color{darklavender}, %
-%  keywords={},
-%    morekeywords=[2]{hiphop,emit, abour,async,Cmd,MorePlease,Sub,Success,Failure, Roll, Html, Random, NewFace, Int, String},
-%  commentstyle=\color{black}\it %mypink
-%}
 
@@
 %% "author year" style.
-%%
-%% If you are preparing content for an event
-%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
-%% citations and references.
 %% Uncommenting
@@
 %% Of note is the shared affiliation of the first two authors, and the
-%% "authornote" and "authornotemark" commands
 %% used to denote shared contribution to the research.
@@
 
-Both preconditions of \codem{addNSugar(n)} requies the 
+Both preconditions of \codem{addNSugar(n)} requires the 
 input  \codem{n} is non-negative, and has no temporal constrains upon 
@@
 a set (possibly infinite) of exact transition systems.
+
+Moreover, we deploy a Hoare-style forward verifier to 
+soundly infer the actual behaviors of given programs 
+concerning the well-defined operational semantics. 
+This approach provides a 
+\emph{direct} (opposite to the techniques which require 
+ manual and remote modeling processes), 
+  and modular compositional 
+verification for real-time systems, which are not possible
+by existing techniques.
 
@@
 
-Having \timedEffects\ to be  the specification language, we are interested in the following verification problem: 
+Having \timedEffects\ to be  the specification language, 
+and the forward verifier to infer the program behaviors, 
+we are interested 
+in the following verification problem: 
 Given a program \code{\mathcal{P}},
-% with the concrete temporal behavior \code{\effect^{\mathcal{P}}}, 
-and a temporal specification \code{\effect^{\prime}}, does 
+and a temporal specification \code{\effect^{\prime}}, does the inclusions 
 \code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds? Typically, 
@@
 
-To efficiently solve the inclusions, i.e., without any translation into
-finite state automata, we develop a TRS
+Since the expressiveness of \timedEffects\ goes beyond 
+finite-state automata, it is neither sufficient nor efficient to 
+ translation them 
+into Timed Automata and reply on the solving engines of Timed Automata.
+Therefore we 
+develop a novel TRS, 
 which  is inspired by Antimirov and Mosses’ algorithm 
@@
 Works based on such a TRS \cite{song2020automated,antimirov1995rewriting,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
-\end{comment}
 
@@
  for the real-time verification. 
-  Our main contributions are:% as follows:
+\end{comment}
+
+ In short, the main contributions of this work are:
 
 \begin{enumerate}
-\item \textbf{The Timed Effects:} We define the syntax 
-({\secref{subsec:Specification_language}}) and semantics 
-({\secref{subsec:Specification_Semantics}}) of \timedEffects, to be the 
-specification language, which captures the target programs' behaviors 
-and non-trivial temporal properties.
-
-\item \textbf{Automated Forward Verifier:} Targeting a core language 
-\code{\timedL} ({\secref{subsec:Targetlanguage}}), we 
-establish its axiomatic semantics via a set of constructive rules 
-(\secref{sec:Verification}), enabling a compositional verifier to 
-infer the program's effects. The verifier triggers the back-end 
+\item \textbf{Language Abstraction:} we formally define 
+a core language \timedL, by defining its syntax and operational semantics, 
+generalizing the real-time systems with mutable variables and timed 
+behavioral patterns. %, such as \emph{delay}, \emph{timeout}, \emph{deadline}.
+
+\item \textbf{Specification Language:} we propose \timedEffects, 
+by defining its 
+syntax and semantics, gaining the expressive power beyond 
+traditional modelling languages for real-time systems.
+
+\item \textbf{Automated Forward Verifier:} we establish a sound axiomatic 
+semantics to infer the 
+temporal behaviors of given target programs.  The verifier triggers the back-end 
 solver TRS.
 
-%which tightly The semantics model closely captures the temporal behaviour of the program,
+%which tightly The semantics model closely captures the temporal behavior of the program,
 
 \item \textbf{An Efficient TRS:}
-We present the rewriting rules, to prove 
-the inferred effects against given temporal properties. %, both expressed by \timedEffects (\secref{sec:Entailment_Prover}).
-
-\item \textbf{Implementation and Evaluation:} We prototype the novel 
+we present the rewriting rules, to prove the inclusion relations between the inferred 
+behaviors and the given temporal specifications, both in  \timedEffects.
+
+\item \textbf{Implementation and Evaluation:} we prototype the novel 
 effects logic and the automated verification system, %on top of the HIP/SLEEK system\cite{chin2012automated}, 
@@
 In step \code{\textcircled{4}}, in order to conduct a further unfolding, we unify time variables \code{t_L^2} and \code{t_R} by adding the constraint \code{t_L^2 {=} t_R}. 
-In step \code{\textcircled{5}}, from the RHS, since \code{\_^\star {=} emp \vee \_ \cdot \_^\star}, eliminating one event \code{\{Ready\}} from it will lead to \code{\bot \vee \_^\star}, which can be normalised into \code{\_^\star} in step \code{\textcircled{6}}.
+In step \code{\textcircled{5}}, from the RHS, since \code{\_^\star {=} emp \vee \_ \cdot \_^\star}, eliminating one event \code{\{Ready\}} from it will lead to \code{\bot \vee \_^\star}, which can be normalized into \code{\_^\star} in step \code{\textcircled{6}}.
 At the end of the rewriting, we manage to prove that \code{(t_L {<}3 {\wedge} t_L^1 {+} t_L^2 {=}t_L {\wedge}t_L^2 {=} t_R)  \Rightarrow  t_R {<} 3} \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
@@
 %and is helpful
-%in further minimising our core language.
 
@@
 \code{val} is the set of primitive values, 
-\code{es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behaviour.
+\code{es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behavior.
 Let \code{d, s, \varphi \models es} denote the model relation, i.e., 
@@
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            CONCATE                            %%
+%%                            CONCATENATE                         %%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 the computation execution (or events multi-trees, per se), indicating 
-the sequential constraint of the temporal behaviour; and we use \code{d} 
+the sequential constraint of the temporal behavior; and we use \code{d} 
 to record the computation duration of given effects. 
@@
 The program state is initialized using \s{\epsilon, True}. 
-  In this section, we give an axiomatic semantics model\footnote{Based on the operational semantics of Esterel and JavaScript's asynchrony formally defined in \cite{berry1992esterel} and  \cite{madsen2017model} respectively.} for the core language \code{\timedL}, by formalising a set of forward inductive rules.
 These rules transfer program states and systematically accumulate the effects syntactically.
@@
 Secondly, we obtain a new proof context \code{\Gamma^\prime} by adding the current inclusion, as an inductive hypothesis, into the current proof context \code{\Gamma}. 
-%(The soundness condition is guaranteed by rule \code{[REOCCUR]} to avoid the possible cyclicity evident in the proof context) 
 Thirdly, we iterate each element \code{(I, \pi, t) \in F}, and compute the partial derivatives (\emph{next-state} effects) of both the antecedent and consequent w.r.t \code{(I, \pi, t)}.
@@
 %The core implementation is less than 3500 LOC, roughly, 1{+} LOC for the verifier, and 2{+} LOC for the TRS. We prove the soundness of the TRS.
-%Next, we show case studies to demonstrate the feasibilities of our \timedEffects comparing to Timed Automata.
 
@@
 
-Trace-based analyses have been shown capable of statically enforcing flow-sensitive security properties such as safe locking behaviour \cite{foster2002flow} and resource usage policies such as file usage protocols and memory management \cite{marriott2003resource}.
+Trace-based analyses have been shown capable of statically enforcing flow-sensitive security properties such as safe locking behavior \cite{foster2002flow} and resource usage policies such as file usage protocols and memory management \cite{marriott2003resource}.
 In \cite{bartoletti2005enforcing}, a trace effect analysis is used to enforce secure service composition.
@@
 %%
-%% The acknowledgments section is defined using the "acks" environment
 %% (and NOT an unnumbered section). This ensures the proper
@@
 %\begin{acks}
-%To Robert, for the bagels and explaining CMYK and color spaces.
 %\end{acks}
@@
   \input{rules/rule2}
-- It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \effect1} is nullable, while \codeme{ \effect_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
+  - It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
 Therefore, these entailments are evidently invalid.\\
@@
   \input{rules/rule3}
-- To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \effect_1}}.
-Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \effect_1}}.
-When the \code{\m{fst}} set of \code{\effect_1} is empty, \code{\effect_1} is possible \code{\bot} or \code{\epsilon}; and \code{\effect_2} is nullable.
+  - To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}.
+Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \es_1}}.
+When the \code{\m{fst}} set of \code{\es_1} is empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon}; and \code{\es_2} is nullable.
 For both cases, the inclusion is valid.
 
-- To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \effect_1}}.
-Given the promises that  \codeme{\pi_1 : \effect_1 \CONTAIN \pi_3 : \effect_3}, we get \codeme{d,  \varphi \models {\pi_3 : \effect_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \effect_3 \CONTAIN  \pi_4 : \effect_4}, we get \codeme{d,  \varphi \models {\pi_4 : \effect_4}}; Given the promises that  \codeme{\pi_4 : \effect_4 \CONTAIN \pi_2 : \effect_2}, we get \codeme{d,  \varphi \models {\pi_2 : \effect_2}}.
+  - To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}.
+Given the promises that  \codeme{\pi_1 : \es_1 \CONTAIN \pi_3 : \es_3}, we get \codeme{d,  \varphi \models {\pi_3 : \es_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \es_3 \CONTAIN  \pi_4 : \es_4}, we get \codeme{d,  \varphi \models {\pi_4 : \es_4}}; Given the promises that  \codeme{\pi_4 : \es_4 \CONTAIN \pi_2 : \es_2}, we get \codeme{d,  \varphi \models {\pi_2 : \es_2}}.
 Therefore,  the inclusion is valid.
@@
 
-- To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \effect_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \effect_2}}.
-For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \effect_1 \rrbracket}; and
-\codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \effect_2 \rrbracket}.
-
-Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bott}, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \effect_2)};
-
-Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \effect_2)}.
-
-By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\effect_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \effect_2)}, the conclusion is valid. 
+  - To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \es_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \es_2}}.
+For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and
+  \codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \es_2 \rrbracket}.
+
+  Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bott}, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};
+
+  Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}.
+
+  By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\es_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}, the conclusion is valid. 
   \\

### 2022-04-12 paper/tv.tex
m

@@
 void addOneSugar() 
-/*req: TRUE/\ _^*
+/*req: true/\ _^*
   ens: t>1 /\ emp#t */ 
@@
 
-\begin{figure}[ht]
-  \vspace{0mm}
-\begin{lstlisting}[columns=fullflexible]
-var x := -1; 
-var ct := 0;
-
-void process (int i)
-/* req  d1<d2,  emp 
-   ens  true, [x=-1](Update(i)#d1.emp#d2.
-   ([x=i]Critical(i).Exit(i) \/ [x!=i]emp))^* */
-{
-  [x=-1] 
-  deadline (event[Update(i)]{x := i}, d1);
-  delay (d2);
-  if (x=i) {
-    event[Critical(i)]{ct := ct +1};
-    event[Exit(i)]{ct := ct-1; x := -1};
-    process (i);
-  } else {
-    process (i);
-}
-
-void main () 
-/* req true /\ emp 
-   ens  true, (!Critical \/ (Critical(i) /\ i=x))^* */
-// ens  true, (ct <= 1)^*
-{ process(0) || process(1) || process(2); }
-\end{lstlisting}  
-  \vspace{0mm}
-  \caption{Fischer's mutual exclusion algorithm.}\label{fig:overview_ficher}
-     \vspace{0mm}
-\end{figure}
-
 %\subsection{HipHop.js and Dependent Effects}
@@
 \begin{lstlisting}[columns=fullflexible]
-void addNSugar(int n)
-/* req n>0,  _^*.Cup 
-   ens  t>=n, Sugar # t */
-{ if n == 0 then event[Sugar] 
-  else {
-    timeout ( addOneSugar(), 1);
-    addNSugar (n-1);}}
-
 void makeCoffee (int n)
-/* req n>0, emp 
- ens  t<5/\t>=n/\t1<3, 
+/*req: n>0 /\ emp 
+  ens: t<5/\t>=n/\t1<3 /\
 Cup.(Sugar#t).(Coffee#t1).Done */
@@
 void main () 
-/* req true, emp 
- ens  t<8, (_^*.Done)#t */
+/*req: true/\ emp 
+  ens: t<8 /\ (_^*.Done)#t */
 { makeCoffee(3);}
 // make coffee with 3 lumps of sugar
-
 \end{lstlisting}  
@@
 
+\begin{figure}[ht]
+  \vspace{0mm}
+\begin{lstlisting}[columns=fullflexible]
+var x := -1; 
+var ct := 0;
+
+void process (int i)
+/* req  d1<d2,  emp 
+   ens  true, [x=-1](Update(i)#d1.emp#d2.
+   ([x=i]Critical(i).Exit(i) \/ [x!=i]emp))^* */
+{
+  [x=-1] 
+  deadline (event["Update"(i)]{x := i}, d1);
+  delay (d2);
+  if (x=i) {
+    event["Critical"(i)]{ct := ct +1};
+    event["Exit"(i)]{ct := ct-1; x := -1};
+    process (i);
+  } else {
+    process (i);
+}
+
+void main () 
+/* req true /\ emp 
+   ens  true, (!Critical \/ (Critical(i) /\ i=x))^* */
+// ens  true, (ct <= 1)^*
+{ process(0) || process(1) || process(2); }
+\end{lstlisting}  
+  \vspace{0mm}
+  \caption{Fischer's mutual exclusion algorithm.}\label{fig:overview_ficher}
+     \vspace{0mm}
+\end{figure}
+
 \section{Language and Specifications}

### 2022-04-12 code/src/program/coffee.c

@@ -27,22 +27,23 @@ ens:  (t>=n)/\ (Sugar #t)
 
 void makeCoffee (int n)
 /*
-req: TRUE/\emp
-ens: (t<=5/\t>=n/\t1<=3)/\Cup.(Sugar#t).(Coffee#t1).Done
+req: TRUE/\(_^*) . Cup
+ens: (t<=5/\t>=n/\t1<=3/\t1>0)/\(Sugar#t).(Coffee#t1)
 */
 {
-    event["Cup"];
     deadline (addSugar(n), 5);
     deadline (event["Coffee"], 3);
-    event["Done"];
 }
 
 
 int main ()
 /*
     req: TRUE /\emp
-    ens: (t<8)/\ (((_^*).Done)#t)
+    ens: (t<=10)/\ ((((~Done)^*))#t).Done 
     */
 {
+    event["Cup"];
     makeCoffee (3);
+    event["Done"];
+
 }

### 2022-04-12 paper/tv.tex
m

@@
 \lstdefinelanguage{JavaScript}{
-  keywords={typeof, void, const, new, int, true, false, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
+  keywords={typeof, void, const, new, int, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
   keywordstyle=\color{blue}\bfseries,
@@
 Moreover, the time bounds 
-can be dependent on the program inputs, demonstrated in \autoref{fig:Value_dependent_intro}, we mark the precondition and postcondition
+can be dependent on the program inputs, demonstrated in \figref{fig:Value_dependent_intro}, we mark the precondition and postcondition
 using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.
@@
   \vspace{-2mm}
-\begin{lstlisting}
+\begin{lstlisting}[name=coffee]
 void addOneSugar() 
@@
 \section{Overview}\label{sec:Overview}
-%We now give a summary of our techniques using running examples.
+
+We now highlight our main methodologies, using the example shown 
+in \figref{fig:overview_coffee}. This example simulate a 
+coffee machine which dynamically adds sugar based on the user's input number.
 
@@
 \subsection{\timedEffects}
-As shown in \figref{fig:overview_eg1}, we define Hoare-triple style specifications (enclosed in \textcolor{darklavender}{\ttfamily{{/*@ ...
-@*/}}}) for each program, which leads to a compositional verification strategy, where static checking and timed temporal verification can be done locally.
-%The set of signals to be present in one logical event are represented within one \code{\_}.
-
-\begin{figure}[ht]
-      \vspace{0mm}
-\begin{lstlisting}[columns=fullflexible]
+As shown in \figref{fig:overview_coffee}, we define Hoare-triple 
+style specifications (enclosed in 
+\textcolor{darklavender}{\ttfamily{{/* ... */}}}) for each function, 
+which leads to a compositional verification strategy, where static 
+checking and timed temporal verification can be done locally.
+
+%columns=fullflexible
+\begin{wrapfigure}{L}{0.45\columnwidth}
+  \vspace{-2mm}
+\begin{lstlisting}[name=coffee]
 void makeCoffee (int n)
-/*req: n>0 /\ emp 
-  ens: t<5/\t>=n/\t1<3 /\
-Cup.(Sugar#t).(Coffee#t1).Done */
-{ event[Cup];
-  deadline (addNSugar(n), 5);
-  deadline (event[Coffee], 3);
-  event[Done];}
-
-void main () 
-/*req: true/\ emp 
-  ens: t<8 /\ (_^*.Done)#t */
-{ makeCoffee(3);}
-// make coffee with 3 lumps of sugar
+/*req: n>=0 /\ _^* . Cup
+  ens: (n<=t<=5 /\ t1<=3) /\
+       (Sugar#t).(Coffee#t1) */
+{ deadline (addNSugar(n), 5);
+  deadline (event["Coffee"], 3);}
+
+int main ()
+/*req: true/\emp
+  ens: t<=8/\((!Done)^*)#t.Done */ 
+{ event["Cup"];
+  makeCoffee (3);
+  event["Done"];}
 \end{lstlisting}  
-      \vspace{0mm}
-      \caption{Dependent Values for Time Bounds (the program is from  \cite{berry2020hiphop}).}\label{fig:overview_eg1}
-         \vspace{0mm}
-\end{figure}
-
-The {\ttfamily{authenticate}} module checks the validity of the identity at each click on login button.
-The operations of requesting the server are wrapped in an {\textbf{\color{purple}\ttfamily{abort}}} statement, which preempts the execution when the responding time goes beyond \code{\m{d}} (given signal \code{\anyevent{Tick}} is present every second).
-
-After emitting the signal \anyevent{Connecting}, it emits  \anyevent{Connected} if the connection succeeds before the  preemptive deadline; otherwise, no signal is emitted. 
-The precondition \code{d{>}3 : \{
-\}^\star \cdot\{\m{Login}\} } requires that the input variable \code{d} is greater than 3, and before entering into this module, the signal \anyevent{Login} should be emitted at the last event, indicating that a login request has been sent.
-The postcondition contains two parts and connected using the disjunction mark \code{{\vee}}: when \code{3{<}t{<}d}, the effects contains two time instances, \code{\{\m{Connecting}\}} and \code{\{\m{Connected}\}}, while the first  event finishes at time \code{t}, %(assuming to reset the clock when executing the module),
-which is no later than \code{\m{d}} time units; otherwise, the effects contains one event \code{\{Connecting\}} which finishes at time \code{d}. \emph{(See a demo from \cite{CODE1})}
-
-As for another example, shown in \figref{fig:overview_eg2}, the module {\ttfamily{main}} %contains a \code{\m{fork/par}   } statement, which 
-spawns two threads running in  parallel.
-The first thread firstly waits for the signal \anyevent{Ready}, then emits  \anyevent{Go}. 
-The second thread firstly emits  \anyevent{Prep}, then calls the function {\ttfamily{cook}} asynchronously. 
-The precondition of {\ttfamily{main}} requires no arithmetic constraints on its input values (expressed as \code{\m{true}}), neither any pre-traces  (expressed as \code{\m{emp}} or \code{\epsilon}, indicating an empty trace).
-The postcondition ensures a trace, where the second event contains at least one signal \code{\anyevent{Cook}} and finishes within 3 time units after the completion of the first event.
-Then we do not care about the rest of the trace (\code{\_} is similar to a wildcard).
-%We omit the implementation of \code{cook} here, while provide the specifications of it. 
-Taking {\ttfamily{main}} as an example, the work flow of the forward verifier is presented in the following sub-section. \emph{(See a demo from \cite{CODE2})}
+      \vspace{-1mm}
+\caption{To make coffee with three portions of sugar 
+within eight time units.}\label{fig:overview_coffee}
+         \vspace{-1mm}
+\end{wrapfigure}
+
+The precondition of \codem{makeCoffee} 
+function says that the input value \codem{n} is a non-negative 
+integer, and it requires that before entering into this 
+function, this history trace must contain the event  
+\anyevent{Cup} in the tail. \codem{makeCoffee} sets a 
+5 time-units deadline while calling 
+\codem{addNSugar} (defined in \figref{fig:Value_dependent_intro}),
+ with argument \codem{n}; then emits event \anyevent{Coffee} with
+ a 3 time-units deadline.
+
+The preconidtion of \codem{main} requies no arithmetic constraints 
+on its inputs (expressed as \codem{true}) and 
+an empty history trace (denoted using \codem{emp} or \code{\epsilon}).
+The postcondition of \codem{main} specifies 
+that before the final \anyevent{Done} happens, there is no 
+occurrence of \anyevent{Done} (\codem{!A} refers to the 
+negation of the event \codem{A}). Moreover, the whole process takes 
+no more than eight time-units to hit the final event.
+
+\timedEffects\ supports more features such as \emph{disjunctions}, 
+\emph{guards} and \emph{parallelism}, etc, which can be found in 
+\secref{subsec:Specification_language} and 
+\secref{subsec:Specification_Semantics}.  
+Directly from the specifications, we are aware of:  
+(i) branching properties: different arithmetic conditions on the input parameters lead to different temporal effects;
+and (ii) required history traces: by defining the prior effects 
+in precondition. 
+The examples 
+already show that our  effects provide more detail information than 
+traditional timed verification, and in fact, it cannot be fully 
+captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
+
+Nevertheless, the gain in expressive power comes at the efforts 
+of a more dedicated verification process, namely handled by our forward verifier and TRS.
 
@@
 An overview of our automated verification system is given in \figref{fig:Verification_oberview} It consists of a Hoare-style forward verifier and a TRS. 
-The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in \timedEffects (cf. \figref{fig:overview_eg1}).
+The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in \timedEffects (cf. \figref{fig:overview_coffee}).
 

### 2022-04-12 code/src/program/coffee.c

@@ -28,18 +28,17 @@ ens:  (t>=n)/\ (Sugar #t)
 void makeCoffee (int n)
 /*
 req: TRUE/\(_^*) . Cup
-ens: (t<=5/\t>=n/\t1<=3/\t1>0)/\(Sugar#t).(Coffee#t1)
+ens: (t<=5/\t>=n/\t1<=3)/\(Sugar#t).(Coffee#t1)
 */
 {
     deadline (addSugar(n), 5);
     deadline (event["Coffee"], 3);
 }
 
-
 int main ()
 /*
     req: TRUE /\emp
-    ens: (t<=10)/\ ((((~Done)^*))#t).Done 
+    ens: (t<=8)/\ ((((~Done)^*))#t).Done 
     */
 {
     event["Cup"];

### 2022-04-12 paper/tv.tex
m

@@
    keywordstyle=[2]\color{purple}\bfseries, %
-   morekeywords=[2]{do, hiphop,every, loop,suspend, when, signal, end, present, nothing, emit,in, out, yield, module,abort, fork, par, run},
+   morekeywords=[2]{do, hiphop,every, loop,suspend, when, signal, end, present, nothing, emit,in, out, yield,abort, fork, par, run},
 }
@@
 \begin{wrapfigure}{L}{0.39\columnwidth}
-  \vspace{-2mm}
 \begin{lstlisting}[name=coffee]
@@
 void addNSugar (int n) 
-/*req: n>=0 /\ _^*
+/*req: true /\ _^*
   ens: d>=n /\ Sugar#d */
@@
 \end{lstlisting}
-\vspace{-1mm}
 \caption{Value-dependent specification.} 
 \label{fig:Value_dependent_intro}
-\vspace{-1mm}
+\vspace{0mm}
 \end{wrapfigure}
@@
 
-Both preconditions of \codem{addNSugar(n)} requires the 
-input  \codem{n} is non-negative, and has no temporal constrains upon 
+Both preconditions require no arithmetic constrains,   
+and  have no temporal constrains upon 
 the history traces. 
@@
 syntax and semantics, gaining the expressive power beyond 
-traditional modelling languages for real-time systems.
+traditional modeling languages for real-time systems.
 
@@
 
-%which tightly The semantics model closely captures the temporal behavior of the program,
-
 \item \textbf{An Efficient TRS:}
-we present the rewriting rules, to prove the inclusion relations between the inferred 
+we present the rewriting rules to prove the inclusion relations between the inferred 
 behaviors and the given temporal specifications, both in  \timedEffects.
@@
 \item \textbf{Implementation and Evaluation:} we prototype the novel 
-effects logic and the automated verification system, %on top of the HIP/SLEEK system\cite{chin2012automated}, 
-%which is available online\cite{Demo}, 
+effects logic and the automated verification system, 
 prove the correctness, report on case studies and experimental results.
-%investigating how it can help to debug errors related to both synchronous and asynchronous programs (\secref{subsec:Case_Studies}).
 
@@
 We now highlight our main methodologies, using the example shown 
-in \figref{fig:overview_coffee}. This example simulate a 
-coffee machine which dynamically adds sugar based on the user's input number.
+in \figref{fig:overview_coffee} This example simulates a 
+coffee machine, which dynamically adds sugar based on the user's input number.
 
@@
 %columns=fullflexible
-\begin{wrapfigure}{L}{0.45\columnwidth}
-  \vspace{-2mm}
+\begin{wrapfigure}{L}{0.47\columnwidth}
+  %\vspace{-1mm}
 \begin{lstlisting}[name=coffee]
@@
 /*req: true/\emp
-  ens: t<=8/\((!Done)^*)#t.Done */ 
+  ens: t<=8/\(((!Done)^*)#t).Done */ 
 { event["Cup"];
@@
 \end{lstlisting}  
-      \vspace{-1mm}
+   %   \vspace{-1mm}
 \caption{To make coffee with three portions of sugar 
 within eight time units.}\label{fig:overview_coffee}
-         \vspace{-1mm}
+ %        \vspace{0mm}
 \end{wrapfigure}
@@
 The precondition of \codem{makeCoffee} 
-function says that the input value \codem{n} is a non-negative 
-integer, and it requires that before entering into this 
+ specifies that the input integer value \codem{n} is non-negative, and it requires that before entering into this 
 function, this history trace must contain the event  
-\anyevent{Cup} in the tail. \codem{makeCoffee} sets a 
-5 time-units deadline while calling 
+\anyevent{Cup} on the tail. Therefore, function calls to \codem{makeCoffee} which 
+do not satisfy the precondition lead to a failure of the verification. 
+\codem{makeCoffee} sets a 
+five time-units deadline while calling 
 \codem{addNSugar} (defined in \figref{fig:Value_dependent_intro}),
  with argument \codem{n}; then emits event \anyevent{Coffee} with
- a 3 time-units deadline.
+ a three time-units deadline.
 
@@
 \secref{subsec:Specification_Semantics}.  
-Directly from the specifications, we are aware of:  
-(i) branching properties: different arithmetic conditions on the input parameters lead to different temporal effects;
-and (ii) required history traces: by defining the prior effects 
+Note that directly from the specifications, we are aware of:  
+(i) the branching properties: different arithmetic conditions on the input parameters lead to different temporal effects;
+and (ii) the required history traces: by defining the prior effects 
 in precondition. 
 The examples 
-already show that our  effects provide more detail information than 
+already show that our  effects provide more detailed information than 
 traditional timed verification, and in fact, it cannot be fully 
 captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
-
-Nevertheless, the gain in expressive power comes at the efforts 
-of a more dedicated verification process, namely handled by our forward verifier and TRS.
+Nevertheless, the gain in expressive power comes from the efforts 
+of a more dedicated verification process, handled by our forward verifier and TRS.
 
 \subsection{Forward Verification}
-As shown in \figref{fig:forward_example}, we demonstrate the forward verification process of the module  {\ttfamily{main}}.
-The program effects states  are captured in the form of \code{\langle \textcolor{huntergreen}{\effect} \rangle}.
-To facilitate the illustration, we label the verification steps by (1), ..., (9), and mark the deployed inference rules (cf.
-\secref{Forward_Rules}) in \textcolor{mGray}{[gray]}.
+As shown in \figref{fig:forward_example}, we demonstrate the 
+forward verification process of the functions \codem{addOneSugar} and   {\codem{addNSugar}}.
+The current effects states are captured 
+in the form of 
+\code{\{ \textcolor{darklavender}{\effect_C} \}}. 
+To facilitate the illustration, we label the verification 
+steps by (1), ..., (11), and mark the deployed inference 
+rules (cf. \secref{Forward_Rules}) in \textcolor{mGray}{[gray]}.
+The verifier invokes the TRS to check language inclusions along the way.
 
@@
          \begin{enumerate}
-\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
-     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
-      \siderule{\scriptsize[FV\text{-}Meth] } \\
+\item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
+\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}}} \\
+\textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
+\quad \siderule{\scriptsize[FV\text{-}Meth] } \\
+
+\item ~\qquad \lstinline|timeout ((), 1);}| \\
+\textcolor{darklavender}{\code{\effect_C^\prime {=} t_0{>}1   \wedge \_^\star \cdot \epsilon \mysharp t_0  }} 
+\quad \siderule {\scriptsize [FV\text{-}Timeout]}
+\item 
+\textcolor{darkred}{\code{
+%\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
+\effect_C^\prime \CONTAIN \effect_{pre}^{addOneSugar(n)} \cdot \effect_{post}^{addOneSugar(n)} \Leftrightarrow  }} 
+ %\textcolor{mGray}{  \emph{(-- check postcondition --) }}
+ \textcolor{darkred}{\code{\code{\code{t_0{>}1   \wedge \epsilon \mysharp t_0}
+ \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
+ \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked }}
+ \\ 
+%ens: t>1 /\ emp#t */ { 
+  \noindent\rule{0.9\columnwidth}{0.4pt}
+~\\
+\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize 
+\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addNSugar(n)}}.}} \\
+     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  true \wedge  \_^\star \} }} 
+      \quad \siderule{\scriptsize[FV\text{-}Meth] } \\
      \item ~\qquad \lstinline|if (n == 0) {| \\
-     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
+     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} 
+     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
       \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
-     \textcolor{darklavender}{\code{\{n{=}0 \wedge  \_^\star \cdot Sugar\} }} \siderule{\scriptsize [FV\text{-}Event]}
+     \textcolor{darklavender}{\code{\{n{=}0 \wedge   \_^\star \cdot Sugar\} }} 
+     \quad \siderule{\scriptsize [FV\text{-}Event]}
      \item 
      ~\qquad \lstinline|else {| \\
-     \textcolor{darklavender}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
+     \textcolor{darklavender}{\code{\{ n  {\neq} 0 \wedge   \_^\star \}  }} 
+     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
     \item 
-     ~\qquad~\qquad \lstinline|timeout ( addOneSugar() , 1);| \\
-     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
+     ~\qquad~\qquad \lstinline|addOneSugar();| \\
+     \textcolor{darklavender}{\code{\{n  {\neq} 0 \wedge  t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} 
+     \quad \siderule {\scriptsize [FV\text{-}Call]}
      \item 
@@
      \textcolor{huntergreen}{\code{n  {\neq} 0   \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
-      \textcolor{mGray}{  \emph{(-check precondition-) }}\\
+      \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: precondition checked.}}
+\\
      \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
      \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
-     \siderule {\scriptsize [FV\text{-}Call]}
+     \quad \siderule {\scriptsize [FV\text{-}Call]}
       \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
       \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }} 
+      \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
+      %\quad \siderule {\scriptsize [Normalization]}
       \\
        \item 
+       %\textcolor{mGray}{  \emph{(-TRS: check the  postcondition; Succeed, cf. \autoref{tab:rewriting_tree_send}-) }}\\
        \textcolor{darkred}{\code{
@@
        \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}  
-        \textcolor{mGray}{  \emph{(-- check postcondition --) }}
+       \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked, cf. \autoref{tab:rewriting_tree_send}. }}
         \\ 
@@
       \caption{The forward verification example for method \code{send}. }\label{fig:forward_example}
-      \vspace{-4mm}
+     % \vspace{-4mm}
 \end{figure}
@@
 
-The effects states (1) and (4) are initial effects entering into the \code{fork/par} statement. The effects state (2) is obtained by [FV-Await], which concatenates a blocking signal 
-%(with a question mark) 
-%followed by a new empty event
- to the current effects. 
-%The effects state (3) is obtained by [FV-Emit], which simply adds  %concatenates an empty event to the current effects. %to be the new current state. 
-The effects states (3) and (5) are obtained by [FV-Emit], which simply adds the emitted  signal to the current event. The intermediate effects state of (7) is obtained by [FV-Call]. 
-Before each function call, it invokes the TRS to check whether the current effects state satisfies the precondition of the callee module.
-If it is not satisfied, the verification fails, otherwise it concatenates the callee's postcondition to the current effects state.
-The final effects state of (7) is obtained by [FV-Async], which adds a new event \code{\{Ready\}} to the current effects state, indicating that the asynchronous program has been resolved.
-In step (8), we parallel compose the effects from both of the branches, and normalize the final effects. 
-After these states transformations, step (9) checks the satisfiability of the inferred effects against the declared postcondition by invoking the TRS.
+The effects states (1) and (4) are obtained by initializing 
+\code{\effect_C} from the precondition, by the \code{[FV\text{-}Meth]} rule. 
+The effects states (5), (7), and (10) are obtained by  
+\code{[FV\text{-}If\text{-}Else]}, which adds the constraints 
+from the conditionals into the current effects state, 
+and unions the effects accumulated from two branches in the end. 
+The effects states (6) is obtained by \code{[FV\text{-}Event]}, 
+which concatenates the triggered singleton event to the 
+end of the current effects state. 
+The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
+Before each function call, it invokes the TRS to check whether the current effects state 
+satisfies the precondition of the callee function. 
+If it is not satisfied, the verification fails; otherwise, 
+it concatenates the callee's postcondition to the current 
+effects state. (We omitted the precondition check for (8) here.)
+The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
+which adds a lower time-bound to the trace. 
+After these states transformations, steps (3) and (11) check the 
+satisfiability of the inferred effects against the declared 
+postcondition by invoking the TRS.
+
+Note that the prior effects in precondition is new regarding 
+the existing real-time verification.
 
@@
 demonstrate how the TRS handles arithmetic constraints and dependent values. 
-%We use the postcondition proving for module \code{main} as an example to briefly demonstrate the rewriting process. 
+%We use the postcondition proving for function \code{main} as an example to briefly demonstrate the rewriting process. 
 As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
@@
 \centering
-      \vspace{0mm}
+     % \vspace{0mm}
 \caption{\label{tab:rewriting_tree_send} The inclusion proving example. }
 
-\vspace{-1mm}
+%\vspace{-1mm}
 \begin{adjustbox}{width=1\textwidth}
@@
 \end{adjustbox}
-            \vspace{0mm}
+      %      \vspace{0mm}
 \end{table*}
@@
 
-\begin{figure}[ht]
+\subsection{The Fischer's mutual exclusion algorithm}
+
+\begin{wrapfigure}{L}{0.47\columnwidth}
   \vspace{0mm}
-\begin{lstlisting}[columns=fullflexible]
+\begin{lstlisting}
 var x := -1; 
@@
      \vspace{0mm}
-\end{figure}
+\end{wrapfigure}
+
+The following models Fischer's mutual exclusion algorithm. 
+where d1 and d2 are two integer constants with d1 < d2; 
+x and ct are global variables. The protocol is modeled as 
+process Protocol, which is the parallel composition of three 
+processes. Each of the three processes attempts to enter 
+the critical section when x is -1, i.e. no other process is 
+currently attempting. Once the process is active, it sets x 
+to its identity i within d1 time units (captured by deadline[d1]). 
+Then it idles for d2 time units (captured by Wait[d2]) and then 
+checks whether x is still i. If so, it enters the critical 
+section and leaves later. Otherwise, it restarts from the 
+beginning.
 
@@
 \defref{Inclusion} and \tabref{tab:rewriting_tree_send}).
-It is triggered i) prior to temporal property assertions; ii) prior to module calls for the precondition checking; and iii) at the end of verifying a module for the post condition checking.
+It is triggered i) prior to temporal property assertions; ii) prior to function calls for the precondition checking; and iii) at the end of verifying a function for the post condition checking.
 Given two effects \code{\effect_1,\ \effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
@@
 
-In practice, system requirements are often structured into phases, which are then composed in many different ways, while TA is deficiency in modelling complex compositional systems.
+In practice, system requirements are often structured into phases, which are then composed in many different ways, while TA is deficiency in modeling complex compositional systems.
 Users often need to manually cast high-level requirements into a set of clock variables with carefully calculated clock constraints, which is tedious and error-prone \cite{sun2013modeling}.
-%Also real-time system modelling based on timed process algebras often suffers from lack of language features or automated tool support. 
+%Also real-time system modeling based on timed process algebras often suffers from lack of language features or automated tool support. 
 On the other hand, all the translation-based approaches share the common problem: 
@@
 In particularly, SKA's \emph{demanding relation} can be reflected by our \emph{instances subsumption} (\defref{Subsumption}), which contributes to the inductive unfolding process.
-Yet our timed effects further capture the time bounds constraints by adding the operator \code{\mysharp }, adapting to real-time system modelling and verification, which is not covered by any existing KA variants/extensions.
+Yet our timed effects further capture the time bounds constraints by adding the operator \code{\mysharp }, adapting to real-time system modeling and verification, which is not covered by any existing KA variants/extensions.
 
@@
 
-However, none of the previous works have considered adding real-time abstractions into the modelling for a more extensive timed verification, which is our work's main contribution.
+However, none of the previous works have considered adding real-time abstractions into the modeling for a more extensive timed verification, which is our work's main contribution.
  %The purely algebraic TRS is flexible to accommodate possibly extended expressiveness for the effects logics.

### 2022-04-12 paper/tv.tex
m

@@
 and a temporal specification \code{\effect^{\prime}}, does the inclusions 
-\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds? Typically, 
+\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds\footnote{The 
+inclusion relation $\CONTAIN$ is formally defined in \defref{Inclusion}.}? Typically, 
 checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.
@@
 develop a novel TRS, 
-which  is inspired by Antimirov and Mosses’ algorithm 
-\cite{antimirov1995rewriting}\footnote{Antimirov and Mosses' 
+which  is inspired by Antimirov and Mosses’ algorithm\footnote{Antimirov and Mosses' 
 algorithm was designed for deciding the inequalities of regular 
@@
 complete 
-axiomatic algorithm of the algebra of regular sets.} but solving the 
+axiomatic algorithm of the algebra of regular sets.} \cite{DBLP:journals/tcs/AntimirovM95} but solving the 
 language inclusions between more expressive \timedEffects.
@@
 \cite{antimirov1995partial}. 
-Works based on such a TRS \cite{song2020automated,antimirov1995rewriting,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+Works based on such a TRS \cite{song2020automated,DBLP:journals/tcs/AntimirovM95,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
 
@@
          \centering
-         {\small
+         {%\small
          \begin{enumerate}
@@
 %ens: t>1 /\ emp#t */ { 
-  \noindent\rule{0.9\columnwidth}{0.4pt}
+  \noindent\rule{0.92\columnwidth}{0.4pt}
 ~\\
@@
 end of the current effects state.
+
 The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
@@
 it concatenates the callee's postcondition to the current 
-effects state. (We omitted the precondition check for (8) here.)
+effects state (the precondition check for step (8) is omitted here).
+
 The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
@@
 \subsection{The TRS}
-Our TRS is obligated to check the inclusions between \timedEffects, which is an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{antimirov1995rewriting}  
-%a TRS 
-%for deciding the inequalities of regular expressions (REs), based on a complete axiomatic algorithm of the algebra of regular sets. 
-%This method is shown to be a better average-case algorithm than those based on the comparison of minimal deterministic finite automatons (DFAs).}
-%Basically, 
-decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their \emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
-\code{[DISPROVE]}, which infers false from trivially inconsistent inequalities; and  
-\code{[UNFOLD]}, which applies \defref{RegularInclusion} to generate new inequalities.
-
-Given \code{\Sigma} is the whole set of the alphabet, 
-\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the signal \code{\anyevent{A}}.
+
+Our TRS is 
+%obligated to check the inclusions between \effectNameSyncEffs, which is 
+an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{DBLP:journals/tcs/AntimirovM95}  
+decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their 
+\emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
+$\codeme{[DISPROVE]}$, which infers false from trivially inconsistent inequalities; and  
+$\codeme{[UNFOLD]}$, which applies \autoref{RegularInclusion} to generate new inequalities.
+In detail, given \code{\Sigma} is the whole set of the alphabet, 
+\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the event \code{\anyevent{A}}.
 
@@
 
-Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  between \timedEffects, where \code{D_{I\mysharp  t}(\effect)} is the partial derivative of \code{\effect} w.r.t the event \code{I} and time bound \code{t}.
-
-\begin{definition}[\timedEffects Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
-For \timedEffects \code{\effect_1 } and \code{\effect_2}, 
-\code{\effect_1  \CONTAIN \effect_2 \Leftrightarrow \forall I. \forall t {\geq} 0.\ D_{I\mysharp  t}(\effect_1)  \CONTAIN D_{I\mysharp  t}(\effect_2)}.
+\begin{definition}[\timedEffects\ Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
+For \timedEffects\ \code{\effect_1 } and \code{\effect_2}, 
+\code{\effect_1 { \CONTAIN} \effect_2 {\Leftrightarrow} \forall \anyevent{A}. \forall t {\geq} 0.\ D_{\anyevent{A} \mysharp  t}(\effect_1)  
+{\CONTAIN} D_{\anyevent{A} \mysharp  t}(\effect_2)}.
 \end{definition}
@@
 
+Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  
+between \timedEffects, where \code{D_{\anyevent{A}\mysharp  t}(\effect)} 
+is the partial derivative of \code{\effect} w.r.t the event 
+\anyevent{A} and the time variable \code{t}.
+
 %Adapting to the context of checking inclusions between \timedEffects, we extend the Antimirov algorithm with
@@
 
-Next, we continue with the step (9) in \figref{fig:forward_example}, to 
+Next, we continue with the step (11) in \figref{fig:forward_example}, to 
 demonstrate how the TRS handles arithmetic constraints and dependent values. 
@@
 
-%\vspace{-1mm}
+\vspace{-1mm}
 \begin{adjustbox}{width=1\textwidth}
@@
   \hline\\
+
+  \code{(I):}\quad
+
   {
-
 \begin{prooftree}
 \Hypo{
-  \code{\siderule{[Prove]}}
-}
-
-\Infer[dashed]1[]{ \code{ n{=}0 \wedge \epsilon 
-\CONTAIN t_r{\geq}0 \wedge \epsilon \mysharp t_r}}
-
-\Infer[dashed]1[]{ \code{ n{=}0 \wedge Sugar
-\CONTAIN t_r{\geq}0 \wedge Sugar \mysharp t_r}}
-
-\Hypo{
-  \code{\textcolor {darkred}{  t{>}1 {\wedge} t_l{\geq}(n\text{-}1) 
-   {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1  \Rightarrow t_r{\geq}n
-}  } 
-\code{\siderule{[Prove]}}
- }
-
- \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
- \epsilon
-\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t {\wedge}  t_l{=}t_r^1 
-\wedge \epsilon}}
-
- \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge 
- Sugar \mysharp t_l
-\CONTAIN t_r{\geq}n {\wedge}  t_r{=}t_r^1 {+}t
-\wedge Sugar \mysharp t_r^1}}
-
- \Infer[dashed]1[]{ \code{ n  {\neq} 0  {\wedge}  t{>}1 {\wedge} t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
- Sugar \mysharp t_l
-\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r}}
-
-\Infer[dashed]2[]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
-\code{ (n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)  \wedge \epsilon \mysharp t \cdot 
+  \code{\textcircled{4}\siderule{[\codeme{PROVE}]}}
+}
+
+\Infer[dashed]1[]{ \code{\textcolor {darkred}{n{=}0} \wedge \epsilon 
+\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \epsilon \mysharp t_r}}
+
+\Infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u : true}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge Sugar
+\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge Sugar \mysharp t_r}}
+
+\Hypo{\code{(II)}}
+
+\Infer[dashed]2[{\textcircled{2}\siderule{[\codeme{LHS\text{-}OR}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
+\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge \epsilon \mysharp t \cdot 
  Sugar \mysharp t_l) } 
-\CONTAIN t_r{\geq}n \wedge Sugar \mysharp t_r  }
-
-\Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
-\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r  }
+
+\Infer[dashed]1[{\textcircled{1}\siderule{[\codeme{RENAME}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
+\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1}  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
 \CONTAIN \effect_{post}^{addNSugar(n)}  }
 \end{prooftree}}
+\\~\\
+
+\hline \\
+\code{(II):} \quad
+
+{\begin{prooftree}
+  \Hypo{
+  \code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
+   \wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
+}  } 
+ }
+
+ \Infer[dashed]1[{\textcircled{7}\siderule{[\codeme{PROVE}]}}]{ \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
+ \epsilon
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
+\wedge \epsilon}}
+
+ \Infer[dashed]1[{\textcircled{6}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1)}}]
+ { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
+ Sugar \mysharp t_l
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
+\wedge Sugar \mysharp t_r^1}}
+
+ \Infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
+ { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \epsilon \mysharp t \cdot 
+ Sugar \mysharp t_l
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r}}
+
+\end{prooftree}
+}
+
 \\~\\
@@
 }
-
-Note that event \code{\{Prep\}} entails \code{\_} because the former contains more constraints. We formally define the subsumption for time instances in \defref{Subsumption}.
-Intuitively, we use \code{[DISPROVE]} wherever the left-hand side (LHS) is \emph{nullable}\footnote{If the event sequence is possibly empty, i.e.
-contains \code{\empt}, we call it nullable, formally defined in \defref{Nullable}.} while the right-hand side (RHS) is not.
-\code{[DISPROVE]} is the heuristic refutation step to disprove the inclusion early, improving the verification efficiency.
 
@@
 %(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
-Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic} (cf.
+Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic}.
+%(cf.
 \tabref{tab:rewriting_tree_case_study_finit_infinit}).
@@
 Moreover, our \timedEffects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
-%Antimirov and Mosses' algorithm \cite{antimirov1995rewriting} was designed for deciding the inclusion of regular expressions.   
+%Antimirov and Mosses' algorithm \cite{DBLP:journals/tcs/AntimirovM95} was designed for deciding the inclusion of regular expressions.   
 Kleene algebra (KA) is a decades-old sound and complete equational theory of regular expressions. Among many extensions of KA,

### 2022-04-12 paper/tv.tex
m

@@
   \noindent\rule{0.92\columnwidth}{0.4pt}
+  \vspace{2mm}
 ~\\
@@
 
-\Infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u : true}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge Sugar
-\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge Sugar \mysharp t_r}}
-
-\Hypo{\code{(II)}}
+%\textcolor{blue}{\code{\pi_u : true}}
+\Infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge \cancel{Sugar}
+\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \cancel{Sugar \mysharp t_r}}}
+
+\Hypo{\qquad \code{(II)}}
 
@@
 \hline \\
-\code{(II):} \quad
+\code{(II):} \quad\ \
 
@@
  { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
+\cancel{ Sugar \mysharp t_l}
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
+\wedge \cancel{Sugar \mysharp t_r^1}}}
+
+ \Infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
+ { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \cancel{\epsilon \mysharp t} \cdot 
  Sugar \mysharp t_l
-\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
-\wedge Sugar \mysharp t_r^1}}
-
- \Infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
- { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \epsilon \mysharp t \cdot 
- Sugar \mysharp t_l
-\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r}}
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \cancel{\mysharp t_r}}}
 
@@
 
-As shown in \tabref{tab:rewriting_tree_send}, in step \code{\textcircled{1}}, we rename the time variables to avoid the name clashes between the antecedent and the consequent.  
-In step \code{\textcircled{2}}, we design a new rule \code{[SPLIT]} to accommodate the extended real-time constraints, which introduces two new time variables \code{t_L^1} and \code{t_L^2}, and 
-extends the previous constraint \code{t_L {<} 3} with constraints  \code{t_L^1 {+} t_L^2 {=} t_L}.
-Then \code{t_L^1} and \code{t_L^2} mark the real-time constraints for time instances  \code{\{Prep\}} and \code{\{Cook\}} respectively.
-Then in step \code{\textcircled{3}}, we eliminate \code{\{Prep\}} from the LHS and \code{\_} from the RHS, as the instances entailment  \code{\{Prep\} \subseteq \_} holds.  
-In step \code{\textcircled{4}}, in order to conduct a further unfolding, we unify time variables \code{t_L^2} and \code{t_R} by adding the constraint \code{t_L^2 {=} t_R}. 
-In step \code{\textcircled{5}}, from the RHS, since \code{\_^\star {=} emp \vee \_ \cdot \_^\star}, eliminating one event \code{\{Ready\}} from it will lead to \code{\bot \vee \_^\star}, which can be normalized into \code{\_^\star} in step \code{\textcircled{6}}.
-At the end of the rewriting, we manage to prove that \code{(t_L {<}3 {\wedge} t_L^1 {+} t_L^2 {=}t_L {\wedge}t_L^2 {=} t_R)  \Rightarrow  t_R {<} 3} \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
+As shown in \tabref{tab:rewriting_tree_send}, step 
+\textcircled{1}, renames the time variables to avoid 
+the name clashes between the antecedent and the consequent.  
+Step \textcircled{2} splits the proof tree into two 
+branches, according to the different 
+arithmetic constrains, by rule  $\codeme{[LHS\text{-}OR]}$.
+
+In the first branch, step \textcircled{3} takes the rule 
+$\codeme{[UNFOLD]}$ to eliminate the head of the antecedent. 
+Step \textcircled{4} proves the inclusion, because 
+evidently the consequent \code{t_r {\geq} 0 \wedge \epsilon \mysharp t_r} 
+contains \code{epsilon} when \code{t_r{=}0}.
+
+In the second branch, step \textcircled{5} eliminates the 
+head of the antecedent, where the head is a time duration \code{\epsilon\mysharp t}. 
+Therefore the rule $\codeme{[UNFOLD]}$ subtract the time duration 
+from the consequent, leaving a fresh time variable \code{t_r^1} and 
+an unification constraint \textcolor{blue}{\code{\pi_u : t_r{=}t_r^1 {+}t}}. 
+Similarly, step \textcircled{6} eliminates the head 
+\code{\anyevent{Sugar}\mysharp t_l}, adding \textcolor{blue}{\code{t_l{=}t_r^1}} 
+to the unification constraints. 
+At the end of the rewriting, step \textcircled{7} manages to prove that 
+\code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
+\wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
+}  } \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
 
@@
 %(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
-Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic}.
-%(cf.
-\tabref{tab:rewriting_tree_case_study_finit_infinit}).
+Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using 
+\emph{memorization} \cite{brotherston2005cyclic}, cf., \tabref{tab:reoccur}.
 
@@
 
-\begin{wrapfigure}{L}{0.47\columnwidth}
-  \vspace{0mm}
+\begin{wrapfigure}{L}{0.53\columnwidth}
+  \vspace{-1mm}
 \begin{lstlisting}
@@
 var ct := 0;
-
-void process (int i)
-/* req  d1<d2,  emp 
-   ens  true, [x=-1](Update(i)#d1.emp#d2.
-   ([x=i]Critical(i).Exit(i) \/ [x!=i]emp))^* */
-{
+void proc (int i) {
   [x=-1] 
-  deadline (event["Update"(i)]{x := i}, d1);
+  deadline(event["Update"(i)]{x:=i},d1);
   delay (d2);
   if (x=i) {
-    event["Critical"(i)]{ct := ct +1};
-    event["Exit"(i)]{ct := ct-1; x := -1};
-    process (i);
+    event["Critical"(i)]{ct:=ct+1};
+    event["Exit"(i)]{ct:=ct-1; x:=-1};
+    proc (i);
   } else {
-    process (i);
-}
-
-void main () 
-/* req true /\ emp 
-   ens  true, (!Critical \/ (Critical(i) /\ i=x))^* */
-// ens  true, (ct <= 1)^*
-{ process(0) || process(1) || process(2); }
+    proc (i);}}
+void main () { 
+  proc(0) || proc(1) || proc(2); }
 \end{lstlisting}  
-  \vspace{0mm}
+  \vspace{-1mm}
   \caption{Fischer's mutual exclusion algorithm.}\label{fig:overview_ficher}
-     \vspace{0mm}
+     \vspace{-1mm}
 \end{wrapfigure}
@@
 
+We show that our method is able to prove the algorithm in the 
+section of implementation.
+
 \section{Language and Specifications}
@@
 We here formally define the syntax of \code{\timedL}, as shown in \figref{fig:code_language}
+
+{
+ % \vspace{-2mm}
+\begin{figure}[!ht]
+\renewcommand{\arraystretch}{1.1}
+\centering%\small
+  $
+  \begin{array}{lrcl}
+
+    \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }&
+    \code{%{datat^*}  \  
+   (\alpha^*, {meth^*})} 
+%\qquad   \qquad\quad 
+ %   \m{(Basic\ Types)} \qquad  \code{b} \code{\quad  ::= \quad }
+  %   \code{int\ |\ bool\ |\ void}
+    \\
+    \m{(Assignment)} &  \code{\alpha }&\code{  ::= }&
+    \code{x:=v} 
+   \\
+
+%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
+ %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
+ %   \\
+
+%     \m{(Types)} &  \code{t}&\code{  ::= }&
+% \code{d\ |\ \tau} 
+% \\    
+  \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
+  \code{ mn  \ {(x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
+  \\
+  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
+  \\
+  \m{(Expressions)} &  \code{e}&\code{  ::= }&
+    \code{ v \ | \ 
+    [b]\ e \ |\ mn({v^*}) \ }
+  \code{| 
+ % v.f:=e \ | 
+ \ e_1;e_2\ | \ e_1 || e_2 \ 
+  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
+ }  \\
+
+ &   & & \code{
+  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
+  | \ \textbf{delay} [d] \ 
+  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
+  | \ \textbf{deadline}  [d] \ e \  
+  }  \\
+  ~\\
+
+    \multicolumn{4}{c}{
+ % \code{k^\tau:constant\ of\ type\ \tau\ } 
+ % \qquad\quad
+\code{c  \in \mathbb{Z}}
+\qquad \ \ 
+\code{b  \in \mathbb{B}}
+\qquad \ \ 
+\code{x, mn  ::\in \textbf{var}}  
+\qquad\ \ 
+ \code{(Action\ labels)\ \anyevent{A}  \in \Sigma 
+\qquad\ \ 
+\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
+}   
+    }\\  
+    \hline
+  \end{array}  
+  $
+ \caption{A core first-order imperative language with timed constructs, \timedL.} 
+ \label{fig:code_language}
+
+\end{figure}
+}
 
@@
 Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units.
-
-{
- % \vspace{-2mm}
-\begin{figure}[!ht]
-\renewcommand{\arraystretch}{1.1}
-\centering%\small
-  $
-  \begin{array}{lrcl}
-
-    \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }&
-    \code{%{datat^*}  \  
-   (\alpha^*, {meth^*})} 
-%\qquad   \qquad\quad 
- %   \m{(Basic\ Types)} \qquad  \code{b} \code{\quad  ::= \quad }
-  %   \code{int\ |\ bool\ |\ void}
-    \\
-    \m{(Assignment)} &  \code{\alpha }&\code{  ::= }&
-    \code{x:=v} 
-   \\
-
-%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
- %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
- %   \\
-
-%     \m{(Types)} &  \code{t}&\code{  ::= }&
-% \code{d\ |\ \tau} 
-% \\    
-  \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
-  \code{ mn  \ {(x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
-  \\
-  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
-  \\
-  \m{(Expressions)} &  \code{e}&\code{  ::= }&
-    \code{ v \ | \ 
-    [b]\ e \ |\ mn({v^*}) \ }
-  \code{| 
- % v.f:=e \ | 
- \ e_1;e_2\ | \ e_1 || e_2 \ 
-  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
- }  \\
-
- &   & & \code{
-  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
-  | \ \textbf{delay} [d] \ 
-  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
-  | \ \textbf{deadline}  [d] \ e \  
-  }  \\
-  ~\\
-
-    \multicolumn{4}{c}{
- % \code{k^\tau:constant\ of\ type\ \tau\ } 
- % \qquad\quad
-\code{c  \in \mathbb{Z}}
-\qquad \ \ 
-\code{b  \in \mathbb{B}}
-\qquad \ \ 
-\code{x, mn  ::\in \textbf{var}}  
-\qquad\ \ 
- \code{(Action\ labels)\ \anyevent{A}  \in \Sigma 
-\qquad\ \ 
-\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
-}   
-    }\\  
-    \hline
-  \end{array}  
-  $
- \caption{A core first-order imperative language with timed constructs, \timedL.} 
- \label{fig:code_language}
-
-\end{figure}
-}
 

### 2022-04-13 paper/tv.tex
m

@@
 %\copyrightyear{2018}           %% If different from \acmYear
+
+\usepackage{xcolor}
+\usepackage[thicklines]{cancel}
+\renewcommand{\CancelColor}{\color{lightgray}}
 
@@
 A number of automatic verification support for Timed Automata have proven 
-to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
+to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,DBLP:conf/seke/WangWH05}.
 
@@
 provide real-time abstractions into traditional linear temporal logics. 
-%Resource usages, provided by a \emph{dynamic ticks}\cite{von2017real}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
+%Resource usages, provided by a \emph{dynamic ticks}\cite{DBLP:conf/fdl/HanxledenBG17}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
 For example, one safety property, \textit{"The event \anyevent{Done} 
@@
 Here, \code{\wedge} connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
-constraints for the \emph{logical-time} sequences \cite{von2017real}; 
+constraints for the \emph{logical-time} sequences \cite{DBLP:conf/fdl/HanxledenBG17}; 
 \code{\_} is a wildcard matching to any event; 
@@
 \cite{antimirov1995partial}. 
-Works based on such a TRS \cite{song2020automated,DBLP:journals/tcs/AntimirovM95,almeida2009antimirov,keil2014symbolic,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,almeida2009antimirov,DBLP:conf/fsttcs/KeilT14,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
 
@@
 
-The preconidtion of \codem{main} requies no arithmetic constraints 
+The precondition of \codem{main} requires no arithmetic constraints 
 on its inputs (expressed as \codem{true}) and 
@@
 traditional timed verification, and in fact, it cannot be fully 
-captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.
+captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,DBLP:conf/seke/WangWH05}.
 Nevertheless, the gain in expressive power comes from the efforts 
@@
 \item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
-\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}}} \\
+\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}.}} \\
 \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
@@
  \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
- \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked }}
+ \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked. }}
  \\ 
@@
 
-%The rule \code{[REOCCUR]} finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{brotherston2005cyclic}.
+%The rule \code{[REOCCUR]} finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{DBLP:conf/tableaux/Brotherston05}.
 (We use \code{\textcolor{persianplum}{(\dagger)}} in \tabref{tab:rewriting_tree_send} to indicate such pairings.)
@@
 \begin{prooftree}
-\Hypo{
-  \code{\textcircled{4}\siderule{[\codeme{PROVE}]}}
-}
-
-\Infer[dashed]1[]{ \code{\textcolor {darkred}{n{=}0} \wedge \epsilon 
+\hypo{\text{\textcircled{4}}
+  \code{\siderule{[\codeme{PROVE}]}}
+}
+
+\infer[dashed]1[]{ \code{\textcolor {darkred}{n{=}0} \wedge \epsilon 
 \CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \epsilon \mysharp t_r}}
@@
 %\textcolor{blue}{\code{\pi_u : true}}
-\Infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge \cancel{Sugar}
+\infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge \cancel{Sugar}
 \CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \cancel{Sugar \mysharp t_r}}}
 
-\Hypo{\qquad \code{(II)}}
-
-\Infer[dashed]2[{\textcircled{2}\siderule{[\codeme{LHS\text{-}OR}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
+\hypo{\qquad \code{(II)}}
+
+\infer[dashed]2[{\textcircled{2}\siderule{[\codeme{LHS\text{-}OR}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
 \code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge \epsilon \mysharp t \cdot 
@@
 
-\Infer[dashed]1[{\textcircled{1}\siderule{[\codeme{RENAME}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
+\infer[dashed]1[{\textcircled{1}\siderule{[\codeme{RENAME}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
 \code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1}  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
@@
 {\begin{prooftree}
-  \Hypo{
+  \hypo{
   \code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
@@
 
- \Infer[dashed]1[{\textcircled{7}\siderule{[\codeme{PROVE}]}}]{ \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
+ \infer[dashed]1[{\textcircled{7}\siderule{[\codeme{PROVE}]}}]{ \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
  \epsilon
@@
 
- \Infer[dashed]1[{\textcircled{6}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1)}}]
+ \infer[dashed]1[{\textcircled{6}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1)}}]
  { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
@@
 
- \Infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
+ \infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
  { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \cancel{\epsilon \mysharp t} \cdot 
@@
 \wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
-}  } \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
+}  } \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{DBLP:conf/tacas/MouraB08}.}; therefore, the proof succeed.
 
@@
 Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using 
-\emph{memorization} \cite{brotherston2005cyclic}, cf., \tabref{tab:reoccur}.
+\emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf., \tabref{tab:reoccur}.
 
@@
 We show that our method is able to prove the algorithm in the 
+section of implementation.  prove the algorithm in the 
 section of implementation.
@@
 \code{[I]} to represent the sequence only contains one event.
-\code{{\tt{SAT}(\pi)} } indicates the pure \code{\pi} is satisfiable, which is discharged by the constraint solver Z3 \cite{de2008z3}.
+\code{{\tt{SAT}(\pi)} } indicates the pure \code{\pi} is satisfiable, which is discharged by the constraint solver Z3 \cite{DBLP:conf/tacas/MouraB08}.
 
@@
 the implementations according to basic regular expressions can be found 
-in prior work \cite{keil2014symbolic}. 
+in prior work \cite{DBLP:conf/fsttcs/KeilT14}. 
 %Here, we focus on presenting 
@@
 \label{table:normalization}
-\setlength{\tabcolsep}{10pt}
+\setlength{\tabcolsep}{8pt}
 \renewcommand{\arraystretch}{1.2}
@@
 
-\begin{minipage}[t]{0.4\textwidth}
+\begin{minipage}[t]{0.45\textwidth}
 \begin{tabular}{||l|l}
@@
 \footnotesize
-  \begin{minipage}[t]{0.6\textwidth}
+  \begin{minipage}[t]{0.45\textwidth}
 \begin{tabular}{||l|l|}
@@
 using OCaml \emph{(A demo page  and source code are available from \cite{CODE})}. 
-The proof obligations generated by the verifier are discharged using constraint solver Z3 \citep{de2008z3}. 
+The proof obligations generated by the verifier are discharged using constraint solver Z3 \citep{DBLP:conf/tacas/MouraB08}. 
 We prove termination and correctness of the TRS. We validate the front-end forward verifier for conformance, against two implementations: the Columbia Esterel Compiler (CEC) 
@@
 %(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
-Termination of TRS is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{brotherston2005cyclic}, i.e., the rule \code{[REOCCUR]}.
+Termination of TRS is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, i.e., the rule \code{[REOCCUR]}.
 % Check out this following example:
 
-As shown in \tabref{tab:reoccur}, the LHS formula is a disjunction of two effects.
-An inclusion with a disjunctive antecedent succeeds if both disjunctions entail the consequent, shown in step \code{\textcircled{1}}.
+As shown in \tabref{tab:reoccur}, the LHS formula is a 
+disjunction of two effects. An inclusion with a disjunctive 
+antecedent succeeds if both disjunctions entail the consequent, 
+shown in step {\textcircled{1}}.  
 %Now we have 2 subtrees, the first subtree is for
@@
 %in . 
-In step \code{\textcircled{2}} of the first sub-tree, in order to eliminate the first event \code{\{B\}}, \code{\{A\}^\star \mysharp  t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
+In step \textcircled{2} of the first sub-tree, in order to eliminate the first event \code{\{B\}}, \code{\{A\}^\star \mysharp  t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
 % is 
 %eliminated by \code{\epsilon}, 
-Then in steps \code{\code{\textcircled{4}}}, we
+Then in steps \textcircled{4}, we
 can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} succeed.
@@
 
-Looking at the second sub-tree, in step \code{\textcircled{5}}, \code{t_L} and \code{t_R} are firstly split 
+Looking at the second sub-tree, in step \textcircled{5}, \code{t_L} and \code{t_R} are firstly split 
 into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
-Then in step \code{\textcircled{6}}, 
+Then in step {\textcircled{6}, 
 \code{\{A\} \mysharp  t_L^1} together with \code{\{A\} \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
@@
 %are unified as new constraint \code{t_L^1{=}t_R^1}.
-In step \code{\textcircled{7}}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
+In step {\textcircled{7}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
 %one in
@@
 
-\Hypo{
+\hypo{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{\textcircled{4}[PROVE]}}]{
+\infer[dashed]1[{\textcircled{4}\siderule{[PROVE]}}]{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{\textcircled{3}[Normalisation]}}]{
+\infer[dashed]1[{\textcircled{3}\siderule{[Normalisation]}}]{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{\textcircled{2}[UNFOLD]}}]{
+\infer[dashed]1[{\textcircled{2}\siderule{[UNFOLD]}}]{
   \code{
@@
 }
-\Hypo{\code{II}}
-
-\Infer[dashed]1[{\siderule{}}]{
+\hypo{\code{II}}
+
+\infer[dashed]1[{\siderule{}}]{
   \code{
@@
 
-\Infer[dashed]2[{\siderule{\textcircled{1}[Disj\text{-}L]}}]{
+\infer[dashed]2[{\textcircled{1}\siderule{[Disj\text{-}L]}}]{
   \code{
@@
 {\begin{prooftree}
-\Hypo{
+\hypo{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{}}]{
+\infer[dashed]1[{\siderule{}}]{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{\textcircled{7}[REOCCUR]}}]{
+\infer[dashed]1[{\textcircled{7}\siderule{[REOCCUR]}}]{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{\textcircled{6}[UNFOLD]}}]{
+\infer[dashed]1[{\textcircled{6}\siderule{[UNFOLD]}}]{
   \code{
@@
 
-\Infer[dashed]1[{\siderule{\textcircled{5}[SPLIT]}}]{
+\infer[dashed]1[{\textcircled{5}\siderule{[SPLIT]}}]{
   \code{
@@
 Compositional specification for real-time systems based on timed process algebras has been extensively studied.
-Examples include the CCS\code{\text{+}}Time \cite{yi1991ccs} and Timed CSP \cite{dong2008timed}.
+Examples include the CCS\code{\text{+}}Time \cite{DBLP:conf/icalp/Yi91} and Timed CSP \cite{dong2008timed}.
 The differences are: 
@@
 We believe in that the goal of verifying real-time systems, in particular safety-critical systems is to check logical temporal properties, which can be done without constructing the whole reachability graph or the full power of model-checking.
-We are of the opinion that our approach is simpler as it is based directly on constraint-solving techniques and can be fairly efficient in verifying systems consisting of many components as it avoids to explore the whole state-space \cite{song2020automated,yi1995automatic}.
-
-%About that, between TRS and the construction of efficient automata, recent work \cite{song2020automated} has shown that the former has a minor performance advantage (over a
+We are of the opinion that our approach is simpler as it is based directly on constraint-solving techniques and can be fairly efficient in verifying systems consisting of many components as it avoids to explore the whole state-space \cite{DBLP:conf/icfem/SongC20,DBLP:conf/forte/YiPD94}.
+
+%About that, between TRS and the construction of efficient automata, recent work \cite{DBLP:conf/icfem/SongC20} has shown that the former has a minor performance advantage (over a
 %benchmark suite) when it is compared with
-%state-of-the-art PAT \cite{sun2009pat} model checker.
+%state-of-the-art PAT \cite{DBLP:conf/cav/SunLDP09} model checker.
 %Improvement came from the avoidance of the more
@@
 
-Moreover, our \timedEffects also draws similarities to Synchronous Kleene Algebra (SKA) \cite{prisacariu2010synchronous}. 
-%Antimirov and Mosses' algorithm \cite{DBLP:journals/tcs/AntimirovM95} was designed for deciding the inclusion of regular expressions.   
-Kleene algebra (KA) is a decades-old sound and complete equational theory of regular expressions. Among many extensions of KA,
- %timed synchronous 
-  SKA is KA extended with a synchrony combinator for actions.
-In particularly, SKA's \emph{demanding relation} can be reflected by our \emph{instances subsumption} (\defref{Subsumption}), which contributes to the inductive unfolding process.
-Yet our timed effects further capture the time bounds constraints by adding the operator \code{\mysharp }, adapting to real-time system modeling and verification, which is not covered by any existing KA variants/extensions.
-
-%Presently, SKA allows the synchrony combinator \code{\times} to be expressed over any two SKA terms to support concurrency.
-%We achieve a similar outcome in Synced Effects by supporting normalization operations during trace synchronization, via a \code{zip} function in the forward rule of \code{[FV\text{-}Par]}.
-%This leads to one major difference in the inclusion/equivalence checking procedure, whereby a TRS for SKA would have to rely on
-%\emph{nullable}, \emph{first}, and \emph{partial derivatives} for terms constructed by the added combinator \code{\times}, but
-%carefully avoided by our TRS construction.
-
 While the original equivalence checking algorithm for SKA terms in \cite{prisacariu2010synchronous} has
-relied on well-studied decision procedures based on classical Thompson \code{\epsilon}-NFA construction, prior work \cite{broda2015deciding}  shows that the use of Antimirov's partial derivatives
+relied on well-studied decision procedures based on classical Thompson \code{\epsilon}-NFA construction, prior work \cite{DBLP:conf/wia/BrodaCFM15}  shows that the use of Antimirov's partial derivatives
 could result in better average-case algorithms for automata construction. 
@@
 %and customized the TRS for inclusion (instead of equivalence) checking. These decisions led to some opportunities for improvements.
-Moreover, between TRS and the construction of efficient automata, prior work has recently shown in \cite{song2020automated} that the former has a minor performance advantage (over a benchmark suite) when it is compared with state-of-the-art PAT \cite{sun2009pat} model checker.
+Moreover, between TRS and the construction of efficient automata, prior work has recently shown in \cite{DBLP:conf/icfem/SongC20} that the former has a minor performance advantage (over a benchmark suite) when it is compared with state-of-the-art PAT \cite{DBLP:conf/cav/SunLDP09} model checker.
 Improvement came from the avoidance of the more expensive automata construction process.
@@
 Combining program events with a temporal program logic for asserting properties of event traces yields a powerful and general engine for enforcing program properties.
-Results in \cite{skalka2008types,skalka2004history,marriott2003resource} have demonstrated that static approximations of program event traces can be generated by type and effect analyses \cite{talpin1994type,amtoft1999type}, in a form amenable to existing model-checking techniques for verification.
+Results in \cite{skalka2008types,DBLP:conf/aplas/SkalkaS04,DBLP:conf/aplas/MarriottSS03} have demonstrated that static approximations of program event traces can be generated by type and effect analyses \cite{talpin1994type,amtoft1999type}, in a form amenable to existing model-checking techniques for verification.
 We call these approximations trace-based effects.
 
-Trace-based analyses have been shown capable of statically enforcing flow-sensitive security properties such as safe locking behavior \cite{foster2002flow} and resource usage policies such as file usage protocols and memory management \cite{marriott2003resource}.
-In \cite{bartoletti2005enforcing}, a trace effect analysis is used to enforce secure service composition.
- Stack-based security policies are also amenable to this form of analysis, as shown in \cite{skalka2004history}.
+Trace-based analyses have been shown capable of statically enforcing flow-sensitive security properties such as safe locking behavior \cite{DBLP:conf/pldi/FosterTA02} and resource usage policies such as file usage protocols and memory management \cite{DBLP:conf/aplas/MarriottSS03}.
+In \cite{DBLP:conf/csfw/BartolettiDF05}, a trace effect analysis is used to enforce secure service composition.
+ Stack-based security policies are also amenable to this form of analysis, as shown in \cite{DBLP:conf/aplas/SkalkaS04}.
 
@@
 The work \cite{malecha2011trace} focuses on finite traces (terminating runs) for web applications, leaving the divergent computation, which indicates \code{false}, verified for every specification.
-The work \cite{nakata2010hoare} focuses on infinite traces (non-terminating runs) by providing coinductively trace definitions.
-More recent works \cite{bubel2015dynamic,song2020automated} proposed dynamic logics and unified operators to reason about possibly finite and infinite traces at the same time.
-
-Moreover, this paper draws similarities to \textit{contextual effects} \cite{neamtiu2008contextual}, which computes the effects that have already occurred as the prior effects.
+The work \cite{DBLP:conf/esop/NakataU10} focuses on infinite traces (non-terminating runs) by providing coinductively trace definitions.
+More recent works \cite{DBLP:conf/tableaux/BubelDHN15,DBLP:conf/icfem/SongC20} proposed dynamic logics and unified operators to reason about possibly finite and infinite traces at the same time.
+
+Moreover, this paper draws similarities to \textit{contextual effects} \cite{DBLP:conf/popl/NeamtiuHFP08}, which computes the effects that have already occurred as the prior effects.
 The effects of the computation yet to take place as the future effects.
-Besides, prior work \cite{nielson1998behaviour} proposes an annotated type and effect system and infers behaviors from CML \cite{reppy1993concurrent} programs for channel-based communications, though it did not provide any inclusion solving process.
+Besides, prior work \cite{DBLP:conf/fase/NielsonAN98} proposes an annotated type and effect system and infers behaviors from CML \cite{DBLP:conf/mcmaster/Reppy93} programs for channel-based communications, though it did not provide any inclusion solving process.
 
 However, none of the previous works have considered adding real-time abstractions into the modeling for a more extensive timed verification, which is our work's main contribution.
- %The purely algebraic TRS is flexible to accommodate possibly extended expressiveness for the effects logics.
-Furthermore, as an extension of prior work \cite{song2020automated}, this work is able to reason about both finite and infinite traces, using cyclic proof techniques established  from \cite{brotherston2005cyclic}.
 

### 2022-04-13 paper/tv.tex
m

@@
 A number of automatic verification support for Timed Automata have proven 
-to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,DBLP:conf/seke/WangWH05}.
+to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
 
@@
 \cite{antimirov1995partial}. 
-Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,almeida2009antimirov,DBLP:conf/fsttcs/KeilT14,hovland2012inclusion}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
 
@@
 traditional timed verification, and in fact, it cannot be fully 
-captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,DBLP:conf/seke/WangWH05}.
+captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
 Nevertheless, the gain in expressive power comes from the efforts 
@@
 \tabref{table:normalization}
-We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A11), suggested by \cite{salomaa1966two}, which was designed for regular languages.
+We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A11), suggested by \cite{DBLP:journals/jacm/Salomaa66}, which was designed for regular languages.
 We develop axioms (A12) to (A22) to further accommodate effects constructed by \code{||},   \code{\mysharp } and \code{\omega}.
@@
 
+Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:conf/vmcai/SongC21,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12,prisacariu2010synchronous}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+
 \section{Related Work}\label{sec:Related_work}
@@
 Compositional specification for real-time systems based on timed process algebras has been extensively studied.
-Examples include the CCS\code{\text{+}}Time \cite{DBLP:conf/icalp/Yi91} and Timed CSP \cite{dong2008timed}.
+Examples include the CCS\code{\text{+}}Time \cite{DBLP:conf/icalp/Yi91} and Timed CSP \cite{DBLP:journals/tse/DongHQSY08}.
 The differences are: 
@@
 There have been a number of translation-based approaches on building verification support for timed process algebras.
-For example, Timed CSP \cite{dong2008timed} is translated to Timed Automata (TA) so that the model checker Uppaal can be \cite{DBLP:journals/sttt/LarsenPY97} applied.
+For example, Timed CSP \cite{DBLP:journals/tse/DongHQSY08} is translated to Timed Automata (TA) so that the model checker Uppaal can be \cite{DBLP:journals/sttt/LarsenPY97} applied.
 TA are finite state automata equipped with clock variables. Models based on TA often have simple structures. For example, the input models of the Uppaal are networks of TA with no hierarchy.
@@
 In practice, system requirements are often structured into phases, which are then composed in many different ways, while TA is deficiency in modeling complex compositional systems.
-Users often need to manually cast high-level requirements into a set of clock variables with carefully calculated clock constraints, which is tedious and error-prone \cite{sun2013modeling}.
+Users often need to manually cast high-level requirements into a set of clock variables with carefully calculated clock constraints, which is tedious and error-prone \cite{DBLP:journals/tosem/00010DLSA13}.
 %Also real-time system modeling based on timed process algebras often suffers from lack of language features or automated tool support. 
 On the other hand, all the translation-based approaches share the common problem: 
-%i) the worst-case complexity of any efficient  equivalences/inclusion checking algorithm \cite{de2006antichains} %based on such translation 
 %goes  exponential in the number of automata states; and ii) 
@@
 
-We believe in that the goal of verifying real-time systems, in particular safety-critical systems is to check logical temporal properties, which can be done without constructing the whole reachability graph or the full power of model-checking.
-We are of the opinion that our approach is simpler as it is based directly on constraint-solving techniques and can be fairly efficient in verifying systems consisting of many components as it avoids to explore the whole state-space \cite{DBLP:conf/icfem/SongC20,DBLP:conf/forte/YiPD94}.
+We believe in that the goal of verifying real-time systems, in particular 
+safety-critical systems is to check logical temporal properties, which can 
+be done without constructing the whole reachability graph or the full power 
+of model-checking. We are of the opinion that our approach is simpler as 
+it is based directly on constraint-solving techniques and can be fairly 
+efficient in verifying systems consisting of many components as it avoids 
+to explore the whole state-space \cite{DBLP:conf/icfem/SongC20,DBLP:conf/forte/YiPD94}.
 
@@
 
-While the original equivalence checking algorithm for SKA terms in \cite{prisacariu2010synchronous} has
-relied on well-studied decision procedures based on classical Thompson \code{\epsilon}-NFA construction, prior work \cite{DBLP:conf/wia/BrodaCFM15}  shows that the use of Antimirov's partial derivatives
-could result in better average-case algorithms for automata construction. 
 %Our present work avoided the consideration for the more general \code{\times} operation from SKA
@@
 Combining program events with a temporal program logic for asserting properties of event traces yields a powerful and general engine for enforcing program properties.
-Results in \cite{skalka2008types,DBLP:conf/aplas/SkalkaS04,DBLP:conf/aplas/MarriottSS03} have demonstrated that static approximations of program event traces can be generated by type and effect analyses \cite{talpin1994type,amtoft1999type}, in a form amenable to existing model-checking techniques for verification.
+Results in \cite{DBLP:journals/jfp/SkalkaSH08,DBLP:conf/aplas/SkalkaS04,DBLP:conf/aplas/MarriottSS03} have demonstrated that static approximations of program event traces can be generated by type and effect analyses \cite{DBLP:journals/iandc/TalpinJ94,DBLP:books/daglib/0098135}, in a form amenable to existing model-checking techniques for verification.
 We call these approximations trace-based effects.
@@
 More related to our work, prior research has been extending Hoare logic with event traces.
-The work \cite{malecha2011trace} focuses on finite traces (terminating runs) for web applications, leaving the divergent computation, which indicates \code{false}, verified for every specification.
+The work \cite{DBLP:journals/jsc/MalechaMW11} focuses on finite traces (terminating runs) for web applications, leaving the divergent computation, which indicates \code{false}, verified for every specification.
 The work \cite{DBLP:conf/esop/NakataU10} focuses on infinite traces (non-terminating runs) by providing coinductively trace definitions.

### 2022-04-13 paper/tv.tex
m

@@
 \code{c  \in \mathbb{Z}}
-\qquad \ \ 
+\qquad \ 
 \code{b  \in \mathbb{B}}
-\qquad \ \ 
+\qquad \  
 \code{x, mn  ::\in \textbf{var}}  
-\qquad\ \ 
- \code{(Action\ labels)\ \anyevent{A}  \in \Sigma 
-\qquad\ \ 
+\qquad\ 
+ \code{(Action\ labels)\ \anyevent{A}  \in \Sigma %\cup \{\tau\}
+\qquad\ 
 \m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
@@
 
-Here, \code{c} is for integer constants, \code{b} is for boolean values, 
+Here, \code{c} and \code{b} are for integer and boolean constants, 
  \code{mn} and \code{x} are for meta-variables.  
  \textbf{var} represents the countably infinite set of arbitrary distinct identifiers.
-\code{ev} refers to a singleton event coming from the finite 
-set of events \code{\Sigma}. 
-%Without loss of generality, any event can be further parametrized with 
-%constant values, e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events. 
-%leading to infinite alphabet.
-%We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
-%Each events raising expression \code{\textbf{event}} is parametrized with an event, to trigger such a single event. 
+
 A program \code{\mathcal{P}} comprises a list of 
-global values initializations \code{\alpha^*} and 
+global-variable initializations \code{\alpha^*} and 
 a list of 
@@
 %Besides, \code{d} denotes the name of a user-defined data type, \code{f} denotes a field name. 
-
 Each method \code{meth} has a name \code{mn}, an expression-oriented body \code{e}, also is associated with a precondition  \code{\effect_{pre}} and a postcondition \code{\effect_{post}} (the syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects}).
@@
 The expression \code{ \textbf{event} [\anyevent{A}(v,  \alpha^*)] } 
-raises an event \anyevent{A} parametrized with \code{v}, 
-and takes a set of 
-assignment actions \code{\alpha^*}. 
+raises an event \anyevent{A}, which comes from the finite 
+set of event labels \code{\Sigma}. %or can be an invisible event, denoted by $\tau$. 
+Without loss of generality, events can be further parametrized with 
+one constant value \code{v} and a set of assignments \code{\alpha^*} upon 
+the mutable variables. %e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events. 
+%leading to infinite alphabet.
+%We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
+%Each events raising expression \code{\textbf{event}} is parametrized with an event, to trigger such a single event.
+
+%parametrized with \code{v}, 
+%and takes a set of 
+%assignment actions \code{\alpha^*}.
+
 Furthermore, a number of timed process constructs can be used to capture common 
 real-time system behavior patterns. Without loss of generality, we 
-assume d is a non-negative integer constant.  $\textbf{delay} [d]$ idles for exactly $d$ 
-time units. In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
+assume \code{d} is a non-negative integer constant.  
+$\textbf{delay} [d]$ idles for exactly $d$ 
+time units.
+ In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
 $e_1$ shall occur before d time units elapse (since the process starts). 
 Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
+Note that the usage of timeout in \figref{fig:Value_dependent_intro} is a 
+special case of the primitive presented here, where \code{e_1} never starts. 
 Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units.
@@
 In order to define the operational semantics of a system model, 
-we define the notion of a configuration to capture the global 
-system state during system execution.
-
-\begin{definition}[System configuration]
-A system configuration is a pair $c = (\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
+we define the notion of a configuration, in \defref{sys_configuration}, to capture 
+the global system state during system execution.
+
+\begin{definition}[System configuration]\label{sys_configuration}
+A system configuration \code{\zeta} is a pair $(\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
 \end{definition}
 
-A transition of the system is of the form $c \xrightarrow[]{l} c^\prime$ where $c$ and $c^\prime$ are 
+A transition of the system is of the form $\zeta \xrightarrow[]{l} \zeta^\prime$ 
+where $\zeta$ and $\zeta^\prime$ are 
 the system configurations before and after the transition respectively. 
-Transition labels \code{l} consist: 
-%We adopt the following naming convention for transition labels: 
-$t$, denoting a non-negative real integer; 
-$\tau$, denoting an invisible event;
-$\anyevent{A} \in \Sigma $ is an observable 
-event; and $\sigma \in \Sigma\cup \{\tau\}$. 
-For event, $c \xrightarrow[]{\text{t}} c^\prime$ denotes a transition of \codem{t} time units elapsing. 
+%There are four type of the transition labels  :
+We adopt the following naming convention \cite{DBLP:conf/icfem/SunLDZ09} for the transition labels \code{l}: 
+(1) $t$, denoting a non-negative real integer; 
+(2) $\tau$, denoting an invisible event; % which do not make changes to the global valuation;
+(3) $\anyevent{A}$ is an observable event. 
+%and (4) $\sigma \in \Sigma\cup \{\tau\}$. 
+For example, $\zeta \xrightarrow[]{\text{t}} \zeta^\prime$ denotes a transition 
+of \code{t} time-units elapsing. 
 In the following, we present the firing rules which are associated with 
 the timed process constructs. 
-
 {{\small
@@
   t {\leq} d 
-}{(\env, \textbf{delay}[d]) \xrightarrow[]{\text{t}} (\env, \textbf{delay} [d \text{-}t])}\ [de_1]} 
+}{(\env, \textbf{delay}[d]) \xrightarrow[]{\text{t}} (\env, \textbf{delay} [d \text{-}t])}\ [delay_1]} 
 \qquad \qquad 
 \code{\frac{
-}{(\env, \textbf{delay} [0]) \xrightarrow[]{\tau} (\env, ())}\ [de_2]} 
+}{(\env, \textbf{delay} [0]) \xrightarrow[]{\tau} (\env, ())}\ [delay_2]} 
 \end{flalign*}}}
 
-The above captures behaviors of process \code{\textbf{delay}[d]}. 
-Rule \code{de_1} states that the process may idle for 
-any amount of time as long as it is less than or equal to \codem{d} time units; 
-Rule \code{de_2} states that the process terminates immediately after 
-\codem{d} becomes \codem{0}.
+The above captures behaviors of process \textbf{delay}[d]. 
+Rule \code{[delay_1]} states that the process may idle for 
+any amount of time as long as it is less than or equal to \code{d} time units; 
+Rule \code{[delay_2]} states that the process terminates immediately after 
+\code{d} becomes \code{0}.
 {{\small\begin{flalign*}
@@
   (\env,e_1) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_1^\prime)
-}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)}\ [to_1]} 
+}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)}\ [tot_1]} 
 \quad  
@@
   (\env,e_1) \xrightarrow[]{\tau} (\env^\prime,e_1^\prime)  
-}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [to_2]} 
+}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [tot_2]} 
 \\
@@
   (\env,e_1) \xrightarrow[]{\text{t}} (\env,e_1^\prime)  \quad (t {\leq} d) 
-}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [to_3]} 
+}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [tot_3]} 
 \quad  
 \code{\frac{
-}{(\env, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (\env, e_2)}\ [to_4]} 
+}{(\env, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (\env, e_2)}\ [tot_4]} 
 \end{flalign*}}}
 If an observable event \anyevent{A} can be engaged by \code{e_1}, 
-then \code{e_1\ \textbf{timeout}[d]\ e_2} becomes \code{e_1^\prime} (rule \code{[to_1]}). 
-An invisible transition does 
-not solve the choice (rule \code{[to_2]}). 
+then $e_1\ \textbf{timeout}[d]\ e_2$ becomes \code{e_1^\prime} (rule \code{[tot_1]}). 
+An invisible transition continues the waiting on \code{e_1} (rule \code{[tot_2]}). 
 If \code{e_1} may idle for less than or equal 
-to \codem{d} time units, so is the composition (rule \code{[to_3]}). 
-When \codem{d} becomes \codem{0}, 
-\code{e_2} takes over control by a silent transition (rule \code{[to_4]}).
+to \code{d} time units, so is the composition (rule \code{[tot_3]}). 
+When \code{d} becomes \code{0}, 
+\code{e_2} takes over control by a silent transition (rule \code{[tot_4]}).
 {{\small\begin{flalign*}
@@
   (\env,e) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)
-}{(\env, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (\env^\prime, \textbf{deadline}  [d] \ e^\prime)} [dl_1]} 
-\quad 
+}{(\env, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (\env^\prime, \textbf{deadline}  [d] \ e^\prime)} [ddl_1]} 
+\ \ \  
 \code{\frac{
   (\env,e) \xrightarrow[]{\text{t}} (\env,e^\prime)  \quad (t {\leq} d)
-}{(\env, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (\env, \textbf{deadline}  [d \text{-}t] \ e^\prime )} [dl_2]} 
+}{(\env, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (\env, \textbf{deadline}  [d \text{-}t] \ e^\prime )} [ddl_2]} 
 \end{flalign*}}}
 
-Intuitively, \code{\textbf{deadline}\  [d] \ e} behaves exactly as 
-\code{e} except that it must terminate before \codem{d} time units.
+Intuitively, $\textbf{deadline}\  [d] \ e$ behaves exactly as 
+\code{e} except that it must terminate before \code{d} time units.
 
@@
     \env \not\models  b 
-  }{(\env, [b] \ e ) \xrightarrow[]{t} (\env, [b] \ e)}\ [gu_1]} 
+  }{(\env, [b] \ e ) \xrightarrow[]{t} (\env, [b] \ e)}\ [guard_1]} 
   \ \ \qquad
@@
     \env \models  b 
-  }{(\env, [b] \ e ) \xrightarrow[]{\tau} (\env, e)}\ [gu_2]} 
+  }{(\env, [b] \ e ) \xrightarrow[]{\tau} (\env, e)}\ [guard_2]} 
+\end{flalign*}}}
+
+{{\small\begin{flalign*}
+\code{\frac{
+  (\env,e_1) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime,e_1^\prime) 
+}{(\env, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime, e_1^\prime ; e_2)}\ [se]} 
   \ \ \qquad 
@@
   }{(\env, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (\env^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
-\ \ 
-\code{\frac{
-  (\env,e_1) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime,e_1^\prime) 
-}{(\env, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime, e_1^\prime ; e_2)}\ [se]} 
 \end{flalign*}}}

### 2022-04-13 paper/tv.tex
m

@@
 Expressions comprise simple values \code{v};
-a guarded process is written as \code{[b]e} where if b is true, 
+a guarded process is written as \code{[b]e} where if \code{b} is true, 
 then it behaves as \code{e}, else it idles until \code{b} becomes true; 
@@
   \code{\frac{
+    \env \models  b 
+  }{(\env, [b] \ e ) \xrightarrow[]{\tau} (\env, e)}\ [guard_1]} 
+  \ \ \qquad\qquad 
+  \code{\frac{
     \env \not\models  b 
-  }{(\env, [b] \ e ) \xrightarrow[]{t} (\env, [b] \ e)}\ [guard_1]} 
-  \ \ \qquad
-  \code{\frac{
-    \env \models  b 
-  }{(\env, [b] \ e ) \xrightarrow[]{\tau} (\env, e)}\ [guard_2]} 
+  }{(\env, [b] \ e ) \xrightarrow[]{t} (\env, [b] \ e)}\ [guard_2]} 
 \end{flalign*}}}
-
+The guarded process \code{[b]e} behaves as \code{e} when \code{b} is true, 
+otherwise it idles until \code{b} becomes true. 
 {{\small\begin{flalign*}
 \code{\frac{
-  (\env,e_1) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime,e_1^\prime) 
-}{(\env, e_1; e_2 ) \xrightarrow[]{\anyevent{A}/\tau} (\env^\prime, e_1^\prime ; e_2)}\ [se]} 
-  \ \ \qquad 
+  (\env,e_1) \xrightarrow[]{l} (\env^\prime,e_1^\prime) 
+}{(\env, e_1; e_2 ) \xrightarrow[]{l} (\env^\prime, e_1^\prime ; e_2)}\ [seq_1]} 
+\qquad
 \code{\frac{
-  }{(\env, \alpha ) \xrightarrow[]{\tau} (\alpha(\env), ())}\ [assign]} 
+}{(\env, (); e_2 ) \xrightarrow[]{\tau} (\env, e_2)}\ [seq_2]} 
+\qquad
+\code{\frac{
+  (\env,e_1) \xrightarrow[]{l} (\env^\prime,e_1^\prime) 
+}{(\env, e_1 || e_2 ) \xrightarrow[]{l} (\env^\prime, e_1^\prime || e_2)}\ [par_1]} 
+\\ 
+  \code{\frac{
+    (\env,e_2) \xrightarrow[]{l} (\env^\prime,e_2^\prime) 
+  }{(\env, e_1 || e_2 ) \xrightarrow[]{l} (\env^\prime, e_1 || e_2^\prime)}\ [par_2]} 
+  \qquad \qquad 
+  \code{\frac{
+    (\env,e_1) \xrightarrow[]{t} (\env,e_1^\prime) 
+    \qquad 
+    (\env,e_2) \xrightarrow[]{t} (\env,e_2^\prime) 
+  }{(\env, e_1 || e_2 ) \xrightarrow[]{t} (\env, e_1^\prime || e_2^\prime)}\ [par_3]} 
 \end{flalign*}}}
-
-{{\small\begin{flalign*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  %%   deadline                 %%
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \code{\frac{
-    (\env,e_1) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_1^\prime) 
-  }{(\env, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (\env^\prime, e_1^\prime || e_2)}\ [pa_1]} 
-  \ \   
-  \code{\frac{
-    (\env,e_2) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_2^\prime) 
-  }{(\env, e_1 || e_2 ) \xrightarrow[]{\anyevent{A}} (\env^\prime, e_1 || e_2^\prime)}\ [pa_2]} 
-\end{flalign*}}}
+Rules \code{[seq_1]} and \code{[seq_2]} state that \code{e_1} takes the control 
+when it still can behave; then the control transfers to \code{e_2} when \code{e_1}
+terminates. Rules \code{[par_1]} and \code{[par_2]} state that in a parallel composition, 
+if any of \code{e_1} or \code{e_2} can proceed, they proceed on their own. Rule 
+\code{[par_3]} states that if both of the branches idle, they idle together.
 
@@
     \ | \ \ev
-   \  | \ \es_1 {\seq} \es_2
-    \ | \ \es_1 {\vee} \es_2
+   \  | \ \es_1 \seq \es_2
+    \ | \ \es_1 \vee \es_2
     \ | \ \es_1 {||} \es_2
@@
 
-The  syntax of the \timedEffects is formally defined in 
+The  syntax of the \timedEffects\ is formally defined in 
 \figref{fig:Syntax_of_Types_and_Effects} Effects is 
- a conditioned time  event sequence \code{{\pi},  es} or a disjunction of two effects $\es_1 \vee \es_2$.
+ a conditioned event sequence \code{{\pi}\wedge es} or a disjunction of 
+ two effects $\effect_1 \vee \effect_2$.
 Timed sequences comprise \textit{nil} ($\bott$);
@@
 parallel composition of two processes is written as \code{\es_1 || \es_2}, where \code{\es_1} and \code{\es_2} 
-may communicate via multi-party event synchronization or shared variables. 
-We introduce a new operator \code{\mysharp }, and the effects \code{es \mysharp  t } represents that a trace takes real-time \code{t} to complete, where \code{t} is a \emph{term}. 
-A time sequence can be constructed by \code{\star}, representing zero or more times repetition of a trace.
-
-\code{\anyevent{A}(v, \pi, \alpha^*)} stands for an event labeled 
-as \anyevent{A} with parameter \code{v}, guard \code{\pi} and assignment operations \code{\alpha^*}. 
+may communicate via multi-party event synchronization or shared variables;
+a blocking waiting for a certain of constraint to be satisfied \code{\pi ?}; 
+We introduce a new operator \code{\mysharp }, and the effects 
+\code{\es \mysharp t} represents that a trace takes real-time 
+\code{t} to complete, where \code{t} is a \emph{term}. 
+A timed sequence can be constructed by \code{\es^\star}, representing zero or 
+more times repetition of the trace \code{\es}.
+
+\anyevent{A}\code{(v, \alpha^*)} stands for an observable event with label 
+\anyevent{A}, parameterized by \code{v}, and the assignment operations \code{\alpha^*}. 
+\code{\tau(\pi)} is an invisible event, which can be parameterized with a pure formula 
+\code{\pi}\footnote{The difference between 
+\code{\tau(\pi)} and \code{\pi?} is \code{\tau(\pi)} leads to false (\code{\bot}) if 
+\code{\pi} is not satisfied, whereas  \code{\pi?} waits until \code{\pi} is satisfied.}. 
 To make the specification more expressive, events can also be 
-\code{\anynotevent{A}}, representing  events which are not 
+{\anynotevent{A}}, referring to those events which are not 
 labeled using \anyevent{A}; and a wildcard \code{\_}, which matches to all the events.
@@
 \code{val} is the set of primitive values, 
-\code{es} is the set of event sequences (or event multi-trees, per se), indicating the sequencing constraints on temporal behavior.
-Let \code{d, s, \varphi \models es} denote the model relation, i.e., 
-the effects \code{es} take exactly \code{d} time units to complete; 
+\code{\es} is the set of event sequences (or event multi-trees, per se), 
+indicating the sequencing constraints on temporal behaviors.
+Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
+the effects \code{\effect} take \code{d} time units to complete; 
 the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
-temporal effects \code{es}, with \code{d}, \code{s}, \code{\varphi} 
+temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
 from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
-\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{ev^*} \ .
-
-As shown in \figref{fig:Sementic}, we define the semantics of our effects. 
-We use $\lappend$ to represent the append operation of two event sequences. 
-We use $[]$ to represent the empty sequence, \code{[ev]} to represent 
-the sequence only contains a singleton event.
-
-\begin{figure}[]
+\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{\es} \ .
+
+\begin{figure}[!ht]
   \vspace{-1mm}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge \es_1{\vee}\es_2}  
+&\code{d, s, \varphi \models {\pi} \wedge (\es_1{\vee}\es_2)}  
 &\m{iff}\quad & 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge (\ev_1{\cdot}\es_1)||(\ev_2{\cdot}\es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models {\pi}  \wedge \ev_1{\cdot} (\es_1||(\ev_2{\cdot}\es_2)) } 
-\ or\ \code{d, s, \varphi \models {\pi}  \wedge \ev_2{\cdot}((\ev_1{\cdot}\es_1)||\es_2)  } \\
+&\code{d, s, \varphi \models {\pi} \wedge (\ev_1 \cdot \es_1)||(\ev_2 \cdot \es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models {\pi}  \wedge \ev_1 \cdot  (\es_1||(\ev_2 \cdot \es_2)) } 
+\ or\ \code{d, s, \varphi \models {\pi}  \wedge \ev_2 \cdot ((\ev_1 \cdot \es_1)||\es_2)  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 &\code{d, s, \varphi \models {\pi} \wedge (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models {(\pi{\wedge}t_1 {\geq}t_2)}, (\ev\mysharp t_1) } 
-\ or\ \code{d, s, \varphi \models {(\pi{\wedge}t_1 {<}t_2)}  , (\ev\mysharp t_1){\cdot}(\epsilon \mysharp  (t_2\text{-}t_1))  } \\
+&\m{iff}\quad & \code{d, s, \varphi \models {(\pi{\wedge}t_1 {\geq}t_2)} \wedge (\ev\mysharp t_1) } 
+\ or\ \code{d, s, \varphi \models {(\pi{\wedge}t_1 {<}t_2)}  \wedge (\ev\mysharp t_1) \cdot (\epsilon \mysharp  (t_2\text{-}t_1))  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 {True} }, 
-\  \exists \code{\es_1,\es_2}. \  \code{\es_1 {\cdot} \es_2 {=} es}\\
+\  \exists \code{\es_1,\es_2}. \  \code{\es_1  \cdot  \es_2 {=} es}, \  \m{fresh}\ t_1, t_2,\\
 &&& \qquad  s.t. \ \code{d, s, \varphi {\models} {(\pi 
-{\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)}  , 
-(\es_1\mysharp t_1) {\cdot} (\es_2\mysharp t_2) } \\
+{\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)} \wedge 
+(\es_1\mysharp t_1)  \cdot  (\es_2\mysharp t_2) } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \code{d, s, \varphi \models {\pi}  \wedge \empt}\ or \ 
-\code{d, s, \varphi \models {\pi}  \wedge es {\cdot} es^\star}\\
+\code{d, s, \varphi \models {\pi}  \wedge es  \cdot  es^\star}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
+
+As shown in \figref{fig:Sementic}, we define the semantics of our effects. 
+We use $\lappend$ to represent the append operation of two event sequences. 
+We use $[]$ to describe the empty sequence, \code{[\ev]} to represent 
+the sequence that only contains one singleton event. 
+Notice that, except for the traces constructed by \code{\mysharp}, simple events 
+are taken to be happening in instant time.
 

### 2022-04-13 paper/tv.tex
m

@@
 
+\usepackage{tikz}
 \usepackage{xcolor}
@@
 \begin{figure}[!ht]
-  \vspace{-1mm}
+  \vspace{-3mm}
   \renewcommand{\arraystretch}{1.2}
@@
 
-\begin{wrapfigure}{R}{0.5\columnwidth}
+\begin{wrapfigure}{R}{0.54\columnwidth}
   \vspace{-3mm}
-\centering
-\includegraphics[width=0.5\columnwidth]{verification.png}
-        \vspace{-3mm}
+
+\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
+
+\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.65,xscale=0.65]
+%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
+
+%Rounded Rect [id:dp1113766752673011] 
+\draw  [line width=1.5]  (68,142.52) ..
+controls (68,136.24) and (73.09,131.15) ..
+(79.37,131.15) -- (216.63,131.15) ..
+controls (222.91,131.15) and (228,136.24) ..
+(228,142.52) -- (228,176.63) ..
+controls (228,182.91) and (222.91,188) ..
+(216.63,188) -- (79.37,188) ..
+controls (73.09,188) and (68,182.91) ..
+(68,176.63) -- cycle ;
+%Shape: Rectangle [id:dp6438165442964394] 
+\draw  [line width=1.5]  (67,51) -- (287,51) -- (287,104) -- (67,104) -- cycle ;
+%Rounded Rect [id:dp29624677487783313] 
+\draw  [line width=1.5]  (328,142.52) ..
+controls (328,136.24) and (333.09,131.15) ..
+(339.37,131.15) -- (473.63,131.15) ..
+controls (479.91,131.15) and (485,136.24) ..
+(485,142.52) -- (485,176.63) ..
+controls (485,182.91) and (479.91,188) ..
+(473.63,188) -- (339.37,188) ..
+controls (333.09,188) and (328,182.91) ..
+(328,176.63) -- cycle ;
+%Shape: Rectangle [id:dp5138829561825217] 
+\draw  [line width=1.5]  (309,52) -- (486,52) -- (486,104) -- (309,104) -- cycle ;
+%Straight Lines [id:da1612175737893331] 
+\draw [line width=1.5]    (137,109) -- (137,127.22) ;
+\draw [shift={(137,130.22)}, rotate = 270] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) ..
+controls (9.04,-1.82) and (4.3,-0.39) ..
+(0,0) ..
+controls (4.3,0.39) and (9.04,1.82) ..
+(14.21,4.28)   ;
+%Straight Lines [id:da5383095517878319] 
+\draw [line width=1.5]    (428,108) -- (428,127.95) ;
+\draw [shift={(428,130.95)}, rotate = 270] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) ..
+controls (9.04,-1.82) and (4.3,-0.39) ..
+(0,0) ..
+controls (4.3,0.39) and (9.04,1.82) ..
+(14.21,4.28)   ;
+%Straight Lines [id:da5450046441977192] 
+\draw [line width=1.5]  [dash pattern={on 5.63pt off 4.5pt}]  (229,164.5) -- (275,165.5) -- (325,165.97) ;
+\draw [shift={(328,166)}, rotate = 180.54] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) ..
+controls (9.04,-1.82) and (4.3,-0.39) ..
+(0,0) ..
+controls (4.3,0.39) and (9.04,1.82) ..
+(14.21,4.28)   ;
+
+% Text Node
+\draw (61,57) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{113.09pt}\setlength\topsep{0pt}
+\begin{center}
+Target Program \&\\ Temporal Specifications
+\end{center}
+
+\end{minipage}};
+% Text Node
+\draw (66.57,139.15) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{77.55pt}\setlength\topsep{0pt}
+\begin{center}
+Hoare-style \\Forward Verifier 
+\end{center}
+
+\end{minipage}};
+% Text Node
+\draw (325,58) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{66.79pt}\setlength\topsep{0pt}
+\begin{center}
+Two \textit{Timeffs} \\LHS and RHS
+\end{center}
+
+\end{minipage}};
+% Text Node
+\draw (325,139.9) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{79.64pt}\setlength\topsep{0pt}
+\begin{center}
+Effects Inclusion \\Prover (TRS)
+\end{center}
+
+\end{minipage}};
+% Text Node
+\draw (223.8,117.63) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{51.49pt}\setlength\topsep{0pt}
+\begin{center}
+Proof \\obligations
+\end{center}
+
+\end{minipage}};
+
+\end{tikzpicture}
+
+ %   \vspace{-4mm}
+%\centering
+%\includegraphics[width=1\columnwidth]{verification.png}
+%        \vspace{-3mm}
+%\caption{\label{fig:Verification_oberview}System Overview.}
+%      \vspace{-1mm}
 \caption{\label{fig:Verification_oberview}System Overview.}
-      \vspace{-1mm}
 \end{wrapfigure}
 
-An overview of our automated verification system is given in \figref{fig:Verification_oberview} It consists of a Hoare-style forward verifier and a TRS. 
-The inputs of the forward verifier are HipHop.js programs annotated with temporal specifications written in \timedEffects (cf. \figref{fig:overview_coffee}).
-
-The input of the TRS is a pair of effects LHS and RHS, referring to the inclusion LHS \code{\CONTAIN} RHS to be checked 
-\textit{(LHS refers to left-hand side effects, and RHS refers to right-hand side effects.)}.
-Besides, the verifier calls the TRS to prove produced inclusions, i.e., between the effects states and pre/post conditions or assertions (cf.
-\figref{fig:forward_example}).
+An overview of our automated verification system is given 
+in \figref{fig:Verification_oberview} 
+Rounded boxes are the main procedures, and both return \emph{true} 
+when the forward reasoning/proving succeeds, return \emph{false} 
+otherwise. Rectangular boxes describe the inputs to the procedures.
+The input of the TRS is a pair of effects LHS and RHS, referring to the 
+inclusion LHS \code{\CONTAIN} RHS to be checked 
+\textit{(LHS refers to left-hand-side effects, and RHS refers to right-hand-side 
+effects)}. 
+Besides, the verifier calls the TRS to prove produced inclusions (dash line). 
 The TRS will be explained in \secref{sec:Entailment_Prover}.

### 2022-04-13 paper/tv.tex
m

@@
 {{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
-\newcommand{\seq}{\cdot}
+\newcommand{\seq} \cdot 
 \newcommand{\choice}{\vee}
@@
 %which replaces temporal operators by time-constrained versions from 
-Here, \code{\wedge} connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
+Here, \code \wedge  connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
 constraints for the \emph{logical-time} sequences \cite{DBLP:conf/fdl/HanxledenBG17}; 
@@
    \ |  {A(}{t_1, t_2}{)}
-  \  |   {{\pi_1}} {\wedge} \code{{\pi}}_2
+  \  |   {{\pi_1}}  \wedge  \code{{\pi}}_2
    \ |  {{\pi_1}} {\vee} \code{{\pi}}_2
@@
 &\code{d, s, \varphi \models {\pi} \wedge (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models {(\pi{\wedge}t_1 {\geq}t_2)} \wedge (\ev\mysharp t_1) } 
-\ or\ \code{d, s, \varphi \models {(\pi{\wedge}t_1 {<}t_2)}  \wedge (\ev\mysharp t_1) \cdot (\epsilon \mysharp  (t_2\text{-}t_1))  } \\
+&\m{iff}\quad & \code{d, s, \varphi \models {(\pi \wedge t_1 {\geq}t_2)} \wedge (\ev\mysharp t_1) } 
+\ or\ \code{d, s, \varphi \models {(\pi \wedge t_1 {<}t_2)}  \wedge (\ev\mysharp t_1) \cdot (\epsilon \mysharp  (t_2\text{-}t_1))  } \\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 &&& \qquad  s.t. \ \code{d, s, \varphi {\models} {(\pi 
-{\wedge} t_1{\geq}0{\wedge}t_2{\geq}0 {\wedge} t_1{+} t_2{=}t)} \wedge 
+ \wedge  t_1{\geq}0 \wedge t_2{\geq}0  \wedge  t_1{+} t_2{=}t)} \wedge 
 (\es_1\mysharp t_1)  \cdot  (\es_2\mysharp t_2) } \\
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1{\cdot}\es_2)}  
+&\code{d, \varphi \models  \pi : (\es_1 \cdot \es_2)}  
 &\m{iff}\quad 
@@
 inheriting the current program state.
-$[FV\text{-}Guard]$ updates the event sequences with with
-the guard \code{b}. 
+$[FV\text{-}Guard]$ computes the effects of \code{e} after concatenating
+\code{(b{=}True)}? in to the current program states.  
 {{\small\begin{gather*}
@@
  \code{\frac{
-  \vdash \{  \Pi, \Theta \}\  e \ 
+  \vdash \{  \Pi, \Theta \cdot (b{=}True)? \}\  e \ 
   \{ \Pi^\prime, \Theta^\prime \}
@@
 {  \vdash \{  \Pi, \Theta \}\  [b]\ e \ 
-\{  \Pi^\prime, b? \Theta^\prime \}} \  
+\{  \Pi^\prime, \Theta^\prime \}} \  
  {[FV\text{-}Guard]}} 
@@
 
-$[FV\text{-}Seq]$ infers  \code{ \{  \Pi_1, \Theta_1\} } 
+$[FV\text{-}Seq]$ computes  \code{ \{  \Pi_1, \Theta_1\} } 
 from \code{e_1}, 
-then further computes  \code{ \{  \Pi_2, \Theta_2 \} } by 
-continuously infer the behaviors of \code{e_2}, to be the final state.
-$[FV\text{-}Par]$ infers behaviors for  \code{e_1} and \code{e_2} independently,
+then further gets  \code{ \{  \Pi_2, \Theta_2 \} } by 
+continuously computing the behaviors of \code{e_2}, to be the final state.
+$[FV\text{-}Par]$ computes behaviors for  \code{e_1} and \code{e_2} independently,
 then parallel merges the effects from these two branches.  
@@
   \code{\frac{ 
- \vdash \{ \Pi, \Theta\} \ e_1 \ \{  \Pi_1, \Theta_1\} 
-\ \  
-\vdash \{ \Pi_1, \Theta_1\} \ e_2 \  \{  \Pi_2, \Theta_2 \} 
+ \vdash \{ \Pi, \Theta\}  e_1  \{  \Pi_1, \Theta_1\} 
+\ \  \ 
+\vdash \{ \Pi_1, \Theta_1\}  e_2   \{  \Pi_2, \Theta_2 \} 
 }{
@@
    {[FV\text{-}Seq]}}  
-\  
+\quad 
   \code{\frac{
- \vdash \{ \Pi, \Theta \} \ e_1 \  \{  \Pi_1, \Theta_1\} 
-\ \  
-\vdash \{  \Pi, \Theta \} \ e_2 \  \{  \Pi_2, \Theta_2 \} 
+ \vdash \{ \Pi, \Theta \}  e_1   \{  \Pi_1, \Theta_1\} 
+\ \  \ 
+\vdash \{  \Pi, \Theta \}  e_2   \{  \Pi_2, \Theta_2 \} 
     }{
 \vdash \{   \Pi, \Theta \}\  e_1 || e_2 \ \{ 
-\Pi_1 {\wedge}\Pi_2 , \Theta_1 || \Theta_2
+\Pi_1  \wedge \Pi_2 , \Theta_1 || \Theta_2
 \}}  
@@
 
+The \code{[FV\text{-}If\text{-}Else]} computes an 
+over-approximation of the program states, by adding different constrains into 
+different branches. \code{\Pi \wedge v} enforces 
+\code{v} into the pure constraints of every traces in the state, same 
+for \code{\Pi \wedge \neg v }.
 {{\small\begin{gather*}
@@
     \begin{matrix}
-\vdash \{ \Pi{\wedge} v, \Theta    \} \ e_1 \ \{  \Theta^{\prime} , \Pi_1 \} 
+\vdash \{ \Pi \wedge v, \Theta    \} \ e_1 \ \{  \Pi_1, \Theta_2 \} 
 \qquad 
-\vdash \{ \Pi{\wedge} \neg v , \Theta  \} \ e_2 \ 
+\vdash \{ \Pi \wedge \neg v , \Theta  \} \ e_2 \ 
 \{  \Pi_2, \Theta_2 \}  
@@
   {\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
-  \textbf{else}\ e_2 \ \s{ \Theta^{\prime} , \Pi_1} {\cup} \s{\Pi_2, \Theta_2} } \  
+  \textbf{else}\ e_2 \ \s{ \Pi_1, \Theta_2} \cup \s{\Pi_2, \Theta_2} } \  
   {[FV\text{-}If\text{-}Else\text{-}Local]}} 
-\\
-\code{\frac{ 
-  \begin{matrix}
-\vdash \{ \Pi, \Theta    \} \ e_1 \ \{  \Theta^{\prime} , \Pi_1 \} 
-\qquad 
-\vdash \{ \Pi , \Theta  \} \ e_2 \ 
-\{  \Pi_2, \Theta_2 \}  
-\qquad (v\ is\ global)
-\end{matrix}}
-{\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
-\textbf{else}\ e_2 \ \s{\Pi, v. \Theta_1 \vee \Theta_2 }} \  
-{[FV\text{-}If\text{-}Else\text{-}Global]}} 
   \end{gather*}}}
-
+  %\\
+%\code{\frac{ 
+%  \begin{matrix}
+%\vdash \{ \Pi, \Theta    \} \ e_1 \ \{ \Pi_1, \Theta_2 \} 
+%\qquad 
+%\vdash \{ \Pi , \Theta  \} \ e_2 \ 
+%\{  \Pi_2, \Theta_2 \}  
+%\qquad (v\ is\ global)
+%\end{matrix}}
+%{\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
+%\textbf{else}\ e_2 \ \s{\Pi, v. \Theta_1 \vee \Theta_2 }} \  
+%{[FV\text{-}If\text{-}Else\text{-}Global]}} 
+Rule \code{[FV\text{-}Event]} simply constructs an new event and 
+concatenates it to the current program states. 
+Rule \code{[FV\text{-}Delay]} creates a trace \code{\epsilon\mysharp t}
+, where \code{t} is fresh, and concatenates it to the current program states, 
+together with the additional constraint \code{t{=}d}. 
   {{\small\begin{gather*}
@@
   \textbf{delay} [d] 
-   \ \{ \Pi{\wedge} t {=}d,  \Theta^\prime \}} \   {[FV\text{-}Delay]}} 
+   \ \{ \Pi \wedge  t {=}d,  \Theta^\prime \}} \   {[FV\text{-}Delay]}} 
 \end{gather*}}}
-
+Rule \code{[FV\text{-}Timeout]} computes the effects from \code{e_1} and \code{e_2}
+using the starting state \code{\s{\Pi, \epsilon}}. The final states are the union 
+of these effects with their corresponding time variables and arithmetic constrains. 
 {{\small\begin{gather*}
@@
     \begin{matrix}
-      \vdash \{ \epsilon, \Pi \}\ e_1 \ \{  \Pi_1, \Theta_1\} 
+      \vdash \{\Pi, \epsilon \}\ e_1 \ \{  \Pi_1, \Theta_1\} 
       \qquad 
-      \vdash \{  \epsilon, \Pi \}\ e_2 \ \{  \Pi_2, \Theta_2 \} 
+      \vdash \{ \Pi, \epsilon \}\ e_2 \ \{  \Pi_2, \Theta_2 \} 
       \\
-      \s{\Theta_f, \Pi_f} {=} \s{\Pi_1 {\wedge}t{\leq}d, \Theta {\cdot}(\Theta_1\mysharp t)}
+      \s{\Theta_f, \Pi_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (\Theta_1\mysharp t)}
       \cup 
-  \s{\Pi_2 {\wedge}t{>}d, \Theta {\cdot}(\Theta_2\mysharp t)}   
-  \quad (t\ is\ fresh)     
+  \s{\Pi_2  \wedge t_2{>}d,  (\Theta_2\mysharp t)}   
+  \quad (t_1, t_2\ are\ fresh)     
 \end{matrix}
@@
   e_1\ \textbf{timeout} [d] \  e_2
-   \ \s{\Theta_f, \Pi_f} } \   {[FV\text{-}Timeout]}} 
+   \ \s{\Pi_f, \Theta \cdot \Theta_f} } \   {[FV\text{-}Timeout]}} 
 \end{gather*}}}
-
+Similar to the previous rule, \code{[FV\text{-}Ddl]} computes the effects 
+from \code{e} and adds an upper time-bound to the result. 
 {{\small\begin{gather*}
@@
     \begin{matrix}
-      \vdash \{ \epsilon, \Pi \}\ e \ \{  \Pi_1, \Theta_1\} 
+      \vdash \{ \Pi, \epsilon\}\ e \ \{  \Pi_1, \Theta_1\} 
   \quad (t\ is\ fresh)     
@@
   \textbf{deadline}  [d] \ e 
-   \ \s{\Pi_1 {\wedge}t{\leq}d, \Theta {\cdot}(\Theta_1\mysharp t)} }   
-    {[FV\text{-}Deadline]}} 
-\ 
-\code{\frac{  \vdash \effect_{pre} 
- \ e \  \{ \Pi, \Theta \} \quad   \{ \Pi, \Theta \} \CONTAIN  
-  \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ 
+   \ \s{\Pi_1  \wedge t{\leq}d, \Theta  \cdot (\Theta_1\mysharp t)} }   
+    {[FV\text{-}Ddl]}} 
+  \end{gather*}}}
+  Rule \code{[FV\text{-}Meth]} initializes the current effects state 
+using the declared precondition, accumulates the effects from the method body, 
+to obtain \code{ \s{\Pi, \Theta}}; then  it
+checks the  inclusion between \code{ \s{\Pi, \Theta}} and the concatenation of 
+the precondition and the postcondition\footnote{Here, 
+\code{\effect_{post}} only needs to capture the effects from the current method body, excluding the history effects specified in \code{\effect_{pre}}. }.
+  {{\small\begin{gather*}
+\code{\frac{  \vdash \s{\effect_{pre}}
+ \ e \  \{ \Pi, \Theta \} \qquad   \{ \Pi, \Theta \} \CONTAIN  
+ \effect_{pre} \cdot \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ 
   \textbf{ens}\  \effect_{post}\} \ \{ e \}}   {[FV\text{-}Meth]}}  
@@
 
+Rule \code{[FV\text{-}Call]} first checks whether the instantiated 
+  precondition of callee, \code{[v^*/x^*]\effect_{pre}}, is satisfied by 
+  the current program state. When the check is succeeded, the final states are 
+  formed by concatenating the  
+  instantiated postcondition to the current states. 
+  %, in which we use an auxiliary function \code{rev} to reverse the event sequences of effects.
 {{\small\begin{gather*}
@@
 \text{\code{ \s{ \Pi, \Theta} \CONTAIN [v^*/x^*] \effect_{pre}   
-\qquad   \effect_f =  \s{ \Pi, \Theta} \cdot  [y^*/x^*]\effect_{post}}}
+\qquad   \effect_f =  \s{ \Pi, \Theta} \cdot  [v^*/x^*]\effect_{post}}}
 \end{matrix}}
@@
 \begin{definition}[Nullable]\label{Nullable}
-Given any \code{\effect {=} \pi {\wedge} \es}, %we define 
+Given any \code{\effect {=} \pi  \wedge  \es}, %we define 
 %\code{\delta_{{\pi}}(\es)} to be \\
@@
   \begin{cases}
-        \code{true} & \code{if\ \empt \in \llbracket {\pi} {\wedge} \es \rrbracket_{\varphi}}\\
-        \code{false} & \code{if\ \empt \notin \llbracket {\pi} {\wedge} \es \rrbracket_{\varphi}}
+        \code{true} & \code{if\ \empt \in \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}\\
+        \code{false} & \code{if\ \empt \notin \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}
       \end{cases} }
@@
 {
- \code{D^{\env}_{h}(\pi \wedge \es_1 {\cdot} \es_2) {=} }
+ \code{D^{\env}_{h}(\pi \wedge \es_1  \cdot  \es_2) {=} }
 \begin{cases}
@@
  \code{D^{\env}_{t}(\pi \wedge  \epsilon \mysharp t^\prime) } {=}  
- \code{\pi{\wedge}(t{=}t^\prime) \wedge \epsilon}
+ \code{\pi \wedge (t{=}t^\prime) \wedge \epsilon}
  \\
  \code{D^{\env}_{t}(\pi \wedge  \es \mysharp t^\prime) } {=} 
- \code{\pi{\wedge}(t{+}t^{\prime\prime}{=}t^\prime) \wedge  
+ \code{\pi \wedge (t{+}t^{\prime\prime}{=}t^\prime) \wedge  
  \es \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)} } 
@@
 \code{D^{\env}_{\ev}(\pi \wedge  \ev^\prime) } {=} 
-\code{\pi{\wedge}(\ev{=}\ev^\prime) \wedge \epsilon} 
+\code{\pi \wedge (\ev{=}\ev^\prime) \wedge \epsilon} 
 \qquad \quad 
@@
 \code{D^{\env}_{(\ev, t)}(\pi \wedge  \es \mysharp t^\prime) } {=} 
-\code{\pi{\wedge}(t{+}t^{\prime\prime}{=}t^\prime) \wedge  
+\code{\pi \wedge (t{+}t^{\prime\prime}{=}t^\prime) \wedge  
 (D^{\env}_{\ev}(\pi \wedge  \es)) \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)}} 
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \mysharp  t_L {\cdot} \{B\}
+    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \mysharp  t_L  \cdot  \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \mysharp  t_R {\cdot} \{B\}
+    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \mysharp  t_R  \cdot  \{B\}
   }
@@
     \textcolor {
-      darkred}{\cdots {\wedge} \cdots
-%      
-%      t_L^1{+}t_L^2{=}t_L{<}3 {\wedge} t_R{=}t_R^1{+}t_R^2 {\wedge} t_L^1{=}t_R^1
-%      {\wedge} t_L^2{=}t_R^2
+      darkred}{\cdots  \wedge  \cdots
+%      
+%      t_L^1{+}t_L^2{=}t_L{<}3  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge  t_L^1{=}t_R^1
+%       \wedge  t_L^2{=}t_R^2
     } :
@@
       darkred}{
-%t_L^1{+}t_L^2{=}t_L {\wedge} t_R{=}t_R^1{+}t_R^2 {\wedge}      
+%t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge       
        t_L^1{=}t_R^1
     } :
-     \cancel{\{A\} \mysharp  t_L^1} {\cdot} \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
+     \cancel{\{A\} \mysharp  t_L^1}  \cdot  \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} :
-     \cancel{\{A\} \mysharp  t_R^1} {\cdot} \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
+     \cancel{\{A\} \mysharp  t_R^1}  \cdot  \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
   }
@@
   \code{
-    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L {\wedge} t_R{=}t_R^1{+}t_R^2} :
-     ( \{A\} \mysharp  t_L^1 {\cdot} \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
+    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} :
+     ( \{A\} \mysharp  t_L^1  \cdot  \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} :
-     ( \{A\} \mysharp  t_R^1 {\cdot} \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
+     ( \{A\} \mysharp  t_R^1  \cdot  \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
   }

### 2022-04-13 paper/tv.tex
m

@@
 {{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
-\newcommand{\seq} \cdot 
-\newcommand{\choice}{\vee}
-\newcommand{\fullname}{Integrated Dependent Effects}
-\newcommand{\name}{integrated effects}
 \newcommand{\code}[1]{{\tt{\ensuremath{\m{#1}}}}}
 \newcommand{\codeme}[1]{{\tt{\ensuremath{#1}}}}
-\newcommand{\empt}{\textcolor{black}{\ensuremath{\epsilon}}}
-\newcommand{\bott}{\textcolor{black}{\ensuremath{\bot}}}
 \newcommand{\CONTAIN}{\sqsubseteq}
@@
 
-\newcommand{\toolName}{Tvide}
 \def\defeq{\ensuremath{\,\triangleq}}
@@
 we prototype the verification system; prove its 
-correctness; report on case studies and the experimental results.
+soundness; report on case studies and the experimental results.
 
@@
 effects logic and the automated verification system, 
-prove the correctness, report on case studies and experimental results.
+prove the soundness, report on case studies and experimental results.
 
@@
 
-   \code{ \bott
-   \  | \ \empt 
+   \code{ \bot 
+   \  | \  \epsilon 
     \ | \ \ev
-   \  | \ \es_1 \seq \es_2
+   \  | \ \es_1 \cdot \es_2
     \ | \ \es_1 \vee \es_2
@@
  two effects $\effect_1 \vee \effect_2$.
-Timed sequences comprise \textit{nil} ($\bott$);
- an empty trace $\empt$;
+Timed sequences comprise \textit{nil} ($\bot $);
+ an empty trace $ \epsilon$;
 a single event \code{ev};
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s,  \varphi \models {\pi} \wedge \empt}  
+&\code{d, s,  \varphi \models {\pi} \wedge  \epsilon}  
 &\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
@@
  \code{\llbracket {\pi}  \wedge t {=} 0 \rrbracket_{s} {=}  
- {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge \empt}\ or  \\
+ {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or  \\
 & & &  \code{\llbracket {\pi}\wedge t {>} 0 \rrbracket_{s} {=}  
@@
 &\code{d, s, \varphi \models {\pi}\wedge es^\star}  &\m{iff}\quad & 
-\code{d, s, \varphi \models {\pi}  \wedge \empt}\ or \ 
+\code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or \ 
 \code{d, s, \varphi \models {\pi}  \wedge es  \cdot  es^\star}\\
@@
 & \code{d, s, \varphi \models false}  &\m{iff}\quad &
- \code{\llbracket {\pi}  \rrbracket_{s} {=} {False} } \ or \ \code{\varphi {=} \bott}
+ \code{\llbracket {\pi}  \rrbracket_{s} {=} {False} } \ or \ \code{\varphi {=} \bot }
 \end{align*}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models \pi : \empt }  
+&\code{d, \varphi \models \pi :  \epsilon }  
 &\m{iff}\quad 
@@
 
+\begin{theorem}[Soundness of the Forward Rules]\label{Soundness_forward_rules}
+  Given any system configuration \code{\zeta = (\env, e)}, by applying the operational
+  semantics rules, 
+  if \code{(\env, e) {\rightarrow^*} (\env^\prime, ())} produces concrete 
+  execution time \code{d} and event trace \code{\varphi}, and \code{ \vdash  
+  \s{\env, \epsilon} e \s{\Pi, \Theta}}, then, 
+  \code{\exists (\pi\wedge \es) \in \s{\Pi, \Theta} } such that 
+  \code{d, \env^\prime, \varphi  \models (\pi\wedge \es)}. 
+  %.
+
+%  pair $(\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
+  \end{theorem}
+
+  \begin{proof}
+    By induction. 
+  %See %the technical report\cite{TR}. 
+  %\appref{proof:SoundnessProof}.
+  \end{proof}
+
 \section{Temporal Verification via a TRS}
@@
 
-The TRS  is an automated entailment checker to prove language inclusions among \timedEffects (cf.
-\defref{Inclusion} and \tabref{tab:rewriting_tree_send}).
-It is triggered i) prior to temporal property assertions; ii) prior to function calls for the precondition checking; and iii) at the end of verifying a function for the post condition checking.
-Given two effects \code{\effect_1,\ \effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
+The TRS  is an automated entailment checker to prove language 
+inclusions among \timedEffects\ (cf. \defref{Inclusion} and 
+\tabref{tab:rewriting_tree_send}). It is triggered i) prior to 
+temporal property assertions; ii) prior to function calls for the 
+precondition checking; and iii) at the end of verifying a function 
+for the post condition checking. Given two effects 
+\code{\effect_1,\ \effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
 
@@
 Note that \code{\Gamma}, \code{\effect} are derived during the inclusion proof. 
-The inclusion checking is initially invoked with \code{\Gamma{=}\_} and \code{\effect{=} True : \empt}.
+The inclusion checking is initially invoked with \code{\Gamma{=}\{\}} and 
+\code{\effect{=} True \wedge  \epsilon}.
 
@@
 %
-%we allow the $\empt$transitions without carrying constraints and resetting clocks at the same time.
+%we allow the $ \epsilon$transitions without carrying constraints and resetting clocks at the same time.
 
@@
   \begin{cases}
-        \code{true} & \code{if\ \empt \in \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}\\
-        \code{false} & \code{if\ \empt \notin \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}
+        \code{true} & \code{if\  \epsilon \in \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}\\
+        \code{false} & \code{if\  \epsilon \notin \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}
       \end{cases} }
@@
 \begin{gather*}
-\code{\delta_{\pi}(\bott) {=} false} 
+\code{\delta_{\pi}(\bot ) {=} false} 
 \qquad\quad
-\code{\delta_{\pi}(\empt) {=} true} 
+\code{\delta_{\pi}( \epsilon) {=} true} 
 \qquad\quad
@@
 \\ 
-\code{\delta_{\pi}(\es \seq \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
+\code{\delta_{\pi}(\es \cdot \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
 \qquad\qquad\quad
-  \code{\delta_{\pi}(\es_1 \choice \es_2) {=} \delta(\es_1) \vee \delta(\es_2)}   
+  \code{\delta_{\pi}(\es_1 \vee \es_2) {=} \delta(\es_1) \vee \delta(\es_2)}   
   \\
@@
    \begin{gather*} 
-  \code{fst_{{\pi}}( \bott) {=} \{\} } \qquad\ \ 
-  \code{fst_{{\pi}}(\empt) {=}  \{\} } \qquad\ \ 
+  \code{fst_{{\pi}}( \bot ) {=} \{\} } \qquad\ \ 
+  \code{fst_{{\pi}}( \epsilon) {=}  \{\} } \qquad\ \ 
   \code{fst_{{\pi}}( \ev) {=} \{ \ev \}  }
@@
   {
-  \code{fst_{{\pi}}(\es_1 {\seq} \es_2) {=} } 
+  \code{fst_{{\pi}}(\es_1 {\cdot} \es_2) {=} } 
   \begin{cases}
@@
 
-\begin{definition}[Partial Derivative\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bott}; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}.
+\begin{definition}[Partial Derivative\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bot }; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}.
 Here we come up with a new notion of partial derivative for \timedEffects.
@@
 \begin{gather*}
-\code{D^{\env}_{h}(\pi \wedge \bott) {=}}  \code{False \wedge \bott} 
+\code{D^{\env}_{h}(\pi \wedge \bot ) {=}}  \code{False \wedge \bot } 
 \qquad\ \ \  
-\code{D^{\env}_{h}( \pi \wedge \empt) {=}}  \code{False \wedge \bott} 
+\code{D^{\env}_{h}( \pi \wedge  \epsilon) {=}}  \code{False \wedge \bot } 
 \qquad\ \ \ 
@@
 \\
-\code{D^{\env}_{h}(\pi \wedge  \es_1 {\choice} \es_2) } {=} \code{ D^{\env}_{h}(\pi \wedge  \es_1) \choice D^{\env}_{h}( \pi \wedge \es_2)} 
+\code{D^{\env}_{h}(\pi \wedge  \es_1 {\vee} \es_2) } {=} \code{ D^{\env}_{h}(\pi \wedge  \es_1) \vee D^{\env}_{h}( \pi \wedge \es_2)} 
 \qquad 
@@
  ~\\
- \code{D^{\env}_{t}(\pi \wedge  \ev) } {=} \code{False \wedge \bott} 
+ \code{D^{\env}_{t}(\pi \wedge  \ev) } {=} \code{False \wedge \bot } 
  \qquad\qquad 
@@
 \code{D^{\env}_{(\ev, t)}(\pi \wedge  \ev^\prime) } {=} 
-\code{False \wedge \bott}  
+\code{False \wedge \bot }  
 \qquad \ \ \  
@@
     \begin{cases}
-          \code{\pi \wedge \es} & \code{if\ D^{\env}_{h}(\pi \wedge \es) = (False \wedge \bott)}\\
+          \code{\pi \wedge \es} & \code{if\ D^{\env}_{h}(\pi \wedge \es) = (False \wedge \bot )}\\
           \code{D^{\env}_{h}(\pi \wedge \es)} & \code{otherwise}
@@
 \label{Base}
-Analogous to  the standard propositional logic, \code{\bott} (referring to \textit{false}) entails any effects, while no \textit{non-false} effects entails \code{\bott}.
+Analogous to  the standard propositional logic, \code{\bot } (referring to \textit{false}) entails any effects, while no \textit{non-false} effects entails \code{\bot }.
 \input{rules/rule1}
@@
 %\hline
-%  \code{\effect \choice \effect \rightarrow \effect} 
-%  &\code{\bott \cdot \effect \rightarrow \bott }  
+%  \code{\effect \vee \effect \rightarrow \effect} 
+%  &\code{\bot  \cdot \effect \rightarrow \bot  }  
 %  &
@@
 %
-%  \code{\bott \choice \effect \rightarrow \effect } & \code{ \effect  \cdot \bott \rightarrow \bott }  &
+%  \code{\bot  \vee \effect \rightarrow \effect } & \code{ \effect  \cdot \bot  \rightarrow \bot  }  &
 %
@@
 %
-%\code{ \effect \choice \bott \rightarrow \effect }
-%&\code{\bott ^\star \rightarrow \empt}
+%\code{ \effect \vee \bot  \rightarrow \effect }
+%&\code{\bot  ^\star \rightarrow  \epsilon}
 %& 
@@
 %
-% \code{\empt \cdot \effect  \rightarrow \effect }
+% \code{ \epsilon \cdot \effect  \rightarrow \effect }
 % &  \code{\epsilon^\star \rightarrow \epsilon}
@@
 %
-%\code{ \effect \cdot \empt \rightarrow \effect}
-%& \code{(\empt \vee \effect)^\star \rightarrow \effect^\star}
+%\code{ \effect \cdot  \epsilon \rightarrow \effect}
+%& \code{( \epsilon \vee \effect)^\star \rightarrow \effect^\star}
 %& \code{ }
@@
 (A15)  &
-\code{ \effect\ ||\ \empt \rightarrow \effect}\\
+\code{ \effect\ ||\  \epsilon \rightarrow \effect}\\
 \hline
 (A16)  &
-\code{ \effect\ ||\ \bott \rightarrow \bott}\\
+\code{ \effect\ ||\ \bot  \rightarrow \bot }\\
 \hline
@@
 (A19)  &
- \code{\empt \mysharp  t \rightarrow \empt}\\
+ \code{ \epsilon \mysharp  t \rightarrow  \epsilon}\\
 \hline
 (A20)  &
- \code{\bot \mysharp  t \rightarrow  \bott}\\
+ \code{\bot \mysharp  t \rightarrow  \bot }\\
 \hline
 (A21)  &
- \code{{{False}} : \effect \rightarrow {{False}} : \bott}\\
+ \code{{{False}} : \effect \rightarrow {{False}} : \bot }\\
 \hline
 (A22)  &
- \code{{\pi} : \bott \rightarrow {{False}} : \bott}\\
-\hline
- %\code{\effect \choice \effect \rightarrow \effect} 
-%  &\code{\bott \cdot \effect \rightarrow \bott }  
+ \code{{\pi} : \bot  \rightarrow {{False}} : \bot }\\
+\hline
+ %\code{\effect \vee \effect \rightarrow \effect} 
+%  &\code{\bot  \cdot \effect \rightarrow \bot  }  
 %  &
@@
 The proof obligations generated by the verifier are discharged using constraint solver Z3 \citep{DBLP:conf/tacas/MouraB08}. 
-We prove termination and correctness of the TRS. We validate the front-end forward verifier for conformance, against two implementations: the Columbia Esterel Compiler (CEC) 
+We prove termination and soundness of the TRS. We validate the front-end forward verifier for conformance, against two implementations: the Columbia Esterel Compiler (CEC) 
 \cite{CEC} and Hiphop.js \cite{HH_im}.
@@
 
-Let's recall the existing challenges in different programming paradigms discussed in \secref{sec:Preliminaries}.
-In this section, we first investigate how our effects logic can help to debug errors related to both synchronous and asynchronous programs.
-Specifically, it effectively resolves the logical correctness checking (for synchronous languages) and critical anti-patterns checking (for premise asynchrony).
 Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.
@@
     \textcolor {darkred}{True} : \cancel{\{B\}} \CONTAIN
-    \textcolor {darkred}{True} : \cancel{\empt \cdot \{B\}}
+    \textcolor {darkred}{True} : \cancel{ \epsilon \cdot \{B\}}
   }
@@
 %Formally, given a KA is \code{(A,+,\cdot, \star,  0, 1)}, a SKA over a finite set \code{A_B} is \code{(A,+, \cdot, \times, \star,  0, 1,  A_B)}, \code{A_B {\subseteq} A}. 
-%Our \code{\bot} corresponds to the \code{0}; our \code{\empt} corresponds to the \code{1}; our \emph{event} containing simultaneous signals can be expressed via \code{\times};
+%Our \code{\bot} corresponds to the \code{0}; our \code{ \epsilon} corresponds to the \code{1}; our \emph{event} containing simultaneous signals can be expressed via \code{\times};
 
@@
 
-%due to the reason that Hoare logic only captures partial correctness, 
-%
-%
-% only captures partial correctness, 
 %
@@
 
-  Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bott}, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};
+  Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bot }, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};
 

### 2022-04-14 paper/tv.tex
m

@@
 The TRS  is an automated entailment checker to prove language 
-inclusions among \timedEffects\ (cf. \defref{Inclusion} and 
-\tabref{tab:rewriting_tree_send}). It is triggered i) prior to 
+inclusions between \timedEffects, cf., \defref{Inclusion} and 
+\tabref{tab:rewriting_tree_send} It is triggered i) prior to 
 temporal property assertions; ii) prior to function calls for the 
@@
 for the post condition checking. Given two effects 
-\code{\effect_1,\ \effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
+\code{\effect_1} and \code{\effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
 
@@
  initial \emph{heads}, denoted as \code{h},  of \code{{\pi} \wedge \es}; and the Derivative 
-function \code{D^{\env}_{h}(\pi \wedge \es)} computes a next-state 
+function \code{D^{\pi}_{h}(\es)} computes a next-state 
 effects after eliminating the head  \code{h} from the current 
-effects \code{{\pi} \wedge \es}, w.r.t \code{\env}.
+effects \code{{\pi} \wedge \es}.
 
@@
 
-\begin{definition}[Nullable]\label{Nullable}
+\begin{definition}[Nullable \footnote{The proof obligations are 
+  discharged using the Z3 SMT prover, while deciding the nullability of effects constructed by symbolic terms, represented by \code{SAT({\pi})}.}]\label{Nullable}
 Given any \code{\effect {=} \pi  \wedge  \es}, %we define 
@@
   \begin{cases}
-        \code{true} & \code{if\  \epsilon \in \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}\\
-        \code{false} & \code{if\  \epsilon \notin \llbracket {\pi}  \wedge  \es \rrbracket_{\varphi}}
+        \code{true} & \code{if\  \epsilon \in \llbracket {\pi}  \wedge  \es \rrbracket}\\
+        \code{false} & \code{if\  \epsilon \notin \llbracket {\pi}  \wedge  \es \rrbracket}
       \end{cases} }
@@
 \qquad\quad
-\code{\delta_{\pi}(\pi^\prime? \es){=} \delta_{\pi}(\es)}   
+\code{\delta_{\pi}(\pi^\prime?){=} false}  
 \qquad\quad\
@@
 \\ 
+\ \ 
 \code{\delta_{\pi}(\es \cdot \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
@@
 A head can be  $t$, denoting a pure time passing; 
-  $\ev $, denoting a pure event passing; 
+  $\ev $, denoting an instant event passing; or 
   $(\ev, t)$, denoting an event passing which takes time \code{t}. 
@@
    \begin{gather*} 
-  \code{fst_{{\pi}}( \bot ) {=} \{\} } \qquad\ \ 
-  \code{fst_{{\pi}}( \epsilon) {=}  \{\} } \qquad\ \ 
+  \code{fst_{{\pi}}( \bot ) {=} \{\} } \qquad\quad 
+  \code{fst_{{\pi}}( \epsilon) {=}  \{\} } \qquad\quad
   \code{fst_{{\pi}}( \ev) {=} \{ \ev \}  }
-  \qquad\ \ 
+  \qquad\quad
   \code{fst_{{\pi}}(  \epsilon \mysharp  t) {=}  \{ t \}}
-  \qquad\ \ 
+  \qquad\quad
   \code{fst_{{\pi}}( {\es^\star} ) {=} fst_{{\pi}}({ \es})}
    \\
-   \code{fst_{{\pi}}(\es \mysharp  t) {=}  \{(\ev, t) \ | \ \ev \in fst_{\pi}(\es) \}} 
-   \ \ \  \emph{(t\ is\ fresh)}
-  \qquad\quad 
-  \qquad\quad
-  \code{fst_{{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }  \\
-  \code{fst_{{\pi}}(\epsilon \mysharp  t) {=}  \{t\}} 
-   \qquad \qquad
-  \code{fst_{{\pi}}( \pi^\prime? \es ) {=} fst_{\pi}(\es)  }
-      \qquad\qquad
+   \code{fst_{{\pi}}(\es \mysharp  t) {=}  \{(\ev, t^\prime) \ | \ \ev \in fst_{\pi}(\es) \}} 
+   \ \ \  \emph{($t^\prime$\ is\ fresh)}
+  \quad  
+  \qquad
+  \code{fst_{{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }  
+  \\
+  \code{fst_{{\pi}}( \pi^\prime? ) {=} \{\tau(\pi^\prime); \tau(\neg \pi^\prime)\}  }
+      \qquad\qquad\qquad 
      \code{fst_{{\pi}}(  \es_1 {||} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }   
@@
   {
-  \code{fst_{{\pi}}(\es_1 {\cdot} \es_2) {=} } 
+  \code{fst_{{\pi}}(\es_1 \cdot \es_2) {=} } 
   \begin{cases}
-        \code{\code{fst_{{\pi}}(  \es_1)} \cup \code{fst_{{\pi}}(  \es_2)} } & \code{ if\ \delta(\es_1) {=} true}\\
-        \code{\code{fst_{{\pi}}(  \es_1)}} & \code{  if\ \delta(\es_1) {=} false}
+        \code{\code{fst_{{\pi}}(  \es_1)} \cup \code{fst_{{\pi}}(  \es_2)} } \quad   & \code{ if\ \  \delta(\es_1) {=} true}\\
+        \code{\code{fst_{{\pi}}(  \es_1)}} & \code{  if\ \  \delta(\es_1) {=} false}
       \end{cases} 
@@
 
-\begin{definition}[Partial Derivative\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bot }; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}.
-Here we come up with a new notion of partial derivative for \timedEffects.
-}]\label{Derivative}
-Given any \code{\effect {=} \pi \wedge \es}, and a variable valuation function \code{\env}, 
-the partial derivative \code{D^{\env}_{h}(\pi \wedge \es)} 
+\begin{definition}[Partial Derivative]\label{Derivative}
+  Given any \code{\effect {=}\pi \wedge  \es}, 
+  %and a variable valuation function \code{\env}, 
+  the partial derivative \code{D^{\pi}_{h}( \es)} 
    computes the  effects for the 
   left quotient \code{(h)^{\text{-}1}\llbracket \pi \wedge \es 
-\rrbracket_{\env}}. 
+  \rrbracket}\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bot }; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}.
+Here we come up with a new notion of partial derivative for \timedEffects.
+  }. 
   %\footnote{As the reader may notice, our First and Derivative function does not handle the timed sequences constructed by \code{||}, as the synchronous parallel is reduced during the normalization phase.}
   \begin{gather*}
-\code{D^{\env}_{h}(\pi \wedge \bot ) {=}}  \code{False \wedge \bot } 
-\qquad\ \ \  
-\code{D^{\env}_{h}( \pi \wedge  \epsilon) {=}}  \code{False \wedge \bot } 
-\qquad\ \ \ 
-\code{D^{\env}_{h}( \pi \wedge {\es^\star}) } {=} \code{ D^{\env}_{h}(\pi \wedge  {\es}) \cdot {\es^\star}}  
+  \code{D^{\pi}_{h}( \bot ) {=}}  \code{False \wedge \bot } 
+  \qquad\qquad 
+  \code{D^{\pi}_{h}(   \epsilon) {=}}  \code{False \wedge \bot } 
+  \qquad\qquad
+  \code{D^{\pi}_{h}(  \ev^\prime) } {=} 
+  \code{  (\pi \wedge h{=}\ev^\prime) \wedge \epsilon} 
   \\
   {
- \code{\code{D^{\env}_{h}(\pi \wedge \pi^\prime? \es)} {=}}
+   \code{\code{D^{\pi}_{h}( \pi^\prime?)} {=}}
   \begin{cases}
-      \code{\pi \wedge \pi^\prime? \es} \quad &\code{if\ \llbracket \pi^\prime  \rrbracket_{\env} {=} false}   \\
-      \code{D^{\env}_{h}(\pi \wedge \es)} & \code{if\ \llbracket \pi^\prime  \rrbracket_{\env} {=} true} 
+        \code{\pi \wedge \pi^\prime? } &\code{if\ h {\not\Rightarrow}  \pi^\prime}   \\
+        \code{\pi \wedge \epsilon} & \code{if\ h {\Rightarrow} \pi^\prime} 
       \end{cases} 
       }
+      \qquad \quad \ \ \ 
+  {
+   \code{D^{\pi}_{h}( \es_1  \cdot  \es_2) {=} }
+  \begin{cases}
+        \code{D^{\pi}_{h}( \es_1) \cdot  \es_2\ \vee \  D^{\pi}_{h}( \es_2)}  &\code{if\ \delta_{\pi}(\es_1) {=} true}   \\
+        \code{D^{\pi}_{h}( \es_2) \cdot  \es_2} & \code{if\ \delta_{\pi}(\es_1) {=} false} 
+      \end{cases} 
+      }
   \\
-{
- \code{D^{\env}_{h}(\pi \wedge \es_1  \cdot  \es_2) {=} }
-\begin{cases}
-      \code{D^{\env}_{h}(\pi \wedge \es_1) \cdot  \es_2\ \vee \  D^{\env}_{h}(\pi \wedge \es_2)} \quad &\code{if\ \delta_{\pi}(\es_1) {=} true}   \\
-      \code{D^{\env}_{h}(\pi \wedge \es_2) \cdot  \es_2} & \code{if\ \delta_{\pi}(\es_1) {=} false} 
-    \end{cases} 
-    }
+  \code{D^{\pi}_{h}(  {\es^\star}) } {=} \code{ D^{\pi}_{h}(  {\es}) \cdot {\es^\star}}  
+  \qquad\quad \ \ \ 
+  \code{D^{\pi}_{h}(  \es_1 {\vee} \es_2) } {=} \code{ D^{\pi}_{h}(  \es_1) \vee D^{\pi}_{h}(  \es_2)} 
+  \qquad \quad\ \ \ 
+  \code{D^{\pi}_{h}( \es_1 {||}\es_2)} {=} \code{\Bar{\Bar{D}}^{\pi}_{h}( \es_1)} || \code{\Bar{\Bar{D}}^{\pi}_{h}( \es_2)} 
    \\
-\code{D^{\env}_{h}(\pi \wedge  \es_1 {\vee} \es_2) } {=} \code{ D^{\env}_{h}(\pi \wedge  \es_1) \vee D^{\env}_{h}( \pi \wedge \es_2)} 
+   \code{D^{\pi}_{\ev}(  \es \mysharp t) } {=} {\bigvee}
+   \code{ \{ (\pi^\prime \wedge \es^\prime  \mysharp t) \ | \ (\pi^\prime, \es^\prime) \in D^{\pi}_{\ev}(\es) \} } 
 \qquad 
-\code{D^{\env}_{h}(\pi \wedge \es_1 {||}\es_2)} {=} \code{PD^{\env}_{h}(\pi \wedge \es_1)} || \code{PD^{\env}_{h}(\pi \wedge \es_2)} 
- \\~\\
- \hline
- ~\\
- \code{D^{\env}_{t}(\pi \wedge  \ev) } {=} \code{False \wedge \bot } 
- \qquad\qquad 
- \code{D^{\env}_{t}(\pi \wedge  \epsilon \mysharp t^\prime) } {=}  
- \code{\pi \wedge (t{=}t^\prime) \wedge \epsilon}
- \\
- \code{D^{\env}_{t}(\pi \wedge  \es \mysharp t^\prime) } {=} 
- \code{\pi \wedge (t{+}t^{\prime\prime}{=}t^\prime) \wedge  
+   \code{D^{\pi}_{t}(  \es \mysharp t^\prime) } {=} 
+   \code{ (\pi \wedge t{+}t^{\prime\prime}{=}t^\prime) \wedge  
    \es \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)} } 
-\\~\\
-\hline
-~\\
-\code{D^{\env}_{\ev}(\pi \wedge  \ev^\prime) } {=} 
-\code{\pi \wedge (\ev{=}\ev^\prime) \wedge \epsilon} 
-\qquad \quad 
-\code{D^{\env}_{\ev}(\pi \wedge  \es \mysharp t^\prime) } {=} 
-\code{\{(\pi^\prime \wedge \es^\prime \mysharp t^\prime) \ | \ (\pi^\prime \wedge \es^\prime) \in D^{\env}_{\ev}(\pi \wedge  \es)\}} 
-\\~\\
-\hline
-~\\
-\code{D^{\env}_{(\ev, t)}(\pi \wedge  \ev^\prime) } {=} 
-\code{False \wedge \bot }  
-\qquad \ \ \  
-\code{D^{\env}_{(\ev, t)}(\pi \wedge  \es \mysharp t^\prime) } {=} 
-\code{\pi \wedge (t{+}t^{\prime\prime}{=}t^\prime) \wedge  
-(D^{\env}_{\ev}(\pi \wedge  \es)) \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)}} 
-\\
   \end{gather*}
@@
 
+Notice that the derivatives of a parallel composition makes use of the \emph{Parallel Derivative} \code{\Bar{\Bar{D}}^{\pi}_{h}(\es)}, defined as follows: 
   \begin{definition}[Parallel Derivative]\label{Derivative_maybe}
@@
     the parallel derivative is defined as: {
-    \code{PD^{\env}_{h}(\pi \wedge \es) {=}
+      \code{\Bar{\Bar{D}}^{\pi}_{h}( \es) {=}
       \begin{cases}
-          \code{\pi \wedge \es} & \code{if\ D^{\env}_{h}(\pi \wedge \es) = (False \wedge \bot )}\\
-          \code{D^{\env}_{h}(\pi \wedge \es)} & \code{otherwise}
+            \code{ \es} & \code{if\ D^{\pi}_{h}(\pi \wedge \es) = (False \wedge \bot )}\\
+            \code{D^{\pi}_{h}( \es)} & \code{otherwise}
           \end{cases} }
-        }
-
+    }.
   \end{definition}

### 2022-04-14 paper/tv.tex
m

@@
   \begin{cases}
-        \code{\pi \wedge \pi^\prime? } &\code{if\ h {\not\Rightarrow}  \pi^\prime}   \\
-        \code{\pi \wedge \epsilon} & \code{if\ h {\Rightarrow} \pi^\prime} 
+        \code{\pi \wedge \pi^\prime? } &\code{if\ h \not\Rightarrow  \pi^\prime}   \\
+        \code{\pi \wedge \epsilon} & \code{if\ h \Rightarrow \pi^\prime} 
       \end{cases} 
@@
 \label{Prove}
-We use two rules to prove an inclusion: (i) \codeme{[PROVE]} is used when the fst set of the antecedent is empty; and (ii) $\code{[REOCCUR]}$ to prove an inclusion
+We use two rules to prove an inclusion: (i) $\codeme{[PROVE]}$ is 
+used when the fst set of the antecedent is empty; and 
+(ii) $\codeme{[REOCCUR]}$ to prove an inclusion
 when there exist inclusion hypotheses 
-in the proof context $\m{\Gamma}$, which are able to soundly prove the current goal.
-One of the special cases of this rule is when the identical inclusion is shown in the proof context, we then terminate the procedure and prove it as a valid inclusion.
+in the proof context $\m{\Gamma}$, which are able to 
+soundly prove the current goal. One of the special cases of 
+this rule is when the identical inclusion is shown in the proof 
+context, we then terminate the procedure and prove it as a valid 
+inclusion. 
 \input{rules/rule3}
@@
 \label{unfolding}
-This is the inductive step of unfolding the inclusions.
-Firstly, we make use of the auxiliary function \code{fst} to get a set of instances \code{F}, which are all the possible initial time instances from the antecedent.
-Secondly, we obtain a new proof context \code{\Gamma^\prime} by adding the current inclusion, as an inductive hypothesis, into the current proof context \code{\Gamma}. 
-Thirdly, we iterate each element \code{(I, \pi, t) \in F}, and compute the partial derivatives (\emph{next-state} effects) of both the antecedent and consequent w.r.t \code{(I, \pi, t)}.
-The proof of the original inclusion succeeds if all the derivative inclusions succeeds.
+This is the inductive step of unfolding the inclusions. Firstly, 
+we make use of the auxiliary function \code{fst} to get a set of 
+heads \code{H}, which are all the possible initial time instances 
+from the antecedent. 
+Secondly, we obtain a new proof context \code{\Gamma^\prime} by 
+adding the current inclusion, as an inductive hypothesis, into 
+the current proof context \code{\Gamma}. 
+Thirdly, we iterate each element \code{h \in H}, and compute the 
+partial derivatives (\emph{next-state} effects) of both the 
+antecedent and consequent w.r.t \code{h}. The proof 
+of the original inclusion succeeds if all the derivative 
+inclusions succeeds.
 \input{rules/rule4}
@@
 \tabref{table:normalization}
-We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A11), suggested by \cite{DBLP:journals/jacm/Salomaa66}, which was designed for regular languages.
-We develop axioms (A12) to (A22) to further accommodate effects constructed by \code{||},   \code{\mysharp } and \code{\omega}.
-
-%\begin{table}[ht]
-%\vspace{0mm}
-%  \caption{Some Normalization Lemmas for \timedEffects.}
-%  \label{table:normalization}
-%\setlength{\tabcolsep}{13pt}
-%\renewcommand{\arraystretch}{1.1}
-%\centering
-%\vspace{0mm}
-%\begin{tabular}{l || l || l}
-%\hline
-%  \code{\effect \vee \effect \rightarrow \effect} 
-%  &\code{\bot  \cdot \effect \rightarrow \bot  }  
-%  &
-% 
-%  
-%\\ \hline
-%
-%  \code{\bot  \vee \effect \rightarrow \effect } & \code{ \effect  \cdot \bot  \rightarrow \bot  }  &
-%
-%\code{ (\effect_1 \cdot \effect_2) \cdot \effect_3 \rightarrow \effect_1 \cdot (\effect_2 \cdot \effect_3)}
-%\\ \hline
-%
-%\code{ \effect \vee \bot  \rightarrow \effect }
-%&\code{\bot  ^\star \rightarrow  \epsilon}
-%& 
-%
-%
-%
-%\\ \hline
-%
-%
-% \code{ \epsilon \cdot \effect  \rightarrow \effect }
-% &  \code{\epsilon^\star \rightarrow \epsilon}
-% &  
-%
-% 
-%\\ \hline
-%
-%
-%\code{ \effect \cdot  \epsilon \rightarrow \effect}
-%& \code{( \epsilon \vee \effect)^\star \rightarrow \effect^\star}
-%& \code{ }
-%
-% 
-% 
-%\\ \hline
-%
-%
-% 
-%
-%\\ \hline
-%
-%\end{tabular}
-%\vspace{0mm}
-%\end{table}
+We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A10), suggested by \cite{DBLP:journals/jacm/Salomaa66}, 
+which was designed for regular languages. We develop axioms (A11) 
+to (A16) to further accommodate effects constructed by 
+\code{||} and \code{\mysharp}.
 
@@
   \label{table:normalization}
-\setlength{\tabcolsep}{8pt}
+  \setlength{\tabcolsep}{10pt}
   \renewcommand{\arraystretch}{1.2}
@@
 
-\begin{minipage}[t]{0.45\textwidth}
+  \begin{minipage}[t]{0.36\textwidth}
   \begin{tabular}{||l|l}
@@
   (A1)  &
-\code{\effect_1 \vee (\effect_2 \vee \effect_3) \rightarrow   (\effect_1 \vee \effect_2) \vee \effect_3 }\\
+  \code{\es_1 \vee (\es_2 \vee \es_3) \rightarrow   (\es_1 \vee \es_2) \vee \es_3 }\\
   \hline
   (A2)  &
-\code{\effect_1 \cdot (\effect_2 \cdot \effect_3)\rightarrow     (\effect_1 \cdot \effect_2) \cdot \effect_3 }\\
+  \code{\es_1 \cdot (\es_2 \cdot \es_3)\rightarrow     (\es_1 \cdot \es_2) \cdot \es_3 }\\
   \hline
   (A3)  &
-\code{\effect_1 \vee \effect_2 \rightarrow   \effect_2 \vee \effect_1 }\\
+  \code{\es \cdot (\es_1 \vee \es_2)  \rightarrow \es \cdot \es_1  \vee \es \cdot \es_2 }\\
   \hline
   (A4)  &
-\code{\effect \cdot (\effect_1 \vee \effect_2)  \rightarrow \effect \cdot \effect_1  \vee \effect \cdot \effect_2 }\\
+   \code{(\es_1 \vee \es_2)\cdot \es   \rightarrow \es_1 \cdot \es   \vee  \es_2 \cdot \es}\\
   \hline
   (A5)  &
- \code{(\effect_1 \vee \effect_2)\cdot \effect   \rightarrow \effect_1 \cdot \effect   \vee  \effect_2 \cdot \effect}\\
+   \code{\es \vee \es   \rightarrow \es}\\
   \hline
   (A6)  &
- \code{\effect \vee \effect   \rightarrow \effect}\\
+   \code{  \es \cdot \epsilon   \rightarrow \es}\\
   \hline
   (A7)  &
- \code{  \effect \cdot \epsilon   \rightarrow \effect}\\
+   \code{  \es \cdot  \bot \rightarrow \bot}\\
   \hline
   (A8)  &
- \code{  \effect \cdot  \bot \rightarrow \bot}\\
+  \code{\es \vee \bot   \rightarrow \es}\\
+  \hline
+
+  \end{tabular}
+    \end{minipage}
+
+    &
+  \footnotesize
+    \begin{minipage}[t]{0.6\textwidth}
+  \begin{tabular}{||l|l|}
   \hline
   (A9)  &
- \code{\effect \vee \bot   \rightarrow \effect}\\
+  \code{\epsilon \vee (\es \cdot \es^\star)   \rightarrow  \es^\star}\\
   \hline
   (A10)  &
- \code{\epsilon \vee (\effect \cdot \effect^\star)   \rightarrow  \effect^\star}\\
+  \code{(\epsilon \vee \es)^\star   \rightarrow  \es^\star}\\
   \hline
-(A11)  &
- \code{(\epsilon \vee \effect)^\star   \rightarrow  \effect^\star}\\
+  (A11)\code{^\heartsuit}  &
+  \code{ \es\ ||\  \epsilon \rightarrow \es}\\
   \hline
-
-\end{tabular}
-  \end{minipage}
-
-  &
-\footnotesize
-  \begin{minipage}[t]{0.45\textwidth}
-\begin{tabular}{||l|l|}
+  (A12)\code{^\heartsuit}  &
+  \code{ \es\ ||\ \bot  \rightarrow \bot }\\
   \hline
-(A12)  &
-\code{\bot^\omega  \rightarrow \bot }\\
-\hline
-(A13)  &
-\code{\effect^\omega \cdot \effect_1 \rightarrow \effect^\omega }\\
-\hline
-(A14)  &
-\code{\epsilon^\omega \rightarrow \bot }\\
-\hline
-(A15)  &
-\code{ \effect\ ||\  \epsilon \rightarrow \effect}\\
-\hline
-(A16)  &
-\code{ \effect\ ||\ \bot  \rightarrow \bot }\\
-\hline
-(A17)  &
- \code{(I\mysharp  t) \cdot \effect_1\ ||\ J \cdot\effect_2 \rightarrow ((I  {\cup} J) \mysharp  t) \cdot (\effect_1 || \effect_2)}\\
-\hline
-(A18)  &
-\code{\pi : (\effect \mysharp  t_1 ) \mysharp  t_2 \rightarrow \pi  \wedge (t_1 {=} t_2) : \effect \mysharp  t_1 }\\
-\hline
-(A19)  &
- \code{ \epsilon \mysharp  t \rightarrow  \epsilon}\\
-\hline
-(A20)  &
+  (A13)\code{^\heartsuit}  &
   \code{\bot \mysharp  t \rightarrow  \bot }\\
   \hline
-(A21)  &
- \code{{{False}} : \effect \rightarrow {{False}} : \bot }\\
+  (A14)\code{^\heartsuit}  &
+  \code{\pi \wedge (\es \mysharp  t_1 ) \mysharp  t_2 
+  \rightarrow \pi  \wedge (t_1 {=} t_2) \wedge \es \mysharp  t_1 }\\
   \hline
-(A22)  &
- \code{{\pi} : \bot  \rightarrow {{False}} : \bot }\\
+  (A15)\code{^\heartsuit}  &
+   \code{(\epsilon \mysharp  t_1) ||(\epsilon \mysharp  t_2) \rightarrow 
+   (t_1 {\geq}t_2 \wedge\epsilon\mysharp t_1) \vee   (t_1 {<}t_2 \wedge \epsilon\mysharp t_2) }\\
   \hline
- %\code{\effect \vee \effect \rightarrow \effect} 
-%  &\code{\bot  \cdot \effect \rightarrow \bot  }  
-%  &
+  (A16)\code{^\heartsuit}  &
+   \code{{{False}} \wedge \es = {\pi} \wedge \bot  \rightarrow {{False}} \wedge \bot }\\
+  \hline
 
@@
 %HipHop.js
-We define the syntax and semantics of the novel \timedEffects, to capture reactive program behaviors and  temporal properties.
-We demonstrate how to give a rather axiomatic semantics to \code{\timedL} by timed-trace processing functions.
-We use this semantic model to enable  a Hoare-style forward verifier,  which computes the program effects constructively.
-We present an effects inclusion checker (the TRS) to prove the annotated temporal properties efficiently. We prototype the verification system and show its feasibility.
-To the best of our knowledge, our work is the first that formulates semantics of a mixed Sync-Async concurrency paradigm; and that automates modular timed verification for reactive programs using an expressive effects logic.
+We define the syntax and semantics of the novel \timedEffects, 
+to capture real-time systems' behaviors and  temporal properties. 
+We demonstrate how to give a rather axiomatic semantics to 
+\code{\timedL} by timed-trace processing functions. We use 
+this semantic model to enable  a Hoare-style forward verifier,  
+which computes the program effects constructively.
+We present an effects inclusion checker (the TRS) to prove the 
+annotated temporal properties efficiently. We prototype the 
+verification system and show its feasibility.
+To the best of our knowledge, our work is the first 
+automates modular timed verification for real-time systems 
+using an expressive effects logic.
 

### 2022-04-15 paper/tv.tex
no copilation error

@@
 \subsection{Implementation}
-To show the feasibility of our approach, we have prototyped our automated verification system 
-using OCaml \emph{(A demo page  and source code are available from \cite{CODE})}. 
-The proof obligations generated by the verifier are discharged using constraint solver Z3 \citep{DBLP:conf/tacas/MouraB08}. 
-We prove termination and soundness of the TRS. We validate the front-end forward verifier for conformance, against two implementations: the Columbia Esterel Compiler (CEC) 
-\cite{CEC} and Hiphop.js \cite{HH_im}.
-
-CEC is an open-source compiler designed for research in both hardware and software generation from the Esterel synchronous language to C or Verilog circuit description.
-It currently supports a subset of Esterel V5, and provides pure Esterel programs for testing.
-Hiphop.js's implementation facilitates the design of complex web applications by smoothly integrating Esterel and JavaScript, and provides a bench of programs for testing purposes.
-
-%The core implementation is less than 3500 LOC, roughly, 1{+} LOC for the verifier, and 2{+} LOC for the TRS. We prove the soundness of the TRS.
-
-%We summarize the underlying reasons which lead to the improvement: (1)When the transition states of the models are small, the average execution time spent by the T.r.s is even less than the automata construction time, which means it is not necessary to construct the automata when a TRS solves it faster; (2)When the total states become larger, on average, the TRS outperforms automata-based algorithms, due to the significantly reduced search branches provided by the normalization lemmas; and (3)For the invalid cases, the TRS disproves them earlier without constructing the whole automata.
-
-%\subsubsection{Experimental Setup}~\\
-
-   %   \vspace{-2mm}
+To show the feasibility of our approach, we have prototyped 
+our automated verification system 
+using OCaml. The proof obligations generated by the verifier 
+are discharged using constraint solver Z3 
+\citep{DBLP:conf/tacas/MouraB08}. 
+We prove termination and soundness of the TRS. We validate 
+the front-end forward verifier for conformance.
 

### 2022-04-15 code/src/program/fischer.c

@@ -1,10 +1,10 @@
 x := -1; 
 ct := 0;
+pc := -1;
 
 void process (int i)
-/* req: TRUE /\ (_^*) 
-   ens: (t0<=d1/\t1=d2) /\ ([x=-1]? . (Update(i)#t0) . (emp#t1) . (([x=i] . Critical(i) . Exit(i) ) + [(~(x=i))]) ^*) */
-
+/* req: (d1>0/\d2>d1) /\ (_^*) 
+   ens: (t0<=d1/\t1=d2) /\ (([x=-1]? . (Update(i){x := i}#t0) . (emp#t1) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
 {
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);
@@ -19,7 +19,7 @@ void process (int i)
 }
 
 void main () 
-/* req: TRUE /\ emp 
-   ens: TRUE /\ (_^*)  */
+/* req: (d1>0/\d2>d1) /\ emp 
+   ens: TRUE /\ (([pc=-1] + [pc=x])^*)  */
 { process(0) || process(1); }
 

### 2022-04-15 code/src/program/fischer.c
m

@@ -18,8 +18,14 @@ void process (int i)
   }
 }
 
+void process1 (int i)
+/* req: (d1>0/\d2>d1) /\ (_^*) 
+   ens: (t0<=d1/\t1=d2) /\ [x=-1]? . Update(i){x := i} */
+{ 1
+}
+
 void main () 
 /* req: (d1>0/\d2>d1) /\ emp 
    ens: TRUE /\ (([pc=-1] + [pc=x])^*)  */
-{ process(0) || process(1); }
+{ process1(0) || process1(1); }
 

### 2022-04-15 code/src/program/fischer.c
m

@@ -4,7 +4,7 @@ pc := -1;
 
 void process (int i)
 /* req: (d1>0/\d2>d1) /\ (_^*) 
-   ens: (t0<=d1/\t1=d2) /\ (([x=-1]? . (Update(i){x := i}#t0) . (emp#t1) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
+   ens: (t1<=d1/\t2=d2) /\ (([x=-1]? . (Update(i){x := i}#t1) . (emp#t2) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
 {
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);
@@ -20,14 +20,14 @@ void process (int i)
 
 void process1 (int i)
 /* req: (d1>0/\d2>d1) /\ (_^*) 
-   ens: (t1>0/\t0>0/\t0<d1/\t1=d2) /\ [x=-1]? . 
-   (Update(i){x := i}#t0). (emp#t1) . 
-   (([x=i] . Critical(i){pc:=i}  ) + [(~(x=i))])*/
+   ens: (t2>0/\t1>0/\t1=d1/\t2=d2) /\ ([x=-1]? . 
+   (Update(i){x := i}#t1). (emp#t2) . 
+   (([x=i] . Critical(i){pc:=i} .Exit(i){x := -1; pc:= -1} ) + [(~(x=i))]) )*/
 { 1
 }
 
 void main () 
 /* req: (d1>0/\d2>d1) /\ emp 
-   ens: TRUE /\ (([pc=-1] + [pc=x])^*)  */
+   ens: TRUE /\ (([pc=-1] + [pc=(x)])^*)  */
 { process1(0) || process1(1); }
 

### 2022-04-15 paper/tv.tex
m

@@
 numbers=left,   
-xleftmargin=1.5em, 
+xleftmargin=1em, 
     numberstyle=\tiny\color{mGray},
@@
 \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf., \tabref{tab:reoccur}. 
-
-\subsection{The Fischer's mutual exclusion algorithm}
-
-\begin{wrapfigure}{L}{0.53\columnwidth}
-  \vspace{-1mm}
+\\
+
+\subsection{Verifying the Fischer’s Mutual Exclusion Protocol}
+
+\begin{wrapfigure}{L}{0.51\columnwidth}
+  \vspace{-5mm}
 \begin{lstlisting}
 var x := -1; 
-var ct := 0;
+var ct:= -1;
+
 void proc (int i) {
@@
   if (x=i) {
-    event["Critical"(i)]{ct:=ct+1};
-    event["Exit"(i)]{ct:=ct-1; x:=-1};
+    event["Critical"(i)]{ct:=i};
+    event["Exit"(i)]{ct:=-1; x:=-1};
     proc (i);
@@
     proc (i);}}
-void main () { 
-  proc(0) || proc(1) || proc(2); }
+
+void main () 
+/*req: d1<d2/\emp
+  ens: true /\ (([ct=-1]\/[ct=x])^*) */ 
+{ proc(0) || proc(1) || proc(2); }
 \end{lstlisting}  
-  \vspace{-1mm}
+  %\vspace{-1mm}
   \caption{Fischer's mutual exclusion algorithm.}\label{fig:overview_ficher}
-     \vspace{-1mm}
+    % \vspace{-2mm}
 \end{wrapfigure}
 
-The following models Fischer's mutual exclusion algorithm. 
-where d1 and d2 are two integer constants with d1 < d2; 
-x and ct are global variables. The protocol is modeled as 
-process Protocol, which is the parallel composition of three 
+\figref{fig:overview_ficher} presents the classical 
+Fischer's mutual exclusion algorithm. 
+where \codem{d1} and \codem{d2} are two integer constants
+ with \codem{d1<d2}; 
+\code{x} and \code{ct} are global variables. The protocol is 
+modeled as 
+process protocol, which is the parallel composition of three 
 processes. Each of the three processes attempts to enter 
-the critical section when x is -1, i.e. no other process is 
-currently attempting. Once the process is active, it sets x 
-to its identity i within d1 time units (captured by deadline[d1]). 
-Then it idles for d2 time units (captured by Wait[d2]) and then 
-checks whether x is still i. If so, it enters the critical 
+the critical section when \code{x} is \code{-1}, i.e. no 
+other process is 
+currently attempting. Once the process is active, it sets \codeme{}{x} 
+to its identity \codem{i} within \codem{d1} time units (captured by \codem{deadline(..., d1}). 
+Then it idles for \codem{d2} time units (captured by \codem{delay(d2)}) and then 
+checks whether \codem{x} is still \codem{i}. If so, 
+it enters the critical 
 section and leaves later. Otherwise, it restarts from the 
@@
 
-We show that our method is able to prove the algorithm in the 
-section of implementation.  prove the algorithm in the 
-section of implementation.
+We show the specification of \codem{main} using \timedEffects, which
+restricts the relation between \codem{d1} and \codem{d2}. When 
+\codem{d1<d2} is provided, it ensures a repeated trace where the value of 
+\codem{ct} is either \codem{-1} or equals to \codem{x}. The specification
+implies that this implementation is indeed mutual exclusive. 
+Our prototype system is able to soundly check such time-critical 
+algorithms. \autoref{sec:Evaluation} presents the details about the implementation and evaluation.
 

### 2022-04-15 code/src/program/fischer.c

@@ -29,5 +29,5 @@ void process1 (int i)
 void main () 
 /* req: (d1>0/\d2>d1) /\ emp 
    ens: TRUE /\ (([pc=-1] + [pc=(x)])^*)  */
-{ process1(0) || process1(1); }
+{ process1(0) || process1(1) || process1(2); }
 

### 2022-04-15 paper/tv.tex
m

@@
 void addNSugar (int n) 
-/*req: true /\ _^*
-  ens: d>=n /\ Sugar#d */
+/*req: true/\ _^*
+  ens: d>=n/\ Sugar#d */
 { if (n == 0) { 
@@
      % \vspace{0mm}
-\caption{\label{tab:rewriting_tree_send} The inclusion proving example. }
+\caption{\label{tab:rewriting_tree_send} The inclusion proving example. 
+\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}
 
@@
 \textbf{Normalization.}
-We present a set of normalization rules to soundly transfer the timed effects into a normal form, in particular after getting their derivatives. 
+We present some normalization rules to soundly transfer the timed effects into a normal form, in particular after getting their derivatives. 
 Before getting into the above inference rules, we assume that the effects formulae are tailored accordingly based on the axioms shown in
 \tabref{table:normalization}
-We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A10), suggested by \cite{DBLP:journals/jacm/Salomaa66}, 
+We built the axiom system on top of an axiom system \code{F_1}, from (A1) to (A10), suggested by \cite{DBLP:journals/jacm/Salomaa66}, 
 which was designed for regular languages. We develop axioms (A11) 
@@
 \begin{table}[ht]
-  \caption{Normalization Axioms for \timedEffects.}
+  \caption{Some Normalization Axioms for \timedEffects.}
   \label{table:normalization}
@@
 
-\subsection{Implementation}
 To show the feasibility of our approach, we have prototyped 
@@
 We prove termination and soundness of the TRS. We validate 
-the front-end forward verifier for conformance.
-
-Based on these two benchmarks, we validate the verifier using 155  programs, varying from 15 lines to 300 lines.
-We manually annotate temporal specifications in our timed effects, including both succeeded and failed instances (roughly with the a 1:1 ratio).
-Out of the whole test suite, 101 were from the CEC benchmark, 54 were from the Hiphop.js benchmark.
-Since async-await was inherited from JavaScript features, it only presents in the 54 hiphop.js programs.
+the front-end forward verifier against the state-of-the-art PAT 
+\cite{DBLP:conf/cav/SunLDP09} model checker for conformance. 
+Next, we show experimental results and case studies to evaluate the 
+capability of our proposals.
+
+\subsection{Experimental Results}
+\label{subsec:Experimental_Results}
+
 We conduct experiments on a MacBook Pro with a 2.6 GHz Intel Core i7 processor. Given our benchmark, the running time varying from 0 to 500 ms.
@@
 
-Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.
+%Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.
 
@@
 %(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
-Termination of TRS is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, i.e., the rule \code{[REOCCUR]}.
+Termination of TRS is guaranteed because the set of derivatives 
+to be considered is finite, and possible cycles are detected 
+using \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, 
+i.e., the rule $\codeme{[REOCCUR]}$. 
 % Check out this following example:
@@
 \caption{\label{tab:reoccur} The reoccurrence proving example. 
-\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}
+\code{(I)} The main rewriting proof tree; \code{(II)} Right hand side sub-tree of the rewriting process.}
 
@@
 
-\code{I:}\
+\code{(I):}\
 {
@@
 
-\infer[dashed]1[{\textcircled{4}\siderule{[PROVE]}}]{
+\infer[dashed]1[{\textcircled{4}\siderule{\codeme{[PROVE]}}}]{
   \code{
-    \textcolor {darkred}{True} : \epsilon \CONTAIN
-    \textcolor {darkred}{True} : \epsilon
-  }
-}
-
-\infer[dashed]1[{\textcircled{3}\siderule{[Normalisation]}}]{
+    \textcolor {darkred}{True} \wedge \epsilon \CONTAIN
+    \textcolor {darkred}{True} \wedge \epsilon
+  }
+}
+
+\infer[dashed]1[{\textcircled{3}\siderule{\codeme{[Normalisation]}}}]{
   \code{
-    \textcolor {darkred}{True} : \cancel{\{B\}} \CONTAIN
-    \textcolor {darkred}{True} : \cancel{ \epsilon \cdot \{B\}}
-  }
-}
-
-\infer[dashed]1[{\textcircled{2}\siderule{[UNFOLD]}}]{
+    \textcolor {darkred}{True} \wedge \cancel{\{B\}} \CONTAIN
+    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot \{B\}}
+  }
+}
+
+\infer[dashed]1[{\textcircled{2}\siderule{\codeme{[UNFOLD]}}}]{
   \code{
-    \textcolor {darkred}{True} : \{B\} \CONTAIN
-    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
-  }
-}
-\hypo{\code{II}}
+    \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
+    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
+  }
+}
+\hypo{(\code{II})}
 
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \mysharp  t_L  \cdot  \{B\}
+    \textcolor {darkred}{t_L{<}3}  \wedge  \{A\}^\star \mysharp  t_L  \cdot  \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \mysharp  t_R  \cdot  \{B\}
-  }
-}
-
-\infer[dashed]2[{\textcircled{1}\siderule{[Disj\text{-}L]}}]{
+    \textcolor {darkred}{t_R{<}4}  \wedge  \{A\}^\star \mysharp  t_R  \cdot  \{B\}
+  }
+}
+
+\infer[dashed]2[{\textcircled{1}\siderule{\codeme{[OR\text{-}LHS]}}}]{
   \code{
-    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
-    \vee \textcolor {darkred}{True} : \{B\} \CONTAIN
-    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
+    \vee \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
+    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
   }
@@
 \hline \\
-\code{II:} 
+\code{(II):} \qquad 
 {\begin{prooftree}
@@
 %       \wedge  t_L^2{=}t_R^2
-    } :
+    } \wedge 
      \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} :
+    \textcolor {darkred}{t_R{<}4} \wedge 
      \{A\}^\star \mysharp  t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
@@
 
-\infer[dashed]1[{\textcircled{7}\siderule{[REOCCUR]}}]{
+\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[REOCCUR]}}}]{
   \code{
@@
        t_L^1{=}t_R^1
-    } :
+    } \wedge 
      \cancel{\{A\} \mysharp  t_L^1}  \cdot  \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} :
+    \textcolor {darkred}{t_R{<}4} \wedge 
      \cancel{\{A\} \mysharp  t_R^1}  \cdot  \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
@@
 
-\infer[dashed]1[{\textcircled{6}\siderule{[UNFOLD]}}]{
+\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}}]{
   \code{
-    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} :
+    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} \wedge 
      ( \{A\} \mysharp  t_L^1  \cdot  \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} :
+    \textcolor {darkred}{t_R{<}4} \wedge 
      ( \{A\} \mysharp  t_R^1  \cdot  \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
@@
 
-\infer[dashed]1[{\textcircled{5}\siderule{[SPLIT]}}]{
+\infer[dashed]1[{\textcircled{5}\siderule{\codeme{[SPLIT]}}}]{
   \code{
-    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}  \quad \textcolor{darklavender}{(\ddagger)}
+    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}  
+    \quad \textcolor{darklavender}{(\ddagger)}
   }
@@
 }
+
+\subsection{Beyond Regular, Context-Free and Context-Sensitive}
+%As explained in \secref{subsec:Specification_language}, t
+The paradigmatic non-regular linear language: 
+\code{t{>} 0 \wedge \anyevent{A}\mysharp{t}\cdot\anyevent{B}\mysharp{t}}, 
+can be naturally expressed by the depended effects. 
+Besides, the effects can also express grammars such as \code{t{>} 0 
+\wedge \anyevent{A}\mysharp{t}\cdot\anyevent{B}\mysharp{t}
+\cdot\anyevent{C}\mysharp{t}}, or 
+\code{n{>} 0 \wedge m{>} 0 \wedge  \anyevent{A}\mysharp{n}
+\cdot\anyevent{B}\mysharp{m}\cdot\anyevent{C}\mysharp{n}}, 
+which are beyond context-free grammar.
+%(by a contradiction proof using Pumping lemma) 
+%and categorized as context-sensitive grammar. 
+Those examples show that the traces which cannot be recognized 
+even by push-down automata (PDA) can be represented by our effects. 
+%As regular grammar and context-free grammar are equivalent to finite state automata (FSA) and  respectively, our effects can not be fully translated into either FSA or PDA.
+However, such specifications are significant, suppose we 
+have a traffic light control system, we could have a 
+specifications \code{n{>} 0 \wedge m{>} 0 \wedge  
+(\anyevent{Red}\mysharp{n}\cdot\anyevent{Yellow}\mysharp{m}\cdot
+\anyevent{Green}\mysharp{n})^\star}, which specifies that  
+(i) all the colors will occur at each life circle; and 
+(ii) the duration of the green light and the red light is 
+always the same. Moreover, these effects can not be translated 
+into linear bounded automata (LBA) either, which equivalents to 
+context-sensitive grammar, as LBA are only capable of expressing 
+finite traces.
 
@@
   \input{rules/rule1}
-  - It is easy to verify that antecedent of goal entailments in the rule \codeme{[Bot\text{-}LHS]} is unsatisfiable. Therefore, these entailments are evidently valid.\\
-  - It is easy to verify that consequent of goal entailments in the rule \codeme{[Bot\text{-}RHS]} is unsatisfiable. Therefore, these entailments are evidently invalid.\\
+  - It is easy to verify that antecedent of goal entailments in the rule $\codeme{[Bot\text{-}LHS]}$ is unsatisfiable. Therefore, these entailments are evidently valid.\\
+  - It is easy to verify that consequent of goal entailments in the rule $\codeme{[Bot\text{-}RHS]}$ is unsatisfiable. Therefore, these entailments are evidently invalid.\\
 
@@
   \input{rules/rule2}
-  - It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
+  - It's straightforward to prove soundness of the rule $\codeme{[DISPROVE]}$, Given that \codeme{\es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
 Therefore, these entailments are evidently invalid.\\
@@
   \input{rules/rule3}
-  - To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}.
-Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \es_1}}.
-When the \code{\m{fst}} set of \code{\es_1} is empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon}; and \code{\es_2} is nullable.
-For both cases, the inclusion is valid.
-
-  - To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}.
-Given the promises that  \codeme{\pi_1 : \es_1 \CONTAIN \pi_3 : \es_3}, we get \codeme{d,  \varphi \models {\pi_3 : \es_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \es_3 \CONTAIN  \pi_4 : \es_4}, we get \codeme{d,  \varphi \models {\pi_4 : \es_4}}; Given the promises that  \codeme{\pi_4 : \es_4 \CONTAIN \pi_2 : \es_2}, we get \codeme{d,  \varphi \models {\pi_2 : \es_2}}.
-Therefore,  the inclusion is valid.
+  - To prove soundness of the rule $\codeme{[PROVE]}$, we consider an arbitrary model, \codeme{d, s, \varphi} such that:  
+  \codeme{d,  s, \varphi \models  {\pi_1 \wedge \es_1}}. Given the side 
+  conditions from the promises, we get \codeme{d,  s, \varphi \models 
+  {\pi_2 \wedge \es_2}}. When the \code{\m{fst}} set of \code{\es_1} is 
+  empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon} and 
+  \code{\pi_2 \wedge \es_2} is nullable. For both cases, the inclusion 
+  is valid.
+
+  - To prove soundness of the rule $\codeme{[REOCCUR]}$, we consider 
+  an arbitrary model, \codeme{d, s, \varphi} such that:  \codeme{d,  s, 
+  \varphi \models  {\pi_1 \wedge \es_1}}. Given the promises that  
+  \codeme{\pi_1 \wedge \es_1 \CONTAIN \pi_3 \wedge \es_3}, we get 
+  \codeme{d,  s, \varphi \models {\pi_3 \wedge \es_3}}; Given the 
+  promise that there exists a hypothesis \codeme{\pi_3 \wedge \es_3 
+  \CONTAIN  \pi_4 \wedge \es_4}, we get \codeme{d, s, \varphi \models 
+  {\pi_4 \wedge \es_4}}; Given the promises that  
+  \codeme{\pi_4 \wedge \es_4 \CONTAIN \pi_2 \wedge \es_2}, we get 
+  \codeme{d, s,  \varphi \models {\pi_2 \wedge \es_2}}. Therefore,  
+  the inclusion is valid. 
   \\
@@
 
-  - To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \es_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \es_2}}.
-For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and
-  \codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \es_2 \rrbracket}.
-
-  Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bot }, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};
-
-  Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}.
-
-  By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\es_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}, the conclusion is valid. 
+  - To prove soundness of the rule $\codeme{[UNFOLD]}$, we consider an 
+  arbitrary model, \codeme{d_1, s_1,  \varphi_1} and \codeme{d_2, s_2,
+   \varphi_2}  such that:  \codeme{d_1, s_1,  \varphi_1 \models {\pi_1 \wedge
+    \es_1}} and \codeme{d_2, s_2,  \varphi_2 \models  {\pi_2 \wedge \es_2}}. 
+    For an arbitrary event \codeme{h}, let \codeme{d_1^\prime, s_1^\prime,
+     {\varphi_1}^\prime \models \codeme{h}^{\text{-}1}\llbracket  \pi_1\wedge \es_1 \rrbracket}; 
+     and 
+  \codeme{d_2^\prime, s_2^\prime, {\varphi_2}^\prime \models 
+  \codeme{h}^{\text{-}1}\llbracket \pi_2 \wedge \es_2 \rrbracket}.
+
+  Case 1), \codeme{\codeme{h} \notin F}, 
+  \codeme{d_1^\prime, {\varphi_1}^\prime \models \bot }, 
+  thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime 
+  \models D^{\pi_2}_{\codeme{h}}( \es_2)};
+
+  Case 2), \codeme{\codeme{h} \in F}, given that inclusions 
+  in the rule's premise is valid, then \codeme{d_1^\prime, s_1^\prime, 
+  {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{h}}( \es_2)}.
+
+  By \defref{Inclusion}, since for all \codeme{h}, 
+  \codeme{D^{\pi_1}_{\codeme{h}} (\es_1) \CONTAIN   
+   D^{\pi_2}_{\codeme{h}}( \es_2)}, the conclusion is valid. 
   \\
@@
   \end{enumerate}
-  All the inference rules used in the TRS are sound, therefore the TRS is sound.
+  All the inference rules used in the TRS are sound, therefore the
+   TRS is sound.
   \end{proof}

### 2022-04-15 paper/tv.tex
m

@@
 %\copyrightyear{2018}           %% If different from \acmYear
+\usepackage{pifont}% http://ctan.org/pkg/pifont
 
 \usepackage{tikz}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
+
 \usepackage{xcolor}
@@
 
+\autoref{tab:Experimental} presents the evaluation results of a microbenchmark. % summary of a lightweight . 
+In this experiment, we select 16 \timedL\ programs, and  annotate temporal specifications
+with a 1:1 ratio for succeeded/failed cases. 
+It records: 
+the index of the program, \textbf{No.};
+lines of code, \textbf{LOC}; 
+effects inference time, \textbf{Infer(ms)}; 
+number of valid properties, \textbf{$\mysharp$Prop(\cmark)}; 
+average proving time for the valid properties, \textbf{Avg\text{-}Prove(ms)};
+number of invalid properties, \textbf{$\mysharp$Prop(\xmark)}; and 
+average disproving time for the invalid properties, \textbf{Avg\text{-}Dis(ms)}. 
+Times are counted using milliseconds, and the experiment is done on 
+a MacBook Pro with a 2.6 GHz 6-Core Intel Core i7 processor.
+
+\begin{table}[!ht]
+\caption{\label{tab:Experimental} Experimental Results. }
+%\vspace{-1mm}
+\centering
+\renewcommand{\arraystretch}{1}
+\begin{tabular} {c|c|c|c|c |c|c}
+\hline
+\textbf{No.} & \textbf{LOC} & \textbf{Infer(ms)} & \textbf{$\mysharp$Prop(\cmark)}   
+& \textbf{Avg\text{-}Prove(ms)} & \textbf{$\mysharp$Prop(\xmark)}   & \textbf{Avg\text{-}Dis(ms)} \\ \hline\hline
+1    &    18    & 0.037&  5     &  0.7634    & 5   &   0.0116   \\ \hline
+2    &    33    & 0.145&  5     &  1.3074    & 5   &   0.045    \\ \hline
+3    &    55    & 0.34 &  5     &  6.0766    & 5   &   1.1682   \\ \hline
+4    &    84    & 0.098&  5     &  3.0678    & 5   &   0.1058   \\ \hline
+5    &    110   & 0.191&  7     &  1.7544    & 7   &   0.5031   \\ \hline
+6    &    124   & 0.323&  7     &  4.0114    & 7   &   0.3957   \\ \hline
+7    &    138   & 0.321&  7     &  3.8399    & 7   &   0.4261   \\ \hline
+8    &    163   & 0.594&  7     &  6.1009    & 7   &   1.5019   \\ \hline
+9    &    178   & 0.941&  9     &  10.7758   & 9   &   0.5769   \\ \hline
+10   &    185   & 1.921&  9     &  13.9332   & 9   &   0.04422  \\ \hline
+11   &    202   & 3.434&  9     &  27.4447   & 9   &   0.0561   \\ \hline
+12   &    220   & 6.439&  9     &  59.2226   & 9   &   0.745   \\ \hline
+13   &    250   & 3.6  &  11    &  29.5766   & 11  &   0.0662  \\ \hline
+14   &    261   & 7.552&  11    &  64.2137   & 11  &   0.6121  \\ \hline     
+15   &    293   & 14.896& 11   &  115.9795   & 11  &   0.5462   \\ \hline
+16   &    304   &  30.889  &  11    & 237.2522    & 11  &  0.07164        \\ \hline            
+%\hline
+%\textbf{\quad \ \ Total}  & 2546    &  235   &  446.88   &   305.33   \\ \hline
+\end{tabular}
+%  \vspace{-1mm}
+\end{table}
+
 Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i.
@@
 %are unified as new constraint \code{t_L^1{=}t_R^1}.
-In step {\textcircled{7}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
+In step {\textcircled{8}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
 %one in
@@
   \code{
-    \textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True} \qquad
-    \epsilon \CONTAIN \epsilon
-  }
-}
-
-\infer[dashed]1[{\textcircled{4}\siderule{\codeme{[PROVE]}}}]{
+   % \textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True} \qquad
+   % \epsilon \CONTAIN \epsilon
+   {\textcircled{4}\siderule{\codeme{[PROVE]}}}
+  }
+}
+
+\infer[dashed]1[]{
   \code{
@@
   \code{
-    \textcolor {darkred}{True} \wedge \cancel{\{B\}} \CONTAIN
-    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot \{B\}}
+    \textcolor {darkred}{True} \wedge \cancel{  B  } \CONTAIN
+    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot   B  }
   }
@@
   \code{
-    \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
+    \textcolor {darkred}{True} \wedge   B   \CONTAIN
+    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B  
   }
@@
   \code{
-    \textcolor {darkred}{t_L{<}3}  \wedge  \{A\}^\star \mysharp  t_L  \cdot  \{B\}
+    \textcolor {darkred}{t_L{<}3}  \wedge    A  ^\star \mysharp  t_L  \cdot    B  
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4}  \wedge  \{A\}^\star \mysharp  t_R  \cdot  \{B\}
+    \textcolor {darkred}{t_R{<}4}  \wedge    A  ^\star \mysharp  t_R  \cdot    B  
   }
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
-    \vee \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} \wedge   A  ^\star \mysharp  t_L \cdot   B  
+    \vee \textcolor {darkred}{True} \wedge   B   \CONTAIN
+    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B  
   }
@@
 \hline \\
-\code{(II):} \qquad 
+\code{(II):}
 {\begin{prooftree}
@@
     \textcolor {
-      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
+      darkred}{t_L{<}3 \wedge } \ \textcolor {
+        blue}{t_L^1{+}t_L^2{=}t_L \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
       \wedge t_L^2{=}t_R^2
@@
 %\qquad
-%     \{A\}^\star \cdot \{B\}
+%       A  ^\star \cdot   B  
 %    \CONTAIN
-%     \{A\}^\star \cdot \{B\}
-  }
-}
-
-\infer[dashed]1[{\siderule{}}]{
+%       A  ^\star \cdot   B  
+  }
+}
+
+\infer[dashed]1[{\textcircled{8}\siderule{\codeme{[REOCCUR]}}}]{
   \code{
     \textcolor {
-      darkred}{\cdots  \wedge  \cdots
-%      
-%      t_L^1{+}t_L^2{=}t_L{<}3  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge  t_L^1{=}t_R^1
-%       \wedge  t_L^2{=}t_R^2
-    } \wedge 
-     \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
+      darkred}{t_L{<}3} \wedge 
+       A  ^\star \mysharp  t_L^2 \cdot   B  
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} \wedge 
-     \{A\}^\star \mysharp  t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
-  }
-}
-
-\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[REOCCUR]}}}]{
+       A  ^\star \mysharp  t_R^2 \cdot   B   \quad  \textcolor{darklavender}{(\ddagger)}
+  }
+}
+
+\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[UNFOLD]}}} \textcolor{blue}{\code{\pi_u :  (t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1)}}]{
   \code{
-    \textcolor {
-      darkred}{
-%t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge       
-       t_L^1{=}t_R^1
-    } \wedge 
-     \cancel{\{A\} \mysharp  t_L^1}  \cdot  \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} \wedge 
+     \cancel{  A   \mysharp  t_L^1}  \cdot    A  ^\star \mysharp  t_L^2 \cdot   B  
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} \wedge 
-     \cancel{\{A\} \mysharp  t_R^1}  \cdot  \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
-  }
-}
-
-\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}}]{
+     \cancel{  A   \mysharp  t_R^1}  \cdot    A  ^\star \mysharp  t_R^2 \cdot   B  
+  }
+}
+
+\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}} \textcolor{blue}{\code{\pi_u :  (t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2)}}]{
   \code{
-    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} \wedge 
-     ( \{A\} \mysharp  t_L^1  \cdot  \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} \wedge 
+     (   A   \mysharp  t_L^1  \cdot    A  ^\star \mysharp  t_L^2) \cdot   B  
     \CONTAIN
     \textcolor {darkred}{t_R{<}4} \wedge 
-     ( \{A\} \mysharp  t_R^1  \cdot  \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
+     (   A   \mysharp  t_R^1  \cdot    A  ^\star \mysharp  t_R^2) \cdot   B  
   }
@@
   \code{
-    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
+    \textcolor {darkred}{t_L{<}3} \wedge   A  ^\star \mysharp  t_L \cdot   B  
     \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}  
+    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B    
     \quad \textcolor{darklavender}{(\ddagger)}

### 2022-04-15 paper/tv.tex
m

@@
 \newcommand{\anyevent}[1]{{\textcolor{darkred}
-{{\textbf{\footnotesize #1}}}}}
+{{\textbf{\small #1}}}}}
 \newcommand{\anynotevent}[1]{{\textcolor{darkred}
@@
 \begin{figure}[!ht]
-  \vspace{-3mm}
+  %\vspace{-3mm}
   \renewcommand{\arraystretch}{1.2}
@@
 \end{align*}
-  \vspace{-2mm}
+ % \vspace{-2mm}
 \caption{Semantics of \timedEffects.}
 \label{fig:Sementic}
-\vspace{-2mm}
+%\vspace{-2mm}
 \end{figure}
@@
 
+\vspace{1mm}
 $[FV\text{-}Seq]$ computes  \code{ \{  \Pi_1, \Theta_1\} } 
@@
 
+\vspace{1mm}
 The \code{[FV\text{-}If\text{-}Else]} computes an 
@@
 %{[FV\text{-}If\text{-}Else\text{-}Global]}}
+
+\vspace{1mm}
 Rule \code{[FV\text{-}Event]} simply constructs an new event and 
@@
 \end{gather*}}}
+
+\vspace{1mm}
 Rule \code{[FV\text{-}Timeout]} computes the effects from \code{e_1} and \code{e_2}
@@
 \end{gather*}}}
-Similar to the previous rule, \code{[FV\text{-}Ddl]} computes the effects 
+
+\vspace{1mm}
+Similar to \code{[FV\text{-}Timeout]}, \code{[FV\text{-}Ddl]} computes the effects 
 from \code{e} and adds an upper time-bound to the result. 
@@
   \end{gather*}}}
+
+  \vspace{1mm}
   Rule \code{[FV\text{-}Meth]} initializes the current effects state 
@@
 
+  \vspace{1mm}
 Rule \code{[FV\text{-}Call]} first checks whether the instantiated 
@@
 
+\vspace{2mm}
 Now, the inclusions are disjunction-free formulas. 
@@
 
+\vspace{2mm}
 \begin{definition}[Heads]\label{Heads}
@@
 
+\vspace{2mm}
 \begin{definition}[First]\label{First}
@@
 
+\vspace{2mm}
 \begin{definition}[Partial Derivative]\label{Derivative}
@@
 
+  \vspace{2mm}
 \subsection{Rewriting Rules}
@@
 Therefore, the inclusion is invalid.
-
-\vspace{-4mm}
 \input{rules/rule2}
@@
 
-\subsection{Beyond Regular, Context-Free and Context-Sensitive}
-%As explained in \secref{subsec:Specification_language}, t
+\subsection{Expressiveness.}
+%for (timed) linear temporal properties
+\label{subsec:Expressive}
+
+Classical LTL
+extended propositional logic with the temporal operators 
+\code{\mathcal{G} } (``globally") 
+and 
+ \code{\mathcal{F}} (``in the future"), which we also write
+ \code{\square} and \code{\Diamond}, respectively. 
+ %and introduced the concept of fairness. %, which ensures an infinite-paths semantics. 
+ LTL was subsequently extended to include the  \code{\mathcal{U} }
+  (``until") and  \code{\mathcal{X}} (``next time") 
+  operators. 
+  Our \timedEffects\ draws similarities to the metric temporal logic (MTL), 
+which is defined similarly to LTL, 
+  where a set of non-negative real number is added to temporal modal operators.   
+  As shown in 
+  \autoref{tab:ltl_effects}, we are able to recursively encode 
+  these basic MTL operators into \timedEffects, making it 
+   more intuitive and readable, mainly when nested operators 
+   occur.
+
+\begin{table}[h]
+  \vspace{-1mm}
+\caption{\label{tab:ltl_effects} Examples for converting MTL formulae 
+into Effects.  (\code{  \anyevent{A}  ,   \anyevent{B}  } represent 
+different time instants which contain signal \code{\anyevent{A}} and 
+\code{\anyevent{B}} to be present.)
+}
+\setlength{\tabcolsep}{12pt}
+\renewcommand{\arraystretch}{1.4}
+
+\begin{tabular}{llllllll}
+\multicolumn{2}{l|}{\code{ \square \anyevent{A} \equiv   \anyevent{A}    ^\star}} 
+&
+ \multicolumn{2}{l|}{\code{ \Diamond_{[m, n]} \anyevent{A}  \equiv m{\leq}t{\leq}n \wedge ({\_}^\star \mysharp t) \cdot   \anyevent{A}    } } 
+ &
+  \multicolumn{2}{l|}{\code{ \anyevent{A}\ \mathcal{U}\ \anyevent{B}  \equiv {  \anyevent{A}  }^\star \cdot   \anyevent{B}   }} 
+  &
+  \multicolumn{2}{l}{\code{ \anyevent{A} \rightarrow \anyevent{B}  \equiv {  \overline{\anyevent{A}}  } \vee   \anyevent{A}, \anyevent{B}   }}
+
+  \\
+\hline
+\multicolumn{2}{l|}{\code{ \mathcal{X} \anyevent{A} \equiv      \cdot   \anyevent{A}      }} 
+&
+ \multicolumn{2}{l|}{\code{ \square\Diamond \anyevent{A} \equiv   ( {    }^\star \cdot   \anyevent{A}   )^\star }} 
+ &
+  \multicolumn{2}{l|}{\code{ \Diamond\square \anyevent{A} \equiv {    }^\star  \cdot   \anyevent{A}  ^\star }} 
+  &
+  \multicolumn{2}{l}{\code{\square (\mathcal{X} \anyevent{A}) \equiv (     \cdot   \anyevent{A}  )^\star }}
+
+\end{tabular}
+  %\vspace{-6mm}
+  \vspace{-1mm}
+\end{table}
+
+%$A  B$ | $\{\overline{A}\} \vee \{A, B\}$ |  Implication
+%Furthermore, consider a property from \textit{Metric Temporal Logic (MTL)}: \code{\anyevent{A}\ \ \mathcal{U}_{[1, 3]}\ \anyevent{B}},
+
+Besides the high compatibility with standard first-order logic, \timedEffects\ makes the 
+temporal verification more scalable. It avoids 
+the %\textit{must-provided} 
+translation schemas for each LTL temporal operator to automata, 
+as comparing to how it has been done in the 
+prior work \cite{DBLP:conf/cav/JagadeesanPO95}.
+Furthermore, by putting the effects in the
+   precondition, our approach naturally composites \emph{past-time LTL} \cite{DBLP:conf/fmics/ReinbacherBHSK11} along the way.
+
+%to express that the server keeps sending messages to its clients 
+%until the work is done (within a time ), the corresponding synced effects can be \code{\anyevent{Send}^5 \cdot \anyevent{Done}} (as we provide the syntactical sugar of \code{\anyevent{Send}^5} to express 5 times concatenation of \code{\anyevent{Send}}).
+%These properties cannot be expressed using standard LTL, as they can only refer to the relative order of events, not to their relative distance in time, yet can be expressed by our effects logic.
+
+\paragraph{Beyond Regular, Context-Free and Context-Sensitive}
+
 The paradigmatic non-regular linear language: 
@@
 
-Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:conf/vmcai/SongC21,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12,prisacariu2010synchronous}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:conf/vmcai/SongC21,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
 

### 2022-04-16 paper/tv.tex
m

@@
 \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf., \tabref{tab:reoccur}.
-\\
 
@@
 \end{flalign*}}}
-
 The above captures behaviors of process \textbf{delay}[d]. 
@@
 }{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [tot_2]} 
-\\
+\end{flalign*}}}
+
+{{\small\begin{flalign*}
 \code{\frac{
@@
 \code{e_2} takes over control by a silent transition (rule \code{[tot_4]}).
+
 {{\small\begin{flalign*}
@@
 otherwise it idles until \code{b} becomes true.
+
 {{\small\begin{flalign*}
@@
 \centering
-\renewcommand{\arraystretch}{1}
-\begin{tabular} {c|c|c|c|c |c|c}
+\renewcommand{\arraystretch}{1.1}
+\begin{tabular} {c|c|c|c|c |c|c|c}
 \hline
 \textbf{No.} & \textbf{LOC} & \textbf{Infer(ms)} & \textbf{$\mysharp$Prop(\cmark)}   
-& \textbf{Avg\text{-}Prove(ms)} & \textbf{$\mysharp$Prop(\xmark)}   & \textbf{Avg\text{-}Dis(ms)} \\ \hline\hline
-1    &    18    & 0.037&  5     &  0.7634    & 5   &   0.0116   \\ \hline
-2    &    33    & 0.145&  5     &  1.3074    & 5   &   0.045    \\ \hline
-3    &    55    & 0.34 &  5     &  6.0766    & 5   &   1.1682   \\ \hline
-4    &    84    & 0.098&  5     &  3.0678    & 5   &   0.1058   \\ \hline
-5    &    110   & 0.191&  7     &  1.7544    & 7   &   0.5031   \\ \hline
-6    &    124   & 0.323&  7     &  4.0114    & 7   &   0.3957   \\ \hline
-7    &    138   & 0.321&  7     &  3.8399    & 7   &   0.4261   \\ \hline
-8    &    163   & 0.594&  7     &  6.1009    & 7   &   1.5019   \\ \hline
-9    &    178   & 0.941&  9     &  10.7758   & 9   &   0.5769   \\ \hline
-10   &    185   & 1.921&  9     &  13.9332   & 9   &   0.04422  \\ \hline
-11   &    202   & 3.434&  9     &  27.4447   & 9   &   0.0561   \\ \hline
-12   &    220   & 6.439&  9     &  59.2226   & 9   &   0.745   \\ \hline
-13   &    250   & 3.6  &  11    &  29.5766   & 11  &   0.0662  \\ \hline
-14   &    261   & 7.552&  11    &  64.2137   & 11  &   0.6121  \\ \hline     
-15   &    293   & 14.896& 11   &  115.9795   & 11  &   0.5462   \\ \hline
-16   &    304   &  30.889  &  11    & 237.2522    & 11  &  0.07164        \\ \hline            
+& \textbf{Avg\text{-}Prove(ms)} & \textbf{$\mysharp$Prop(\xmark)}   & \textbf{Avg\text{-}Dis(ms)} &\textbf{$\mysharp$AskZ3} \\ \hline\hline
+1    &    30    & 0.031  &  5     &  4.185   & 5   &  3.242  & 68 \\ \hline
+2    &    35    & 0.038  &  3     &  13.761  & 7   &  9.331  & 214 \\ \hline
+3    &    44    & 0.049  &  4     &  12.149  & 6   & 7.853   & 215 \\ \hline
+4    &    72    & 0.061  &  5     &  37.268 & 5   & 28.3054 & 617 \\ \hline
+5    &    95    & 0.105  &  7     &  6.139    & 7   &  5.238  & 186 \\ \hline
+6    &    108   & 0.16   &  7     &  43.667    & 7   &  17.178  & 818 \\ \hline
+7    &    106   & 0.142  &  7     &  18.776    & 7   &  8.432  & 346 \\ \hline
+8    &    144   & 0.141  &  7     &  22.238    & 7   &  10.051  & 426 \\ \hline
+9    &    155   & 0.308  &  9     &  194.666   & 9   &  56.344  & 4059 \\ \hline
+10   &    174   & 0.373  &  9     &  78.132   & 9   &   24.665  & 1740 \\ \hline
+11   &    196   & 0.557  &  9     &  111.100   & 9   &   31.262  & 2403 \\ \hline
+12   &    213   & 0.516  &  9     &  114.667   & 9   &  30.284   & 2484 \\ \hline
+13   &    265   & 1.895  &  11    & 616.619    & 11  &  302.975  & 9068 \\ \hline
+14   &    271   & 1.702  &  11    &  302.145   & 11  &  131.938  & 7779 \\ \hline     
+15   &    276   & 2.121 & 11     &  466.174  & 11  &   181.116  & 12239 \\ \hline
+16   &    314   & 1.654 &  11    & 1094.231   & 11  &  465.704  & 32620 \\ \hline            
 %\hline
@@
 \end{table}
-
-Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i.
-e., whose timing constants are not known yet), and hence cannot be used in early design phases; ii) verifying a system for a set of timing constants usually requires to enumerate all of them one by one if they are supposed to be integer-valued; in addition, Timed Automata cannot be used to verify a system for a set of timing constants that are to be taken in a real-valued dense interval.
-
-A term rewriting system is efficient because \emph{it only constructs automata as far as it needed}, which makes it more efficient when disproving incorrect specifications, as we can disprove it earlier without constructing the whole automata.
-In other words, the more incorrect specifications are, the more efficient our solver is.
 
@@
 
-\subsubsection{Prove it when Reoccur}~\\
+\subsubsection{Prove it when Reoccur}
 
@@
 
-\subsection{Expressiveness.}
+\subsubsection{Expressiveness.}
 %for (timed) linear temporal properties
@@
 
-\paragraph{Beyond Regular, Context-Free and Context-Sensitive}
+\subsubsection{Beyond Regular, Context-Free and Context-Sensitive}
 
@@
 
+Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i.
+e., whose timing constants are not known yet), and hence cannot be used in early design phases; ii) verifying a system for a set of timing constants usually requires to enumerate all of them one by one if they are supposed to be integer-valued; in addition, Timed Automata cannot be used to verify a system for a set of timing constants that are to be taken in a real-valued dense interval.
+
+A term rewriting system is efficient because \emph{it only constructs automata as far as it needed}, which makes it more efficient when disproving incorrect specifications, as we can disprove it earlier without constructing the whole automata.
+In other words, the more incorrect specifications are, the more efficient our solver is.
+
 %%

### 2022-04-16 code/src/program/test1.c

@@ -1,0 +1,30 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"]
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (t <21)/\ ((A.B) # t)
+ens: (t <21)/\ ((_.B) # t)
+ens: (t <21)/\ ((_._) # t)
+ens: (t <21)/\ ((A._) # t)
+ens: ((t1+t2) <21)/\ (A#t1). (B # t2)
+ens: (t <20)/\ ((A.B) # t)
+ens: (t <21)/\ ((~A.B) # t)
+ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
+ens: ((t1+t2) <21)/\ (A#t1). (~B # t2)
+ens: (t <21)/\ ((A.~B) # t)
+*/
+{
+    deadline (callee ()  , 20);
+}

### 2022-04-16 code/src/program/test10.c

@@ -1,0 +1,173 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (x=0/\f0>0/\f0<=20/\z=0)/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D)))))))))))))))) \/ (x=0/\f0>0/\f0<=20/\(~(z=0)))/\(((A . B)#f0) . (M . (N . (F . (G . (C . (D . (C . D)))))))) \/ ((~(x=0))/\y=0)/\(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) \/ ((~(x=0))/\(~(y=0))/\y=0)/\(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) \/ ((~(x=0))/\(~(y=0))/\(~(y=0)))/\(M . (N . (F . (G . (C . (D . (C . D)))))))
[…]

### 2022-04-16 code/src/program/test11.c

@@ -1,0 +1,196 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
[…]

### 2022-04-16 code/src/program/test12.c

@@ -1,0 +1,212 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
[…]

### 2022-04-16 code/src/program/test13.c

@@ -1,0 +1,264 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(_ . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(_ . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(_ . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void callee7 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(W. K)
+ens: TRUE/\(A )
+*/
+{
+    event["W"];
+    event["K"];
+}
+
+
+void callee8 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(_ . S)
+ens: TRUE/\(A )
+*/
+{
+    event["L"];
+    event["S"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
[…]

### 2022-04-16 code/src/program/test14.c

@@ -1,0 +1,270 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void callee7 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(W. K)
+ens: TRUE/\(A )
+*/
+{
+    event["W"];
+    event["K"];
+}
+
+
+void callee8 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(L . S)
+ens: TRUE/\(A )
+*/
+{
+    event["L"];
+    event["S"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+
[…]

### 2022-04-16 code/src/program/test15.c

@@ -1,0 +1,275 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void callee7 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(W. K)
+ens: TRUE/\(A )
+*/
+{
+    event["W"];
+    event["K"];
+}
+
+
+void callee8 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(L . S)
+ens: TRUE/\(A )
+*/
+{
+    event["L"];
+    event["S"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+
[…]

### 2022-04-16 code/src/program/test16.c

@@ -1,0 +1,314 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void callee7 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(W. K)
+ens: TRUE/\(A )
+*/
+{
+    event["W"];
+    event["K"];
+}
+
+
+void callee8 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(L . S)
+ens: TRUE/\(A )
+*/
+{
+    event["L"];
+    event["S"];
+}
+
+void callee9 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(W. K)
+ens: TRUE/\(A )
+*/
+{
+    event["W"];
+    event["K"];
+}
+
+
+void callee10 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(L . S)
+ens: TRUE/\(A )
+*/
+{
+    event["L"];
+    event["S"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+
[…]

### 2022-04-16 code/src/program/test2.c

@@ -1,0 +1,35 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . ((A . B)#f1))
+ens: (f0>0/\f0<=20/\f1>30)/\(((_ . B)#f0) . ((A . B)#f1))
+ens: (f0>0/\f0<=20/\f1>30)/\(((~B . B)#f0) . ((A . B)#f1))
+ens: (f0>0/\f0<=20/\f1>30)/\(((A . _)#f0) . ((~C . B)#f1))
+ens: (f0>0/\f0<=20/\f1>30)/\(((_ . _)#f0) . ((A . _)#f1))
+
+ens: (t <20)/\ ((A.B) # t)
+ens: (t <21)/\ ((~A.B) # t)
+ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
+ens: ((t1+t2) <21)/\ (A#t1). (~B # t2)
+ens: (t <21)/\ ((A.~B) # t)
+*/
+{
+    deadline (callee ()  , 
+        20);
+    timeout  (callee () , 
+        30);
+}

### 2022-04-16 code/src/program/test3.c

@@ -1,0 +1,43 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . B)#f0) . ((C . D)#f1))
+ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((_ . B)#f0) . ((C . D)#f1))
+ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . ~A)#f0) . ((C . D)#f1))
+ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . B)#f0) . ((_ . D)#f1))
+ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . B)#f0) . ((C . ~A)#f1))
+
+ens: (t <20)/\ ((A.B) # t)
+ens: (t <21)/\ ((~A.B) # t)
+ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
+ens: ((t1+t2) <21)/\ (A#t1). (~B # t2)
+ens: (t <21)/\ ((A.~B) # t)
+*/
+{
+    deadline (callee ()  , 20);
+    deadline (callee1 () , 30);
+}

### 2022-04-16 code/src/program/test4.c

@@ -1,0 +1,71 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
+ens: (f0>0/\f0<=20/\f1>30)/\(((_ . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
+ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . (((C . D)#f1) . ((C . D)^*)))
+ens: (f0>0/\f0<=20/\f1>30)/\(((A . _)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
+ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . (((C . D)#f1) . ((C . _)^*)))
+
+ens: (t <20)/\ ((A.B) # t)
+ens: (t <21)/\ ((~A.B) # t)
+ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
+ens: ((t1+t2) <21)/\ (A#t1). (~B # t2)
+ens: (t <21)/\ ((A.~B) # t)
+*/
+{
+    deadline (callee ()  , 
+    20);
+    timeout (callee1 () , 
+    30);
+    callee3 ();
+    callee4 ();
+}

### 2022-04-16 code/src/program/test5.c

@@ -1,0 +1,95 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void callee2 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+ens: (x=1)/\(_^*) \/ (~(x=1))/\(_^*)
+ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+
[…]

### 2022-04-16 code/src/program/test6.c

@@ -1,0 +1,108 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void callee2 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (f0>0/\f0<=20/\x=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) \/ (f0>0/\f0<=20/\(~(x=1))/\y=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) \/ (f0>0/\f0<=20/\(~(x=1))/\(~(y=1)))/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
+ens: (f0>0/\f0<=20/\x=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) \/ (f0>0/\f0<=20/\(~(x=1))/\y=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) \/ (f0>0/\f0<=20/\(~(x=1))/\(~(y=1)))/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
[…]

### 2022-04-16 code/src/program/test7.c

@@ -1,0 +1,105 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void callee2 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (f0>0/\f0<=20/\x=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) \/ (f0>0/\f0<=20/\(~(x=1))/\y=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) \/ (f0>0/\f0<=20/\(~(x=1))/\(~(y=1)))/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
+ens: (x=1/\f0>0/\f0<=20)/\((A . B)#f0) \/ ((~(x=1))/\y=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ ((~(x=1))/\(~(y=1)))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
+ens: (x=1/\f0>0/\f0<=20)/\((A . B)#f0) \/ ((~(x=1))/\y=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ ((~(x=1))/\(~(y=1)))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
[…]

### 2022-04-16 code/src/program/test8.c

@@ -1,0 +1,144 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+void callee2 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (f0>0/\f0<=20/\x=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) \/ (f0>0/\f0<=20/\(~(x=1))/\y=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) \/ (f0>0/\f0<=20/\(~(x=1))/\(~(y=1)))/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
[…]

### 2022-04-16 code/src/program/test9.c

@@ -1,0 +1,154 @@
+#include "primitives.c"
+
+void callee () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(A . B)
+ens: TRUE/\(A )
+*/
+{
+    event["A"];
+    event["B"];
+}
+
+void callee1 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee3 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee4 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(C . D)
+ens: TRUE/\(A )
+*/
+{
+    event["C"];
+    event["D"];
+}
+
+
+void callee5 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(M. N)
+ens: TRUE/\(A )
+*/
+{
+    event["M"];
+    event["N"];
+}
+
+
+void callee6 () 
+/*
+req: TRUE/\(_^*)
+ens: TRUE/\(F . G)
+ens: TRUE/\(A )
+*/
+{
+    event["F"];
+    event["G"];
+}
+
+void process() 
+/*
+req: TRUE/\(_^*)
+ens: (x=0/\f0>0/\f0<=20/\f1>30/\z=0)/\(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))))) \/ (x=0/\f0>0/\f0<=20/\f1>30/\(~(z=0)))/\(((A . B)#f0) . (((C . D)#f1) . (M . (N . (F . (G . (C . (D . (C . D))))))))) \/ ((~(x=0))/\y=0)/\(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) \/ ((~(x=0))/\(~(y=0)))/\(M . (N . (F . (G . (C . (D . (C . D)))))))
[…]

### 2022-04-16 paper/tv.tex
m

@@
 
+\vspace{1mm}
 $[FV\text{-}\m{Value}]$  obtains the next program state by 
@@
   \end{tabular}
+  \vspace{-2mm}
+
   \end{table}
@@
 \cite{DBLP:conf/cav/SunLDP09} model checker for conformance. 
-Next, we show experimental results and case studies to evaluate the 
-capability of our proposals.
+Next, we show experimental results and case studies to evaluate our proposals.
 
@@
 \label{subsec:Experimental_Results}
-
-We conduct experiments on a MacBook Pro with a 2.6 GHz Intel Core i7 processor. Given our benchmark, the running time varying from 0 to 500 ms.
 
@@
 \autoref{tab:Experimental} presents the evaluation results of a microbenchmark. % summary of a lightweight .
-In this experiment, we select 16 \timedL\ programs, and  annotate temporal specifications
-with a 1:1 ratio for succeeded/failed cases. 
-It records: 
-the index of the program, \textbf{No.};
-lines of code, \textbf{LOC}; 
-effects inference time, \textbf{Infer(ms)}; 
-number of valid properties, \textbf{$\mysharp$Prop(\cmark)}; 
-average proving time for the valid properties, \textbf{Avg\text{-}Prove(ms)};
-number of invalid properties, \textbf{$\mysharp$Prop(\xmark)}; and 
-average disproving time for the invalid properties, \textbf{Avg\text{-}Dis(ms)}. 
-Times are counted using milliseconds, and the experiment is done on 
-a MacBook Pro with a 2.6 GHz 6-Core Intel Core i7 processor.
 
@@
 \caption{\label{tab:Experimental} Experimental Results. }
-%\vspace{-1mm}
+\vspace{-2mm}
 \centering
-\renewcommand{\arraystretch}{1.1}
+\renewcommand{\arraystretch}{1}
 \begin{tabular} {c|c|c|c|c |c|c|c}
@@
 \end{table}
+
+In this experiment, we select 16 \timedL\ programs, and  annotate temporal specifications
+with a roughly 1:1 ratio for succeeded/failed cases. 
+Times are counted using milliseconds, and the experiment is done on 
+a MacBook Pro with a 2.6 GHz 6-Core Intel Core i7 processor. 
+The table records: 
+\textbf{No.}, the index of the program;
+\textbf{LOC}, lines of code; 
+\textbf{Infer(ms)}, effects inference time; 
+\textbf{$\mysharp$Prop(\cmark)}, number of valid properties; 
+\textbf{Avg\text{-}Prove(ms)}, average proving time for the valid properties;
+\textbf{$\mysharp$Prop(\xmark)}, number of invalid properties; 
+\textbf{Avg\text{-}Dis(ms)}, average disproving time for the invalid properties; and 
+\textbf{$\mysharp$AskZ3}, number of querying Z3 solver through out the experiments.
+
+\paragraph{Discussion:} Generally, the inference time and proving 
+time increase while the program's length increases. 
+Besides, while \emph{the number of querying Z3 per property} (\textbf{$\mysharp$AskZ3}/(\textbf{$\mysharp$Prop(\cmark)} +\textbf{$\mysharp$Prop(\xmark)})) 
+goes up, the 
+proving/disproving time goes up.
+Furthermore, we notice that 
+%that no matter how long the programs are, 
+the disproving
+times for invalid properties are constantly lower than the proving process, 
+regardless of the program complexity. This finding echos the 
+insights from prior TRS-based works \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}, 
+which suggest that TRS is a better average-case algorithm than 
+those based on the comparison of automata.
+
+We summary: a TRS is efficient because 
+\emph{it only constructs automata as far as it needs}, which makes 
+it more efficient when disproving incorrect specifications, as we can 
+disprove it earlier without constructing the whole automata. In other 
+words, the more incorrect specifications are, the more efficient our solver is.
 
@@
 
-As shown in \tabref{tab:reoccur}, the LHS formula is a 
-disjunction of two effects. An inclusion with a disjunctive 
-antecedent succeeds if both disjunctions entail the consequent, 
-shown in step {\textcircled{1}}.  
-%Now we have 2 subtrees, the first subtree is for
-%  \code{
-%    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
-%    \CONTAIN
-%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
-%  }
-%and the second one is for
-%  \code{
-%    \textcolor {darkred}{True} : {B} \CONTAIN
-%    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
-%  }.
-%In order to prove the original proposition, both of the two new propositions have
-%to be proved.
-%Using the disjunction rule \code{\effect_1 \vee \effect_2 \CONTAIN \effect \iff
-%\effect_1 \CONTAIN \effect \ and \  \effect_2 \CONTAIN \effect}, we split the proposition
-%in . 
-In step \textcircled{2} of the first sub-tree, in order to eliminate the first event \code{\{B\}}, \code{\{A\}^\star \mysharp  t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
-% is 
-%eliminated by \code{\epsilon}, 
-Then in steps \textcircled{4}, we
-can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} succeed.
-%and \code{\epsilon \CONTAIN \epsilon}.
-
-Looking at the second sub-tree, in step \textcircled{5}, \code{t_L} and \code{t_R} are firstly split 
-into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
-Then in step {\textcircled{6}, 
-\code{\{A\} \mysharp  t_L^1} together with \code{\{A\} \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
-%, also
-%are unified as new constraint \code{t_L^1{=}t_R^1}.
-In step {\textcircled{8}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
-%one in
-%step \code{\textcircled{1}}, 
-Hence we apply the rule \code{[REOCCUR]} to prove it with a succeed side constraints entailment: \code{\textcolor {
-      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
-      \wedge t_L^2{=}t_R^2
-    }\Rightarrow
-    \textcolor {darkred}{t_R{<}4} }. 
-%Since the structure of terms \code{t_L^2, t_L} and \code{t_R^2, t_R} are isomorphic,
-%we will need to unify \code{t_L^2} and \code{t_R^2} in order to get enough
-%time constraints. And in step \code{\textcircled{5}} we prove the proposition to
-%be true.
-
 {
@@
 
+As shown in \tabref{tab:reoccur}, the LHS formula is a 
+disjunction of two effects. An inclusion with a disjunctive 
+antecedent succeeds if both disjunctions entail the consequent, 
+shown in step {\textcircled{1}}.
+
+In step \textcircled{2} of the first sub-tree, in order to eliminate the first event \code{  B  }, \code{  A  ^\star \mysharp  t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
+Then in steps \textcircled{4}, we
+can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} succeed.
+
+Looking at the second sub-tree, in step \textcircled{5}, \code{t_L} and \code{t_R} are firstly split 
+into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
+Then in step {\textcircled{6}, 
+\code{  A   \mysharp  t_L^1} together with \code{  A   \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
+In step {\textcircled{8}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
+%one in
+%step \code{\textcircled{1}}, 
+Hence we apply the rule \code{[REOCCUR]} to prove it with a succeed side constraints entailment: \code{\textcolor {
+      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
+      \wedge t_L^2{=}t_R^2
+    }\Rightarrow
+    \textcolor {darkred}{t_R{<}4} }.
+
 \subsubsection{Expressiveness.}
@@
 
+\begin{comment}
   Classical LTL
@@
 \subsubsection{Beyond Regular, Context-Free and Context-Sensitive}
+\end{comment}
 
@@
 specifications \code{n{>} 0 \wedge m{>} 0 \wedge  
-(\anyevent{Red}\mysharp{n}\cdot\anyevent{Yellow}\mysharp{m}\cdot
-\anyevent{Green}\mysharp{n})^\star}, which specifies that  
+(\anyevent{Red}\mysharp{n}\cdot\anyevent{Yellow}\mysharp{m}}
+\code{\cdot \anyevent{Green}\mysharp{n})^\star}, which specifies that  
 (i) all the colors will occur at each life circle; and 
@@
 
-As the examples show, our proposed effects logic and the abstract semantics for \code{\timedL} not only tightly capture the behaviors of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm.
-Meanwhile, the inferred temporal traces from a given reactive program enable a compositional timed temporal verification at the source level, which is not yet supported by existing temporal verification techniques.
-
-Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:conf/vmcai/SongC21,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+As the examples show, our proposed effects logic and the abstract semantics for 
+\code{\timedL} not only tightly capture the behaviors of a time-critical model 
+but also help to increase the capability of existing techniques. 
+Meanwhile, the inferred temporal traces from a given reactive program enable a compositional 
+timed temporal verification at the source level, which is not yet supported by existing temporal 
+verification techniques.
+
+Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, 
+which is considered important because it overcomes the following main limitations in traditional 
+timed model checking:  i) they cannot be used to specify and verify systems incompletely 
+specified (i. e., whose timing constants are not known yet), and hence cannot be used in early 
+design phases; ii) verifying a system for a set of timing constants usually requires to enumerate 
+all of them one by one if they are supposed to be integer-valued; in addition, Timed Automata 
+cannot be used to verify a system for a set of timing constants that are to be taken in a 
+real-valued dense interval.
+
+A term rewriting system is efficient because \emph{it only constructs automata as far as it needed}, 
+which makes it more efficient when disproving incorrect specifications, as we can disprove it 
+earlier without constructing the whole automata. In other words, the more incorrect specifications 
+are, the more efficient our solver is.
 
@@
 
-Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, which is considered important because it overcomes the following main limitations in traditional timed model checking:  i) they cannot be used to specify and verify systems incompletely specified (i.
-e., whose timing constants are not known yet), and hence cannot be used in early design phases; ii) verifying a system for a set of timing constants usually requires to enumerate all of them one by one if they are supposed to be integer-valued; in addition, Timed Automata cannot be used to verify a system for a set of timing constants that are to be taken in a real-valued dense interval.
-
-A term rewriting system is efficient because \emph{it only constructs automata as far as it needed}, which makes it more efficient when disproving incorrect specifications, as we can disprove it earlier without constructing the whole automata.
-In other words, the more incorrect specifications are, the more efficient our solver is.
-
 %%

### 2022-04-16 paper/tv.tex
m

@@
 using Implicit Clocks and an Extended Antimirov Algorithm}
-
-%% Automated Temporal Verification for Mixed Sync-Async Reactive Paradigm
 
@@
  with \codem{d1<d2}; 
-\code{x} and \code{ct} are global variables. The protocol is 
+\codem{x} and \codem{ct} are global variables. The protocol is 
 modeled as 
@@
 processes. Each of the three processes attempts to enter 
-the critical section when \code{x} is \code{-1}, i.e. no 
+the critical section when \codem{x} is \codem{-1}, i.e. no 
 other process is 
@@
 restricts the relation between \codem{d1} and \codem{d2}. When 
-\codem{d1<d2} is provided, it ensures a repeated trace where the value of 
+\codem{d1<d2} is provided, it ensures a global state, i.e., the repeated trace, where the value of 
 \codem{ct} is either \codem{-1} or equals to \codem{x}. The specification
@@
 Our prototype system is able to soundly check such time-critical 
-algorithms. \autoref{sec:Evaluation} presents the details about the implementation and evaluation.
+algorithms. \secref{sec:Evaluation} presents the details about the implementation and evaluation.
 
@@
 the timed process constructs.
-{{\small
-\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%   Wait                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\code{\frac{
-  t {\leq} d 
-}{(\env, \textbf{delay}[d]) \xrightarrow[]{\text{t}} (\env, \textbf{delay} [d \text{-}t])}\ [delay_1]} 
-\qquad \qquad 
-\code{\frac{
-}{(\env, \textbf{delay} [0]) \xrightarrow[]{\tau} (\env, ())}\ [delay_2]} 
-\end{flalign*}}}
+
+\input{rules/op_delay.tex}
+
 The above captures behaviors of process \textbf{delay}[d]. 
@@
 \code{d} becomes \code{0}.
-{{\small\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%   timeout                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\code{\frac{
-  (\env,e_1) \xrightarrow[]{\anyevent{A}} (\env^\prime,e_1^\prime)
-}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)}\ [tot_1]} 
-\quad  
-\code{\frac{
-  (\env,e_1) \xrightarrow[]{\tau} (\env^\prime,e_1^\prime)  
-}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env^\prime, e_1^\prime\ \textbf{timeout}[d]\ e_2 )}\ [tot_2]} 
-\end{flalign*}}}
-
-{{\small\begin{flalign*}
-\code{\frac{
-  (\env,e_1) \xrightarrow[]{\text{t}} (\env,e_1^\prime)  \quad (t {\leq} d) 
-}{(\env, e_1\ \textbf{timeout}  [d] \ e_2) \xrightarrow[]{\text{t}} (\env,e_1^\prime\ \textbf{timeout} \  [d\text{-}t] \ e_2)}\ [tot_3]} 
-\quad  
-\code{\frac{
-}{(\env, e_1\ \textbf{timeout}   [0] \ e_2) \xrightarrow[]{\tau} (\env, e_2)}\ [tot_4]} 
-\end{flalign*}}}
+
+\input{rules/op_to.tex}
+
 If an observable event \anyevent{A} can be engaged by \code{e_1}, 
@@
 
-{{\small\begin{flalign*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%   deadline                 %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\code{\frac{
-  (\env,e) \xrightarrow[]{\anyevent{A}} (\env^\prime,e^\prime)
-}{(\env, \textbf{deadline} [d] \ e ) \xrightarrow[]{\anyevent{A}} (\env^\prime, \textbf{deadline}  [d] \ e^\prime)} [ddl_1]} 
-\ \ \  
-\code{\frac{
-  (\env,e) \xrightarrow[]{\text{t}} (\env,e^\prime)  \quad (t {\leq} d)
-}{(\env, \textbf{deadline}  [d]\ e ) \xrightarrow[]{\text{t}} (\env, \textbf{deadline}  [d \text{-}t] \ e^\prime )} [ddl_2]} 
-\end{flalign*}}}
+\input{rules/op_ddl.tex}
 
@@
 
-{{\small\begin{flalign*}
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  %%   deadline                 %%
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \code{\frac{
-    \env \models  b 
-  }{(\env, [b] \ e ) \xrightarrow[]{\tau} (\env, e)}\ [guard_1]} 
-  \ \ \qquad\qquad 
-  \code{\frac{
-    \env \not\models  b 
-  }{(\env, [b] \ e ) \xrightarrow[]{t} (\env, [b] \ e)}\ [guard_2]} 
-\end{flalign*}}}
+\input{rules/op_gu.tex}
+
 The guarded process \code{[b]e} behaves as \code{e} when \code{b} is true, 
@@
 \end{flalign*}}}
+
 Rules \code{[seq_1]} and \code{[seq_2]} state that \code{e_1} takes the control 
@@
 \anyevent{A}\code{(v, \alpha^*)} stands for an observable event with label 
-\anyevent{A}, parameterized by \code{v}, and the assignment operations \code{\alpha^*}. 
+\anyevent{A}, parameterized by \code{v}, and the assignment operations \code{\alpha^*}; and 
 \code{\tau(\pi)} is an invisible event, which can be parameterized with a pure formula 
@@
 indicating the sequencing constraints on temporal behaviors.
-Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
-the effects \code{\effect} take \code{d} time units to complete; 
-the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
-temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
-from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
-\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{\es} \ .
 
@@
 \end{figure}
+
+Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
+the effects \code{\effect} take \code{d} time units to complete; 
+the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
+temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
+from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
+\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{\es} \ .
 
@@
 \begin{wrapfigure}{R}{0.54\columnwidth}
-  \vspace{-3mm}
+ % \vspace{-1mm}
 
@@
 \code{(b{=}True)}? in to the current program states.
+
 {{\small\begin{gather*}
@@
 then parallel merges the effects from these two branches.
+
 {{\small\begin{gather*}
@@
 
-\vspace{1mm}
 The \code{[FV\text{-}If\text{-}Else]} computes an 
@@
 for \code{\Pi \wedge \neg v }.
+
 {{\small\begin{gather*}
@@
 
-\vspace{1mm}
 Rule \code{[FV\text{-}Event]} simply constructs an new event and 
@@
 together with the additional constraint \code{t{=}d}.
+
   {{\small\begin{gather*}
@@
 
-\vspace{1mm}
 Rule \code{[FV\text{-}Timeout]} computes the effects from \code{e_1} and \code{e_2}
@@
 of these effects with their corresponding time variables and arithmetic constrains. 
+Note that, \code{hd(\Theta_1)} and \code{tl(\Theta_1)} return the head and the tail of 
+\code{\Theta_1} respectively.
+
 {{\small\begin{gather*}
@@
       \\
-      \s{\Theta_f, \Pi_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (\Theta_1\mysharp t)}
+      \s{\Theta_f, \Pi_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (hd(\Theta_1)\mysharp t \cdot tl(\Theta_1))}
       \cup 
@@
 
-\vspace{1mm}
 Similar to \code{[FV\text{-}Timeout]}, \code{[FV\text{-}Ddl]} computes the effects 
 from \code{e} and adds an upper time-bound to the result.
+
 {{\small\begin{gather*}
@@
 
-  \vspace{1mm}
   Rule \code{[FV\text{-}Meth]} initializes the current effects state 
@@
 \code{\effect_{post}} only needs to capture the effects from the current method body, excluding the history effects specified in \code{\effect_{pre}}. }.
+
 {{\small\begin{gather*}
@@
 
-  \vspace{1mm}
 Rule \code{[FV\text{-}Call]} first checks whether the instantiated 
@@
   instantiated postcondition to the current states.
+
   %, in which we use an auxiliary function \code{rev} to reverse the event sequences of effects.
@@
   if \code{(\env, e) {\rightarrow^*} (\env^\prime, ())} produces concrete 
-  execution time \code{d} and event trace \code{\varphi}, and \code{ \vdash  
-  \s{\env, \epsilon} e \s{\Pi, \Theta}}, then, 
-  \code{\exists (\pi\wedge \es) \in \s{\Pi, \Theta} } such that 
+  execution time \code{d} and event sequence \code{\varphi}, and the forward verifier reasons \code{ \vdash  
+  \s{\env, \epsilon} \ e\  \s{\Pi, \Theta}}, then, \\
+  \code{\qquad \qquad \qquad \qquad  \qquad 
+   \exists (\pi\wedge \es) \in \s{\Pi, \Theta} } such that 
   \code{d, \env^\prime, \varphi  \models (\pi\wedge \es)}. 
@@
   \begin{proof}
-    By induction. 
-  %See %the technical report\cite{TR}. 
-  %\appref{proof:SoundnessProof}.
+   % By induction.        
+    See \appref{proof:SoundnessProof_FE}.
   \end{proof}
@@
   }.
-  %\footnote{As the reader may notice, our First and Derivative function does not handle the timed sequences constructed by \code{||}, as the synchronous parallel is reduced during the normalization phase.}
+
   \begin{gather*}
@@
 Notice that the derivatives of a parallel composition makes use of the \emph{Parallel Derivative} \code{\Bar{\Bar{D}}^{\pi}_{h}(\es)}, defined as follows:
+
 \begin{definition}[Parallel Derivative]\label{Derivative_maybe}
@@
 
-\begin{theorem}[Termination]\label{termination}
+\begin{theorem}[Termination  of the TRS]\label{termination}
 The rewriting system TRS is terminating.
@@
 
- \begin{theorem}[Soundness]\label{Cyclicsoundness}
+ \begin{theorem}[Soundness of the TRS]\label{Cyclicsoundness}
 Given an inclusion \code{\effect_1 \CONTAIN \effect_2}, if the TRS returns \code{TRUE} when proving \code{\effect_1 \CONTAIN \effect_2}, i.e., it has a cyclic proof, 
@@
 And to test that, we cover a number of test cases with function calls, and the callee's parameters would be used as the time bounds.
-
-\autoref{tab:Experimental} presents the evaluation results of a microbenchmark. % summary of a lightweight .
 
@@
 
+\autoref{tab:Experimental} presents the evaluation results of a microbenchmark. % summary of a lightweight . 
 In this experiment, we select 16 \timedL\ programs, and  annotate temporal specifications
@@
     \textcolor {darkred}{t_R{<}4} 
-%\qquad
-%       A  ^\star \cdot   B  
-%    \CONTAIN
-%       A  ^\star \cdot   B  
   }
@@
 
-In step \textcircled{2} of the first sub-tree, in order to eliminate the first event \code{  B  }, \code{  A  ^\star \mysharp  t_R} has to be reduced to be \code{\epsilon}, therefore the time constraints have nothing to do in this branch.
+In step \textcircled{2} of the first sub-tree, in order to eliminate the first event 
+\code{  B  }, \code{  A  ^\star \mysharp  t_R} has to be reduced to \code{\epsilon}, therefore 
+the time constraints have nothing to do in this branch. 
 Then in steps \textcircled{4}, we
@@
 %step \code{\textcircled{1}}, 
-Hence we apply the rule \code{[REOCCUR]} to prove it with a succeed side constraints entailment: \code{\textcolor {
-      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
+Hence we apply the rule $\codeme{[REOCCUR]}$ to prove it with a succeed side constraints entailment: 
+\code{
+  \textcolor {
+    darkred}{t_L{<}3 \wedge } \ \textcolor {
+      blue}{t_L^1{+}t_L^2{=}t_L \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
     \wedge t_L^2{=}t_R^2
-    }\Rightarrow
-    \textcolor {darkred}{t_R{<}4} }.
+  } \Rightarrow
+  \textcolor {darkred}{t_R{<}4} 
+}.
 
@@
 
-%
-%
-%compare to Timed Automata:
-%modular and can plug in anywhere. 
-%absolute time and relative time. 
-%$
-%//
-%(lower_t, upper_time)
-%lower_ti<=upper_t
-%lower_t<5
-%lower_t>8
-%modular and can plug in anywhere. 
-%absolote time and relative time. 
-%it can be only for synchronous system, t.sync, 
-%or or real time t.rt.dur. 
-%$
-
 \section{Conclusion}
@@
 
-\section{Termination Proof}  \label{proof:TerminationProof}
+\section{Soundness of the Forward Rules} 
+ \label{proof:SoundnessProof_FE}
+
+Given any system configuration \code{\zeta = (\env, e)}, by applying the operational
+  semantics rules, \\
+  if \code{(\env, e) {\rightarrow^*} (\env^\prime, ())} produces concrete 
+  execution time \code{d} and event sequence \code{\varphi}, and the forward verifier reasons \code{ \vdash  
+  \s{\env, \epsilon} \ e\  \s{\Pi, \Theta}}, then, 
+  \code{
+   \exists (\pi \wedge \es) \in \s{\Pi, \Theta} } such that 
+  \code{d, \env^\prime, \varphi  \models (\pi\wedge \es)}
+
+  \begin{proof}
+    ~\\
+  \begin{enumerate}
+  \item \textbf{Delay:}  
+  \input{rules/op_delay.tex}
+\noindent When $\zeta = (\env,  \textbf{delay}[d]) {\rightarrow^*} (\env, ()) $, by applying rules \code{[delay_1]} and \code{[delay_2]}, 
+it produces the concrete sequence [], and takes concrete time \codeme{d}. \\
+By \code{[FV\text{-}Delay]}, $\vdash  \s{\env, \epsilon} \ \textbf{delay}[d]\  \s{\env \wedge (t{=}d), \epsilon\mysharp t}$. \\
+Then \code{\env \wedge (t{=}d) \wedge \epsilon\mysharp t} is the witness such that \code{d, \env, []  \models (\env \wedge (t{=}d) \wedge \epsilon\mysharp t)}. 
+\\
+
+\item \textbf{Timeout:}  
+\input{rules/op_to.tex}
+\noindent When $\zeta = (\env,  e_1\ \textbf{timeout}  [d] \ e_2) {\rightarrow^*} (\env^\prime, ()) $, 
+there are two possibilities:
+
+- \code{e_1} started before time limit \code{d}, by applying rules \code{[to_2]}, \code{[to_3]} and \code{[to_1]}, 
+it produces the concrete sequence [\anyevent{A}; \code{\varphi(e_1^\prime)}], and \anyevent{A} takes less than \codeme{d} time-units. \\
+By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
+\s{\env \wedge (t{\leq}d), \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}$. \\
+Then \code{\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})} is 
+the witness such that \code{d, \env, [\anyevent{A}; \code{\varphi(e_1^\prime)}]  
+\models (\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}. 
+\\
+- \code{e_1} never started, by applying rules \code{[to_4]}, 
+it produces the concrete sequence [\code{\varphi(e_2)}], and it takes more than \codeme{d} time-units. \\
+By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
+\s{\env \wedge (t{>}d), (\es_2 \mysharp t)}$. \\
+Then \code{\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)} is 
+the witness such that \code{d, \env, [\varphi(e_2)]  
+\models (\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)}.
+
+\item \textbf{Deadline:}  
+\input{rules/op_ddl.tex}
+When $\zeta = (\env,  \textbf{deadline}  [d]\ e) {\rightarrow^*} (\env^\prime, ()) $, 
+by applying rules \code{[ddl_1]}, \code{[ddl_2]}, 
+it produces the concrete sequence [\code{\varphi(e)}], and it takes less than \codeme{d} time-units. \\
+By \code{[FV\text{-}Deadline]}, $\vdash  \s{\env, \epsilon} \ \textbf{deadline}[d]\ e 
+\ \s{\env \wedge (t{<}d), \es(e)\mysharp t}$. \\
+Then \code{\env \wedge (t{<}d) \wedge \es(e)\mysharp t} is the witness such that 
+\code{d, \env, [\code{\varphi(e)}]  \models (\env \wedge (t{<}d) \wedge \es(e)\mysharp t)}. \\
+
+\item We omit the primitives which are not related to the timing.
+
+  \end{enumerate}
+
+ \end{proof}
+
+\section{Termination  of the TRS}  \label{proof:TerminationProof}
 
@@
 
-\section{Soundness Proof} 
+\section{Soundness  of the TRS} 
  \label{proof:SoundnessProof}
 
+  For each inference rules, if inclusions in their premises are valid, and their side conditions are satisfied, then goal inclusions in their conclusions are valid.
+
   \begin{proof}
-  For each inference rules, if inclusions in their premises are valid, and their side conditions are satisfied, then goal inclusions in their conclusions are valid.
-
+    ~\\
   \begin{enumerate}

### 2022-04-16 paper/tv.tex
m

@@
 Then \code{\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})} is 
-the witness such that \code{d, \env, [\anyevent{A}; \code{\varphi(e_1^\prime)}]  
+the witness such that \code{d, \env^\prime, [\anyevent{A}; \code{\varphi(e_1^\prime)}]  
 \models (\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}. 
@@
 Then \code{\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)} is 
-the witness such that \code{d, \env, [\varphi(e_2)]  
+the witness such that \code{d, \env^\prime, [\varphi(e_2)]  
 \models (\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)}.
@@
 Then \code{\env \wedge (t{<}d) \wedge \es(e)\mysharp t} is the witness such that 
-\code{d, \env, [\code{\varphi(e)}]  \models (\env \wedge (t{<}d) \wedge \es(e)\mysharp t)}. \\
+\code{d, \env^\prime, [\code{\varphi(e)}]  \models (\env \wedge (t{<}d) \wedge \es(e)\mysharp t)}. \\
 

### 2022-06-15 paper/popl2022.tex
m

--- 2022-02-27 popl2022.tex
@@
 \newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
+\newcommand{\lappend}{\mathrel{\texttt{++}}}
 
@@
 a waiting for a single signal \code{\textbf{S}?};
-  %where \anyevent{a} is an element from a finite set of events, donated by \code{\Sigma};
+  %where \anyevent{a} is an element from a finite set of events, denoted by \code{\Sigma};
 %parametrized event \code{ \anyevent{a}.\iota} where \code{\iota} is a list pattern expressing a possibly infinite list (for example, \code{\anyevent{a}.[1,2,3,4]},  \code{\anyevent{a}.[1 ..
@@
 
-We use \code{\pure{\pi}} to donate a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
+We use \code{\pure{\pi}} to denote a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
 We use \code{\pure{A(}{t_1, t_2}\pure{)}} to represent atomic formulas of two terms (including $  {=},
@@
 
-\begin{figure}[h]
-    \vspace{-1mm}
-    \renewcommand{\arraystretch}{1}
+\begin{figure}[!ht]
+  \renewcommand{\arraystretch}{1.2}
 \begin{align*} 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models \pi : \empt }  
+&\code{d, \varphi \models \pi : \epsilon }  
 &\m{iff}\quad 
-&  d{=}0 \ and\  {\tt{SAT}(\pi)}  \ and \ \varphi {=} [] 
+&  d{=}0 \ and\  {\m{SAT}(\pi)}  \ and \ \varphi {=} [] 
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : I }  &\m{iff}\quad 
-& d {\geq} 0 \ and\ {\tt{SAT}(\pi)}  \ and \ 
-\varphi {=} \code{[I]}
+&\code{d, \varphi \models  \pi : \anyevent{A} }  &\m{iff}\quad 
+& d {\geq} 0 \ and\ {\m{SAT}(\pi)}  \ and \ 
+\varphi {=} \code{[\anyevent{A}]}
 \\[0.2em]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          waiting                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : \textbf{S}?}  &\m{iff}\quad 
-& d {\geq} 0  \ and\  {\tt{SAT}(\pi)}  \ and \
-\exists n {\geq} 0.\ \varphi {=} \code{\{ \overline{\textbf{S}} \}^{n} {+}{+} [\{ {\textbf{S}} \}] }
-  \\[0.2em]
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            CONCATE                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1{\cdot}\es_2)}  
+%%                            CONCATEnate                            %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, \varphi \models  \pi : (es_1{\cdot}es_2)}  
 &\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \exists \code{\varphi_1, \varphi_2, d_1, d_2}\ and\ \code{
-\varphi {=} \varphi_1 {+}{+} \varphi_2, d {=} d_1 {+} d_2 \ and 
+& {\m{SAT}(\pi)}  \ and \ \exists \code{\varphi_1, \varphi_2, d_1, d_2}\ and\ \code{
+\varphi {=} \varphi_1 \lappend \varphi_2, d {=} d_1 {+} d_2 
 }\\
 & & &
-\code{d_1, \varphi_1 \models  \pi : \es_1}  \ and \ 
-\code{d_2, \varphi_2 \models  \pi : \es_2}  
+\m{and}\ \code{d_1, \varphi_1 \models  \pi : es_1}  \ and \ 
+\code{d_2, \varphi_2 \models  \pi : es_2}  
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1 {\vee} \es_2)}  
+&\code{d, \varphi \models  \pi : (es_1 {\vee} es_2)}  
 &\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ or \ 
- \code{d, \varphi \models  \pi :  \es_2}  
+& {\m{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  es_1 } \ or \ 
+\code{d, \varphi \models  \pi :  es_2}  
 \\[0.2em]
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                       par                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1 || \es_2) }  
+%%                       timed                         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, \varphi \models  \pi : es \mysharp  t }  
 &\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ and \ 
- \code{d, \varphi \models  \pi :  \es_2}  
+& d, \varphi \models  (\pi \wedge t{=}d) : es
 \\[0.2em]
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                       timed                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : \es \# t }  
+%%                            KLEENE                            %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d,  \varphi \models \pi : \esn{es}{\star}  }  
 &\m{iff}\quad 
-& d, \varphi \models  (\pi \wedge t{=}d) : \es
+&d, \varphi \models \pi :  \epsilon \ or \ 
+d, \varphi \models \pi :  (es \cdot \esn{es}{\star} ) 
 \\[0.2em]
   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            KLEENE                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d,  \varphi \models \pi : \esn{\es}{\star}  }  
-&\m{iff}\quad 
-&d, \varphi \models \pi :  \empt \ or \ 
-d, \varphi \models \pi :  (\es \cdot \esn{\es}{\star} ) 
- \\[0.2em]
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%                            OMEGA                            %%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d,  \varphi \models \pi : \esn{\es}{\omega}   }  
+&\code{d,  \varphi \models \pi : \esn{es}{\omega}   }  
 &\m{iff}\quad 
 &
-d, \varphi \models \pi :  (\es \cdot \esn{\es}{\omega} )  
+d, \varphi \models \pi :  (es \cdot \esn{es}{\omega} )  
 \\[0.2em]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-& \code{d, \varphi \models False : \bot }  
+& \code{d, \varphi \models \m{False} : \bot }  
 &\m{iff}\quad 
 &   otherwise
-%{\tt{UNSAT}(\pi)}  \ or \  \varphi  {=} \bot
-%\exists t, d(t) \not\models \llbracket \pure{\pi} \rrbracket_{t}
+%{\m{UNSAT}(\pi)}  \ or \  \varphi  {=} \bot
+%\exists t, d(t) \not\models \llbracket {\pi} \rrbracket_{t}
 \end{align*}
-    \vspace{-3mm}
-\caption{Semantics of Timed Synchronous Effects.}
-\label{fig:Sementic}
-  \vspace{-1mm}
+\caption{Semantics of \timedEffs\ .}
+\label{work3_fig:Sementic}
 \end{figure}
@@
 
-%\subsection{closure of clock constrains}
 %how to eliminate the unobservable transitions. 
@@
 \anyevent{Send}, then makes a recursive call with parameter \code{n{-}1}.
-Note that the post condition contains both finite effects and infinite effects in one single formula, separated by arithmetic constrains.
+Note that the post condition contains both finite effects and infinite effects in one single formula, separated by arithmetic constraints.
 
@@
 where \code{|X|} stands for the cardinality of a set \code{X}.
-Let \code{\Rightarrow} donate the rewrite relation, then \code{\Rightarrow^*} denotes its reflexive transitive closure.
+Let \code{\Rightarrow} denote the rewrite relation, then \code{\Rightarrow^*} denotes its reflexive transitive closure.
 For any given \code{S_0}, \code{H_0}, this ordering is well founded on the set of pairs \code{\{\langle S, H \rangle | \langle S_0, H_0 \rangle \Rightarrow^* \langle S, H \rangle \}}, due to the fact that \code{H} is a subset of the finite set of pairs of all possible derivatives in initial inclusion.

### 2022-06-15 paper/tv.tex
m

@@
 \newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
-\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}.}
+\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}}
 \newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
@@
 Moreover, the time bounds 
-can be dependent on the program inputs, demonstrated in \figref{fig:Value_dependent_intro}, we mark the precondition and postcondition
+can be dependent on the program inputs, demonstrated in 
+\figref{fig:Value_dependent_intro}; we mark the precondition and postcondition
 using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.
@@
 
-Both preconditions require no arithmetic constrains,   
-and  have no temporal constrains upon 
+Both preconditions require no arithmetic constraints,   
+and  have no temporal constraints upon 
 the history traces. 
@@
 finite-state automata, it is neither sufficient nor efficient to 
- translation them 
+translate them 
 into Timed Automata and reply on the solving engines of Timed Automata.
@@
 five time-units deadline while calling 
-\codem{addNSugar} (defined in \figref{fig:Value_dependent_intro}),
+\codem{addNSugar} (defined in 
+Fig. \textcolor{black}{\ref{fig:Value_dependent_intro}}),
  with argument \codem{n}; then emits event \anyevent{Coffee} with
@@
 \timedEffects\ supports more features such as \emph{disjunctions}, 
-\emph{guards} and \emph{parallelism}, etc, which can be found in 
+\emph{guards} and \emph{parallelism}, etc., which can be found in 
 \secref{subsec:Specification_language} and 
@@
 
-Note that the prior effects in precondition is new regarding 
+Note that the prior effects in precondition are new regarding 
 the existing real-time verification.
@@
 branches, according to the different 
-arithmetic constrains, by rule  $\codeme{[LHS\text{-}OR]}$.
+arithmetic constraints, by rule  $\codeme{[LHS\text{-}OR]}$.
 
@@
 Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using 
-\emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf., \tabref{tab:reoccur}.
+\emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf.\ \tabref{tab:reoccur}.
 
@@
   %\vspace{-1mm}
-  \caption{Fischer's mutual exclusion algorithm.}\label{fig:overview_ficher}
+  \caption{Fischer's mutually exclusion algorithm.}\label{fig:overview_ficher}
     % \vspace{-2mm}
@@
 \figref{fig:overview_ficher} presents the classical 
-Fischer's mutual exclusion algorithm. 
+Fischer's mutually exclusion algorithm. 
 where \codem{d1} and \codem{d2} are two integer constants
@@
 
-Here, \code{c} and \code{b} are for integer and boolean constants, 
+Here, \code{c} and \code{b} are for integer and Boolean constants, 
  \code{mn} and \code{x} are for meta-variables.  
@@
 special case of the primitive presented here, where \code{e_1} never starts. 
-Process $\textbf{deadline} [d]\ e$ constrains $e$ to terminate before $d$ time units.
+Process $\textbf{deadline} [d]\ e$ constraints $e$ to terminate before $d$ time units.
 
@@
 a single event \code{ev};
-  %where \anyevent{a} is an element from a finite set of events, donated by \code{\Sigma};
+  %where \anyevent{a} is an element from a finite set of events, denoted by \code{\Sigma};
 %parametrized event \code{ \anyevent{a}.\iota} where \code{\iota} is a list pattern expressing a possibly infinite list (for example, \code{\anyevent{a}.[1,2,3,4]},  \code{\anyevent{a}.[1 ..
@@
 may communicate via multi-party event synchronization or shared variables;
-a blocking waiting for a certain of constraint to be satisfied \code{\pi ?}; 
+a blocking waiting for a certain constraint to be satisfied \code{\pi ?}; 
 We introduce a new operator \code{\mysharp }, and the effects 
@@
 
-We use \code{{\pi}} to donate a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
+We use \code{{\pi}} to denote a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
 We use \code{{A(}{t_1, t_2}{)}} to represent atomic formulas of two terms (including $  {=},
@@
 A term also allows simple computations of terms, \code{t_1{+}t_2} and \code{t_1\text{-}t_2}.
-To abstract the elapsed time, the default and implicit pure constraints of all the terms is to be greater or e
-qual to  0.
+To abstract the elapsed time, the default and implicit pure constraints of all the terms is to be greater or equal to  0.
 
@@
 The \code{[FV\text{-}If\text{-}Else]} computes an 
-over-approximation of the program states, by adding different constrains into 
+over-approximation of the program states, by adding different constraints into 
 different branches. \code{\Pi \wedge v} enforces 
-\code{v} into the pure constraints of every traces in the state, same 
+\code{v} into the pure constraints of every trace in the state, same 
 for \code{\Pi \wedge \neg v }.
@@
 
-Rule \code{[FV\text{-}Event]} simply constructs an new event and 
+Rule \code{[FV\text{-}Event]} simply constructs a new event and 
 concatenates it to the current program states. 
@@
 using the starting state \code{\s{\Pi, \epsilon}}. The final states are the union 
-of these effects with their corresponding time variables and arithmetic constrains. 
+of these effects with their corresponding time variables and arithmetic constraints. 
 Note that, \code{hd(\Theta_1)} and \code{tl(\Theta_1)} return the head and the tail of 
@@
 The TRS  is an automated entailment checker to prove language 
-inclusions between \timedEffects, cf., \defref{Inclusion} and 
+inclusions between \timedEffects, cf. \defref{Inclusion} and 
 \tabref{tab:rewriting_tree_send} It is triggered i) prior to 
@@
 for the post condition checking. Given two effects 
-\code{\effect_1} and \code{\effect_2}, TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
+\code{\effect_1} and \code{\effect_2}, the TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
 
@@
 } of Nullable, First and Derivative respectively. Intuitively, 
-the Nullable function \code{\delta_{{\pi}}(\es)} returns a boolean 
+the Nullable function \code{\delta_{{\pi}}(\es)} returns a Boolean 
 value indicating whether \code{{\pi} \wedge \es} contains the empty 
@@
 
-%\subsection{closure of clock constrains}
+%\subsection{closure of clock constraints}
 %how to eliminate the unobservable transitions. 
@@
 \begin{definition}[Heads]\label{Heads}
-If \code{h} is a head of \code{\pi \wedge \es}, then there exists 
+If \code{h} is a head of \code{\pi \wedge \es}, then there exist 
 \code{\pi^\prime} and \code{\es^\prime}, 
@@
   Given any \code{\effect {=} \pi \wedge \es},
-  \code{fst_{{\pi}}(\es)} return a set of heads, be the set of initial elements   
+  \code{fst_{{\pi}}(\es)} returns a set of heads, be the set of initial elements   
   derivable from effects \code{\pi \wedge \es}, where: 
@@
 of the original inclusion succeeds if all the derivative 
-inclusions succeeds.
+inclusions succeed.
 \input{rules/rule4}
@@
 
-We summary: a TRS is efficient because 
+As a summary: a TRS is efficient because 
 \emph{it only constructs automata as far as it needs}, which makes 
@@
 In step \textcircled{2} of the first sub-tree, in order to eliminate the first event 
-\code{  B  }, \code{  A  ^\star \mysharp  t_R} has to be reduced to \code{\epsilon}, therefore 
+\code{  B  }, \code{  A  ^\star \mysharp  t_R} has to be reduced to~\code{\epsilon}, therefore 
 the time constraints have nothing to do in this branch. 
 Then in steps \textcircled{4}, we
-can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} succeed.
+can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} 
+succeed.
 
@@
 (ii) the duration of the green light and the red light is 
-always the same. Moreover, these effects can not be translated 
+always the same. Moreover, these effects cannot be translated 
 into linear bounded automata (LBA) either, which equivalents to 

### 2022-06-16 paper/tv.tex
m

@@
 \code{\pi} is not satisfied, whereas  \code{\pi?} waits until \code{\pi} is satisfied.}. 
-To make the specification more expressive, events can also be 
+To make the specification more practical, events can also be 
 {\anynotevent{A}}, referring to those events which are not 

### 2022-06-16 paper/Response.md
m

# OVERVIEW:

Many thanks to our reviewers for their interest 
and appreciation of certain aspects of our work.

We acknowledge our weaknesses upon related work and evaluations. 
Thanks again for the time and effort in pointing out our typos 
and giving out constructive suggestions.

We took all the valuable comments into account and made the 
following change list.

# CHANGE LIST:

| | Changes     | Description | Timeline (Working days)    |
| ---  | ----------- | ----------- | ----------- |
|1 | Typos       | Mentioned in the reviews  | Already Done| 
|2 | Related work | [Song & Chin 2020]  | 5 days (Partly done in by responding to our Reviewers) |
|3 | Evaluation data | Have a table detailing summary statistics | 5-10 days |
|4 | Writing polishing | Find a buddy to check the writings | 5 days | 
|  | In total  | | 15 - 20 days

Other minor adjustments below can be done within a couple of days :

- Drop the organization paragraph;

In total, we plan to finish all the changes within one month.

# RESPONSE:

## To Reviewer A

### Q1. Was there any actual comparison with another tool (e.g. PAT)?

### Q2. Where do the models come from? Do the authors plan to make their tool and experiments publicly available? (e.g. as part as an artifact)

### Q3. Does this mean that the time is discrete, or does this mean that the time bounds are integer-valued (while time can still be continuous)?
Time is continuous. The current implementation makes use of SMT in 
integer numbers domain.
It is not hard to adapt it into real numbers given the suitable SMT solver.

### Q4. I find the event name Sugar slightly misleading: if this denotes the completion of the sugar addition phase, perhaps EndSugar would be more appropriate? 
`Sugar` denotes the completion of the sugar addition phase, we will change it to `EndSugar`. Thanks!

### Q5. "our effects provide more detailed information than traditional timed verification, and in fact, it cannot be fully captured by any prior works " This requires some discussion, and does not seem obvious to me, especially when compared with Uppaal.

Using the example $\Phi_{addNSuggar(n)} = n{<}3 \wedge n{=}t \wedge Sugar\# t $, 
there are two main advantages shown comparing the proposed Effects with timed-automata based modelling:
1. The time-bounds can be depended on the function inputs. The specifications are dynamically instantiated 
during the execution. 
2. the time-bounds can be a range of values (possibly an infinite set). In this example, Sugar\# t is an integration of Sugar\# 0 or Sugar\# 1 or Sugar\# 2.

### Q6. why isn't there any rule that "gets rid of" deadline?

Yes there is, we omitted it for a better presentation.

### Q7. Section 3.4: is the notation [[\pi]]_s defined?

$\llbracket {\pi} \rrbracket_s {=}  
{True}$ stands that: with the current stack state $s$,
the arithmetic constraint ${\pi}$ holds.

### Q8. "We validate the front-end forward verifier against the state-of-the-art PAT" This does not seem to appear in the experiments.

Sorry about the confusion. The validation here refers 
to the correctness of our forward verifier. The 
experiments is about the efficiency of our implementation.

## To Reviewer B

### Q1. The significant overlap with the work in [Song & Chin 2020].

The major overlapping parts are:
1. they both integrate arithmetic constraints with 
extended regular expressions. 
2. they both support dependent values.
3. they both deploy term rewriting systems (TRS) as the back-end solvers.

However, we argue that the differences are MORE THAN  `just applied to different programming languages`.

(I) First of all, the detailed designs and the 
purposes of the designs are rather different:

In [Song & Chin 2020], $\Phi_{send(n)} = n{<}5 \wedge Send^n$ stands 
for the specification of function $send(n)$, which emits the event 
$Send$ $n$ times.
As in $\Phi_{send(1)} = 1{<}5 \wedge Send$, or 
$\Phi_{send(3)} = 3{<}5 \wedge Send{\cdot}Send{\cdot}Send$. 
However, in current work: $\Phi_{send(n)} = n{<}5 \wedge Send \# n$
stands for the function $send(n)$ emits the event 
$Send$ ONCE, but the time of emitting $Send$ has a upper 
bound 5. This difference can be spotted in the specification semantics models of each paper  
(Fig. 7 in current paper vs. Fig. 4 in [Song & Chin 2020]).

(II) Secondly, apart from the dependent values, 
in current work, the specification supports $\pi?$ (stands for a blocking waiting for a certain 
constraint to be satisfied) and the concurrency constructor || 
(cf Fig. 6). These are generally essential 
in timed verification (or more generally, for asynchronous programming), 
which are simply not supported in [Song & Chin 2020].

(III) Thirdly, if the TRS in [Song & Chin 2020] wished to 
support the inclusion checking 
of $TimEffs$ in this work, it needs to deal 
with the different semantics of the logic and extra operators. 
These achievements are considered to be the contributions 
of the TRS in the current paper. The detailed technical differences 
can be spotted in the rewriting rules in each paper (Sec. 5 in current paper vs. Sec. 5 in [Song & Chin 2020]).

Lastly, we acknowledge that our current work is an extensions 
of [Song & Chin 2020], and we sincerely thank our reviews of pointing 
it out, which should have explained better in the submission.

### +P1: The code in Fig. 1 says (I think) that addNSugar will emit the event Sugar after at least n time units. But the text (lines 63-68) seems to indicate that n portions of Sugar will be added, ie Sugar will be emitted n times.

## To Reviewer C

### Q1. Which aspects of

### 2022-06-16 paper/Response.md
m

@@
 
-Yes there is, we omitted it for a better presentation.
+It should have. We will need to add a rule where 
+e reduced to a value within the deadline. Then we can "gets rid of" the deadline.
 
@@
 ### +P1: The code in Fig.
-1 says (I think) that addNSugar will emit the event Sugar after at least n time units.
+1 says that addNSugar will emit the event Sugar after at least n time units.
 But the text (lines 63-68) seems to indicate that n portions of Sugar will be added, ie Sugar will be emitted n times.
+
+Event `Sugar` denotes the completion of the whole sugar addition phase (which adds n portions of Sugar in total). 
+We will change `Sugar` to `EndSugar` (as suggested by our review A) and revise the explanations.
+
+### +P2: line 90 “valid traces \Phi' … why “valid”? I thought that \Phi' is the specification of the program. Are some traces invalid? If so, where is the term "invalid trace" defined?
+
+$\Phi^\prime$ indeed is the specification of the program. In another word, 
+it is an over-approximation (or superset per se) of all the desired/expected behaviours. 
+We consider any unexpected traces  are `invalid`.
+
+### P4 line 312, you are talking of assignments \alpha^*, but you do not define them anywhere.
+
+$\alpha$ is defined in Fig. 5 (assignment), and $\alpha^*$ is a list of $\alpha$.
+
+### +P5 line 318. What happens if e does not terminate on time? Does the program abort?
+
+Like other modeling languages, the timed constructs 
+are used in a abstract modeling way, where e must terminate 
+before the deadline. If e is possibly go beyond the deadline, it should 
+be modelled using conditionals where the other possibilities are explicitly modeled.
+
+### +P6 line 320 “potentially allows efficient clock manipulation”. I am not clear what you mean. Where does this clock manipulation happen?
+
+This comes from the context of how people usually make uses of the timed automata. 
+For example, to use the model checker Uppaal, uses need to draw the automata 
+themselves, including the clock naming, clock constrains annotation, 
+transition constrains annotation. And this process most likely is not the most 
+efficient way of manipulating the clocks, which leads to redundant clocks/constrains or bugs.
+
+### +P7 line 346, rule $[tot_1]$ should the conclusion say $(V, e_1’)$ rather than $(V, e’)$?
+
+That's right, sorry about the confusion and thanks for pointing it out. Already fixed.
+
+### +P8 line 360. Are we missing a rule to eliminate $\textbf{deadline}$ when the execution of $e$ hs terminated and the deadline has not been reached.
+
+That's right. We will need to add a rule where e reduced to a value within the deadline.
+
+### +P9 How do you express, eg the behaviour of two consecutive delays?
+
+As you mentioned, it should be the case of: 
+$(V,\textbf{delay}\ t_1; \textbf{delay}\ t_2)  \rightarrow^{t_1+t_2} (V, ())$
+
+This is achieved by applying the sequence rules $[seq_1]$ and $[seq_2]$ and delay
+rules $[delay_1]$ and $[delay_2]$ in a certain order.
+
+### +P10 Make sure that the definitions of $d$, $s$, $\phi$ appear before Fig.
+7.
+The page break make mw wonder whether these were defined anywhere.
+Moreover, I think you should replace $\triangleq$ in line 444, with $:$.
+Namely $d$ is one natural number, not the set of natural numbers.
+
+Thanks! Already fixed accordingly.
+
+### +P11 I think the definition on line 430 is badly formed when $\pi$ is not satisfied -- ie non terminating recursion.
+
+I am not sure if I understood the question correctly. 
+Line 430 is $d, s, \varphi \models {\pi} \wedge \pi_1 ? es$,
+and when $\pi_1$ is not satisfied at time $d$, it will continue
+to block the execution till $\pi_1$ is satisfied. 
+If $\pi_1$ is never satisfied,  $es$ will be eventually abandoned.
+
+### +P12 Fig.
+7 I think some cases are missing: How is the judgement defined for $\textbf{A}(\nu, \alpha^*)$, or for $\tau (\pi)$.
+Also, what is $es$?
+Does it stand for $\theta$.
+I wonder whether the RHS on Lines 431-433 belong to the LHS on line 430.
+
+$\textbf{A}(\nu, \alpha^*)$, $\tau (\pi)$, $\overline{A}$ and  $\_$ are possible constructors 
+of $ev$ (cf Fig. 6). So the corresponding case is in line 423 for $\pi \wedge ev$.
+
+And es is for  $\theta$, it supposed to be `\es` in our latex writing. Sorry! Fixed already.
+
+To define the LHS of 431, it includes all the RHS from lines 431 - 434.
+
+### +P14 line 470, I think you also need to say that $\{\pi_i,\theta_i\}\in\{\Pi,\Theta\}$
+
+Fixed, thanks!
+
+### +P15 Lines 505-509.
+I think the definition does not take into consideration that it is possible for $e_1$ to execute and apply some side-effects to the $V$, then for $d$ to be exceeded before $e_1$ terminates, and then we continue with $e_2$.
+I think the rule needs to consider the side-effects of the incomplete $e_1$ too.
+
+There is no possible incompletion of $e_1$ in timeout. 
+Informally, in process $e_1$ timeout[𝑑] $e_2$, the first 
+observable event of
+$e_1$ shall occur before d time units elapse 
+(since the process starts). Otherwise, $e_2$ takes over control
+after exactly 𝑑 time units elapse.
+
+So it's either $e_1$ or $e_2$ to be executed. The formal semantics can 
+be found in $[to_1]$ to $[to_4]$ (on top of the page 8).
+
+### +P16
+
+### +P18 Is there a definition of when $\Phi \sqsubseteq \Phi’$ is valid?
+
+Definition 2.2 (TimEffs Inclusion), at line 211.
+
+### +P19 Can you describe the 16 $C^t$ programs used in the benchmark in section 6?
 

### 2022-06-16 paper/tv.tex
m

@@
 
+Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
+the effects \code{\effect} take \code{d} time units to complete; 
+the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
+temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
+from the following concrete domains: \code{d}  :\  \code{\mathbb{N}}, 
+\code{s}  :\  \code{var {\rightarrow} val } and \code{\varphi}   :\ \code{\es} \ .
+
 \begin{figure}[!ht]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge \pi_1 ? es}  &\m{iff}\quad & 
+&\code{d, s, \varphi \models {\pi} \wedge \pi_1 ? \es}  &\m{iff}\quad & 
 \code{\llbracket \pi_1  \rrbracket_{s} {=}  
- {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge es}\ or  \ 
+ {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge \es}\ or  \ 
   \code{\llbracket \pi_1 \rrbracket_{s} {=}  
 {False} }, 
-\  \code{d, s, \varphi \models {\pi} \wedge \pi_1 ? es}\\
+\  \code{d, s, \varphi \models {\pi} \wedge \pi_1 ? \es}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi}  \wedge es\mysharp  t}  &\m{iff}\quad &
+&\code{d, s, \varphi \models {\pi}  \wedge \es\mysharp  t}  &\m{iff}\quad &
  \code{\llbracket {\pi}  \wedge t {=} 0 \rrbracket_{s} {=}  
@@
 {True} }, 
-\  \exists \code{\es_1,\es_2}. \  \code{\es_1  \cdot  \es_2 {=} es}, \  \m{fresh}\ t_1, t_2,\\
+\  \exists \code{\es_1,\es_2}. \  \code{\es_1  \cdot  \es_2 {=} \es}, \  \m{fresh}\ t_1, t_2,\\
 &&& \qquad  s.t. \ \code{d, s, \varphi {\models} {(\pi 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi}\wedge es^\star}  &\m{iff}\quad & 
+&\code{d, s, \varphi \models {\pi}\wedge \es^\star}  &\m{iff}\quad & 
 \code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or \ 
-\code{d, s, \varphi \models {\pi}  \wedge es  \cdot  es^\star}\\
+\code{d, s, \varphi \models {\pi}  \wedge \es  \cdot  \es^\star}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{figure}
-
-Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
-the effects \code{\effect} take \code{d} time units to complete; 
-the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
-temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
-from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{N}}, 
-\code{s}  \defeq\  \code{var {\rightarrow} val } and \code{\varphi}   \defeq\ \code{\es} \ .
 
@@
 \vspace{2mm}
-\qquad\qquad\quad \code{\s{ \Pi^\prime, \Theta^\prime } = 
+\qquad \code{\s{ \Pi^\prime, \Theta^\prime } = 
 \wbigcup_{i{=}0}^{|\s{ \Pi, \Theta }| \text{-} 1}  
-\s{\pi_i^\prime, \es_i^\prime} \ \ where\ \ 
+\s{\pi_i^\prime, \es_i^\prime}  \ \ where\ \ \code{
+  \s{\pi_i, \es_i} {\in} \s{ \Pi^\prime, \Theta^\prime }
+}  \ \m{and} \ 
  \vdash  \s{\pi_i, \es_i} \ e \ \s{\pi_i^\prime, \es_i^\prime}.} 
@@
       \\
-      \s{\Theta_f, \Pi_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (hd(\Theta_1)\mysharp t \cdot tl(\Theta_1))}
+      \s{\Pi_f, \Theta_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (hd(\Theta_1)\mysharp t \cdot tl(\Theta_1))}
       \cup 

### 2022-06-16 paper/Response.md
m

@@
 |3 | Evaluation data | Have a table detailing summary statistics | 5-10 days |
-|4 | Writing polishing | Find a buddy to check the writings | 5 days | 
+|4 | Paper polishing | Find a buddy to check the writings | 5 days | 
 |  | In total  | | 15 - 20 days
@@
 
+## Common Questions Upon the Evaluation
+
+### Q1. Where do the models come from?
+
+The evaluation benchmark (16 selected programs) was created by ourselves. 
+We developed a set of testing programs (~70 programs) during the development process.
+The testing programs were designed in a functionality-oriented way, where each 
+forward rules in Sec. 4.1 has 3-8 testing testing programs. The rest ~20 programs 
+are mixed combinations of different constructs and some stress tests.
+
+Our selected programs were from the last ~20 programs varying from lines of code.
+
+### Q2. We like to explain why not choosing existing benchmarks:
+
+Model checkers like Uppaal take timed automata directly as their inputs, 
+which is not feasible for our tool.
+
+Model checkers like PAT take timed process algebras as their inputs are more 
+feasible. We indeed included some tests from their examples into our tests, 
+such as the Fischer’s Mutual Exclusion Protocol (cf Fig. 4).
+But they do not support value dependent bounds in their timed behavioral patterns.
+However, we take the `value dependent bounds` to be one of our main novelties, therefore 
+most programs in our benchmark are created ourselves, and 
+have value dependent time bounds.
+
+### Q3. What kinds of specifications you check and comparison with PAT?
+
+All the specifications are with value-depended constructors. 
+For each program, the very first specification is its strongest postcondition 
+(which should be valid). Then we derived the rest specifications by 
+adding various mutations (or mixture of the mutations) into the strongest postcondition, such as: 
+disjunctions, negation of certain events, modification of the clock constraints, 
+inserting parallel traces etc.
+
+For the programs we included from PAT benchmark, we validate the verification 
+results against PAT implementation (as in given the same logic model and the same 
+specification, our tool and PAT return the same verification results). 
+For the rest  specifications, we manually label the expected verification results. 
+And all the results presented in Table. 3 were as expected.
+
+### Q4. Do the authors plan to make their tool and experiments publicly available?
+
+Yes. In fact the source code is open sourced now. We 
+plan to release the benchmark after further documentation.
+
 ## To Reviewer A
 
-### Q1. Was there any actual comparison with another tool (e.g. PAT)?
-
-### Q2. Where do the models come from? Do the authors plan to make their tool and experiments publicly available? (e.g. as part as an artifact)
-
-### Q3. Does this mean that the time is discrete, or does this mean that the time bounds are integer-valued (while time can still be continuous)?
+### Q1. Does this mean that the time is discrete, or does this mean that the time bounds are integer-valued (while time can still be continuous)?
 Time is continuous. The current implementation makes use of SMT in 
@@
 
-### Q4. I find the event name Sugar slightly misleading: if this denotes the completion of the sugar addition phase, perhaps EndSugar would be more appropriate? 
+### Q2. I find the event name Sugar slightly misleading: if this denotes the completion of the sugar addition phase, perhaps EndSugar would be more appropriate? 
 `Sugar` denotes the completion of the sugar addition phase, we will change it to `EndSugar`. Thanks!
 
-### Q5.
+### Q3.
 "our effects provide more detailed information than traditional timed verification, and in fact, it cannot be fully captured by any prior works " This requires some discussion, and does not seem obvious to me, especially when compared with Uppaal.
@@
 
-### Q6. why isn't there any rule that "gets rid of" deadline?
+### Q4. why isn't there any rule that "gets rid of" deadline?
 
@@
 
-### Q7. Section 3.4: is the notation [[\pi]]_s defined?
+### Q5. Section 3.4: is the notation [[\pi]]_s defined?
 
@@
 
-### Q8. "We validate the front-end forward verifier against the state-of-the-art PAT" This does not seem to appear in the experiments.
+### Q6. "We validate the front-end forward verifier against the state-of-the-art PAT" This does not seem to appear in the experiments.
 
@@
 
-### +P19 Can you describe the 16 $C^t$ programs used in the benchmark in section 6?
-
 ## To Reviewer C
 
-### Q1. Which aspects of
+### Q1. Please comment on the related work I cite.
+
+### Q2. Please comment on some of the technical questions I raised
+
+(why talk about trace leading to a method in preconditions, 
+are quantified Presburger conditions used in your benchmarks?)
+
+Can't you not express loop invariants using specifications and reason with programs using verification conditions written for iteration-free code snippets, like in Floyd-style verification?
+
+### Q3. Do you capture the strongest post?
+
+Yes, it is meant to capture the strongest post.
+
+### Q4. Are there any relative completeness results that you can show that narrow the space where your reasoning is incomplete?
+
+### Q5. Can you give some (simple) examples where your technique does not work?

### 2022-06-16 paper/Response.md
m

@@
 |1 | Typos       | Mentioned in the reviews  | Already Done| 
-|2 | Related work | [Song & Chin 2020]  | 5 days (Partly done in by responding to our Reviewers) |
-|3 | Evaluation data | Have a table detailing summary statistics | 5-10 days |
+|2 | Related work | [Song & Chin 2020]  | 5 days (Partly done in the response) |
+|3 | Evaluation data | Add more detailed explanations for the evaluation and make the benchmark and documentation public | 5-10 days |
 |4 | Paper polishing | Find a buddy to check the writings | 5 days | 
 |  | In total  | | 15 - 20 days
-
-Other minor adjustments below can be done within a couple of days :
-
-- Drop the organization paragraph;
 
@@
 
-## Common Questions Upon the Evaluation
+###  Common Questions Upon the Evaluation
 
-### Q1. Where do the models come from?
+#### Q1. Where do the models come from?
 
@@
 
-### Q2. We like to explain why not choosing existing benchmarks:
+#### Q2. We like to explain why not choosing existing benchmarks:
 
@@
 
-### Q3. What kinds of specifications you check and comparison with PAT?
+#### Q3. What kinds of specifications you check and any comparisons with PAT?
 
@@
 
-### Q4. Do the authors plan to make their tool and experiments publicly available?
+#### Q4. Do the authors plan to make their tool and experiments publicly available?
 
@@
 
-## To Reviewer A
+---
 
-### Q1. Does this mean that the time is discrete, or does this mean that the time bounds are integer-valued (while time can still be continuous)?
+###  To Reviewer A
+
+Many thanks for pointing out the related works. We will be checking them 
+out and add comparisons accordingly.
+
+#### Q1. Does this mean that the time is discrete, or does this mean that the time bounds are integer-valued (while time can still be continuous)?
 Time is continuous. The current implementation makes use of SMT in 
@@
 
-### Q2. I find the event name Sugar slightly misleading: if this denotes the completion of the sugar addition phase, perhaps EndSugar would be more appropriate? 
+#### Q2. I find the event name Sugar slightly misleading: if this denotes the completion of the sugar addition phase, perhaps EndSugar would be more appropriate? 
 `Sugar` denotes the completion of the sugar addition phase, we will change it to `EndSugar`. Thanks!
 
-### Q3.
+#### Q3.
 "our effects provide more detailed information than traditional timed verification, and in fact, it cannot be fully captured by any prior works " This requires some discussion, and does not seem obvious to me, especially when compared with Uppaal.
@@
 
-### Q4. why isn't there any rule that "gets rid of" deadline?
+#### Q4. why isn't there any rule that "gets rid of" deadline?
 
@@
 
-### Q5. Section 3.4: is the notation [[\pi]]_s defined?
+#### Q5. Section 3.4: is the notation [[\pi]]_s defined?
 
@@
 
-### Q6. "We validate the front-end forward verifier against the state-of-the-art PAT" This does not seem to appear in the experiments.
+#### Q6. "We validate the front-end forward verifier against the state-of-the-art PAT" This does not seem to appear in the experiments.
 
@@
 
-## To Reviewer B
+---
 
-### Q1. The significant overlap with the work in [Song & Chin 2020].
+###  To Reviewer B
+
+#### Q1. The significant overlap with the work in [Song & Chin 2020].
 
@@
 
-### +P1: The code in Fig.
+#### +P1: The code in Fig.
 1 says that addNSugar will emit the event Sugar after at least n time units.
@@
 
-### +P2: line 90 “valid traces \Phi' … why “valid”? I thought that \Phi' is the specification of the program. Are some traces invalid? If so, where is the term "invalid trace" defined?
+#### +P2: line 90 “valid traces \Phi' … why “valid”? I thought that \Phi' is the specification of the program. Are some traces invalid? If so, where is the term "invalid trace" defined?
 
@@
 
-### P4 line 312, you are talking of assignments \alpha^*, but you do not define them anywhere.
+#### P4 line 312, you are talking of assignments \alpha^*, but you do not define them anywhere.
 
@@
 
-### +P5 line 318. What happens if e does not terminate on time? Does the program abort?
+#### +P5 line 318. What happens if e does not terminate on time? Does the program abort?
 
@@
 
-### +P6 line 320 “potentially allows efficient clock manipulation”. I am not clear what you mean. Where does this clock manipulation happen?
+#### +P6 line 320 “potentially allows efficient clock manipulation”. I am not clear what you mean. Where does this clock manipulation happen?
 
@@
 
-### +P7 line 346, rule $[tot_1]$ should the conclusion say $(V, e_1’)$ rather than $(V, e’)$?
+#### +P7 line 346, rule $[tot_1]$ should the conclusion say $(V, e_1’)$ rather than $(V, e’)$?
 
@@
 
-### +P8 line 360. Are we missing a rule to eliminate $\textbf{deadline}$ when the execution of $e$ hs terminated and the deadline has not been reached.
+#### +P8 line 360. Are we missing a rule to eliminate $\textbf{deadline}$ when the execution of $e$ hs terminated and the deadline has not been reached.
 
@@
 
-### +P9 How do you express, eg the behaviour of two consecutive delays?
+#### +P9 How do you express, eg the behaviour of two consecutive delays?
 
@@
 
-### +P10 Make sure that the definitions of $d$, $s$, $\phi$ appear before Fig.
+#### +P10 Make sure that the definitions of $d$, $s$, $\phi$ appear before Fig.
 7.
@@
 
-### +P11 I think the definition on line 430 is badly formed when $\pi$ is not satisfied -- ie non terminating recursion.
+#### +P11 I think the definition on line 430 is badly formed when $\pi$ is not satisfied -- ie non terminating recursion.
 
@@
 
-### +P12 Fig.
+#### +P12 Fig.
 7 I think some cases are missing: How is the judgement defined for $\textbf{A}(\nu, \alpha^*)$, or for $\tau (\pi)$.
@@
 
-### +P14 line 470, I think you also need to say that $\{\pi_i,\theta_i\}\in\{\Pi,\Theta\}$
+#### +P14 line 470, I think you also need to say that $\{\pi_i,\theta_i\}\in\{\Pi,\Theta\}$
 
@@
 
-### +P15 Lines 505-509.
+#### +P15 Lines 505-509.
 I think the definition does not take into consideration that it is possible for $e_1$ to execute and apply some side-effects to the $V$, then for $d$ to be exceeded before $e_1$ terminates, and then we continue with $e_2$.
@@
 
-### +P16
-
-### +P18 Is there a definition of when $\Phi \sqsubseteq \Phi’$ is valid?
+#### +P18 Is there a definition of when $\Phi \sqsubseteq \Phi’$ is valid?
 
@@
 
-## To Reviewer C
+---
 
-### Q1. Please comment on the related work I cite.
+###  To Reviewer C
 
-### Q2. Please comment on some of the technical questions I raised
+#### Q1. Please comment on the related work I cite.
 
-(why talk about trace leading to a method in preconditions, 
-are quantified Presburger conditions used in your benchmarks?)
+Specification of real-time and hybrid systems in rewriting logic, by Olveczky and Meseguer.
 
-Can't you not express loop invariants using specifications and reason with programs using verification conditions written for iteration-free code snippets, like in Floyd-style verification?
+Specification and Analysis of Real-Time and Hybrid Systems in Rewriting Logic - Olveczky (PhD thesis) 
+See also: Verification of clocked and hybrid systems- Kesten, Manna, Pnueli
 
-### Q3. Do you capture the strongest post?
+You are also missing references to work done by Cook and Koskinen and others on LTL/CTL verification of programs, which also include reductions to standard Hoare-style verification.
 
-Yes, it is meant to capture the strongest post.
+#### Q2. Please comment on some of the technical questions I raised
 
-### Q4. Are there any relative completeness results that you can show that narrow the space where your reasoning is incomplete?
+1. I find it strange that you don't have iterative loops. Why is that?
 
-### Q5. Can you give some (simple) examples where your technique does not work?
+The language allows each iterative
+loop to be optimized to an equivalent tail-recursive method, where mutation
+on parameters is made visible to the caller. The technique of translating away
+iterative loops is standard and is helpful in further minimising our core language.
+
+2. Why talk about trace leading to a method in preconditions?
+
+We politely disagree upon the opinion mentioned in the review: 
+`While verification of a method does depend on the values of variables at the time it's called, the events that happened earlier seem irrelevant.`
+
+Just like particular requirements of the input values, there are possible 
+requirements upon the history traces. 
+For example, before reading a file, we wish to make sure the file was actually opened 
+(and not yet closed) is the history. This can be written in precondition as:
+$\Phi_{pre} = \_^\star {\cdot} Open {\cdot} ({\overline{Close}})^\star $. 
+Such examples extend to the timed processes in different contexts.
+
+3. Are quantified Presburger conditions used in your benchmarks?
+
+We do not have quantified Presburger conditions in current benchmarks. 
+Indeed 'Purely universal quantification' better describes our implementation. 
+(Although having TRS solving quantified Presburger conditions with traces seems 
+useful and challenging.)
+
+#### Q3. Do you capture the strongest post?
+
+To be precise, it only captures the 'strongest over-approximation'.
+
+The forward verifier creates over-approximation when there are conditionals 
+(cf [FV-If-Else-Local] on top of page 11).
+
+For example, $\Phi_{post}{=} (n {>} 0 \wedge A{\cdot}B)  \vee (n {\leq} 0 \wedge C{\cdot}D)$
+
+Therefore in theorem 4.1,
+if we have $\{P\}\ e\ \{Q\}$ 
+ we can only say there exists a post in Q which captures the 
+actual execution.
+
+#### Q4. Are there any relative completeness results that you can show that narrow the space where your reasoning is incomplete?
+#### Q5. Can you give some (simple) examples where your technique does not work?
+
+We like to answer Q4 and Q5 together.
+
+For example, while proving this following (expected to be valid) inclusion: 
+$ t_1 {<}3 {\wedge} t_2 {<}4 {\wedge}  (\epsilon \# t_1) {\cdot} (\epsilon \# t_2) 
+\sqsubseteq  t {<}7 {\wedge} (\epsilon \# t)$
+
+The current rewriting would simple unify $t_1$ and $t$ leaving $t_2$ behind, which 
+leads to the next step:
+
+$ t_2 {<}4 {\wedge}  (\epsilon \# t_2) 
+\sqsubseteq   \epsilon $, then eliminate $(\epsilon \# t_2) $ from the both side, 
+leads to the next step:
+
+$True {\wedge} \epsilon \sqsubseteq   \bot$, then disproves this inclusion.
+
+This can be solved by adding an axiom: $(\epsilon \# t_1) {\cdot} (\epsilon \# t_2) = 
+(\epsilon \# (t_1{+}t_2))$. 
+However, we did not include it because it seems to be leading to other incomplete situations.
+
+#### Q6. Am I reading it correctly that your system is able to prove all valid properties and disprove all invalid ones?
+Yes. cf  Q3 in `Common Questions Upon the Evaluation`.

### 2022-06-16 paper/Response.md
m

@@
 
-We acknowledge our weaknesses upon related work and evaluations. 
+We acknowledge our weaknesses in related work and evaluations. 
 Thanks again for the time and effort in pointing out our typos 
-and giving out constructive suggestions.
+and giving constructive suggestions.
 
-We took all the valuable comments into account and made the 
+We considered all the valuable comments and made the 
 following change list.
@@
 |1 | Typos       | Mentioned in the reviews  | Already Done| 
-|2 | Related work | [Song & Chin 2020]  | 5 days (Partly done in the response) |
+|2 | Related work | Further compare our work with i) other rewriting systems for timed verification; ii) dynamic clock manipulations for timed automata, and iii) [Song & Chin 2020].
+| 5 days (Partly done in the response) |
 |3 | Evaluation data | Add more detailed explanations for the evaluation and make the benchmark and documentation public | 5-10 days |
@@
 The evaluation benchmark (16 selected programs) was created by ourselves. 
-We developed a set of testing programs (~70 programs) during the development process.
-The testing programs were designed in a functionality-oriented way, where each 
-forward rules in Sec. 4.1 has 3-8 testing testing programs. The rest ~20 programs 
+We developed a set of testing programs (~70) during the development process.
+The testing programs were designed functionality-oriented, where each 
+forward rule in Sec. 4.1 has 3-8 testing programs. The rest ~20 programs 
 are mixed combinations of different constructs and some stress tests.
@@
 
-#### Q2. We like to explain why not choosing existing benchmarks:
+#### Q2. We like to explain why not to choose existing benchmarks:
 
@@
 Model checkers like PAT take timed process algebras as their inputs are more 
-feasible. We indeed included some tests from their examples into our tests, 
+feasible. We indeed included some tests from their examples in our tests, 
 such as the Fischer’s Mutual Exclusion Protocol (cf Fig. 4).
-But they do not support value dependent bounds in their timed behavioral patterns.
-However, we take the `value dependent bounds` to be one of our main novelties, therefore 
-most programs in our benchmark are created ourselves, and 
-have value dependent time bounds.
+But they do not support value-dependent bounds in their timed behavioral patterns.
+However, we take the `value-dependent bounds` as one of our main novelties. Therefore 
+most programs in our benchmark are created ourselves and 
+have value-dependent time bounds.
 
-#### Q3. What kinds of specifications you check and any comparisons with PAT?
+#### Q3. What kinds of specifications do you check and any comparisons with PAT?
 
@@
 (which should be valid). Then we derived the rest specifications by 
-adding various mutations (or mixture of the mutations) into the strongest postcondition, such as: 
-disjunctions, negation of certain events, modification of the clock constraints, 
+adding various mutations (or a mixture of the mutations) into the strongest postcondition, such as: 
+disjunctions, the negation of certain events, modification of the clock constraints, 
 inserting parallel traces etc.
 
-For the programs we included from PAT benchmark, we validate the verification 
+For the programs we included from the PAT benchmark, we validate the verification 
 results against PAT implementation (as in given the same logic model and the same 
@@
 For the rest specifications, we manually label the expected verification results. 
-And all the results presented in Table. 3 were as expected.
+And all the results are presented in Table. 3 were as expected.
 
-#### Q4. Do the authors plan to make their tool and experiments publicly available?
+#### Q4. Do the authors plan to make their tools and experiments publicly available?
 
-Yes. In fact the source code is open sourced now. We 
+Yes. The source code is open-sourced now. We 
 plan to release the benchmark after further documentation.
@@
 integer numbers domain.
-It is not hard to adapt it into real numbers given the suitable SMT solver.
+Given the suitable SMT solver, it is not hard to adapt it to real numbers.
 
 #### Q2. I find the event name Sugar slightly misleading: if this denotes the completion of the sugar addition phase, perhaps EndSugar would be more appropriate? 
-`Sugar` denotes the completion of the sugar addition phase, we will change it to `EndSugar`. Thanks!
+`Sugar` denotes the completion of the sugar addition phase; we will change it to `EndSugar`. Thanks!
 
 #### Q3.
-"our effects provide more detailed information than traditional timed verification, and in fact, it cannot be fully captured by any prior works " This requires some discussion, and does not seem obvious to me, especially when compared with Uppaal.
+"our effects provide more detailed information than traditional timed verification, and in fact, it cannot be fully captured by any prior works " This requires some discussion and does not seem obvious to me, especially when compared with Uppaal.
 
@@
 there are two main advantages shown comparing the proposed Effects with timed-automata based modelling:
-1. The time-bounds can be depended on the function inputs. The specifications are dynamically instantiated 
+1. The time bounds can be depended on the function inputs. The specifications are dynamically instantiated 
 during the execution. 
@@
 
-It should have. We will need to add a rule where 
-e reduced to a value within the deadline. Then we can "gets rid of" the deadline.
+It should have. We need to add a rule where 
+e is reduced to a value within the deadline. Then we can "get rid of" the deadline.
 
@@
 to the correctness of our forward verifier. The 
-experiments is about the efficiency of our implementation.
+experiment is about the performance of our implementation.
 
@@
 
-#### Q1. The significant overlap with the work in [Song & Chin 2020].
+#### Q1. The a significant overlap with the work in [Song & Chin 2020].
 
@@
 (cf Fig. 6). These are generally essential 
-in timed verification (or more generally, for asynchronous programming), 
-which are simply not supported in [Song & Chin 2020].
+in timed verification (or, more generally, for asynchronous programming), 
+which are not supported in [Song & Chin 2020].
 
@@
 of the TRS in the current paper. The detailed technical differences 
-can be spotted in the rewriting rules in each paper (Sec. 5 in current paper vs. Sec. 5 in [Song & Chin 2020]).
+can be spotted in the rewriting rules in each paper (Sec. 5 in the current paper vs. Sec. 5 in [Song & Chin 2020]).
 
-Lastly, we acknowledge that our current work is an extensions 
-of [Song & Chin 2020], and we sincerely thank our reviews of pointing 
-it out, which should have explained better in the submission.
+Lastly, we acknowledge that our current work is an extension 
+of [Song & Chin 2020], and we sincerely thank our reviews for pointing 
+it out, which should have been explained better in the submission.
 
@@
 1 says that addNSugar will emit the event Sugar after at least n time units.
-But the text (lines 63-68) seems to indicate that n portions of Sugar will be added, ie Sugar will be emitted n times.
+But the text (lines 63-68) indicates that n portions of Sugar will be added, i.e., Sugar will be emitted n times.
 
@@
 
-$\Phi^\prime$ indeed is the specification of the program. In another word, 
-it is an over-approximation (or superset per se) of all the desired/expected behaviours. 
+$\Phi^\prime$ indeed is the specification of the program. In other words, 
+it is an over-approximation (or superset per se) of all the desired/expected behaviors. 
 We consider any unexpected traces are `invalid`.
@@
 Like other modeling languages, the timed constructs 
-are used in a abstract modeling way, where e must terminate 
-before the deadline. If e is possibly go beyond the deadline, it should 
-be modelled using conditionals where the other possibilities are explicitly modeled.
+are used in an abstract modeling way, where e must terminate 
+before the deadline. If e possibly goes beyond the deadline, it should 
+be modeled using conditionals where the other possibilities are explicitly modeled.
 
@@
 
-This comes from the context of how people usually make uses of the timed automata. 
-For example, to use the model checker Uppaal, uses need to draw the automata 
+This comes from the context of how people usually make use of the timed automata. 
+For example, to use the model checker Uppaal, users need to draw the automata 
 themselves, including the clock naming, clock constrains annotation, 
 transition constrains annotation. And this process most likely is not the most 
-efficient way of manipulating the clocks, which leads to redundant clocks/constrains or bugs.
+efficient way of manipulating the clocks, which leads to redundant clocks/constraints or bugs.
 
@@
 
-That's right, sorry about the confusion and thanks for pointing it out. Already fixed.
+That's right; sorry about the confusion, and thanks for pointing it out. It is already fixed.
 
-#### +P8 line 360. Are we missing a rule to eliminate $\textbf{deadline}$ when the execution of $e$ hs terminated and the deadline has not been reached.
+#### +P8 line 360. Are we missing a rule to eliminate $\textbf{deadline}$ when the execution of $e$ is terminated, and the deadline has not been reached?
 
@@
 
-Specification of real-time and hybrid systems in rewriting logic, by Olveczky and Meseguer.
+[1] Deductive Verification of Real-Time Systems Using STEP, by Bjorner, Manna, Sipma, Uribe proposes
+[2] Specification of real-time and hybrid systems in rewriting logic, by Olveczky and Meseguer.
+[3] Specification and Analysis of Real-Time and Hybrid Systems in Rewriting Logic - Olveczky (PhD thesis) 
+[4] Verification of clocked and hybrid systems - Kesten, Manna, Pnueli
 
-Specification and Analysis of Real-Time and Hybrid Systems in Rewriting Logic - Olveczky (PhD thesis) 
-See also: Verification of clocked and hybrid systems- Kesten, Manna, Pnueli
+Thanks for pointing out the very related works, which used rewriting strategies to 
+solve difference problems upon different format of the logics. 
+[1,4] mention rewriting linear temporal logic formula; 
+[2,3] mention rewriting timed automata, or timed extensions of Petri net;
+and our work is rewriting extended regular expressions.
 
-You are also missing references to work done by Cook and Koskinen and others on LTL/CTL verification of programs, which also include reductions to standard Hoare-style verification.
+We think the main differences get back to the expressiveness of the logics.
+As we presented in the paper, we aim at studying more practical and expressive 
+logics, therefore it leads to the creation/rewriting of our TimEffs. 
+The dependent values and putting timed traces into the precondition are novel 
+comparing to prior works. 
+Together with the cited papers, we certainly show the applicability of 
+rewriting systems.
 

### 2022-06-18 paper/Response.md
m

@@
 Yes. cf  Q3 in `Common Questions Upon the Evaluation`.
+
+#### +P16 Theorem 4.1: You are saying “produces a concrete execution time d, and event sequence" ….
+But the operational semantics does not produce one execution time.
+Perhaps it produces a sequence of execution times and event, and then you obtain d through the sum of all execution times, and π by distilling all the events?
+I could not find the definition in the paper, but even som such a definition would allow me to distinguish important cases (eg delay(2).Sugar.delay(1).Sugar from delay(3).Sugar.Sugar).
+
+-> `Perhaps it produces a sequence of execution times and event, and then you 
+obtain d through the sum of all execution times`
+
+That' right. If we use `|-|` to denote one time unit, and `S` denotes the emission of Sugar, then
+
+delay(2).Sugar.delay(1).Sugar is 
+```
+0 1 2 3 4
+|-|-|-|-|--> d
+    S S
+```
+
+and delay(3).Sugar.Sugar is 
+```
+0 1 2 3 4
+|-|-|-|-|--> d
+      S 
+      S
+```
+
+In the semantic of effects, Fig.7 line 423, we defined the emission of a single event takes 0 time.
+
+#### +P16 Proof of Theorem 4.1. I had a look in the appendix, and have several questions
+
+a. It is not clear whether the proof is by induction on the number of steps 
+  or the shape of the expression. Looking at the proof it seems that it is by 
+  the latter, but if so the proof would not go through, because method call 
+  increases the expression.
+
+c. Proof is missing method call, and the proof of this requires,
+
+Answer for a and c:
+It is induction on the shape of the expression.
+
+Informally, the operation semantics rule for method call is:
+```
+mn(x^*)[P, Q]{e} {\in} P    
+the history traces should entail P
+e[v*/x*] ==> e'
+------------------------------- [op-call]
+(V, mn(v*)) --> (V, e')
+```
+The promise of [op-call] assumes mn(x^*) is verified, i.e., |- {P} e {Q} is valid. 
+(P, Q are the pre/post-condition of mn)
+
+The forward rule of call [FV-Call] is defined at line 520.
+
+Based on Theorem 4.1:
+Given configuration (V, mn(v*)), it equals to (V, e[v*/x*]).
+
+There are two cases:
+
+i) $\{V, \epsilon \} \in P$, by [FV-Call], 
+|- {$\{V, \epsilon \}$} e[v*/x*] {$\{V, \epsilon \} \cdot$  Q[v*/x*]}, 
+prove by induction;
+
+ii) $\{V, \epsilon \} \notin P$, both execution and forward rule got stuck.
+
+---
+
+b. The proof for timeout does not cover the case where e1​
+  started but times out, and we continue with e2
+
+This is a similar question to +P15. 
+As we have answered, the semantics of $e_1$ timeout[𝑑] $e_2$ is, 
+if the initial events (written as $hd(\Theta_1)$ in the rule $[FV\text{-}Timeout]$ at line 508) 
+of $e_1$ happened before time d, then $e_1$ continues to take the control; 
+otherwise, i.e., $e_1$ never started within time d, $e_2$ takes the control.
+
+Therefore `the case where e1​
+  started but times out, and we continue with e2` should never happen.
+
+---
+
+d. I think Theorem 5.7 Proof is missing the inductive step
+ In line 1046, the proof for the unfold is the inductive step. 
+ The rule adds the current inclusion into the hypostasis, then proves the inclusion 
+ of its derivatives.

### 2022-06-19 paper/Response.md
m

--- 2022-06-16 paper/Response.md
@@
 
-| | Changes     | Description | Timeline (Working days)    |
+| | Changes     | Description | Timeline    |
 | ---  | ----------- | ----------- | ----------- |
@@
 |2 | Related work | Further compare our work with i) other rewriting systems for timed verification; ii) dynamic clock manipulations for timed automata, and iii) [Song & Chin 2020].
-| 5 days (Partly done in the response) |
-|3 | Evaluation data | Add more detailed explanations for the evaluation and make the benchmark and documentation public | 5-10 days |
+| 3 days (Partly done in the response) |
+|3 | Evaluation data | Add more detailed explanations for the evaluation and make the benchmark and documentation public | 3-6 days |
 |4 | Paper polishing | Find a buddy to check the writings | 5 days | 
-|  | In total  | | 15 - 20 days
+|  | In total  | | 11 - 14 days
 
-In total, we plan to finish all the changes within one month.
+In total, we plan to finish all the changes within two weeks.
 
@@
 
-Using the example $\Phi_{addNSuggar(n)} = n{<}3 \wedge n{=}t \wedge Sugar\# t $, 
+Using the example $\Phi_{addNSuggar(n)} = n{<}3 \wedge n{=}t \wedge Sugar\# t$, 
 there are two main advantages shown comparing the proposed Effects with timed-automata based modelling:
@@
 (and not yet closed) is the history. This can be written in precondition as:
-$\Phi_{pre} = \_^\star {\cdot} Open {\cdot} ({\overline{Close}})^\star $. 
+$\Phi_{pre} = \_^\star {\cdot} Open {\cdot} ({\overline{Close}})^\star$. 
 Such examples extend to the timed processes in different contexts.
@@
 For example, while proving this following (expected to be valid) inclusion: 
-$ t_1 {<}3 {\wedge} t_2 {<}4 {\wedge}  (\epsilon \# t_1) {\cdot} (\epsilon \# t_2) 
+$t_1 {<}3 {\wedge} t_2 {<}4 {\wedge}  (\epsilon \# t_1) {\cdot} (\epsilon \# t_2) 
 \sqsubseteq  t {<}7 {\wedge} (\epsilon \# t)$
 
-The current rewriting would simple unify $t_1$ and $t$ leaving $t_2$ behind, which 
+The current rewriting would simple unifies $t_1$ and $t$ leaving $t_2$ behind, which 
 leads to the next step:
 
-$ t_2 {<}4 {\wedge}  (\epsilon \# t_2) 
-\sqsubseteq   \epsilon $, then eliminate $(\epsilon \# t_2) $ from the both side, 
+$t_2 {<}4 {\wedge}  (\epsilon \# t_2) \sqsubseteq   \epsilon$, then eliminates $(\epsilon \# t_2)$ from the both side, 
 leads to the next step:
@@
 
-This can be solved by adding an axiom: $(\epsilon \# t_1) {\cdot} (\epsilon \# t_2) = 
-(\epsilon \# (t_1{+}t_2))$. 
+This can be solved by adding an axiom: $(\epsilon \# t_1) {\cdot} (\epsilon \# t_2) = (\epsilon \# (t_1{+}t_2))$. 
 However, we did not include it because it seems to be leading to other incomplete situations.

### 2022-07-06 paper/tv.tex
m

@@
 %\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-\documentclass[acmsmall,10pt,review]{acmart}
+\documentclass[acmsmall,10pt,review,anonymous]{acmart}
 
@@
 using mutable variables and timed behavioral patterns, 
-such as \emph{delay}, \emph{timeout}, \emph{deadline}. 
+such as \emph{delay}, \emph{timeout}, \emph{interrupt}, \emph{deadline}. 
 Secondly, to capture real-time specifications, 
@@
    (\alpha^*, {meth^*})} 
-%\qquad   \qquad\quad 
- %   \m{(Basic\ Types)} \qquad  \code{b} \code{\quad  ::= \quad }
-  %   \code{int\ |\ bool\ |\ void}
     \\
+
+    \m{(Basic\ Types)} &   \code{\iota} &\code{  ::=  }&
+     \code{int\ |\ bool\ |\ void}
+
+    \\
+%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
+ %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
+ %   \\
+
+  \m{(Method\ Def.)} &  \code{meth}&\code{ ::= }&
+  \code{\iota\  mn  \ {(\iota\ x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
+  \\
+  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
+  \\
+
   \m{(Assignment)} &  \code{\alpha }&\code{  ::= }&
@@
  \\
-
-%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
- %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
- %   \\
-
-%     \m{(Types)} &  \code{t}&\code{  ::= }&
-% \code{d\ |\ \tau} 
-% \\    
-  \m{(Method\ Def.)} &  \code{meth}&\code{  ::= }&
-  \code{ mn  \ {(x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
-  \\
-  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
-  \\
   \m{(Expressions)} &  \code{e}&\code{  ::= }&
-    \code{ v \ | \ 
+    \code{ v \ 
+    | \ \alpha \ | \ 
     [b]\ e \ |\ mn({v^*}) \ }
-  \code{| 
- % v.f:=e \ | 
- \ e_1;e_2\ | \ e_1 || e_2 \ 
+  \code{|  \ e_1;e_2\ | \ e_1 || e_2 \ 
   |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
@@
  &   & & \code{
-  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] 
-  | \ \textbf{delay} [d] \ 
-  | \ e_1\ \textbf{timeout} [d] \  e_2 \ 
-  | \ \textbf{deadline}  [d] \ e \  
+  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] \ 
+  | \ \textbf{delay} [t] \ 
+  | \ e_1\ \textbf{interrupt} [t] \  e_2 \ 
   }  \\
+
+  &   & & \code{
+    | \ e_1\ \textbf{timeout} [t] \  e_2 \ 
+    | \ e \ \textbf{deadline}  [t] \ 
+    | \ e \ \textbf{waituntil} [t]  \ 
+    }  \\
+
+    \m{(Real\text{-}Time\ Terms)}  & \code{t} &\code{  ::= }&
+    \code{ c
+    \ | \  x
+    \ | \  t_1{+}t_2
+    \ | \  t_1\text{-}t_2
+   }
+
+    \\
     ~\\
@@
 \code{c  \in \mathbb{Z}}
-\qquad \ 
+\qquad \qquad 
 \code{b  \in \mathbb{B}}
-\qquad \  
-\code{x, mn  ::\in \textbf{var}}  
-\qquad\ 
+\qquad \qquad  
+\code{x, mn  \in \textbf{var}}  
+\qquad \qquad 
  \code{(Action\ labels)\ \anyevent{A}  \in \Sigma %\cup \{\tau\}
-\qquad\ 
-\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
+%\qquad\ 
+%\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
 }   
@@
   \  |   {{\pi_1}} {\Rightarrow} {{\pi_2}}
-   \ |  \forall x. \code{{\pi}}
-   \ |  \exists x. \code{{\pi}}
+  % \ |  \forall x. \code{{\pi}}
+  %s \ |  \exists x. \code{{\pi}}
 
@@
 
-    \m{(Real\text{-}Time\ Term)}  & \code{t} &\code{  ::= }&
+    \m{(Real\text{-}Time\ Terms)}  & \code{t} &\code{  ::= }&
     \code{ c
@@
    %\qquad
-    \code{c ::\in \mathbb{Z}} 
+    \code{c \in \mathbb{Z}} 
      \qquad \qquad 
-           \code{x  ::\in \textbf{var} } 
+           \code{x  \in \textbf{var} } 
            \qquad\qquad
@@
 a single event \code{ev};
-  %where \anyevent{a} is an element from a finite set of events, denoted by \code{\Sigma};
-%parametrized event \code{ \anyevent{a}.\iota} where \code{\iota} is a list pattern expressing a possibly infinite list (for example, \code{\anyevent{a}.[1,2,3,4]},  \code{\anyevent{a}.[1 ..
-4]} and \code{\anyevent{a}.[1, 2..
-4]} all refer to the finite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot \anyevent{a}.4},
-%while \code{\anyevent{a}.[1 ..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.2 \cdot \anyevent{a}.3 \cdot}..., and \code{\anyevent{a}.[1, 3..]} refers to the infinite event sequence \code{\anyevent{a}.1 \cdot \anyevent{a}.3 \cdot \anyevent{a}.5\cdot}...);
  sequences concatenation \code{\es_1\cdot \es_2};
@@
       \\
-      \s{\Pi_f, \Theta_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (hd(\Theta_1)\mysharp t \cdot tl(\Theta_1))}
+      \s{\Pi_f, \Theta_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (hd(\Theta_1)\mysharp t_1 \cdot tl(\Theta_1))}
       \cup 

### 2022-07-07 paper/popl2022.tex
m

@@
 /*@ requires d>3000 : {}^*.{Login} @*/
-/*@ ensures	(3000<t/\t<d : {Connecting}#t.{Connected}) \/ (t=d :  {Connecting}#t) @*/
+/*@ ensures	(3000<t∧t<d : {Connecting}#t.{Connected}) ∨ (t=d :  {Connecting}#t) @*/
 {
@@
 The second thread firstly emits  \anyevent{Prep}, then calls the function {\ttfamily{cook}} asynchronously. 
-The precondition of {\ttfamily{main}} requires no arithmetic constraints on its input values (expressed as \code{\m{true}}), neither any pre-traces  (expressed as \code{\m{emp}} or \code{\epsilon}, indicating an empty trace).
+The precondition of {\ttfamily{main}} requires no arithmetic constraints on its input values (expressed as \code{\m{true}}), neither any pre-traces  (expressed as \code{\m{ε}} or \code{\epsilon}, indicating an empty trace).
 The postcondition ensures a trace, where the second time instance contains at least one signal \code{\anyevent{Cook}} and finishes within 3000 milliseconds after the completion of the first time instance.
@@
 hiphop module main (out Prep, in Tick, out Ready, out Go, out Cook)
-/*@ requires true : emp @*/
-/*@ ensures  0<=t/\t<3000 : {}.({Cook})#t.{}^* @*/
+/*@ requires true : ε @*/
+/*@ ensures  0<=t∧t<3000 : {}.({Cook})#t.{}^* @*/
 {
@@
 		async Ready { run cook (3000, Tick, Cook); }}}
-// The final effects for main is  0<=t/\t<3000 : ({Prep}.{Cook})#t.{Ready}.{Go}
+// The final effects for main is  0<=t∧t<3000 : ({Prep}.{Cook})#t.{Ready}.{Go}
 
@@
 /*@ requires d>2000  : {}^*.{Prep} @*/
-/*@ ensures  0<=t/\t<d : ({}.{Cook})#t @*/
+/*@ ensures  0<=t∧t<d : ({}.{Cook})#t @*/
 {	abort count(d, Tick) { yield; emit Cook; }}
@@
   \\
- \code{\langle  \textcolor{darklavender}{true : emp} \rangle }
-                  \textcolor{mGray}{  \emph{(– emp indicates an empty trace –)}}
+ \code{\langle  \textcolor{darklavender}{true : ε} \rangle }
+                  \textcolor{mGray}{  \emph{(– ε indicates an empty trace –)}}
   \item    \code{~\qquad \key{await}\ Ready;}
@@
   \\
- \code{\langle  \textcolor{darklavender}{true : emp} \rangle }
+ \code{\langle  \textcolor{darklavender}{true : ε} \rangle }
   \item    \code{~\qquad \key{emit}\ Prep; }
@@
 } \qquad
-\code{emp  \CONTAIN  \{\}^\star}
+\code{ε  \CONTAIN  \{\}^\star}
 }
@@
 {\wedge}   t_L^2 {=} t_R
-} :  emp
+} :  ε
  \CONTAIN \textcolor {darkred}{t_R {<}3} : \bot \vee \{\}^\star}}
@@
 } :  \cancel{\{Go\}}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\{\}} \cdot \{\}^\star}}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{ε} \vee \cancel{\{\}} \cdot \{\}^\star}}
 \Infer[dashed]1[{\siderule{\textcircled{6}[Normalization]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L 
@@
 :  \cancel{\{ Ready\}} \cdot \{Go\}
- \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{emp} \vee \cancel{\{\}} \cdot \{\}^\star}}
+ \CONTAIN \textcolor {darkred}{t_R {<}3} : \cancel{ε} \vee \cancel{\{\}} \cdot \{\}^\star}}
 \Infer[dashed]1[{\siderule{\textcircled{4}[UNFOLD{-}UNIFY]}}]{\code{ \textcolor {darkred}{t_L {<}3  {\wedge} t_L^1 {+} t_L^2 {=}t_L
@@
 In step \code{\textcircled{4}}, in order to conduct a further unfolding, we unify time variables \code{t_L^2} and \code{t_R} by adding the constraint \code{t_L^2 {=} t_R}. 
-In step \code{\textcircled{5}}, from the RHS, since \code{\{\}^\star {=} emp \vee \{\} \cdot \{\}^\star}, eliminating one time instance \code{\{Ready\}} from it will lead to \code{\bot \vee \{\}^\star}, which can be normalised into \code{\{\}^\star} in step \code{\textcircled{6}}.
+In step \code{\textcircled{5}}, from the RHS, since \code{\{\}^\star {=} ε \vee \{\} \cdot \{\}^\star}, eliminating one time instance \code{\{Ready\}} from it will lead to \code{\bot \vee \{\}^\star}, which can be normalised into \code{\{\}^\star} in step \code{\textcircled{6}}.
 At the end of the rewriting, we manage to prove that \code{(t_L {<}3 {\wedge} t_L^1 {+} t_L^2 {=}t_L {\wedge}t_L^2 {=} t_R)  \Rightarrow  t_R {<} 3} \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{de2008z3}.}; therefore, the proof succeed.
@@
     \\
- \code{\langle  \textcolor{darklavender}{true : emp} \rangle }     
+ \code{\langle  \textcolor{darklavender}{true : ε} \rangle }     
        \item  \code{~\qquad \key{yield}}  
@@
 hiphop module send (var n, out Send, out Done)
-/*@ requires true : emp @*/
+/*@ requires true : ε @*/
 /*@ ensures	(n>=0 : {}^*. {Done}) 
-          \/ (n<0   : {Send}^w)  @*/
+          ∨ (n<0   : {Send}^w)  @*/
 {
@@
 \code{
-\textcolor {darkred}{n{=}0} \Rightarrow \textcolor {darkred}{n{\geq}0} \qquad emp \subseteq \{\}^\star \qquad  \code{\siderule{[PROVE]}}
-}
-}
-\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : emp
- \CONTAIN \textcolor {darkred}{n{\geq}0} :  \bot \vee \{\}^\star \vee emp }  
+\textcolor {darkred}{n{=}0} \Rightarrow \textcolor {darkred}{n{\geq}0} \qquad ε \subseteq \{\}^\star \qquad  \code{\siderule{[PROVE]}}
+}
+}
+\Infer[dashed]1[]{\code{ \textcolor {darkred}{n{=}0} : ε
+ \CONTAIN \textcolor {darkred}{n{\geq}0} :  \bot \vee \{\}^\star \vee ε }  
  }

### 2022-07-07 code/src/program/coffee.c

@@ -2,8 +2,8 @@
 
 void oneSugar() 
 /*
-req: TRUE/\(_^*).emp
-ens: (t1>1)/\ (emp # t1)
+req: TRUE∧(_^*).ε
+ens: (t>1)∧ (ε # t)
 */
 {
     timeout (() , 1);
@@ -11,8 +11,8 @@ ens: (t1>1)/\ (emp # t1)
 
 void addSugar (int n) 
 /*
-req: TRUE/\(_^*)
-ens:  (t>=n)/\ (Sugar #t)
+req: TRUE∧(_^*)
+ens:  (t>=n)∧ (Sugar #t)
 */
 {
 
@@ -27,8 +27,8 @@ ens:  (t>=n)/\ (Sugar #t)
 
 void makeCoffee (int n)
 /*
-req: TRUE/\(_^*) . Cup
-ens: (t<=5/\t>=n/\t1<=3)/\(Sugar#t).(Coffee#t1)
+req: TRUE∧(_^*) . Cup
+ens: (t<=5∧t>=n∧t1<=3)∧(Sugar#t).(Coffee#t1)
 */
 {
     deadline (addSugar(n), 5);
@@ -37,8 +37,8 @@ ens: (t<=5/\t>=n/\t1<=3)/\(Sugar#t).(Coffee#t1)
 
 int main ()
 /*
-    req: TRUE /\emp
-    ens: (t<=8)/\ ((((~Done)^*))#t).Done 
+    req: TRUE ∧ ε
+    ens: (t<=8)∧ ((((~Done)^*))#t).Done 
     */
 {
     event["Cup"];

### 2022-07-07 code/src/program/fischer.c

@@ -3,8 +3,8 @@ ct := 0;
 pc := -1;
 
 void process (int i)
-/* req: (d1>0/\d2>d1) /\ (_^*) 
-   ens: (t1<=d1/\t2=d2) /\ (([x=-1]? . (Update(i){x := i}#t1) . (emp#t2) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
+/* req: (d1>0∧d2>d1) ∧ (_^*) 
+   ens: (t1<=d1∧t2=d2) ∧ (([x=-1]? . (Update(i){x := i}#t1) . (ε#t2) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
 {
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);
@@ -19,15 +19,15 @@ void process (int i)
 }
 
 void process1 (int i)
-/* req: (d1>0/\d2>d1) /\ (_^*) 
-   ens: (t2>0/\t1>0/\t1=d1/\t2=d2) /\ ([x=-1]? . 
-   (Update(i){x := i}#t1). (emp#t2) . 
+/* req: (d1>0∧d2>d1) ∧ (_^*) 
+   ens: (t2>0∧t1>0∧t1=d1∧t2=d2) ∧ ([x=-1]? . 
+   (Update(i){x := i}#t1). (ε#t2) . 
    (([x=i] . Critical(i){pc:=i} .Exit(i){x := -1; pc:= -1} ) + [(~(x=i))]) )*/
 { 1
 }
 
 void main () 
-/* req: (d1>0/\d2>d1) /\ emp 
-   ens: TRUE /\ (([pc=-1] + [pc=(x)])^*)  */
+/* req: (d1>0∧d2>d1) ∧ ε 
+   ens: TRUE ∧ (([pc=-1] + [pc=(x)])^*)  */
 { process1(0) || process1(1) || process1(2); }
 

### 2022-07-07 code/src/program/test1.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,17 +13,17 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
-ens: (t <21)/\ ((A.B) # t)
-ens: (t <21)/\ ((_.B) # t)
-ens: (t <21)/\ ((_._) # t)
-ens: (t <21)/\ ((A._) # t)
-ens: ((t1+t2) <21)/\ (A#t1). (B # t2)
-ens: (t <20)/\ ((A.B) # t)
-ens: (t <21)/\ ((~A.B) # t)
-ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
-ens: ((t1+t2) <21)/\ (A#t1). (~B # t2)
-ens: (t <21)/\ ((A.~B) # t)
+req: TRUE∧(_^*)
+ens: (t <21)∧ ((A.B) # t)
+ens: (t <21)∧ ((_.B) # t)
+ens: (t <21)∧ ((_._) # t)
+ens: (t <21)∧ ((A._) # t)
+ens: ((t1+t2) <21)∧ (A#t1). (B # t2)
+ens: (t <20)∧ ((A.B) # t)
+ens: (t <21)∧ ((~A.B) # t)
+ens: ((t1+t2) <21)∧ (~A#t1). (B # t2)
+ens: ((t1+t2) <21)∧ (A#t1). (~B # t2)
+ens: (t <21)∧ ((A.~B) # t)
 */
 {
     deadline (callee ()  , 20);

### 2022-07-07 code/src/program/test10.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,26 +72,26 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
[…]

### 2022-07-07 code/src/program/test11.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,26 +72,26 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
[…]

### 2022-07-07 code/src/program/test13.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(_ . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(_ . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(_ . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(_ . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(_ . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(_ . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,9 +72,9 @@ ens: TRUE/\(A )
 
 void callee7 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(W. K)
-ens: TRUE/\(A )
[…]

### 2022-07-07 code/src/program/test14.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,9 +72,9 @@ ens: TRUE/\(A )
 
 void callee7 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(W. K)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
[…]

### 2022-07-07 code/src/program/test15.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,9 +72,9 @@ ens: TRUE/\(A )
 
 void callee7 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(W. K)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
[…]

### 2022-07-07 code/src/program/test16.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,9 +72,9 @@ ens: TRUE/\(A )
 
 void callee7 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(W. K)
-ens: TRUE/\(A )
[…]

### 2022-07-07 code/src/program/test2.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -14,18 +14,18 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
-ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . ((A . B)#f1))
-ens: (f0>0/\f0<=20/\f1>30)/\(((_ . B)#f0) . ((A . B)#f1))
-ens: (f0>0/\f0<=20/\f1>30)/\(((~B . B)#f0) . ((A . B)#f1))
-ens: (f0>0/\f0<=20/\f1>30)/\(((A . _)#f0) . ((~C . B)#f1))
-ens: (f0>0/\f0<=20/\f1>30)/\(((_ . _)#f0) . ((A . _)#f1))
+req: TRUE∧(_^*)
+ens: (f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . ((A . B)#f1))
+ens: (f0>0∧f0<=20∧f1>30)∧(((_ . B)#f0) . ((A . B)#f1))
+ens: (f0>0∧f0<=20∧f1>30)∧(((~B . B)#f0) . ((A . B)#f1))
+ens: (f0>0∧f0<=20∧f1>30)∧(((A . _)#f0) . ((~C . B)#f1))
+ens: (f0>0∧f0<=20∧f1>30)∧(((_ . _)#f0) . ((A . _)#f1))
 
-ens: (t <20)/\ ((A.B) # t)
-ens: (t <21)/\ ((~A.B) # t)
-ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
-ens: ((t1+t2) <21)/\ (A#t1). (~B # t2)
-ens: (t <21)/\ ((A.~B) # t)
+ens: (t <20)∧ ((A.B) # t)
+ens: (t <21)∧ ((~A.B) # t)
+ens: ((t1+t2) <21)∧ (~A#t1). (B # t2)
+ens: ((t1+t2) <21)∧ (A#t1). (~B # t2)
+ens: (t <21)∧ ((A.~B) # t)
 */
 {
     deadline (callee ()  , 

### 2022-07-07 code/src/program/test3.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -24,18 +24,18 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
-ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . B)#f0) . ((C . D)#f1))
-ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((_ . B)#f0) . ((C . D)#f1))
-ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . ~A)#f0) . ((C . D)#f1))
-ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . B)#f0) . ((_ . D)#f1))
-ens: (f0>0/\f0<=20/\f1>0/\f1<=30)/\(((A . B)#f0) . ((C . ~A)#f1))
+req: TRUE∧(_^*)
+ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . B)#f0) . ((C . D)#f1))
+ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((_ . B)#f0) . ((C . D)#f1))
+ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . ~A)#f0) . ((C . D)#f1))
+ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . B)#f0) . ((_ . D)#f1))
+ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . B)#f0) . ((C . ~A)#f1))
 
-ens: (t <20)/\ ((A.B) # t)
-ens: (t <21)/\ ((~A.B) # t)
-ens: ((t1+t2) <21)/\ (~A#t1). (B # t2)
[…]

### 2022-07-07 code/src/program/test4.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -48,18 +48,18 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
-ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
-ens: (f0>0/\f0<=20/\f1>30)/\(((_ . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
-ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . (((C . D)#f1) . ((C . D)^*)))
-ens: (f0>0/\f0<=20/\f1>30)/\(((A . _)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
-ens: (f0>0/\f0<=20/\f1>30)/\(((A . B)#f0) . (((C . D)#f1) . ((C . _)^*)))
+req: TRUE∧(_^*)
[…]

### 2022-07-07 code/src/program/test5.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -24,9 +24,9 @@ ens: TRUE/\(A )
 
 void callee2 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -36,9 +36,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -48,9 +48,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -59,22 +59,22 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
-ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1)/\(_^*) \/ (~(x=1))/\(_^*)
-ens: (x=1)/\(C . (D . (C . (D . (C . (D . (C . D))))))) \/ (~(x=1))/\(C . (D . (C . (D . (C . (D . (C . D)))))))
[…]

### 2022-07-07 code/src/program/test6.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -24,9 +24,9 @@ ens: TRUE/\(A )
 
 void callee2 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -36,9 +36,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -48,9 +48,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -59,22 +59,22 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
-ens: (f0>0/\f0<=20/\x=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) \/ (f0>0/\f0<=20/\(~(x=1))/\y=1)/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) \/ (f0>0/\f0<=20/\(~(x=1))/\(~(y=1)))/\(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
[…]

### 2022-07-07 code/src/program/test7.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -24,9 +24,9 @@ ens: TRUE/\(A )
 
 void callee2 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -36,9 +36,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -48,9 +48,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -59,22 +59,22 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
[…]

### 2022-07-07 code/src/program/test8.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -24,9 +24,9 @@ ens: TRUE/\(A )
 
 void callee2 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -36,9 +36,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -48,9 +48,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -60,9 +60,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -72,9 +72,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
[…]

### 2022-07-07 code/src/program/test9.c

@@ -2,9 +2,9 @@
 
 void callee () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(A . B)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(A . B)
+ens: TRUE∧(A )
 */
 {
     event["A"];
@@ -13,9 +13,9 @@ ens: TRUE/\(A )
 
 void callee1 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -25,9 +25,9 @@ ens: TRUE/\(A )
 
 void callee3 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -37,9 +37,9 @@ ens: TRUE/\(A )
 
 void callee4 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(C . D)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(C . D)
+ens: TRUE∧(A )
 */
 {
     event["C"];
@@ -49,9 +49,9 @@ ens: TRUE/\(A )
 
 void callee5 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(M. N)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(M. N)
+ens: TRUE∧(A )
 */
 {
     event["M"];
@@ -61,9 +61,9 @@ ens: TRUE/\(A )
 
 void callee6 () 
 /*
-req: TRUE/\(_^*)
-ens: TRUE/\(F . G)
-ens: TRUE/\(A )
+req: TRUE∧(_^*)
+ens: TRUE∧(F . G)
+ens: TRUE∧(A )
 */
 {
     event["F"];
@@ -72,26 +72,26 @@ ens: TRUE/\(A )
 
 void process() 
 /*
-req: TRUE/\(_^*)
[…]

### 2022-07-07 paper/popl2022.tex
m

@@
 function enableLoginButton(){
-  return (Rname.length >= 2 
-	   && Rpasswd.length >= 2);}
+  return (Rname.length ≥ 2 
+	   && Rpasswd.length ≥ 2);}
 function nameKeypress(value){
@@
 	  emit enableLogin(
-		  		name.length >= 2 
-		  	 && passwd.length >= 2); 
+		  		name.length ≥ 2 
+		  	 && passwd.length ≥ 2); 
   } every(name || passwd)
@@
 /*@ requires true : ε @*/
-/*@ ensures	(n>=0 : {}^*. {Done}) 
+/*@ ensures	(n≥0 : {}^*. {Done}) 
           ∨ (n<0   : {Send}^w)  @*/

### 2022-07-07 code/src/program/coffee.c

@@ -12,7 +12,7 @@ ens: (t>1)∧ (ε # t)
 void addSugar (int n) 
 /*
 req: TRUE∧(_^*)
-ens:  (t>=n)∧ (Sugar #t)
+ens:  (t≥n)∧ (Sugar #t)
 */
 {
 
@@ -28,7 +28,7 @@ ens:  (t>=n)∧ (Sugar #t)
 void makeCoffee (int n)
 /*
 req: TRUE∧(_^*) . Cup
-ens: (t<=5∧t>=n∧t1<=3)∧(Sugar#t).(Coffee#t1)
+ens: (t≤5∧t≥n∧t1≤3)∧(Sugar#t).(Coffee#t1)
 */
 {
     deadline (addSugar(n), 5);
@@ -38,7 +38,7 @@ ens: (t<=5∧t>=n∧t1<=3)∧(Sugar#t).(Coffee#t1)
 int main ()
 /*
     req: TRUE ∧ ε
-    ens: (t<=8)∧ ((((~Done)^*))#t).Done 
+    ens: (t≤8)∧ ((((!Done)^*))#t).Done 
     */
 {
     event["Cup"];

### 2022-07-07 code/src/program/fischer.c

@@ -4,7 +4,7 @@ pc := -1;
 
 void process (int i)
 /* req: (d1>0∧d2>d1) ∧ (_^*) 
-   ens: (t1<=d1∧t2=d2) ∧ (([x=-1]? . (Update(i){x := i}#t1) . (ε#t2) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
+   ens: (t1≤d1∧t2=d2) ∧ (([x=-1]? . (Update(i){x := i}#t1) . (ε#t2) . (([x=i] . Critical(i){ct := (ct + 1); pc:=i} . Exit(i){ct := (ct-1); x := -1; pc:= -1} ) + [(~(x=i))])) ^*) */
 {
   [x=-1] 
   deadline (event["Update"(i)]{x := i}, d1);

### 2022-07-07 code/src/program/test10.c

@@ -73,15 +73,15 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (x=0∧f0>0∧f0<=20∧z=0)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D)))))))))))))))) ∨ (x=0∧f0>0∧f0<=20∧(~(z=0)))∧(((A . B)#f0) . (M . (N . (F . (G . (C . (D . (C . D)))))))) ∨ ((~(x=0))∧y=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(y=0))∧y=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(y=0))∧(~(y=0)))∧(M . (N . (F . (G . (C . (D . (C . D)))))))
-ens: (x=0∧f0>0∧f0<=20∧z=0)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D)))))))))))))))) ∨ (x=0∧f0>0∧f0<=20∧(~(z=0)))∧(((A . B)#f0) . (M . (N . (F . (G . (C . (D . (C . D)))))))) ∨ ((~(x=0))∧y=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(y=0))∧y=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(y=0))∧(~(y=0)))∧(M . (N . (F . (G . (C . (D . (C . D)))))))
[…]

### 2022-07-07 code/src/program/test12.c

@@ -73,15 +73,15 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (x=0∧f0>0∧f0<=20∧z=0)∧(((A . B)#f0) . (C . (D . (C . (_ . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D)))))))))))))))) ∨ (x=0∧f0>0∧f0<=20∧(~(z=0)))∧(((A . B)#f0) . (M . (N . (F . (G . (C . (D . (C . D)))))))) ∨ ((~(x=0))∧k=0∧y1=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))))))))))) ∨ ((~(x=0))∧k=0∧(~(y1=0)))∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(k=0))∧y1=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(k=0))∧(~(y1=0)))∧(M . (N . (F . (G . (C . (D . (C . D)))))))
[…]

### 2022-07-07 code/src/program/test13.c

@@ -96,17 +96,17 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens:  (f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . (((_ . D)#f1) . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (M . (N . (F . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (M . (N . (F . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (M . (N . (W . (~A . (_ . (_ . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (M . (N . (W . (~A . (_ . (_ . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (M . (N . (F . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (M . (N . (W . (~A . (_ . (_ . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (M . (N . (W . (~A . (_ . (_ . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (M . (N . (F . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (M . (N . (W . (~A . (_ . (_ . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (M . (N . (F . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . (S . (_ . (_ . (M . (N . (W . (~A . (_ . (_ . (_ . (S . (_ . (_ . (_ . (_ . (_ . (_ . (M . (N . (F . (_ . (_ . (_ . (_ . (_ . (_ . (_ . (W . (~A . (_ . S))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))
[…]

### 2022-07-07 code/src/program/test14.c

@@ -97,17 +97,17 @@ void process()
 /*
 req: TRUE∧(_^*)
 
-ens: (x=0∧f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . ((C . D)#f1)) ∨ ((~(x=0)))∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . S)))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))
[…]

### 2022-07-07 code/src/program/test15.c

@@ -97,17 +97,17 @@ void process()
 /*
 req: TRUE∧(_^*)
 
-ens:(x=0∧f0>0∧f0<=20∧f1>30∧f2>0∧f2<=10∧f3>70)∧(((A . B)#f0) . (((C . D)#f1) . (((C . D)#f2) . ((C . D)#f3)))) ∨ ((~(x=0)))∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . S)))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))
[…]

### 2022-07-07 code/src/program/test16.c

@@ -120,17 +120,17 @@ void process()
 /*
 req: TRUE∧(_^*)
 
-ens:(x=0∧f0>0∧f0<=20∧f1>30∧f2>0∧f2<=10∧f3>70∧f4>0∧f4<=10)∧(((A . B)#f0) . (((C . D)#f1) . (((C . D)#f2) . (((C . D)#f3) . (((L . S)#f4) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (C . D)))))))))))))))))))))))) ∨ ((~(x=0)))∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . (S . (C . (D . (M . (N . (W . (K . (C . (D . (L . (S . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . (D . (C . (D . (W . (K . (L . S))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))))
[…]

### 2022-07-07 code/src/program/test2.c

@@ -15,11 +15,11 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . ((A . B)#f1))
-ens: (f0>0∧f0<=20∧f1>30)∧(((_ . B)#f0) . ((A . B)#f1))
-ens: (f0>0∧f0<=20∧f1>30)∧(((~B . B)#f0) . ((A . B)#f1))
-ens: (f0>0∧f0<=20∧f1>30)∧(((A . _)#f0) . ((~C . B)#f1))
-ens: (f0>0∧f0<=20∧f1>30)∧(((_ . _)#f0) . ((A . _)#f1))
+ens: (f0>0∧f0≤20∧f1>30)∧(((A . B)#f0) . ((A . B)#f1))
+ens: (f0>0∧f0≤20∧f1>30)∧(((_ . B)#f0) . ((A . B)#f1))
+ens: (f0>0∧f0≤20∧f1>30)∧(((~B . B)#f0) . ((A . B)#f1))
+ens: (f0>0∧f0≤20∧f1>30)∧(((A . _)#f0) . ((~C . B)#f1))
+ens: (f0>0∧f0≤20∧f1>30)∧(((_ . _)#f0) . ((A . _)#f1))
 
 ens: (t <20)∧ ((A.B) # t)
 ens: (t <21)∧ ((~A.B) # t)

### 2022-07-07 code/src/program/test3.c

@@ -25,11 +25,11 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . B)#f0) . ((C . D)#f1))
-ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((_ . B)#f0) . ((C . D)#f1))
-ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . ~A)#f0) . ((C . D)#f1))
-ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . B)#f0) . ((_ . D)#f1))
-ens: (f0>0∧f0<=20∧f1>0∧f1<=30)∧(((A . B)#f0) . ((C . ~A)#f1))
+ens: (f0>0∧f0≤20∧f1>0∧f1≤30)∧(((A . B)#f0) . ((C . D)#f1))
+ens: (f0>0∧f0≤20∧f1>0∧f1≤30)∧(((_ . B)#f0) . ((C . D)#f1))
+ens: (f0>0∧f0≤20∧f1>0∧f1≤30)∧(((A . ~A)#f0) . ((C . D)#f1))
+ens: (f0>0∧f0≤20∧f1>0∧f1≤30)∧(((A . B)#f0) . ((_ . D)#f1))
+ens: (f0>0∧f0≤20∧f1>0∧f1≤30)∧(((A . B)#f0) . ((C . ~A)#f1))
 
 ens: (t <20)∧ ((A.B) # t)
 ens: (t <21)∧ ((~A.B) # t)

### 2022-07-07 code/src/program/test4.c

@@ -49,11 +49,11 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
-ens: (f0>0∧f0<=20∧f1>30)∧(((_ . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
-ens: (f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . (((C . D)#f1) . ((C . D)^*)))
-ens: (f0>0∧f0<=20∧f1>30)∧(((A . _)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
-ens: (f0>0∧f0<=20∧f1>30)∧(((A . B)#f0) . (((C . D)#f1) . ((C . _)^*)))
+ens: (f0>0∧f0≤20∧f1>30)∧(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
+ens: (f0>0∧f0≤20∧f1>30)∧(((_ . B)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
+ens: (f0>0∧f0≤20∧f1>30)∧(((A . B)#f0) . (((C . D)#f1) . ((C . D)^*)))
+ens: (f0>0∧f0≤20∧f1>30)∧(((A . _)#f0) . (((C . D)#f1) . (C . (D . (C . D)))))
+ens: (f0>0∧f0≤20∧f1>30)∧(((A . B)#f0) . (((C . D)#f1) . ((C . _)^*)))
 
 ens: (t <20)∧ ((A.B) # t)
 ens: (t <21)∧ ((~A.B) # t)

### 2022-07-07 code/src/program/test6.c

@@ -60,13 +60,13 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (f0>0∧f0<=20∧x=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧y=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧(~(y=1)))∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
-ens: (f0>0∧f0<=20∧x=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧y=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧(~(y=1)))∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
-ens: (f0>0∧f0<=20∧x=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧y=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧(~(y=1)))∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
-ens: (f0>0∧f0<=20∧x=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧y=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧(~(y=1)))∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
[…]

### 2022-07-07 code/src/program/test7.c

@@ -60,13 +60,13 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (f0>0∧f0<=20∧x=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧y=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧(~(y=1)))∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
[…]

### 2022-07-07 code/src/program/test8.c

@@ -85,13 +85,13 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (f0>0∧f0<=20∧x=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . D)))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧y=1)∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D)))))))) ∨ (f0>0∧f0<=20∧(~(x=1))∧(~(y=1)))∧(((A . B)#f0) . (C . (D . (C . (D . (C . (D . (C . D))))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
-ens: (x=1∧f0>0∧f0<=20)∧((A . B)#f0) ∨ ((~(x=1))∧y=1)∧(C . (D . (C . (D . (C . (D . (C . D))))))) ∨ ((~(x=1))∧(~(y=1)))∧(C . (D . (C . (D . (C . (D . (C . D)))))))
[…]

### 2022-07-07 code/src/program/test9.c

@@ -73,15 +73,15 @@ ens: TRUE∧(A )
 void process() 
 /*
 req: TRUE∧(_^*)
-ens: (x=0∧f0>0∧f0<=20∧f1>30∧z=0)∧(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))))) ∨ (x=0∧f0>0∧f0<=20∧f1>30∧(~(z=0)))∧(((A . B)#f0) . (((C . D)#f1) . (M . (N . (F . (G . (C . (D . (C . D))))))))) ∨ ((~(x=0))∧y=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(y=0)))∧(M . (N . (F . (G . (C . (D . (C . D)))))))
-ens: (x=0∧f0>0∧f0<=20∧f1>30∧z=0)∧(((A . B)#f0) . (((C . D)#f1) . (C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))))) ∨ (x=0∧f0>0∧f0<=20∧f1>30∧(~(z=0)))∧(((A . B)#f0) . (((C . D)#f1) . (M . (N . (F . (G . (C . (D . (C . D))))))))) ∨ ((~(x=0))∧y=0)∧(C . (D . (C . (D . (C . (D . (C . (D . (M . (N . (F . (G . (C . (D . (C . D))))))))))))))) ∨ ((~(x=0))∧(~(y=0)))∧(M . (N . (F . (G . (C . (D . (C . D)))))))
[…]

### 2022-08-04 paper/icse23.tex
m

--- 2022-07-06 paper/tv.tex
@@
-%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
-\documentclass[acmsmall,10pt,review,anonymous]{acmart}
-
-%%
-%% \BibTeX command to typeset BibTeX logo in the docs
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-    \acmJournal{PACMPL}
-\acmVolume{1}
-\acmNumber{CONF} % CONF = POPL or ICFP or OOPSLA
-\acmArticle{1}
-\acmYear{2018}
-\acmMonth{1}
-
-\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
-\startPage{1}
-
-\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\copyrightyear{2018}           %% If different from \acmYear
-\usepackage{pifont}% http://ctan.org/pkg/pifont
-
-\usepackage{tikz}
-\newcommand{\cmark}{\ding{51}}%
-\newcommand{\xmark}{\ding{55}}%
-
+\documentclass[10pt,conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{comment}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
 \usepackage{xcolor}
-\usepackage[thicklines]{cancel}
-\renewcommand{\CancelColor}{\color{lightgray}}
-
-%% Some recommended packages.
-\usepackage{booktabs}   %% For formal tables:
-                        %% http://ctan.org/pkg/booktabs
-\usepackage{subcaption} 
-                        %% http://ctan.org/pkg/subcaption
-
-\newcommand{\wbigcup}{\mathop{\widetilde{\bigcup}}\displaylimits}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-\usepackage{enumerate}
-\usepackage[utf8]{inputenc}
-\usepackage{parcolumns}
-\usepackage[spanish,english]{babel}
-\usepackage{amsmath}
-\usepackage{csquotes}
-\usepackage{varwidth}
-\newcommand{\key}[1]{\textcolor{purple}{\code{#1}}}
-\newcommand{\jskey}[1]{\textcolor{blue}{\code{#1}}}
-\definecolor{palered-violet}{rgb}{0.86, 0.44, 0.58}
-\definecolor{bittersweet}{rgb}{1.0, 0.44, 0.37}
-\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
-\definecolor{persianplum}{rgb}{0.44, 0.11, 0.11}
-\newcommand{\hide}[1]{}
-\newcommand{\siderule}[1]{
-\code{\footnotesize{\textcolor{mGray}{#1}}}}
-\usepackage{adjustbox}
-\usepackage{ebproof}
-\usepackage{cancel}
-\newcommand{\env}{\code{\mathcal{V}}}
-
-\newcommand{\es}{\theta}
-\newcommand{\ev}{ev}
-\newcommand{\codem}[1]{{\lstinline[basicstyle=\small\ttfamily]|#1|}}
-
 \newcommand{\timedEffects}{\emph{TimEffs}}
-\usepackage{xcolor}
-\definecolor{javablue}{rgb}{0.25,0,1} % for strings
-\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
-\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
-\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} 
-\definecolor{mGray}{rgb}{0.4,0.4,0.4}
-\definecolor{mPurple}{rgb}{0.58,0,0.82}
-\definecolor{huntergreen}{rgb}{0.33, 0.42, 0.18}
-
-\definecolor{darklavender}{rgb}{0, 0, 0}
-\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}
-\definecolor{brickred}{rgb}{0.8, 0.25, 0.33}
-\definecolor{red}{rgb}{0.6,0,0} 
-\definecolor{blue}{rgb}{0,0,0.6}
-\definecolor{green}{rgb}{0,0.8,0}
-\definecolor{cyan}{rgb}{0.0,0.6,0.6}
-\definecolor{cloudwhite}{rgb}{0.9412, 0.9608, 0.8471} 
-\definecolor{davysgrey}{rgb}{0.33, 0.33, 0.33}
-\definecolor{deepfuchsia}{rgb}{0.76, 0.33, 0.76}
-\definecolor{deeplilac}{rgb}{0.6, 0.33, 0.73}
-\definecolor{deepskyblue}{rgb}{0.0, 0.75, 1.0}
-\definecolor{indianred}{rgb}{0.8, 0.36, 0.36}
-\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
-\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
-\usepackage{wrapfig}
-\newcommand{\effect}{{\ensuremath{\mathrm{\Phi}}}}
-\definecolor{color_pure}{RGB}{3,35,14}
-\usepackage{epigraph}
+\newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
+\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}}
+\newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
+\newcommand{\timedL}{\code{C^{t}}}
 \newcommand{\anyevent}[1]{{\textcolor{darkred}
@@
 
-\def\defeq{\ensuremath{\,\triangleq}}
-\definecolor{regalia}{rgb}{0.32, 0.18, 0.5}
-\newcommand{\inclusion}{\code{\mathcal{I}}}
-\definecolor{mypink}{RGB}{219, 48, 122}
-\definecolor{darklavender}{rgb}{0.45, 0.31, 0.59}
-\definecolor{deepcerise}{rgb}{0.85, 0.2, 0.53}
-\newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
-\newcommand\tabref[1]{Table \textcolor{black}{\ref{#1}}}
-\newcommand\secref[1]{Sec. \textcolor{black}{\ref{#1}}}
-\newcommand{\timedL}{\code{C^{t}}}
-
 \newcommand\theoref[1]{Theorem~\textcolor{blue}{\ref{#1}}}
@@
 \newcommand\algoref[1]{Algorithm~\textcolor{blue}{\ref{#1}}}
-\usepackage{listings}
 
-\lstdefinelanguage{JavaScript}{
-  keywords={typeof, void, const, new, int, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywords={class, export, boolean,event, timeout, deadline, delay,  throw, implements, import, this},
-  ndkeywordstyle=\color{darkgray}\bfseries,
-  identifierstyle=\color{black},
-  sensitive=false,
-  comment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  commentstyle=\color{darklavender}\ttfamily,
-  stringstyle=\color{red}\ttfamily,
-  morestring=[b]',
-  morestring=[b]"
-}
-
-\lstset{
-   language=JavaScript,
-   %%backgroundcolor=\color{lightgray},
-   extendedchars=true,
-   basicstyle=\footnotesize\ttfamily,
-   showstringspaces=false,
-   showspaces=false,
-%frame=single
-numbers=left,   
-xleftmargin=1em, 
-    numberstyle=\tiny\color{mGray},
-   numbersep=10pt,
-   tabsize=4,
-   breaklines=true,
-   showtabs=false,
-   captionpos=b,
-   keywordstyle=[2]\color{purple}\bfseries, %
-   morekeywords=[2]{do, hiphop,every, loop,suspend, when, signal, end, present, nothing, emit,in, out, yield,abort, fork, par, run},
-}
-
-%\lstset{
-%  frame=none,
-%  xleftmargin=2pt,
-%  stepnumber=1,
-%  numbers=left,
-%  numbersep=5pt,
-%  numberstyle=\ttfamily\tiny\color[gray]{0.3},
-%  belowcaptionskip=\bigskipamount,
-%  captionpos=b,
-%  escapeinside={*'}{'*},
-%  language=JavaScript,
-%  tabsize=2,
-
-%%
-%% Submission ID.
-%% Use this when submitting an article to a sponsored event. You'll
-%% receive a unique submission ID from the organizers
-%% of the event, and this ID should be used as the parameter to this command.
-%%\acmSubmissionID{123-A56-BU3}
-
-%%
-%% The majority of ACM publications use numbered citations and
-%% references.  The command \citestyle{authoryear} switches to the
-%% "author year" style.
-%% Uncommenting
-%% the next command will enable that style.
-%%\citestyle{acmauthoryear}
-\citestyle{acmauthoryear}   %% For author/year citations
-
-%%
-%% end of the preamble, start of the body of the document source.
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 \begin{document}
 
-%%
-%% The "title" command has an optional parameter,
-%% allowing the author to define a "short title" to be used in page headers.
 \title{Automated Verification for Real-Time Systems 
@@
 
-%%
-%% The "author" command and its associated commands are used to define
-%% the authors and their affiliations.
-%% Of note is the shared affiliation of the first two authors, and the
-%% used to denote shared contribution to the research.
+\author{(Anonymous Authors)}
 
-\author{(Anonymous Authors)}
-%\author{Valerie B\'eranger}
-%\affiliation{%
-%  \institution{Inria Paris-Rocquencourt}
-%  \city{Rocquencourt}
-%  \country{France}
-%}
+\begin{comment}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+}
+\end{comment}
 
-%%
-%% By default, the full list of authors will be used in the page
-%% headers. Often, this list is too long, and will overlap
-%% other information printed in the page headers. This command allows
-%% the author to define a more concise list
-%% of authors' names for this purpose.
-%\renewcommand{\shortauthors}{Trovato and Tobin, et al.}
+\maketitle
 
-%%
-%% The abstract is a short summary of the work to be presented in the
-%% article.
 \begin{abstract}
@@
     soundness; report on case studies and the experimental results.     
-
 \end{abstract}
 
-%%
-%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
-%% Please copy and paste the code instead of the example below.
-%%
-
-\ccsdesc[500]{Theory of computation~Logic}
-\ccsdesc[300]{Theory of computation~Semantics and reasoning}
-\ccsdesc[300]{Theory of computation~Finite Model Theory}
-
-%%
-%% Keywords. The author(s) should pick words that accurately describe
-%% the work being presented. Separate the keywords with commas.
-\keywords{Temporal Verification,
-Dependant Effects,
-Hoare-style Forward Verifier,
-Term Rewriting System,
-Timed Verification}
-
-%%
-%% This command processes the author and affiliation and title
-%% information and builds the first part of the formatted document.
-\maketitle
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
 
 \section{Introduction}
-\label{Introduction}
-
-Specification and verification of real-time systems are essential 
-to research topics with practical implications. During the last 
-more than two decades, a popular approach for specifying real-time systems has been 
-based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
-Timed Automata are powerful 
-in designing real-time models with explicit clock variables. Real-time 
-constraints are captured by explicitly setting/resetting clock variables. 
-A number of automatic verification support for Timed Automata have proven 
-to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
-
-Models based on Timed Automata often adopt a simple structure, e.g., a 
-network with no hierarchy. The benefit is that 
-efficient model checking is made feasible. Nonetheless, designing and 
-verifying compositional real-time systems is becoming an increasingly 
-difficult task due to the widespread applications and increasing complexity 
-of such systems. In industrial case studies of real-time system verification, system 
-requirements are often structured into phases, which are then composed 
-sequentially, in parallel and alternatively \cite{DBLP:conf/emsoft/LarsenMNS05}. 
-Unlike timed process algebras, Timed Automata lack high-level 
-compositional patterns for hierarchical design. As a result, users often 
-need to manually cast those terms into a set of clock variables with 
-carefully calculated clock constraints. The process is tedious and error-prone.
-
-We investigate an alternative approach for modeling and verifying 
-compositional real-time systems. In this work, 
-we propose a novel temporal specification language, 
-which enables a compositional verification via a  Hoare-style 
-forward verifier and a term rewriting system (TRS). 
-More specifically, we specify system behaviors in the form of 
-{Timed Effects} (\timedEffects), which integrates the Kleene Algebra 
-with dependent values and arithmetic constraints, 
-%gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
-to 
-%capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
-provide real-time abstractions into traditional linear temporal logics. 
-%Resource usages, provided by a \emph{dynamic ticks}\cite{DBLP:conf/fdl/HanxledenBG17}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
-For example, one safety property, \textit{"The event \anyevent{Done} 
-will be triggered no later than one time unit"}\footnote{Without loss of generality, 
-we use integer values to represent time units in this 
-paper.% while it can bes extended to real numbers and other 
-%time measurement units.
-}, is expressed in \timedEffects\ as: 
-\begin{align*}
-  \code{\effect \defeq \  0 {\leq} t {<}1 \wedge ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}
-\end{align*}  
-%The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
-%and .
-%which replaces temporal operators by time-constrained versions from 
-Here, \code \wedge  connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
-constraints for the \emph{logical-time} sequences \cite{DBLP:conf/fdl/HanxledenBG17}; 
-\code{\_} is a wildcard matching to any event; 
-Kleene star \code{\star} denotes trace repetition.
-The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1)}\ }\anyevent{Done}' 
-in metric temporal logic (MTL), reads \textit{"within one second, 
-\anyevent{Done} finally happens"}.
-
-Moreover, the time bounds 
-can be dependent on the program inputs, demonstrated in 
-\figref{fig:Value_dependent_intro}; we mark the precondition and postcondition
-using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.
-
-\begin{wrapfigure}{L}{0.39\columnwidth}
-\begin{lstlisting}[name=coffee]
-void addOneSugar() 
-/*req: true/\ _^*
-  ens: t>1 /\ emp#t */ 
-{ timeout ((), 1); }
-
-void addNSugar (int n) 
-/*req: true/\ _^*
-  ens: d>=n/\ Sugar#d */
-{ if (n == 0) { 
-      event ["Sugar"];} 
-  else {
-      addOneSugar();
-      addNSugar (n-1);}} 
-\end{lstlisting}
-\caption{Value-dependent specification.} 
-\label{fig:Value_dependent_intro}
-\vspace{0mm}
-\end{wrapfigure}
-
-The function \codem{addNSugar} takes a parameter \codem{n}, representing 
-the portion of the sugar we need to add. When \codem{n} 
-equals to \codem{0}, 
-it simply raises an event \anyevent{Sugar} to mark the end of the process. 
-Otherwise, it adds one portion of the sugar by calling
-\codem{addOneSugar()}, then recursively calls 
-\codem{addNSugar} with parameter \codem{n-1}. 
-The use of statement \lstinline|timeout(e, d)| is standard \cite{JSTO}, 
-which executes a block of code \codem{e} after the specified time \codem{d}.
-Therefore, the time spent on adding one portion of the sugar is 
-no less than one time unit. Note that {\color{darklavender}\code{\emph{emp\#t}}} 
-refers to an empty trace which takes time \codem{t}.
-
-Both preconditions require no arithmetic constraints,   
-and  have no temporal constraints upon 
-the history traces. 
-The postcondition of \codem{addNSugar(n)} indicates that  the method 
-generates a finite trace where \anyevent{Sugar} takes a no 
-less 
-than \codem{d} time-units delay to finish.
-
-Although these examples are simple, they show the benefits of deploying 
-value-dependent 
-time bounds, which is beyond the capability of Timed Automata. Intuitively, if traditional Timed Automata define an 
-\emph{exact} transition system, \timedEffects\ define 
-a set (possibly infinite) of exact transition systems.
-
-Moreover, we deploy a Hoare-style forward verifier to 
-soundly infer the actual behaviors of given programs 
-concerning the well-defined operational semantics. 
-This approach provides a 
-\emph{direct} (opposite to the techniques which require 
- manual and remote modeling processes), 
-  and modular compositional 
-verification for real-time systems, which are not possible
-by existing techniques.
-
-\begin{comment}
-  we express, the effects of \code{addNSugar(d)} as:
-\begin{align*}
-&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
-\end{align*}  
-effects of \code{addNSugar(n)} as:
-\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}
-
-\end{comment}
-
-   %they already illustrate the gain of expressiveness from  existing temporal logics and traditional Timed Automata.
-
-%properties
-
-Having \timedEffects\ to be  the specification language, 
-and the forward verifier to infer the program behaviors, 
-we are interested 
-in the following verification problem: 
-Given a program \code{\mathcal{P}},
-and a temporal specification \code{\effect^{\prime}}, does the inclusions 
-\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds\footnote{The 
-inclusion relation $\CONTAIN$ is formally defined in \defref{Inclusion}.}? Typically, 
-checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.
-
-Since the expressiveness of \timedEffects\ goes beyond 
-finite-state automata, it is neither sufficient nor efficient to 
-translate them 
-into Timed Automata and reply on the solving engines of Timed Automata.
-Therefore we 
-develop a novel TRS, 
-which  is inspired by Antimirov and Mosses’ algorithm\footnote{Antimirov and Mosses' 
-algorithm was designed for deciding the inequalities of regular 
-expressions based on an 
-complete 
-axiomatic algorithm of the algebra of regular sets.} \cite{DBLP:journals/tcs/AntimirovM95} but solving the 
-language inclusions between more expressive \timedEffects.
-
-\begin{comment}
-  several compositional ,  
-are introduced to capture quantitative timing constraints.
-The idea is to
-
-In this work, we study temporal verification of 
-compositional real-time systems,
-
-Existing automatic verification techniques massively rely on 
-the Timed Automata which requires manually cast of clock variables with 
-carefully calculated clock constraints.
-
-A TRS is a refutation method that normalizes expressions in such a way 
-that checking their inclusion corresponds to an iterated process of 
-checking the inclusion of their \emph{partial derivatives} 
-\cite{antimirov1995partial}. 
-Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
-
-This work targets timed temporal verification, and to the best of 
-the authors' knowledge, it proposes the first algebraic TRS 
- for the real-time verification. 
-\end{comment}
-
- In short, the main contributions of this work are:
-
-\begin{enumerate}
-\item \textbf{Language Abstraction:} we formally define 
-a core language \timedL, by defining its syntax and operational semantics, 
-generalizing the real-time systems with mutable variables and timed 
-behavioral patterns. %, such as \emph{delay}, \emph{timeout}, \emph{deadline}.
-
-\item \textbf{Specification Language:} we propose \timedEffects, 
-by defining its 
-syntax and semantics, gaining the expressive power beyond 
-traditional modeling languages for real-time systems.
-
-\item \textbf{Automated Forward Verifier:} we establish a sound axiomatic 
-semantics to infer the 
-temporal behaviors of given target programs.  The verifier triggers the back-end 
-solver TRS.
-
-\item \textbf{An Efficient TRS:}
-we present the rewriting rules to prove the inclusion relations between the inferred 
-behaviors and the given temporal specifications, both in  \timedEffects.
-
-\item \textbf{Implementation and Evaluation:} we prototype the novel 
-effects logic and the automated verification system, 
-prove the soundness, report on case studies and experimental results.
-
-\end{enumerate}
-
-\section{Overview}\label{sec:Overview}
-
-We now highlight our main methodologies, using the example shown 
-in \figref{fig:overview_coffee} This example simulates a 
-coffee machine, which dynamically adds sugar based on the user's input number.
-
-%\subsection{HipHop.js and Dependent Effects}
-\subsection{\timedEffects}
-As shown in \figref{fig:overview_coffee}, we define Hoare-triple 
-style specifications (enclosed in 
-\textcolor{darklavender}{\ttfamily{{/* ... */}}}) for each function, 
-which leads to a compositional verification strategy, where static 
-checking and timed temporal verification can be done locally.
-
-%columns=fullflexible
-\begin{wrapfigure}{L}{0.47\columnwidth}
-  %\vspace{-1mm}
-\begin{lstlisting}[name=coffee]
-void makeCoffee (int n)
-/*req: n>=0 /\ _^* . Cup
-  ens: (n<=t<=5 /\ t1<=3) /\
-       (Sugar#t).(Coffee#t1) */
-{ deadline (addNSugar(n), 5);
-  deadline (event["Coffee"], 3);}
-
-int main ()
-/*req: true/\emp
-  ens: t<=8/\(((!Done)^*)#t).Done */ 
-{ event["Cup"];
-  makeCoffee (3);
-  event["Done"];}
-\end{lstlisting}  
-   %   \vspace{-1mm}
-\caption{To make coffee with three portions of sugar 
-within eight time units.}\label{fig:overview_coffee}
- %        \vspace{0mm}
-\end{wrapfigure}
-
-The precondition of \codem{makeCoffee} 
- specifies that the input integer value \codem{n} is non-negative, and it requires that before entering into this 
-function, this history trace must contain the event  
-\anyevent{Cup} on the tail. Therefore, function calls to \codem{makeCoffee} which 
-do not satisfy the precondition lead to a failure of the verification. 
-\codem{makeCoffee} sets a 
-five time-units deadline while calling 
-\codem{addNSugar} (defined in 
-Fig. \textcolor{black}{\ref{fig:Value_dependent_intro}}),
- with argument \codem{n}; then emits event \anyevent{Coffee} with
- a three time-units deadline.
-
-The precondition of \codem{main} requires no arithmetic constraints 
-on its inputs (expressed as \codem{true}) and 
-an empty history trace (denoted using \codem{emp} or \code{\epsilon}).
-The postcondition of \codem{main} specifies 
-that before the final \anyevent{Done} happens, there is no 
-occurrence of \anyevent{Done} (\codem{!A} refers to the 
-negation of the event \codem{A}). Moreover, the whole process takes 
-no more than eight time-units to hit the final event.
-
-\timedEffects\ supports more features such as \emph{disjunctions}, 
-\emph{guards} and \emph{parallelism}, etc., which can be found in 
-\secref{subsec:Specification_language} and 
-\secref{subsec:Specification_Semantics}.  
-Note that directly from the specifications, we are aware of:  
-(i) the branching properties: different arithmetic conditions on the input parameters lead to different temporal effects;
-and (ii) the required history traces: by defining the prior effects 
-in precondition. 
-The examples 
-already show that our  effects provide more detailed information than 
-traditional timed verification, and in fact, it cannot be fully 
-captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
-Nevertheless, the gain in expressive power comes from the efforts 
-of a more dedicated verification process, handled by our forward verifier and TRS.
-
-\subsection{Forward Verification}
-As shown in \figref{fig:forward_example}, we demonstrate the 
-forward verification process of the functions \codem{addOneSugar} and   {\codem{addNSugar}}.
-The current effects states are captured 
-in the form of 
-\code{\{ \textcolor{darklavender}{\effect_C} \}}. 
-To facilitate the illustration, we label the verification 
-steps by (1), ..., (11), and mark the deployed inference 
-rules (cf. \secref{Forward_Rules}) in \textcolor{mGray}{[gray]}.
-The verifier invokes the TRS to check language inclusions along the way.
-
-\begin{comment}
-
-/*require n>=0, _^*
-  ensure  t>=n, Sugar#t */
-{
-
-\end{comment}
-
-{
-\begin{figure}[!ht]
-    %  \vspace{-4mm}
-     \begin{minipage}[c]{\columnwidth}
-         \centering
-         {%\small
-         \begin{enumerate}
-\item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
-\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}.}} \\
-\textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
-\quad \siderule{\scriptsize[FV\text{-}Meth] } \\
-
-\item ~\qquad \lstinline|timeout ((), 1);}| \\
-\textcolor{darklavender}{\code{\effect_C^\prime {=} t_0{>}1   \wedge \_^\star \cdot \epsilon \mysharp t_0  }} 
-\quad \siderule {\scriptsize [FV\text{-}Timeout]}
-\item 
-\textcolor{darkred}{\code{
-%\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
-\effect_C^\prime \CONTAIN \effect_{pre}^{addOneSugar(n)} \cdot \effect_{post}^{addOneSugar(n)} \Leftrightarrow  }} 
- %\textcolor{mGray}{  \emph{(-- check postcondition --) }}
- \textcolor{darkred}{\code{\code{\code{t_0{>}1   \wedge \epsilon \mysharp t_0}
- \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
- \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked. }}
- \\ 
-%ens: t>1 /\ emp#t */ { 
-  \noindent\rule{0.92\columnwidth}{0.4pt}
-  \vspace{2mm}
-~\\
-\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize 
-\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addNSugar(n)}}.}} \\
-     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  true \wedge  \_^\star \} }} 
-      \quad \siderule{\scriptsize[FV\text{-}Meth] } \\
-     \item ~\qquad \lstinline|if (n == 0) {| \\
-     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} 
-     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
-      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
-     \textcolor{darklavender}{\code{\{n{=}0 \wedge   \_^\star \cdot Sugar\} }} 
-     \quad \siderule{\scriptsize [FV\text{-}Event]}
-     \item 
-     ~\qquad \lstinline|else {| \\
-     \textcolor{darklavender}{\code{\{ n  {\neq} 0 \wedge   \_^\star \}  }} 
-     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
-    \item 
-     ~\qquad~\qquad \lstinline|addOneSugar();| \\
-     \textcolor{darklavender}{\code{\{n  {\neq} 0 \wedge  t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} 
-     \quad \siderule {\scriptsize [FV\text{-}Call]}
-     \item 
-     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
-     \textcolor{huntergreen}{\code{n  {\neq} 0   \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
-      \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: precondition checked.}}
-\\
-     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
-     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
-     \quad \siderule {\scriptsize [FV\text{-}Call]}
-      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
-      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }} 
-      \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
-      %\quad \siderule {\scriptsize [Normalization]}
-      \\
-       \item 
-       %\textcolor{mGray}{  \emph{(-TRS: check the  postcondition; Succeed, cf. \autoref{tab:rewriting_tree_send}-) }}\\
-       \textcolor{darkred}{\code{
-       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
-       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}  
-       \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked, cf. \autoref{tab:rewriting_tree_send}. }}
-        \\ 
-        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
-        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\
-
-\end{enumerate}}
-
-     \end{minipage}
-
-      \caption{The forward verification example for method \code{send}. }\label{fig:forward_example}
-     % \vspace{-4mm}
-\end{figure}
-}
-
-The effects states (1) and (4) are obtained by initializing 
-\code{\effect_C} from the precondition, by the \code{[FV\text{-}Meth]} rule. 
-The effects states (5), (7), and (10) are obtained by  
-\code{[FV\text{-}If\text{-}Else]}, which adds the constraints 
-from the conditionals into the current effects state, 
-and unions the effects accumulated from two branches in the end. 
-The effects states (6) is obtained by \code{[FV\text{-}Event]}, 
-which concatenates the triggered singleton event to the 
-end of the current effects state.
-
-The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
-Before each function call, it invokes the TRS to check whether the current effects state 
-satisfies the precondition of the callee function. 
-If it is not satisfied, the verification fails; otherwise, 
-it concatenates the callee's postcondition to the current 
-effects state (the precondition check for step (8) is omitted here).
-
-The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
-which adds a lower time-bound to the trace. 
-After these states transformations, steps (3) and (11) check the 
-satisfiability of the inferred effects against the declared 
-postcondition by invoking the TRS.
-
-Note that the prior effects in precondition are new regarding 
-the existing real-time verification.
-
-\subsection{The TRS}
-
-Our TRS is 
-%obligated to check the inclusions between \effectNameSyncEffs, which is 
-an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{DBLP:journals/tcs/AntimirovM95}  
-decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their 
-\emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
-$\codeme{[DISPROVE]}$, which infers false from trivially inconsistent inequalities; and  
-$\codeme{[UNFOLD]}$, which applies \autoref{RegularInclusion} to generate new inequalities.
-In detail, given \code{\Sigma} is the whole set of the alphabet, 
-\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the event \code{\anyevent{A}}.
-
-\begin{definition}[REs Inequality]\label{RegularInclusion}  For REs \code{r} and \code{s}, \code{r \preceq s \Leftrightarrow \forall (\anyevent{A} \in \Sigma).\ D_{\anyevent{A}}(r) \preceq D_{\anyevent{A}}(s)}.
-\end{definition}
-
-\begin{definition}[\timedEffects\ Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
-For \timedEffects\ \code{\effect_1 } and \code{\effect_2}, 
-\code{\effect_1 { \CONTAIN} \effect_2 {\Leftrightarrow} \forall \anyevent{A}. \forall t {\geq} 0.\ D_{\anyevent{A} \mysharp  t}(\effect_1)  
-{\CONTAIN} D_{\anyevent{A} \mysharp  t}(\effect_2)}.
-\end{definition}
-%\in fst(\effect_1)
-
-Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  
-between \timedEffects, where \code{D_{\anyevent{A}\mysharp  t}(\effect)} 
-is the partial derivative of \code{\effect} w.r.t the event 
-\anyevent{A} and the time variable \code{t}.
-
-%Adapting to the context of checking inclusions between \timedEffects, we extend the Antimirov algorithm with
-
-%The rule \code{[REOCCUR]} finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{DBLP:conf/tableaux/Brotherston05}.
-(We use \code{\textcolor{persianplum}{(\dagger)}} in \tabref{tab:rewriting_tree_send} to indicate such pairings.)
-
-%(introduce \code{t_L^1} and \code{t_L^2}, let \code{t_L^1 {+} t_L^2 {=} t_L}
-
-%(\code{\{Cook\} {\Rightarrow} \{Cook\}}, \code{t_L^1 {+} t_L^2 {<}3 {\Rightarrow} t_L^1 {<}3})
-
-Next, we continue with the step (11) in \figref{fig:forward_example}, to 
-demonstrate how the TRS handles arithmetic constraints and dependent values. 
-%We use the postcondition proving for function \code{main} as an example to briefly demonstrate the rewriting process. 
-As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
- satisfy the declared postcondition. 
-%property \code{\effect_1  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\mysharp  t)\cdot\_^\star}, 
-%where \code{\effect_1} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces.
-We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.
-
-{
-\begin{table*}[ht]
-\centering
-     % \vspace{0mm}
-\caption{\label{tab:rewriting_tree_send} The inclusion proving example. 
-\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}
-
-\vspace{-1mm}
-\begin{adjustbox}{width=1\textwidth}
- \Large\begin{tabular}[t]{l}
-  \hline\\
-
-  \code{(I):}\quad
-
-  {
-\begin{prooftree}
-\hypo{\text{\textcircled{4}}
-  \code{\siderule{[\codeme{PROVE}]}}
-}
-
-\infer[dashed]1[]{ \code{\textcolor {darkred}{n{=}0} \wedge \epsilon 
-\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \epsilon \mysharp t_r}}
-
-%\textcolor{blue}{\code{\pi_u : true}}
-\infer[dashed]1[{\textcircled{3}\siderule{[\codeme{UNFOLD}]}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge \cancel{Sugar}
-\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \cancel{Sugar \mysharp t_r}}}
-
-\hypo{\qquad \code{(II)}}
-
-\infer[dashed]2[{\textcircled{2}\siderule{[\codeme{LHS\text{-}OR}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
-\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge \epsilon \mysharp t \cdot 
- Sugar \mysharp t_l) } 
-\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r  }
-
-\infer[dashed]1[{\textcircled{1}\siderule{[\codeme{RENAME}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
-\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1}  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
-\CONTAIN \effect_{post}^{addNSugar(n)}  }
-\end{prooftree}}
-\\~\\
-
-\hline \\
-\code{(II):} \quad\ \
-
-{\begin{prooftree}
-  \hypo{
-  \code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
-   \wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
-}  } 
- }
-
- \infer[dashed]1[{\textcircled{7}\siderule{[\codeme{PROVE}]}}]{ \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
- \epsilon
-\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
-\wedge \epsilon}}
-
- \infer[dashed]1[{\textcircled{6}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1)}}]
- { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
-\cancel{ Sugar \mysharp t_l}
-\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
-\wedge \cancel{Sugar \mysharp t_r^1}}}
-
- \infer[dashed]1[{\textcircled{5}\siderule{[\codeme{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
- { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \cancel{\epsilon \mysharp t} \cdot 
- Sugar \mysharp t_l
-\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \cancel{\mysharp t_r}}}
-
-\end{prooftree}
-}
-
-\\~\\
-
-\hline
-
-\end{tabular}
-\end{adjustbox}
-      %      \vspace{0mm}
-\end{table*}
-}
-
-As shown in \tabref{tab:rewriting_tree_send}, step 
-\textcircled{1}, renames the time variables to avoid 
-the name clashes between the antecedent and the consequent.  
-Step \textcircled{2} splits the proof tree into two 
-branches, according to the different 
-arithmetic constraints, by rule  $\codeme{[LHS\text{-}OR]}$.
-
-In the first branch, step \textcircled{3} takes the rule 
-$\codeme{[UNFOLD]}$ to eliminate the head of the antecedent. 
-Step \textcircled{4} proves the inclusion, because 
-evidently the consequent \code{t_r {\geq} 0 \wedge \epsilon \mysharp t_r} 
-contains \code{epsilon} when \code{t_r{=}0}.
-
-In the second branch, step \textcircled{5} eliminates the 
-head of the antecedent, where the head is a time duration \code{\epsilon\mysharp t}. 
-Therefore the rule $\codeme{[UNFOLD]}$ subtract the time duration 
-from the consequent, leaving a fresh time variable \code{t_r^1} and 
-an unification constraint \textcolor{blue}{\code{\pi_u : t_r{=}t_r^1 {+}t}}. 
-Similarly, step \textcircled{6} eliminates the head 
-\code{\anyevent{Sugar}\mysharp t_l}, adding \textcolor{blue}{\code{t_l{=}t_r^1}} 
-to the unification constraints. 
-At the end of the rewriting, step \textcircled{7} manages to prove that 
-\code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
-\wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
-}  } \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{DBLP:conf/tacas/MouraB08}.}; therefore, the proof succeed.
-
-%(\code{\{Go\} \Rightarrow \_})
-%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
-Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using 
-\emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf.\ \tabref{tab:reoccur}.
-
-\subsection{Verifying the Fischer’s Mutual Exclusion Protocol}
-
-\begin{wrapfigure}{L}{0.51\columnwidth}
-  \vspace{-5mm}
-\begin{lstlisting}
-var x := -1; 
-var ct:= -1;
-
-void proc (int i) {
-  [x=-1] 
-  deadline(event["Update"(i)]{x:=i},d1);
-  delay (d2);
-  if (x=i) {
-    event["Critical"(i)]{ct:=i};
-    event["Exit"(i)]{ct:=-1; x:=-1};
-    proc (i);
-  } else {
-    proc (i);}}
-
-void main () 
-/*req: d1<d2/\emp
-  ens: true /\ (([ct=-1]\/[ct=x])^*) */ 
-{ proc(0) || proc(1) || proc(2); }
-\end{lstlisting}  
-  %\vspace{-1mm}
-  \caption{Fischer's mutually exclusion algorithm.}\label{fig:overview_ficher}
-    % \vspace{-2mm}
-\end{wrapfigure}
-
-\figref{fig:overview_ficher} presents the classical 
-Fischer's mutually exclusion algorithm. 
-where \codem{d1} and \codem{d2} are two integer constants
- with \codem{d1<d2}; 
-\codem{x} and \codem{ct} are global variables. The protocol is 
-modeled as 
-process protocol, which is the parallel composition of three 
-processes. Each of the three processes attempts to enter 
-the critical section when \codem{x} is \codem{-1}, i.e. no 
-other process is 
-currently attempting. Once the process is active, it sets \codeme{}{x} 
-to its identity \codem{i} within \codem{d1} time units (captured by \codem{deadline(..., d1}). 
-Then it idles for \codem{d2} time units (captured by \codem{delay(d2)}) and then 
-checks whether \codem{x} is still \codem{i}. If so, 
-it enters the critical 
-section and leaves later. Otherwise, it restarts from the 
-beginning.
-
-We show the specification of \codem{main} using \timedEffects, which
-restricts the relation between \codem{d1} and \codem{d2}. When 
-\codem{d1<d2} is provided, it ensures a global state, i.e., the repeated trace, where the value of 
-\codem{ct} is either \codem{-1} or equals to \codem{x}. The specification
-implies that this implementation is indeed mutual exclusive. 
-Our prototype system is able to soundly check such time-critical 
-algorithms. \secref{sec:Evaluation} presents the details about the implementation and evaluation.
-
-\section{Language and Specifications}
-\label{sec:LanguageSpecifications}
-
-\subsection{The Target Language}
-\label{subsec:Targetlanguage}
-
-To formulate the target language, we generalize the design of the real-time systems
- into a core language \code{\timedL}, 
- which provides the infrastructure for mutable variables and timed behavioral patterns, 
- such as \emph{delay}, \emph{timeout}, \emph{deadline}. 
-We here formally define the syntax of \code{\timedL}, as shown in \figref{fig:code_language}
-
-{
- % \vspace{-2mm}
-\begin{figure}[!ht]
-\renewcommand{\arraystretch}{1.1}
-\centering%\small
-  $
-  \begin{array}{lrcl}
-
-    \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }&
-    \code{%{datat^*}  \  
-   (\alpha^*, {meth^*})} 
-    \\
-
-    \m{(Basic\ Types)} &   \code{\iota} &\code{  ::=  }&
-     \code{int\ |\ bool\ |\ void}
-
-    \\
-%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
- %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
- %   \\
-
-  \m{(Method\ Def.)} &  \code{meth}&\code{ ::= }&
-  \code{\iota\  mn  \ {(\iota\ x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
-  \\
-  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
-  \\
-
-  \m{(Assignment)} &  \code{\alpha }&\code{  ::= }&
-  \code{x:=v} 
- \\
-  \m{(Expressions)} &  \code{e}&\code{  ::= }&
-    \code{ v \ 
-    | \ \alpha \ | \ 
-    [b]\ e \ |\ mn({v^*}) \ }
-  \code{|  \ e_1;e_2\ | \ e_1 || e_2 \ 
-  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
- }  \\
-
- &   & & \code{
-  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] \ 
-  | \ \textbf{delay} [t] \ 
-  | \ e_1\ \textbf{interrupt} [t] \  e_2 \ 
-  }  \\
-
-  &   & & \code{
-    | \ e_1\ \textbf{timeout} [t] \  e_2 \ 
-    | \ e \ \textbf{deadline}  [t] \ 
-    | \ e \ \textbf{waituntil} [t]  \ 
-    }  \\
-
-    \m{(Real\text{-}Time\ Terms)}  & \code{t} &\code{  ::= }&
-    \code{ c
-    \ | \  x
-    \ | \  t_1{+}t_2
-    \ | \  t_1\text{-}t_2
-   }
-
-    \\
-    ~\\
-
-    \multicolumn{4}{c}{
- % \code{k^\tau:constant\ of\ type\ \tau\ } 
- % \qquad\quad
-\code{c  \in \mathbb{Z}}
-\qquad \qquad 
-\code{b  \in \mathbb{B}}
-\qquad \qquad  
-\code{x, mn  \in \textbf{var}}  
-\qquad \qquad 
- \code{(Action\ labels)\ \anyevent{A}  \in \Sigma %\cup \{\tau\}
-%\qquad\ 
-%\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
-}   
-    }\\  
-    \hline
-  \end{array}  
-  $
- \caption{A core first-order imperative language with timed constructs, \timedL.} 
- \label{fig:code_language}
-
-\end{figure}
-}
-
-Here, \code{c} and \code{b} are for integer and Boolean constants, 
- \code{mn} and \code{x} are for meta-variables.  
- \textbf{var} represents the countably infinite set of arbitrary distinct identifiers.
-
-A program \code{\mathcal{P}} comprises a list of 
-global-variable initializations \code{\alpha^*} and 
-a list of 
-method declarations \code{{meth^*}}. 
-Here, we use the \code{*} superscript to denote a finite list (possibly empty) of items, for example, \code{{x^*}} refers to a list of variables, \code{x_1, ...,\ x_n}. 
-%Besides, \code{d} denotes the name of a user-defined data type, \code{f} denotes a field name. 
-Each method \code{meth} has a name \code{mn}, an expression-oriented body \code{e}, also is associated with a precondition  \code{\effect_{pre}} and a postcondition \code{\effect_{post}} (the syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects}).
-The language allows each iterative loop to be optimized to an equivalent 
-tail-recursive method, where mutation on parameters is made visible 
-to the caller. 
-%The technique of translating away iterative loops is standard
-%\citeref{insa2015automatic} 
-%and is helpful
-
-Expressions comprise simple values \code{v};
-a guarded process is written as \code{[b]e} where if \code{b} is true, 
-then it behaves as \code{e}, else it idles until \code{b} becomes true; 
-%one-level field access \code{v.f} (rather than \code{v.f1.f2...} for the sake of simplicity), 
-%data structure allocation \code{\textbf{new}\ d({v^*})},  
-%local variable declaration \code{\alpha; e}, 
-method calls \code{mn({x^*})}; 
-%variable assignments \code{\alpha}; 
-%field update \code{v.f:=e}, 
-expression sequences \code{e_1;e_2};
-parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
-may communicate via multi-party event synchronization or shared variables; 
-conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}.
-
-The expression \code{ \textbf{event} [\anyevent{A}(v,  \alpha^*)] } 
-raises an event \anyevent{A}, which comes from the finite 
-set of event labels \code{\Sigma}. %or can be an invisible event, denoted by $\tau$. 
-Without loss of generality, events can be further parametrized with 
-one constant value \code{v} and a set of assignments \code{\alpha^*} upon 
-the mutable variables. %e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events. 
-%leading to infinite alphabet.
-%We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
-%Each events raising expression \code{\textbf{event}} is parametrized with an event, to trigger such a single event.
-
-%parametrized with \code{v}, 
-%and takes a set of 
-%assignment actions \code{\alpha^*}.
-
-Furthermore, a number of timed process constructs can be used to capture common 
-real-time system behavior patterns. Without loss of generality, we 
-assume \code{d} is a non-negative integer constant.  
-$\textbf{delay} [d]$ idles for exactly $d$ 
-time units.
- In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
-$e_1$ shall occur before d time units elapse (since the process starts). 
-Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
-Note that the usage of timeout in \figref{fig:Value_dependent_intro} is a 
-special case of the primitive presented here, where \code{e_1} never starts. 
-Process $\textbf{deadline} [d]\ e$ constraints $e$ to terminate before $d$ time units.
-
-In this setting, clock variables are 
-made implicit and hence they cannot be compared with each other 
-directly, which potentially allows efficient clock manipulation and 
-hence system verification.
-
-%
-
-\subsection{Semantics of the target language}
-\label{subsec:Targetlanguage_Semantics}
-
-In order to define the operational semantics of a system model, 
-we define the notion of a configuration, in \defref{sys_configuration}, to capture 
-the global system state during system execution.
-
-\begin{definition}[System configuration]\label{sys_configuration}
-A system configuration \code{\zeta} is a pair $(\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
-\end{definition}
-
-A transition of the system is of the form $\zeta \xrightarrow[]{l} \zeta^\prime$ 
-where $\zeta$ and $\zeta^\prime$ are 
-the system configurations before and after the transition respectively. 
-%There are four type of the transition labels  :
-We adopt the following naming convention \cite{DBLP:conf/icfem/SunLDZ09} for the transition labels \code{l}: 
-(1) $t$, denoting a non-negative real integer; 
-(2) $\tau$, denoting an invisible event; % which do not make changes to the global valuation;
-(3) $\anyevent{A}$ is an observable event. 
-%and (4) $\sigma \in \Sigma\cup \{\tau\}$. 
-For example, $\zeta \xrightarrow[]{\text{t}} \zeta^\prime$ denotes a transition 
-of \code{t} time-units elapsing. 
-In the following, we present the firing rules which are associated with 
-the timed process constructs.
-
-\input{rules/op_delay.tex}
-
-The above captures behaviors of process \textbf{delay}[d]. 
-Rule \code{[delay_1]} states that the process may idle for 
-any amount of time as long as it is less than or equal to \code{d} time units; 
-Rule \code{[delay_2]} states that the process terminates immediately after 
-\code{d} becomes \code{0}.
-
-\input{rules/op_to.tex}
-
-If an observable event \anyevent{A} can be engaged by \code{e_1}, 
-then $e_1\ \textbf{timeout}[d]\ e_2$ becomes \code{e_1^\prime} (rule \code{[tot_1]}). 
-An invisible transition continues the waiting on \code{e_1} (rule \code{[tot_2]}). 
-If \code{e_1} may idle for less than or equal 
-to \code{d} time units, so is the composition (rule \code{[tot_3]}). 
-When \code{d} becomes \code{0}, 
-\code{e_2} takes over control by a silent transition (rule \code{[tot_4]}).
-
-\input{rules/op_ddl.tex}
-
-Intuitively, $\textbf{deadline}\  [d] \ e$ behaves exactly as 
-\code{e} except that it must terminate before \code{d} time units.
-
-\input{rules/op_gu.tex}
-
-The guarded process \code{[b]e} behaves as \code{e} when \code{b} is true, 
-otherwise it idles until \code{b} becomes true.
-
-{{\small\begin{flalign*}
-\code{\frac{
-  (\env,e_1) \xrightarrow[]{l} (\env^\prime,e_1^\prime) 
-}{(\env, e_1; e_2 ) \xrightarrow[]{l} (\env^\prime, e_1^\prime ; e_2)}\ [seq_1]} 
-\qquad
-\code{\frac{
-}{(\env, (); e_2 ) \xrightarrow[]{\tau} (\env, e_2)}\ [seq_2]} 
-\qquad
-\code{\frac{
-  (\env,e_1) \xrightarrow[]{l} (\env^\prime,e_1^\prime) 
-}{(\env, e_1 || e_2 ) \xrightarrow[]{l} (\env^\prime, e_1^\prime || e_2)}\ [par_1]} 
-\\ 
-  \code{\frac{
-    (\env,e_2) \xrightarrow[]{l} (\env^\prime,e_2^\prime) 
-  }{(\env, e_1 || e_2 ) \xrightarrow[]{l} (\env^\prime, e_1 || e_2^\prime)}\ [par_2]} 
-  \qquad \qquad 
-  \code{\frac{
-    (\env,e_1) \xrightarrow[]{t} (\env,e_1^\prime) 
-    \qquad 
-    (\env,e_2) \xrightarrow[]{t} (\env,e_2^\prime) 
-  }{(\env, e_1 || e_2 ) \xrightarrow[]{t} (\env, e_1^\prime || e_2^\prime)}\ [par_3]} 
-\end{flalign*}}}
-
-Rules \code{[seq_1]} and \code{[seq_2]} state that \code{e_1} takes the control 
-when it still can behave; then the control transfers to \code{e_2} when \code{e_1}
-terminates. Rules \code{[par_1]} and \code{[par_2]} state that in a parallel composition, 
-if any of \code{e_1} or \code{e_2} can proceed, they proceed on their own. Rule 
-\code{[par_3]} states that if both of the branches idle, they idle together.
-
-\subsection{The Specification Language}
-\label{subsec:Specification_language}
-
-We plant the effects specifications into the Hoare-style verification system, using \code{ es_{pre}} and \code{  es_{post} }  to capture the temporal pre/post 
-condition. %\code{es_{pre}} and the postcondition \code{es_{post}}.
-
-{
-    \vspace{0mm}
-\begin{figure*}[ht]
-\renewcommand{\arraystretch}{1.1}
-\centering
-  $
-  \begin{array}{rrcl}
-
-    \m{(Timed\ Effects)} &  \effect &\code{  ::= }&
-    \code{
-          {\pi} \wedge \es
-   \ | \ \effect_1 \vee \effect_2
-}
-    \\
- \m{(Event \ Sequences)}  & \ \code{\es}   &\code{ ::=}&
-
-   \code{ \bot 
-   \  | \  \epsilon 
-    \ | \ \ev
-   \  | \ \es_1 \cdot \es_2
-    \ | \ \es_1 \vee \es_2
-    \ | \ \es_1 {||} \es_2
-    \ | \ \pi ? 
-      %    \  | \ \es_1 \times \es_2
-      \ | \ \es \mysharp  t 
-   \  | \  \es^\star
-}
-
-\\
-\m{(Events)} & \ev  &  ::=  & 
-\code{
-  \anyevent{A}(v, \alpha^*)
-    \ | \ \tau (\pi)
-    \ | \ \anynotevent{A} 
-    \ | \ \_  
-}
-
-\\
-
-    \m{(Pure)}  & \code{\code{{\pi}}}&\code{  ::= }&
-{ {True}}
-   \ |  {False}
-   \ |  {A(}{t_1, t_2}{)}
-  \  |   {{\pi_1}}  \wedge  \code{{\pi}}_2
-   \ |  {{\pi_1}} {\vee} \code{{\pi}}_2
-   \ |  \neg\code{{\pi}}
-  \  |   {{\pi_1}} {\Rightarrow} {{\pi_2}}
-  % \ |  \forall x. \code{{\pi}}
-  %s \ |  \exists x. \code{{\pi}}
-
-    \\
-
-    \m{(Real\text{-}Time\ Terms)}  & \code{t} &\code{  ::= }&
-    \code{ c
-    \ | \  x
-    \ | \  t_1{+}t_2
-    \ | \  t_1\text{-}t_2
-    %\ | \ k {\times} n
-   }
-
-    \\~\\
-    \multicolumn{4}{c}{
-     % \code{(Events)  \anyevent{A} ::\in \Sigma}   
-   %\qquad
-    \code{c \in \mathbb{Z}} 
-     \qquad \qquad 
-           \code{x  \in \textbf{var} } 
-           \qquad\qquad
-
-     \m{(Real\ Time\ Bound)}\ \code{\mysharp }
-     \qquad \qquad 
-        \m{(Kleene\ Star) \ \star}
-
-}\\     
-      \hline
-
-  \end{array}  
-  $ \\
-  \caption{Syntax of \timedEffects.}
-  \label{fig:Syntax_of_Types_and_Effects}
-  \vspace{0mm}
-\end{figure*}
-
-}
-
-The  syntax of the \timedEffects\ is formally defined in 
-\figref{fig:Syntax_of_Types_and_Effects} Effects is 
- a conditioned event sequence \code{{\pi}\wedge es} or a disjunction of 
- two effects $\effect_1 \vee \effect_2$.
-Timed sequences comprise \textit{nil} ($\bot $);
- an empty trace $ \epsilon$;
-a single event \code{ev};
- sequences concatenation \code{\es_1\cdot \es_2};
-disjunction  \code{\es_1\vee \es_2};
-parallel composition of two processes is written as \code{\es_1 || \es_2}, where \code{\es_1} and \code{\es_2} 
-may communicate via multi-party event synchronization or shared variables;
-a blocking waiting for a certain constraint to be satisfied \code{\pi ?}; 
-We introduce a new operator \code{\mysharp }, and the effects 
-\code{\es \mysharp t} represents that a trace takes real-time 
-\code{t} to complete, where \code{t} is a \emph{term}. 
-A timed sequence can be constructed by \code{\es^\star}, representing zero or 
-more times repetition of the trace \code{\es}.
-
-\anyevent{A}\code{(v, \alpha^*)} stands for an observable event with label 
-\anyevent{A}, parameterized by \code{v}, and the assignment operations \code{\alpha^*}; and 
-\code{\tau(\pi)} is an invisible event, which can be parameterized with a pure formula 
-\code{\pi}\footnote{The difference between 
-\code{\tau(\pi)} and \code{\pi?} is \code{\tau(\pi)} leads to false (\code{\bot}) if 
-\code{\pi} is not satisfied, whereas  \code{\pi?} waits until \code{\pi} is satisfied.}. 
-To make the specification more practical, events can also be 
-{\anynotevent{A}}, referring to those events which are not 
-labeled using \anyevent{A}; and a wildcard \code{\_}, which matches to all the events.
-
-We use \code{{\pi}} to denote a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
-We use \code{{A(}{t_1, t_2}{)}} to represent atomic formulas of two terms (including $  {=},
-   \ {>},
-   \ {<},
-   \ {\geq}\ $ and $ {\leq} $).
-%e.g. the equality between constant 0 and an integer variable \code{x}.
-A term can be a constant integer value \code{c}, an integer variable \code{n} which is an input parameter of the program and can be constrained by a pure formula. 
-A term also allows simple computations of terms, \code{t_1{+}t_2} and \code{t_1\text{-}t_2}.
-To abstract the elapsed time, the default and implicit pure constraints of all the terms is to be greater or equal to  0.
-
-\subsection{Semantic Model of Timed Effects}
-\label{subsec:Specification_Semantics}
-
-To define the model, 
-\code{var} is the set of program variables, 
-\code{val} is the set of primitive values, 
-\code{\es} is the set of event sequences (or event multi-trees, per se), 
-indicating the sequencing constraints on temporal behaviors.
-
-Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
-the effects \code{\effect} take \code{d} time units to complete; 
-the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
-temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
-from the following concrete domains: \code{d}  :\  \code{\mathbb{N}}, 
-\code{s}  :\  \code{var {\rightarrow} val } and \code{\varphi}   :\ \code{\es} \ .
-
-\begin{figure}[!ht]
-  %\vspace{-3mm}
-  \renewcommand{\arraystretch}{1.2}
-\small\begin{align*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%     Disjunction        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models \effect_1 \vee \effect_2}  
-&\m{iff}\quad & \code{d, s, \varphi \models \effect_1 } \ 
-or\ \code{d, s, \varphi \models \effect_2 }  \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%         Empty          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s,  \varphi \models {\pi} \wedge  \epsilon}  
-&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
-{True} } \ and\  \code{ \varphi {=} [] }\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%         Event          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge \ev }  
-&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
-{True} }\ and \ \varphi {=} [\ev]  \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%     Concatenate        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge (\es_1\cdot \es_2)}  
-&\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
-\code{ \varphi_1 {\lappend} \varphi_2 {=} \varphi}\ and\ 
-\exists \code{d_1,d_2}. \  
-\code{ d_1 {+} d_2 {=} d} \\
-&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} {\pi}  \wedge \es_1 }
-\ and \ \code{d_2, s, \varphi_2 {\models} {\pi}  \wedge \es_2 }\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    disjunction         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge (\es_1{\vee}\es_2)}  
-&\m{iff}\quad & 
-\code{d, s, \varphi \models {\pi}  \wedge \es_1 } 
-\ or\  
-\code{d, s, \varphi \models {\pi}  \wedge \es_2 } \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    parallel         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge (\ev_1 \cdot \es_1)||(\ev_2 \cdot \es_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models {\pi}  \wedge \ev_1 \cdot  (\es_1||(\ev_2 \cdot \es_2)) } 
-\ or\ \code{d, s, \varphi \models {\pi}  \wedge \ev_2 \cdot ((\ev_1 \cdot \es_1)||\es_2)  } \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    parallel  2        %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
-&\m{iff}\quad & \code{d, s, \varphi \models {(\pi \wedge t_1 {\geq}t_2)} \wedge (\ev\mysharp t_1) } 
-\ or\ \code{d, s, \varphi \models {(\pi \wedge t_1 {<}t_2)}  \wedge (\ev\mysharp t_1) \cdot (\epsilon \mysharp  (t_2\text{-}t_1))  } \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    block         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi} \wedge \pi_1 ? \es}  &\m{iff}\quad & 
-\code{\llbracket \pi_1  \rrbracket_{s} {=}  
- {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge \es}\ or  \ 
-  \code{\llbracket \pi_1 \rrbracket_{s} {=}  
-{False} }, 
-\  \code{d, s, \varphi \models {\pi} \wedge \pi_1 ? \es}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    t times         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi}  \wedge \es\mysharp  t}  &\m{iff}\quad &
- \code{\llbracket {\pi}  \wedge t {=} 0 \rrbracket_{s} {=}  
- {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or  \\
-& & &  \code{\llbracket {\pi}\wedge t {>} 0 \rrbracket_{s} {=}  
-{True} }, 
-\  \exists \code{\es_1,\es_2}. \  \code{\es_1  \cdot  \es_2 {=} \es}, \  \m{fresh}\ t_1, t_2,\\
-&&& \qquad  s.t. \ \code{d, s, \varphi {\models} {(\pi 
- \wedge  t_1{\geq}0 \wedge t_2{\geq}0  \wedge  t_1{+} t_2{=}t)} \wedge 
-(\es_1\mysharp t_1)  \cdot  (\es_2\mysharp t_2) } \\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    star         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, s, \varphi \models {\pi}\wedge \es^\star}  &\m{iff}\quad & 
-\code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or \ 
-\code{d, s, \varphi \models {\pi}  \wedge \es  \cdot  \es^\star}\\
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%    FALSE         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-& \code{d, s, \varphi \models false}  &\m{iff}\quad &
- \code{\llbracket {\pi}  \rrbracket_{s} {=} {False} } \ or \ \code{\varphi {=} \bot }
-\end{align*}
- % \vspace{-2mm}
-\caption{Semantics of \timedEffects.}
-\label{fig:Sementic}
-%\vspace{-2mm}
-\end{figure}
-
-As shown in \figref{fig:Sementic}, we define the semantics of our effects. 
-We use $\lappend$ to represent the append operation of two event sequences. 
-We use $[]$ to describe the empty sequence, \code{[\ev]} to represent 
-the sequence that only contains one singleton event. 
-Notice that, except for the traces constructed by \code{\mysharp}, simple events 
-are taken to be happening in instant time.
-
-\begin{comment}
-
-\begin{figure}[ht]
-    \vspace{-1mm}
-    \renewcommand{\arraystretch}{1}
-\begin{align*} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          Disjunction                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models \es_1 {\vee} \es_2}  
-&\m{iff}\quad 
-&  d, \varphi \models \es_1 \ or \ d, \varphi \models \es_2
-\\[0.2em]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          EMPTY                          %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models \pi :  \epsilon }  
-&\m{iff}\quad 
-&  d{=}0 \ and\  {\tt{SAT}(\pi)}  \ and \ \varphi {=} [] 
-\\[0.2em]
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                          I                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : ev }  &\m{iff}\quad 
-& d {\geq} 0 \ and\ {\tt{SAT}(\pi)}  \ and \ 
-\varphi {=} \code{[ev]}
-  \\[0.2em]
-  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            CONCATENATE                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1 \cdot \es_2)}  
-&\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \exists \code{\varphi_1, \varphi_2, d_1, d_2}\ and\ \code{
-\varphi {=} \varphi_1 \lappend \varphi_2, d {=} d_1 {+} d_2 \ and 
-}\\
-& & &
-\code{d_1, \varphi_1 \models  \pi : \es_1}  \ and \ 
-\code{d_2, \varphi_2 \models  \pi : \es_2}  
- \\[0.2em]
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                       DISJUNCTION                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : (\es_1 {\vee} \es_2)}  
-&\m{iff}\quad 
-& {\tt{SAT}(\pi)}  \ and \ \code{d, \varphi \models  \pi :  \es_1 } \ or \ 
- \code{d, \varphi \models  \pi :  \es_2}  
-\\[0.2em]
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                       timed                         %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-&\code{d, \varphi \models  \pi : es \mysharp  t }  
-&\m{iff}\quad 
-& d, \varphi \models  (\pi \wedge t{=}d) : es
-\\[0.2em]
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            KLEENE                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-   %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%                            FALSE                            %%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-& \code{d, \varphi \models False : \bot }  
-&\m{iff}\quad 
-&   otherwise
-%{\tt{UNSAT}(\pi)}  \ or \  \varphi  {=} \bot
-%\exists t, d(t) \not\models \llbracket {\pi} \rrbracket_{t}
-\end{align*}
-    \vspace{-3mm}
-\caption{Semantics of \timedEffects.}
-\label{fig:Sementic}
-  \vspace{-1mm}
-\end{figure}
-
-To define the semantic model, 
-we use \code{\varphi} (\emph{a trace of events}) to represent 
-the computation execution (or events multi-trees, per se), indicating 
-the sequential constraint of the temporal behavior; and we use \code{d} 
-to record the computation duration of given effects. 
-Let \code{d, \varphi \models es} denote the model relation, i.e., 
-the effects \code{es} take exactly \code{d} time units to complete; and 
-the linear temporal sequence \code{\varphi} satisfies the sequential time  instances defined from \code{es}, with \code{d}, \code{\varphi} from the following concrete domains: \code{d}  {\defeq}\  \code{\mathbb{Z^+}} and \code{\varphi}   {\defeq}\ \code{list\ of\ I} (a sequence of time instances).
-
-As shown in \figref{fig:Sementic}, we define the semantics of \timedEffects. 
-We use 
-$[]$ to represent the empty sequence;
-$\lappend$ to represent the append operation of two traces;
-\code{[I]} to represent the sequence only contains one event.
-\code{{\tt{SAT}(\pi)} } indicates the pure \code{\pi} is satisfiable, which is discharged by the constraint solver Z3 \cite{DBLP:conf/tacas/MouraB08}.
-
-%The signals shown in one event  represent the \emph{minimal} set of signals which are required/guaranteed to be there. An empty set \code{\_} represents any set of signals
-
-\end{comment}
-
-\section{Automated Forward Verification}\label{sec:Verification}
-
-\begin{wrapfigure}{R}{0.54\columnwidth}
- % \vspace{-1mm}
-
-\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt
-
-\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-0.65,xscale=0.65]
-%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
-
-%Rounded Rect [id:dp1113766752673011] 
-\draw  [line width=1.5]  (68,142.52) ..
-controls (68,136.24) and (73.09,131.15) ..
-(79.37,131.15) -- (216.63,131.15) ..
-controls (222.91,131.15) and (228,136.24) ..
-(228,142.52) -- (228,176.63) ..
-controls (228,182.91) and (222.91,188) ..
-(216.63,188) -- (79.37,188) ..
-controls (73.09,188) and (68,182.91) ..
-(68,176.63) -- cycle ;
-%Shape: Rectangle [id:dp6438165442964394] 
-\draw  [line width=1.5]  (67,51) -- (287,51) -- (287,104) -- (67,104) -- cycle ;
-%Rounded Rect [id:dp29624677487783313] 
-\draw  [line width=1.5]  (328,142.52) ..
-controls (328,136.24) and (333.09,131.15) ..
-(339.37,131.15) -- (473.63,131.15) ..
-controls (479.91,131.15) and (485,136.24) ..
-(485,142.52) -- (485,176.63) ..
-controls (485,182.91) and (479.91,188) ..
-(473.63,188) -- (339.37,188) ..
-controls (333.09,188) and (328,182.91) ..
-(328,176.63) -- cycle ;
-%Shape: Rectangle [id:dp5138829561825217] 
-\draw  [line width=1.5]  (309,52) -- (486,52) -- (486,104) -- (309,104) -- cycle ;
-%Straight Lines [id:da1612175737893331] 
-\draw [line width=1.5]    (137,109) -- (137,127.22) ;
-\draw [shift={(137,130.22)}, rotate = 270] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) ..
-controls (9.04,-1.82) and (4.3,-0.39) ..
-(0,0) ..
-controls (4.3,0.39) and (9.04,1.82) ..
-(14.21,4.28)   ;
-%Straight Lines [id:da5383095517878319] 
-\draw [line width=1.5]    (428,108) -- (428,127.95) ;
-\draw [shift={(428,130.95)}, rotate = 270] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) ..
-controls (9.04,-1.82) and (4.3,-0.39) ..
-(0,0) ..
-controls (4.3,0.39) and (9.04,1.82) ..
-(14.21,4.28)   ;
-%Straight Lines [id:da5450046441977192] 
-\draw [line width=1.5]  [dash pattern={on 5.63pt off 4.5pt}]  (229,164.5) -- (275,165.5) -- (325,165.97) ;
-\draw [shift={(328,166)}, rotate = 180.54] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=1.5]    (14.21,-4.28) ..
-controls (9.04,-1.82) and (4.3,-0.39) ..
-(0,0) ..
-controls (4.3,0.39) and (9.04,1.82) ..
-(14.21,4.28)   ;
-
-% Text Node
-\draw (61,57) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{113.09pt}\setlength\topsep{0pt}
-\begin{center}
-Target Program \&\\ Temporal Specifications
-\end{center}
-
-\end{minipage}};
-% Text Node
-\draw (66.57,139.15) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{77.55pt}\setlength\topsep{0pt}
-\begin{center}
-Hoare-style \\Forward Verifier 
-\end{center}
-
-\end{minipage}};
-% Text Node
-\draw (325,58) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{66.79pt}\setlength\topsep{0pt}
-\begin{center}
-Two \textit{Timeffs} \\LHS and RHS
-\end{center}
-
-\end{minipage}};
-% Text Node
-\draw (325,139.9) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{79.64pt}\setlength\topsep{0pt}
-\begin{center}
-Effects Inclusion \\Prover (TRS)
-\end{center}
-
-\end{minipage}};
-% Text Node
-\draw (223.8,117.63) node [anchor=north west][inner sep=0.75pt]   [align=left] {\begin{minipage}[lt]{51.49pt}\setlength\topsep{0pt}
-\begin{center}
-Proof \\obligations
-\end{center}
-
-\end{minipage}};
-
-\end{tikzpicture}
-
- %   \vspace{-4mm}
-%\centering
-%\includegraphics[width=1\columnwidth]{verification.png}
-%        \vspace{-3mm}
-%\caption{\label{fig:Verification_oberview}System Overview.}
-%      \vspace{-1mm}
-\caption{\label{fig:Verification_oberview}System Overview.}
-\end{wrapfigure}
-
-An overview of our automated verification system is given 
-in \figref{fig:Verification_oberview} 
-Rounded boxes are the main procedures, and both return \emph{true} 
-when the forward reasoning/proving succeeds, return \emph{false} 
-otherwise. Rectangular boxes describe the inputs to the procedures.
-The input of the TRS is a pair of effects LHS and RHS, referring to the 
-inclusion LHS \code{\CONTAIN} RHS to be checked 
-\textit{(LHS refers to left-hand-side effects, and RHS refers to right-hand-side 
-effects)}. 
-Besides, the verifier calls the TRS to prove produced inclusions (dash line). 
-The TRS will be explained in \secref{sec:Entailment_Prover}.
-
-\newcommand{\s}[1]{\code{\{ #1\}}}
-
-\subsection{Forward Inference Rules}
-\label{Forward_Rules}
-
- We here present the forward verification rules, 
-which are used to systematically accumulate the effects based on 
-the syntax of each statement.
-\code{\mathcal{P}} denotes the program being checked. 
-The rules are in the Hoare-style triples: 
-\code{\ \vdash \s{ \Pi, \Theta } \ e\ 
-\s{\Pi^\prime, \Theta^\prime}},  where 
-$e$ is the given statement;
-\s{ \Pi, \Theta } refers to a set of program states. 
-The meaning of the transition rules, can be described as:
-
-\vspace{2mm}
-\qquad \code{\s{ \Pi^\prime, \Theta^\prime } = 
-\wbigcup_{i{=}0}^{|\s{ \Pi, \Theta }| \text{-} 1}  
-\s{\pi_i^\prime, \es_i^\prime}  \ \ where\ \ \code{
-  \s{\pi_i, \es_i} {\in} \s{ \Pi^\prime, \Theta^\prime }
-}  \ \m{and} \ 
- \vdash  \s{\pi_i, \es_i} \ e \ \s{\pi_i^\prime, \es_i^\prime}.} 
-\footnote{\code{|\s{ \Pi, \Theta }|} is the 
-size of \code{\s{ \Pi, \Theta }}.}
-\vspace{3mm}
-
-\begin{comment}
-
-where 
-\code{\Theta} is the current effects, 
-\code{\Pi} is the current guard, 
-%\code{\env} is the current valuation of the variables;
-and \s{\Pi_1, \Theta_1}  
-is the resulting state by executing \code{e}. 
-The program state is initialized using \s{\epsilon, True}. 
-These rules transfer program states and systematically accumulate the effects syntactically.
-
-To define the model, we introduce a stack \env\ and describe 
-a program state in a four-elements tuple \s{H, G}, with the following concrete domains:
-\begin{flalign*}
-G {\defeq} \pi, \qquad\qquad
-H  {\defeq} \Theta, \qquad\qquad
-\env {\defeq} \code{var {\rightarrow} val }
-\end{flalign*}
-
-Let \code{\Pi} represents the pure constraints for all the terms; \code{H} represents the trace of \emph{history}; \code{C} represents the \emph{current} event or a waiting signal; 
-\code{T} is a term binding \code{C}; 
-\env\ be the environment containing all the local and output signals;
-
-\end{comment}
-
-\vspace{1mm}
-$[FV\text{-}\m{Value}]$  obtains the next program state by 
-inheriting the current program state.
-$[FV\text{-}Guard]$ computes the effects of \code{e} after concatenating
-\code{(b{=}True)}? in to the current program states.
-
-{{\small\begin{gather*}
-  \code{\frac{
-  }
-{  \vdash \{  \Pi, \Theta \}\  v \ 
-\{ \Pi, \Theta \}} \  
- {[FV\text{-}Value]}} 
- \qquad
- \code{\frac{
-  \vdash \{  \Pi, \Theta \cdot (b{=}True)? \}\  e \ 
-  \{ \Pi^\prime, \Theta^\prime \}
-  }
-{  \vdash \{  \Pi, \Theta \}\  [b]\ e \ 
-\{  \Pi^\prime, \Theta^\prime \}} \  
- {[FV\text{-}Guard]}} 
-\end{gather*}}}
-
-\vspace{1mm}
-$[FV\text{-}Seq]$ computes  \code{ \{  \Pi_1, \Theta_1\} } 
-from \code{e_1}, 
-then further gets  \code{ \{  \Pi_2, \Theta_2 \} } by 
-continuously computing the behaviors of \code{e_2}, to be the final state.
-$[FV\text{-}Par]$ computes behaviors for  \code{e_1} and \code{e_2} independently,
-then parallel merges the effects from these two branches.
-
-{{\small\begin{gather*}
-  \code{\frac{ 
- \vdash \{ \Pi, \Theta\}  e_1  \{  \Pi_1, \Theta_1\} 
-\ \  \ 
-\vdash \{ \Pi_1, \Theta_1\}  e_2   \{  \Pi_2, \Theta_2 \} 
-}{
-  \vdash \{  \Pi, \Theta \}\  
-  e_1;e_2 \ \{ \Pi_2, \Theta_2
-  \}} 
-   {[FV\text{-}Seq]}}  
-\quad 
-  \code{\frac{
- \vdash \{ \Pi, \Theta \}  e_1   \{  \Pi_1, \Theta_1\} 
-\ \  \ 
-\vdash \{  \Pi, \Theta \}  e_2   \{  \Pi_2, \Theta_2 \} 
-    }{
-\vdash \{   \Pi, \Theta \}\  e_1 || e_2 \ \{ 
-\Pi_1  \wedge \Pi_2 , \Theta_1 || \Theta_2
-\}}  
-{[FV\text{-}Par]}} 
-\end{gather*}}}
-
-The \code{[FV\text{-}If\text{-}Else]} computes an 
-over-approximation of the program states, by adding different constraints into 
-different branches. \code{\Pi \wedge v} enforces 
-\code{v} into the pure constraints of every trace in the state, same 
-for \code{\Pi \wedge \neg v }.
-
-{{\small\begin{gather*}
-  \code{\frac{ 
-    \begin{matrix}
-\vdash \{ \Pi \wedge v, \Theta    \} \ e_1 \ \{  \Pi_1, \Theta_2 \} 
-\qquad 
-\vdash \{ \Pi \wedge \neg v , \Theta  \} \ e_2 \ 
-\{  \Pi_2, \Theta_2 \}  
-\qquad (v\ is\ local)
-\end{matrix}}
-  {\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
-  \textbf{else}\ e_2 \ \s{ \Pi_1, \Theta_2} \cup \s{\Pi_2, \Theta_2} } \  
-  {[FV\text{-}If\text{-}Else\text{-}Local]}} 
-  \end{gather*}}}
-  %\\
-%\code{\frac{ 
-%  \begin{matrix}
-%\vdash \{ \Pi, \Theta    \} \ e_1 \ \{ \Pi_1, \Theta_2 \} 
-%\qquad 
-%\vdash \{ \Pi , \Theta  \} \ e_2 \ 
-%\{  \Pi_2, \Theta_2 \}  
-%\qquad (v\ is\ global)
-%\end{matrix}}
-%{\vdash \s{ \Pi, \Theta}\  \textbf{if}\ v\ \textbf{then}\ e_1\ 
-%\textbf{else}\ e_2 \ \s{\Pi, v. \Theta_1 \vee \Theta_2 }} \  
-%{[FV\text{-}If\text{-}Else\text{-}Global]}}
-
-Rule \code{[FV\text{-}Event]} simply constructs a new event and 
-concatenates it to the current program states. 
-Rule \code{[FV\text{-}Delay]} creates a trace \code{\epsilon\mysharp t}
-, where \code{t} is fresh, and concatenates it to the current program states, 
-together with the additional constraint \code{t{=}d}.
-
-  {{\small\begin{gather*}
-  \code{\frac{
-    \Theta^\prime {=} \Theta\cdot \anyevent{A}(v, \alpha^*) 
-    }
-  {\vdash \s{ \Pi, \Theta} \  
-  \textbf{event} [\anyevent{A}(v, \alpha^*)] 
-   \ \{\Pi, \Theta^\prime \}} \   {[FV\text{-}Event]}} 
-   \qquad
-  \code{\frac{
-    \Theta^\prime {=} \Theta\cdot \epsilon\mysharp t \quad (t\ is\ fresh) 
-    }
-  {\vdash \s{ \Pi, \Theta} \  
-  \textbf{delay} [d] 
-   \ \{ \Pi \wedge  t {=}d,  \Theta^\prime \}} \   {[FV\text{-}Delay]}} 
-\end{gather*}}}
-
-Rule \code{[FV\text{-}Timeout]} computes the effects from \code{e_1} and \code{e_2}
-using the starting state \code{\s{\Pi, \epsilon}}. The final states are the union 
-of these effects with their corresponding time variables and arithmetic constraints. 
-Note that, \code{hd(\Theta_1)} and \code{tl(\Theta_1)} return the head and the tail of 
-\code{\Theta_1} respectively.
-
-{{\small\begin{gather*}
-  \code{\frac{
-    \begin{matrix}
-      \vdash \{\Pi, \epsilon \}\ e_1 \ \{  \Pi_1, \Theta_1\} 
-      \qquad 
-      \vdash \{ \Pi, \epsilon \}\ e_2 \ \{  \Pi_2, \Theta_2 \} 
-      \\
-      \s{\Pi_f, \Theta_f} {=} \s{\Pi_1  \wedge t_1{\leq}d, (hd(\Theta_1)\mysharp t_1 \cdot tl(\Theta_1))}
-      \cup 
-  \s{\Pi_2  \wedge t_2{>}d,  (\Theta_2\mysharp t)}   
-  \quad (t_1, t_2\ are\ fresh)     
-\end{matrix}
-  }
-  {\vdash \s{ \Pi, \Theta} \  
-  e_1\ \textbf{timeout} [d] \  e_2
-   \ \s{\Pi_f, \Theta \cdot \Theta_f} } \   {[FV\text{-}Timeout]}} 
-\end{gather*}}}
-
-Similar to \code{[FV\text{-}Timeout]}, \code{[FV\text{-}Ddl]} computes the effects 
-from \code{e} and adds an upper time-bound to the result.
-
-{{\small\begin{gather*}
-  \code{\frac{
-    \begin{matrix}
-      \vdash \{ \Pi, \epsilon\}\ e \ \{  \Pi_1, \Theta_1\} 
-  \quad (t\ is\ fresh)     
-\end{matrix}
-  }
-  {\vdash \s{ \Pi, \Theta} \  
-  \textbf{deadline}  [d] \ e 
-   \ \s{\Pi_1  \wedge t{\leq}d, \Theta  \cdot (\Theta_1\mysharp t)} }   
-    {[FV\text{-}Ddl]}} 
-  \end{gather*}}}
-
-  Rule \code{[FV\text{-}Meth]} initializes the current effects state 
-using the declared precondition, accumulates the effects from the method body, 
-to obtain \code{ \s{\Pi, \Theta}}; then  it
-checks the  inclusion between \code{ \s{\Pi, \Theta}} and the concatenation of 
-the precondition and the postcondition\footnote{Here, 
-\code{\effect_{post}} only needs to capture the effects from the current method body, excluding the history effects specified in \code{\effect_{pre}}. }.
-
-{{\small\begin{gather*}
-\code{\frac{  \vdash \s{\effect_{pre}}
- \ e \  \{ \Pi, \Theta \} \qquad   \{ \Pi, \Theta \} \CONTAIN  
- \effect_{pre} \cdot \effect_{post}}{  \vdash  \ mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ 
-  \textbf{ens}\  \effect_{post}\} \ \{ e \}}   {[FV\text{-}Meth]}}  
-  \end{gather*}}}
-
-Rule \code{[FV\text{-}Call]} first checks whether the instantiated 
-  precondition of callee, \code{[v^*/x^*]\effect_{pre}}, is satisfied by 
-  the current program state. When the check is succeeded, the final states are 
-  formed by concatenating the  
-  instantiated postcondition to the current states.
-
-  %, in which we use an auxiliary function \code{rev} to reverse the event sequences of effects.
-{{\small\begin{gather*}
-\code{\frac{
-\begin{matrix}
-{\code{  mn  \ {x^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \} \in \mathcal{P}\ \ }}
-\\
-\text{\code{ \s{ \Pi, \Theta} \CONTAIN [v^*/x^*] \effect_{pre}   
-\qquad   \effect_f =  \s{ \Pi, \Theta} \cdot  [v^*/x^*]\effect_{post}}}
-\end{matrix}}
-{\vdash \s{ \Pi, \Theta} \ mn({v^*})  \ 
-\effect_f} \ {[FV\text{-}Call]}}
-\end{gather*}}}
-
-\begin{theorem}[Soundness of the Forward Rules]\label{Soundness_forward_rules}
-  Given any system configuration \code{\zeta = (\env, e)}, by applying the operational
-  semantics rules, 
-  if \code{(\env, e) {\rightarrow^*} (\env^\prime, ())} produces concrete 
-  execution time \code{d} and event sequence \code{\varphi}, and the forward verifier reasons \code{ \vdash  
-  \s{\env, \epsilon} \ e\  \s{\Pi, \Theta}}, then, \\
-  \code{\qquad \qquad \qquad \qquad  \qquad 
-   \exists (\pi\wedge \es) \in \s{\Pi, \Theta} } such that 
-  \code{d, \env^\prime, \varphi  \models (\pi\wedge \es)}. 
-  %.
-
-%  pair $(\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
-  \end{theorem}
-
-  \begin{proof}
-   % By induction.        
-    See \appref{proof:SoundnessProof_FE}.
-  \end{proof}
-
-\section{Temporal Verification via a TRS}
-\label{sec:Entailment_Prover}
-
-The TRS  is an automated entailment checker to prove language 
-inclusions between \timedEffects, cf. \defref{Inclusion} and 
-\tabref{tab:rewriting_tree_send} It is triggered i) prior to 
-temporal property assertions; ii) prior to function calls for the 
-precondition checking; and iii) at the end of verifying a function 
-for the post condition checking. Given two effects 
-\code{\effect_1} and \code{\effect_2}, the TRS decides if the inclusion \code{\effect_1 \CONTAIN  \effect_2 } is valid.
-
-During the effects rewriting process, the inclusions are in the form of \code{\Gamma \vdash  \effect_1 \CONTAIN^{\effect}  \effect_2 }, a shorthand for: \code{\Gamma \vdash  \effect \cdot \effect_1 \CONTAIN   \effect \cdot  \effect_2}.
-To prove such inclusions is to check whether all the possible timed traces in the antecedent \code{\effect_1} are legitimately allowed  in the possible timed traces from the consequent \code{\effect_2}.
-\code{\Gamma} is the proof context, i.e., a set of effects inclusion hypothesis, \code{\effect} is the history effects from the antecedent that have been used to match the effects from the consequent.
-Note that \code{\Gamma}, \code{\effect} are derived during the inclusion proof. 
-The inclusion checking is initially invoked with \code{\Gamma{=}\{\}} and 
-\code{\effect{=} True \wedge  \epsilon}.
-
-\paragraph{\textbf{Effects Disjunctions.}}
-An inclusion with a disjunctive antecedent succeeds if both disjunctions entail the consequent.
-An inclusion with a disjunctive consequent succeeds if the antecedent entails either of the disjunctions.
-{ 
-\input{rules/rule7}
-}
-
-\vspace{2mm}
-Now, the inclusions are disjunction-free formulas. 
-Next we provide the definitions and the key implementations\footnote{As 
-the implementations according to basic regular expressions can be found 
-in prior work \cite{DBLP:conf/fsttcs/KeilT14}. 
-%Here, we focus on presenting 
-%the definitions and how do we deal with dependent values in the effects, 
-%as the key novelties of this work. 
-%More detail implementations can be found in the extended technical report\citeref{Demo}.
-} of Nullable, First and Derivative respectively. Intuitively, 
-the Nullable function \code{\delta_{{\pi}}(\es)} returns a Boolean 
-value indicating whether \code{{\pi} \wedge \es} contains the empty 
-trace; the First function \code{fst_{{\pi}}( \es)} computes a set of 
- initial \emph{heads}, denoted as \code{h},  of \code{{\pi} \wedge \es}; and the Derivative 
-function \code{D^{\pi}_{h}(\es)} computes a next-state 
-effects after eliminating the head  \code{h} from the current 
-effects \code{{\pi} \wedge \es}.
-
-%\subsection{closure of clock constraints}
-%how to eliminate the unobservable transitions. 
-%
-%we allow the $ \epsilon$transitions without carrying constraints and resetting clocks at the same time.
-
-\begin{definition}[Nullable \footnote{The proof obligations are 
-  discharged using the Z3 SMT prover, while deciding the nullability of effects constructed by symbolic terms, represented by \code{SAT({\pi})}.}]\label{Nullable}
-Given any \code{\effect {=} \pi  \wedge  \es}, %we define 
-%\code{\delta_{{\pi}}(\es)} to be \\
-{
-  \code{\delta_{{\pi}}(\es) :bool {=}
-  \begin{cases}
-        \code{true} & \code{if\  \epsilon \in \llbracket {\pi}  \wedge  \es \rrbracket}\\
-        \code{false} & \code{if\  \epsilon \notin \llbracket {\pi}  \wedge  \es \rrbracket}
-      \end{cases} }
-      }, where:  
-\begin{comment}
- a boolean value, indicating whether \code{\effect} contains the empty trace, i.e., $\epsilon$. 
-We define recursively:  
-\end{comment} 
-{ 
-\begin{gather*}
-\code{\delta_{\pi}(\bot ) {=} false} 
-\qquad\quad
-\code{\delta_{\pi}( \epsilon) {=} true} 
-\qquad\quad
-\code{\delta_{\pi}(\ev){=} false}   
-\qquad\quad
-\code{\delta_{\pi}(\pi^\prime?){=} false}  
-\qquad\quad\
-    \code{\delta({\es^\star} ) {=} true}   
-\\ 
-\ \ 
-\code{\delta_{\pi}(\es \cdot \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
-\qquad\qquad\quad
-  \code{\delta_{\pi}(\es_1 \vee \es_2) {=} \delta(\es_1) \vee \delta(\es_2)}   
-  \\
-\code{\delta_{\pi}(\es_1 || \es_2) {=} \delta(\es_1) \wedge \delta(\es_2)}
-\qquad\qquad\quad
- \code{\delta_{\pi}(\es \mysharp  t) {=} SAT ({\pi} \wedge (t {=} 0) )}
-\end{gather*}}
-\end{definition}
-
-%Next, we define the novel  \emph{First} function used in this work, denoted using \code{fst}. 
-%but helps to build up our \emph{First} function \code{fst}.
-
-\vspace{2mm}
-\begin{definition}[Heads]\label{Heads}
-If \code{h} is a head of \code{\pi \wedge \es}, then there exist 
-\code{\pi^\prime} and \code{\es^\prime}, 
-such that \code{\pi \wedge \es} {=} \code{\pi^\prime \wedge h \cdot \es^\prime}. 
-   %We adopt the following naming convention for transition labels: 
-A head can be  $t$, denoting a pure time passing; 
-  $\ev $, denoting an instant event passing; or 
-  $(\ev, t)$, denoting an event passing which takes time \code{t}. 
-\end{definition}
-
-\vspace{2mm}
-\begin{definition}[First]\label{First}
-  Given any \code{\effect {=} \pi \wedge \es},
-  \code{fst_{{\pi}}(\es)} returns a set of heads, be the set of initial elements   
-  derivable from effects \code{\pi \wedge \es}, where: 
-    { 
-   \begin{gather*} 
-  \code{fst_{{\pi}}( \bot ) {=} \{\} } \qquad\quad 
-  \code{fst_{{\pi}}( \epsilon) {=}  \{\} } \qquad\quad
-  \code{fst_{{\pi}}( \ev) {=} \{ \ev \}  }
-  \qquad\quad
-  \code{fst_{{\pi}}(  \epsilon \mysharp  t) {=}  \{ t \}}
-  \qquad\quad
-  \code{fst_{{\pi}}( {\es^\star} ) {=} fst_{{\pi}}({ \es})}
-   \\
-   \code{fst_{{\pi}}(\es \mysharp  t) {=}  \{(\ev, t^\prime) \ | \ \ev \in fst_{\pi}(\es) \}} 
-   \ \ \  \emph{($t^\prime$\ is\ fresh)}
-  \quad  
-  \qquad
-  \code{fst_{{\pi}}(  \es_1 {\vee} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }  
-  \\
-  \code{fst_{{\pi}}( \pi^\prime? ) {=} \{\tau(\pi^\prime); \tau(\neg \pi^\prime)\}  }
-      \qquad\qquad\qquad 
-     \code{fst_{{\pi}}(  \es_1 {||} \es_2) {=} fst_{{\pi}}(  \es_1) \cup fst_{{\pi}}(  \es_2)  }   
-     \\
-  {
-  \code{fst_{{\pi}}(\es_1 \cdot \es_2) {=} } 
-  \begin{cases}
-        \code{\code{fst_{{\pi}}(  \es_1)} \cup \code{fst_{{\pi}}(  \es_2)} } \quad   & \code{ if\ \  \delta(\es_1) {=} true}\\
-        \code{\code{fst_{{\pi}}(  \es_1)}} & \code{  if\ \  \delta(\es_1) {=} false}
-      \end{cases} 
-      }  
-  \end{gather*}
-  }
-\end{definition}
-
-\begin{comment}
-  \begin{definition}[Heads Subsumption]\label{Subsumption1}
-Given two time instances \code{(I, \pi_1, t_1)} and \code{(J, \pi_2, t_2)}, we define the subset relation \code{(I, \pi_1, t_1) {\subseteq} (J, \pi_2, t_2)} as:  \code{I {\subseteq} J} and \code{\pi_1[t_2/t_1]  {\Rightarrow}   \pi_2  }.
-
-\end{definition}
-\end{comment}
-
-\vspace{2mm}
-\begin{definition}[Partial Derivative]\label{Derivative}
-  Given any \code{\effect {=}\pi \wedge  \es}, 
-  %and a variable valuation function \code{\env}, 
-  the partial derivative \code{D^{\pi}_{h}( \es)} 
-   computes the  effects for the 
-  left quotient \code{(h)^{\text{-}1}\llbracket \pi \wedge \es 
-  \rrbracket}\footnote{Intuitively, the partial derivative refers to the left quotient of a language equation, for example, for REs, \code{x^{{-}1} \llbracket x\cdot y\rrbracket {=} y};  \code{y^{{-}1} \llbracket x\cdot y\rrbracket {=} \bot }; and  \code{y^{{-}1} \llbracket x + y\rrbracket {=} \epsilon}.
-Here we come up with a new notion of partial derivative for \timedEffects.
-  }.
-
-  \begin{gather*}
-  \code{D^{\pi}_{h}( \bot ) {=}}  \code{False \wedge \bot } 
-  \qquad\qquad 
-  \code{D^{\pi}_{h}(   \epsilon) {=}}  \code{False \wedge \bot } 
-  \qquad\qquad
-  \code{D^{\pi}_{h}(  \ev^\prime) } {=} 
-  \code{  (\pi \wedge h{=}\ev^\prime) \wedge \epsilon} 
-  \\
-  {
-   \code{\code{D^{\pi}_{h}( \pi^\prime?)} {=}}
-  \begin{cases}
-        \code{\pi \wedge \pi^\prime? } &\code{if\ h \not\Rightarrow  \pi^\prime}   \\
-        \code{\pi \wedge \epsilon} & \code{if\ h \Rightarrow \pi^\prime} 
-      \end{cases} 
-      }
-      \qquad \quad \ \ \ 
-  {
-   \code{D^{\pi}_{h}( \es_1  \cdot  \es_2) {=} }
-  \begin{cases}
-        \code{D^{\pi}_{h}( \es_1) \cdot  \es_2\ \vee \  D^{\pi}_{h}( \es_2)}  &\code{if\ \delta_{\pi}(\es_1) {=} true}   \\
-        \code{D^{\pi}_{h}( \es_2) \cdot  \es_2} & \code{if\ \delta_{\pi}(\es_1) {=} false} 
-      \end{cases} 
-      }
-  \\
-  \code{D^{\pi}_{h}(  {\es^\star}) } {=} \code{ D^{\pi}_{h}(  {\es}) \cdot {\es^\star}}  
-  \qquad\quad \ \ \ 
-  \code{D^{\pi}_{h}(  \es_1 {\vee} \es_2) } {=} \code{ D^{\pi}_{h}(  \es_1) \vee D^{\pi}_{h}(  \es_2)} 
-  \qquad \quad\ \ \ 
-  \code{D^{\pi}_{h}( \es_1 {||}\es_2)} {=} \code{\Bar{\Bar{D}}^{\pi}_{h}( \es_1)} || \code{\Bar{\Bar{D}}^{\pi}_{h}( \es_2)} 
-   \\
-   \code{D^{\pi}_{\ev}(  \es \mysharp t) } {=} {\bigvee}
-   \code{ \{ (\pi^\prime \wedge \es^\prime  \mysharp t) \ | \ (\pi^\prime, \es^\prime) \in D^{\pi}_{\ev}(\es) \} } 
-\qquad 
-   \code{D^{\pi}_{t}(  \es \mysharp t^\prime) } {=} 
-   \code{ (\pi \wedge t{+}t^{\prime\prime}{=}t^\prime) \wedge  
-   \es \mysharp t^{\prime\prime} \ \ \  {(t^{\prime\prime}\ is\ fresh)} } 
-  \end{gather*}
-  \end{definition}
-
-Notice that the derivatives of a parallel composition makes use of the \emph{Parallel Derivative} \code{\Bar{\Bar{D}}^{\pi}_{h}(\es)}, defined as follows:
-
-\begin{definition}[Parallel Derivative]\label{Derivative_maybe}
-    Given any \code{\effect {=} \pi \wedge \es}, and a variable valuation function \code{\env}, 
-    the parallel derivative is defined as: {
-      \code{\Bar{\Bar{D}}^{\pi}_{h}( \es) {=}
-      \begin{cases}
-            \code{ \es} & \code{if\ D^{\pi}_{h}(\pi \wedge \es) = (False \wedge \bot )}\\
-            \code{D^{\pi}_{h}( \es)} & \code{otherwise}
-          \end{cases} }
-    }.
-  \end{definition}
-
-  \vspace{2mm}
-\subsection{Rewriting Rules}
-\label{InferenceRules}
-Given the well-defined auxiliary functions above, we now discuss the key steps and related rewriting rules that we may use in such an effects inclusion proof.
-
-\begin{enumerate}
-\item 
-\textbf{Axiom rules.}
-\label{Base}
-Analogous to  the standard propositional logic, \code{\bot } (referring to \textit{false}) entails any effects, while no \textit{non-false} effects entails \code{\bot }.
-\input{rules/rule1}
-
-\item 
-\textbf{Disprove (Heuristic Refutation).}
-\label{Refutation}
-This rule is used to disprove the inclusions when the antecedent is nullable, while the consequent is not nullable.
-Intuitively, the antecedent contains at least one more trace (the empty trace) than the consequent.
-Therefore, the inclusion is invalid.
-\input{rules/rule2}
-
-\item 
-\textbf{Prove.}
-\label{Prove}
-We use two rules to prove an inclusion: (i) $\codeme{[PROVE]}$ is 
-used when the fst set of the antecedent is empty; and 
-(ii) $\codeme{[REOCCUR]}$ to prove an inclusion
-when there exist inclusion hypotheses 
-in the proof context $\m{\Gamma}$, which are able to 
-soundly prove the current goal. One of the special cases of 
-this rule is when the identical inclusion is shown in the proof 
-context, we then terminate the procedure and prove it as a valid 
-inclusion. 
-\input{rules/rule3}
-
-\item 
-\textbf{Unfolding (Induction).}
-\label{unfolding}
-This is the inductive step of unfolding the inclusions. Firstly, 
-we make use of the auxiliary function \code{fst} to get a set of 
-heads \code{H}, which are all the possible initial time instances 
-from the antecedent. 
-Secondly, we obtain a new proof context \code{\Gamma^\prime} by 
-adding the current inclusion, as an inductive hypothesis, into 
-the current proof context \code{\Gamma}. 
-Thirdly, we iterate each element \code{h \in H}, and compute the 
-partial derivatives (\emph{next-state} effects) of both the 
-antecedent and consequent w.r.t \code{h}. The proof 
-of the original inclusion succeeds if all the derivative 
-inclusions succeed.
-\input{rules/rule4}
-
-\item 
-\textbf{Normalization.}
-We present some normalization rules to soundly transfer the timed effects into a normal form, in particular after getting their derivatives. 
-Before getting into the above inference rules, we assume that the effects formulae are tailored accordingly based on the axioms shown in
-\tabref{table:normalization}
-We built the axiom system on top of an axiom system \code{F_1}, from (A1) to (A10), suggested by \cite{DBLP:journals/jacm/Salomaa66}, 
-which was designed for regular languages. We develop axioms (A11) 
-to (A16) to further accommodate effects constructed by 
-\code{||} and \code{\mysharp}.
-
-\begin{table}[ht]
-  \caption{Some Normalization Axioms for \timedEffects.}
-  \label{table:normalization}
-  \setlength{\tabcolsep}{10pt}
-  \renewcommand{\arraystretch}{1.2}
-  \centering
-  \begin{tabular}{rl}
-  \footnotesize
-
-  \begin{minipage}[t]{0.36\textwidth}
-  \begin{tabular}{||l|l}
-  \hline
-  (A1)  &
-  \code{\es_1 \vee (\es_2 \vee \es_3) \rightarrow   (\es_1 \vee \es_2) \vee \es_3 }\\
-  \hline
-  (A2)  &
-  \code{\es_1 \cdot (\es_2 \cdot \es_3)\rightarrow     (\es_1 \cdot \es_2) \cdot \es_3 }\\
-  \hline
-  (A3)  &
-  \code{\es \cdot (\es_1 \vee \es_2)  \rightarrow \es \cdot \es_1  \vee \es \cdot \es_2 }\\
-  \hline
-  (A4)  &
-   \code{(\es_1 \vee \es_2)\cdot \es   \rightarrow \es_1 \cdot \es   \vee  \es_2 \cdot \es}\\
-  \hline
-  (A5)  &
-   \code{\es \vee \es   \rightarrow \es}\\
-  \hline
-  (A6)  &
-   \code{  \es \cdot \epsilon   \rightarrow \es}\\
-  \hline
-  (A7)  &
-   \code{  \es \cdot  \bot \rightarrow \bot}\\
-  \hline
-  (A8)  &
-  \code{\es \vee \bot   \rightarrow \es}\\
-  \hline
-
-  \end{tabular}
-    \end{minipage}
-
-    &
-  \footnotesize
-    \begin{minipage}[t]{0.6\textwidth}
-  \begin{tabular}{||l|l|}
-  \hline
-  (A9)  &
-  \code{\epsilon \vee (\es \cdot \es^\star)   \rightarrow  \es^\star}\\
-  \hline
-  (A10)  &
-  \code{(\epsilon \vee \es)^\star   \rightarrow  \es^\star}\\
-  \hline
-  (A11)\code{^\heartsuit}  &
-  \code{ \es\ ||\  \epsilon \rightarrow \es}\\
-  \hline
-  (A12)\code{^\heartsuit}  &
-  \code{ \es\ ||\ \bot  \rightarrow \bot }\\
-  \hline
-  (A13)\code{^\heartsuit}  &
-  \code{\bot \mysharp  t \rightarrow  \bot }\\
-  \hline
-  (A14)\code{^\heartsuit}  &
-  \code{\pi \wedge (\es \mysharp  t_1 ) \mysharp  t_2 
-  \rightarrow \pi  \wedge (t_1 {=} t_2) \wedge \es \mysharp  t_1 }\\
-  \hline
-  (A15)\code{^\heartsuit}  &
-   \code{(\epsilon \mysharp  t_1) ||(\epsilon \mysharp  t_2) \rightarrow 
-   (t_1 {\geq}t_2 \wedge\epsilon\mysharp t_1) \vee   (t_1 {<}t_2 \wedge \epsilon\mysharp t_2) }\\
-  \hline
-  (A16)\code{^\heartsuit}  &
-   \code{{{False}} \wedge \es = {\pi} \wedge \bot  \rightarrow {{False}} \wedge \bot }\\
-  \hline
-
-  \end{tabular}
-    \end{minipage}
-
-  \end{tabular}
-  \vspace{-2mm}
-
-  \end{table}
-
-\end{enumerate}
-
-\begin{theorem}[Termination  of the TRS]\label{termination}
-The rewriting system TRS is terminating.
-\end{theorem}
-\begin{proof}
-See %the technical report\cite{TR}. 
-\appref{proof:TerminationProof}.
-\end{proof}
-
- \begin{theorem}[Soundness of the TRS]\label{Cyclicsoundness}
-Given an inclusion \code{\effect_1 \CONTAIN \effect_2}, if the TRS returns \code{TRUE} when proving \code{\effect_1 \CONTAIN \effect_2}, i.e., it has a cyclic proof, 
-then \code{\effect_1 \CONTAIN \effect_2} is valid.
-\end{theorem}
-
-\begin{proof}
-See %the technical report\cite{TR}. 
-\appref{proof:SoundnessProof}.
-\end{proof}
-
-\section{Implementation and Case Study}
-\label{sec:Evaluation}
-
-To show the feasibility of our approach, we have prototyped 
-our automated verification system 
-using OCaml. The proof obligations generated by the verifier 
-are discharged using constraint solver Z3 
-\citep{DBLP:conf/tacas/MouraB08}. 
-We prove termination and soundness of the TRS. We validate 
-the front-end forward verifier against the state-of-the-art PAT 
-\cite{DBLP:conf/cav/SunLDP09} model checker for conformance. 
-Next, we show experimental results and case studies to evaluate our proposals.
-
-\subsection{Experimental Results}
-\label{subsec:Experimental_Results}
-
-%We claim that the extra expressiveness gained from our logic is the symbolic time-bounds.
-The timed effects represent not only one exact Timed Automata but also a set of Timed Automata.
-Together with our back-end inclusion solver, it enables a verification framework for a group of Automata.
-More specifically, instead of running the model checker many times for one non-deterministic time-bound at each time, we can define arithmetic constraints bounding the time variable.
-And to test that, we cover a number of test cases with function calls, and the callee's parameters would be used as the time bounds.
-
-\begin{table}[!ht]
-\caption{\label{tab:Experimental} Experimental Results. }
-\vspace{-2mm}
-\centering
-\renewcommand{\arraystretch}{1}
-\begin{tabular} {c|c|c|c|c |c|c|c}
-\hline
-\textbf{No.} & \textbf{LOC} & \textbf{Infer(ms)} & \textbf{$\mysharp$Prop(\cmark)}   
-& \textbf{Avg\text{-}Prove(ms)} & \textbf{$\mysharp$Prop(\xmark)}   & \textbf{Avg\text{-}Dis(ms)} &\textbf{$\mysharp$AskZ3} \\ \hline\hline
-1    &    30    & 0.031  &  5     &  4.185   & 5   &  3.242  & 68 \\ \hline
-2    &    35    & 0.038  &  3     &  13.761  & 7   &  9.331  & 214 \\ \hline
-3    &    44    & 0.049  &  4     &  12.149  & 6   & 7.853   & 215 \\ \hline
-4    &    72    & 0.061  &  5     &  37.268 & 5   & 28.3054 & 617 \\ \hline
-5    &    95    & 0.105  &  7     &  6.139    & 7   &  5.238  & 186 \\ \hline
-6    &    108   & 0.16   &  7     &  43.667    & 7   &  17.178  & 818 \\ \hline
-7    &    106   & 0.142  &  7     &  18.776    & 7   &  8.432  & 346 \\ \hline
-8    &    144   & 0.141  &  7     &  22.238    & 7   &  10.051  & 426 \\ \hline
-9    &    155   & 0.308  &  9     &  194.666   & 9   &  56.344  & 4059 \\ \hline
-10   &    174   & 0.373  &  9     &  78.132   & 9   &   24.665  & 1740 \\ \hline
-11   &    196   & 0.557  &  9     &  111.100   & 9   &   31.262  & 2403 \\ \hline
-12   &    213   & 0.516  &  9     &  114.667   & 9   &  30.284   & 2484 \\ \hline
-13   &    265   & 1.895  &  11    & 616.619    & 11  &  302.975  & 9068 \\ \hline
-14   &    271   & 1.702  &  11    &  302.145   & 11  &  131.938  & 7779 \\ \hline     
-15   &    276   & 2.121 & 11     &  466.174  & 11  &   181.116  & 12239 \\ \hline
-16   &    314   & 1.654 &  11    & 1094.231   & 11  &  465.704  & 32620 \\ \hline            
-%\hline
-%\textbf{\quad \ \ Total}  & 2546    &  235   &  446.88   &   305.33   \\ \hline
-\end{tabular}
-%  \vspace{-1mm}
-\end{table}
-
-\autoref{tab:Experimental} presents the evaluation results of a microbenchmark. % summary of a lightweight . 
-In this experiment, we select 16 \timedL\ programs, and  annotate temporal specifications
-with a roughly 1:1 ratio for succeeded/failed cases. 
-Times are counted using milliseconds, and the experiment is done on 
-a MacBook Pro with a 2.6 GHz 6-Core Intel Core i7 processor. 
-The table records: 
-\textbf{No.}, the index of the program;
-\textbf{LOC}, lines of code; 
-\textbf{Infer(ms)}, effects inference time; 
-\textbf{$\mysharp$Prop(\cmark)}, number of valid properties; 
-\textbf{Avg\text{-}Prove(ms)}, average proving time for the valid properties;
-\textbf{$\mysharp$Prop(\xmark)}, number of invalid properties; 
-\textbf{Avg\text{-}Dis(ms)}, average disproving time for the invalid properties; and 
-\textbf{$\mysharp$AskZ3}, number of querying Z3 solver through out the experiments.
-
-\paragraph{Discussion:} Generally, the inference time and proving 
-time increase while the program's length increases. 
-Besides, while \emph{the number of querying Z3 per property} (\textbf{$\mysharp$AskZ3}/(\textbf{$\mysharp$Prop(\cmark)} +\textbf{$\mysharp$Prop(\xmark)})) 
-goes up, the 
-proving/disproving time goes up.
-Furthermore, we notice that 
-%that no matter how long the programs are, 
-the disproving
-times for invalid properties are constantly lower than the proving process, 
-regardless of the program complexity. This finding echos the 
-insights from prior TRS-based works \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}, 
-which suggest that TRS is a better average-case algorithm than 
-those based on the comparison of automata.
-
-As a summary: a TRS is efficient because 
-\emph{it only constructs automata as far as it needs}, which makes 
-it more efficient when disproving incorrect specifications, as we can 
-disprove it earlier without constructing the whole automata. In other 
-words, the more incorrect specifications are, the more efficient our solver is.
-
-%
-%\subsubsection{Experimental Results}~\\
-%\label{subsec:Experimental_Results}
-%
-%\begin{table}[ht]
-%        \vspace{-2mm}
-%\caption{\label{tab:Experimental} The experiments are based on 16 real world C programs, we record the lines of code (LOC), the number of testing temporal properties ($\mysharp $Prop.), and the (dis-) proving times (in time units) using PAT and our T.r.s respectively.
-}
-%\centering
-%\footnotesize
-%\renewcommand{\arraystretch}{1.1}
-%\begin{tabular} {l|c|c|c|c}
-%\hline
-%\textbf{Programs} & \textbf{LOC} & \textbf{$\mysharp $Prop.}  & \textbf{PAT(ms)} & \textbf{T.r.s(ms)} \\ \hline\hline
-%1. Chrome\_Dino\_Game    &      80    &    12  &  32.09 &  7.66  \\ \hline
-%2. Cradle\_with\_Joystick  &      89     &   12   &  31.22    &   9.85  \\ \hline
-%3. Small\_Linear\_Actuator  &    180  &     12  &   21.65      &  38.68  \\ \hline
-%4. Large\_Linear\_Actuator &    155   &    12   &  17.41   &   14.66   \\ \hline
-%5. Train\_Detect  &                    78   &     12    &   19.50   & 17.35     \\ \hline
-%6. Motor\_Control  &                 216  &    15  &     22.89  &  4.71  \\ \hline
-%7. Train\_Demo\_2  &                133  &   15    &     49.51   &  59.28   \\ \hline
-% 8. Fridge\_Timer  &                  292   &    15   &   17.05   & 9.11 \\ \hline
-%  9. Match\_the\_Light   &         143     &    15  &  23.34    &  49.65 \\ \hline
-%   10. Tank\_Control  &              104   &    15    &  24.96   &   19.39 \\ 
-%     \hline
-%  \textbf{\quad \ \ Total}  & 2546    &  235   &  446.88   &   305.33   \\ \hline
-%\end{tabular}
-%        \vspace{0mm}
-%\end{table}
-%
-%
-%        \vspace{-2mm}
-%
-%
-%
-
-\subsection{Case Studies}
-\label{subsec:Case_Studies}
-
-%Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.
-
-%how our proposal makes it flexible for different effects logics.
-
-\subsubsection{Prove it when Reoccur}
-
-   %   \vspace{-2mm}
-%(\code{\{Go\} \Rightarrow \_})
-%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
-Termination of TRS is guaranteed because the set of derivatives 
-to be considered is finite, and possible cycles are detected 
-using \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, 
-i.e., the rule $\codeme{[REOCCUR]}$. 
-% Check out this following example:
-
-{
-\begin{table}[ht]
-      \vspace{0mm}
-\caption{\label{tab:reoccur} The reoccurrence proving example. 
-\code{(I)} The main rewriting proof tree; \code{(II)} Right hand side sub-tree of the rewriting process.}
-
-\vspace{-1mm}
-\begin{adjustbox}{width=1\textwidth}
- \Large\begin{tabular}[t]{l}
-  \hline\\
-
-\code{(I):}\
-{
-
-\begin{prooftree}
-
-\hypo{
-  \code{
-   % \textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True} \qquad
-   % \epsilon \CONTAIN \epsilon
-   {\textcircled{4}\siderule{\codeme{[PROVE]}}}
-  }
-}
-
-\infer[dashed]1[]{
-  \code{
-    \textcolor {darkred}{True} \wedge \epsilon \CONTAIN
-    \textcolor {darkred}{True} \wedge \epsilon
-  }
-}
-
-\infer[dashed]1[{\textcircled{3}\siderule{\codeme{[Normalisation]}}}]{
-  \code{
-    \textcolor {darkred}{True} \wedge \cancel{  B  } \CONTAIN
-    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot   B  }
-  }
-}
-
-\infer[dashed]1[{\textcircled{2}\siderule{\codeme{[UNFOLD]}}}]{
-  \code{
-    \textcolor {darkred}{True} \wedge   B   \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B  
-  }
-}
-\hypo{(\code{II})}
-
-\infer[dashed]1[{\siderule{}}]{
-  \code{
-    \textcolor {darkred}{t_L{<}3}  \wedge    A  ^\star \mysharp  t_L  \cdot    B  
-    \CONTAIN
-    \textcolor {darkred}{t_R{<}4}  \wedge    A  ^\star \mysharp  t_R  \cdot    B  
-  }
-}
-
-\infer[dashed]2[{\textcircled{1}\siderule{\codeme{[OR\text{-}LHS]}}}]{
-  \code{
-    \textcolor {darkred}{t_L{<}3} \wedge   A  ^\star \mysharp  t_L \cdot   B  
-    \vee \textcolor {darkred}{True} \wedge   B   \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B  
-  }
-}
-\end{prooftree}}
-\\~\\
-
-\hline \\
-\code{(II):}
-{\begin{prooftree}
-\hypo{
-  \code{
-    \textcolor {
-      darkred}{t_L{<}3 \wedge } \ \textcolor {
-        blue}{t_L^1{+}t_L^2{=}t_L \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
-      \wedge t_L^2{=}t_R^2
-    } \Rightarrow
-    \textcolor {darkred}{t_R{<}4} 
-  }
-}
-
-\infer[dashed]1[{\textcircled{8}\siderule{\codeme{[REOCCUR]}}}]{
-  \code{
-    \textcolor {
-      darkred}{t_L{<}3} \wedge 
-       A  ^\star \mysharp  t_L^2 \cdot   B  
-    \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge 
-       A  ^\star \mysharp  t_R^2 \cdot   B   \quad  \textcolor{darklavender}{(\ddagger)}
-  }
-}
-
-\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[UNFOLD]}}} \textcolor{blue}{\code{\pi_u :  (t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1)}}]{
-  \code{
-    \textcolor {darkred}{t_L{<}3} \wedge 
-     \cancel{  A   \mysharp  t_L^1}  \cdot    A  ^\star \mysharp  t_L^2 \cdot   B  
-    \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge 
-     \cancel{  A   \mysharp  t_R^1}  \cdot    A  ^\star \mysharp  t_R^2 \cdot   B  
-  }
-}
-
-\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}} \textcolor{blue}{\code{\pi_u :  (t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2)}}]{
-  \code{
-    \textcolor {darkred}{t_L{<}3} \wedge 
-     (   A   \mysharp  t_L^1  \cdot    A  ^\star \mysharp  t_L^2) \cdot   B  
-    \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge 
-     (   A   \mysharp  t_R^1  \cdot    A  ^\star \mysharp  t_R^2) \cdot   B  
-  }
-}
-
-\infer[dashed]1[{\textcircled{5}\siderule{\codeme{[SPLIT]}}}]{
-  \code{
-    \textcolor {darkred}{t_L{<}3} \wedge   A  ^\star \mysharp  t_L \cdot   B  
-    \CONTAIN
-    \textcolor {darkred}{t_R{<}4} \wedge   A  ^\star \mysharp  t_R \cdot   B    
-    \quad \textcolor{darklavender}{(\ddagger)}
-  }
-}
-\end{prooftree}}
-
-\\~\\
-
-\hline
-
-\end{tabular}
-\end{adjustbox}
-            \vspace{-3mm}
-\end{table}
-}
-
-As shown in \tabref{tab:reoccur}, the LHS formula is a 
-disjunction of two effects. An inclusion with a disjunctive 
-antecedent succeeds if both disjunctions entail the consequent, 
-shown in step {\textcircled{1}}.
-
-In step \textcircled{2} of the first sub-tree, in order to eliminate the first event 
-\code{  B  }, \code{  A  ^\star \mysharp  t_R} has to be reduced to~\code{\epsilon}, therefore 
-the time constraints have nothing to do in this branch. 
-Then in steps \textcircled{4}, we
-can simply prove it with the side constraint entailment \code{\textcolor {darkred}{True} \Rightarrow  \textcolor {darkred}{True}} 
-succeed.
-
-Looking at the second sub-tree, in step \textcircled{5}, \code{t_L} and \code{t_R} are firstly split 
-into \code{t_L^1{+}t_L^2} and \code{t_R^1{+}t_R^2}. 
-Then in step {\textcircled{6}, 
-\code{  A   \mysharp  t_L^1} together with \code{  A   \mysharp  t_R^1} are eliminated, unifying \code{t_L^1} and \code{t_R^1} (adding the constraint \code{ t_L^1 {=}  t_R^1}).
-In step {\textcircled{8}, we observe the proposition is isomorphic with one of the the previous step, marked using \code{\textcolor{darklavender}{(\ddagger)}}. 
-%one in
-%step \code{\textcircled{1}}, 
-Hence we apply the rule $\codeme{[REOCCUR]}$ to prove it with a succeed side constraints entailment: 
-\code{
-  \textcolor {
-    darkred}{t_L{<}3 \wedge } \ \textcolor {
-      blue}{t_L^1{+}t_L^2{=}t_L \wedge  t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
-    \wedge t_L^2{=}t_R^2
-  } \Rightarrow
-  \textcolor {darkred}{t_R{<}4} 
-}.
-
-\subsubsection{Expressiveness.}
-%for (timed) linear temporal properties
-\label{subsec:Expressive}
-
-\begin{comment}
-  Classical LTL
-extended propositional logic with the temporal operators 
-\code{\mathcal{G} } (``globally") 
-and 
- \code{\mathcal{F}} (``in the future"), which we also write
- \code{\square} and \code{\Diamond}, respectively. 
- %and introduced the concept of fairness. %, which ensures an infinite-paths semantics. 
- LTL was subsequently extended to include the  \code{\mathcal{U} }
-  (``until") and  \code{\mathcal{X}} (``next time") 
-  operators. 
-  Our \timedEffects\ draws similarities to the metric temporal logic (MTL), 
-which is defined similarly to LTL, 
-  where a set of non-negative real number is added to temporal modal operators.   
-  As shown in 
-  \autoref{tab:ltl_effects}, we are able to recursively encode 
-  these basic MTL operators into \timedEffects, making it 
-   more intuitive and readable, mainly when nested operators 
-   occur.
-
-\begin{table}[h]
-  \vspace{-1mm}
-\caption{\label{tab:ltl_effects} Examples for converting MTL formulae 
-into Effects.  (\code{  \anyevent{A}  ,   \anyevent{B}  } represent 
-different time instants which contain signal \code{\anyevent{A}} and 
-\code{\anyevent{B}} to be present.)
-}
-\setlength{\tabcolsep}{12pt}
-\renewcommand{\arraystretch}{1.4}
-
-\begin{tabular}{llllllll}
-\multicolumn{2}{l|}{\code{ \square \anyevent{A} \equiv   \anyevent{A}    ^\star}} 
-&
- \multicolumn{2}{l|}{\code{ \Diamond_{[m, n]} \anyevent{A}  \equiv m{\leq}t{\leq}n \wedge ({\_}^\star \mysharp t) \cdot   \anyevent{A}    } } 
- &
-  \multicolumn{2}{l|}{\code{ \anyevent{A}\ \mathcal{U}\ \anyevent{B}  \equiv {  \anyevent{A}  }^\star \cdot   \anyevent{B}   }} 
-  &
-  \multicolumn{2}{l}{\code{ \anyevent{A} \rightarrow \anyevent{B}  \equiv {  \overline{\anyevent{A}}  } \vee   \anyevent{A}, \anyevent{B}   }}
-
-  \\
-\hline
-\multicolumn{2}{l|}{\code{ \mathcal{X} \anyevent{A} \equiv      \cdot   \anyevent{A}      }} 
-&
- \multicolumn{2}{l|}{\code{ \square\Diamond \anyevent{A} \equiv   ( {    }^\star \cdot   \anyevent{A}   )^\star }} 
- &
-  \multicolumn{2}{l|}{\code{ \Diamond\square \anyevent{A} \equiv {    }^\star  \cdot   \anyevent{A}  ^\star }} 
-  &
-  \multicolumn{2}{l}{\code{\square (\mathcal{X} \anyevent{A}) \equiv (     \cdot   \anyevent{A}  )^\star }}
-
-\end{tabular}
-  %\vspace{-6mm}
-  \vspace{-1mm}
-\end{table}
-
-%$A  B$ | $\{\overline{A}\} \vee \{A, B\}$ |  Implication
-%Furthermore, consider a property from \textit{Metric Temporal Logic (MTL)}: \code{\anyevent{A}\ \ \mathcal{U}_{[1, 3]}\ \anyevent{B}},
-
-Besides the high compatibility with standard first-order logic, \timedEffects\ makes the 
-temporal verification more scalable. It avoids 
-the %\textit{must-provided} 
-translation schemas for each LTL temporal operator to automata, 
-as comparing to how it has been done in the 
-prior work \cite{DBLP:conf/cav/JagadeesanPO95}.
-Furthermore, by putting the effects in the
-   precondition, our approach naturally composites \emph{past-time LTL} \cite{DBLP:conf/fmics/ReinbacherBHSK11} along the way.
-
-%to express that the server keeps sending messages to its clients 
-%until the work is done (within a time ), the corresponding synced effects can be \code{\anyevent{Send}^5 \cdot \anyevent{Done}} (as we provide the syntactical sugar of \code{\anyevent{Send}^5} to express 5 times concatenation of \code{\anyevent{Send}}).
-%These properties cannot be expressed using standard LTL, as they can only refer to the relative order of events, not to their relative distance in time, yet can be expressed by our effects logic.
-
-\subsubsection{Beyond Regular, Context-Free and Context-Sensitive}
-\end{comment}
-
-The paradigmatic non-regular linear language: 
-\code{t{>} 0 \wedge \anyevent{A}\mysharp{t}\cdot\anyevent{B}\mysharp{t}}, 
-can be naturally expressed by the depended effects. 
-Besides, the effects can also express grammars such as \code{t{>} 0 
-\wedge \anyevent{A}\mysharp{t}\cdot\anyevent{B}\mysharp{t}
-\cdot\anyevent{C}\mysharp{t}}, or 
-\code{n{>} 0 \wedge m{>} 0 \wedge  \anyevent{A}\mysharp{n}
-\cdot\anyevent{B}\mysharp{m}\cdot\anyevent{C}\mysharp{n}}, 
-which are beyond context-free grammar.
-%(by a contradiction proof using Pumping lemma) 
-%and categorized as context-sensitive grammar. 
-Those examples show that the traces which cannot be recognized 
-even by push-down automata (PDA) can be represented by our effects. 
-%As regular grammar and context-free grammar are equivalent to finite state automata (FSA) and  respectively, our effects can not be fully translated into either FSA or PDA.
-However, such specifications are significant, suppose we 
-have a traffic light control system, we could have a 
-specifications \code{n{>} 0 \wedge m{>} 0 \wedge  
-(\anyevent{Red}\mysharp{n}\cdot\anyevent{Yellow}\mysharp{m}}
-\code{\cdot \anyevent{Green}\mysharp{n})^\star}, which specifies that  
-(i) all the colors will occur at each life circle; and 
-(ii) the duration of the green light and the red light is 
-always the same. Moreover, these effects cannot be translated 
-into linear bounded automata (LBA) either, which equivalents to 
-context-sensitive grammar, as LBA are only capable of expressing 
-finite traces.
-
-\subsection{Discussion}
-
-As the examples show, our proposed effects logic and the abstract semantics for 
-\code{\timedL} not only tightly capture the behaviors of a time-critical model 
-but also help to increase the capability of existing techniques. 
-Meanwhile, the inferred temporal traces from a given reactive program enable a compositional 
-timed temporal verification at the source level, which is not yet supported by existing temporal 
-verification techniques.
-
-Our implementation is the first that solves the  inclusion problem of symbolic Timed Automata, 
-which is considered important because it overcomes the following main limitations in traditional 
-timed model checking:  i) they cannot be used to specify and verify systems incompletely 
-specified (i. e., whose timing constants are not known yet), and hence cannot be used in early 
-design phases; ii) verifying a system for a set of timing constants usually requires to enumerate 
-all of them one by one if they are supposed to be integer-valued; in addition, Timed Automata 
-cannot be used to verify a system for a set of timing constants that are to be taken in a 
-real-valued dense interval.
-
-A term rewriting system is efficient because \emph{it only constructs automata as far as it needed}, 
-which makes it more efficient when disproving incorrect specifications, as we can disprove it 
-earlier without constructing the whole automata. In other words, the more incorrect specifications 
-are, the more efficient our solver is.
-
-\section{Related Work}\label{sec:Related_work}
-
-\subsection{Specifications and Real-Time Verification}
-
-%Formally, given a KA is \code{(A,+,\cdot, \star,  0, 1)}, a SKA over a finite set \code{A_B} is \code{(A,+, \cdot, \times, \star,  0, 1,  A_B)}, \code{A_B {\subseteq} A}. 
-%Our \code{\bot} corresponds to the \code{0}; our \code{ \epsilon} corresponds to the \code{1}; our \emph{event} containing simultaneous signals can be expressed via \code{\times};
-
-Compositional specification for real-time systems based on timed process algebras has been extensively studied.
-Examples include the CCS\code{\text{+}}Time \cite{DBLP:conf/icalp/Yi91} and Timed CSP \cite{DBLP:journals/tse/DongHQSY08}.
-The differences are: 
-i) in CCS\code{\text{+}}Time, if there is no timed constraints specified, transitions takes no time; whereas in our effects logic, it means \code{true} (arbitrary time), which is more close to the real life context where the time bounds are often unpredictable.
-ii) Timed CSP does not allow explicit representation of real-time through the manipulation of clock variables.
-
-%relies on implicit clocks, which means it
-
-There have been a number of translation-based approaches on building verification support for timed process algebras.
-For example, Timed CSP \cite{DBLP:journals/tse/DongHQSY08} is translated to Timed Automata (TA) so that the model checker Uppaal can be \cite{DBLP:journals/sttt/LarsenPY97} applied.
-TA are finite state automata equipped with clock variables. Models based on TA often have simple structures. For example, the input models of the Uppaal are networks of TA with no hierarchy.
-
-%Given the well-established TA techniques,
-
-In practice, system requirements are often structured into phases, which are then composed in many different ways, while TA is deficiency in modeling complex compositional systems.
-Users often need to manually cast high-level requirements into a set of clock variables with carefully calculated clock constraints, which is tedious and error-prone \cite{DBLP:journals/tosem/00010DLSA13}.
-%Also real-time system modeling based on timed process algebras often suffers from lack of language features or automated tool support. 
-On the other hand, all the translation-based approaches share the common problem: 
-%goes  exponential in the number of automata states; and ii) 
-the overhead introduced by
-the complex translation makes it particularly inefficient when \emph{disproving} properties.
-
-We believe in that the goal of verifying real-time systems, in particular 
-safety-critical systems is to check logical temporal properties, which can 
-be done without constructing the whole reachability graph or the full power 
-of model-checking. We are of the opinion that our approach is simpler as 
-it is based directly on constraint-solving techniques and can be fairly 
-efficient in verifying systems consisting of many components as it avoids 
-to explore the whole state-space \cite{DBLP:conf/icfem/SongC20,DBLP:conf/forte/YiPD94}.
-
-%About that, between TRS and the construction of efficient automata, recent work \cite{DBLP:conf/icfem/SongC20} has shown that the former has a minor performance advantage (over a
-%benchmark suite) when it is compared with
-%state-of-the-art PAT \cite{DBLP:conf/cav/SunLDP09} model checker.
-%Improvement came from the avoidance of the more
-%expensive automata construction process.
-
-%Our present work avoided the consideration for the more general \code{\times} operation from SKA
-%and customized the TRS for inclusion (instead of equivalence) checking. These decisions led to some opportunities for improvements.
-Moreover, between TRS and the construction of efficient automata, prior work has recently shown in \cite{DBLP:conf/icfem/SongC20} that the former has a minor performance advantage (over a benchmark suite) when it is compared with state-of-the-art PAT \cite{DBLP:conf/cav/SunLDP09} model checker.
-Improvement came from the avoidance of the more expensive automata construction process.
-
-\subsection{Existing Traces-Based Effects Systems}
-
-Combining program events with a temporal program logic for asserting properties of event traces yields a powerful and general engine for enforcing program properties.
-Results in \cite{DBLP:journals/jfp/SkalkaSH08,DBLP:conf/aplas/SkalkaS04,DBLP:conf/aplas/MarriottSS03} have demonstrated that static approximations of program event traces can be generated by type and effect analyses \cite{DBLP:journals/iandc/TalpinJ94,DBLP:books/daglib/0098135}, in a form amenable to existing model-checking techniques for verification.
-We call these approximations trace-based effects.
-
-Trace-based analyses have been shown capable of statically enforcing flow-sensitive security properties such as safe locking behavior \cite{DBLP:conf/pldi/FosterTA02} and resource usage policies such as file usage protocols and memory management \cite{DBLP:conf/aplas/MarriottSS03}.
-In \cite{DBLP:conf/csfw/BartolettiDF05}, a trace effect analysis is used to enforce secure service composition.
- Stack-based security policies are also amenable to this form of analysis, as shown in \cite{DBLP:conf/aplas/SkalkaS04}.
-
- %  has effects capturing sequences of events, including requirements about things that must have happened prior to executing a given block of code
-
-More related to our work, prior research has been extending Hoare logic with event traces.
-The work \cite{DBLP:journals/jsc/MalechaMW11} focuses on finite traces (terminating runs) for web applications, leaving the divergent computation, which indicates \code{false}, verified for every specification.
-The work \cite{DBLP:conf/esop/NakataU10} focuses on infinite traces (non-terminating runs) by providing coinductively trace definitions.
-More recent works \cite{DBLP:conf/tableaux/BubelDHN15,DBLP:conf/icfem/SongC20} proposed dynamic logics and unified operators to reason about possibly finite and infinite traces at the same time.
-
-Moreover, this paper draws similarities to \textit{contextual effects} \cite{DBLP:conf/popl/NeamtiuHFP08}, which computes the effects that have already occurred as the prior effects.
-The effects of the computation yet to take place as the future effects.
-Besides, prior work \cite{DBLP:conf/fase/NielsonAN98} proposes an annotated type and effect system and infers behaviors from CML \cite{DBLP:conf/mcmaster/Reppy93} programs for channel-based communications, though it did not provide any inclusion solving process.
-
-However, none of the previous works have considered adding real-time abstractions into the modeling for a more extensive timed verification, which is our work's main contribution.
-
-%
-%
-%deploys a Hoare logics based on  while its  networking library does not capture timeout, making certain properties difficult or impossible to specify. And because 
-%
-
-%While  , , the reasoning on timed traces is new.
-Prior timed effects in precondition is also new, allowing greater safety to be applied to sequential reactive controlling systems such as web applications, communication protocols and IoT systems.
-
-\section{Conclusion}
-\label{sec:conclusion}
-%HipHop.js
-We define the syntax and semantics of the novel \timedEffects, 
-to capture real-time systems' behaviors and  temporal properties. 
-We demonstrate how to give a rather axiomatic semantics to 
-\code{\timedL} by timed-trace processing functions. We use 
-this semantic model to enable  a Hoare-style forward verifier,  
-which computes the program effects constructively.
-We present an effects inclusion checker (the TRS) to prove the 
-annotated temporal properties efficiently. We prototype the 
-verification system and show its feasibility.
-To the best of our knowledge, our work is the first 
-automates modular timed verification for real-time systems 
-using an expressive effects logic.
-
-%%
-%% (and NOT an unnumbered section). This ensures the proper
-%% identification of the section in the article metadata, and the
-%% consistent spelling of the heading.
-%\begin{acks}
-%\end{acks}
-
-%%
-%% The next two lines define the bibliography style to be used, and
-%% the bibliography file.
+This document is a model and instructions for \LaTeX.
+Please observe the conference page limits.
 
@@
 
-\section{Soundness of the Forward Rules} 
- \label{proof:SoundnessProof_FE}
-
-Given any system configuration \code{\zeta = (\env, e)}, by applying the operational
-  semantics rules, \\
-  if \code{(\env, e) {\rightarrow^*} (\env^\prime, ())} produces concrete 
-  execution time \code{d} and event sequence \code{\varphi}, and the forward verifier reasons \code{ \vdash  
-  \s{\env, \epsilon} \ e\  \s{\Pi, \Theta}}, then, 
-  \code{
-   \exists (\pi \wedge \es) \in \s{\Pi, \Theta} } such that 
-  \code{d, \env^\prime, \varphi  \models (\pi\wedge \es)}
-
-  \begin{proof}
-    ~\\
-  \begin{enumerate}
-  \item \textbf{Delay:}  
-  \input{rules/op_delay.tex}
-\noindent When $\zeta = (\env,  \textbf{delay}[d]) {\rightarrow^*} (\env, ()) $, by applying rules \code{[delay_1]} and \code{[delay_2]}, 
-it produces the concrete sequence [], and takes concrete time \codeme{d}. \\
-By \code{[FV\text{-}Delay]}, $\vdash  \s{\env, \epsilon} \ \textbf{delay}[d]\  \s{\env \wedge (t{=}d), \epsilon\mysharp t}$. \\
-Then \code{\env \wedge (t{=}d) \wedge \epsilon\mysharp t} is the witness such that \code{d, \env, []  \models (\env \wedge (t{=}d) \wedge \epsilon\mysharp t)}. 
-\\
-
-\item \textbf{Timeout:}  
-\input{rules/op_to.tex}
-\noindent When $\zeta = (\env,  e_1\ \textbf{timeout}  [d] \ e_2) {\rightarrow^*} (\env^\prime, ()) $, 
-there are two possibilities:
-
-- \code{e_1} started before time limit \code{d}, by applying rules \code{[to_2]}, \code{[to_3]} and \code{[to_1]}, 
-it produces the concrete sequence [\anyevent{A}; \code{\varphi(e_1^\prime)}], and \anyevent{A} takes less than \codeme{d} time-units. \\
-By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
-\s{\env \wedge (t{\leq}d), \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}$. \\
-Then \code{\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})} is 
-the witness such that \code{d, \env^\prime, [\anyevent{A}; \code{\varphi(e_1^\prime)}]  
-\models (\env \wedge (t{\leq}d) \wedge \anyevent{A}\mysharp t \cdot (\es_{e_1^\prime})}. 
-\\
-- \code{e_1} never started, by applying rules \code{[to_4]}, 
-it produces the concrete sequence [\code{\varphi(e_2)}], and it takes more than \codeme{d} time-units. \\
-By \code{[FV\text{-}Timeout]}, $\vdash  \s{\env, \epsilon} \ e_1\ \textbf{timeout}  [d] \ e_2\  
-\s{\env \wedge (t{>}d), (\es_2 \mysharp t)}$. \\
-Then \code{\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)} is 
-the witness such that \code{d, \env^\prime, [\varphi(e_2)]  
-\models (\env \wedge (t{>}d) \wedge (\es_2 \mysharp t)}.
-
-\item \textbf{Deadline:}  
-\input{rules/op_ddl.tex}
-When $\zeta = (\env,  \textbf{deadline}  [d]\ e) {\rightarrow^*} (\env^\prime, ()) $, 
-by applying rules \code{[ddl_1]}, \code{[ddl_2]}, 
-it produces the concrete sequence [\code{\varphi(e)}], and it takes less than \codeme{d} time-units. \\
-By \code{[FV\text{-}Deadline]}, $\vdash  \s{\env, \epsilon} \ \textbf{deadline}[d]\ e 
-\ \s{\env \wedge (t{<}d), \es(e)\mysharp t}$. \\
-Then \code{\env \wedge (t{<}d) \wedge \es(e)\mysharp t} is the witness such that 
-\code{d, \env^\prime, [\code{\varphi(e)}]  \models (\env \wedge (t{<}d) \wedge \es(e)\mysharp t)}. \\
-
-\item We omit the primitives which are not related to the timing.
-
-  \end{enumerate}
-
- \end{proof}
-
-\section{Termination  of the TRS}  \label{proof:TerminationProof}
-
-\begin{proof}\label{proof:termination} 
-Let Set[\inclusion] be a data structure representing the sets of inclusions.
-
-We use \code{S} to denote the inclusions to be proved, and \code{H} to accumulate  "inductive hypotheses", i.e., \code{S,  H \in Set[\inclusion]}.
-
-Consider the following partial ordering \code{\succ} on pairs \code{\langle S, H \rangle}:
-\begin{gather*}
-\code{\langle S_1, H_1 \rangle \succ \langle S_2, H_2 \rangle}\ \ \text{iff}\ \ \code{|H_1| < |H_2| \vee 
-(|H_1| = |H_2| \wedge |S_1| > |S_2|)}. 
-\end{gather*}
-where \code{|X|} stands for the cardinality of a set \code{X}.
-Let \code{\Rightarrow} denote the rewrite relation, then \code{\Rightarrow^*} denotes its reflexive transitive closure.
-For any given \code{S_0}, \code{H_0}, this ordering is well founded on the set of pairs \code{\{\langle S, H \rangle | \langle S_0, H_0 \rangle \Rightarrow^* \langle S, H \rangle \}}, due to the fact that \code{H} is a subset of the finite set of pairs of all possible derivatives in initial inclusion.
-
-Inference rules in our TRS given in \secref{InferenceRules} transform current pairs \code{\langle S, H \rangle} to new pairs \code{\langle S^\prime, H^\prime \rangle}. 
-And each rule either increases \code{|H|} (Unfolding) or, otherwise, reduces \code{|S|} (Axiom, Disprove, Prove), therefore the system is terminating.
-
- \end{proof}
-
-\section{Soundness  of the TRS} 
- \label{proof:SoundnessProof}
-
-  For each inference rules, if inclusions in their premises are valid, and their side conditions are satisfied, then goal inclusions in their conclusions are valid.
-
-  \begin{proof}
-    ~\\
-  \begin{enumerate}
-  \item \textbf{Axiom Rules:} 
-  \input{rules/rule1}
-  - It is easy to verify that antecedent of goal entailments in the rule $\codeme{[Bot\text{-}LHS]}$ is unsatisfiable. Therefore, these entailments are evidently valid.\\
-  - It is easy to verify that consequent of goal entailments in the rule $\codeme{[Bot\text{-}RHS]}$ is unsatisfiable. Therefore, these entailments are evidently invalid.\\
-
-  \item \textbf{Disprove Rules:} 
-  \input{rules/rule2}
-  - It's straightforward to prove soundness of the rule $\codeme{[DISPROVE]}$, Given that \codeme{\es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.
-Therefore, these entailments are evidently invalid.\\
-
-  \item \textbf{Prove Rules:} 
-  \input{rules/rule3}
-  - To prove soundness of the rule $\codeme{[PROVE]}$, we consider an arbitrary model, \codeme{d, s, \varphi} such that:  
-  \codeme{d,  s, \varphi \models  {\pi_1 \wedge \es_1}}. Given the side 
-  conditions from the promises, we get \codeme{d,  s, \varphi \models 
-  {\pi_2 \wedge \es_2}}. When the \code{\m{fst}} set of \code{\es_1} is 
-  empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon} and 
-  \code{\pi_2 \wedge \es_2} is nullable. For both cases, the inclusion 
-  is valid.
-
-  - To prove soundness of the rule $\codeme{[REOCCUR]}$, we consider 
-  an arbitrary model, \codeme{d, s, \varphi} such that:  \codeme{d,  s, 
-  \varphi \models  {\pi_1 \wedge \es_1}}. Given the promises that  
-  \codeme{\pi_1 \wedge \es_1 \CONTAIN \pi_3 \wedge \es_3}, we get 
-  \codeme{d,  s, \varphi \models {\pi_3 \wedge \es_3}}; Given the 
-  promise that there exists a hypothesis \codeme{\pi_3 \wedge \es_3 
-  \CONTAIN  \pi_4 \wedge \es_4}, we get \codeme{d, s, \varphi \models 
-  {\pi_4 \wedge \es_4}}; Given the promises that  
-  \codeme{\pi_4 \wedge \es_4 \CONTAIN \pi_2 \wedge \es_2}, we get 
-  \codeme{d, s,  \varphi \models {\pi_2 \wedge \es_2}}. Therefore,  
-  the inclusion is valid. 
-  \\
-
-  \item \textbf{Unfolding Rule:} 
-  \input{rules/rule4}
-
-  - To prove soundness of the rule $\codeme{[UNFOLD]}$, we consider an 
-  arbitrary model, \codeme{d_1, s_1,  \varphi_1} and \codeme{d_2, s_2,
-   \varphi_2}  such that:  \codeme{d_1, s_1,  \varphi_1 \models {\pi_1 \wedge
-    \es_1}} and \codeme{d_2, s_2,  \varphi_2 \models  {\pi_2 \wedge \es_2}}. 
-    For an arbitrary event \codeme{h}, let \codeme{d_1^\prime, s_1^\prime,
-     {\varphi_1}^\prime \models \codeme{h}^{\text{-}1}\llbracket  \pi_1\wedge \es_1 \rrbracket}; 
-     and 
-  \codeme{d_2^\prime, s_2^\prime, {\varphi_2}^\prime \models 
-  \codeme{h}^{\text{-}1}\llbracket \pi_2 \wedge \es_2 \rrbracket}.
-
-  Case 1), \codeme{\codeme{h} \notin F}, 
-  \codeme{d_1^\prime, {\varphi_1}^\prime \models \bot }, 
-  thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime 
-  \models D^{\pi_2}_{\codeme{h}}( \es_2)};
-
-  Case 2), \codeme{\codeme{h} \in F}, given that inclusions 
-  in the rule's premise is valid, then \codeme{d_1^\prime, s_1^\prime, 
-  {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{h}}( \es_2)}.
-
-  By \defref{Inclusion}, since for all \codeme{h}, 
-  \codeme{D^{\pi_1}_{\codeme{h}} (\es_1) \CONTAIN   
-   D^{\pi_2}_{\codeme{h}}( \es_2)}, the conclusion is valid. 
-  \\
-
-  \end{enumerate}
-  All the inference rules used in the TRS are sound, therefore the
-   TRS is sound.
-  \end{proof}
-
-% \section{Completeness Proof} 
-% \label{proof:Completeness}
-
 \end{document}
-\endinput
-%%
-%% End of file `sample-manuscript.tex'.

### 2022-08-05 paper/icse23.tex
m

@@
 \usepackage{cite}
-\usepackage{comment}
+\usepackage[numbers]{natbib}
+\usepackage{filecontents}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{xcolor}
-\newcommand{\timedEffects}{\emph{TimEffs}}
+\usepackage{comment}
+\usepackage{stmaryrd}
+\usepackage{pifont}% http://ctan.org/pkg/pifont
+\newtheorem{definition}{Definition}
+\usepackage{tikz}
+\usepackage{enumerate}
+\usepackage{amsmath}
+\usepackage{csquotes}
+\usepackage{varwidth}
+\newcommand{\cmark}{\ding{51}}%
+\newcommand{\xmark}{\ding{55}}%
+\newcommand{\anynotevent}[1]{{\textcolor{darkred}
+{{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
+\newcommand{\env}{\code{\mathcal{V}}}
+\newcommand{\es}{\theta}
+\newcommand{\ev}{ev}
+\newcommand{\siderule}[1]{
+\code{\footnotesize{\textcolor{mGray}{#1}}}}
+\usepackage{adjustbox}
+\usepackage{ebproof}
+\usepackage{cancel}
+\newcommand{\CONTAIN}{\sqsubseteq}
+\definecolor{mypink}{RGB}{219, 48, 122}
+\definecolor{darklavender}{rgb}{0.45, 0.31, 0.59}
+\definecolor{deepcerise}{rgb}{0.85, 0.2, 0.53}
+\def\defeq{\ensuremath{\,\triangleq}}
+\definecolor{darkred}{rgb}{0.55, 0.0, 0.0}
+\newcommand{\anyevent}[1]{{\textcolor{darkred}
+{{\textbf{\small #1}}}}}
 \newcommand\figref[1]{Fig. \textcolor{black}{\ref{#1}}.}
@@
 \newcommand{\timedL}{\code{C^{t}}}
-\newcommand{\anyevent}[1]{{\textcolor{darkred}
-{{\textbf{\small #1}}}}}
-\newcommand{\anynotevent}[1]{{\textcolor{darkred}
-{{\textbf{\footnotesize $\overline{\text{#1}}$}}}}}
-\newcommand{\code}[1]{{\tt{\ensuremath{\m{#1}}}}}
-\newcommand{\codeme}[1]{{\tt{\ensuremath{#1}}}}
-\newcommand{\CONTAIN}{\sqsubseteq}
-\newcommand{\underscore}{\textcolor{vividauburn}{\code{\_}}}
-\newcommand{\m}{\mathit} 
-\newcommand{\lappend}{\mathrel{\texttt{++}}}
-
-\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
 
@@
 \newcommand\algoref[1]{Algorithm~\textcolor{blue}{\ref{#1}}}
+\newcommand{\code}[1]{{\tt{\ensuremath{\m{#1}}}}}
+\newcommand{\m}{\mathit} 
+\newcommand{\lappend}{\mathrel{\texttt{++}}}
+\definecolor{mGray}{rgb}{0.4,0.4,0.4}
+\definecolor{mPurple}{rgb}{0.58,0,0.82}
+\definecolor{huntergreen}{rgb}{0.33, 0.42, 0.18}
+
+\newcommand{\mysharp}{{\mathrel{\texttt{\#}}}}
+\newcommand{\timedEffects}{\emph{TimEffs}}
+\usepackage{wrapfig}
+\newcommand{\effect}{{\ensuremath{\mathrm{\Phi}}}}
+\usepackage{listings}
+
+\lstdefinelanguage{JavaScript}{
+  keywords={typeof, void, const, new, int, catch, function, return, null, catch, switch, var,async, await, if, setTimeout, this, then, while, post, else, case, break, return},
+  keywordstyle=\color{blue}\bfseries,
+  ndkeywords={class, export, boolean,event, timeout, deadline, delay,  throw, implements, import, this},
+  ndkeywordstyle=\color{darkgray}\bfseries,
+  identifierstyle=\color{black},
+  sensitive=false,
+  comment=[l]{//},
+  morecomment=[s]{/*}{*/},
+  commentstyle=\color{darklavender}\ttfamily,
+  stringstyle=\color{red}\ttfamily,
+  morestring=[b]',
+  morestring=[b]"
+}
+
+\lstset{
+   language=JavaScript,
+   %%backgroundcolor=\color{lightgray},
+   extendedchars=true,
+   basicstyle=\footnotesize\ttfamily,
+   showstringspaces=false,
+   showspaces=false,
+%frame=single
+numbers=left,   
+xleftmargin=1em, 
+    numberstyle=\tiny\color{mGray},
+   numbersep=10pt,
+   tabsize=4,
+   breaklines=true,
+   showtabs=false,
+   captionpos=b,
+   keywordstyle=[2]\color{purple}\bfseries, %
+   morekeywords=[2]{do, hiphop,every, loop,suspend, when, signal, end, present, nothing, emit,in, out, yield,abort, fork, par, run},
+}
 
@@
 email address or ORCID}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
+\and
+\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
 }
 \end{comment}
-
+\pagestyle{plain}
 \maketitle
@@
     soundness; report on case studies and the experimental results.
+
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+    Temporal Verification,
+    Dependant Effects,
+    Hoare-style Forward Verifier,
+    Term Rewriting System,
+    Timed Verification
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+\label{Introduction}
 
-\bibliographystyle{ACM-Reference-Format}
+Specification and verification of real-time systems are essential 
+to research topics with practical implications. During the last 
+more than two decades, a popular approach for specifying real-time systems has been 
+based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
+Timed Automata are powerful 
+in designing real-time models with explicit clock variables. Real-time 
+constraints are captured by explicitly setting/resetting clock variables. 
+A number of automatic verification support for Timed Automata have proven 
+to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
+
+Models based on Timed Automata often adopt a simple structure, e.g., a 
+network with no hierarchy. The benefit is that 
+efficient model checking is made feasible. Nonetheless, designing and 
+verifying compositional real-time systems is becoming an increasingly 
+difficult task due to the widespread applications and increasing complexity 
+of such systems. In industrial case studies of real-time system verification, system 
+requirements are often structured into phases, which are then composed 
+sequentially, in parallel and alternatively \cite{DBLP:conf/emsoft/LarsenMNS05}. 
+Unlike timed process algebras, Timed Automata lack high-level 
+compositional patterns for hierarchical design. As a result, users often 
+need to manually cast those terms into a set of clock variables with 
+carefully calculated clock constraints. The process is tedious and error-prone.
+
+We investigate an alternative approach for modeling and verifying 
+compositional real-time systems. In this work, 
+we propose a novel temporal specification language, 
+which enables a compositional verification via a  Hoare-style 
+forward verifier and a term rewriting system (TRS). 
+More specifically, we specify system behaviors in the form of 
+{Timed Effects} (\timedEffects), which integrates the Kleene Algebra 
+with dependent values and arithmetic constraints, 
+%gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
+to 
+%capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
+provide real-time abstractions into traditional linear temporal logics. 
+%Resource usages, provided by a \emph{dynamic ticks}\cite{DBLP:conf/fdl/HanxledenBG17}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
+For example, one safety property, \textit{"The event \anyevent{Done} 
+will be triggered no later than one time unit"}\footnote{Without loss of generality, 
+we use integer values to represent time units in this 
+paper.% while it can bes extended to real numbers and other 
+%time measurement units.
+}, is expressed in \timedEffects\ as: 
+\begin{align*}
+  \code{\effect \defeq \  0 {\leq} t {<}1 \wedge ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}
+\end{align*}  
+%The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
+%and .
+%which replaces temporal operators by time-constrained versions from 
+Here, \code \wedge  connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
+constraints for the \emph{logical-time} sequences \cite{DBLP:conf/fdl/HanxledenBG17}; 
+\code{\_} is a wildcard matching to any event; 
+Kleene star \code{\star} denotes trace repetition.
+The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1)}\ }\anyevent{Done}' 
+in metric temporal logic (MTL), reads \textit{"within one second, 
+\anyevent{Done} finally happens"}.
+
+Moreover, the time bounds 
+can be dependent on the program inputs, demonstrated in 
+\figref{fig:Value_dependent_intro}; we mark the precondition and postcondition
+using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.
+
+\begin{wrapfigure}{L}{0.39\columnwidth}
+\begin{lstlisting}[name=coffee]
+void addOneSugar() 
+/*req: true/\ _^*
+  ens: t>1 /\ emp#t */ 
+{ timeout ((), 1); }
+
+void addNSugar (int n) 
+/*req: true/\ _^*
+  ens: d>=n/\ Sugar#d */
+{ if (n == 0) { 
+      event ["Sugar"];} 
+  else {
+      addOneSugar();
+      addNSugar (n-1);}} 
+\end{lstlisting}
+\caption{Value-dependent specification.} 
+\label{fig:Value_dependent_intro}
+\vspace{0mm}
+\end{wrapfigure}
+
+The function \code{addNSugar} takes a parameter \code{n}, representing 
+the portion of the sugar we need to add. When \code{n} 
+equals to \code{0}, 
+it simply raises an event \anyevent{Sugar} to mark the end of the process. 
+Otherwise, it adds one portion of the sugar by calling
+\code{addOneSugar()}, then recursively calls 
+\code{addNSugar} with parameter \code{n-1}. 
+The use of statement \lstinline|timeout(e, d)| is standard \cite{JSTO}, 
+which executes a block of code \code{e} after the specified time \code{d}.
+Therefore, the time spent on adding one portion of the sugar is 
+no less than one time unit. Note that {\color{darklavender}\code{\emph{emp\#t}}} 
+refers to an empty trace which takes time \code{t}.
+
+Both preconditions require no arithmetic constraints,   
+and  have no temporal constraints upon 
+the history traces. 
+The postcondition of \code{addNSugar(n)} indicates that  the method 
+generates a finite trace where \anyevent{Sugar} takes a no 
+less 
+than \code{d} time-units delay to finish.
+
+Although these examples are simple, they show the benefits of deploying 
+value-dependent 
+time bounds, which is beyond the capability of Timed Automata. Intuitively, if traditional Timed Automata define an 
+\emph{exact} transition system, \timedEffects\ define 
+a set (possibly infinite) of exact transition systems.
+
+Moreover, we deploy a Hoare-style forward verifier to 
+soundly infer the actual behaviors of given programs 
+concerning the well-defined operational semantics. 
+This approach provides a 
+\emph{direct} (opposite to the techniques which require 
+ manual and remote modeling processes), 
+  and modular compositional 
+verification for real-time systems, which are not possible
+by existing techniques.
+
+\begin{comment}
+  we express, the effects of \code{addNSugar(d)} as:
+\begin{align*}
+&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
+\end{align*}  
+effects of \code{addNSugar(n)} as:
+\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}
+
+\end{comment}
+
+   %they already illustrate the gain of expressiveness from  existing temporal logics and traditional Timed Automata.
+
+%properties
+
+Having \timedEffects\ to be  the specification language, 
+and the forward verifier to infer the program behaviors, 
+we are interested 
+in the following verification problem: 
+Given a program \code{\mathcal{P}},
+and a temporal specification \code{\effect^{\prime}}, does the inclusions 
+\code{\effect^{\mathcal{P}} \CONTAIN \effect^{\prime}} holds\footnote{The 
+inclusion relation $\CONTAIN$ is formally defined in \defref{Inclusion}.}? Typically, 
+checking the inclusion/entailment between the concrete program effects \code{\effect^{\mathcal{P}}} and the valid traces \code{\effect^{\prime}} proves that: the program \code{\mathcal{P}} will never lead to unsafe traces which violate \code{\effect^{\prime}}.
+
+Since the expressiveness of \timedEffects\ goes beyond 
+finite-state automata, it is neither sufficient nor efficient to 
+translate them 
+into Timed Automata and reply on the solving engines of Timed Automata.
+Therefore we 
+develop a novel TRS, 
+which  is inspired by Antimirov and Mosses’ algorithm\footnote{Antimirov and Mosses' 
+algorithm was designed for deciding the inequalities of regular 
+expressions based on an 
+complete 
+axiomatic algorithm of the algebra of regular sets.} \cite{DBLP:journals/tcs/AntimirovM95} but solving the 
+language inclusions between more expressive \timedEffects.
+
+\begin{comment}
+  several compositional ,  
+are introduced to capture quantitative timing constraints.
+The idea is to
+
+In this work, we study temporal verification of 
+compositional real-time systems,
+
+Existing automatic verification techniques massively rely on 
+the Timed Automata which requires manually cast of clock variables with 
+carefully calculated clock constraints.
+
+A TRS is a refutation method that normalizes expressions in such a way 
+that checking their inclusion corresponds to an iterated process of 
+checking the inclusion of their \emph{partial derivatives} 
+\cite{antimirov1995partial}. 
+Works based on such a TRS \cite{DBLP:conf/icfem/SongC20,DBLP:journals/tcs/AntimirovM95,DBLP:journals/ijfcs/AlmeidaMR09,DBLP:conf/fsttcs/KeilT14,DBLP:journals/jcss/Hovland12}  show its feasibility and suggest that this method is a better average-case algorithm than those based on the comparison of automata.
+
+This work targets timed temporal verification, and to the best of 
+the authors' knowledge, it proposes the first algebraic TRS 
+ for the real-time verification. 
+\end{comment}
+
+ In short, the main contributions of this work are:
+
+\begin{enumerate}
+\item \textbf{Language Abstraction:} we formally define 
+a core language \timedL, by defining its syntax and operational semantics, 
+generalizing the real-time systems with mutable variables and timed 
+behavioral patterns. %, such as \emph{delay}, \emph{timeout}, \emph{deadline}.
+
+\item \textbf{Specification Language:} we propose \timedEffects, 
+by defining its 
+syntax and semantics, gaining the expressive power beyond 
+traditional modeling languages for real-time systems.
+
+\item \textbf{Automated Forward Verifier:} we establish a sound axiomatic 
+semantics to infer the 
+temporal behaviors of given target programs.  The verifier triggers the back-end 
+solver TRS.
+
+\item \textbf{An Efficient TRS:}
+we present the rewriting rules to prove the inclusion relations between the inferred 
+behaviors and the given temporal specifications, both in  \timedEffects.
+
+\item \textbf{Implementation and Evaluation:} we prototype the novel 
+effects logic and the automated verification system, 
+prove the soundness, report on case studies and experimental results.
+
+\end{enumerate}
+
+\section{Overview}\label{sec:Overview}
+
+We now highlight our main methodologies, using the example shown 
+in \figref{fig:overview_coffee} This example simulates a 
+coffee machine, which dynamically adds sugar based on the user's input number.
+
+%\subsection{HipHop.js and Dependent Effects}
+\subsection{\timedEffects}
+As shown in \figref{fig:overview_coffee}, we define Hoare-triple 
+style specifications (enclosed in 
+\textcolor{darklavender}{\ttfamily{{/* ... */}}}) for each function, 
+which leads to a compositional verification strategy, where static 
+checking and timed temporal verification can be done locally.
+
+%columns=fullflexible
+\begin{wrapfigure}{L}{0.47\columnwidth}
+  %\vspace{-1mm}
+\begin{lstlisting}[name=coffee]
+void makeCoffee (int n)
+/*req: n>=0 /\ _^* . Cup
+  ens: (n<=t<=5 /\ t1<=3) /\
+       (Sugar#t).(Coffee#t1) */
+{ deadline (addNSugar(n), 5);
+  deadline (event["Coffee"], 3);}
+
+int main ()
+/*req: true/\emp
+  ens: t<=8/\(((!Done)^*)#t).Done */ 
+{ event["Cup"];
+  makeCoffee (3);
+  event["Done"];}
+\end{lstlisting}  
+   %   \vspace{-1mm}
+\caption{To make coffee with three portions of sugar 
+within eight time units.}\label{fig:overview_coffee}
+ %        \vspace{0mm}
+\end{wrapfigure}
+
+The precondition of \code{makeCoffee} 
+ specifies that the input integer value \code{n} is non-negative, and it requires that before entering into this 
+function, this history trace must contain the event  
+\anyevent{Cup} on the tail. Therefore, function calls to \code{makeCoffee} which 
+do not satisfy the precondition lead to a failure of the verification. 
+\code{makeCoffee} sets a 
+five time-units deadline while calling 
+\code{addNSugar} (defined in 
+Fig. \textcolor{black}{\ref{fig:Value_dependent_intro}}),
+ with argument \code{n}; then emits event \anyevent{Coffee} with
+ a three time-units deadline.
+
+The precondition of \code{main} requires no arithmetic constraints 
+on its inputs (expressed as \code{true}) and 
+an empty history trace (denoted using \code{emp} or \code{\epsilon}).
+The postcondition of \code{main} specifies 
+that before the final \anyevent{Done} happens, there is no 
+occurrence of \anyevent{Done} (\code{!A} refers to the 
+negation of the event \code{A}). Moreover, the whole process takes 
+no more than eight time-units to hit the final event.
+
+\timedEffects\ supports more features such as \emph{disjunctions}, 
+\emph{guards} and \emph{parallelism}, etc., which can be found in 
+\secref{subsec:Specification_language} and 
+\secref{subsec:Specification_Semantics}.  
+Note that directly from the specifications, we are aware of:  
+(i) the branching properties: different arithmetic conditions on the input parameters lead to different temporal effects;
+and (ii) the required history traces: by defining the prior effects 
+in precondition. 
+The examples 
+already show that our  effects provide more detailed information than 
+traditional timed verification, and in fact, it cannot be fully 
+captured by any prior works \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,DBLP:journals/sttt/Yovine97,DBLP:conf/seke/WangWH05}.
+Nevertheless, the gain in expressive power comes from the efforts 
+of a more dedicated verification process, handled by our forward verifier and TRS.
+
+\subsection{Forward Verification}
+As shown in \figref{fig:forward_example}, we demonstrate the 
+forward verification process of the functions \code{addOneSugar} and   {\code{addNSugar}}.
+The current effects states are captured 
+in the form of 
+\code{\{ \textcolor{darklavender}{\effect_C} \}}. 
+To facilitate the illustration, we label the verification 
+steps by (1), ..., (11), and mark the deployed inference 
+rules (cf. \secref{Forward_Rules}) in \textcolor{mGray}{[gray]}.
+The verifier invokes the TRS to check language inclusions along the way.
+
+\begin{comment}
+
+/*require n>=0, _^*
+  ensure  t>=n, Sugar#t */
+{
+
+\end{comment}
+
+{
+\begin{figure}[!ht]
+    %  \vspace{-4mm}
+     \begin{minipage}[c]{\columnwidth}
+         \centering
+         {%\small
+         \begin{enumerate}
+\item \lstinline|void addOneSugar() {| \textcolor{mGray}{\footnotesize 
+\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addOneSugar(n)}}.}} \\
+\textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addOneSugar(n)} =  true \wedge  \_^\star \} }} 
+\quad \siderule{\scriptsize[FV\text{-}Meth] } \\
+
+\item ~\qquad \lstinline|timeout ((), 1);}| \\
+\textcolor{darklavender}{\code{\effect_C^\prime {=} t_0{>}1   \wedge \_^\star \cdot \epsilon \mysharp t_0  }} 
+\quad \siderule {\scriptsize [FV\text{-}Timeout]}
+\item 
+\textcolor{darkred}{\code{
+%\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
+\effect_C^\prime \CONTAIN \effect_{pre}^{addOneSugar(n)} \cdot \effect_{post}^{addOneSugar(n)} \Leftrightarrow  }} 
+ %\textcolor{mGray}{  \emph{(-- check postcondition --) }}
+ \textcolor{darkred}{\code{\code{\code{t_0{>}1   \wedge \epsilon \mysharp t_0}
+ \CONTAIN t{>}1   \wedge \epsilon \mysharp t }}}
+ \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked. }}
+ \\ 
+%ens: t>1 /\ emp#t */ { 
+  \noindent\rule{0.92\columnwidth}{0.4pt}
+  \vspace{2mm}
+~\\
+\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize 
+\quad \emph{// initialize the effects state using the function precondition \code{\effect_{pre}^{addNSugar(n)}}.}} \\
+     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  true \wedge  \_^\star \} }} 
+      \quad \siderule{\scriptsize[FV\text{-}Meth] } \\
+     \item ~\qquad \lstinline|if (n == 0) {| \\
+     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} 
+     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
+      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
+     \textcolor{darklavender}{\code{\{n{=}0 \wedge   \_^\star \cdot Sugar\} }} 
+     \quad \siderule{\scriptsize [FV\text{-}Event]}
+     \item 
+     ~\qquad \lstinline|else {| \\
+     \textcolor{darklavender}{\code{\{ n  {\neq} 0 \wedge   \_^\star \}  }} 
+     \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
+    \item 
+     ~\qquad~\qquad \lstinline|addOneSugar();| \\
+     \textcolor{darklavender}{\code{\{n  {\neq} 0 \wedge  t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} 
+     \quad \siderule {\scriptsize [FV\text{-}Call]}
+     \item 
+     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
+     \textcolor{huntergreen}{\code{n  {\neq} 0   \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
+      \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: precondition checked.}}
+\\
+     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
+     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
+     \quad \siderule {\scriptsize [FV\text{-}Call]}
+      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
+      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }} 
+      \quad \siderule{\scriptsize [FV\text{-}If\text{-}Else]}
+      %\quad \siderule {\scriptsize [Normalization]}
+      \\
+       \item 
+       %\textcolor{mGray}{  \emph{(-TRS: check the  postcondition; Succeed, cf. \autoref{tab:rewriting_tree_send}-) }}\\
+       \textcolor{darkred}{\code{
+       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
+       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}  
+       \quad \textcolor{mGray}{\footnotesize  \emph{// TRS: postcondition checked, cf. \tabref{tab:rewriting_tree_send}. }}
+        \\ 
+        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
+        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\
+
+\end{enumerate}}
+
+     \end{minipage}
+
+      \caption{The forward verification example for method \code{send}. }\label{fig:forward_example}
+     % \vspace{-4mm}
+\end{figure}
+}
+
+The effects states (1) and (4) are obtained by initializing 
+\code{\effect_C} from the precondition, by the \code{[FV\text{-}Meth]} rule. 
+The effects states (5), (7), and (10) are obtained by  
+\code{[FV\text{-}If\text{-}Else]}, which adds the constraints 
+from the conditionals into the current effects state, 
+and unions the effects accumulated from two branches in the end. 
+The effects states (6) is obtained by \code{[FV\text{-}Event]}, 
+which concatenates the triggered singleton event to the 
+end of the current effects state.
+
+The intermediate effects states of (8) and (9) are obtained by \code{[FV\text{-}Call]}. 
+Before each function call, it invokes the TRS to check whether the current effects state 
+satisfies the precondition of the callee function. 
+If it is not satisfied, the verification fails; otherwise, 
+it concatenates the callee's postcondition to the current 
+effects state (the precondition check for step (8) is omitted here).
+
+The effects state (2) is obtained by \code{[FV\text{-}Timeout]}, 
+which adds a lower time-bound to the trace. 
+After these states transformations, steps (3) and (11) check the 
+satisfiability of the inferred effects against the declared 
+postcondition by invoking the TRS.
+
+Note that the prior effects in precondition are new regarding 
+the existing real-time verification.
+
+\subsection{The TRS}
+
+Our TRS is 
+%obligated to check the inclusions between \effectNameSyncEffs, which is 
+an extension of Antimirov and Mosses's algorithm. The rewriting system in {\cite{DBLP:journals/tcs/AntimirovM95}  
+decides inequalities of regular expressions (REs) through an iterated process of checking the inequalities of their 
+\emph{partial derivatives} \cite{antimirov1995partial}. There are two basic rules: 
+$\code{[DISPROVE]}$, which infers false from trivially inconsistent inequalities; and  
+$\code{[UNFOLD]}$, which applies \defref{RegularInclusion} to generate new inequalities.
+In detail, given \code{\Sigma} is the whole set of the alphabet, 
+\code{D_{\anyevent{A}}(r)} is the partial derivative of \code{r} w.r.t the event \code{\anyevent{A}}.
+
+\begin{definition}[REs Inequality]\label{RegularInclusion}  For REs \code{r} and \code{s}, \code{r \preceq s \Leftrightarrow \forall (\anyevent{A} \in \Sigma).\ D_{\anyevent{A}}(r) \preceq D_{\anyevent{A}}(s)}.
+\end{definition}
+
+\begin{definition}[\timedEffects\ Inclusion]\label{Inclusion}  %Let \code{\varrho} be the signal set. 
+For \timedEffects\ \code{\effect_1 } and \code{\effect_2}, 
+\code{\effect_1 { \CONTAIN} \effect_2 {\Leftrightarrow} \forall \anyevent{A}. \forall t {\geq} 0.\ D_{\anyevent{A} \mysharp  t}(\effect_1)  
+{\CONTAIN} D_{\anyevent{A} \mysharp  t}(\effect_2)}.
+\end{definition}
+%\in fst(\effect_1)
+
+Similarly, we defined the \defref{Inclusion} for unfolding the inclusions  
+between \timedEffects, where \code{D_{\anyevent{A}\mysharp  t}(\effect)} 
+is the partial derivative of \code{\effect} w.r.t the event 
+\anyevent{A} and the time variable \code{t}.
+
+%Adapting to the context of checking inclusions between \timedEffects, we extend the Antimirov algorithm with
+
+%The rule \code{[REOCCUR]} finds the syntactic identity, as a companion, of the current open goal, as a bud, from the internal proof tree \cite{DBLP:conf/tableaux/Brotherston05}.
+(We use \code{\textcolor{persianplum}{(\dagger)}} in \tabref{tab:rewriting_tree_send} to indicate such pairings.)
+
+%(introduce \code{t_L^1} and \code{t_L^2}, let \code{t_L^1 {+} t_L^2 {=} t_L}
+
+%(\code{\{Cook\} {\Rightarrow} \{Cook\}}, \code{t_L^1 {+} t_L^2 {<}3 {\Rightarrow} t_L^1 {<}3})
+
+Next, we continue with the step (11) in \figref{fig:forward_example}, to 
+demonstrate how the TRS handles arithmetic constraints and dependent values. 
+%We use the postcondition proving for function \code{main} as an example to briefly demonstrate the rewriting process. 
+As shown in \tabref{tab:rewriting_tree_send}, it automatically proves that the inferred effects of {\ttfamily{main}}
+ satisfy the declared postcondition. 
+%property \code{\effect_1  {=} 0{\leq} t {<}3 : \_\cdot(\{Cook\}\mysharp  t)\cdot\_^\star}, 
+%where \code{\effect_1} simply indicates that the signal \anyevent{Cook} needs to happen at the second event, and takes no more than \code{3} time units after the first event has completed; and \code{\_^\star} means we do not care the rest of the traces.
+We mark the rewriting rules (cf. \secref{sec:Entailment_Prover}) in \textcolor{mGray}{[gray]}.
+
+{
+\begin{table*}[ht]
+\centering
+     % \vspace{0mm}
+\caption{\label{tab:rewriting_tree_send} The inclusion proving example. 
+\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}
+
+\vspace{-1mm}
+\begin{adjustbox}{width=1\textwidth}
+ \Large\begin{tabular}[t]{l}
+  \hline\\
+
+  \code{(I):}\quad
+
+  {
+\begin{prooftree}
+\hypo{\text{\textcircled{4}}
+  \code{\siderule{[\code{PROVE}]}}
+}
+
+\infer[dashed]1[]{ \code{\textcolor {darkred}{n{=}0} \wedge \epsilon 
+\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \epsilon \mysharp t_r}}
+
+%\textcolor{blue}{\code{\pi_u : true}}
+\infer[dashed]1[{\textcircled{3}\siderule{[\code{UNFOLD}]}}]{ \code{ \textcolor {darkred}{n{=}0} \wedge \cancel{Sugar}
+\CONTAIN \textcolor {darkred}{t_r{\geq}0} \wedge \cancel{Sugar \mysharp t_r}}}
+
+\hypo{\qquad \code{(II)}}
+
+\infer[dashed]2[{\textcircled{2}\siderule{[\code{LHS\text{-}OR}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
+\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge \epsilon \mysharp t \cdot 
+ Sugar \mysharp t_l) } 
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \mysharp t_r  }
+
+\infer[dashed]1[{\textcircled{1}\siderule{[\code{RENAME}]}}]{\code{(\textcolor {darkred}{n{=}0} \wedge Sugar)\ \vee\ }
+\code{ (\textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1}  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
+\CONTAIN \effect_{post}^{addNSugar(n)}  }
+\end{prooftree}}
+\\~\\
+
+\hline \\
+\code{(II):} \quad\ \
+
+{\begin{prooftree}
+  \hypo{
+  \code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
+   \wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
+}  } 
+ }
+
+ \infer[dashed]1[{\textcircled{7}\siderule{[\code{PROVE}]}}]{ \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
+ \epsilon
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
+\wedge \epsilon}}
+
+ \infer[dashed]1[{\textcircled{6}\siderule{[\code{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1)}}]
+ { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1)}  \wedge 
+\cancel{ Sugar \mysharp t_l}
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} 
+\wedge \cancel{Sugar \mysharp t_r^1}}}
+
+ \infer[dashed]1[{\textcircled{5}\siderule{[\code{UNFOLD}]}} \textcolor{blue}{\code{\pi_u :  (t_r{=}t_r^1 {+}t)}}]
+ { \code{ \textcolor {darkred}{n  {\neq} 0  \wedge  t{>}1 \wedge t_l{\geq}(n\text{-}1) } \wedge \cancel{\epsilon \mysharp t} \cdot 
+ Sugar \mysharp t_l
+\CONTAIN \textcolor {darkred}{t_r{\geq}n} \wedge Sugar \cancel{\mysharp t_r}}}
+
+\end{prooftree}
+}
+
+\\~\\
+
+\hline
+
+\end{tabular}
+\end{adjustbox}
+      %      \vspace{0mm}
+\end{table*}
+}
+
+As shown in \tabref{tab:rewriting_tree_send}, step 
+\textcircled{1}, renames the time variables to avoid 
+the name clashes between the antecedent and the consequent.  
+Step \textcircled{2} splits the proof tree into two 
+branches, according to the different 
+arithmetic constraints, by rule  $\code{[LHS\text{-}OR]}$.
+
+In the first branch, step \textcircled{3} takes the rule 
+$\code{[UNFOLD]}$ to eliminate the head of the antecedent. 
+Step \textcircled{4} proves the inclusion, because 
+evidently the consequent \code{t_r {\geq} 0 \wedge \epsilon \mysharp t_r} 
+contains \code{epsilon} when \code{t_r{=}0}.
+
+In the second branch, step \textcircled{5} eliminates the 
+head of the antecedent, where the head is a time duration \code{\epsilon\mysharp t}. 
+Therefore the rule $\code{[UNFOLD]}$ subtract the time duration 
+from the consequent, leaving a fresh time variable \code{t_r^1} and 
+an unification constraint \textcolor{blue}{\code{\pi_u : t_r{=}t_r^1 {+}t}}. 
+Similarly, step \textcircled{6} eliminates the head 
+\code{\anyevent{Sugar}\mysharp t_l}, adding \textcolor{blue}{\code{t_l{=}t_r^1}} 
+to the unification constraints. 
+At the end of the rewriting, step \textcircled{7} manages to prove that 
+\code{\textcolor {darkred}{  t{>}1 \wedge t_l{\geq}(n\text{-}1) 
+\wedge  \textcolor{blue}{t_r{=}t_r^1 {+}t \wedge  t_l{=}t_r^1}  \Rightarrow t_r{\geq}n
+}  } \footnote{The proof obligations generated by the verifier are discharged using constraint solver Z3 \cite{DBLP:conf/tacas/MouraB08}.}; therefore, the proof succeed.
+
+%(\code{\{Go\} \Rightarrow \_})
+%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
+Termination is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using 
+\emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, cf.\ \tabref{tab:reoccur}.
+
+\subsection{Verifying the Fischer’s Mutual Exclusion Protocol}
+
+\begin{wrapfigure}{L}{0.51\columnwidth}
+  \vspace{-5mm}
+\begin{lstlisting}
+var x := -1; 
+var ct:= -1;
+
+void proc (int i) {
+  [x=-1] 
+  deadline(event["Update"(i)]{x:=i},d1);
+  delay (d2);
+  if (x=i) {
+    event["Critical"(i)]{ct:=i};
+    event["Exit"(i)]{ct:=-1; x:=-1};
+    proc (i);
+  } else {
+    proc (i);}}
+
+void main () 
+/*req: d1<d2/\emp
+  ens: true /\ (([ct=-1]\/[ct=x])^*) */ 
+{ proc(0) || proc(1) || proc(2); }
+\end{lstlisting}  
+  %\vspace{-1mm}
+  \caption{Fischer's mutually exclusion algorithm.}\label{fig:overview_ficher}
+    % \vspace{-2mm}
+\end{wrapfigure}
+
+\figref{fig:overview_ficher} presents the classical 
+Fischer's mutually exclusion algorithm. 
+where \code{d1} and \code{d2} are two integer constants
+ with \code{d1<d2}; 
+\code{x} and \code{ct} are global variables. The protocol is 
+modeled as 
+process protocol, which is the parallel composition of three 
+processes. Each of the three processes attempts to enter 
+the critical section when \code{x} is \code{-1}, i.e. no 
+other process is 
+currently attempting. Once the process is active, it sets \code{}{x} 
+to its identity \code{i} within \code{d1} time units (captured by \code{deadline(..., d1}). 
+Then it idles for \code{d2} time units (captured by \code{delay(d2)}) and then 
+checks whether \code{x} is still \code{i}. If so, 
+it enters the critical 
+section and leaves later. Otherwise, it restarts from the 
+beginning.
+
+We show the specification of \code{main} using \timedEffects, which
+restricts the relation between \code{d1} and \code{d2}. When 
+\code{d1<d2} is provided, it ensures a global state, i.e., the repeated trace, where the value of 
+\code{ct} is either \code{-1} or equals to \code{x}. The specification
+implies that this implementation is indeed mutual exclusive. 
+Our prototype system is able to soundly check such time-critical 
+algorithms. \secref{sec:Evaluation} presents the details about the implementation and evaluation.
+
+\section{Language and Specifications}
+\label{sec:LanguageSpecifications}
+
+\subsection{The Target Language}
+\label{subsec:Targetlanguage}
+
+To formulate the target language, we generalize the design of the real-time systems
+ into a core language \code{\timedL}, 
+ which provides the infrastructure for mutable variables and timed behavioral patterns, 
+ such as \emph{delay}, \emph{timeout}, \emph{deadline}. 
+We here formally define the syntax of \code{\timedL}, as shown in \figref{fig:code_language}
+
+{
+ % \vspace{-2mm}
+\begin{figure}[!ht]
+\renewcommand{\arraystretch}{1.1}
+\centering%\small
+  $
+  \begin{array}{lrcl}
+
+    \m{(Program)} &  \code{\mathcal{P} }&\code{  ::= }&
+    \code{%{datat^*}  \  
+   (\alpha^*, {meth^*})} 
+    \\
+
+    \m{(Basic\ Types)} &   \code{\iota} &\code{  ::=  }&
+     \code{int\ |\ bool\ |\ void}
+
+    \\
+%     \m{(Data\ Struct.)} &  \code{datat}&\code{  ::= }&
+ %    \code{\textbf{struct}\ d\ \{ {(t\ f)^*} \}}  
+ %   \\
+
+  \m{(Method\ Def.)} &  \code{meth}&\code{ ::= }&
+  \code{\iota\  mn  \ {(\iota\ x)^*}\ \{\textbf{req}\ \effect_{pre}\ \textbf{ens}\  \effect_{post}\} \ \{ e \}}
+  \\
+  \m{(Values)} & \code{v} &\code{  ::= } & ()\ |\ c \ | \ b \ |\ x\  
+  \\
+
+  \m{(Assignment)} &  \code{\alpha }&\code{  ::= }&
+  \code{x:=v} 
+ \\
+  \m{(Expressions)} &  \code{e}&\code{  ::= }&
+    \code{ v \ 
+    | \ \alpha \ | \ 
+    [b]\ e \ |\ mn({v^*}) \ }
+  \code{|  \ e_1;e_2\ | \ e_1 || e_2 \ 
+  |\ {if}\ b\ {then}\ e_1\ {else}\ e_2 \
+ }  \\
+
+ &   & & \code{
+  |\ \textbf{event} [\anyevent{A}(v, \alpha^*)] \ 
+  | \ \textbf{delay} [t] \ 
+  | \ e_1\ \textbf{interrupt} [t] \  e_2 \ 
+  }  \\
+
+  &   & & \code{
+    | \ e_1\ \textbf{timeout} [t] \  e_2 \ 
+    | \ e \ \textbf{deadline}  [t] \ 
+    | \ e \ \textbf{waituntil} [t]  \ 
+    }  \\
+
+    \m{(Real\text{-}Time\ Terms)}  & \code{t} &\code{  ::= }&
+    \code{ c
+    \ | \  x
+    \ | \  t_1{+}t_2
+    \ | \  t_1\text{-}t_2
+   }
+
+    \\
+    ~\\
+
+    \multicolumn{4}{c}{
+ % \code{k^\tau:constant\ of\ type\ \tau\ } 
+ % \qquad\quad
+\code{c  \in \mathbb{Z}}
+\qquad \qquad 
+\code{b  \in \mathbb{B}}
+\qquad \qquad  
+\code{x, mn  \in \textbf{var}}  
+\qquad \qquad 
+ \code{(Action\ labels)\ \anyevent{A}  \in \Sigma %\cup \{\tau\}
+%\qquad\ 
+%\m{(Time\ Bounds)}\ \code{d} \code{\in \mathbb{N}}    
+}   
+    }\\  
+    \hline
+  \end{array}  
+  $
+ \caption{A core first-order imperative language with timed constructs, \timedL.} 
+ \label{fig:code_language}
+
+\end{figure}
+}
+
+Here, \code{c} and \code{b} are for integer and Boolean constants, 
+ \code{mn} and \code{x} are for meta-variables.  
+ \textbf{var} represents the countably infinite set of arbitrary distinct identifiers.
+
+A program \code{\mathcal{P}} comprises a list of 
+global-variable initializations \code{\alpha^*} and 
+a list of 
+method declarations \code{{meth^*}}. 
+Here, we use the \code{*} superscript to denote a finite list (possibly empty) of items, for example, \code{{x^*}} refers to a list of variables, \code{x_1, ...,\ x_n}. 
+%Besides, \code{d} denotes the name of a user-defined data type, \code{f} denotes a field name. 
+Each method \code{meth} has a name \code{mn}, an expression-oriented body \code{e}, also is associated with a precondition  \code{\effect_{pre}} and a postcondition \code{\effect_{post}} (the syntax of effects specification \code{\effect} is given in \figref{fig:Syntax_of_Types_and_Effects}).
+The language allows each iterative loop to be optimized to an equivalent 
+tail-recursive method, where mutation on parameters is made visible 
+to the caller. 
+%The technique of translating away iterative loops is standard
+%\citeref{insa2015automatic} 
+%and is helpful
+
+Expressions comprise simple values \code{v};
+a guarded process is written as \code{[b]e} where if \code{b} is true, 
+then it behaves as \code{e}, else it idles until \code{b} becomes true; 
+%one-level field access \code{v.f} (rather than \code{v.f1.f2...} for the sake of simplicity), 
+%data structure allocation \code{\textbf{new}\ d({v^*})},  
+%local variable declaration \code{\alpha; e}, 
+method calls \code{mn({x^*})}; 
+%variable assignments \code{\alpha}; 
+%field update \code{v.f:=e}, 
+expression sequences \code{e_1;e_2};
+parallel composition \code{e_1 || e_2}, where \code{e_1} and \code{e_2} 
+may communicate via multi-party event synchronization or shared variables; 
+conditional expressions \code{{if}\ v\ {then}\ e_1\ {else}\ e_2}.
+
+The expression \code{ \textbf{event} [\anyevent{A}(v,  \alpha^*)] } 
+raises an event \anyevent{A}, which comes from the finite 
+set of event labels \code{\Sigma}. %or can be an invisible event, denoted by $\tau$. 
+Without loss of generality, events can be further parametrized with 
+one constant value \code{v} and a set of assignments \code{\alpha^*} upon 
+the mutable variables. %e.g. \code{\anyevent{a}.0} and  \code{\anyevent{a}}.1 are distinct two events. 
+%leading to infinite alphabet.
+%We assume that programs we use are well-typed conforming to basic types \code{\tau} (we take () as the \code{void} type).
+%Each events raising expression \code{\textbf{event}} is parametrized with an event, to trigger such a single event.
+
+%parametrized with \code{v}, 
+%and takes a set of 
+%assignment actions \code{\alpha^*}.
+
+Furthermore, a number of timed process constructs can be used to capture common 
+real-time system behavior patterns. Without loss of generality, we 
+assume \code{d} is a non-negative integer constant.  
+$\textbf{delay} [d]$ idles for exactly $d$ 
+time units.
+ In process $e_1\ \textbf{timeout} [d]\ e_2$, the first observable event of 
+$e_1$ shall occur before d time units elapse (since the process starts). 
+Otherwise, $e_2$ takes over control after exactly $d$ time units elapse. 
+Note that the usage of timeout in \figref{fig:Value_dependent_intro} is a 
+special case of the primitive presented here, where \code{e_1} never starts. 
+Process $\textbf{deadline} [d]\ e$ constraints $e$ to terminate before $d$ time units.
+
+In this setting, clock variables are 
+made implicit and hence they cannot be compared with each other 
+directly, which potentially allows efficient clock manipulation and 
+hence system verification.
+
+%
+
+\subsection{Semantics of the target language}
+\label{subsec:Targetlanguage_Semantics}
+
+In order to define the operational semantics of a system model, 
+we define the notion of a configuration, in \defref{sys_configuration}, to capture 
+the global system state during system execution.
+
+\begin{definition}[System configuration]\label{sys_configuration}
+A system configuration \code{\zeta} is a pair $(\env , e)$ where $\env$ is a variable valuation function and $e$ is an expression.
+\end{definition}
+
+A transition of the system is of the form $\zeta \xrightarrow[]{l} \zeta^\prime$ 
+where $\zeta$ and $\zeta^\prime$ are 
+the system configurations before and after the transition respectively. 
+%There are four type of the transition labels  :
+We adopt the following naming convention \cite{DBLP:conf/icfem/SunLDZ09} for the transition labels \code{l}: 
+(1) $t$, denoting a non-negative real integer; 
+(2) $\tau$, denoting an invisible event; % which do not make changes to the global valuation;
+(3) $\anyevent{A}$ is an observable event. 
+%and (4) $\sigma \in \Sigma\cup \{\tau\}$. 
+For example, $\zeta \xrightarrow[]{\text{t}} \zeta^\prime$ denotes a transition 
+of \code{t} time-units elapsing. 
+In the following, we present the firing rules which are associated with 
+the timed process constructs.
+
+\input{rules/op_delay.tex}
+
+The above captures behaviors of process \textbf{delay}[d]. 
+Rule \code{[delay_1]} states that the process may idle for 
+any amount of time as long as it is less than or equal to \code{d} time units; 
+Rule \code{[delay_2]} states that the process terminates immediately after 
+\code{d} becomes \code{0}.
+
+\input{rules/op_to.tex}
+
+If an observable event \anyevent{A} can be engaged by \code{e_1}, 
+then $e_1\ \textbf{timeout}[d]\ e_2$ becomes \code{e_1^\prime} (rule \code{[tot_1]}). 
+An invisible transition continues the waiting on \code{e_1} (rule \code{[tot_2]}). 
+If \code{e_1} may idle for less than or equal 
+to \code{d} time units, so is the composition (rule \code{[tot_3]}). 
+When \code{d} becomes \code{0}, 
+\code{e_2} takes over control by a silent transition (rule \code{[tot_4]}).
+
+\input{rules/op_ddl.tex}
+
+Intuitively, $\textbf{deadline}\  [d] \ e$ behaves exactly as 
+\code{e} except that it must terminate before \code{d} time units.
+
+\input{rules/op_gu.tex}
+
+The guarded process \code{[b]e} behaves as \code{e} when \code{b} is true, 
+otherwise it idles until \code{b} becomes true.
+
+{{\small\begin{flalign*}
+\code{\frac{
+  (\env,e_1) \xrightarrow[]{l} (\env^\prime,e_1^\prime) 
+}{(\env, e_1; e_2 ) \xrightarrow[]{l} (\env^\prime, e_1^\prime ; e_2)}\ [seq_1]} 
+\qquad
+\code{\frac{
+}{(\env, (); e_2 ) \xrightarrow[]{\tau} (\env, e_2)}\ [seq_2]} 
+\qquad
+\code{\frac{
+  (\env,e_1) \xrightarrow[]{l} (\env^\prime,e_1^\prime) 
+}{(\env, e_1 || e_2 ) \xrightarrow[]{l} (\env^\prime, e_1^\prime || e_2)}\ [par_1]} 
+\\ 
+  \code{\frac{
+    (\env,e_2) \xrightarrow[]{l} (\env^\prime,e_2^\prime) 
+  }{(\env, e_1 || e_2 ) \xrightarrow[]{l} (\env^\prime, e_1 || e_2^\prime)}\ [par_2]} 
+  \qquad \qquad 
+  \code{\frac{
+    (\env,e_1) \xrightarrow[]{t} (\env,e_1^\prime) 
+    \qquad 
+    (\env,e_2) \xrightarrow[]{t} (\env,e_2^\prime) 
+  }{(\env, e_1 || e_2 ) \xrightarrow[]{t} (\env, e_1^\prime || e_2^\prime)}\ [par_3]} 
+\end{flalign*}}}
+
+Rules \code{[seq_1]} and \code{[seq_2]} state that \code{e_1} takes the control 
+when it still can behave; then the control transfers to \code{e_2} when \code{e_1}
+terminates. Rules \code{[par_1]} and \code{[par_2]} state that in a parallel composition, 
+if any of \code{e_1} or \code{e_2} can proceed, they proceed on their own. Rule 
+\code{[par_3]} states that if both of the branches idle, they idle together.
+
+\subsection{The Specification Language}
+\label{subsec:Specification_language}
+
+We plant the effects specifications into the Hoare-style verification system, using \code{ es_{pre}} and \code{  es_{post} }  to capture the temporal pre/post 
+condition. %\code{es_{pre}} and the postcondition \code{es_{post}}.
+
+{
+    \vspace{0mm}
+\begin{figure*}[ht]
+\renewcommand{\arraystretch}{1.1}
+\centering
+  $
+  \begin{array}{rrcl}
+
+    \m{(Timed\ Effects)} &  \effect &\code{  ::= }&
+    \code{
+          {\pi} \wedge \es
+   \ | \ \effect_1 \vee \effect_2
+}
+    \\
+ \m{(Event \ Sequences)}  & \ \code{\es}   &\code{ ::=}&
+
+   \code{ \bot 
+   \  | \  \epsilon 
+    \ | \ \ev
+   \  | \ \es_1 \cdot \es_2
+    \ | \ \es_1 \vee \es_2
+    \ | \ \es_1 {||} \es_2
+    \ | \ \pi ? 
+      %    \  | \ \es_1 \times \es_2
+      \ | \ \es \mysharp  t 
+   \  | \  \es^\star
+}
+
+\\
+\m{(Events)} & \ev  &  ::=  & 
+\code{
+  \anyevent{A}(v, \alpha^*)
+    \ | \ \tau (\pi)
+    \ | \ \anynotevent{A} 
+    \ | \ \_  
+}
+
+\\
+
+    \m{(Pure)}  & \code{\code{{\pi}}}&\code{  ::= }&
+{ {True}}
+   \ |\  {False}
+   \ |\  {A(}{t_1, t_2}{)}
+  \  |\   {{\pi_1}}  \wedge  \code{{\pi}}_2
+   \ |\  {{\pi_1}} {\vee} \code{{\pi}}_2
+   \ |\  \neg\code{{\pi}}
+  \  |\   {{\pi_1}} {\Rightarrow} {{\pi_2}}
+  % \ |  \forall x. \code{{\pi}}
+  %s \ |  \exists x. \code{{\pi}}
+
+    \\
+
+    \m{(Real\text{-}Time\ Terms)}  & \code{t} &\code{  ::= }&
+    \code{ c
+    \ | \  x
+    \ | \  t_1{+}t_2
+    \ | \  t_1\text{-}t_2
+    %\ | \ k {\times} n
+   }
+
+    \\~\\
+    \multicolumn{4}{c}{
+     % \code{(Events)  \anyevent{A} ::\in \Sigma}   
+   %\qquad
+    \code{c \in \mathbb{Z}} 
+     \qquad \qquad 
+           \code{x  \in \textbf{var} } 
+           \qquad\qquad
+
+     \m{(Real\ Time\ Bound)}\ \code{\mysharp }
+     \qquad \qquad 
+        \m{(Kleene\ Star) \ \star}
+
+}\\     
+      \hline
+
+  \end{array}  
+  $ \\
+  \caption{Syntax of \timedEffects.}
+  \label{fig:Syntax_of_Types_and_Effects}
+  \vspace{0mm}
+\end{figure*}
+
+}
+
+The  syntax of the \timedEffects\ is formally defined in 
+\figref{fig:Syntax_of_Types_and_Effects} Effects is 
+ a conditioned event sequence \code{{\pi}\wedge es} or a disjunction of 
+ two effects $\effect_1 \vee \effect_2$.
+Timed sequences comprise \textit{nil} ($\bot $);
+ an empty trace $ \epsilon$;
+a single event \code{ev};
+ sequences concatenation \code{\es_1\cdot \es_2};
+disjunction  \code{\es_1\vee \es_2};
+parallel composition of two processes is written as \code{\es_1 || \es_2}, where \code{\es_1} and \code{\es_2} 
+may communicate via multi-party event synchronization or shared variables;
+a blocking waiting for a certain constraint to be satisfied \code{\pi ?}; 
+We introduce a new operator \code{\mysharp }, and the effects 
+\code{\es \mysharp t} represents that a trace takes real-time 
+\code{t} to complete, where \code{t} is a \emph{term}. 
+A timed sequence can be constructed by \code{\es^\star}, representing zero or 
+more times repetition of the trace \code{\es}.
+
+\anyevent{A}\code{(v, \alpha^*)} stands for an observable event with label 
+\anyevent{A}, parameterized by \code{v}, and the assignment operations \code{\alpha^*}; and 
+\code{\tau(\pi)} is an invisible event, which can be parameterized with a pure formula 
+\code{\pi}\footnote{The difference between 
+\code{\tau(\pi)} and \code{\pi?} is \code{\tau(\pi)} leads to false (\code{\bot}) if 
+\code{\pi} is not satisfied, whereas  \code{\pi?} waits until \code{\pi} is satisfied.}. 
+To make the specification more practical, events can also be 
+{\anynotevent{A}}, referring to those events which are not 
+labeled using \anyevent{A}; and a wildcard \code{\_}, which matches to all the events.
+
+We use \code{{\pi}} to denote a pure formula which captures the (Presburger) arithmetic conditions on terms or program parameters. 
+We use \code{{A(}{t_1, t_2}{)}} to represent atomic formulas of two terms (including $  {=},
+   \ {>},
+   \ {<},
+   \ {\geq}\ $ and $ {\leq} $).
+%e.g. the equality between constant 0 and an integer variable \code{x}.
+A term can be a constant integer value \code{c}, an integer variable \code{n} which is an input parameter of the program and can be constrained by a pure formula. 
+A term also allows simple computations of terms, \code{t_1{+}t_2} and \code{t_1\text{-}t_2}.
+To abstract the elapsed time, the default and implicit pure constraints of all the terms is to be greater or equal to  0.
+
+\subsection{Semantic Model of Timed Effects}
+\label{subsec:Specification_Semantics}
+
+To define the model, 
+\code{var} is the set of program variables, 
+\code{val} is the set of primitive values, 
+\code{\es} is the set of event sequences (or event multi-trees, per se), 
+indicating the sequencing constraints on temporal behaviors.
+
+Let \code{d, s, \varphi \models \effect} denote the model relation, i.e., 
+the effects \code{\effect} take \code{d} time units to complete; 
+the stack \code{s} and linear temporal events \code{\varphi} satisfy the 
+temporal effects \code{\effect}, with \code{d}, \code{s}, \code{\varphi} 
+from the following concrete domains: \code{d}  :\  \code{\mathbb{N}}, 
+\code{s}  :\  \code{var {\rightarrow} val } and \code{\varphi}   :\ \code{\es} \ .
+
+\begin{figure}[!ht]
+  %\vspace{-3mm}
+  \renewcommand{\arraystretch}{1.2}
+\small\begin{align*}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%     Disjunction        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models \effect_1 \vee \effect_2}  
+&\m{iff}\quad & \code{d, s, \varphi \models \effect_1 } \ 
+or\ \code{d, s, \varphi \models \effect_2 }  \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%         Empty          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s,  \varphi \models {\pi} \wedge  \epsilon}  
+&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
+{True} } \ and\  \code{ \varphi {=} [] }\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%         Event          %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi} \wedge \ev }  
+&\m{iff}\quad & \code{d{=}0}\ and  \ \code{\llbracket {\pi} \rrbracket_s {=}  
+{True} }\ and \ \varphi {=} [\ev]  \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%     Concatenate        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi} \wedge (\es_1\cdot \es_2)}  
+&\m{iff}\quad & \exists \code{\varphi_1,\varphi_2}. \  
+\code{ \varphi_1 {\lappend} \varphi_2 {=} \varphi}\ and\ 
+\exists \code{d_1,d_2}. \  
+\code{ d_1 {+} d_2 {=} d} \\
+&&& \qquad  s.t. \ \code{d_1, s, \varphi_1 {\models} {\pi}  \wedge \es_1 }
+\ and \ \code{d_2, s, \varphi_2 {\models} {\pi}  \wedge \es_2 }\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    disjunction         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi} \wedge (\es_1{\vee}\es_2)}  
+&\m{iff}\quad & 
+\code{d, s, \varphi \models {\pi}  \wedge \es_1 } 
+\ or\  
+\code{d, s, \varphi \models {\pi}  \wedge \es_2 } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    parallel         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi} \wedge (\ev_1 \cdot \es_1)||(\ev_2 \cdot \es_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models {\pi}  \wedge \ev_1 \cdot  (\es_1||(\ev_2 \cdot \es_2)) } 
+\ or\ \code{d, s, \varphi \models {\pi}  \wedge \ev_2 \cdot ((\ev_1 \cdot \es_1)||\es_2)  } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    parallel  2        %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi} \wedge (\ev\mysharp t_1) || (\epsilon \mysharp  t_2)}  
+&\m{iff}\quad & \code{d, s, \varphi \models {(\pi \wedge t_1 {\geq}t_2)} \wedge (\ev\mysharp t_1) } 
+\ or\ \code{d, s, \varphi \models {(\pi \wedge t_1 {<}t_2)}  \wedge (\ev\mysharp t_1) \cdot (\epsilon \mysharp  (t_2\text{-}t_1))  } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    block         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi} \wedge \pi_1 ? \es}  &\m{iff}\quad & 
+\code{\llbracket \pi_1  \rrbracket_{s} {=}  
+ {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge \es}\ or  \ 
+  \code{\llbracket \pi_1 \rrbracket_{s} {=}  
+{False} }, 
+\  \code{d, s, \varphi \models {\pi} \wedge \pi_1 ? \es}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    t times         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi}  \wedge \es\mysharp  t}  &\m{iff}\quad &
+ \code{\llbracket {\pi}  \wedge t {=} 0 \rrbracket_{s} {=}  
+ {True} }, \ \code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or  \\
+& & &  \code{\llbracket {\pi}\wedge t {>} 0 \rrbracket_{s} {=}  
+{True} }, 
+\  \exists \code{\es_1,\es_2}. \  \code{\es_1  \cdot  \es_2 {=} \es}, \  \m{fresh}\ t_1, t_2,\\
+&&& \qquad  s.t. \ \code{d, s, \varphi {\models} {(\pi 
+ \wedge  t_1{\geq}0 \wedge t_2{\geq}0  \wedge  t_1{+} t_2{=}t)} \wedge 
+(\es_1\mysharp t_1)  \cdot  (\es_2\mysharp t_2) } \\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    star         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+&\code{d, s, \varphi \models {\pi}\wedge \es^\star}  &\m{iff}\quad & 
+\code{d, s, \varphi \models {\pi}  \wedge  \epsilon}\ or \ 
+\code{d, s, \varphi \models {\pi}  \wedge \es  \cdot  \es^\star}\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%    FALSE         %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+& \code{d, s, \varphi \models false}  &\m{iff}\quad &
+ \code{\llbracket {\pi}  \rrbracket_{s} {=} {False} } \ or \ \code{\varphi {=} \bot }
+\end{align*}
+ % \vspace{-2mm}
+\caption{Semantics of \timedEffects.}
+\label{fig:Sementic}
+%\vspace{-2mm}
+\end{figure}
+
+As shown in \figref{fig:Sementic}, we define the semantics of our effects. 
+We use $\lappend$ to represent the append operation of two event sequences. 
+We use $[]$ to describe the empty sequence, \code{[\ev]} to represent 
+the sequence that only contains one singleton event. 
+Notice that, except for the traces constructed by \code{\mysharp}, simple events 
+are taken to be happening in instant time.
+
+\bibliographystyle{IEEEtranN}
 \bibliography{references}
-%% Citation style
-%% Note: author/year citations are required for papers published as an
-%% issue of PACMPL.
-
-%%
-%% If your work has an appendix, this is the place to put it.
-\appendix
 
